### 2017-02-14 SRO_Retest_Analyses.Rmd
First commit

---
title: 'Self Regulation Ontology Retest Data: Initial Exploration'
output:
  html_notebook: default
  pdf_document: default
---

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
sem <- function(x) {sd(x) / sqrt(length(x))}
```

Load original data
```{r}
test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/variables_exhaustive.csv')
```

Load retest data
```{r}
retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/variables_exhaustive.csv')
```

Quick check to make sure there isn't anything weird with anonymization of retest data

```{r}
last_lookup <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_Data_NewApi/retest_worker_lookup.json')

old_lookup1 <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_Data_NewApi/old/worker_lookup_3.json')

old_lookup2 <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_Data_NewApi/old/worker_lookup_8.json')

process_lookup <- function(lookup_json){
  lookup_json <- data.frame(unlist(lookup_json))
  lookup_json$sub_id <- as.character(row.names(lookup_json))
  row.names(lookup_json) <- seq(1:nrow(lookup_json))
  names(lookup_json)[1] <- 'worker_id'
  lookup_json$worker_id <- as.character(lookup_json$worker_id)
  lookup_json$complete <- ifelse(lookup_json$worker_id == lookup_json$sub_id, 0, 1)
  lookup_json <- lookup_json %>% arrange(-complete, sub_id)
  return(lookup_json)
}

last_lookup <- process_lookup(last_lookup)
old_lookup1 <- process_lookup(old_lookup1)
old_lookup2 <- process_lookup(old_lookup2)

old_lookup1[old_lookup1$complete == 1, 'worker_id'] == last_lookup[1:68, 'worker_id'] 
old_lookup2[old_lookup2$complete == 1, 'worker_id'] == last_lookup[1:113, 'worker_id']

rm(last_lookup, old_lookup1, old_lookup2)
```

Extract retest participants
```{r}
test_worker_lookup <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_Data_NewApi/worker_lookup.json')

retest_worker_lookup <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_Data_NewApi/retest_worker_lookup.json')

#Process full lookup tables for both datasets
test_worker_lookup <- process_lookup(test_worker_lookup)
retest_worker_lookup <- process_lookup(retest_worker_lookup)

#Process sub_id columns in the data dataframes
retest_data$X <- as.character(retest_data$X)
test_data$X <- as.character(test_data$X)

names(retest_data)[1] <- 'sub_id'
names(test_data)[1] <- 'sub_id'

#Trim lookup tables to only include those we have data for
retest_worker_lookup <- retest_worker_lookup[retest_worker_lookup$sub_id %in% retest_data$sub_id,]

test_worker_lookup <- test_worker_lookup[test_worker_lookup$sub_id %in% test_data$sub_id,]

#Are all retest workers in test data?
retest_worker_lookup$worker_id %in% test_worker_lookup$worker_id
```

One retest participant is not in test data. Remove that subject from lookup table and from retest_data
```{r}
retest_worker_lookup <- retest_worker_lookup[retest_worker_lookup$worker_id %in% test_worker_lookup$worker_id,]

retest_data <- retest_data[retest_data$sub_id %in% retest_worker_lookup$sub_id,]
```

Id match df
```{r}
id_match_df <- merge(retest_worker_lookup, test_worker_lookup, by='worker_id', all.x=T)

id_match_df <- id_match_df %>%
  select(-complete.x, -complete.y) %>%
  rename(retest_sub_id = sub_id.x, test_sub_id = sub_id.y) %>%
  arrange(retest_sub_id)

sub_id_lookup <- id_match_df %>% select(-worker_id)
write.csv(sub_id_lookup, 'sub_id_lookup.csv')
rm(sub_id_lookup)
```

Extract test data for retest subjects, add worker_id column to both datasets and arrange by worker_id, check if the rows match
```{r}
test_data <- merge(id_match_df, test_data, by.x='test_sub_id', by.y='sub_id', all.x=T)
retest_data <- merge(id_match_df, retest_data, by.x='retest_sub_id', by.y='sub_id', all.x=T)
test_data <- test_data %>% arrange(worker_id)
retest_data <- retest_data %>% arrange(worker_id)
test_data$worker_id == retest_data$worker_id
```

Drop columns from original data that are not in retest data

Retest data columns that are not in the original data:

```{r}
names(retest_data)[names(retest_data) %in% names(test_data) == FALSE]
```

Test data columns that are not in the retest data:
(as expected; three by two is not added yet)
```{r}
names(test_data)[names(test_data) %in% names(retest_data) == FALSE]
```

Datasets with only matching columns

```{r}
all_columns <- unique(c(names(test_data), names(retest_data)))

matching_columns <- c()
for(i in 1:length(all_columns)){
  if(all_columns[i] %in% names(test_data) & all_columns[i] %in% names(retest_data)){
    matching_columns <- c(matching_columns, all_columns[i])
  }
}

matching_retest_data <- retest_data[,matching_columns]
matching_test_data <- test_data[,matching_columns]
```

Get list of test retest correlations

TODO: write a nicer of getting rid of non numeric columns

```{r}
matching_dv_columns <- c()
for(i in 1:length(matching_columns)){
  if(is.numeric(matching_test_data[,matching_columns[i]]) & is.numeric(matching_test_data[,matching_columns[i]])){
    matching_dv_columns <- c(matching_dv_columns, matching_columns[i])
  }
}

cor_df <- data.frame(pearson = rep(NA, length(matching_dv_columns)), spearman = rep(NA, length(matching_dv_columns)))

row.names(cor_df) <- matching_dv_columns

for(i in 1:length(matching_dv_columns)){
  cor_df[matching_dv_columns[i], 'pearson'] <- cor(matching_test_data[,matching_dv_columns[i]], matching_retest_data[,matching_dv_columns[i]], method = 'pearson', use = "pairwise.complete.obs")
  cor_df[matching_dv_columns[i], 'spearman'] <- cor(matching_test_data[,matching_dv_columns[i]],matching_retest_data[,matching_dv_columns[i]], method = 'spearman', use = "pairwise.complete.obs")
}

write.csv(cor_df,'cor_df.csv')

ggplot(cor_df, aes(pearson))+
  geom_histogram()+
  theme_bw()

ggplot(cor_df, aes(spearman))+
  geom_histogram()+
  theme_bw()
```

 Distribution of each variable

 Completion times/days

 - First data release email esp to ASU
 - Send the spreadsheet with meaningul variables + demographics
 - Fix the worker id's not sharing

 Rank order correlations
 Separately for tasks vs. surveys
 Mean reliabilities for different kinds of variables (e.g. drift rates and NDs; separately for EX and HDDM; subtraction vs basic variables - single vs. multiple)
 Can you get the factor structure for the retest
 step 1:Ttest on all measures of T1 for people w and without retest
 step2 : efa on the people you don't have retest on and then predict how well this holds up for people w retest on t1 and on t2
T1 comparison for people who came back vs didn't (of all that are invited)

### 2017-02-14 SRO_Retest_Analyses.Rmd
working on analyses

@@
 
-Quick check to make sure there isn't anything weird with anonymization of retest data
-
+Function to process lookup table
 ```{r}
-last_lookup <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_Data_NewApi/retest_worker_lookup.json')
-
-old_lookup1 <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_Data_NewApi/old/worker_lookup_3.json')
-
-old_lookup2 <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_Data_NewApi/old/worker_lookup_8.json')
-
 process_lookup <- function(lookup_json){
@@
 }
-
-last_lookup <- process_lookup(last_lookup)
-old_lookup1 <- process_lookup(old_lookup1)
-old_lookup2 <- process_lookup(old_lookup2)
-
-old_lookup1[old_lookup1$complete == 1, 'worker_id'] == last_lookup[1:68, 'worker_id'] 
-old_lookup2[old_lookup2$complete == 1, 'worker_id'] == last_lookup[1:113, 'worker_id']
-
-rm(last_lookup, old_lookup1, old_lookup2)
 ```
 
-Extract retest participants
+Extract retest participants from test data
+
 ```{r}
-test_worker_lookup <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_Data_NewApi/worker_lookup.json')
-
-retest_worker_lookup <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_Data_NewApi/retest_worker_lookup.json')
+test_worker_lookup <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/Local/worker_lookup.json')
 
@@
 test_worker_lookup <- process_lookup(test_worker_lookup)
-retest_worker_lookup <- process_lookup(retest_worker_lookup)
 
@@
 
-#Trim lookup tables to only include those we have data for
-retest_worker_lookup <- retest_worker_lookup[retest_worker_lookup$sub_id %in% retest_data$sub_id,]
-
+#Trim lookup table to only include those we have data for
 test_worker_lookup <- test_worker_lookup[test_worker_lookup$sub_id %in% test_data$sub_id,]
 
-#Are all retest workers in test data?
-retest_worker_lookup$worker_id %in% test_worker_lookup$worker_id
+#Replace worker_id's in retest_data with original sub_id's 
+correct_subids <- function(row, lookup_table){
+  sub_id = row$sub_id
+  if(sub_id %in% lookup_table$worker_id){
+    index = which(sub_id == lookup_table$worker_id)
+    sub_id = lookup_table$sub_id[index]
+    row$sub_id = sub_id
+  }
+  return(row)
+}
+
+retest_data <- retest_data %>%
+  group_by(sub_id) %>%
+  do(correct_subids(.,test_worker_lookup))
+
+#Are all retest subjects in test_data? No. 
+sum(retest_data$sub_id %in% test_data$sub_id) == nrow(retest_data)
+
+#Who is missing?
+retest_data$sub_id[which(retest_data$sub_id %in% test_data$sub_id == FALSE)]
 ```
 
-One retest participant is not in test data. Remove that subject from lookup table and from retest_data
+One retest participant is not in test data. Remove that subject from retest_data for now
 ```{r}
-retest_worker_lookup <- retest_worker_lookup[retest_worker_lookup$worker_id %in% test_worker_lookup$worker_id,]
+retest_data <- retest_data[retest_data$sub_id %in% test_data$sub_id,]
 
-retest_data <- retest_data[retest_data$sub_id %in% retest_worker_lookup$sub_id,]
+retest_data
 ```
 
-Id match df
+Extract test data for retest subjects
 ```{r}
-id_match_df <- merge(retest_worker_lookup, test_worker_lookup, by='worker_id', all.x=T)
+retest_subs_test_data <- test_data[test_data$sub_id %in% retest_data$sub_id,]
 
-id_match_df <- id_match_df %>%
-  select(-complete.x, -complete.y) %>%
-  rename(retest_sub_id = sub_id.x, test_sub_id = sub_id.y) %>%
-  arrange(retest_sub_id)
+rest_subs_test_data <- test_data[test_data$sub_id %in% retest_data$sub_id == FALSE,]
 
-sub_id_lookup <- id_match_df %>% select(-worker_id)
-write.csv(sub_id_lookup, 'sub_id_lookup.csv')
-rm(sub_id_lookup)
-```
+#Arrange datasets of same size by sub_id
+retest_data = retest_data %>% arrange(sub_id)
+retest_subs_test_data = retest_subs_test_data %>% arrange(sub_id)
 
-Extract test data for retest subjects, add worker_id column to both datasets and arrange by worker_id, check if the rows match
-```{r}
-test_data <- merge(id_match_df, test_data, by.x='test_sub_id', by.y='sub_id', all.x=T)
-retest_data <- merge(id_match_df, retest_data, by.x='retest_sub_id', by.y='sub_id', all.x=T)
-test_data <- test_data %>% arrange(worker_id)
-retest_data <- retest_data %>% arrange(worker_id)
-test_data$worker_id == retest_data$worker_id
+#CHECK IF EVERYTHING IS ORDERED RIGHT
+retest_subs_test_data$sub_id == retest_data$sub_id
 ```
@@
 
-Retest data columns that are not in the original data:
+Are there any columns in retest data columns that are not in the original data: No.
 
 ```{r}
-names(retest_data)[names(retest_data) %in% names(test_data) == FALSE]
+names(retest_data)[names(retest_data) %in% names(retest_subs_test_data) == FALSE]
 ```
 
-Test data columns that are not in the retest data:
-(as expected; three by two is not added yet)
+Test data columns that are not in the retest data: Two stage hasn't been fixed yet.
+
 ```{r}
-names(test_data)[names(test_data) %in% names(retest_data) == FALSE]
+names(retest_subs_test_data)[names(retest_subs_test_data) %in% names(retest_data) == FALSE]
 ```
@@
 ```{r}
-all_columns <- unique(c(names(test_data), names(retest_data)))
+all_columns <- unique(c(names(retest_data), names(retest_subs_test_data)))
 
@@
 for(i in 1:length(all_columns)){
-  if(all_columns[i] %in% names(test_data) & all_columns[i] %in% names(retest_data)){
+  if(all_columns[i] %in% names(retest_data) & all_columns[i] %in% names(retest_subs_test_data)){
     matching_columns <- c(matching_columns, all_columns[i])
@@
 
-matching_retest_data <- retest_data[,matching_columns]
-matching_test_data <- test_data[,matching_columns]
+retest_data <- retest_data[,matching_columns]
+retest_subs_test_data <- retest_subs_test_data[,matching_columns]
 ```
@@
  - Send the spreadsheet with meaningul variables + demographics
- - Fix the worker id's not sharing
 

### 2017-02-15 SRO_Retest_Analyses.Rmd
cont working on initial retest analyses

@@
 sem <- function(x) {sd(x) / sqrt(length(x))}
+options(digits = 4)
 ```
@@
 ```{r}
+retest_data <- as.data.frame(retest_data)
+retest_subs_test_data <- as.data.frame(retest_subs_test_data)
 matching_dv_columns <- c()
 for(i in 1:length(matching_columns)){
-  if(is.numeric(matching_test_data[,matching_columns[i]]) & is.numeric(matching_test_data[,matching_columns[i]])){
+  if(is.numeric(retest_data[,matching_columns[i]]) & is.numeric(retest_subs_test_data[,matching_columns[i]])){
     matching_dv_columns <- c(matching_dv_columns, matching_columns[i])
@@
 for(i in 1:length(matching_dv_columns)){
-  cor_df[matching_dv_columns[i], 'pearson'] <- cor(matching_test_data[,matching_dv_columns[i]], matching_retest_data[,matching_dv_columns[i]], method = 'pearson', use = "pairwise.complete.obs")
-  cor_df[matching_dv_columns[i], 'spearman'] <- cor(matching_test_data[,matching_dv_columns[i]],matching_retest_data[,matching_dv_columns[i]], method = 'spearman', use = "pairwise.complete.obs")
+  cor_df[matching_dv_columns[i], 'pearson'] <- cor(retest_data[,matching_dv_columns[i]], retest_subs_test_data[,matching_dv_columns[i]], method = 'pearson', use = "pairwise.complete.obs")
+  cor_df[matching_dv_columns[i], 'spearman'] <- cor(retest_data[,matching_dv_columns[i]],retest_subs_test_data[,matching_dv_columns[i]], method = 'spearman', use = "pairwise.complete.obs")
 }
+```
 
-write.csv(cor_df,'cor_df.csv')
-
+Distribution of Pearson correlations
+```{r}
 ggplot(cor_df, aes(pearson))+
@@
   theme_bw()
+```
 
+Distribution of spearman correlations
+```{r}
 ggplot(cor_df, aes(spearman))+
@@
   theme_bw()
+```
+
+Add column to tasks vs. surveys in correlation table
+
+```{r}
+cor_df$dv = row.names(cor_df)
+row.names(cor_df) = seq(1:nrow(cor_df))
+cor_df$task = 'task'
+cor_df[grep('survey', cor_df$dv), 'task'] = 'survey'
+```
+
+Distributions of correlations by task vs. survey
+```{r}
+cor_df %>%
+  gather(key, value, -dv, -task) %>%
+  ggplot(aes(value))+
+  geom_histogram()+
+  theme_bw()+
+  facet_wrap(key~task)
+```
+
+Rank order correlations
+For tasks
+```{r}
+cor_df %>%
+  filter(task == 'task') %>%
+  select(dv, spearman, pearson) %>%
+  arrange(-pearson, -spearman)
+```
+
+Mean reliability for surveys
+```{r}
+cor_df %>%
+  filter(task == 'task') %>%
+  select(dv, spearman, pearson) %>%
+  arrange(-pearson, -spearman) %>%
+  summarise(mean_pearson = mean(pearson),
+            mean_spearman = mean(spearman))
+```
+
+For surveys
+
+Note: Holt and Laury test-retest is pretty terrible. In previous data it was ~.35. Should check to see if there is a coding error there.
+```{r}
+cor_df %>%
+  filter(task == 'survey') %>%
+  select(dv, spearman, pearson) %>%
+  arrange(-pearson, -spearman)
+```
+
+Mean reliability for surveys
+```{r}
+cor_df %>%
+  filter(task == 'survey') %>%
+  select(dv, spearman, pearson) %>%
+  arrange(-pearson, -spearman) %>%
+  summarise(mean_pearson = mean(pearson),
+            mean_spearman = mean(spearman))
+```
+
+Drift diffusion variables: raw vars vs. EZ vs. hddm
+
+Mean reliabilities for different kinds of variables (e.g. drift rates and NDs; separately for EZ and HDDM; subtraction vs basic variables - single vs. multiple)
+```{r}
+cor_df$dv
 ```
@@
 
- Rank order correlations
- Separately for tasks vs. surveys
- Mean reliabilities for different kinds of variables (e.g. drift rates and NDs; separately for EX and HDDM; subtraction vs basic variables - single vs. multiple)
  Can you get the factor structure for the retest

### 2017-02-15 SRO_Retest_Analyses.Rmd
cont working on retest exploration

@@
 
+Data cleaning for efa
+```{r}
+#read in only meaningful vars
+meaningful_var_test <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_clean.csv')
+
+meaningful_var_retest <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/meaningful_variables_clean.csv')
+
+#Process sub_id columns in the data dataframes
+meaningful_var_retest$X <- as.character(meaningful_var_retest$X)
+meaningful_var_test$X <- as.character(meaningful_var_test$X)
+
+names(meaningful_var_retest)[1] <- 'sub_id'
+names(meaningful_var_test)[1] <- 'sub_id'
+
+#Clean and subset dfs as before
+meaningful_var_retest <- meaningful_var_retest %>%
+  group_by(sub_id) %>%
+  do(correct_subids(.,test_worker_lookup))
+
+#Are all retest subjects in test_data? No. 
+sum(meaningful_var_retest$sub_id %in% meaningful_var_test$sub_id) == nrow(meaningful_var_retest)
+
+#Who is missing?
+meaningful_var_retest$sub_id[which(meaningful_var_retest$sub_id %in% meaningful_var_test$sub_id == FALSE)]
+
+#Remove sub w missing test data from retest data
+retest_data_mngf <- meaningful_var_retest[meaningful_var_retest$sub_id %in% meaningful_var_test$sub_id,]
+
+#Extract test data for subs w retest data
+retest_subs_test_mngf <- meaningful_var_test[meaningful_var_test$sub_id %in% meaningful_var_retest$sub_id,]
+
+#Extract test data for subs without retest data (efa df)
+rest_subs_test_mngf <- meaningful_var_test[meaningful_var_test$sub_id %in% meaningful_var_retest$sub_id == FALSE,]
+
+#Arrange datasets of same size by sub_id
+retest_data_mngf = retest_data_mngf %>% arrange(sub_id)
+retest_subs_test_mngf = retest_subs_test_mngf %>% arrange(sub_id)
+
+#CHECK IF EVERYTHING IS ORDERED RIGHT
+retest_subs_test_mngf$sub_id == retest_data_mngf$sub_id
+```
+
+Checking columns for efa:
+NEED TO RESOLVE SOME DIFFERENCES IN MEANINGFUL VARS BETWEEN THE TWO DATASETS
+```{r}
+#Check columns 
+names(retest_data_mngf)[names(retest_data_mngf) %in% names(retest_subs_test_mngf) == FALSE]
+
+names(retest_subs_test_mngf)[names(retest_subs_test_mngf) %in% names(retest_data_mngf) == FALSE]
+
+#Subset datasets with only matching columns
+all_columns_mngf <- unique(c(names(retest_data_mngf), names(retest_subs_test_mngf)))
+
+matching_columns_mngf <- c()
+for(i in 1:length(all_columns_mngf)){
+  if(all_columns_mngf[i] %in% names(retest_data_mngf) & all_columns_mngf[i] %in% names(retest_subs_test_mngf)){
+    matching_columns_mngf <- c(matching_columns_mngf, all_columns_mngf[i])
+  }
+}
+
+retest_data_mngf <- retest_data_mngf[,matching_columns_mngf]
+retest_subs_test_mngf <- retest_subs_test_mngf[,matching_columns_mngf]
+rest_subs_test_mngf <- rest_subs_test_mngf[,matching_columns_mngf]
+
+#standardize all vars going in to factor analysis
+rest_subs_test_mngf_z <- rest_subs_test_mngf
+
+for(i in 1:length(rest_subs_test_mngf)){
+  if(names(rest_subs_test_mngf)[i] == 'sub_id'){
+    rest_subs_test_mngf_z$sub_id = rest_subs_test_mngf$sub_id
+  }
+  else{
+    rest_subs_test_mngf_z[,names(rest_subs_test_mngf)[i]] = scale(rest_subs_test_mngf[,i])
+  }
+}
+```
+
+Efa on subjects from original dataset withOUT retest data (using meaningful vars only)
+```{r}
+unrotated <- efaUnrotate(rest_subs_test_mngf_z, nf=3, varList=names(rest_subs_test_mngf_z)[-1], estimator="mlr")
+
+summary(unrotated, std=TRUE)
+inspect(unrotated, "std")
+```
+
+```{r}
+library(psych)
+corMat <- cor(rest_subs_test_mngf_z)
+solution <- fa(r = corMat, nfactors = 2, rotate = "oblimin", fm = "pa")
+```
+
 Drift diffusion variables: raw vars vs. EZ vs. hddm
@@
  step2 : efa on the people you don't have retest on and then predict how well this holds up for people w retest on t1 and on t2
+
 T1 comparison for people who came back vs didn't (of all that are invited)

### 2017-02-15 SRO_Retest_Analyses.Rmd
cont working on retest exploration

@@
 library(jsonlite)
+library(lavaan)
+library(semTools)
+library(psych)
+library(GPArotation)
 sem <- function(x) {sd(x) / sqrt(length(x))}
@@
 
-Distribution of Pearson correlations
+Distribution of all Pearson correlations
 ```{r}
@@
 
-Distribution of spearman correlations
+Distribution of all Spearman correlations
 ```{r}
@@
 Distributions of correlations by task vs. survey
+Task reliability distributions looks alsmost bimodal. Should figure out whether the lower ones are specific tasks or if they are certain kinds of vars (e.g. certain ddm parameters)
 ```{r}
@@
 ```
+
+Distribution of each variable
+```{r}
+#Function to check if the variables that went in to cor_df have normal distributions
+
+diff_from_normal <- function(col){
+  return(shapiro.test(col)$p.value < 0.05)
+}
+```
+
+Check distributions of retest data
+```{r}
+dist_retest_data <- as.data.frame(apply(retest_data[,matching_dv_columns], 2, diff_from_normal))
+names(dist_retest_data) <- c('not_normal')
+dist_retest_data$dv <- row.names(dist_retest_data)
+row.names(dist_retest_data) <- seq(1:nrow(dist_retest_data))
+dist_retest_data = dist_retest_data %>% select(dv, not_normal)
+```
+
+Check distributions of test data (for subjects who have retest data - restricting here since there are the subsets of data that went in to the correlation matrix)
+```{r}
+dist_retest_subs_test_data <- as.data.frame(apply(retest_subs_test_data[,matching_dv_columns], 2, diff_from_normal))
+names(dist_retest_subs_test_data) <- c('not_normal')
+dist_retest_subs_test_data$dv <- row.names(dist_retest_subs_test_data)
+row.names(dist_retest_subs_test_data) <- seq(1:nrow(dist_retest_subs_test_data))
+dist_retest_subs_test_data = dist_retest_subs_test_data %>% select(dv, not_normal)
+```
+
+What proportion is not normal?
+```{r}
+sum(dist_retest_data$not_normal)/nrow(dist_retest_data)
+```
+
+```{r}
+sum(dist_retest_subs_test_data$not_normal)/nrow(dist_retest_subs_test_data)
+```
+
+Are the same vars that are not normally distributed in the retest data not normal in test data as well?
+List of variables that have different distributions in the two time points (shown here is whether they are normally distributed in the retest data)
+A majority of them are drift diffusion parameters (but note that these vars are overrepresented to begin with).
+```{r}
+dist_retest_data[which(dist_retest_data$not_normal != dist_retest_subs_test_data$not_normal),]
+```
+
+Transform non normal vars
+Transform both retest and test data if not normally distributed in either. 
+Order of transformations tried: log and sqrt
+```{r}
+transform_dv_df = data.frame(dv = c(), transform = c(), not_normal = c())
+#check if normal
+diff_from_normal(retest_data[,2])
+diff_from_normal(log(retest_data[,2]))
+diff_from_normal(sqrt(retest_data[,2]))
+#if yes stop and record transformation = none
+#if transform: log
+#check if normal
+#if yes stop and record transformation = log
+#if no transform: sqrt
+
+```
+
+Drift diffusion variables: raw vars vs. EZ vs. hddm
+
+Mean reliabilities for different kinds of variables (e.g. drift rates and NDs; separately for EZ and HDDM; subtraction vs basic variables - single vs. multiple)
+```{r}
+```
+
+--------------------------------
+
+Can you get the factor structure for the retest
+step 1:Ttest on all measures of T1 for people w and without retest
+```{r}
+
+```
+
+step2 : efa on the people you don't have retest on and then predict how well this holds up for people w retest on t1 and on t2
 
@@
 }
+
+rest_subs_test_mngf_z <- as.data.frame(rest_subs_test_mngf_z)
 ```
@@
 ```{r}
-library(psych)
-corMat <- cor(rest_subs_test_mngf_z)
-solution <- fa(r = corMat, nfactors = 2, rotate = "oblimin", fm = "pa")
+corMat <- rest_subs_test_mngf_z %>% select(-sub_id) %>% cor(.,use = 'complete.obs')
+
+solution <- fa(r = corMat, nfactors = 3, rotate = "oblimin", fm = "pa")
 ```
 
-Drift diffusion variables: raw vars vs. EZ vs. hddm
-
-Mean reliabilities for different kinds of variables (e.g. drift rates and NDs; separately for EZ and HDDM; subtraction vs basic variables - single vs. multiple)
 ```{r}
-cor_df$dv
+solution
 ```
-
-Distribution of each variable
 
@@
 
- Can you get the factor structure for the retest
- step 1:Ttest on all measures of T1 for people w and without retest
- step2 : efa on the people you don't have retest on and then predict how well this holds up for people w retest on t1 and on t2
-
 T1 comparison for people who came back vs didn't (of all that are invited)

### 2017-02-21 SRO_Retest_Analyses.Rmd
cont working on retest exploration

--- 2017-02-15 SRO_Retest_Analyses.Rmd
@@
   do(correct_subids(.,test_worker_lookup))
+```
 
-#Are all retest subjects in test_data? No. 
+Are all retest subjects in test_data? No. 
+```{r}
 sum(retest_data$sub_id %in% test_data$sub_id) == nrow(retest_data)
+```
 
-#Who is missing?
+Who is missing?
+```{r}
 retest_data$sub_id[which(retest_data$sub_id %in% test_data$sub_id == FALSE)]
@@
 retest_subs_test_data <- as.data.frame(retest_subs_test_data)
+
 matching_dv_columns <- c()
+
 for(i in 1:length(matching_columns)){
@@
 
-Distribution of Pearson correlations
+Distribution of all Pearson and Spearman correlations
 ```{r}
-ggplot(cor_df, aes(pearson))+
+cor_df %>%
+  gather(key, value) %>%
+  ggplot(aes(value))+
   geom_histogram()+
-  theme_bw()
-```
-
-Distribution of spearman correlations
-```{r}
-ggplot(cor_df, aes(spearman))+
-  geom_histogram()+
-  theme_bw()
+  theme_bw()+
+  facet_wrap(~key)
 ```
@@
 Distributions of correlations by task vs. survey
+
+Survey reliabilities are noticably higher than task reliabilities.
+
+Task reliability distributions looks alsmost bimodal. **Should figure out whether the lower ones are specific tasks or if they are certain kinds of vars (e.g. certain ddm parameters)**
 ```{r}
@@
 
-Mean reliability for surveys
+Mean reliability for tasks
 ```{r}
@@
   summarise(mean_pearson = mean(pearson),
-            mean_spearman = mean(spearman))
+            mean_spearman = mean(spearman),
+            num_vars = n())
 ```
@@
   summarise(mean_pearson = mean(pearson),
-            mean_spearman = mean(spearman))
+            mean_spearman = mean(spearman),
+            num_vars = n())
 ```
+
+Distribution of each variable
+
+Check if the variables that went in to the correlation matrix have normal distributions since at least the Pearson correlations depend on this assumption.
+If not transform data columns in both retest and test data and calculate a new correlation df.
+
+Function to check if the variables that went in to cor_df have normal distributions
+```{r}
+diff_from_normal <- function(col){
+  return(shapiro.test(col)$p.value < 0.05)
+}
+```
+
+Check distributions of retest data
+
+The smaller meaningful vars have been somewhat cleaned. So far in this notebook we looked at all the vars in their rawest form.
+
+Create and organize new df where distribution of vars data is stored.
+First for retest data only; then for test data for subjects who have retest data - restricting here since these are the subsets of data that went in to the correlation matrix.
+Merge and cleanup
+```{r}
+dist_retest_data <- as.data.frame(apply(retest_data[,matching_dv_columns], 2, diff_from_normal))
+names(dist_retest_data) <- c('retest_not_normal')
+dist_retest_data$dv <- row.names(dist_retest_data)
+row.names(dist_retest_data) <- seq(1:nrow(dist_retest_data))
+dist_retest_data = dist_retest_data %>% select(dv, retest_not_normal)
+
+dist_retest_subs_test_data <- as.data.frame(apply(retest_subs_test_data[,matching_dv_columns], 2, diff_from_normal))
+names(dist_retest_subs_test_data) <- c('test_not_normal')
+dist_retest_subs_test_data$dv <- row.names(dist_retest_subs_test_data)
+row.names(dist_retest_subs_test_data) <- seq(1:nrow(dist_retest_subs_test_data))
+dist_retest_subs_test_data = dist_retest_subs_test_data %>% select(dv, test_not_normal)
+
+dist_data <- merge(dist_retest_data, dist_retest_subs_test_data, by = 'dv')
+
+rm(dist_retest_data, dist_retest_subs_test_data)
+```
+
+Add whether dv's are tasks or survey to distribution dfs
+```{r}
+dist_data = cor_df %>%
+  select(dv, task) %>%
+  left_join(dist_data, by = 'dv')
+```
+
+What proportion is not normal?
+A large proportion of the variables are not normal for data from both sources. Larger proportions of survey data are not normal compared to task data. 
+```{r}
+dist_data %>%
+  group_by(task) %>%
+  summarise(mean_retest_not_normal  = mean(retest_not_normal),
+            mean_test_not_normal = mean(test_not_normal))
+```
+
+Are the same vars that are not normally distributed in the retest data not normal in test data as well?
+List of variables that have different distributions in the two time points (shown here is whether they are normally distributed in the retest data)
+A majority of them are drift diffusion parameters (but note that these vars are overrepresented to begin with - more on them later).
+```{r}
+dist_data %>%
+  filter(retest_not_normal != test_not_normal)
+```
+
+Apply the same cleaning procedure that was used for meaningful vars for all vars:
+```{r}
+transform_remove_skew = function(data, threshold = 1){
+}
+```
+
+Transform non normal vars
+Transform both retest and test data if not normally distributed in either. 
+Order of transformations tried: log and sqrt
+```{r}
+#Add columns to dist_data that will be updated
+dist_data = dist_data %>%
+  mutate(retest_transform = ifelse(retest_not_normal, NA, 'none'),
+         test_transform = ifelse(test_not_normal, NA, 'none'))
+
+get_transform <- function(data){
+  t_data = data
+  transform = 'none'
+  if(diff_from_normal(data) & !is.na(diff_from_normal(data))){
+    t_data = log1p(data)
+    transform = 'log1p'
+    if(diff_from_normal(t_data) & !is.na(diff_from_normal(t_data))){
+      t_data = sqrt(data)
+      transform = 'sqrt'
+      if(diff_from_normal(t_data) & !is.na(diff_from_normal(t_data))){
+        transform = 'failed'
+      }
+    }
+  }
+  return(transform)
+}
+
+for(i in 1:nrow(dist_data)){
+  if(is.na(dist_data$retest_transform[i])){
+    dist_data$retest_transform[i] = get_transform(retest_data[,dist_data$dv[i]])
+  }
+  if(is.na(dist_data$test_transform[i])){
+    dist_data$test_transform[i] = get_transform(retest_subs_test_data[,dist_data$dv[i]])
+  }
+}
+
+t_retest_data = retest_data
+t_retest_subs_test_data = retest_subs_test_data
+
+#check if normal
+#if yes stop and record transformation = none
+#if transform: log
+#check if normal
+#if yes stop and record transformation = log
+#if no transform: sqrt
+```
+
+Drift diffusion variables: raw vars vs. EZ vs. hddm
+
+Mean reliabilities for different kinds of variables (e.g. drift rates and NDs; separately for EZ and HDDM; subtraction vs basic variables - single vs. multiple)
+```{r}
+```
+
+--------------------------------
+
+Can you get the factor structure for the retest
+step 1:Ttest on all measures of T1 for people w and without retest
+```{r}
+
+```
+
+step2 : efa on the people you don't have retest on and then predict how well this holds up for people w retest on t1 and on t2
 

### 2017-02-22 SRO_Retest_Analyses.Rmd
cont working on retest exploration

@@
 ```{r}
-transform_remove_skew = function(data, threshold = 1){
+"%w/o%" <- function(x, y) x[!x %in% y]
+
+transform_remove_skew = function(data, cols, threshold = 1){
+
+  tmp = as.data.frame(apply(data[,columns],2,skew))
+  names(tmp) = c("skew")
+  tmp$dv = row.names(tmp)
+  tmp = tmp %>% 
+    filter(abs(skew)>threshold)
+
+  skewed_variables = tmp$dv
+  skew_subset = data[, skewed_variables]
+  positive_subset = data[,tmp$dv[tmp$skew>0]]
+  negative_subset = data[,tmp$dv[tmp$skew<0]]
+
+  # transform variables
+  # log transform for positive skew
+  positive_subset = log(positive_subset)
+  successful_transforms = as.data.frame(apply(positive_subset, 2, skew))
+  names(successful_transforms) = c('skew')
+  successful_transforms$dv = row.names(successful_transforms)
+  successful_transforms = successful_transforms %>% filter(abs(skew)<threshold)
+  successful_transforms = successful_transforms$dv
+  successful_transforms = positive_subset[,successful_transforms]
+  dropped_vars = names(positive_subset) %w/o% names(successful_transforms)
+
+  # replace transformed variables
+  data = data[,-c(which(names(data) %in% names(positive_subset)))]
+  names(successful_transforms) = paste0(names(successful_transforms), '.logTr')
+  print.noquote(rep('*', 40))
+  print(paste0('Dropping', length(dropped_vars) ,'positively skewed data that could not be transformed successfully:')
+
+  print('\n'.join(dropped_vars))
+  print.noquote(rep('*', 40))
+  data = pd.concat([data, successful_transforms], axis = 1)
 }
+
+tmp = as.data.frame(apply(retest_data[, matching_dv_columns], 2, skew))
+names(tmp) = c('skew')
+tmp$dv = row.names(tmp)
+tmp = tmp %>%
+  filter(abs(skew)>1)
+positive_subset = retest_data[,tmp$dv[tmp$skew>0]]
+
+positive_subset = log(positive_subset)
+successful_transforms = as.data.frame(apply(positive_subset, 2, skew))
+names(successful_transforms) = c('skew')
+successful_transforms$dv = row.names(successful_transforms)
+successful_transforms = successful_transforms %>% filter(abs(skew)<1)
+successful_transforms = successful_transforms$dv
+successful_transforms = positive_subset[,successful_transforms]
+dropped_vars = names(positive_subset) %w/o% names(successful_transforms)
+
+tmp_retest_data = retest_data
+tmp_retest_data = tmp_retest_data[,-c(which(names(tmp_retest_data) %in% 
+                                              names(positive_subset)))]
+
+#transform_remove_skew(retest_data, matching_dv_columns)
 ```

### 2017-02-23 SRO_Retest_Analyses.Rmd
cont working on retest exploration

--- 2017-02-21 SRO_Retest_Analyses.Rmd
@@
   pdf_document: default
+  html_document:
+    toc: true
+    toc_depth: 2
+    toc_float: true
 ---
@@
 ```
+
+# Loading and matching test and retest datasets
 
@@
 
-Get list of test retest correlations
+# Correlations of exhaustive variables
 
-TODO: write a nicer of getting rid of non numeric columns
+Get list of test retest correlations for all matching (numeric) columns in the test and retest data. Note two caveats:
+1. There are still some columns that weren't in both datasets (e.g. two stage)
+2. Unlike meaningful variables these variables are not (yet) rid of outliers or log transformed if skewed. This will be detailed below along with its problems.
 
@@
 
-The smaller meaningful vars have been somewhat cleaned. So far in this notebook we looked at all the vars in their rawest form.
+The smaller meaningful vars dataframe have been somewhat cleaned.
+So far in this notebook we looked at all the vars in their rawest form.
+Here we'll first check the distributions of all the variables and then apply the same cleaning procedure that was used for the meaningful variables to all of them.
+
+Note that I'm doing this for the sake of consistency for now.
+We might later decide that we would like to transform certain variables of interest in other ways to be able to include them in our analyses without violating the assumptions of those analyses.
+The current procedure checks the skewness of a column
 
@@
 ```{r}
-transform_remove_skew = function(data, threshold = 1){
+remove_outliers = function(data_column, quantile_range = 2.5){
+
+  q_25 = quantile(data_column, na.rm=T)[2]
+  q_50 = quantile(data_column, na.rm=T)[3]
+  q_75 = quantile(data_column, na.rm=T)[4]
+
+  lowlimit = q_50 - quantile_range*(q_75 - q_25)
+  highlimit = q_50 + quantile_range*(q_75 - q_25)
+
+  data_column = ifelse(data_column<lowlimit, NA, ifelse(data_column>highlimit, NA, data_column))
+
+  return(data_column)
+}
+
+"%w/o%" <- function(x, y) x[!x %in% y]
+
+neg_log <- function(column){
+  col_max = max(column, na.rm=T)
+  column = col_max+1-column
+  return(log(column))
+}
+
+transform_remove_skew = function(data, columns, threshold = 1){
+
+  tmp = as.data.frame(apply(data[,columns],2,skew))
+  names(tmp) = c("skew")
+  tmp$dv = row.names(tmp)
+  tmp = tmp %>% 
+    filter(abs(skew)>threshold)
+
+  skewed_variables = tmp$dv
+  skew_subset = data[, skewed_variables]
+  positive_subset = data[,tmp$dv[tmp$skew>0]]
+  negative_subset = data[,tmp$dv[tmp$skew<0]]
+
+  # transform variables
+  # log transform for positive skew
+  positive_subset = log(positive_subset)
+  successful_transforms = as.data.frame(apply(positive_subset, 2, skew))
+  names(successful_transforms) = c('skew')
+  successful_transforms$dv = row.names(successful_transforms)
+  successful_transforms = successful_transforms %>% filter(abs(skew)<threshold)
+  successful_transforms = successful_transforms$dv
+  successful_transforms = positive_subset[,successful_transforms]
+  dropped_vars = names(positive_subset) %w/o% names(successful_transforms)
+
+  # replace transformed variables
+  data = data[,-c(which(names(data) %in% names(positive_subset)))]
+  names(successful_transforms) = paste0(names(successful_transforms), '.logTr')
+  print.noquote(rep('*', 40))
+  print(paste0('Dropping ', length(dropped_vars) ,' positively skewed data that could not be transformed successfully:'))
+  print(dropped_vars)
+  print.noquote(rep('*', 40))
+  data = cbind(data, successful_transforms)
+
+  # reflected log transform for negative skew      
+  negative_subset = as.data.frame(apply(negative_subset, 2, neg_log))
+  successful_transforms = as.data.frame(apply(negative_subset, 2, skew))
+  names(successful_transforms) = c('skew')
+  successful_transforms$dv = row.names(successful_transforms)
+  successful_transforms = successful_transforms %>% filter(abs(skew)<1)
+  successful_transforms = successful_transforms$dv
+  successful_transforms = negative_subset[,successful_transforms]
+  dropped_vars = names(negative_subset) %w/o% names(successful_transforms)
+
+  # replace transformed variables
+  data = data[,-c(which(names(data) %in% names(negative_subset)))]
+  names(successful_transforms) = paste0(names(successful_transforms), '.ReflogTr')
+  print.noquote(rep('*', 40))
+  print(paste0('Dropping ', length(dropped_vars) ,' negatively skewed data that could not be transformed successfully:'))
+  print(dropped_vars)
+  print.noquote(rep('*', 40))
+  data = cbind(data, successful_transforms)
+
+  return(data)
 }
@@
 
-Transform non normal vars
-Transform both retest and test data if not normally distributed in either. 
-Order of transformations tried: log and sqrt
 ```{r}
-#Add columns to dist_data that will be updated
-dist_data = dist_data %>%
-  mutate(retest_transform = ifelse(retest_not_normal, NA, 'none'),
-         test_transform = ifelse(test_not_normal, NA, 'none'))
+clean_retest_data = as.data.frame(apply(retest_data[, matching_dv_columns], 2, remove_outliers))
+clean_retest_data = transform_remove_skew(clean_retest_data, matching_dv_columns)
+```
 
-get_transform <- function(data){
-  t_data = data
-  transform = 'none'
-  if(diff_from_normal(data) & !is.na(diff_from_normal(data))){
-    t_data = log1p(data)
-    transform = 'log1p'
-    if(diff_from_normal(t_data) & !is.na(diff_from_normal(t_data))){
-      t_data = sqrt(data)
-      transform = 'sqrt'
-      if(diff_from_normal(t_data) & !is.na(diff_from_normal(t_data))){
-        transform = 'failed'
-      }
-    }
-  }
-  return(transform)
-}
+I'm not sure what is the right thing to do regarding the cleaning of the test data for the retest subjects.
+Should they be cleaned on the whole sample for the time they were collected on and then extracted (this should have an effect on outliers as well as transformations) or extracted and then cleaned.
+Here I am doing the latter but this seems to be resulting in more skewed variables.
 
-for(i in 1:nrow(dist_data)){
-  if(is.na(dist_data$retest_transform[i])){
-    dist_data$retest_transform[i] = get_transform(retest_data[,dist_data$dv[i]])
-  }
-  if(is.na(dist_data$test_transform[i])){
-    dist_data$test_transform[i] = get_transform(retest_subs_test_data[,dist_data$dv[i]])
-  }
-}
+```{r}
+clean_retest_subs_test_data = as.data.frame(apply(retest_subs_test_data[, matching_dv_columns], 2, remove_outliers))
+clean_retest_subs_test_data = transform_remove_skew(retest_subs_test_data, matching_dv_columns)
+```
 
-t_retest_data = retest_data
-t_retest_subs_test_data = retest_subs_test_data
-
-#check if normal
-#if yes stop and record transformation = none
-#if transform: log
-#check if normal
-#if yes stop and record transformation = log
-#if no transform: sqrt
-```
+But what about dropping different variables from the two dataframes
 

### 2017-02-25 SRO_Retest_Analyses.Rmd
cont working on retest exploration

@@
 output:
-  html_notebook: default
-  pdf_document: default
   html_document:
-    toc: true
-    toc_depth: 2
-    toc_float: true
+    toc: yes
+    toc_float: yes
 ---
@@
 Data cleaning for efa
-```{r}
+```{r eval=FALSE}
 #read in only meaningful vars
@@
 NEED TO RESOLVE SOME DIFFERENCES IN MEANINGFUL VARS BETWEEN THE TWO DATASETS
-```{r}
+```{r eval=FALSE}
 #Check columns 
@@
 Efa on subjects from original dataset withOUT retest data (using meaningful vars only)
-```{r}
+```{r eval=FALSE}
 unrotated <- efaUnrotate(rest_subs_test_mngf_z, nf=3, varList=names(rest_subs_test_mngf_z)[-1], estimator="mlr")
@@
 
-```{r}
+```{r eval = FALSE}
 corMat <- rest_subs_test_mngf_z %>% select(-sub_id) %>% cor(.,use = 'complete.obs')
@@
 
-```{r}
+```{r eval = FALSE}
 solution

### 2017-02-25 SRO_Retest_Analyses.Rmd
cont working on retest exploration

@@
 
-# Loading and matching test and retest datasets
+# Loading and matching datasets
 
-Load original data
+### Load original data
 ```{r}
@@
 
-Load retest data
+### Load retest data
 ```{r}
@@
 
-Extract retest participants from test data
+### Extract retest participants from test data
 
@@
 ```
+
+### Checks and matching issues
 
@@
 Get list of test retest correlations for all matching (numeric) columns in the test and retest data. Note two caveats:  
-1. There are still some columns that weren't in both datasets (e.g. two stage)
-2. Unlike meaningful variables these variables are not (yet) rid of outliers or log transformed if skewed. This will be detailed below along with its problems.
+**1. There are still some columns that weren't in both datasets listed above (e.g. two stage)**  
+**2. Unlike meaningful variables these variables are not (yet) rid of outliers or log transformed if skewed. This will be detailed below along with its problems.**
 
@@
 
-Distributions of correlations by task vs. survey
+## Distributions of correlations by task vs. survey
 
@@
 
-Rank order correlations
-For tasks
+```{r}
+cor_df %>%
+  group_by(task) %>%
+  summarise(mean_pearson = mean(pearson),
+            mean_spearman = mean(spearman),
+            num_vars = n())
+```
+
+### Rank order of correlations
+
+#### For tasks
 ```{r}
@@
 
-Mean reliability for tasks
-```{r}
-cor_df %>%
-  filter(task == 'task') %>%
-  select(dv, spearman, pearson) %>%
-  arrange(-pearson, -spearman) %>%
-  summarise(mean_pearson = mean(pearson),
-            mean_spearman = mean(spearman),
-            num_vars = n())
-```
-
-For surveys
+#### For surveys
 
@@
   arrange(-pearson, -spearman)
-```
-
-Mean reliability for surveys
-```{r}
-cor_df %>%
-  filter(task == 'survey') %>%
-  select(dv, spearman, pearson) %>%
-  arrange(-pearson, -spearman) %>%
-  summarise(mean_pearson = mean(pearson),
-            mean_spearman = mean(spearman),
-            num_vars = n())
 ```
@@
 
-```{r}
+```{r warning=FALSE}
 clean_retest_data = as.data.frame(apply(retest_data[, matching_dv_columns], 2, remove_outliers))
@@
 
-```{r}
+```{r warning=FALSE}
 clean_retest_subs_test_data = as.data.frame(apply(retest_subs_test_data[, matching_dv_columns], 2, remove_outliers))

### 2017-02-26 SRO_Retest_Analyses.Rmd
cont working on retest exploration

@@
 
-One retest participant is not in test data. Remove that subject from retest_data for now
+One retest participant is not in test data.
+Remove that subject from retest_data.
+This participant should not have completed the retest battery to begin with because they had failed our previous criterion on number of properly completed trials.
+The first HIT I posted, however, had an issue with the qualifications and before I could terminate it a handful of subjects had accepted and begun the battery so we had to let them finish.
+So this subject has given us good data for the retest battery but worse data for the test battery.
 ```{r}
@@
 Distribution of all Pearson and Spearman correlations
-```{r}
+```{r warning=FALSE, message=FALSE}
 cor_df %>%
@@
 Task reliability distributions looks alsmost bimodal. **Should figure out whether the lower ones are specific tasks or if they are certain kinds of vars (e.g. certain ddm parameters)**
-```{r}
+```{r warning=FALSE, message=FALSE}
 cor_df %>%
@@
 ```
-
+Mean reliability and the number of variables for both the surveys and the tasks
 ```{r}
@@
 
-Note: Holt and Laury test-retest is pretty terrible. In previous data it was ~.35. Should check to see if there is a coding error there.
+Note: Holt and Laury test-retest is pretty terrible. In previous data I have worked with it was ~.35. Should check to see if there is a coding error there.
 ```{r}
@@
 
-Distribution of each variable
+## Distribution of each variable
 
-Check if the variables that went in to the correlation matrix have normal distributions since at least the Pearson correlations depend on this assumption.
-If not transform data columns in both retest and test data and calculate a new correlation df.
+The smaller meaningful_vars dataframe has been somewhat cleaned.
+So far in this notebook we looked at all the vars in their rawest form.
+Here we'll first check the distributions of all the variables and then apply the same cleaning procedure that was used for the meaningful variables to all of them.
+
+Note that I'm doing this for the sake of consistency for now.
+We might later decide that we would like to transform certain variables of interest in other ways to be able to include them in our analyses without violating the assumptions of those analyses.
+The current procedure checks the skewness of a column first removes the outliers defined as greater than 2.5 IQR from median then variables with skewness >1 are log transformed.
+
+First I'll check if the variables that went in to the correlation matrix have normal distributions since at least the Pearson correlations depend on this assumption.
+Then everything will be cleaned the way meaningful variables was cleaned.
+There is a problem with this approach that I'm not sure how to deal with yet but this will be detailed below.
 
@@
 
-Check distributions of retest data
-
-The smaller meaningful vars dataframe have been somewhat cleaned.
-So far in this notebook we looked at all the vars in their rawest form.
-Here we'll first check the distributions of all the variables and then apply the same cleaning procedure that was used for the meaningful variables to all of them.
-
-Note that I'm doing this for the sake of consistency for now.
-We might later decide that we would like to transform certain variables of interest in other ways to be able to include them in our analyses without violating the assumptions of those analyses.
-The current procedure checks the skewness of a column
-
 Create and organize new df where distribution of vars data is stored.
 First for retest data only; then for test data for subjects who have retest data - restricting here since these are the subsets of data that went in to the correlation matrix.
-Merge and cleanup
+Merge and cleanup.
 ```{r}
@@
 Are the same vars that are not normally distributed in the retest data not normal in test data as well?  
-List of variables that have different distributions in the two time points (shown here is whether they are normally distributed in the retest data)
+List of variables that have different distributions in the two time points.
 A majority of them are drift diffusion parameters (but note that these vars are overrepresented to begin with - more on them later).
@@
   names(successful_transforms) = paste0(names(successful_transforms), '.logTr')
-  print.noquote(rep('*', 40))
-  print(paste0('Dropping ', length(dropped_vars) ,' positively skewed data that could not be transformed successfully:'))
-  print(dropped_vars)
-  print.noquote(rep('*', 40))
+  cat(rep('*', 40))
+  cat(paste0('Dropping ', length(dropped_vars) ,' positively skewed data that could not be transformed successfully:'))
+  cat(dropped_vars, sep = '\n')
+  cat(rep('*', 40))
   data = cbind(data, successful_transforms)
@@
   names(successful_transforms) = paste0(names(successful_transforms), '.ReflogTr')
-  print.noquote(rep('*', 40))
-  print(paste0('Dropping ', length(dropped_vars) ,' negatively skewed data that could not be transformed successfully:'))
-  print(dropped_vars)
-  print.noquote(rep('*', 40))
+  cat(rep('*', 40))
+  cat(paste0('Dropping ', length(dropped_vars) ,' negatively skewed data that could not be transformed successfully:'))
+  cat(dropped_vars, sep = '\n')
+  cat(rep('*', 40))
   data = cbind(data, successful_transforms)
@@
 
+Clean retest data with these rules.
 ```{r warning=FALSE}
@@
 
-I'm not sure what is the right thing to do regarding the cleaning of the test data for the retest subjects.
-Should they be cleaned on the whole sample for the time they were collected on and then extracted (this should have an effect on outliers as well as transformations) or extracted and then cleaned.
-Here I am doing the latter but this seems to be resulting in more skewed variables.
+**I'm not sure what the right thing to do is regarding the cleaning of the test data for the retest subjects.** Should they be cleaned on the whole sample for the time they were collected on and then extracted (this should have an effect on outliers as well as transformations) or extracted and then cleaned.
+Here I am doing the latter but this seems to be resulting in more skewed variables for test data compared to the retest data so the later correlation matrix might not include all the variables we would like to look at.
 
@@
 
-But what about dropping different variables from the two dataframes
+## Correlations on cleaned variables
+
+```{r}
+clean_all_columns <- unique(c(names(clean_retest_data), names(clean_retest_subs_test_data)))
+
+clean_matching_columns <- c()
+for(i in 1:length(clean_all_columns)){
+  if(clean_all_columns[i] %in% names(clean_retest_data) & clean_all_columns[i] %in% names(clean_retest_subs_test_data)){
+    clean_matching_columns <- c(clean_matching_columns, clean_all_columns[i])
+  }
+}
+
+clean_retest_data <- clean_retest_data[,clean_matching_columns]
+clean_retest_subs_test_data <- clean_retest_subs_test_data[,clean_matching_columns]
+
+clean_matching_dv_columns <- c()
+
+for(i in 1:length(clean_matching_columns)){
+  if(is.numeric(clean_retest_data[,clean_matching_columns[i]]) & is.numeric(clean_retest_subs_test_data[,clean_matching_columns[i]])){
+    clean_matching_dv_columns <- c(clean_matching_dv_columns, clean_matching_columns[i])
+  }
+}
+
+clean_cor_df <- data.frame(pearson = rep(NA, length(clean_matching_dv_columns)), spearman = rep(NA, length(clean_matching_dv_columns)))
+
+row.names(clean_cor_df) <- clean_matching_dv_columns
+
+for(i in 1:length(clean_matching_dv_columns)){
+  clean_cor_df[clean_matching_dv_columns[i], 'pearson'] <- cor(clean_retest_data[,clean_matching_dv_columns[i]], clean_retest_subs_test_data[,clean_matching_dv_columns[i]], method = 'pearson', use = "pairwise.complete.obs")
+  clean_cor_df[clean_matching_dv_columns[i], 'spearman'] <- cor(clean_retest_data[,clean_matching_dv_columns[i]],clean_retest_subs_test_data[,clean_matching_dv_columns[i]], method = 'spearman', use = "pairwise.complete.obs")
+}
+```
+
+```{r}
+clean_cor_df %>%
+  gather(key, value) %>%
+  ggplot(aes(value))+
+  geom_histogram()+
+  theme_bw()+
+  facet_wrap(~key)
+```
+
+```{r}
+clean_cor_df$dv = row.names(clean_cor_df)
+row.names(clean_cor_df) = seq(1:nrow(clean_cor_df))
+clean_cor_df$task = 'task'
+clean_cor_df[grep('survey', clean_cor_df$dv), 'task'] = 'survey'
+```
+
+```{r}
+clean_cor_df %>%
+  gather(key, value, -dv, -task) %>%
+  ggplot(aes(value))+
+  geom_histogram()+
+  theme_bw()+
+  facet_wrap(key~task)
+```
+
+This cleaning led to a slight change in the mean reliabilities but a lot of dropped variables.
+
+```{r}
+clean_cor_df %>%
+  group_by(task) %>%
+  summarise(mean_pearson = mean(pearson),
+            mean_spearman = mean(spearman),
+            num_vars = n())
+```
+
+--------------------------------
 

### 2017-02-26 SRO_Retest_Analyses.Rmd
cont working on retest exploration

@@
 
-What proportion is not normal?  
+**What proportion is not normal?**  
 A large proportion of the variables are not normal for data from both sources. Larger proportions of survey data are not normal compared to task data. 
@@
 
-Are the same vars that are not normally distributed in the retest data not normal in test data as well?  
+**Are the same vars that are not normally distributed in the retest data not normal in test data as well?**  
 List of variables that have different distributions in the two time points.
@@
   cat(rep('*', 40))
+  cat('\n')
   cat(paste0('Dropping ', length(dropped_vars) ,' positively skewed data that could not be transformed successfully:'))
+  cat('\n')
   cat(dropped_vars, sep = '\n')
   cat(rep('*', 40))
+  cat('\n')
   data = cbind(data, successful_transforms)
@@
   cat(rep('*', 40))
+  cat('\n')
   cat(paste0('Dropping ', length(dropped_vars) ,' negatively skewed data that could not be transformed successfully:'))
+  cat('\n')
   cat(dropped_vars, sep = '\n')
   cat(rep('*', 40))
+  cat('\n')
   data = cbind(data, successful_transforms)
@@
 
-**I'm not sure what the right thing to do is regarding the cleaning of the test data for the retest subjects.** Should they be cleaned on the whole sample for the time they were collected on and then extracted (this should have an effect on outliers as well as transformations) or extracted and then cleaned.
+**I'm not sure what the right thing to do is regarding the cleaning of the test data for the retest subjects.**   
+Should they be cleaned on the whole sample for the time they were collected on and then extracted (this should have an effect on outliers as well as transformations) or extracted and then cleaned.
 Here I am doing the latter but this seems to be resulting in more skewed variables for test data compared to the retest data so the later correlation matrix might not include all the variables we would like to look at.
@@
 
+Create the same list of correlations as before but this time on a smaller set of cleaned variables.
 ```{r}
@@
 }
-```
 
-```{r}
-clean_cor_df %>%
-  gather(key, value) %>%
-  ggplot(aes(value))+
-  geom_histogram()+
-  theme_bw()+
-  facet_wrap(~key)
-```
-
-```{r}
 clean_cor_df$dv = row.names(clean_cor_df)
@@
 
-```{r}
-clean_cor_df %>%
+Let's look at the distributions again: The distributions don't look terribly different but there are noticably fewer variables post cleaning. 
+```{r warning=FALSE, message=FALSE}
+cor_df %>%
+  left_join(clean_cor_df, by='dv') %>%
+  select(-task.y)%>%
+  rename(pearson_preClean = pearson.x, spearman_preClean = spearman.x,
+         pearson_postClean = pearson.y, spearman_postClean = spearman.y,
+         task = task.x) %>%
   gather(key, value, -dv, -task) %>%
-  ggplot(aes(value))+
-  geom_histogram()+
+  separate(key, c('cor_type', 'clean_type'),sep = "_") %>%
+  ggplot(aes(x=value, fill=factor(clean_type, levels = c('preClean', 'postClean'),
+                                  labels = c('Before', 'After'))))+
+  geom_histogram(position='identity', alpha = 0.5)+
+  facet_wrap(cor_type~task)+
   theme_bw()+
-  facet_wrap(key~task)
+  theme(legend.title = element_blank())
 ```
-
 This cleaning led to a slight change in the mean reliabilities but a lot of dropped variables.
@@
 
---------------------------------
+**What changed most with cleaning?**    
+Difference in correlation pre and post correlation for the variables that survived cleaning.  
+Things that changed most seem to be RTs and parameter estimates.
 
-Drift diffusion variables: raw vars vs. EZ vs. hddm
+```{r}
+clean_cor_df %>%
+  left_join(cor_df, by='dv') %>%
+  mutate(pearson_diff = abs(pearson.y - pearson.x),
+         spearman_diff = abs(spearman.y - spearman.x)) %>%
+  select(dv, pearson_diff, spearman_diff) %>%
+  arrange(-pearson_diff, -spearman_diff)
+```
+
+# Different variable types
+
+##
+
+## Drift diffusion variables: raw vars vs. EZ vs. hddm
 

### 2017-02-26 SRO_Retest_Analyses.Rmd
cont working on retest exploration

@@
 library(GPArotation)
-sem <- function(x) {sd(x) / sqrt(length(x))}
+sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
 options(digits = 4)
@@
 
-# Different variable types
+# Different task variable types
 
-##
+Mean reliabilities for different types of dependant variables
 
@@
 
-Mean reliabilities for different kinds of variables (e.g. drift rates and NDs; separately for EZ and HDDM; subtraction vs basic variables - single vs. multiple)
+We should probably take a closer look at model fits instead but this could be a first step.  
+I'm not sure why there are so many more EZ variables than hddm variables.
+
+```{r message=FALSE, warning=FALSE, fig.height=12, fig.width=9}
+cor_df%>%
+  select(-pearson) %>%
+  filter(grepl('EZ|hddm|_rt|_acc', dv)) %>%
+  mutate(var_type = ifelse(grepl('EZ',dv), 'EZ', ifelse(grepl('hddm',dv), 'hddm', 'raw')),
+         var = ifelse(grepl('_rt', dv), 'rt', ifelse(grepl('_acc', dv), 'acc', ifelse(grepl('_non_decision', dv), 'non_decision', ifelse(grepl('_thresh', dv), 'thresh', ifelse(grepl('_drift', dv), 'drift', NA)))))) %>%
+  left_join(clean_cor_df[,c('spearman', 'dv')], by = 'dv') %>%
+  gather(clean_type, spearman, -dv, -var_type, -var, -task) %>%
+  mutate(clean_type = ifelse(clean_type == 'spearman.x','Before','After')) %>%
+  ggplot(aes(spearman, fill = clean_type))+
+  geom_histogram(position='stack', alpha = 0.5)+
+  theme_bw()+
+  facet_wrap(var_type~var)+
+  scale_fill_discrete(name = 'Clean type')
+
+```
+
+Average reliabilities
+
+1. Cleaning doesn't seem to make a huge difference except for raw accuracies and hddm non_decision  
+2. There are many more EZ variabiles but the few hddm variables have slightly higher reliabilities  
+3. Raw accuracies seem to have the worst reliabilities on average while hddm parameters the highest
+
+```{r}
+cor_df%>%
+  select(-pearson) %>%
+  filter(grepl('EZ|hddm|_rt|_acc', dv)) %>%
+  mutate(var_type = ifelse(grepl('EZ',dv), 'EZ', ifelse(grepl('hddm',dv), 'hddm', 'raw')),
+         var = ifelse(grepl('_rt', dv), 'rt', ifelse(grepl('_acc', dv), 'acc', ifelse(grepl('_non_decision', dv), 'non_decision', ifelse(grepl('_thresh', dv), 'thresh', ifelse(grepl('_drift', dv), 'drift', NA)))))) %>%
+  left_join(clean_cor_df[,c('spearman', 'dv')], by = 'dv') %>%
+  gather(clean_type, spearman, -dv, -var_type, -var, -task) %>%
+  mutate(clean_type = ifelse(clean_type == 'spearman.x','Before','After')) %>%
+  group_by(var_type, clean_type, var) %>%
+  summarise(mean_spearman = mean(spearman, na.rm=T),
+            sem_spear = sem(spearman),
+            num_vars = n())
+```
+
+## Model fits versus raw
+
+```{r}
+```
+
+## Subtraction vs. Basic
+
+```{r}
+```
+
+## Single vs. multiple
+
 ```{r}

### 2017-02-27 SRO_Retest_Analyses.Rmd
cont working on retest exploration

@@
 
-1. Cleaning doesn't seem to make a huge difference except for raw accuracies and hddm non_decision  
-2. There are many more EZ variabiles but the few hddm variables have slightly higher reliabilities  
+1. Cleaning doesn't seem to make a huge difference (at least for Spearman correlations) except for raw accuracies and hddm non_decision  
+2. There are many more EZ variabiles but the few hddm variables have slightly higher reliabilities (I'm not sure about the reason for the discrepancy between the number of variables)  
 3. Raw accuracies seem to have the worst reliabilities on average while hddm parameters the highest
@@
             sem_spear = sem(spearman),
-            num_vars = n())
+            num_vars = sum(ifelse(is.na(spearman)==FALSE,1,0))) %>%
+  arrange(var_type, -as.numeric(as.factor(clean_type)))
 ```
@@
 
---------------------------------
+# Replicating the factor structure
 
-Can you get the factor structure for the retest
-step 1:Ttest on all measures of T1 for people w and without retest
+## Confirm comparability of retest and rest sample
+
+First do a t-test on all measures of T1 for subjects with and without retest to confirm that these two samples do not differ from each other significantly
 ```{r}
+ttest_df = data.frame(t_stat = rep(NA, length(matching_dv_columns)),
+                      p_val = rep(NA, length(matching_dv_columns)))
 
+row.names(ttest_df) <- matching_dv_columns
+
+for(i in 1:length(matching_dv_columns)){
+  ttest_df[matching_dv_columns[i], 't_stat'] <- t.test(retest_subs_test_data[,matching_dv_columns[i]], rest_subs_test_data[,matching_dv_columns[i]])$statistic
+
+  ttest_df[matching_dv_columns[i], 'p_val'] <- t.test(retest_subs_test_data[,matching_dv_columns[i]], rest_subs_test_data[,matching_dv_columns[i]])$p.value
+}
+
+ttest_df$dv = row.names(ttest_df)
+row.names(ttest_df) = seq(1:nrow(ttest_df))
+ttest_df$task = 'task'
+ttest_df[grep('survey', ttest_df$dv), 'task'] = 'survey'
 ```
+
+Distribution of t values
+
+```{r warning=FALSE, message=FALSE}
+ttest_df %>%
+  ggplot(aes(t_stat)) +
+  geom_histogram()+
+  theme_bw()+
+  facet_wrap(~task)
+```
+
+**Which variables are significantly different between the two samples (those with and without retest data for T1)?**
+
+A handful of variables. None of them are very strongly different though.
+
+```{r}
+ttest_df %>%
+  filter(p_val<0.05) %>%
+  select(dv, task, t_stat, p_val)
+```
+
+Do this again with cleaned data.
+
+## Efa and Cfa
 
@@
 
-Completion times/days
+# Completion times/days
 
-- First data release email esp to ASU
-- Send the spreadsheet with meaningul variables + demographics
+# Invited vs. completed retest
 

### 2017-02-28 SRO_Retest_Analyses.Rmd
cont working on retest exploration

@@
 library(GPArotation)
+library(rmarkdown)
 sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
+render_this <- function(){rmarkdown::render('SRO_Retest_Analyses.Rmd', html_notebook(toc = T, toc_float = T))}
 options(digits = 4)
@@
 clean_retest_subs_test_data = as.data.frame(apply(retest_subs_test_data[, matching_dv_columns], 2, remove_outliers))
-clean_retest_subs_test_data = transform_remove_skew(retest_subs_test_data, matching_dv_columns)
+clean_retest_subs_test_data = transform_remove_skew(clean_retest_subs_test_data, matching_dv_columns)
 ```
@@
 Create the same list of correlations as before but this time on a smaller set of cleaned variables.
-```{r}
+
+```{r warning=FALSE, message=FALSE}
 clean_all_columns <- unique(c(names(clean_retest_data), names(clean_retest_subs_test_data)))
@@
 
-clean_retest_data <- clean_retest_data[,clean_matching_columns]
-clean_retest_subs_test_data <- clean_retest_subs_test_data[,clean_matching_columns]
+# clean_retest_data <- clean_retest_data[,clean_matching_columns]
+# clean_retest_subs_test_data <- clean_retest_subs_test_data[,clean_matching_columns]
 
@@
 for(i in 1:length(clean_matching_dv_columns)){
-  clean_cor_df[clean_matching_dv_columns[i], 'pearson'] <- cor(clean_retest_data[,clean_matching_dv_columns[i]], clean_retest_subs_test_data[,clean_matching_dv_columns[i]], method = 'pearson', use = "pairwise.complete.obs")
-  clean_cor_df[clean_matching_dv_columns[i], 'spearman'] <- cor(clean_retest_data[,clean_matching_dv_columns[i]],clean_retest_subs_test_data[,clean_matching_dv_columns[i]], method = 'spearman', use = "pairwise.complete.obs")
+
+  robustCor <- function(...) {
+    obj<-try(cor(...), silent=TRUE)
+    if (is(obj, "try-error")) return(NA) else return(obj)
+  }
+
+  tmp_pearson = robustCor(clean_retest_data[,clean_matching_dv_columns[i]], clean_retest_subs_test_data[,clean_matching_dv_columns[i]], method = 'pearson', use = "pairwise.complete.obs")
+
+  tmp_spearman = robustCor(clean_retest_data[,clean_matching_dv_columns[i]], clean_retest_subs_test_data[,clean_matching_dv_columns[i]], method = 'spearman', use = "pairwise.complete.obs")
+
+  clean_cor_df[clean_matching_dv_columns[i], 'pearson'] <- tmp_pearson 
+  clean_cor_df[clean_matching_dv_columns[i], 'spearman'] <- tmp_spearman
+
 }
@@
 clean_cor_df[grep('survey', clean_cor_df$dv), 'task'] = 'survey'
+```
+
+Correlations could not be calculated for the following variables due to lack of variance.
+
+```{r}
+clean_cor_df %>%
+  filter(is.na(pearson)) %>%
+  select(dv)
 ```
@@
 ```
+
 This cleaning led to a slight change in the mean reliabilities but a lot of dropped variables.
-
 ```{r}
@@
   group_by(task) %>%
-  summarise(mean_pearson = mean(pearson),
-            mean_spearman = mean(spearman),
-            num_vars = n())
+  summarise(mean_pearson = mean(pearson, na.rm=T),
+            mean_spearman = mean(spearman, na.rm=T),
+            num_vars = sum(ifelse(is.na(pearson)==FALSE,1,0)))
 ```
@@
   ggplot(aes(spearman, fill = clean_type))+
-  geom_histogram(position='stack', alpha = 0.5)+
+  geom_histogram(position='identity', alpha = 0.5)+
   theme_bw()+
@@
 
-## Model fits versus raw
+## Other variable types
 
-```{r}
-```
-
-## Subtraction vs. Basic
-
-```{r}
-```
-
-## Single vs. multiple
-
-```{r}
-```
+I planned to look at differences between distributions of reliabilities for other variables types as well but I am not sure what these categories should be so I am deferring this for further discussions.
+My earlier notes suggested differences between other model parameters versus raw variables; subtraction versus basic variables; single versus multiple variables.I'm hoping we can come up with a more systematic definition that I can automatize or at least restrict to certain groups of variable instead of going through all 600+ variables and manually labeling them.
 
@@
 
-A handful of variables. None of them are very strongly different though.
+43 variables. None of them are very strongly different though.
 
@@
 Do this again with cleaned data.  
+Clean the T1 data for the subsets first.  
+**Here again I'm not sure if I should clean before or after splitting.
+Before it seemed appropriate to clean subjects with retest data after separating them from the remaining subjects but here it might be better to clean first and then separate.
+But then it would differ from what was done for earlier anaylses and it seems like the kind of thing that should be kept consistent.**
+
+Clean T1 for subjects with retest data (doing it again because this df was subsetted before)
+
+```{r warning=FALSE}
+clean_retest_subs_test_data = as.data.frame(apply(retest_subs_test_data[, matching_dv_columns], 2, remove_outliers))
+clean_retest_subs_test_data = transform_remove_skew(clean_retest_subs_test_data, matching_dv_columns)
+```
+
+Clean T1 for rest of the subjects
+
+```{r warning=FALSE}
+clean_rest_subs_test_data = as.data.frame(apply(rest_subs_test_data[, matching_dv_columns], 2, remove_outliers))
+clean_rest_subs_test_data = transform_remove_skew(clean_rest_subs_test_data, matching_dv_columns)
+```
+
+Get numeric dv's from both cleaned datasets to compute t-tests on.
+```{r}
+clean_all_columns <- unique(c(names(clean_rest_subs_test_data), names(clean_retest_subs_test_data)))
+
+clean_matching_columns <- c()
+for(i in 1:length(clean_all_columns)){
+  if(clean_all_columns[i] %in% names(clean_rest_subs_test_data) & clean_all_columns[i] %in% names(clean_retest_subs_test_data)){
+    clean_matching_columns <- c(clean_matching_columns, clean_all_columns[i])
+  }
+}
+
+clean_matching_dv_columns <- c()
+
+for(i in 1:length(clean_matching_columns)){
+  if(is.numeric(clean_rest_subs_test_data[,clean_matching_columns[i]]) & is.numeric(clean_rest_subs_test_data[,clean_matching_columns[i]])){
+    clean_matching_dv_columns <- c(clean_matching_dv_columns, clean_matching_columns[i])
+  }
+}
+```
+
+Compute t-tests for cleaned variables.
+```{r}
+clean_ttest_df = data.frame(t_stat = rep(NA, length(clean_matching_dv_columns)),
+                      p_val = rep(NA, length(clean_matching_dv_columns)))
+
+row.names(clean_ttest_df) <- clean_matching_dv_columns
+
+for(i in 1:length(clean_matching_dv_columns)){
+
+  robustTTest <- function(...) {
+    obj<-try(t.test(...), silent=TRUE)
+    if (is(obj, "try-error")) return(obj = data.frame(statistic = NA, p.value=NA)) else return(obj)
+  }
+
+  tmp = robustTTest(clean_retest_subs_test_data[,clean_matching_dv_columns[i]], clean_rest_subs_test_data[,clean_matching_dv_columns[i]])
+
+  clean_ttest_df[clean_matching_dv_columns[i], 't_stat'] <- tmp$statistic 
+  clean_ttest_df[clean_matching_dv_columns[i], 'p_val'] <- tmp$p.value
+    }
+
+clean_ttest_df$dv = row.names(clean_ttest_df)
+row.names(clean_ttest_df) = seq(1:nrow(clean_ttest_df))
+clean_ttest_df$task = 'task'
+clean_ttest_df[grep('survey', clean_ttest_df$dv), 'task'] = 'survey'
+```
+
+Variables for which t-tests cannot be computed due to lack of variance.
+```{r}
+clean_ttest_df %>%
+  filter(is.na(t_stat)) %>%
+  select(dv)
+```
+
+Distribution of t-tests for the cleaned variables with sufficient variance
+```{r warning=FALSE, message=FALSE}
+clean_ttest_df %>%
+  filter(!is.na(t_stat)) %>%
+ggplot(aes(t_stat)) +
+  geom_histogram()+
+  theme_bw()+
+  facet_wrap(~task)
+```
+
+**Which variables are significantly different between the two samples on cleaned data (those with and without retest data for T1)?**
+
+More variables (that are thought to have been properly cleaned for these analyses) are significantly different between the two samples.   
+**Not sure what to do with this especially for the next set of analyses.**
+
+```{r}
+clean_ttest_df %>%
+  filter(!is.na(p_val) & p_val<0.05) %>%
+  select(dv, task, t_stat, p_val)
+```
 
@@
 
-step2 : efa on the people you don't have retest on and then predict how well this holds up for people w retest on t1 and on t2
+Step 2: Efa on the people you don't have retest on and then predict how well this holds up for people w retest on t1 and on t2.
+
+I'm restricting the factor analyses to the meaningful variables for now (instead of the 600+ exhaustive variables) to keep it manageable.
+I haven't consulted other factor analyses that have been done on the full dataset in doing this but will be happy to adjust as necessary.
 
@@
 
-#Are all retest subjects in test_data? No. 
-sum(meaningful_var_retest$sub_id %in% meaningful_var_test$sub_id) == nrow(meaningful_var_retest)
-
-#Who is missing?
-meaningful_var_retest$sub_id[which(meaningful_var_retest$sub_id %in% meaningful_var_test$sub_id == FALSE)]
-
 #Remove sub w missing test data from retest data
@@
 Checking columns for efa:
-NEED TO RESOLVE SOME DIFFERENCES IN MEANINGFUL VARS BETWEEN THE TWO DATASETS
+There
 ```{r eval=FALSE}
@@
 names(retest_subs_test_mngf)[names(retest_subs_test_mngf) %in% names(retest_data_mngf) == FALSE]
+```
 
+For now I'm just removing these variables but will have to do re-do them once I resolve why they weren't in both datasets to begin with (The answer will be a combination of not having run the most recent analysis script on some tasks and dropped variables as a result of cleaning)
+```{r}
 #Subset datasets with only matching columns
@@
 Efa on subjects from original dataset withOUT retest data (using meaningful vars only)
+
+Trying to use `lavaan` first. It's not happy with me.
 ```{r eval=FALSE}
@@
 
+Using the `psych` package I get some sort of solution but these are probably not valid given all the warnings.
 ```{r eval = FALSE}
@@
 ```{r eval = FALSE}
-solution
+print(solution$loadings, sort=T)
 ```

### 2017-02-28 SRO_Retest_Analyses.Rmd
cont working on retest exploration

@@
 Trying to use `lavaan` first. It's not happy with me.
-```{r eval=FALSE}
+```{r}
 unrotated <- efaUnrotate(rest_subs_test_mngf_z, nf=3, varList=names(rest_subs_test_mngf_z)[-1], estimator="mlr")
@@
 Using the `psych` package I get some sort of solution but these are probably not valid given all the warnings.
-```{r eval = FALSE}
+```{r}
 corMat <- rest_subs_test_mngf_z %>% select(-sub_id) %>% cor(.,use = 'complete.obs')
@@
 
-```{r eval = FALSE}
+```{r}
 print(solution$loadings, sort=T)

### 2017-02-28 SRO_Retest_Analyses.Rmd
cont working on retest exploration

@@
 ```{r}
-unrotated <- efaUnrotate(rest_subs_test_mngf_z, nf=3, varList=names(rest_subs_test_mngf_z)[-1], estimator="mlr")
+unrotated <- try(efaUnrotate(rest_subs_test_mngf_z, nf=3, varList=names(rest_subs_test_mngf_z)[-1], estimator="mlr"))
 
-summary(unrotated, std=TRUE)
-inspect(unrotated, "std")
+# summary(unrotated, std=TRUE)
+# inspect(unrotated, "std")
 ```

### 2017-03-07 SRO_Meaningful_Vars.Rmd
made new notebook just looking at meaningful vars

--- 2017-02-28 SRO_Retest_Analyses.Rmd
@@
 ---
-title: 'Self Regulation Ontology Retest Data: Initial Exploration'
+title: 'Self Regulation Ontology Retest Data: Meaningful Variables Clean'
 output:
@@
 sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
-render_this <- function(){rmarkdown::render('SRO_Retest_Analyses.Rmd', html_notebook(toc = T, toc_float = T))}
+render_this <- function(){rmarkdown::render('SRO_Meaningful_Vars.Rmd', html_notebook(toc = T, toc_float = T))}
 options(digits = 4)
@@
 
-### Load original data
+### Load original data (only cleaned meaningful variables)
 ```{r}
-test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/variables_exhaustive.csv')
+test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_clean.csv')
 ```
 
-### Load retest data
+### Load retest data (all variables; will subset and clean based on cleaned variables for test data)
 ```{r}
@@
 
-Drop columns from original data that are not in retest data
+```{r echo=FALSE}
+rm(test_worker_lookup, correct_subids, process_lookup)
+```
 
-Are there any columns in retest data columns that are not in the original data: No.
+Get only cleaned meaningful var columns based on test data from retest data
 
 ```{r}
-names(retest_data)[names(retest_data) %in% names(retest_subs_test_data) == FALSE]
+#Get list of meaningful vars
+meaningful_vars = names(test_data)
+
+#Remove transofrmation suffices to be able to use for subsetting of retest data
+meaningful_vars = gsub(".logTr|.ReflogTr", "", meaningful_vars)
+
+#Get list of transformed variables and the sign of their skew
+logTr_vars = data.frame(grep('logTr', names(test_data), value=T))
+names(logTr_vars) = c('var')
+logTr_vars$sign = ifelse(grepl(".ReflogTr",logTr_vars$var), 'negative', 'positive')
+logTr_vars$var = gsub(".logTr|.ReflogTr", "", logTr_vars$var)
+
+#Subset retest data
+retest_data = retest_data[, names(retest_data) %in% meaningful_vars]
 ```
 
-Test data columns that are not in the retest data: Two stage hasn't been fixed yet.
+Clean columns subsetted from retest data the way they have been for test data 
+**Question: Should I be removing outliers from the retest data? Or keep them if they were within the ranges in the test data even if they aren't in the retest data**
+````{r}
+#Function to remove outliers as they have been removed for the test data
+remove_outliers = function(data_column, quantile_range = 2.5){
 
-```{r}
-names(retest_subs_test_data)[names(retest_subs_test_data) %in% names(retest_data) == FALSE]
+  q_25 = quantile(data_column, na.rm=T)[2]
+  q_50 = quantile(data_column, na.rm=T)[3]
+  q_75 = quantile(data_column, na.rm=T)[4]
+
+  lowlimit = q_50 - quantile_range*(q_75 - q_25)
+  highlimit = q_50 + quantile_range*(q_75 - q_25)
+
+  data_column = ifelse(data_column<lowlimit, NA, ifelse(data_column>highlimit, NA, data_column))
+
+  return(data_column)
+}
+
+#Function to transform the variables with negative skew
+neg_log <- function(column){
+  col_max = max(column, na.rm=T)
+  column = col_max+1-column
+  return(log(column))
+}
+
+#Remove outliers from retest data the way they have been from test data
+retest_data = cbind(sub_id = retest_data$sub_id, as.data.frame(apply(retest_data[, -which(names(retest_data) %in% c("sub_id"))], 2, remove_outliers)))
+
+#Transform necessary vars and rename those columns
+for(i in 1:length(names(retest_data))){
+  tmp_col = names(retest_data)[i]
+  if(tmp_col %in% logTr_vars$var){
+    sign = logTr_vars$sign[which(tmp_col == logTr_vars$var)]
+      if(sign == 'positive'){
+        retest_data[,tmp_col] = log(retest_data[,tmp_col])
+        names(retest_data)[i] = paste0(tmp_col, '.logTr')
+      }
+      else if(sign == 'negative'){
+        retest_data[,tmp_col] = neg_log(retest_data[,tmp_col])
+        names(retest_data)[i] = paste0(tmp_col, '.ReflogTr')
+      }
+    }
+}
+
 ```
 
-Datasets with only matching columns
+```{r echo = FALSE}
+rm(i, sign, tmp_col)
+```
+
+Check transformations are correct
+```{r}
+retest_logTr_vars = data.frame(grep('logTr', names(retest_data), value=T))
+names(retest_logTr_vars) = c('var')
+retest_logTr_vars$sign = ifelse(grepl(".ReflogTr",retest_logTr_vars$var), 'negative', 'positive')
+retest_logTr_vars$var = gsub(".logTr|.ReflogTr", "", logTr_vars$var)
+retest_logTr_vars == logTr_vars
+```
+
+```{r echo=FALSE}
+rm(logTr_vars, retest_logTr_vars, meaningful_vars)
+```
+
+# Correlations for all cleaned meaningful variables
+Spearman only
 
@@
 
-retest_data <- retest_data[,matching_columns]
-retest_subs_test_data <- retest_subs_test_data[,matching_columns]
-```
-
-# Correlations of exhaustive variables
-
-Get list of test retest correlations for all matching (numeric) columns in the test and retest data. Note two caveats:  
-**1. There are still some columns that weren't in both datasets listed above (e.g. two stage)**  
-**2. Unlike meaningful variables these variables are not (yet) rid of outliers or log transformed if skewed. This will be detailed below along with its problems.**
-
-```{r}
-retest_data <- as.data.frame(retest_data)
-retest_subs_test_data <- as.data.frame(retest_subs_test_data)
-
 matching_dv_columns <- c()
@@
 
-cor_df <- data.frame(pearson = rep(NA, length(matching_dv_columns)), spearman = rep(NA, length(matching_dv_columns)))
+cor_df <- data.frame(spearman = rep(NA, length(matching_dv_columns)))
 
@@
 for(i in 1:length(matching_dv_columns)){
-  cor_df[matching_dv_columns[i], 'pearson'] <- cor(retest_data[,matching_dv_columns[i]], retest_subs_test_data[,matching_dv_columns[i]], method = 'pearson', use = "pairwise.complete.obs")
   cor_df[matching_dv_columns[i], 'spearman'] <- cor(retest_data[,matching_dv_columns[i]],retest_subs_test_data[,matching_dv_columns[i]], method = 'spearman', use = "pairwise.complete.obs")
@@
 cor_df %>%
-  gather(key, value) %>%
-  ggplot(aes(value))+
+  ggplot(aes(spearman))+
   geom_histogram()+
   theme_bw()+
-  facet_wrap(~key)
+  ggtitle('Distribution of Spearman correlations for cleaned meaningful variables')
 ```
@@
 Survey reliabilities are noticably higher than task reliabilities.
-
-Task reliability distributions looks alsmost bimodal. **Should figure out whether the lower ones are specific tasks or if they are certain kinds of vars (e.g. certain ddm parameters)**
 ```{r warning=FALSE, message=FALSE}
 cor_df %>%
-  gather(key, value, -dv, -task) %>%
-  ggplot(aes(value))+
+  ggplot(aes(spearman))+
   geom_histogram()+
   theme_bw()+
-  facet_wrap(key~task)
+  facet_wrap(~task)
 ```
+
 Mean reliability and the number of variables for both the surveys and the tasks
@@
   group_by(task) %>%
-  summarise(mean_pearson = mean(pearson),
-            mean_spearman = mean(spearman),
+  summarise(mean_spearman = mean(spearman),
             num_vars = n())
@@
   filter(task == 'task') %>%
-  select(dv, spearman, pearson) %>%
-  arrange(-pearson, -spearman)
+  select(dv, spearman) %>%
+  arrange(-spearman)
 ```
@@
 
-Note: Holt and Laury test-retest is pretty terrible. In previous data I have worked with it was ~.35. Should check to see if there is a coding error there.
+- Demographics are excluded from this list of variables.  
+- Holt and Laury test-retest is the worst for *surveys*.
+But note that this is not a survey that has been studied extensively psychometrically like others.
+This is more similar to out tasks (one that is used more often by economists).
+In previous data I have worked retest reliablities for this task was ~.35 so the results here are in line with this.
+- Otherwise the lowest survey reliabilities are 0.5.
 ```{r}
@@
   filter(task == 'survey') %>%
-  select(dv, spearman, pearson) %>%
-  arrange(-pearson, -spearman)
+  select(dv, spearman) %>%
+  arrange(-spearman)
 ```
@@
 
-The smaller meaningful_vars dataframe has been somewhat cleaned.
-So far in this notebook we looked at all the vars in their rawest form.
-Here we'll first check the distributions of all the variables and then apply the same cleaning procedure that was used for the meaningful variables to all of them.
+Keeping a record of the distributions of the cleaned meaningful variables.
 
-Note that I'm doing this for the sake of consistency for now.
-We might later decide that we would like to transform certain variables of interest in other ways to be able to include them in our analyses without violating the assumptions of those analyses.
-The current procedure checks the skewness of a column first removes the outliers defined as greater than 2.5 IQR from median then variables with skewness >1 are log transformed.
-
-First I'll check if the variables that went in to the correlation matrix have normal distributions since at least the Pearson correlations depend on this assumption.
-Then everything will be cleaned the way meaningful variables was cleaned.
-There is a problem with this approach that I'm not sure how to deal with yet but this will be detailed below.
-
-Function to check if the variables that went in to cor_df have normal distributions
 ```{r}
+# Function to check if the variables that went in to cor_df have normal distributions
 diff_from_normal <- function(col){
@@
 }
-```
 
-Create and organize new df where distribution of vars data is stored.
+# Create and organize new df where distribution of vars data is stored.
 First for retest data only; then for test data for subjects who have retest data - restricting here since these are the subsets of data that went in to the correlation matrix.
 Merge and cleanup.
-```{r}
+
 dist_retest_data <- as.data.frame(apply(retest_data[,matching_dv_columns], 2, diff_from_normal))
@@
 rm(dist_retest_data, dist_retest_subs_test_data)
-```
 
-Add whether dv's are tasks or survey to distribution dfs
-```{r}
+# Add whether dv's are tasks or survey to distribution dfs
+
 dist_data = cor_df %>%
@@
 List of variables that have different distributions in the two time points.
-A majority of them are drift diffusion parameters (but note that these vars are overrepresented to begin with - more on them later).
 ```{r}
@@
   filter(retest_not_normal != test_not_normal)
-```
-
-Apply the same cleaning procedure that was used for meaningful vars for all vars: 
-```{r}
-remove_outliers = function(data_column, quantile_range = 2.5){
-
-  q_25 = quantile(data_column, na.rm=T)[2]
-  q_50 = quantile(data_column, na.rm=T)[3]
-  q_75 = quantile(data_column, na.rm=T)[4]
-
-  lowlimit = q_50 - quantile_range*(q_75 - q_25)
-  highlimit = q_50 + quantile_range*(q_75 - q_25)
-
-  data_column = ifelse(data_column<lowlimit, NA, ifelse(data_column>highlimit, NA, data_column))
-
-  return(data_column)
-}
-
-"%w/o%" <- function(x, y) x[!x %in% y]
-
-neg_log <- function(column){
-  col_max = max(column, na.rm=T)
-  column = col_max+1-column
-  return(log(column))
-}
-
-transform_remove_skew = function(data, columns, threshold = 1){
-
-  tmp = as.data.frame(apply(data[,columns],2,skew))
-  names(tmp) = c("skew")
-  tmp$dv = row.names(tmp)
-  tmp = tmp %>% 
-    filter(abs(skew)>threshold)
-
-  skewed_variables = tmp$dv
-  skew_subset = data[, skewed_variables]
-  positive_subset = data[,tmp$dv[tmp$skew>0]]
-  negative_subset = data[,tmp$dv[tmp$skew<0]]
-
-  # transform variables
-  # log transform for positive skew
-  positive_subset = log(positive_subset)
-  successful_transforms = as.data.frame(apply(positive_subset, 2, skew))
-  names(successful_transforms) = c('skew')
-  successful_transforms$dv = row.names(successful_transforms)
-  successful_transforms = successful_transforms %>% filter(abs(skew)<threshold)
-  successful_transforms = successful_transforms$dv
-  successful_transforms = positive_subset[,successful_transforms]
-  dropped_vars = names(positive_subset) %w/o% names(successful_transforms)
-
-  # replace transformed variables
-  data = data[,-c(which(names(data) %in% names(positive_subset)))]
-  names(successful_transforms) = paste0(names(successful_transforms), '.logTr')
-  cat(rep('*', 40))
-  cat('\n')
-  cat(paste0('Dropping ', length(dropped_vars) ,' positively skewed data that could not be transformed successfully:'))
-  cat('\n')
-  cat(dropped_vars, sep = '\n')
-  cat(rep('*', 40))
-  cat('\n')
-  data = cbind(data, successful_transforms)
-
-  # reflected log transform for negative skew      
-  negative_subset = as.data.frame(apply(negative_subset, 2, neg_log))
-  successful_transforms = as.data.frame(apply(negative_subset, 2, skew))
-  names(successful_transforms) = c('skew')
-  successful_transforms$dv = row.names(successful_transforms)
-  successful_transforms = successful_transforms %>% filter(abs(skew)<1)
-  successful_transforms = successful_transforms$dv
-  successful_transforms = negative_subset[,successful_transforms]
-  dropped_vars = names(negative_subset) %w/o% names(successful_transforms)
-
-  # replace transformed variables
-  data = data[,-c(which(names(data) %in% names(negative_subset)))]
-  names(successful_transforms) = paste0(names(successful_transforms), '.ReflogTr')
-  cat(rep('*', 40))
-  cat('\n')
-  cat(paste0('Dropping ', length(dropped_vars) ,' negatively skewed data that could not be transformed successfully:'))
-  cat('\n')
-  cat(dropped_vars, sep = '\n')
-  cat(rep('*', 40))
-  cat('\n')
-  data = cbind(data, successful_transforms)
-
-  return(data)
-}
-```
-
-Clean retest data with these rules.
-```{r warning=FALSE}
-clean_retest_data = as.data.frame(apply(retest_data[, matching_dv_columns], 2, remove_outliers))
-clean_retest_data = transform_remove_skew(clean_retest_data, matching_dv_columns)
-```
-
-**I'm not sure what the right thing to do is regarding the cleaning of the test data for the retest subjects.**   
-Should they be cleaned on the whole sample for the time they were collected on and then extracted (this should have an effect on outliers as well as transformations) or extracted and then cleaned.
-Here I am doing the latter but this seems to be resulting in more skewed variables for test data compared to the retest data so the later correlation matrix might not include all the variables we would like to look at.
-
-```{r warning=FALSE}
-clean_retest_subs_test_data = as.data.frame(apply(retest_subs_test_data[, matching_dv_columns], 2, remove_outliers))
-clean_retest_subs_test_data = transform_remove_skew(clean_retest_subs_test_data, matching_dv_columns)
-```
-
-## Correlations on cleaned variables
-
-Create the same list of correlations as before but this time on a smaller set of cleaned variables.
-
-```{r warning=FALSE, message=FALSE}
-clean_all_columns <- unique(c(names(clean_retest_data), names(clean_retest_subs_test_data)))
-
-clean_matching_columns <- c()
-for(i in 1:length(clean_all_columns)){
-  if(clean_all_columns[i] %in% names(clean_retest_data) & clean_all_columns[i] %in% names(clean_retest_subs_test_data)){
-    clean_matching_columns <- c(clean_matching_columns, clean_all_columns[i])
-  }
-}
-
-# clean_retest_data <- clean_retest_data[,clean_matching_columns]
-# clean_retest_subs_test_data <- clean_retest_subs_test_data[,clean_matching_columns]
-
-clean_matching_dv_columns <- c()
-
-for(i in 1:length(clean_matching_columns)){
-  if(is.numeric(clean_retest_data[,clean_matching_columns[i]]) & is.numeric(clean_retest_subs_test_data[,clean_matching_columns[i]])){
-    clean_matching_dv_columns <- c(clean_matching_dv_columns, clean_matching_columns[i])
-  }
-}
-
-clean_cor_df <- data.frame(pearson = rep(NA, length(clean_matching_dv_columns)), spearman = rep(NA, length(clean_matching_dv_columns)))
-
-row.names(clean_cor_df) <- clean_matching_dv_columns
-
-for(i in 1:length(clean_matching_dv_columns)){
-
-  robustCor <- function(...) {
-    obj<-try(cor(...), silent=TRUE)
-    if (is(obj, "try-error")) return(NA) else return(obj)
-  }
-
-  tmp_pearson = robustCor(clean_retest_data[,clean_matching_dv_columns[i]], clean_retest_subs_test_data[,clean_matching_dv_columns[i]], method = 'pearson', use = "pairwise.complete.obs")
-
-  tmp_spearman = robustCor(clean_retest_data[,clean_matching_dv_columns[i]], clean_retest_subs_test_data[,clean_matching_dv_columns[i]], method = 'spearman', use = "pairwise.complete.obs")
-
-  clean_cor_df[clean_matching_dv_columns[i], 'pearson'] <- tmp_pearson 
-  clean_cor_df[clean_matching_dv_columns[i], 'spearman'] <- tmp_spearman
-
-}
-
-clean_cor_df$dv = row.names(clean_cor_df)
-row.names(clean_cor_df) = seq(1:nrow(clean_cor_df))
-clean_cor_df$task = 'task'
-clean_cor_df[grep('survey', clean_cor_df$dv), 'task'] = 'survey'
-```
-
-Correlations could not be calculated for the following variables due to lack of variance.
-
-```{r}
-clean_cor_df %>%
-  filter(is.na(pearson)) %>%
-  select(dv)
-```
-
-Let's look at the distributions again: The distributions don't look terribly different but there are noticably fewer variables post cleaning. 
-```{r warning=FALSE, message=FALSE}
-cor_df %>%
-  left_join(clean_cor_df, by='dv') %>%
-  select(-task.y)%>%
-  rename(pearson_preClean = pearson.x, spearman_preClean = spearman.x,
-         pearson_postClean = pearson.y, spearman_postClean = spearman.y,
-         task = task.x) %>%
-  gather(key, value, -dv, -task) %>%
-  separate(key, c('cor_type', 'clean_type'),sep = "_") %>%
-  ggplot(aes(x=value, fill=factor(clean_type, levels = c('preClean', 'postClean'),
-                                  labels = c('Before', 'After'))))+
-  geom_histogram(position='identity', alpha = 0.5)+
-  facet_wrap(cor_type~task)+
-  theme_bw()+
-  theme(legend.title = element_blank())
-```
-
-This cleaning led to a slight change in the mean reliabilities but a lot of dropped variables.
-```{r}
-clean_cor_df %>%
-  group_by(task) %>%
-  summarise(mean_pearson = mean(pearson, na.rm=T),
-            mean_spearman = mean(spearman, na.rm=T),
-            num_vars = sum(ifelse(is.na(pearson)==FALSE,1,0)))
-```
-
-**What changed most with cleaning?**    
-Difference in correlation pre and post correlation for the variables that survived cleaning.  
-Things that changed most seem to be RTs and parameter estimates.
-
-```{r}
-clean_cor_df %>%
-  left_join(cor_df, by='dv') %>%
-  mutate(pearson_diff = abs(pearson.y - pearson.x),
-         spearman_diff = abs(spearman.y - spearman.x)) %>%
-  select(dv, pearson_diff, spearman_diff) %>%
-  arrange(-pearson_diff, -spearman_diff)
 ```
@@
 We should probably take a closer look at model fits instead but this could be a first step.
-I'm not sure why there are so many more EZ variables than hddm variables.
+
+The cleaned meaningful variables do not seem to include neither the EZ estimates nor accuracies
+so analyses on this [here](https://htmlpreview.github.io/?https://github.com/zenkavi/SRO_Retest_Analyses/blob/master/SRO_Retest_Analyses.nb.html) are more informative.
+Otherwise just looking at this one might be tempted to conclude that rt's have higher reliabilities but clearly
 
@@
 cor_df%>%
-  select(-pearson) %>%
   filter(grepl('EZ|hddm|_rt|_acc', dv)) %>%
@@
          var = ifelse(grepl('_rt', dv), 'rt', ifelse(grepl('_acc', dv), 'acc', ifelse(grepl('_non_decision', dv), 'non_decision', ifelse(grepl('_thresh', dv), 'thresh', ifelse(grepl('_drift', dv), 'drift', NA)))))) %>%
-  left_join(clean_cor_df[,c('spearman', 'dv')], by = 'dv') %>%
-  gather(clean_type, spearman, -dv, -var_type, -var, -task) %>%
-  mutate(clean_type = ifelse(clean_type == 'spearman.x','Before','After')) %>%
-  ggplot(aes(spearman, fill = clean_type))+
-  geom_histogram(position='identity', alpha = 0.5)+
+  ggplot(aes(spearman))+
+  geom_histogram()+
   theme_bw()+
-  facet_wrap(var_type~var)+
-  scale_fill_discrete(name = 'Clean type')
-
+  facet_wrap(var_type~var)
 ```
-
-Average reliabilities
-
-1. Cleaning doesn't seem to make a huge difference (at least for Spearman correlations) except for raw accuracies and hddm non_decision  
-2. There are many more EZ variabiles but the few hddm variables have slightly higher reliabilities (I'm not sure about the reason for the discrepancy between the number of variables)  
-3. Raw accuracies seem to have the worst reliabilities on average while hddm parameters the highest
 
@@
          var = ifelse(grepl('_rt', dv), 'rt', ifelse(grepl('_acc', dv), 'acc', ifelse(grepl('_non_decision', dv), 'non_decision', ifelse(grepl('_thresh', dv), 'thresh', ifelse(grepl('_drift', dv), 'drift', NA)))))) %>%
-  left_join(clean_cor_df[,c('spearman', 'dv')], by = 'dv') %>%
-  gather(clean_type, spearman, -dv, -var_type, -var, -task) %>%
-  mutate(clean_type = ifelse(clean_type == 'spearman.x','Before','After')) %>%
-  group_by(var_type, clean_type, var) %>%
+  group_by(var_type, var) %>%
   summarise(mean_spearman = mean(spearman, na.rm=T),
@@
             num_vars = sum(ifelse(is.na(spearman)==FALSE,1,0))) %>%
-  arrange(var_type, -as.numeric(as.factor(clean_type)))
+  arrange(var_type)
 ```
-
-## Other variable types
-
-I planned to look at differences between distributions of reliabilities for other variables types as well but I am not sure what these categories should be so I am deferring this for further discussions.
-My earlier notes suggested differences between other model parameters versus raw variables; subtraction versus basic variables; single versus multiple variables.I'm hoping we can come up with a more systematic definition that I can automatize or at least restrict to certain groups of variable instead of going through all 600+ variables and manually labeling them.
 
@@
 
-First do a t-test on all measures of T1 for subjects with and without retest to confirm that these two samples do not differ from each other significantly
+First do a t-test on all measures of T1 for subjects with and without retest to confirm that these two samples do not differ from each other significantly (FDR corrected)
 ```{r}
 ttest_df = data.frame(t_stat = rep(NA, length(matching_dv_columns)),
-                      p_val = rep(NA, length(matching_dv_columns)))
+                      p_val_raw = rep(NA, length(matching_dv_columns)))
 
@@
 
-  ttest_df[matching_dv_columns[i], 'p_val'] <- t.test(retest_subs_test_data[,matching_dv_columns[i]], rest_subs_test_data[,matching_dv_columns[i]])$p.value
+  ttest_df[matching_dv_columns[i], 'p_val_raw'] <- t.test(retest_subs_test_data[,matching_dv_columns[i]], rest_subs_test_data[,matching_dv_columns[i]])$p.value
 }
@@
 ttest_df[grep('survey', ttest_df$dv), 'task'] = 'survey'
+
+#correct p-values 
+ttest_df$p_val_fdr = p.adjust(ttest_df$p_val_raw, method='fdr')
 ```
 
-Distribution of t values
+```{r echo=TRUE}
+rm(i)
+```
+
+Distribution of t statistics and p values
 
@@
 ttest_df %>%
-  ggplot(aes(t_stat)) +
+  gather(key, value, -dv, -task) %>%
+  ggplot(aes(value)) +
   geom_histogram()+
   theme_bw()+
-  facet_wrap(~task)
+  facet_wrap(key~task, scales='free')
 ```
@@
 
-43 variables. None of them are very strongly different though.
+13 variables have raw p values <0.05 BUT FDR corrected p values for these are not <0.05.
 
@@
 ttest_df %>%
-  filter(p_val<0.05) %>%
-  select(dv, task, t_stat, p_val)
-```
-
-Do this again with cleaned data.  
-Clean the T1 data for the subsets first.  
-**Here again I'm not sure if I should clean before or after splitting.
-Before it seemed appropriate to clean subjects with retest data after separating them from the remaining subjects but here it might be better to clean first and then separate.
-But then it would differ from what was done for earlier anaylses and it seems like the kind of thing that should be kept consistent.**
-
-Clean T1 for subjects with retest data (doing it again because this df was subsetted before)
-
-```{r warning=FALSE}
-clean_retest_subs_test_data = as.data.frame(apply(retest_subs_test_data[, matching_dv_columns], 2, remove_outliers))
-clean_retest_subs_test_data = transform_remove_skew(clean_retest_subs_test_data, matching_dv_columns)
-```
-
-Clean T1 for rest of the subjects
-
-```{r warning=FALSE}
-clean_rest_subs_test_data = as.data.frame(apply(rest_subs_test_data[, matching_dv_columns], 2, remove_outliers))
-clean_rest_subs_test_data = transform_remove_skew(clean_rest_subs_test_data, matching_dv_columns)
-```
-
-Get numeric dv's from both cleaned datasets to compute t-tests on.
-```{r}
-clean_all_columns <- unique(c(names(clean_rest_subs_test_data), names(clean_retest_subs_test_data)))
-
-clean_matching_columns <- c()
-for(i in 1:length(clean_all_columns)){
-  if(clean_all_columns[i] %in% names(clean_rest_subs_test_data) & clean_all_columns[i] %in% names(clean_retest_subs_test_data)){
-    clean_matching_columns <- c(clean_matching_columns, clean_all_columns[i])
-  }
-}
-
-clean_matching_dv_columns <- c()
-
-for(i in 1:length(clean_matching_columns)){
-  if(is.numeric(clean_rest_subs_test_data[,clean_matching_columns[i]]) & is.numeric(clean_rest_subs_test_data[,clean_matching_columns[i]])){
-    clean_matching_dv_columns <- c(clean_matching_dv_columns, clean_matching_columns[i])
-  }
-}
-```
-
-Compute t-tests for cleaned variables.
-```{r}
-clean_ttest_df = data.frame(t_stat = rep(NA, length(clean_matching_dv_columns)),
-                      p_val = rep(NA, length(clean_matching_dv_columns)))
-
-row.names(clean_ttest_df) <- clean_matching_dv_columns
-
-for(i in 1:length(clean_matching_dv_columns)){
-
-  robustTTest <- function(...) {
-    obj<-try(t.test(...), silent=TRUE)
-    if (is(obj, "try-error")) return(obj = data.frame(statistic = NA, p.value=NA)) else return(obj)
-  }
-
-  tmp = robustTTest(clean_retest_subs_test_data[,clean_matching_dv_columns[i]], clean_rest_subs_test_data[,clean_matching_dv_columns[i]])
-
-  clean_ttest_df[clean_matching_dv_columns[i], 't_stat'] <- tmp$statistic 
-  clean_ttest_df[clean_matching_dv_columns[i], 'p_val'] <- tmp$p.value
-    }
-
-clean_ttest_df$dv = row.names(clean_ttest_df)
-row.names(clean_ttest_df) = seq(1:nrow(clean_ttest_df))
-clean_ttest_df$task = 'task'
-clean_ttest_df[grep('survey', clean_ttest_df$dv), 'task'] = 'survey'
-```
-
-Variables for which t-tests cannot be computed due to lack of variance.
-```{r}
-clean_ttest_df %>%
-  filter(is.na(t_stat)) %>%
-  select(dv)
-```
-
-Distribution of t-tests for the cleaned variables with sufficient variance
-```{r warning=FALSE, message=FALSE}
-clean_ttest_df %>%
-  filter(!is.na(t_stat)) %>%
-ggplot(aes(t_stat)) +
-  geom_histogram()+
-  theme_bw()+
-  facet_wrap(~task)
-```
-
-**Which variables are significantly different between the two samples on cleaned data (those with and without retest data for T1)?**
-
-More variables (that are thought to have been properly cleaned for these analyses) are significantly different between the two samples.   
-**Not sure what to do with this especially for the next set of analyses.**
-
-```{r}
-clean_ttest_df %>%
-  filter(!is.na(p_val) & p_val<0.05) %>%
-  select(dv, task, t_stat, p_val)
+  filter(p_val_raw<0.05) %>%
+  select(dv, task, t_stat, p_val_raw, p_val_fdr)
 ```
@@
 
-Step 2: Efa on the people you don't have retest on and then predict how well this holds up for people w retest on t1 and on t2.
+Efa on the people you don't have retest on and then predict how well this holds up for people w retest on t1 and on t2.
 
-I'm restricting the factor analyses to the meaningful variables for now (instead of the 600+ exhaustive variables) to keep it manageable.
 I haven't consulted other factor analyses that have been done on the full dataset in doing this but will be happy to adjust as necessary.
 
-Data cleaning for efa
-```{r eval=FALSE}
-#read in only meaningful vars
-meaningful_var_test <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_clean.csv')
-
-meaningful_var_retest <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/meaningful_variables_clean.csv')
-
-#Process sub_id columns in the data dataframes
-meaningful_var_retest$X <- as.character(meaningful_var_retest$X)
-meaningful_var_test$X <- as.character(meaningful_var_test$X)
-
-names(meaningful_var_retest)[1] <- 'sub_id'
-names(meaningful_var_test)[1] <- 'sub_id'
-
-#Clean and subset dfs as before
-meaningful_var_retest <- meaningful_var_retest %>%
-  group_by(sub_id) %>%
-  do(correct_subids(.,test_worker_lookup))
-
-#Remove sub w missing test data from retest data
-retest_data_mngf <- meaningful_var_retest[meaningful_var_retest$sub_id %in% meaningful_var_test$sub_id,]
-
-#Extract test data for subs w retest data
-retest_subs_test_mngf <- meaningful_var_test[meaningful_var_test$sub_id %in% meaningful_var_retest$sub_id,]
-
-#Extract test data for subs without retest data (efa df)
-rest_subs_test_mngf <- meaningful_var_test[meaningful_var_test$sub_id %in% meaningful_var_retest$sub_id == FALSE,]
-
-#Arrange datasets of same size by sub_id
-retest_data_mngf = retest_data_mngf %>% arrange(sub_id)
-retest_subs_test_mngf = retest_subs_test_mngf %>% arrange(sub_id)
-
-#CHECK IF EVERYTHING IS ORDERED RIGHT
-retest_subs_test_mngf$sub_id == retest_data_mngf$sub_id
-```
-
-Checking columns for efa:
-There
-```{r eval=FALSE}
-#Check columns 
-names(retest_data_mngf)[names(retest_data_mngf) %in% names(retest_subs_test_mngf) == FALSE]
-
-names(retest_subs_test_mngf)[names(retest_subs_test_mngf) %in% names(retest_data_mngf) == FALSE]
-```
-
-For now I'm just removing these variables but will have to do re-do them once I resolve why they weren't in both datasets to begin with (The answer will be a combination of not having run the most recent analysis script on some tasks and dropped variables as a result of cleaning)
 ```{r}
-#Subset datasets with only matching columns
-all_columns_mngf <- unique(c(names(retest_data_mngf), names(retest_subs_test_mngf)))
-
-matching_columns_mngf <- c()
-for(i in 1:length(all_columns_mngf)){
-  if(all_columns_mngf[i] %in% names(retest_data_mngf) & all_columns_mngf[i] %in% names(retest_subs_test_mngf)){
-    matching_columns_mngf <- c(matching_columns_mngf, all_columns_mngf[i])
-  }
-}
-
-retest_data_mngf <- retest_data_mngf[,matching_columns_mngf]
-retest_subs_test_mngf <- retest_subs_test_mngf[,matching_columns_mngf]
-rest_subs_test_mngf <- rest_subs_test_mngf[,matching_columns_mngf]
+retest_data_mngf <- retest_data[,matching_dv_columns]
+retest_subs_test_mngf <- retest_subs_test_data[,matching_dv_columns]
+rest_subs_test_mngf <- rest_subs_test_data[,matching_dv_columns]
 
@@
 for(i in 1:length(rest_subs_test_mngf)){
-  if(names(rest_subs_test_mngf)[i] == 'sub_id'){
-    rest_subs_test_mngf_z$sub_id = rest_subs_test_mngf$sub_id
-  }
-  else{
     rest_subs_test_mngf_z[,names(rest_subs_test_mngf)[i]] = scale(rest_subs_test_mngf[,i])
-  }
 }
@@
 Efa on subjects from original dataset withOUT retest data (using meaningful vars only)  
-
-Trying to use `lavaan` first. It's not happy with me.
-```{r}
-unrotated <- efaUnrotate(rest_subs_test_mngf_z, nf=3, varList=names(rest_subs_test_mngf_z)[-1], estimator="mlr")
-
-summary(unrotated, std=TRUE)
-inspect(unrotated, "std")
-```
-
 Using the `psych` package I get some sort of solution but these are probably not valid given all the warnings.
 ```{r}
-corMat <- rest_subs_test_mngf_z %>% select(-sub_id) %>% cor(.,use = 'complete.obs')
+corMat <- rest_subs_test_mngf_z %>% cor(.,use = 'complete.obs')
 
@@
 ```
-
-# Completion times/days
-
-# Invited vs. completed retest
-
-T1 comparison for people who came back vs didn't (of all that are invited)

### 2017-03-07 SRO_Retest_Analyses.Rmd
made new notebook just looking at meaningful vars

@@
 for(i in 1:length(matching_dv_columns)){
-  ttest_df[matching_dv_columns[i], 't_stat'] <- t.test(retest_subs_test_data[,matching_dv_columns[i]], rest_subs_test_data[,matching_dv_columns[i]])$statistic
+  ttest_df[matching_dv_columns[i], 't_stat'] <- pairwise.t.test(retest_subs_test_data[,matching_dv_columns[i]], rest_subs_test_data[,matching_dv_columns[i]], p.adjust.method = 'fdr')$statistic
 
-  ttest_df[matching_dv_columns[i], 'p_val'] <- t.test(retest_subs_test_data[,matching_dv_columns[i]], rest_subs_test_data[,matching_dv_columns[i]])$p.value
+  ttest_df[matching_dv_columns[i], 'p_val'] <- t.test(retest_subs_test_data[,matching_dv_columns[i]], rest_subs_test_data[,matching_dv_columns[i]], p.adjust.method = 'fdr')$p.value
 }
@@
 ttest_df[grep('survey', ttest_df$dv), 'task'] = 'survey'
+```
+
+```{r eval=FALSE, echo=FALSE}
+corrected_ttest <- function(df1, df2, col){
+
+  x = df1[,col]
+  y = df2[,col]
+
+  n <- max(length(x), length(y))
+  length(x) <- n                      
+  length(y) <- n
+
+  tmp = as.data.frame(cbind(x,y))
+
+  tmp = tmp %>% 
+    gather(key, value)
+
+  return(pairwise.t.test(tmp$value,tmp$key, p.adjust.method = 'fdr'))
+}
 ```
@@
 T1 comparison for people who came back vs didn't (of all that are invited)
+
+- Ignore Pearson for now and just focus on Spearman
+- Eventually want to get to interclass correlations (between versus within group variability - using anova)
+- Clean everything on the whole sample and extract from that. Keep a record of everything that was transformed and whether it was normal at the end

### 2017-03-09 SRO_Meaningful_Vars.Rmd
Organizing shorter nb

@@
 
-```{r echo=TRUE}
+```{r echo=FALSE}
 rm(i)
@@
 
-solution <- fa(r = corMat, nfactors = 3, rotate = "oblimin", fm = "pa")
+solution <- fa(r = corMat, nfactors = 7, rotate = "oblimin", fm = "pa")
 ```
@@
 ```
+
+```{r}
+# Pricipal Components Analysis
+# entering raw data and extracting PCs 
+# from the correlation matrix 
+fit <- principal(rest_subs_test_mngf_z, nfactors=7, rotate="varimax")
+fit
+
+fit <- princomp(rest_subs_test_mngf_z, cor=TRUE)
+summary(fit) # print variance accounted for 
+loadings(fit) # pc loadings 
+plot(fit,type="lines") # scree plot 
+fit$scores # the principal components
+biplot(fit)
+```

### 2017-03-15 SRO_Retest_Analyses.Rmd
minor typo

@@
 - Ignore Pearson for now and just focus on Spearman
-- Eventually want to get to interclass correlations (between versus within group variability - using anova)
+- Eventually want to get to intraclass correlations (between versus within group variability - using anova)
 - Clean everything on the whole sample and extract from that. Keep a record of everything that was transformed and whether it was normal at the end

### 2017-03-16 SRO_Report.Rmd
working on new report

--- 2017-03-09 SRO_Meaningful_Vars.Rmd
@@
 ---
-title: 'Self Regulation Ontology Retest Data: Meaningful Variables Clean'
+title: 'Self Regulation Ontology Retest Data Report'
 output:
@@
 sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
-render_this <- function(){rmarkdown::render('SRO_Meaningful_Vars.Rmd', html_notebook(toc = T, toc_float = T))}
+render_this <- function(){rmarkdown::render('SRO_Report.Rmd', html_notebook(toc = T, toc_float = T))}
 options(digits = 4)
@@
 
-# Loading and matching datasets
+# Introduction
 
-### Load original data (only cleaned meaningful variables)
+# Methods
+
+## Loading and matching datasets
+
+Using the variables that were designated as meaningful before.
+This is not the smallest subset where certain variables are dropped because they are correlated with other variables and includes both accuracies as well as both kinds of DDM variables (EZ and HDDM).
+It will not include variables that were considered not of theoretical interest in the analyses of time 1 data.
+The variables that are not included will be listed for reference as well.
+
+### Load time 1 data
 ```{r}
-test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_clean.csv')
+test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables.csv')
+
+test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_noDDM.csv')
+
+test_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_EZ.csv')
+
+test_data <- merge(test_data, test_data2)
+test_data <- merge(test_data, test_data3)
+rm(test_data2, test_data3)
 ```
 
-### Load retest data (all variables; will subset and clean based on cleaned variables for test data)
+For reference here are the variables that are not included because they were not of theoretical interest in factor structure analyses of this data so far.
+
 ```{r}
-retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/variables_exhaustive.csv')
+test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/variables_exhaustive.csv')
+
+test_data2$X <- as.character(test_data2$X)
+
+names(test_data2)[1] <- 'sub_id'
+
+df <- data.frame(names(test_data2)[which(names(test_data2) %in% names(test_data) == FALSE)])
+names(df) = c('vars')
+
+df
 ```
 
-Function to process lookup table
-```{r}
-process_lookup <- function(lookup_json){
-  lookup_json <- data.frame(unlist(lookup_json))
-  lookup_json$sub_id <- as.character(row.names(lookup_json))
-  row.names(lookup_json) <- seq(1:nrow(lookup_json))
-  names(lookup_json)[1] <- 'worker_id'
-  lookup_json$worker_id <- as.character(lookup_json$worker_id)
-  lookup_json$complete <- ifelse(lookup_json$worker_id == lookup_json$sub_id, 0, 1)
-  lookup_json <- lookup_json %>% arrange(-complete, sub_id)
-  return(lookup_json)
-}
+```{r echo=FALSE}
+rm(test_data2, df)
 ```
 
-### Extract retest participants from test data
+### Load time 2 data 
+```{r}
+retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/meaningful_variables.csv')
+
+retest_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/meaningful_variables_noDDM.csv')
+
+retest_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/meaningful_variables_EZ.csv')
+
+retest_data <- merge(retest_data, retest_data2)
+retest_data <- merge(retest_data, retest_data3)
+rm(retest_data2, retest_data3)
+```
+
+Extract retest participants from test data
 
 ```{r}
-test_worker_lookup <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/Local/worker_lookup.json')
-
-#Process full lookup tables for both datasets
-test_worker_lookup <- process_lookup(test_worker_lookup)
-
 #Process sub_id columns in the data dataframes
@@
 
-#Trim lookup table to only include those we have data for
-test_worker_lookup <- test_worker_lookup[test_worker_lookup$sub_id %in% test_data$sub_id,]
+retest_data <- retest_data[retest_data$sub_id %in% test_data$sub_id,]
+```
 
-#Replace worker_id's in retest_data with original sub_id's 
-correct_subids <- function(row, lookup_table){
-  sub_id = row$sub_id
-  if(sub_id %in% lookup_table$worker_id){
-    index = which(sub_id == lookup_table$worker_id)
-    sub_id = lookup_table$sub_id[index]
-    row$sub_id = sub_id
-  }
-  return(row)
+### Clean t1 data
+
+The cleaning functions here are translated from the python pipeline to mimick the same procedure.
+
+Our cleaning procedures includes two steps:  
+1. removing outliers for each variables where outliers are defined as those who are greater than 2.5 IQR from median  
+2.
+Log transforming variables with skew.
+In cleaning T1 data for the `meaningful_variables_clean.csv` variables for which skew could not be removed successfully were dropped.
+**This step is excluded here.
+Variables that are not successfully transformed will be noted but not dropped.**
+
+```{r}
+remove_outliers = function(data_column, quantile_range = 2.5){
+
+  q_25 = quantile(data_column, na.rm=T)[2]
+  q_50 = quantile(data_column, na.rm=T)[3]
+  q_75 = quantile(data_column, na.rm=T)[4]
+
+  lowlimit = q_50 - quantile_range*(q_75 - q_25)
+  highlimit = q_50 + quantile_range*(q_75 - q_25)
+
+  data_column = ifelse(data_column<lowlimit, NA, ifelse(data_column>highlimit, NA, data_column))
+
+  return(data_column)
 }
 
-retest_data <- retest_data %>%
-  group_by(sub_id) %>%
-  do(correct_subids(.,test_worker_lookup))
+"%w/o%" <- function(x, y) x[!x %in% y]
+
+neg_log <- function(column){
+  col_max = max(column, na.rm=T)
+  column = col_max+1-column
+  return(log(column))
+}
+
+transform_remove_skew = function(data, columns, threshold = 1){
+
+  tmp = as.data.frame(apply(data[,columns],2,skew))
+  names(tmp) = c("skew")
+  tmp$dv = row.names(tmp)
+  tmp = tmp %>% 
+    filter(abs(skew)>threshold)
+
+  skewed_variables = tmp$dv
+  skew_subset = data[, skewed_variables]
+  positive_subset = data[,tmp$dv[tmp$skew>0]]
+  negative_subset = data[,tmp$dv[tmp$skew<0]]
+
+  # transform variables
+  # log transform for positive skew
+  positive_subset = log(positive_subset)
+  successful_transforms = as.data.frame(apply(positive_subset, 2, skew))
+  names(successful_transforms) = c('skew')
+  successful_transforms$dv = row.names(successful_transforms)
+  successful_transforms = successful_transforms %>% filter(abs(skew)<threshold)
+  successful_transforms = successful_transforms$dv
+  successful_transforms = positive_subset[,successful_transforms]
+  dropped_vars = names(positive_subset) %w/o% names(successful_transforms)
+
+  # replace transformed variables
+  data = data[,-c(which(names(data) %in% names(positive_subset)))]
+  names(successful_transforms) = paste0(names(successful_transforms), '.logTr')
+  cat(rep('*', 40))
+  cat('\n')
+  cat(paste0('Dropping ', length(dropped_vars) ,' positively skewed data that could not be transformed successfully:'))
+  cat('\n')
+  cat(dropped_vars, sep = '\n')
+  cat(rep('*', 40))
+  cat('\n')
+  data = cbind(data, successful_transforms)
+
+  # reflected log transform for negative skew      
+  negative_subset = as.data.frame(apply(negative_subset, 2, neg_log))
+  successful_transforms = as.data.frame(apply(negative_subset, 2, skew))
+  names(successful_transforms) = c('skew')
+  successful_transforms$dv = row.names(successful_transforms)
+  successful_transforms = successful_transforms %>% filter(abs(skew)<1)
+  successful_transforms = successful_transforms$dv
+  successful_transforms = negative_subset[,successful_transforms]
+  dropped_vars = names(negative_subset) %w/o% names(successful_transforms)
+
+  # replace transformed variables
+  data = data[,-c(which(names(data) %in% names(negative_subset)))]
+  names(successful_transforms) = paste0(names(successful_transforms), '.ReflogTr')
+  cat(rep('*', 40))
+  cat('\n')
+  cat(paste0('Dropping ', length(dropped_vars) ,' negatively skewed data that could not be transformed successfully:'))
+  cat('\n')
+  cat(dropped_vars, sep = '\n')
+  cat(rep('*', 40))
+  cat('\n')
+  data = cbind(data, successful_transforms)
+
+  return(data)
+}
 ```
 
-### Checks and matching issues
-
-Are all retest subjects in test_data? No. 
-```{r}
-sum(retest_data$sub_id %in% test_data$sub_id) == nrow(retest_data)
-```
-
-Who is missing?
-```{r}
-retest_data$sub_id[which(retest_data$sub_id %in% test_data$sub_id == FALSE)]
-```
-
-One retest participant is not in test data.
-Remove that subject from retest_data.
-This participant should not have completed the retest battery to begin with because they had failed our previous criterion on number of properly completed trials.
-The first HIT I posted, however, had an issue with the qualifications and before I could terminate it a handful of subjects had accepted and begun the battery so we had to let them finish.
-So this subject has given us good data for the retest battery but worse data for the test battery.
-```{r}
-retest_data <- retest_data[retest_data$sub_id %in% test_data$sub_id,]
-
-retest_data
-```
-
+------------------------------------------------------------------------
 Extract test data for retest subjects
@@
 retest_subs_test_data$sub_id == retest_data$sub_id
-```
-
-```{r echo=FALSE}
-rm(test_worker_lookup, correct_subids, process_lookup)
-```
-
-Get only cleaned meaningful var columns based on test data from retest data
-
-```{r}
-#Get list of meaningful vars
-meaningful_vars = names(test_data)
-
-#Remove transofrmation suffices to be able to use for subsetting of retest data
-meaningful_vars = gsub(".logTr|.ReflogTr", "", meaningful_vars)
-
-#Get list of transformed variables and the sign of their skew
-logTr_vars = data.frame(grep('logTr', names(test_data), value=T))
-names(logTr_vars) = c('var')
-logTr_vars$sign = ifelse(grepl(".ReflogTr",logTr_vars$var), 'negative', 'positive')
-logTr_vars$var = gsub(".logTr|.ReflogTr", "", logTr_vars$var)
-
-#Subset retest data
-retest_data = retest_data[, names(retest_data) %in% meaningful_vars]
 ```
@@
 
-# Correlations for all cleaned meaningful variables
+# Results
+
+## Correlations for all cleaned meaningful variables
 Spearman only
@@
 
-## Distributions of correlations by task vs. survey
+### Distributions of correlations by task vs. survey
 
@@
 
-### Rank order of correlations
+#### Rank order of correlations
 
-#### For tasks
+##### For tasks
 ```{r}
@@
 
-#### For surveys
+##### For surveys
 
@@
 
-# Different task variable types
+## Different task variable types
 
@@
 
-## Drift diffusion variables: raw vars vs. EZ vs. hddm
+### Drift diffusion variables: raw vars vs. EZ vs. hddm
+
+**DO THIS ON VARIABLES EXHAUSTIVE GETTING ALL RT AND ACC'S**
 
@@
 
-# Replicating the factor structure
+## Replicating the factor structure
 
-## Confirm comparability of retest and rest sample
+### Confirm comparability of retest and rest sample
 
@@
 
-## Efa and Cfa
+### Efa and Cfa
+
+**DO ONLY ON SURVEY AND TASK DATA SEPARATELY**
 

### 2017-03-16 SRO_Report.Rmd
working on new report

@@
 
-Using the variables that were designated as meaningful before.
-This is not the smallest subset where certain variables are dropped because they are correlated with other variables and includes both accuracies as well as both kinds of DDM variables (EZ and HDDM).
+This report uses the variables that were designated as "meaningful" before.
+This is not the smallest subset where certain variables are dropped because they are correlated with other variables (within a task) and includes both accuracies as well as both kinds of DDM variables (EZ and HDDM).
 It will not include variables that were considered not of theoretical interest in the analyses of time 1 data.
@@
 
-For reference here are the variables that are not included because they were not of theoretical interest in factor structure analyses of this data so far.
+For reference here are the variables that are **not** included because they were not of theoretical interest in factor structure analyses of this data so far.
 
@@
 
-Our cleaning procedures includes two steps:  
+The cleaning procedures include two steps:  
 1. removing outliers for each variables where outliers are defined as those who are greater than 2.5 IQR from median  
@@
 **This step is excluded here.
-Variables that are not successfully transformed will be noted but not dropped.**
+Variables that are not successfully transformed will be listed but not dropped.**
 
@@
 
-transform_remove_skew = function(data, columns, threshold = 1){
+transform_remove_skew = function(data, columns, threshold = 1, drop=FALSE){
 
@@
   data = data[,-c(which(names(data) %in% names(positive_subset)))]
+
+  if(drop == TRUE){
     names(successful_transforms) = paste0(names(successful_transforms), '.logTr')
@@
     data = cbind(data, successful_transforms)
+  }
+  else{
+    names(positive_subset) = paste0(names(positive_subset), '.logTr')
+    cat(rep('*', 40))
+    cat('\n')
+    cat(paste0(length(dropped_vars) ,' positively skewed data could not be transformed successfully:'))
+    cat('\n')
+    cat(dropped_vars, sep = '\n')
+    cat(rep('*', 40))
+    cat('\n')
+    data = cbind(data, positive_subset)
+  }
 
@@
   data = data[,-c(which(names(data) %in% names(negative_subset)))]
+  if(drop == TRUE){
     names(successful_transforms) = paste0(names(successful_transforms), '.ReflogTr')
@@
     data = cbind(data, successful_transforms)
+  }
+  else{
+    names(negative_subset) = paste0(names(negative_subset), '.ReflogTr')
+    cat(rep('*', 40))
+    cat('\n')
+    cat(paste0(length(dropped_vars) ,' negatively skewed data could not be transformed successfully:'))
+    cat('\n')
+    cat(dropped_vars, sep = '\n')
+    cat(rep('*', 40))
+    cat('\n')
+    data = cbind(data, negative_subset)
+  }
 
@@
 
-------------------------------------------------------------------------
-Extract test data for retest subjects
+Clean test data on full sample without dropping any columns. Columns that are not transformed successfully are listed.
+
+```{r}
+numeric_cols = c()
+
+for(i in 1:length(names(test_data))){
+  if(is.numeric(test_data[,i])){
+    numeric_cols <- c(numeric_cols, names(test_data)[i])
+  }
+}
+
+clean_test_data = cbind(sub_id = test_data$sub_id, as.data.frame(apply(test_data[, -which(names(retest_data) %in% c("sub_id"))], 2, remove_outliers)))
+
+clean_test_data = transform_remove_skew(clean_test_data, numeric_cols)
+```
+
+```{r echo=FALSE}
+rm(i)
+```
+
+### Clean t2 data
+
+Instead of applying the same functions applied to t1 data we check which variables are transformed in what way and transform the t2 data the same way.
+
+**Question: Should I be removing outliers from the retest data?
+Or keep them if they were within the ranges in the test data even if they aren't in the retest data.
+Right now I'm removing them depending on t2 distributions**
+
+```{r}
+#Remove outliers from retest data the way they have been from test data
+clean_retest_data = cbind(sub_id = retest_data$sub_id, as.data.frame(apply(retest_data[, -which(names(retest_data) %in% c("sub_id"))], 2, remove_outliers)))
+
+#Get list of transformed variables and the sign of their skew
+logTr_vars = data.frame(grep('logTr', names(clean_test_data), value=T))
+names(logTr_vars) = c('var')
+logTr_vars$sign = ifelse(grepl(".ReflogTr",logTr_vars$var), 'negative', 'positive')
+logTr_vars$var = gsub(".logTr|.ReflogTr", "", logTr_vars$var)
+
+#Transform necessary vars and rename those columns
+for(i in 1:length(names(clean_retest_data))){
+  tmp_col = names(clean_retest_data)[i]
+  if(tmp_col %in% logTr_vars$var){
+    sign = logTr_vars$sign[which(tmp_col == logTr_vars$var)]
+      if(sign == 'positive'){
+        clean_retest_data[,tmp_col] = log(clean_retest_data[,tmp_col])
+        names(clean_retest_data)[i] = paste0(tmp_col, '.logTr')
+      }
+      else if(sign == 'negative'){
+        clean_retest_data[,tmp_col] = neg_log(clean_retest_data[,tmp_col])
+        names(clean_retest_data)[i] = paste0(tmp_col, '.ReflogTr')
+      }
+    }
+}
+```
+
+```{r echo = FALSE}
+rm(i, sign, tmp_col)
+```
+
+Check transformations are correct
+```{r}
+retest_logTr_vars = data.frame(grep('logTr', names(clean_retest_data), value=T))
+names(retest_logTr_vars) = c('var')
+retest_logTr_vars$sign = ifelse(grepl(".ReflogTr",retest_logTr_vars$var), 'negative', 'positive')
+retest_logTr_vars$var = gsub(".logTr|.ReflogTr", "", logTr_vars$var)
+retest_logTr_vars == logTr_vars
+```
+
+```{r echo=F}
+rm(logTr_vars, retest_logTr_vars)
+```
+
+### Extract t-1 data for t-2 subjects
 ```{r}
@@
 retest_subs_test_data$sub_id == retest_data$sub_id
-```
-
-Clean columns subsetted from retest data the way they have been for test data   
-**Question: Should I be removing outliers from the retest data? Or keep them if they were within the ranges in the test data even if they aren't in the retest data**
-````{r}
-#Function to remove outliers as they have been removed for the test data
-remove_outliers = function(data_column, quantile_range = 2.5){
-
-  q_25 = quantile(data_column, na.rm=T)[2]
-  q_50 = quantile(data_column, na.rm=T)[3]
-  q_75 = quantile(data_column, na.rm=T)[4]
-
-  lowlimit = q_50 - quantile_range*(q_75 - q_25)
-  highlimit = q_50 + quantile_range*(q_75 - q_25)
-
-  data_column = ifelse(data_column<lowlimit, NA, ifelse(data_column>highlimit, NA, data_column))
-
-  return(data_column)
-}
-
-#Function to transform the variables with negative skew
-neg_log <- function(column){
-  col_max = max(column, na.rm=T)
-  column = col_max+1-column
-  return(log(column))
-}
-
-#Remove outliers from retest data the way they have been from test data
-retest_data = cbind(sub_id = retest_data$sub_id, as.data.frame(apply(retest_data[, -which(names(retest_data) %in% c("sub_id"))], 2, remove_outliers)))
-
-#Transform necessary vars and rename those columns
-for(i in 1:length(names(retest_data))){
-  tmp_col = names(retest_data)[i]
-  if(tmp_col %in% logTr_vars$var){
-    sign = logTr_vars$sign[which(tmp_col == logTr_vars$var)]
-      if(sign == 'positive'){
-        retest_data[,tmp_col] = log(retest_data[,tmp_col])
-        names(retest_data)[i] = paste0(tmp_col, '.logTr')
-      }
-      else if(sign == 'negative'){
-        retest_data[,tmp_col] = neg_log(retest_data[,tmp_col])
-        names(retest_data)[i] = paste0(tmp_col, '.ReflogTr')
-      }
-    }
-}
-
-```
-
-```{r echo = FALSE}
-rm(i, sign, tmp_col)
-```
-
-Check transformations are correct
-```{r}
-retest_logTr_vars = data.frame(grep('logTr', names(retest_data), value=T))
-names(retest_logTr_vars) = c('var')
-retest_logTr_vars$sign = ifelse(grepl(".ReflogTr",retest_logTr_vars$var), 'negative', 'positive')
-retest_logTr_vars$var = gsub(".logTr|.ReflogTr", "", logTr_vars$var)
-retest_logTr_vars == logTr_vars
-```
-
-```{r echo=FALSE}
-rm(logTr_vars, retest_logTr_vars, meaningful_vars)
 ```

### 2017-03-17 SRO_Report.Rmd
working on new report

@@
 
+```{r}
+tst_mng_cln <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_clean.csv')
+
+rtst_mng_cln <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/meaningful_variables_clean.csv')
+
+names(rtst_mng_cln)[which(names(rtst_mng_cln) %in% names(tst_mng_cln) == FALSE)]
+
+names(tst_mng_cln)[which(names(tst_mng_cln) %in% names(rtst_mng_cln) == FALSE)]
+```
+
 Extract retest participants from test data
@@
 
+  cat(rep('*', 40))
+  cat('\n')
+  cat(paste0(length(names(positive_subset)) ,' data positively skewed data were transformed:'))
+  cat('\n')
+  cat(names(positive_subset), sep = '\n')
+  cat(rep('*', 40))
+  cat('\n')
+
   # replace transformed variables
@@
   dropped_vars = names(negative_subset) %w/o% names(successful_transforms)
+
+  cat(rep('*', 40))
+  cat('\n')
+  cat(paste0(length(names(negative_subset)) ,' data negatively skewed data were transformed:'))
+  cat('\n')
+  cat(names(negative_subset), sep = '\n')
+  cat(rep('*', 40))
+  cat('\n')
 
@@
 
-clean_test_data = cbind(sub_id = test_data$sub_id, as.data.frame(apply(test_data[, -which(names(retest_data) %in% c("sub_id"))], 2, remove_outliers)))
+clean_test_data = cbind(sub_id = test_data$sub_id, as.data.frame(apply(test_data[, -which(names(test_data) %in% c("sub_id"))], 2, remove_outliers)))
 
@@
 
+Remove outliers from retest data the way they have been from test data
 ```{r}
-#Remove outliers from retest data the way they have been from test data
 clean_retest_data = cbind(sub_id = retest_data$sub_id, as.data.frame(apply(retest_data[, -which(names(retest_data) %in% c("sub_id"))], 2, remove_outliers)))
+```
 
-#Get list of transformed variables and the sign of their skew
+Get list of transformed variables and the sign of their skew
+```{r}
 logTr_vars = data.frame(grep('logTr', names(clean_test_data), value=T))
@@
 logTr_vars$var = gsub(".logTr|.ReflogTr", "", logTr_vars$var)
+```
 
-#Transform necessary vars and rename those columns
+Transform the t2 columns the same way t1 columns were transformed.
+
+```{r}
 for(i in 1:length(names(clean_retest_data))){
@@
         clean_retest_data[,tmp_col] = log(clean_retest_data[,tmp_col])
-        names(clean_retest_data)[i] = paste0(tmp_col, '.logTr')
+        names(clean_retest_data)[which(names(clean_retest_data) == tmp_col)] = paste0(tmp_col, '.logTr')
+        cat(paste0(tmp_col ,' was positively skewed and transformed.'))
+        cat('\n')
       }
@@
         clean_retest_data[,tmp_col] = neg_log(clean_retest_data[,tmp_col])
-        names(clean_retest_data)[i] = paste0(tmp_col, '.ReflogTr')
+        names(clean_retest_data)[which(names(clean_retest_data) == tmp_col)] = paste0(tmp_col, '.ReflogTr')
+        cat(paste0(tmp_col ,' was negatively skewed and transformed.'))
+        cat('\n')
       }
@@
 retest_logTr_vars$sign = ifelse(grepl(".ReflogTr",retest_logTr_vars$var), 'negative', 'positive')
-retest_logTr_vars$var = gsub(".logTr|.ReflogTr", "", logTr_vars$var)
+retest_logTr_vars$var = gsub(".logTr|.ReflogTr", "", retest_logTr_vars$var)
+retest_logTr_vars = retest_logTr_vars %>% arrange(var)
+logTr_vars = logTr_vars %>% arrange(var)
 retest_logTr_vars == logTr_vars
@@
 rm(logTr_vars, retest_logTr_vars)
+```
+
+Switch df names
+
+```{r}
+raw_retest_data = retest_data
+raw_test_data = test_data
+test_data = clean_test_data
+retest_data = clean_retest_data
+rm(clean_test_data, clean_retest_data)
 ```
@@
 #CHECK IF EVERYTHING IS ORDERED RIGHT
-retest_subs_test_data$sub_id == retest_data$sub_id
+as.character(retest_subs_test_data$sub_id) == as.character(retest_data$sub_id)
 ```
@@
 ```{r}
-all_columns <- unique(c(names(retest_data), names(retest_subs_test_data)))
+numeric_cols = c()
 
-matching_columns <- c()
-for(i in 1:length(all_columns)){
-  if(all_columns[i] %in% names(retest_data) & all_columns[i] %in% names(retest_subs_test_data)){
-    matching_columns <- c(matching_columns, all_columns[i])
+for(i in 1:length(names(test_data))){
+  if(is.numeric(test_data[,i])){
+    numeric_cols <- c(numeric_cols, names(test_data)[i])
   }
@@
 
-matching_dv_columns <- c()
+cor_df <- data.frame(spearman = rep(NA, length(numeric_cols)))
 
-for(i in 1:length(matching_columns)){
-  if(is.numeric(retest_data[,matching_columns[i]]) & is.numeric(retest_subs_test_data[,matching_columns[i]])){
-    matching_dv_columns <- c(matching_dv_columns, matching_columns[i])
-  }
-}
+row.names(cor_df) <- numeric_cols
 
-cor_df <- data.frame(spearman = rep(NA, length(matching_dv_columns)))
-
-row.names(cor_df) <- matching_dv_columns
-
-for(i in 1:length(matching_dv_columns)){
-  cor_df[matching_dv_columns[i], 'spearman'] <- cor(retest_data[,matching_dv_columns[i]],retest_subs_test_data[,matching_dv_columns[i]], method = 'spearman', use = "pairwise.complete.obs")
+for(i in 1:length(numeric_cols)){
+  cor_df[numeric_cols[i], 'spearman'] <- cor(retest_data[,numeric_cols[i]],retest_subs_test_data[,numeric_cols[i]], method = 'spearman', use = "pairwise.complete.obs")
 }
@@
 
-Distribution of all Pearson and Spearman correlations
+Distribution of Spearman correlations
 ```{r warning=FALSE, message=FALSE}
@@
 
-## Distribution of each variable
-
-Keeping a record of the distributions of the cleaned meaningful variables.
+## ICC for all cleaned meaningful variables
 
 ```{r}
-# Function to check if the variables that went in to cor_df have normal distributions
-diff_from_normal <- function(col){
-  return(shapiro.test(col)$p.value < 0.05)
+library(psych)
+sf <- matrix(c(9,    2,   5,    8,
+6,    1,   3,    2,
+8,    4,   6,    8,
+7,    1,   2,    6,
+10,   5,   6,    9,
+6,   2,   4,    7),ncol=4,byrow=TRUE)
+colnames(sf) <- paste("J",1:4,sep="")
+rownames(sf) <- paste("S",1:6,sep="")
+sf
+ICC(sf)
+```
+
+```{r}
+library('irr')
+
+time1 <- c(0:10)
+time2 <- c(1:11)
+times <- cbind(time1,time2)
+rm(time1, time2)
+times
+```
+
+```{r}
+icc(times,model = "twoway",
+    type = "consistency",
+    unit = "single",
+    r0 = 0,
+    conf.level = 0.95)
+```
+
+```{r}
+#>>ICC=1 for consistency
+
+icc(times,model = "twoway",
+    type = "agreement",
+    unit = "single",
+    r0 = 0,
+    conf.level = 0.95)
+```
+
+```{r}
+tmp = data.frame(persons=c(1,2,3,4,5,6),
+                 rater1=c(9,6,8,7,10,6),
+                 rater2=c(2,1,4,1,5,2),
+                 rater3=c(5,3,6,2,6,4),
+                 rater4=c(8,2,8,6,9,7))
+
+ICC(tmp%>%select(-persons))
+
+tmp = tmp %>% gather(rater,score,-persons)
+tmp
+summary(aov(score ~ rater+Error(factor(persons)), tmp))
+```
+
+```{r}
+match_t1_t2 <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id'){
+  df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var)
+  df = df %>% 
+    gather(time, score, -sub_id) %>%
+    separate(time, c("dv","drop","time"), sep="[.]") %>%
+    select(-drop)%>%
+    mutate(time=ifelse(time=="x",1,2))
+  return(df)
 }
 
-# Create and organize new df where distribution of vars data is stored.
-First for retest data only; then for test data for subjects who have retest data - restricting here since these are the subsets of data that went in to the correlation matrix.
-Merge and cleanup.
+tmp = match_t1_t2("adaptive_n_back.mean_load")
 
-dist_retest_data <- as.data.frame(apply(retest_data[,matching_dv_columns], 2, diff_from_normal))
-names(dist_retest_data) <- c('retest_not_normal')
-dist_retest_data$dv <- row.names(dist_retest_data)
-row.names(dist_retest_data) <- seq(1:nrow(dist_retest_data))
-dist_retest_data = dist_retest_data %>% select(dv, retest_not_normal)
+summary(lmer(score ~ (1|sub_id)+factor(time),data=tmp))
 
-dist_retest_subs_test_data <- as.data.frame(apply(retest_subs_test_data[,matching_dv_columns], 2, diff_from_normal))
-names(dist_retest_subs_test_data) <- c('test_not_normal')
-dist_retest_subs_test_data$dv <- row.names(dist_retest_subs_test_data)
-row.names(dist_retest_subs_test_data) <- seq(1:nrow(dist_retest_subs_test_data))
-dist_retest_subs_test_data = dist_retest_subs_test_data %>% select(dv, test_not_normal)
-
-dist_data <- merge(dist_retest_data, dist_retest_subs_test_data, by = 'dv')
-
-rm(dist_retest_data, dist_retest_subs_test_data)
-
-# Add whether dv's are tasks or survey to distribution dfs
-
-dist_data = cor_df %>%
-  select(dv, task) %>%
-  left_join(dist_data, by = 'dv')
 ```
 
-**What proportion is not normal?**  
-A large proportion of the variables are not normal for data from both sources. Larger proportions of survey data are not normal compared to task data. 
 ```{r}
-dist_data %>%
-  group_by(task) %>%
-  summarise(mean_retest_not_normal  = mean(retest_not_normal),
-            mean_test_not_normal = mean(test_not_normal))
+summary(aov(score ~ factor(time) + Error(sub_id),tmp))
 ```
 
-**Are the same vars that are not normally distributed in the retest data not normal in test data as well?**  
-List of variables that have different distributions in the two time points.
+----------------------------------------------------------------------------------------------------------------
+
 ```{r}
-dist_data %>%
-  filter(retest_not_normal != test_not_normal)
+icc_df <- data.frame(icc = rep(NA, length(numeric_cols)))
+
+row.names(icc_df) <- numeric_cols
+
+for(i in 1:length(numeric_cols)){
+  icc_df[numeric_cols[i], '...'] <- ...
+}
 ```
+
+----------------------------------------------------------------------------------------------------------------
 

### 2017-03-20 ICC_tutorial.Rmd
working on new report

---
title: "ICC tutorial"
output: html_notebook
---

Based on [Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf)

```{r}
tmp = data.frame(time_1=c(146, 148, 170, 90, 157, 156, 176, 205),
                 time_2=c(140, 152, 152, 99, 145, 153, 167, 218), 
                 people=c(1,2,3,4,5,6,7,8))
tmp = tmp %>% gather(key, value,-people)
summary(aov(value ~ factor(key)+Error(factor(people)), tmp))
(30)/(30+400)#eta squared
sd(tmp$value)
(2099-(30.2+57.1))/(2099 + ((2-1)*(30.2+57.1))) #ICC(1,1) ?
(2099-(30.2+57.1))/(2099) #ICC(1,k)
(2099-57.1)/(2099+ ((2-1)*57.1)+ ((2*(30.2-57.1))/8)) #ICC(2,1)
(2099-57.1)/(2099+((2*(30.2-57.1))/8)) #ICC(2,k)
(2099-57.1)/(2099+((2-1)*57.1)) #ICC(3,1)
(2099-57.1)/(2099) #ICC(3,k)
tmp = tmp %>% spread(key, value) %>% select(-people)
# icc(tmp, model = 'twoway', type='agreement')
ICC(tmp)
```

```{r}
tmp = data.frame(time_1=c(166, 168, 160, 150, 147, 146, 156, 155),
                 time_2=c(160, 172, 142, 159, 135, 143, 147, 168), 
                 people=c(1,2,3,4,5,6,7,8))
tmp = tmp %>% gather(key, value,-people)
summary(aov(value ~ factor(key)+Error(factor(people)), tmp))
tmp = tmp %>% spread(key, value) %>% select(-people)
ICC(tmp)
```

```{r}
tmp = data.frame(time_1=c(146, 148, 170, 90, 157, 156, 176, 205),
                 time_2=c(161, 162, 189, 100, 175, 171, 195, 219), 
                 people=c(1,2,3,4,5,6,7,8))
tmp = tmp %>% gather(key, value,-people)
summary(aov(value ~ factor(key)+Error(factor(people)), tmp))
(961)/(961+33)#partial eta-squared
(2275-5)/(2275+ ((2-1)*5)+ ((2*(961-5))/8)) #ICC(2,1)
(2275-5)/(2275+((2*(961-5))/8)) #ICC(2,k)
tmp = tmp %>% spread(key, value) %>% select(-people)
ICC(tmp)
```

### 2017-03-20 SRO_Report.Rmd
working on new report

@@
 rm(retest_data2, retest_data3)
-```
-
-```{r}
-tst_mng_cln <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_clean.csv')
-
-rtst_mng_cln <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/meaningful_variables_clean.csv')
-
-names(rtst_mng_cln)[which(names(rtst_mng_cln) %in% names(tst_mng_cln) == FALSE)]
-
-names(tst_mng_cln)[which(names(tst_mng_cln) %in% names(rtst_mng_cln) == FALSE)]
 ```
@@
 ```{r}
-library(psych)
-sf <- matrix(c(9,    2,   5,    8,
-6,    1,   3,    2,
-8,    4,   6,    8,
-7,    1,   2,    6,
-10,   5,   6,    9,
-6,   2,   4,    7),ncol=4,byrow=TRUE)
-colnames(sf) <- paste("J",1:4,sep="")
-rownames(sf) <- paste("S",1:6,sep="")
-sf
-ICC(sf)
-```
-
-```{r}
-library('irr')
-
-time1 <- c(0:10)
-time2 <- c(1:11)
-times <- cbind(time1,time2)
-rm(time1, time2)
-times
-```
-
-```{r}
-icc(times,model = "twoway",
-    type = "consistency",
-    unit = "single",
-    r0 = 0,
-    conf.level = 0.95)
-```
-
-```{r}
-#>>ICC=1 for consistency
-
-icc(times,model = "twoway",
-    type = "agreement",
-    unit = "single",
-    r0 = 0,
-    conf.level = 0.95)
-```
-
-```{r}
 tmp = data.frame(persons=c(1,2,3,4,5,6),
@@
   df = df %>% 
+    na.omit()%>%
     gather(time, score, -sub_id) %>%
@@
 tmp = match_t1_t2("adaptive_n_back.mean_load") 
+summary(aov(score~Error(sub_id)+time,tmp))
+(0.692-((0.876*1+0.092*133)/134))/(0.692 + ((2-1)*((0.876*1+0.092*133)/134))) #ICC(1,1) ?
+(0.692-0.092)/(0.692+ ((2-1)*0.092)+ ((2*(0.876-0.092))/134)) #ICC(2,1)
+(0.692-0.092)/(0.692+((2-1)*0.092)) #ICC(3,1)
+(0.692-((0.876*1+0.092*133)/134))/(0.692) #ICC(1,k)
+(0.692-0.092)/(0.692+((2*(0.876-0.092))/134)) #ICC(2,k)
+(0.692-0.092)/(0.692) #ICC(3.k)
+sqrt((92.1+0.88+12.29)/133) #sd?
+sd(tmp$score) #sd?
+sqrt(0.092) #sem (smaller the better)
+tmp = tmp %>% spread(time, score) %>% select(-dv, -sub_id)
+ICC(tmp)
 
-summary(lmer(score ~ (1|sub_id)+factor(time),data=tmp))
-
-```
-
-```{r}
-summary(aov(score ~ factor(time) + Error(sub_id),tmp))
+tmp = match_t1_t2("bis_bas_survey.BIS") 
+summary(aov(score~Error(sub_id)+time,tmp))
+# summary(aov(score~Error(sub_id/time)+time,tmp)) #same thing
+sqrt(0.0477)
+tmp = tmp %>% spread(time, score) %>% select(-dv, -sub_id)
+ICC(tmp)
 ```
@@
 ----------------------------------------------------------------------------------------------------------------
+
+Based on Weir 2005 ICC(3,k) does not take in to account within subject differences between two time points (fixed effect/systematic error by time).
+Thus, it is well approximated by Pearson's r and subject to similar criticisms.
+So if you're going to use this you should at least that this effect is not significant for a measure.
+
+Conclusion based on Weir:
+get ICC(3,k)
+report effect size of time (p value and partial eta squared)
+get SEM (sqrt(MS_error))
 

### 2017-03-20 SRO_Report.Rmd
working on new report

@@
 library(rmarkdown)
+library(psych)
 sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
@@
 
-```{r}
-tmp = data.frame(persons=c(1,2,3,4,5,6),
-                 rater1=c(9,6,8,7,10,6),
-                 rater2=c(2,1,4,1,5,2),
-                 rater3=c(5,3,6,2,6,4),
-                 rater4=c(8,2,8,6,9,7))
-
-ICC(tmp%>%select(-persons))
-
-tmp = tmp %>% gather(rater,score,-persons)
-tmp
-summary(aov(score ~ rater+Error(factor(persons)), tmp))
-```
+Based on [Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) ICC(3,k) does not take in to account within subject differences between two time points (i.e.
+the fixed effect of time/systematic error).
+Thus, it is well approximated by Pearson's r and subject to similar criticisms.
+[Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) suggests reporting at least this effect size if one chooses to report with ICC(3,k).
+Based on his conclusions here I report:
+- ICC(3,k): ranges between 0-1; the larger the better  
+- partial $\eta^2$ for time ($SS_{time}/SS_{within}$): effect size of time 
+- SEM ($sqrt(MS_{error})$): standard error of measurement; the smaller the better
 
@@
     na.omit()%>%
-    gather(time, score, -sub_id) %>%
-    separate(time, c("dv","drop","time"), sep="[.]") %>%
-    select(-drop)%>%
-    mutate(time=ifelse(time=="x",1,2))
+    gather(dv, score, -sub_id) %>%
+    mutate(time = ifelse(grepl('\\.x', dv), 1, ifelse(grepl('\\.y', dv), 2, NA))) %>%
+    separate(dv, c("dv", "drop"), sep='\\.([^.]*)$') %>%
+    select(-drop)
    return(df)
@@
 
-tmp = match_t1_t2("adaptive_n_back.mean_load") 
-summary(aov(score~Error(sub_id)+time,tmp))
-(0.692-((0.876*1+0.092*133)/134))/(0.692 + ((2-1)*((0.876*1+0.092*133)/134))) #ICC(1,1) ?
-(0.692-0.092)/(0.692+ ((2-1)*0.092)+ ((2*(0.876-0.092))/134)) #ICC(2,1)
-(0.692-0.092)/(0.692+((2-1)*0.092)) #ICC(3,1)
-(0.692-((0.876*1+0.092*133)/134))/(0.692) #ICC(1,k)
-(0.692-0.092)/(0.692+((2*(0.876-0.092))/134)) #ICC(2,k)
-(0.692-0.092)/(0.692) #ICC(3.k)
-sqrt((92.1+0.88+12.29)/133) #sd?
-sd(tmp$score) #sd?
-sqrt(0.092) #sem (smaller the better)
-tmp = tmp %>% spread(time, score) %>% select(-dv, -sub_id)
-ICC(tmp)
+get_icc <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id'){
+  df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
+  df = df %>% spread(time, score) %>% select(-dv, -sub_id)
+  icc = ICC(df)
+  icc_3k = icc$results['Average_fixed_raters', 'ICC']
+  return(icc_3k)
+  }
 
-tmp = match_t1_t2("bis_bas_survey.BIS") 
-summary(aov(score~Error(sub_id)+time,tmp))
-# summary(aov(score~Error(sub_id/time)+time,tmp)) #same thing
-sqrt(0.0477)
-tmp = tmp %>% spread(time, score) %>% select(-dv, -sub_id)
-ICC(tmp)
+get_eta <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id'){
+  df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
+  mod = summary(aov(score~Error(sub_id)+time, df))
+  ss_time = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq1',]
+  ss_error = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq2',]
+  eta = ss_time/(ss_time+ss_error)
+  return(eta)
+  }
+
+get_sem <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id'){
+  df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
+  mod = summary(aov(score~Error(sub_id)+time, df))
+  ms_error = as.data.frame(unlist(mod$`Error: Within`))['Mean Sq2',]
+  sem = sqrt(ms_error)
+  return(sem)
+}
 ```
 
-----------------------------------------------------------------------------------------------------------------
-
-Based on Weir 2005 ICC(3,k) does not take in to account within subject differences between two time points (fixed effect/systematic error by time).
-Thus, it is well approximated by Pearson's r and subject to similar criticisms.
-So if you're going to use this you should at least that this effect is not significant for a measure.
-
-Conclusion based on Weir:
-get ICC(3,k)
-report effect size of time (p value and partial eta squared)
-get SEM (sqrt(MS_error))
-
 ```{r}
-icc_df <- data.frame(icc = rep(NA, length(numeric_cols)))
+icc_df <- data.frame(icc = rep(NA, length(numeric_cols)), 
+                     eta_sq = rep(NA, length(numeric_cols)),
+                     sem = rep(NA, length(numeric_cols)))
 
@@
 for(i in 1:length(numeric_cols)){
-  icc_df[numeric_cols[i], '...'] <- ...
+  icc_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
+  icc_df[numeric_cols[i], 'eta_sq'] <- get_eta(numeric_cols[i])
+  icc_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
 }
+```
+
+Add column to tasks vs. surveys in icc table
+
+```{r}
+icc_df$dv = row.names(icc_df)
+row.names(icc_df) = seq(1:nrow(icc_df))
+icc_df$task = 'task'
+icc_df[grep('survey', icc_df$dv), 'task'] = 'survey'
+icc_df
+```
+
+### Distributions of ICC's by task vs. survey
+
+Survey reliabilities are noticably higher than task reliabilities.
+```{r warning=FALSE, message=FALSE}
+icc_df %>%
+  gather(key,value,-dv, -task) %>%
+  ggplot(aes(value, fill=task))+
+  geom_histogram(position = 'stack', alpha=0.5)+
+  theme_bw()+
+  facet_wrap(~key,scales='free')
+```
+
+Median reliability and the number of variables for both the surveys and the tasks
+```{r}
+icc_df %>%
+  group_by(task) %>%
+  summarise(median_icc = median(icc),
+            median_eta_sq = median(eta_sq),
+            median_sem = median(sem),
+            num_vars = n())
 ```

### 2017-03-20 SRO_Report.Rmd
working on new report

@@
 render_this <- function(){rmarkdown::render('SRO_Report.Rmd', html_notebook(toc = T, toc_float = T))}
-options(digits = 4)
 ```
@@
 
-For reference here are the variables that are **not** included because they were not of theoretical interest in factor structure analyses of this data so far.
+For reference here are the variables that are **not** included in the analyses of the remainder of this report because they were not of theoretical interest in factor structure analyses of this data so far.
+These include drift diffusion and other model parameters for specific conditions within a task; survey variables that are not part of the dependant variables for that survey in the literature and demographics (these are saved for prediction analyses).
 
@@
 
-Extract retest participants from test data
+Extract t2 participants with good t1 data: We only invited those with good data but due to a technical error a handful of subjects who weren't checked for data quality completed the battery as well.
+One of those subjects gave good t2 data but didn't have good t1 data and therefore is removed from further analyses.
 
@@
 
-The cleaning functions here are translated from the python pipeline to mimick the same procedure.
+The cleaning functions here are translated from the python pipeline to mimick the same procedure that was applied to the `meaningful_variables` in creating `meaningful_variables_clean`.
 
-The cleaning procedures include two steps:  
-1. removing outliers for each variables where outliers are defined as those who are greater than 2.5 IQR from median  
+The original cleaning procedures include three steps:  
+1.
+Removing outliers for each variables where outliers are defined as those who are greater than 2.5 IQR from median.
+**This step is skipped here because removing outliers from either dataset could lead to an unnecessary increase in missing data.
+Since we are interested in how close two measures of the metric for a given subject are to each other instead of how close the measurements for all these metrics are to each other this seemed appropriate.**
 2.
+Removing correlated variables *within* a task.
+In creating `meaningful_variables_clean` if variables for a given task correlated >.85 only one was kept.
+**This step is skipped here because we want to look at the reliability of as many variables as we can.**
+3.
 Log transforming variables with skew.
-In cleaning T1 data for the `meaningful_variables_clean.csv` variables for which skew could not be removed successfully were dropped.
-**This step is excluded here.
-Variables that are not successfully transformed will be listed but not dropped.**
+In cleaning t1 data variables that had a skew > 1 were log transformed and those for which skew could not be removed successfully were dropped.
+**Here we transform all variables that have a skew>1 in t1 data but variables that are not successfully transformed will be listed but not dropped.**
 
@@
 
-```{r}
+```{r warning=FALSE}
 numeric_cols = c()
@@
 
-clean_test_data = cbind(sub_id = test_data$sub_id, as.data.frame(apply(test_data[, -which(names(test_data) %in% c("sub_id"))], 2, remove_outliers)))
+# clean_test_data = cbind(sub_id = test_data$sub_id, as.data.frame(apply(test_data[, -which(names(test_data) %in% c("sub_id"))], 2, remove_outliers)))
 
-clean_test_data = transform_remove_skew(clean_test_data, numeric_cols)
+# clean_test_data = transform_remove_skew(clean_test_data, numeric_cols)
+clean_test_data = transform_remove_skew(test_data, numeric_cols)
 ```
@@
 
-We should probably take a closer look at model fits instead but this could be a first step.
-
-The cleaned meaningful variables do not seem to include neither the EZ estimates nor accuracies
-so analyses on this [here](https://htmlpreview.github.io/?https://github.com/zenkavi/SRO_Retest_Analyses/blob/master/SRO_Retest_Analyses.nb.html) are more informative.
-Otherwise just looking at this one might be tempted to conclude that rt's have higher reliabilities but clearly
-
 ```{r message=FALSE, warning=FALSE, fig.height=12, fig.width=9}
@@
 ```
-
-### Efa and Cfa
-
-**DO ONLY ON SURVEY AND TASK DATA SEPARATELY**
-
-Efa on the people you don't have retest on and then predict how well this holds up for people w retest on t1 and on t2.
-
-I haven't consulted other factor analyses that have been done on the full dataset in doing this but will be happy to adjust as necessary.
-
-```{r}
-retest_data_mngf <- retest_data[,matching_dv_columns]
-retest_subs_test_mngf <- retest_subs_test_data[,matching_dv_columns]
-rest_subs_test_mngf <- rest_subs_test_data[,matching_dv_columns]
-
-#standardize all vars going in to factor analysis
-rest_subs_test_mngf_z <- rest_subs_test_mngf
-
-for(i in 1:length(rest_subs_test_mngf)){
-    rest_subs_test_mngf_z[,names(rest_subs_test_mngf)[i]] = scale(rest_subs_test_mngf[,i])
-}
-
-rest_subs_test_mngf_z <- as.data.frame(rest_subs_test_mngf_z)
-```
-
-Efa on subjects from original dataset withOUT retest data (using meaningful vars only)  
-Using the `psych` package I get some sort of solution but these are probably not valid given all the warnings.
-```{r}
-corMat <- rest_subs_test_mngf_z %>% cor(.,use = 'complete.obs')
-
-solution <- fa(r = corMat, nfactors = 7, rotate = "oblimin", fm = "pa")
-```
-
-```{r}
-print(solution$loadings, sort=T)
-```
-
-```{r}
-# Pricipal Components Analysis
-# entering raw data and extracting PCs 
-# from the correlation matrix 
-fit <- principal(rest_subs_test_mngf_z, nfactors=7, rotate="varimax")
-fit
-
-fit <- princomp(rest_subs_test_mngf_z, cor=TRUE)
-summary(fit) # print variance accounted for 
-loadings(fit) # pc loadings 
-plot(fit,type="lines") # scree plot 
-fit$scores # the principal components
-biplot(fit)
-```

### 2017-03-20 SRO_Report.Rmd
working on new report

@@
 Instead of applying the same functions applied to t1 data we check which variables are transformed in what way and transform the t2 data the same way.
+Again we are not removing outliers in the t2 or dropping variables if the skew is not removed successfully after transforming.
 
-**Question: Should I be removing outliers from the retest data?
-Or keep them if they were within the ranges in the test data even if they aren't in the retest data.
-Right now I'm removing them depending on t2 distributions**
-
-Remove outliers from retest data the way they have been from test data
-```{r}
+```{r eval=FALSE, echo=FALSE}
+# Remove outliers from retest data the way they have been from test data
 clean_retest_data = cbind(sub_id = retest_data$sub_id, as.data.frame(apply(retest_data[, -which(names(retest_data) %in% c("sub_id"))], 2, remove_outliers)))
@@
 
-```{r}
+```{r warning=FALSE}
+clean_retest_data = retest_data
+
 for(i in 1:length(names(clean_retest_data))){
@@
 }
+
+numeric_cols[293]
+raw_test_data[,"directed_forgetting.proactive_interference_acc"]
+match_t1_t2(numeric_cols[293])
+get_icc(numeric_cols[293])
+get_eta(numeric_cols[293])
+get_sem(numeric_cols[293])
 ```

### 2017-03-20 SRO_Report.Rmd
working on new report

--- 2017-03-20 SRO_Report.Rmd
@@
 
+pos_log <- function(column){
+  col_min = min(column, na.rm=T)
+  a = 1-col_min
+  column = column+a
+  return(log(column))
+}
+
 neg_log <- function(column){
@@
   # log transform for positive skew
-  positive_subset = log(positive_subset)
+  # positive_subset = log(positive_subset)
+  positive_subset = pos_log(positive_subset) #slight divergence from original code
   successful_transforms = as.data.frame(apply(positive_subset, 2, skew))
@@
 Instead of applying the same functions applied to t1 data we check which variables are transformed in what way and transform the t2 data the same way.
-
-**Question: Should I be removing outliers from the retest data?
-Or keep them if they were within the ranges in the test data even if they aren't in the retest data.
-Right now I'm removing them depending on t2 distributions**
-
-Remove outliers from retest data the way they have been from test data
-```{r}
-clean_retest_data = cbind(sub_id = retest_data$sub_id, as.data.frame(apply(retest_data[, -which(names(retest_data) %in% c("sub_id"))], 2, remove_outliers)))
-```
+Again we are not removing outliers in the t2 or dropping variables if the skew is not removed successfully after transforming.
 
@@
       if(sign == 'positive'){
-        clean_retest_data[,tmp_col] = log(clean_retest_data[,tmp_col])
+        # clean_retest_data[,tmp_col] = log(clean_retest_data[,tmp_col])
+        clean_retest_data[,tmp_col] = pos_log(clean_retest_data[,tmp_col])
         names(clean_retest_data)[which(names(clean_retest_data) == tmp_col)] = paste0(tmp_col, '.logTr')

### 2017-03-20 SRO_Report.Rmd
working on new report

@@
 
-Extract t2 participants with good t1 data: We only invited those with good data but due to a technical error a handful of subjects who weren't checked for data quality completed the battery as well.
+Extract t2 participants with good t1 data: We only invited those with good data but due to a technical error a handful of subjects who weren't checked for data quality completed the retest battery as well.
 One of those subjects gave good t2 data but didn't have good t1 data and therefore is removed from further analyses.
@@
 1.
-Removing outliers for each variables where outliers are defined as those who are greater than 2.5 IQR from median.
+Removing outliers for each variable where outliers are defined as those who are greater than 2.5 IQR from median.
 **This step is skipped here because removing outliers from either dataset could lead to an unnecessary increase in missing data.
-Since we are interested in how close two measures of the metric for a given subject are to each other instead of how close the measurements for all these metrics are to each other this seemed appropriate.**
+Since we are interested in the average distance between two measures of a metric for a given subject instead of the distance between all these metrics this seemed appropriate.**
 2.
@@
 Log transforming variables with skew.
-In cleaning t1 data variables that had a skew > 1 were log transformed and those for which skew could not be removed successfully were dropped.
-**Here we transform all variables that have a skew>1 in t1 data but variables that are not successfully transformed will be listed but not dropped.**
+In cleaning t1 data variables that had a |skew| > 1 were log transformed and those for which skew could not be removed successfully were dropped.
+**Here we transform all variables that have a |skew|>1 in t1 data but variables that are not successfully transformed will be listed and not dropped.**
 
@@
 
-Clean test data on full sample without dropping any columns. Columns that are not transformed successfully are listed.
+Clean t1 data on full sample without dropping any columns. Columns that are not transformed successfully are listed.
 
@@
 
-```{r echo=F}
+```{r echo=FALSE}
 rm(logTr_vars, retest_logTr_vars)
@@
 
-Switch df names
-
 ```{r}
+# Switch df names
 raw_retest_data = retest_data
@@
 
-Add column to tasks vs. surveys in correlation table
-
 ```{r}
+# Add column to tasks vs. surveys in correlation table
 cor_df$dv = row.names(cor_df)
@@
 
-Survey reliabilities are noticably higher than task reliabilities.
+Spearman correlations for surveys are noticably higher than task reliabilities.
 ```{r warning=FALSE, message=FALSE}
@@
 
-Mean reliability and the number of variables for both the surveys and the tasks
+Mean Spearman correlation and the number of variables for both the surveys and the tasks
 ```{r}
@@
 But note that this is not a survey that has been studied extensively psychometrically like others.
-This is more similar to out tasks (one that is used more often by economists).
-In previous data I have worked retest reliablities for this task was ~.35 so the results here are in line with this.
+This is more similar to our tasks (one that is used more often by economists).
+In previous data I have worked with retest reliablities for this task was ~.35 so the results here are in line with this.
 - Otherwise the lowest survey reliabilities are 0.5.
@@
 Thus, it is well approximated by Pearson's r and subject to similar criticisms.
-[Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) suggests reporting at least this effect size if one chooses to report with ICC(3,k).
+[Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) suggests reporting at least this systematic error effect size if one chooses to report with ICC(3,k).
 Based on his conclusions here I report:
@@
 - partial $\eta^2$ for time ($SS_{time}/SS_{within}$): effect size of time   
-- SEM ($sqrt(MS_{error})$): standard error of measurement; the smaller the better
+- SEM ($\sqrt(MS_{error})$): standard error of measurement; the smaller the better
 
@@
 Survey reliabilities are noticably higher than task reliabilities.
-```{r warning=FALSE, message=FALSE}
+```{r warning=FALSE, message=FALSE, fig.width=10}
 icc_df %>%
@@
 ```
-
-----------------------------------------------------------------------------------------------------------------
-
-## Different task variable types
-
-Mean reliabilities for different types of dependant variables
-
-### Drift diffusion variables: raw vars vs. EZ vs. hddm
-
-**DO THIS ON VARIABLES EXHAUSTIVE GETTING ALL RT AND ACC'S**
-
-```{r message=FALSE, warning=FALSE, fig.height=12, fig.width=9}
-cor_df%>%
-  filter(grepl('EZ|hddm|_rt|_acc', dv)) %>%
-  mutate(var_type = ifelse(grepl('EZ',dv), 'EZ', ifelse(grepl('hddm',dv), 'hddm', 'raw')),
-         var = ifelse(grepl('_rt', dv), 'rt', ifelse(grepl('_acc', dv), 'acc', ifelse(grepl('_non_decision', dv), 'non_decision', ifelse(grepl('_thresh', dv), 'thresh', ifelse(grepl('_drift', dv), 'drift', NA)))))) %>%
-  ggplot(aes(spearman))+
-  geom_histogram()+
-  theme_bw()+
-  facet_wrap(var_type~var)
-```
-
-```{r}
-cor_df%>%
-  filter(grepl('EZ|hddm|_rt|_acc', dv)) %>%
-  mutate(var_type = ifelse(grepl('EZ',dv), 'EZ', ifelse(grepl('hddm',dv), 'hddm', 'raw')),
-         var = ifelse(grepl('_rt', dv), 'rt', ifelse(grepl('_acc', dv), 'acc', ifelse(grepl('_non_decision', dv), 'non_decision', ifelse(grepl('_thresh', dv), 'thresh', ifelse(grepl('_drift', dv), 'drift', NA)))))) %>%
-  group_by(var_type, var) %>%
-  summarise(mean_spearman = mean(spearman, na.rm=T),
-            sem_spear = sem(spearman),
-            num_vars = sum(ifelse(is.na(spearman)==FALSE,1,0))) %>%
-  arrange(var_type)
-```
-
-## Replicating the factor structure
-
-### Confirm comparability of retest and rest sample
-
-First do a t-test on all measures of T1 for subjects with and without retest to confirm that these two samples do not differ from each other significantly (FDR corrected)
-```{r}
-ttest_df = data.frame(t_stat = rep(NA, length(matching_dv_columns)),
-                      p_val_raw = rep(NA, length(matching_dv_columns)))
-
-row.names(ttest_df) <- matching_dv_columns
-
-for(i in 1:length(matching_dv_columns)){
-  ttest_df[matching_dv_columns[i], 't_stat'] <- t.test(retest_subs_test_data[,matching_dv_columns[i]], rest_subs_test_data[,matching_dv_columns[i]])$statistic
-
-  ttest_df[matching_dv_columns[i], 'p_val_raw'] <- t.test(retest_subs_test_data[,matching_dv_columns[i]], rest_subs_test_data[,matching_dv_columns[i]])$p.value
-}
-
-ttest_df$dv = row.names(ttest_df)
-row.names(ttest_df) = seq(1:nrow(ttest_df))
-ttest_df$task = 'task'
-ttest_df[grep('survey', ttest_df$dv), 'task'] = 'survey'
-
-#correct p-values 
-ttest_df$p_val_fdr = p.adjust(ttest_df$p_val_raw, method='fdr')
-```
-
-```{r echo=FALSE}
-rm(i)
-```
-
-Distribution of t statistics and p values
-
-```{r warning=FALSE, message=FALSE}
-ttest_df %>%
-  gather(key, value, -dv, -task) %>%
-  ggplot(aes(value)) +
-  geom_histogram()+
-  theme_bw()+
-  facet_wrap(key~task, scales='free')
-```
-
-**Which variables are significantly different between the two samples (those with and without retest data for T1)?**
-
-13 variables have raw p values <0.05 BUT FDR corrected p values for these are not <0.05.
-
-```{r}
-ttest_df %>%
-  filter(p_val_raw<0.05) %>%
-  select(dv, task, t_stat, p_val_raw, p_val_fdr)
-```

### 2017-03-20 SRO_Report.Rmd
working on new report

@@
 icc_df[grep('survey', icc_df$dv), 'task'] = 'survey'
+icc_df = icc_df %>%
+  select(dv, task, icc, eta_sq, sem)
+row.names(icc_df) = NULL
 icc_df
@@
 ```
+
+### Relationship between ICC and Spearman
+
+```{r}
+icc_df %>%
+  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
+  ggplot(aes(spearman, icc, col=task))+
+  geom_point()+
+  theme_bw()
+```

### 2017-03-21 SRO_Report.Rmd
working on new report

@@
 
+Sort tasks by icc. What's going on with the negative icc's?
+ICC(3,k) would be negative if the $MS_{error}$>$MS_{between}$
+
+Plot their data scatter plots.
+```{r, fig.height=12, fig.width=12}
+neg_icc_vars = icc_df %>%
+  arrange(icc) %>% 
+  filter(icc<0) %>%
+  select(dv)
+
+tmp = data.frame()
+
+for(i in 1:nrow(neg_icc_vars)){
+  tmp = rbind(tmp, match_t1_t2(neg_icc_vars$dv[i]))
+}
+rm(neg_icc_vars)
+
+tmp %>%
+  spread(time, score) %>%
+  ggplot(aes(`1`, `2`))+
+  geom_point()+
+  theme_bw()+
+  facet_wrap(~dv, scales='free')
+
+```
+
+Compare these plots to the variables with highest icc
+
+```{r fig.height=12, fig.width=12}
+high_icc_vars = icc_df %>%
+  arrange(-icc)  %>% 
+  filter(icc>0.92) %>%
+  select(dv)
+
+tmp = data.frame()
+
+for(i in 1:nrow(high_icc_vars)){
+  tmp = rbind(tmp, match_t1_t2(high_icc_vars$dv[i]))
+}
+rm(high_icc_vars)
+
+tmp %>%
+  spread(time, score) %>%
+  ggplot(aes(`1`, `2`))+
+  geom_point()+
+  theme_bw()+
+  facet_wrap(~dv, scales='free')
+
+```
+
+```{r echo=FALSE}
+rm(tmp)
+```
+
 ### Relationship between ICC and Spearman
+Mostly linear except for a bunch of tasks that have an icc ~ 0.
 
@@
   geom_point()+
-  theme_bw()
+  theme_bw()+
+  theme(legend.title = element_blank())
 ```
+
+What are the variables clustered around 0 ICC?
+
+```{r}
+icc_df %>%
+  filter(icc>(-0.1), icc<0.1) %>%
+  arrange(icc)
+```
+
+### Relationship between ICC and $\eta^2$
+
+```{r}
+icc_df %>%
+  ggplot(aes(eta_sq, icc, col=task))+
+  geom_point()+
+  theme_bw()+
+  theme(legend.title = element_blank())
+```
+
+Which tasks show a systematic difference between t1 and t2?
+Are these the tasks where the ICC and Spearman imply different conclusions?
+
+```{r}
+icc_df %>%
+  select(dv, eta_sq) %>%
+  arrange(-eta_sq)
+```

### 2017-03-21 SRO_Report.Rmd
working on new report

@@
 output:
-html_document:
+github_document:
 toc: yes
@@
 library(psych)
+library(stringr)
 sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
@@
   spread(time, score) %>%
+  # mutate(dv_wrap = str_wrap(dv, width = 30)) %>%
   ggplot(aes(`1`, `2`))+
@@
   theme_bw()+
-  facet_wrap(~dv, scales='free')
+  facet_wrap(~dv, scales='free', labeller = label_wrap_gen())
 

### 2017-03-22 SRO_Report.Rmd
working on report

@@
 library(jsonlite)
-library(lavaan)
-library(semTools)
 library(psych)
-library(GPArotation)
 library(rmarkdown)
@@
 library(stringr)
+library(plotly)
 sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
-render_this <- function(){rmarkdown::render('SRO_Report.Rmd', html_notebook(toc = T, toc_float = T))}
+render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Report', html_notebook(toc = T, toc_float = T))}
 ```
@@
 
-Distribution of Spearman correlations
-```{r warning=FALSE, message=FALSE}
-cor_df %>%
-  ggplot(aes(spearman))+
-  geom_histogram()+
-  theme_bw()+
-  ggtitle('Distribution of Spearman correlations for cleaned meaningful variables')
-```
-
 ```{r}
@@
 ```{r warning=FALSE, message=FALSE}
-cor_df %>%
-  ggplot(aes(spearman))+
-  geom_histogram()+
+ggplotly(cor_df %>%
+  ggplot(aes(spearman, fill=task, label=dv))+
+  geom_histogram(alpha=0.5, position='identity')+
   theme_bw()+
-  facet_wrap(~task)
+  theme(legend.title = element_blank()))
 ```
@@
   ggplot(aes(value, fill=task))+
-  geom_histogram(position = 'stack', alpha=0.5)+
+  geom_histogram(position = 'identity', alpha=0.5)+
   theme_bw()+
@@
 ```{r}
-icc_df %>%
+ggplotly(icc_df %>%
            left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
-  ggplot(aes(spearman, icc, col=task))+
+           ggplot(aes(spearman, icc, col=task, label=dv, label2=eta_sq))+
            geom_point()+
            theme_bw()+
-  theme(legend.title = element_blank())
+           theme(legend.title = element_blank())+
+           geom_abline(intercept = 0, slope=1))
 ```
@@
 ```{r}
-icc_df %>%
-  ggplot(aes(eta_sq, icc, col=task))+
+ggplotly(icc_df %>%
+  ggplot(aes(eta_sq, icc, col=task, label=dv))+
   geom_point()+
   theme_bw()+
-  theme(legend.title = element_blank())
+  theme(legend.title = element_blank()))
 ```

### 2017-03-28 SRO_Report.Rmd
working in report

@@
 library(plotly)
+library(jsonlite)
 sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
@@
 Spearman correlations for surveys are noticably higher than task reliabilities.
+
+```{r echo=FALSE}
+get_labels = function(plot_df, ref_df, bin_col, group_col){
+
+  plot_df$bin = as.numeric(factor(plot_df$x))
+  ref_df$bin = NA
+
+  for(i in 1:nrow(ref_df)){
+    for(j in 1:nrow(plot_df)){
+      if(ref_df[i, bin_col] <= plot_df$xmax[j] & ref_df[i, bin_col]>=plot_df$xmin[j] & ref_df[i, group_col] == plot_df[j, group_col]){
+        ref_df$bin[i] <- plot_df$bin[j]
+      }
+    }
+  }
+
+  ref_df = ref_df %>% 
+    group_by(bin, task) %>%
+    mutate(label=as.character(toJSON(unique(dv))))
+
+  label_df = ref_df[!duplicated(ref_df[,c('label')]),c('task', 'bin', 'label')]
+
+  out_df = left_join(plot_df,label_df, by= c("bin", "task"))
+
+  return(out_df)
+}
+
+line_break <- function(cell){
+  out = paste(unlist(strsplit(gsub("\\]","",gsub("\\[","",cell)), ",")), sep="\n", collapse = "</br>")
+  return(out)
+}
+
+prettify_label = function(df){
+  for(i in 1:nrow(df)){
+    df$label[i] =line_break(df$label[i])
+  }
+  return(df)
+}
+```
+
 ```{r warning=FALSE, message=FALSE}
-ggplotly(cor_df %>%
-  ggplot(aes(spearman, fill=task, label=dv))+
-  geom_histogram(alpha=0.5, position='identity')+
-  theme_bw()+
-  theme(legend.title = element_blank()))
+ggplotly(ggplot_build(cor_df %>%
+                        ggplot(aes(spearman, fill=task)) +
+                        geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
+           mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
+           get_labels(.,cor_df, "spearman", "task") %>%
+           prettify_label(.) %>%
+           ggplot(aes(x,y, fill=task, label=label))+
+           geom_bar(stat='identity', position='identity', alpha=0.5)+
+           xlab('Spearman')+
+           ylab('Count')+
+           theme_bw(),
+         tooltip = 'label',
+         hoverinfo = 'text')
 ```

### 2017-04-05 SRO_Report.Rmd
working in report

@@
 sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
-render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Report', html_notebook(toc = T, toc_float = T))}
+render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Report', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
 ```
@@
 }
-```
 
-```{r}
 # Add column to tasks vs. surveys in correlation table
@@
 cor_df[grep('survey', cor_df$dv), 'task'] = 'survey'
+```
+
+Mean Spearman correlation and the number of variables for both the surveys and the tasks
+```{r}
+cor_df %>%
+  group_by(task) %>%
+  summarise(mean_spearman = mean(spearman),
+            num_vars = n())
 ```
@@
 
-Mean Spearman correlation and the number of variables for both the surveys and the tasks
-```{r}
-cor_df %>%
-  group_by(task) %>%
-  summarise(mean_spearman = mean(spearman),
-            num_vars = n())
-```
-
 #### Rank order of correlations
@@
 
-- Demographics are excluded from this list of variables.  
+- Demographics are excluded from this list of variables (because they are saved for predictive analyses).  
 - Holt and Laury test-retest is the worst for *surveys*.
@@
 Based on his conclusions here I report:
-- ICC(3,k): ranges between 0-1; the larger the better  
+- ICC(3,k): As Dave clarified this ranges from 1 to -1/(number of repeated measures -1) so in our case this range would be [-1, 1]; larger values would mean that the two scores of a subject for a given measure are more similar to each other than they are to scores of other people
 - partial $\eta^2$ for time ($SS_{time}/SS_{within}$): effect size of time   
@@
 ```{r}
+#Calculate ICC df
 icc_df <- data.frame(icc = rep(NA, length(numeric_cols)), 
@@
 }
-```
 
-Add column to tasks vs. surveys in icc table
-
-```{r}
 icc_df$dv = row.names(icc_df)
@@
 row.names(icc_df) = NULL
-icc_df
 ```
 
-### Distributions of ICC's by task vs. survey
-
-Survey reliabilities are noticably higher than task reliabilities.
-```{r warning=FALSE, message=FALSE, fig.width=10}
-icc_df %>%
-  gather(key,value,-dv, -task) %>%
-  ggplot(aes(value, fill=task))+
-  geom_histogram(position = 'identity', alpha=0.5)+
-  theme_bw()+
-  facet_wrap(~key,scales='free')
-```
-
-Median reliability and the number of variables for both the surveys and the tasks
+Median reliability and the number of variables for both the surveys and the tasks:
+As implied by Spearman the ICC's are higher for surveys.  
+Systematic differences between the two measurements are higher for tasks than surveys (potentially indicating learning effects).  
+Unexpectedly, median standard error of measurement is higher for surveys but the distribution below suggests that this is a side effect of having too many task measures with very low SEMs.
 ```{r}
@@
             num_vars = n())
+```
+
+### Distributions of ICC's by task vs. survey
+
+```{r warning=FALSE, message=FALSE}
+ggplotly(ggplot_build(icc_df %>%
+                        ggplot(aes(icc, fill=task)) +
+                        geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
+           mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
+           get_labels(.,icc_df, "icc", "task") %>%
+           prettify_label(.) %>%
+           ggplot(aes(x,y, fill=task, label=label))+
+           geom_bar(stat='identity', position='identity', alpha=0.5)+
+           xlab('ICC')+
+           ylab('Count')+
+           theme_bw(),
+         tooltip = 'label',
+         hoverinfo = 'text')
+```
+
+#### Rank order of ICCs
+
+###### For tasks
+
+```{r}
+icc_df %>%
+  filter(task == 'task') %>%
+  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
+  arrange(-icc) %>%
+  select(dv, -task, icc, eta_sq, sem, spearman)
+```
+
+###### For surveys
+
+```{r}
+icc_df %>%
+  filter(task == 'survey') %>%
+  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
+  arrange(-icc) %>%
+  select(dv, -task, icc, eta_sq, sem, spearman)
+```
+
+### Distributions of partial $\eta^2$ by task vs. survey
+
+Tooltip might not work well for this graph for the highest bar because the label is too large.
+But this bar indicates measures where the effect of time is very small anyway.
+We might want to pay closer attention to those not in this lowest bar since those are the variables where there is a non-negligible effect of time, indicating either a learning effect or other kind of systematic change that
+
+```{r warning=FALSE, message=FALSE}
+ggplotly(ggplot_build(icc_df %>%
+                        ggplot(aes(eta_sq, fill=task)) +
+                        geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
+           mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
+           get_labels(.,icc_df, "eta_sq", "task") %>%
+           prettify_label(.) %>%
+           ggplot(aes(x,y, fill=task, label=label))+
+           geom_bar(stat='identity', position='identity', alpha=0.5)+
+           xlab('Partial Eta Squared')+
+           ylab('Count')+
+           theme_bw(),
+         tooltip = 'label',
+         hoverinfo = 'text')
+```
+
+#### Rank order of partial $\eta^2$
+
+###### For tasks
+
+```{r}
+icc_df %>%
+  filter(task == 'task') %>%
+  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
+  arrange(-eta_sq) %>%
+  select(dv, -task, eta_sq, icc, sem, spearman)
+```
+
+###### For surveys
+
+```{r}
+icc_df %>%
+  filter(task == 'survey') %>%
+  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
+  arrange(-eta_sq)%>%
+  select(dv, -task, eta_sq, icc, sem, spearman)
+```
+
+### Distributions of SEM's by task vs. survey
+
+```{r warning=FALSE, message=FALSE}
+ggplotly(ggplot_build(icc_df %>%
+                        ggplot(aes(sem, fill=task)) +
+                        geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
+           mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
+           get_labels(.,icc_df, "sem", "task") %>%
+           prettify_label(.) %>%
+           ggplot(aes(x,y, fill=task, label=label))+
+           geom_bar(stat='identity', position='identity', alpha=0.5)+
+           xlab('SEM')+
+           ylab('Count')+
+           theme_bw(),
+         tooltip = 'label',
+         hoverinfo = 'text')
+```
+
+#### Rank order of SEMs
+
+###### For tasks
+
+```{r}
+icc_df %>%
+  filter(task == 'task') %>%
+  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
+  arrange(-sem) %>%
+  select(dv, -task,  sem, eta_sq, icc, spearman)
+```
+
+###### For surveys
+
+```{r}
+icc_df %>%
+  filter(task == 'survey') %>%
+  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
+  arrange(-sem)%>%
+  select(dv, -task,  sem, eta_sq, icc, spearman)
 ```
@@
 ```
+
+Ties?
+
+The group of zero values for the ICC may be that the ICC is more of a measure of consistency than the Spearman/Pearson measures of rank order similarity.
+Or it could be the ICC calculation is off in some way.
+It would be worth focusing on five of these unusual cases (where the ICC is zero but the Pearson/Spearman is large) and calculate the ICC using other formulas.
+Generally the Spearman and Pearson differ when there are ties.
+
+```{r}
+ties_df <- data.frame(unique_entries = rep(NA, length(numeric_cols)), 
+                     transformed = rep(NA, length(numeric_cols)))
+
+row.names(ties_df) <- numeric_cols
+
+for(i in 1:length(numeric_cols)){
+  ties_df[numeric_cols[i], 'unique_entries'] <- get_unique(numeric_cols[i])
+  ties_df[numeric_cols[i], 'transformed'] <- get_transformed(numeric_cols[i])
+}
+
+icc_df %>%
+  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
+  left_join(ties_df, by = 'dv')
+
+#Function to output: spearman, icc, number of unique values in column, whether it is log transformed
+
+#Gina seems right; these transformed variables have high Spearman but low ICC and they have few unique values (though this isn't )
+length(unique(retest_data$impulsive_venture_survey.impulsiveness.logTr))
+length(unique(retest_data$adaptive_n_back.mean_load.logTr))
+```
+
+# Completion dates

### 2017-04-05 SRO_Report.Rmd
working in report

@@
 But this bar indicates measures where the effect of time is very small anyway.
-We might want to pay closer attention to those not in this lowest bar since those are the variables where there is a non-negligible effect of time, indicating either a learning effect or other kind of systematic change that
+We might want to pay closer attention to those not in this lowest bar since those are the variables where there is a non-negligible effect of time, indicating either a learning effect or other kind of systematic change that we did not hypothesize to observe with any of these measures.
 
@@
   select(dv, -task, eta_sq, icc, sem, spearman)
+```
+
+#### Effect of time
+
+So what variables show a non-negligible effect of time and in what direction?
+
+```{r warning=FALSE, message=FALSE}
+ggplot_build(icc_df %>%
+               ggplot(aes(eta_sq, fill=task)) +
+               geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
+  mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
+  get_labels(.,icc_df, "eta_sq", "task") %>%
+  prettify_label(.) %>%
+  filter(bin != 1 & bin !=2 & !is.na(label)) %>%
+  select(label)
+
+anyNA("NA") 
 ```
@@
 
-Sort tasks by icc. What's going on with the negative icc's?
-ICC(3,k) would be negative if the $MS_{error}$>$MS_{between}$
-
-Plot their data scatter plots.
-```{r, fig.height=12, fig.width=12}
+### Negative icc's?
+```{r}
 neg_icc_vars = icc_df %>%
@@
   select(dv)
+```
 
+Some variables (`r neg_icc_vars$dv`) have <0 ICC's. This would be the case if the $MS_{error}$>$MS_{between}$. That is, ICC would be negative if the ...
+
+Plot data for measures with negative ICC.  
+x-axis is time 1 data and y-axis is time 2 data. The scatter plots show that the scores for measures with negative ICC's have no relationship across time points.
+```{r, fig.height=12, fig.width=12}
 tmp = data.frame()
@@
 
-Compare these plots to the variables with highest icc
+This point is clarified further by compare these scatter plots to those of variables with highest ICC. These variables have strong and clear positive linear relationships.
 
@@
 ### Relationship between ICC and Spearman
-Mostly linear except for a bunch of tasks that have an icc ~ 0.
+These two measures give mostly similar answers regarding the reliabilities of the measures except for
 
@@
 
-The group of zero values for the ICC may be that the ICC is more of a measure of consistency than the Spearman/Pearson measures of rank order similarity.
+"The group of zero values for the ICC may be that the ICC is more of a measure of consistency than the Spearman/Pearson measures of rank order similarity.
 Or it could be the ICC calculation is off in some way.
 It would be worth focusing on five of these unusual cases (where the ICC is zero but the Pearson/Spearman is large) and calculate the ICC using other formulas.
-Generally the Spearman and Pearson differ when there are ties.
+Generally the Spearman and Pearson differ when there are ties.""
 
@@
 # Completion dates
+
+Is a subject more/less consistent depending on how much time has passed in between?
+
+How do you aggregate all this information to decide on what is a good measure?
+
+Do any of these quantifications of reliability relate to number of items (e.g. surveys with fewer items are more or less reliable - easier to remember or noisier?)
+
+--------------------
+One reason why it's difficult to get a sense of what is going on in this paper other than just saying that questionnaires have higher reliability than tasks is because there are too many measures.
+While a discussion on why some measures are more reliable than others might help with this and in building readers' intuitions about better ways to measure these constructs the paper might have a larger impact andbe eeasier to digest with more of an organizational structure, parsing these variables.
+On the one hand this could be a little contrary to our general theory blind approach to these measures but on the other hand it could also help us reinforce the terminology we are converging on with the analyses of the factor structure of these data.
+Because at the end of the day this paper would be most useful if it can make prescriptive recommendations on which tasks to use and reduce the utilitization of non-reliable measures.

### 2017-04-05 SRO_Report.Rmd
working in report

@@
 
-```{r warning=FALSE, message=FALSE}
-ggplot_build(icc_df %>%
+```{r warning=FALSE, message=FALSE, fig.height=72}
+time_effect_vars = ggplot_build(icc_df %>%
                ggplot(aes(eta_sq, fill=task)) +
@@
   prettify_label(.) %>%
-  filter(bin != 1 & bin !=2 & !is.na(label)) %>%
-  select(label)
+  filter(bin != 1 & bin !=2 & label != "NA") %>%
+  select(label, task) %>%
+  separate(label,into=c(as.character(1:27)),sep = "</br>") %>%
+  gather(key, value, -task) %>%
+  select(value, task) %>%
+  na.omit()
 
-anyNA("NA") 
+time_effect_vars$value = gsub("\"", "", time_effect_vars$value)
+
+tmp = data.frame()
+
+for(i in 1:nrow(time_effect_vars)){
+  tmp = rbind(tmp, match_t1_t2(time_effect_vars$value[i]))
+}
+rm(time_effect_vars)
+
+tmp %>%
+  spread(time, score) %>%
+  # mutate(dv_wrap = str_wrap(dv, width = 30)) %>%
+  ggplot(aes(`1`, `2`))+
+  geom_point()+
+  theme_bw()+
+  facet_wrap(~dv, scales='free', labeller = label_wrap_gen())+
+  geom_abline(intercept = 0, slope=1)
+
+tmp
+
+tmp %>% 
+  outer_join(icc_df[,c("dv", "eta_sq"), by="dv"])
+
 ```

### 2017-04-06 SRO_Report.Rmd
changed to new retest release

--- 2017-04-05 SRO_Report.Rmd
@@
 ```{r}
-retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/meaningful_variables.csv')
+retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/meaningful_variables.csv')
 
-retest_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/meaningful_variables_noDDM.csv')
+retest_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/meaningful_variables_noDDM.csv')
 
-retest_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/meaningful_variables_EZ.csv')
+retest_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/meaningful_variables_EZ.csv')
 
@@
 
-So what variables show a non-negligible effect of time and in what direction?
+So what variables show a non-negligible effect of time and in what direction? (sorted by increasing partial $\eta^2$)
 
 ```{r warning=FALSE, message=FALSE}
-ggplot_build(icc_df %>%
+time_effect_vars = ggplot_build(icc_df %>%
                ggplot(aes(eta_sq, fill=task)) +
@@
   prettify_label(.) %>%
-  filter(bin != 1 & bin !=2 & !is.na(label)) %>%
-  select(label)
+  filter(bin != 1 & bin !=2 & label != "NA") %>%
+  select(label, task) %>%
+  separate(label,into=c(as.character(1:27)),sep = "</br>") %>%
+  gather(key, value, -task) %>%
+  select(value, task) %>%
+  na.omit()
 
-anyNA("NA") 
+time_effect_vars$value = gsub("\"", "", time_effect_vars$value)
+time_effect_vars
+```
+
+Here is a scatter plot of these variables but I'm not including it in the report for now because it is too large and because I want to get back to this once I refit the hddm's for retest participants only.
+
+```{r warning=FALSE, message=FALSE, fig.height=72, eval=FALSE}
+tmp = data.frame()
+
+for(i in 1:nrow(time_effect_vars)){
+  tmp = rbind(tmp, match_t1_t2(time_effect_vars$value[i]))
+}
+rm(time_effect_vars)
+
+tmp = tmp %>%
+  inner_join(icc_df[,c("dv", "eta_sq")],by="dv")
+
+tmp = tmp %>% 
+  mutate(dv = factor(dv, levels = unique(tmp$dv[order(tmp$eta_sq)])))
+
+ggplotly(tmp %>%
+  spread(time, score) %>%
+  ggplot(aes(`1`, `2`))+
+  geom_point()+
+  theme_bw()+
+  facet_wrap(~dv, scales='free', labeller = label_wrap_gen())+
+  geom_abline(intercept = 0, slope=1))
 ```
@@
 
-Some variables (`r neg_icc_vars$dv`) have <0 ICC's. This would be the case if the $MS_{error}$>$MS_{between}$. That is, ICC would be negative if the ...
+Some variables (`r neg_icc_vars$dv`) have <0 ICC's. This would be the case if the $MS_{error}$>$MS_{between}$.
 
@@
 
-Ties?
-
-"The group of zero values for the ICC may be that the ICC is more of a measure of consistency than the Spearman/Pearson measures of rank order similarity.
+```{r echo=FALSE, eval=FALSE}
+# Ties?
+# 
+# "The group of zero values for the ICC may be that the ICC is more of a measure of consistency than the Spearman/Pearson measures of rank order similarity.
 Or it could be the ICC calculation is off in some way.
@@
 
-```{r}
 ties_df <- data.frame(unique_entries = rep(NA, length(numeric_cols)), 
@@
 ```
-
-# Completion dates
-
-Is a subject more/less consistent depending on how much time has passed in between?
-
-How do you aggregate all this information to decide on what is a good measure?
-
-Do any of these quantifications of reliability relate to number of items (e.g. surveys with fewer items are more or less reliable - easier to remember or noisier?)
-
---------------------
-One reason why it's difficult to get a sense of what is going on in this paper other than just saying that questionnaires have higher reliability than tasks is because there are too many measures.
-While a discussion on why some measures are more reliable than others might help with this and in building readers' intuitions about better ways to measure these constructs the paper might have a larger impact andbe eeasier to digest with more of an organizational structure, parsing these variables.
-On the one hand this could be a little contrary to our general theory blind approach to these measures but on the other hand it could also help us reinforce the terminology we are converging on with the analyses of the factor structure of these data.
-Because at the end of the day this paper would be most useful if it can make prescriptive recommendations on which tasks to use and reduce the utilitization of non-reliable measures.

### 2017-04-12 SRO_Report.Rmd
beginning to add the labels

@@
 
+## Reliability by measure types
+
+The results presented so far aim to be comprehensive but are difficult to parse through and get a clear sense of what is going on (other than a general impression that surveys tend to have higher reliabilities than tasks).
+In this and the following section we try to deal with this in two ways to make the results more digestable with two kinds of categorizations.
+
+In this section we label the measures based on the putative cognitive process they are intended to measure.
+For tasks this is mainly informed by Patrick's expertise/cognitive atlas and for surveys it is planned to be informed by the factor/IRT analyses.
+We aim to make contact with the literature to make the results more accesible to readers who have experience with our tasks but do not want to
+a. take away from the novelty of the main papers coming out of this project outlining the factor structure that this data unveils   
+b. necessarily make prescriptive recommendations or theoretical arguments on why certain measures of certain processes are more reliable than others.
+
+### Tasks
+
+```{r echo=FALSE}
+measure_labels <- read.csv('/Users/zeynepenkavi/Downloads/retest_measure_labels.csv')
+
+trim <- function (x) gsub("^\\s+|\\s+$", "", x)
+```
+
+```{r warning=FALSE, message=FALSE}
+measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(task == 'task') %>%
+  select(-measure_description, -notes, -variable_type, -task) %>%
+  left_join(icc_df[,c("dv", "icc")], by='dv') %>%
+  left_join(cor_df[,c("dv", "spearman")], by='dv') %>%
+  separate(measure_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
+  gather(key, value, -dv, -icc, -spearman) %>%
+  arrange(dv) %>%
+  drop_na() %>%
+  ggplot(aes(icc))+
+  geom_histogram(position = 'identity', alpha=0.5)+
+  theme_bw()+
+  facet_wrap(~value)
+```
+
+### Surveys
+
+To be filled with factor labels after processing either ASU factor analyses or Russ' MIRT.
+
+## Reliability by variable types
+
+In this section we label the measures based on the procedure behind the creation of a variable.
+This moves further away from the literature and thinking about our measures in terms of specific tasks, surveys or cognitive processes and is a more novel way of presenting our data.
+
+Potentially prescriptive recommendations coming out of this section would intend to build intuitions about different treatments to data that have higher reliabilities especially when researchers plan on making their own tasks and collecting different kinds of measures.
+
+### Tasks
+
+```{r warning=FALSE, message=FALSE}
+measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(task == 'task') %>%
+  select(-measure_description, -notes, -measure_type, -task) %>%
+  left_join(icc_df[,c("dv", "icc")], by='dv') %>%
+  left_join(cor_df[,c("dv", "spearman")], by='dv') %>%
+  separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
+  gather(key, value, -dv, -icc, -spearman) %>%
+  mutate(value = trim(value)) %>%
+  arrange(dv) %>%
+  drop_na() %>%
+  ggplot(aes(icc))+
+  geom_histogram(position = 'identity', alpha=0.5)+
+  theme_bw()+
+  facet_wrap(~value)
+```
+
+#### DDM parameters
+
+##### Difference versus all trials
+
+#### Raw versus model fit
+
+#### Condition versus all
+
+### Surveys
+
+Would this be a cmoparison of factor reliability versus item reliability?
+
 ```{r echo=FALSE, eval=FALSE}

### 2017-04-12 SRO_Report.Rmd
beginning to add the labels

@@
   drop_na() %>%
+  mutate(value = trim(value)) %>%
+  filter(dv %in% c("dot_pattern_expectancy.bias", "go_nogo.bias") == FALSE)%>%
   ggplot(aes(icc))+

### 2017-04-12 SRO_Report.Rmd
added replacing refitted hddm variables for t1 data

@@
 as.character(retest_subs_test_data$sub_id) == as.character(retest_data$sub_id)
+```
+
+### Replace HDDM parameters in t1 data
+
+Since HDDM parameters depend on the sample on which they are fit we refit the model on t1 data for the subjects that have t2 data.
+Here we replace the HDDM parameters in the current t1 dataset with these refitted values and transform them as they would have been transformed for the full sample to mimick the procedure we applied to rest of the t2 data.
+
+Transform hddm refits as they had been transformed for the full sample t1 data.
+```{r}
+hddm_refits <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/hddm_refits_exhaustive.csv')
+
+hddm_refits$X <- as.character(hddm_refits$X)
+
+names(hddm_refits)[1] <- 'sub_id'
+
+hddm_logTr_vars = data.frame(grep('(?=.*hddm)(?=.*logTr)', names(retest_subs_test_data), value=T, perl=T))
+names(hddm_logTr_vars) = c('var')
+hddm_logTr_vars$sign = ifelse(grepl(".ReflogTr",hddm_logTr_vars$var), 'negative', 'positive')
+hddm_logTr_vars$var = gsub(".logTr|.ReflogTr", "", hddm_logTr_vars$var)
+
+transformed_hddm_refits = hddm_refits
+
+for(i in 1:length(names(transformed_hddm_refits))){
+  tmp_col = names(transformed_hddm_refits)[i]
+  if(tmp_col %in% hddm_logTr_vars$var){
+    sign = hddm_logTr_vars$sign[which(tmp_col == hddm_logTr_vars$var)]
+      if(sign == 'positive'){
+        # clean_retest_data[,tmp_col] = log(clean_retest_data[,tmp_col])
+        transformed_hddm_refits[,tmp_col] = pos_log(transformed_hddm_refits[,tmp_col])
+        names(transformed_hddm_refits)[which(names(transformed_hddm_refits) == tmp_col)] = paste0(tmp_col, '.logTr')
+        cat(paste0(tmp_col ,' was positively skewed and transformed.'))
+        cat('\n')
+      }
+      else if(sign == 'negative'){
+        transformed_hddm_refits[,tmp_col] = neg_log(transformed_hddm_refits[,tmp_col])
+        names(transformed_hddm_refits)[which(names(transformed_hddm_refits) == tmp_col)] = paste0(tmp_col, '.ReflogTr')
+        cat(paste0(tmp_col ,' was negatively skewed and transformed.'))
+        cat('\n')
+      }
+    }
+}
+```
+
+Check if transformation of hddm refits worked
+```{r}
+transform_hddm_logTr_vars = data.frame(grep('logTr', names(transformed_hddm_refits), value=T))
+names(transform_hddm_logTr_vars) = c('var')
+transform_hddm_logTr_vars$sign = ifelse(grepl(".ReflogTr",transform_hddm_logTr_vars$var), 'negative', 'positive')
+transform_hddm_logTr_vars$var = gsub(".logTr|.ReflogTr", "", transform_hddm_logTr_vars$var)
+transform_hddm_logTr_vars = transform_hddm_logTr_vars %>% arrange(var)
+hddm_logTr_vars = hddm_logTr_vars %>% arrange(var)
+transform_hddm_logTr_vars == hddm_logTr_vars
+```
+
+Replace t1 hddm parameters for retest subjects
+
+```{r}
+replace_hddm_vars = data.frame(grep('(?=.*hddm)(?=.*logTr)', names(retest_subs_test_data), value=T, perl=T))
+names(replace_hddm_vars) = c('var')
+
+hddm_fix_retest_subs_test_data = retest_subs_test_data
+
+for(i in 1:length(names(hddm_fix_retest_subs_test_data))){
+  if(names(hddm_fix_retest_subs_test_data)[i] %in% replace_hddm_vars$var){
+    hddm_fix_retest_subs_test_data[,names(hddm_fix_retest_subs_test_data)[i]] <- transformed_hddm_refits[,names(hddm_fix_retest_subs_test_data)[i]]
+  }
+}
+
+retest_subs_test_data <- hddm_fix_retest_subs_test_data
+```
+
+```{r}
+rm(hddm_refits, transformed_hddm_refits, hddm_logTr_vars, transform_hddm_logTr_vars, replace_hddm_vars, hddm_fix_retest_subs_test_data)
 ```

### 2017-04-12 SRO_Report.Rmd
reran report with replaced hddm parameters

@@
 ```{r echo=FALSE}
+#Convenience functions to make prettier interactive histograms
 get_labels = function(plot_df, ref_df, bin_col, group_col){
@@
 ```{r}
-match_t1_t2 <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id'){
+match_t1_t2 <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id'){
   df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var)
@@
 
-get_icc <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id'){
+get_icc <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id'){
   df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
@@
 
-get_eta <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id'){
+get_eta <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id'){
   df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
@@
 
-get_sem <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id'){
+get_sem <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id'){
   df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)

### 2017-04-13 SRO_Report.Rmd
cont working on labeling and summarizing per task

@@
 
-In this section we label the measures based on the putative cognitive process they are intended to measure.
-For tasks this is mainly informed by Patrick's expertise/cognitive atlas and for surveys it is planned to be informed by the factor/IRT analyses.
+### Tasks
+
 We aim to make contact with the literature to make the results more accesible to readers who have experience with our tasks but do not want to   
@@
 
-### Tasks
+With this in mind we reduce the list of over 270 task measures to a list of one per task by averaging only the raw measures from all the trials in a task.
+We chose to reduce the information in this manner to avoid any bias stemming from differential amount of interest and procedures applied to certain tasks over others (e.g.
+a task can have over 10 measures because it has multiple conditions and we have chosen to fit DDM's for specific conditions while another might only have 2 due to our relative inexperience and lack of interest in it).
+We check whether the number of trials in a task has a significant effect on these average reliabilities of raw measures as well.
+
+We plan to supplement/potentially replace this with an additional labeling procedure intending to capture the underlying putative cognitive processes but are deferring this until at least for another week.
+This exercise might not even prove helpful but at least a per task summary seemed a reasonable first pass.
 
@@
 
+Summarize all raw per task
+
 ```{r warning=FALSE, message=FALSE}
+measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(task == 'task') %>%
+  select(-measure_description, -notes, -measure_type, -task) %>%
+  left_join(icc_df[,c("dv", "icc")], by='dv') %>%
+  left_join(cor_df[,c("dv", "spearman")], by='dv') %>%
+  separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
+  gather(key, value, -dv, -icc, -spearman, -num_all_trials) %>%
+  arrange(dv) %>%
+  drop_na() %>%
+  mutate(value = trim(value))
+```
+
+Does number of items in a trial have a significant effect on the average reliability of raw measures from a task?
+
+```{r}
+summary(lm(icc ~ num_all_trials))
+```
+
+```{r warning=FALSE, message=FALSE, eval=FALSE}
+#Plot of distribution of icc's faceted by putative measure
 measure_labels %>%

### 2017-04-13 SRO_Report.Rmd
added average reliabilities per task

@@
 
-Summarize all raw per task
+We filter out the DDM parameters and measures for specific contrasts.
+Note that this does leave some tasks with measures that are model fits and/or for specific conditions (because at least the current datasets do not include measures that are based on all the trials **and** are raw though I could dive in to variables_exhaustive for such measures).
+Here's the order of tasks by mean reliability sorted for ICC and then Spearman's $\rho$.
 
 ```{r warning=FALSE, message=FALSE}
-measure_labels %>%
+tmp = measure_labels %>%
   mutate(dv = as.character(dv)) %>%
@@
   separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
-  gather(key, value, -dv, -icc, -spearman, -num_all_trials) %>%
-  arrange(dv) %>%
-  drop_na() %>%
-  mutate(value = trim(value))
-```
-
-Does number of items in a trial have a significant effect on the average reliability of raw measures from a task?
-
-```{r}
-summary(lm(icc ~ num_all_trials))
+  mutate(label_1 = trim(label_1),
+         label_2=trim(label_2),
+         label_3=trim(label_3))%>%
+  filter(label_1 %in% c('difference', 'EZ', 'hddm') ==FALSE & label_2 %in% c('difference', 'EZ', 'hddm') == FALSE) %>%
+  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
+  select(-extra_1, -extra_2) %>%
+  group_by(task_name) %>%
+  summarise(mean_icc = mean(icc),
+            mean_spearman = mean(spearman),
+            num_measures = n(),
+            num_trials = unique(num_all_trials)) %>%
+  arrange(-mean_icc, -mean_spearman)
+
+tmp
+```
+
+Does number of items in a task have a significant effect on the average ICC of (mostly) raw measures for all trials from a task? No.
+
+```{r warning=FALSE, message=FALSE}
+summary(lm(mean_icc ~ num_trials, data = tmp))
+```
+
+Does number of items in a task have a significant effect on the average Spearman $\rho$ of (mostly) raw measures for all trials from a task? No.
+
+```{r warning=FALSE, message=FALSE}
+summary(lm(mean_spearman ~ num_trials, data = tmp))
+```
+
+Does number of measures that went in to this reliability estimate have a significant effect on the average ICC of (mostly) raw measures for all trials from a task? No.
+
+```{r warning=FALSE, message=FALSE}
+summary(lm(mean_icc ~ num_measures, data = tmp))
+```
+
+Does number of measures that went in to this reliability estimate have a significant effect on the average ICC of (mostly) raw measures for all trials from a task?  
+The regression suggests that the more measures that went in to the averaging of Spearman's $\rho$'s the lower the mean Spearman $\rho$ for that task.
+This might suggest that this way of summarizing data might not be a good idea in general or at least that we shouldn't do it for the Spearman correlations.
+
+```{r warning=FALSE, message=FALSE}
+summary(lm(mean_spearman ~ num_measures, data = tmp))
 ```

### 2017-04-13 SRO_Report.Rmd
fixed typo

@@
 
-```{r warning=FALSE, message=FALSE}
+```{r warning=FALSE, message=FALSE, eval=FALSE}
 measure_labels %>%
@@
 
-Would this be a cmoparison of factor reliability versus item reliability?
+Would this be a comparison of factor reliability versus item reliability?
 

### 2017-04-14 SRO_Report.Rmd
begun ddm variable comparisons

@@
   filter(task == 'task') %>%
-  select(-measure_description, -notes, -measure_type, -task) %>%
+  select(-measure_description, -notes, -measure_type, -task, -ddm_task) %>%
   left_join(icc_df[,c("dv", "icc")], by='dv') %>%
@@
 
-```{r warning=FALSE, message=FALSE, eval=FALSE}
-measure_labels %>%
+#### DDM parameters
+
+```{r warning=FALSE, message=FALSE}
+tmp = measure_labels %>%
   mutate(dv = as.character(dv)) %>%
@@
   separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
-  gather(key, value, -dv, -icc, -spearman) %>%
-  mutate(value = trim(value)) %>%
-  arrange(dv) %>%
-  drop_na() %>%
-  ggplot(aes(icc))+
-  geom_histogram(position = 'identity', alpha=0.5)+
+  mutate(label_1 = trim(label_1),
+         label_2=trim(label_2),
+         label_3=trim(label_3))%>%
+  filter(ddm_task == 1) %>%
+  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.', remove=FALSE) %>%
+  select(-extra_1, -extra_2) %>%
+  drop_na()
+```
+
+In addition to raw response time and accuracy measures we get from certain tasks we have also chosen to fit drift diffusion models to them.
+The tasks we have chosen to fit these models are: `unique(tmp$task_name)`.
+This list does not include all cognitive tasks in the battery.
+
+Table of median reliabilities for the two kinds of DDM models' (hddm and EZ) parameters compared to raw response times and accuracies depending on whether they were fit to all data or whether they are contrast of two conditions sorted by mean ICC and mean Spearman's $\rho$.
+
+```{r warning=FALSE, message=FALSE}
+tmp %>%
+  group_by(label_1,label_2, label_3) %>%
+  summarise(mean_icc = mean(icc),
+            mean_spearman = mean(spearman),
+            n_vars = n()) %>%
+  arrange(-mean_icc, -mean_spearman)
+```
+
+This is what the distributions of look like
+
+```{r warning=FALSE, message=FALSE}
+tmp %>%
+  select(dv, icc, spearman, label_1, label_2, label_3) %>%
+  gather(key, value, -dv, -label_1, -label_2, -label_3) %>%
+  ggplot(aes(value, color=label_2, fill=label_3))+
+  geom_histogram(position='identity', alpha = 0.5)+
   theme_bw()+
-  facet_wrap(~value)
-```
-
-#### DDM parameters
-
-##### Difference versus all trials
-
-#### Raw versus model fit
-
-#### Condition versus all
+  facet_wrap(key~label_1)+
+  labs(color="Model", fill="Parameter")
+```
 

### 2017-04-14 SRO_Report.Rmd
begun ddm variable comparisons

@@
 
-```{r warning=FALSE, message=FALSE, eval=FALSE}
-#Plot of distribution of icc's faceted by putative measure
-measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  select(-measure_description, -notes, -variable_type, -task) %>%
-  left_join(icc_df[,c("dv", "icc")], by='dv') %>%
-  left_join(cor_df[,c("dv", "spearman")], by='dv') %>%
-  separate(measure_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
-  gather(key, value, -dv, -icc, -spearman) %>%
-  arrange(dv) %>%
-  drop_na() %>%
-  mutate(value = trim(value)) %>%
-  filter(dv %in% c("dot_pattern_expectancy.bias", "go_nogo.bias") == FALSE)%>%
-  ggplot(aes(icc))+
-  geom_histogram(position = 'identity', alpha=0.5)+
-  theme_bw()+
-  facet_wrap(~value)
-```
-
 ### Surveys
@@
 
+- All parameters that were fit to all trials compared to contrasts have higher relialibilities.   
+- Raw variables are not the variables with highest reliabilities overall.  
+- 2 of 3 hddm parameters also have higher mean reliabilities than EZ parameter estimates.
+
 ```{r warning=FALSE, message=FALSE}

### 2017-04-14 SRO_Report.Rmd
added ddm distributions plot and failed effort to making it interactive

@@
 
+## Tasks
+
+## Surveys
+
 # Methods
+
+## Data collection
 
@@
     for(j in 1:nrow(plot_df)){
-      if(ref_df[i, bin_col] <= plot_df$xmax[j] & ref_df[i, bin_col]>=plot_df$xmin[j] & ref_df[i, group_col] == plot_df[j, group_col]){
+      if(ref_df[i, bin_col] <= plot_df$xmax[j] & ref_df[i, bin_col]>=plot_df$xmin[j] & all(ref_df[i, group_col] == plot_df[j, group_col])){
         ref_df$bin[i] <- plot_df$bin[j]
@@
   ref_df = ref_df %>% 
-    group_by(bin, task) %>%
+    group_by_("bin", group_col) %>%
     mutate(label=as.character(toJSON(unique(dv))))
 
-  label_df = ref_df[!duplicated(ref_df[,c('label')]),c('task', 'bin', 'label')]
-
-  out_df = left_join(plot_df,label_df, by= c("bin", "task"))
+  label_df = ref_df[!duplicated(ref_df[,c('label')]),c(group_col, 'bin', 'label')]
+
+  out_df = left_join(plot_df,label_df, by= c("bin", group_col))
 
@@
 We aim to make contact with the literature to make the results more accesible to readers who have experience with our tasks but do not want to   
-a. take away from the novelty of the main papers coming out of this project outlining the factor structure that this data unveils   
-b. necessarily make prescriptive recommendations or theoretical arguments on why certain measures of certain processes are more reliable than others.
+1. take away from the novelty of the main papers coming out of this project outlining the factor structure that this data unveils   
+2. necessarily make prescriptive recommendations or theoretical arguments on why certain measures of certain processes are more reliable than others.
 
@@
 - All parameters that were fit to all trials compared to contrasts have higher relialibilities.   
-- Raw variables are not the variables with highest reliabilities overall.  
+- Raw variables are not the variables with highest ICC's overall. Raw response times do, however, have the highest Spearman's $\rho$'s on average. 
 - 2 of 3 hddm parameters also have higher mean reliabilities than EZ parameter estimates.
@@
 ```{r warning=FALSE, message=FALSE}
-tmp %>%
+tmp = tmp %>%
   select(dv, icc, spearman, label_1, label_2, label_3) %>%
-  gather(key, value, -dv, -label_1, -label_2, -label_3) %>%
+  gather(key, value, -dv, -label_1, -label_2, -label_3)
+
+tmp %>% ggplot(aes(value, color=label_2, fill=label_3))+
+  geom_histogram(position='identity', alpha = 0.5)+
+  theme_bw()+
+  facet_wrap(key~label_1)+
+  labs(color="Model", fill="Parameter")
+```
+
+```{r message=FALSE, echo=FALSE, eval=FALSE}
+#attempt to make the above interactive. didn't really work
+ggplotly(ggplot_build(tmp %>%
                         ggplot(aes(value, color=label_2, fill=label_3))+
@@
                         facet_wrap(key~label_1)+
-  labs(color="Model", fill="Parameter")
-```
-
+                        labs(color="Model", fill="Parameter"))$data[[1]] %>%
+           mutate(key = ifelse(PANEL %in%  c(1,2), "icc", "spearman"),
+                  label_1 = ifelse(PANEL %in%  c(1,3), "all", "difference"),
+                  label_2 = ifelse(colour == "#F8766D", "EZ", ifelse(colour == "#00BA38", "hddm", "raw")),
+                  label_3 = ifelse(fill == "#A3A500", "drift rate", ifelse(fill == "#00BF7D", "non-decision", ifelse(fill == "#E76BF3", "threshold", ifelse(fill == "#F8766D", "accuracy", "rt"))))) %>%
+           get_labels(.,tmp, "value", c("label_1", "label_2", "label_3", "key")) %>%
+           prettify_label(.) %>%
+           ggplot(aes(x, y, fill = label_3, color=label_2, label=label))+
+           geom_bar(stat='identity',position='identity', alpha=0.5)+
+           facet_wrap(key~label_1)+
+           theme_bw(),
+         tooltip = 'label',
+         hoverinfo = 'text')
+```
 ### Surveys

### 2017-04-16 SRO_Report.Rmd
begun adding the completion time analyses

@@
 ```{r}
-match_t1_t2 <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id'){
+match_t1_t2 <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', format = "long"){
   df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var)
+
   df = df %>% 
@@
     select(-drop)
+
+  if(format == 'wide'){
+    df = df%>% spread(time, score) 
+  }
+
   return(df)
@@
 
+## Completion times
+
+Do people differ in how much their scores change depending on how many days it has been since they completed the initial battery?
+
+Make data frame with standardized difference between two scores for each measure for each subject.
+
+```{r}
+t1_2_difference = data.frame()
+
+for(i in 1:length(numeric_cols)){
+  tmp = match_t1_t2(numeric_cols[i],format='wide')
+  tmp = tmp %>% 
+    mutate(difference = scale(`2` - `1`))
+  t1_2_difference = rbind(t1_2_difference, tmp)
+}
+
+str(as.data.frame(t1_2_difference$difference))
+```
+
+Add completion dates to this data frame.
+
+```{r}
+disc_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/discovery_completion_dates.csv', header=FALSE)
+val_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/validation_completion_dates.csv', header=FALSE)
+test_comp_date = rbind(disc_comp_date, val_comp_date)
+rm(disc_comp_date, val_comp_date)
+retest_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/retest_completion_dates.csv', header=FALSE)
+comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
+names(comp_dates) <- c("sub_id", "retest_comp", "test_comp")
+comp_dates$retest_comp = as.Date(comp_dates$retest_comp)
+comp_dates$test_comp = as.Date(comp_dates$test_comp)
+comp_dates$days_btw = with(comp_dates, retest_comp-test_comp)
+
+t1_2_difference = merge(t1_2_difference, comp_dates[,c('sub_id', 'days_btw')], by='sub_id')
+```
+
+The effect of number of days in between in the full model you'd want (potentially even including the interaction between the fixed effects)
+
+```{r eval = FALSE}
+mod = lmer(difference ~ dv + days_btw + (1|sub_id), data = t1_2_difference)
+
+mod_fixed = as.data.frame(fixef(mod))
+mod_fixed["days_btw",]
+```
+
+Does average standardized difference change with number of days between completion?
+
+```{r}
+tmp = t1_2_difference %>%
+  group_by(sub_id) %>%
+  summarise(mean_diff = mean(difference, na.rm=T),
+            days_btw = unique(days_btw))
+
+length(unique(tmp$mean_diff))
+str(as.data.frame(t1_2_difference$difference))
+
+tmp %>%
+  ggplot(aes(days_btw, mean_diff))+
+  geom_point()+
+  theme_bw()
+```
+
+Box plots showing the distribution of difference scores for each task
+
+```{r}
+t1_2_difference %>%
+  ggplot(aes(dv, difference))+
+  geom_boxplot()+
+  theme_bw()+
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+```
+
 ```{r echo=FALSE, eval=FALSE}

### 2017-04-17 SRO_Report.Rmd
fixed completion times plots

@@
 ```{r}
-rm(hddm_refits, transformed_hddm_refits, hddm_logTr_vars, transform_hddm_logTr_vars, replace_hddm_vars, hddm_fix_retest_subs_test_data)
+rm(hddm_refits, transformed_hddm_refits, hddm_logTr_vars, transform_hddm_logTr_vars, replace_hddm_vars, hddm_fix_retest_subs_test_data, sign, i)
 ```
@@
 Median reliability and the number of variables for both the surveys and the tasks:
-As implied by Spearman the ICC's are higher for surveys.  
-Systematic differences between the two measurements are higher for tasks than surveys (potentially indicating learning effects).  
+As seen with Spearman $\rho$'s as well the ICC's are higher for surveys.  
+Systematic differences between the two measurements ($\eta^2$) are higher for tasks than surveys (potentially indicating learning effects?).  
 Unexpectedly, median standard error of measurement is higher for surveys but the distribution below suggests that this is a side effect of having too many task measures with very low SEMs.
@@
 
-```{r}
+```{r warning=FALSE}
 t1_2_difference = data.frame()
@@
 
-str(as.data.frame(t1_2_difference$difference))
+t1_2_difference$difference = as.data.frame(t1_2_difference$difference)$V1
+```
+
+```{r echo=FALSE}
+rm(tmp, i)
 ```
@@
 
-```{r}
+```{r warning=FALSE}
 disc_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/discovery_completion_dates.csv', header=FALSE)
@@
 t1_2_difference = merge(t1_2_difference, comp_dates[,c('sub_id', 'days_btw')], by='sub_id')
+str(t1_2_difference)
 ```
@@
 
-```{r}
+```{r warning=FALSE, message=FALSE}
 tmp = t1_2_difference %>%
@@
 
-length(unique(tmp$mean_diff))
-str(as.data.frame(t1_2_difference$difference))
-
-tmp %>%
+ggplotly(tmp %>%
   ggplot(aes(days_btw, mean_diff))+
   geom_point()+
-  theme_bw()
+  theme_bw()+
+  xlab("Days between completion")+
+  ylab("Mean standardized difference between two time points")+
+  geom_smooth(method="lm"))
 ```
@@
 
-```{r}
+```{r fig.width=20}
 t1_2_difference %>%

### 2017-04-18 SRO_Report.Rmd
changed box plots of differences

@@
 t1_2_difference = merge(t1_2_difference, comp_dates[,c('sub_id', 'days_btw')], by='sub_id')
-str(t1_2_difference)
 ```
@@
 
-Box plots showing the distribution of difference scores for each task
-
-```{r fig.width=20}
-t1_2_difference %>%
-  ggplot(aes(dv, difference))+
+To confirm the slope of this line is not significant.
+That is, there doesn't seem to be a systematic difference between the two measurements depending on the number of days between the two measurements.
+
+```{r warning=FALSE, message=FALSE}
+summary(lm(mean_diff ~ days_btw, data=tmp))
+```
+
+For reference here are the box plots showing the distribution of difference scores for each task.
+
+```{r warning=FALSE, message=FALSE, fig.height=36}
+ggplotly(t1_2_difference %>%
+           ggplot(aes(dv, difference, label=dv))+
            geom_boxplot()+
            theme_bw()+
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+           coord_flip()+
+           xlab("")+
+           ylab("Standardized difference")
+)
 ```

### 2017-04-18 SRO_Report.Rmd
playing around with not centering the differences between two measurements

@@
   tmp = tmp %>% 
-    mutate(difference = scale(`2` - `1`))
+    # mutate(difference = scale(`2` - `1`))
+  mutate(difference = scale(`2` - `1`, center=F))
   t1_2_difference = rbind(t1_2_difference, tmp)
@@
 t1_2_difference$difference = as.data.frame(t1_2_difference$difference)$V1
+str(t1_2_difference)
 ```
@@
 
+```{r echo=FALSE}
+rm(test_comp_date, retest_comp_date, comp_dates)
+```
+
 The effect of number of days in between in the full model you'd want (potentially even including the interaction between the fixed effects)
@@
            theme_bw()+
-           coord_flip()+
            xlab("")+
-           ylab("Standardized difference")
-)
+           ylab("Standardized difference")+
+           coord_flip())
 ```

### 2017-04-18 SRO_Report.Rmd
clarifications on writing and deleting unused chunks

@@
 
-Here is a scatter plot of these variables but I'm not including it in the report for now because it is too large and because I want to get back to this once I refit the hddm's for retest participants only.
-
-```{r warning=FALSE, message=FALSE, fig.height=72, eval=FALSE}
-tmp = data.frame()
-
-for(i in 1:nrow(time_effect_vars)){
-  tmp = rbind(tmp, match_t1_t2(time_effect_vars$value[i]))
-}
-rm(time_effect_vars)
-
-tmp = tmp %>%
-  inner_join(icc_df[,c("dv", "eta_sq")],by="dv")
-
-tmp = tmp %>% 
-  mutate(dv = factor(dv, levels = unique(tmp$dv[order(tmp$eta_sq)])))
-
-ggplotly(tmp %>%
-  spread(time, score) %>%
-  ggplot(aes(`1`, `2`))+
-  geom_point()+
-  theme_bw()+
-  facet_wrap(~dv, scales='free', labeller = label_wrap_gen())+
-  geom_abline(intercept = 0, slope=1))
-```
+Box plots showing the distributions of difference scores between the measurements at two time points for each measure can be found under the [Completion times](#diff_plot) section.
 
@@
 
-Make data frame with standardized difference between two scores for each measure for each subject.
+Make data frame with difference between two scores for each measure for each subject.
+Since the scores for different measures are on different scales for comparability the difference scores are scaled (i.e.
+divided by their root mean square) but not centered so a value of 0 for the difference scores would indicate a lack of a difference between the scores of a subject.
 
@@
 t1_2_difference$difference = as.data.frame(t1_2_difference$difference)$V1
-str(t1_2_difference)
 ```
@@
 
-The effect of number of days in between in the full model you'd want (potentially even including the interaction between the fixed effects)
-
-```{r eval = FALSE}
+The effect of number of days in between in the full model where the difference scores are regressed on a fixed effect for measure and days between the two scores and random intercepts for each subject (*Should this model include the interaction between the fixed effects?*).
+Since there are over 300 measures the output of the full model is not presented here.
+Instead below are the coefficient for the fixed effect of days between completion times and its t value.
+
+```{r}
 mod = lmer(difference ~ dv + days_btw + (1|sub_id), data = t1_2_difference)
 
-mod_fixed = as.data.frame(fixef(mod))
-mod_fixed["days_btw",]
-```
-
-Does average standardized difference change with number of days between completion?
+data.frame(estimate=coef(summary(mod))["days_btw","Estimate"], tval=coef(summary(mod))["days_btw","t value"])
+```
+
+For visualization purposes I summarized the difference scores per person by looking at the average difference and plot that against the number of days between completion.
 
@@
 
-To confirm the slope of this line is not significant.
+To confirm: the slope of this line is not significant.
 That is, there doesn't seem to be a systematic difference between the two measurements depending on the number of days between the two measurements.
@@
 
+<a id="diff_plot"></a>
 For reference here are the box plots showing the distribution of difference scores for each task.

### 2017-04-18 SRO_Report.Rmd
Began writing methods

@@
 
-## Tasks
-
-## Surveys
-
 # Methods
@@
 ## Data collection
+
+This sample consists of data for 150 subjects of the original sample of 522 that has completed the initial battery of 37 cognitive tasks, 23 surveys and 3 surveys on demographics.
+Details of the original sample as well as quality control (qc) procedures are described elsewhere.
+Invited participants were chosen randomly and only subsets of them were invited for a given batch (instead of opening the battery to all qualified subjects) with the intention to avoid a potential oversampling and bias towards high self regulators.
+
+```{r warning=FALSE, message=FALSE}
+workers = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/User_717570_workers.csv')
+workers = workers %>% 
+  group_by(Worker.ID) %>%
+  mutate(Retest_worker=ifelse(sum(CURRENT.RetestWorker,CURRENT.RetestWorkerB2,CURRENT.RetestWorkerB3,CURRENT.RetestWorkerB4,CURRENT.RetestWorkerB5,na.rm=T)>0,1,0)) %>%
+  ungroup()
+
+worker_counts <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/retest_worker_counts.json')
+
+worker_counts = as.data.frame(unlist(worker_counts))
+names(worker_counts) = "task_count"
+```
+
+In total `r sum(workers$Retest_worker)` participants were invited, `r nrow(worker_counts)` began the battery, `sum(worker_counts$task_count >= 62)` completed the battery and 150 provided data that passed qc for both time points.
+Our target sample size was determined in advance of data collection and data collection continued until this number of participants with data that survived qc was reached.
+
+```{r warning=FALSE, message=FALSE}
+disc_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/discovery_completion_dates.csv', header=FALSE)
+val_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/validation_completion_dates.csv', header=FALSE)
+test_comp_date = rbind(disc_comp_date, val_comp_date)
+rm(disc_comp_date, val_comp_date)
+retest_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/retest_completion_dates.csv', header=FALSE)
+comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
+names(comp_dates) <- c("sub_id", "retest_comp", "test_comp")
+comp_dates$retest_comp = as.Date(comp_dates$retest_comp)
+comp_dates$test_comp = as.Date(comp_dates$test_comp)
+comp_dates$days_btw = with(comp_dates, retest_comp-test_comp)
+```
+
+Data collection took place on average `r round(mean(as.numeric(comp_dates$days_btw)))` number of days after the completion of the initial battery with a range of `r round(range(as.numeric(comp_dates$days_btw)))[1]` to `r round(range(as.numeric(comp_dates$days_btw)))[2]` days.
+
+## Literature
+
+### Tasks
+
+### Surveys
 
@@
 ```{r warning=FALSE}
-disc_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/discovery_completion_dates.csv', header=FALSE)
-val_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/validation_completion_dates.csv', header=FALSE)
-test_comp_date = rbind(disc_comp_date, val_comp_date)
-rm(disc_comp_date, val_comp_date)
-retest_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/retest_completion_dates.csv', header=FALSE)
-comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
-names(comp_dates) <- c("sub_id", "retest_comp", "test_comp")
-comp_dates$retest_comp = as.Date(comp_dates$retest_comp)
-comp_dates$test_comp = as.Date(comp_dates$test_comp)
-comp_dates$days_btw = with(comp_dates, retest_comp-test_comp)
-
 t1_2_difference = merge(t1_2_difference, comp_dates[,c('sub_id', 'days_btw')], by='sub_id')

### 2017-04-20 SRO_Report.Rmd
added new labels

@@
 
-In total `r sum(workers$Retest_worker)` participants were invited, `r nrow(worker_counts)` began the battery, `sum(worker_counts$task_count >= 62)` completed the battery and 150 provided data that passed qc for both time points.
+In total `r sum(workers$Retest_worker)` participants were invited, `r nrow(worker_counts)` began the battery, `r sum(worker_counts$task_count >= 62)` completed the battery and 150 provided data that passed qc for both time points.
 Our target sample size was determined in advance of data collection and data collection continued until this number of participants with data that survived qc was reached.
@@
 measure_labels <- read.csv('/Users/zeynepenkavi/Downloads/retest_measure_labels.csv')
+measure_labels = measure_labels %>% select(-Patrick_hates)
 
@@
 We filter out the DDM parameters and measures for specific contrasts.
-Note that this does leave some tasks with measures that are model fits and/or for specific conditions (because at least the current datasets do not include measures that are based on all the trials **and** are raw though I could dive in to variables_exhaustive for such measures).
+Note that this does leave some tasks with measures that are model fits and/or for specific conditions (because at least the current datasets do not include measures that are based on all the trials **and** are raw though I could dive in to variables_exhaustive for such measures.
+For example the average relialibility for Kirby is based on three discount rates for specific conditions.).
 Here's the order of tasks by mean reliability sorted for ICC and then Spearman's $\rho$.
@@
 summary(lm(mean_spearman ~ num_measures, data = tmp))
+```
+
+In addition to average relilibilities for each task we can look at relilibities of measures organized by the putative cognitive process they are intended to measure.
+Note however that these labels are not determined in a data driven manner.
+
+```{r warning=FALSE, message=FALSE}
+measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(task == 'task') %>%
+  select(-measure_description, -notes, -variable_type, -task, -ddm_task) %>%
+  left_join(icc_df[,c("dv", "icc")], by='dv') %>%
+  left_join(cor_df[,c("dv", "spearman")], by='dv') %>%
+  group_by(measure_type) %>%
+  summarise(mean_icc = mean(icc),
+            mean_spearman = mean(spearman),
+            num_measures = n()) %>%
+  arrange(-mean_icc, -mean_spearman)
+```
+
+Here is what the distributions look like. Thoughts:
+- Alerting: This labels consists only of ANT alerting contrast (no cue - double cue trials). 4/6 are drift diffusion parameters.    
+- Cue encoding: This label consists only of three by two task switch cost contrast (stay (where cue and task remains the same) - switch (where task is the same but cue changes) trials).
+Again most are drift diffusion parameters.
+- Delay discounting: This label consists of the discount rates for the Bickel titrator (3), Kirby items (3) and discount titrate (model fit to random set of stimuli).
+**Does the discrepancy between ICC and Spearman for these measures, given the specific interest in these tasks in the literature warrant a more detailed look in to these?**
+- Information use: This label includes Columbia Card Task (both versions) and information sampling task.
+- Inhibition: This label includes go no-go, motor selective stop signal, stimulus selective stop signal and regular stop signal (excluding specific constrasts).
+- Intelligence: This label includes ravens and tower of london.
+- Learning: This label includes ART, CCT, two stage decision, dietary decision task, hierarchical rule task, information sampling task, probabilistic selection task, shift task, two stage task.  
+- Neutral writing: This label consists only of the writing task.  
+- Orienting: This labels consists only of ANT orienting contrast (center - spatial cue trials). 4/6 are drift diffusion parameters. 
+- Positive writing: This label consists only of the writing task.  
+- Proactive control: This labels consists of one DPX contrast (AY - BY trials), motor selective stop signal and regular stop signal. 
+- Reactive control: This labels consists of one DPX contrast (BX - BY trials) and motor selective stop signal.  
+- Resisting proactive interference: This label consists of one contrast in directed forgetting and recent probes tasks (negative (where the stimulus to respond to is in forgetting set) and control (where the stimulus to respond to is new) trials).
+- Response conflict: This label consists of ANT conflict contrast (congruent-incongruent), DPX, local global conflict contrast, shape matching, simon, stroop.  
+- Response selection: This label consists of choice reaction time task.
+- Risk Taking: This label consists of ART and CCT.
+- Selective attention: This label consists of local global task and ANT (all trials).
+- Set shifting: This label consists of local global, PRT and three by two.  
+- Speed: This label consists of raw response times in information sampling task, simple reaction time, tower of london.  
+- Working memory: This label consists of adaptive n back, digit span, directed forgetting, keep track, recent probes, spatial span.
+
+```{r warning=FALSE, message=FALSE}
+measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(task == 'task') %>%
+  select(-measure_description, -notes, -variable_type, -task, -ddm_task) %>%
+  left_join(icc_df[,c("dv", "icc")], by='dv') %>%
+  left_join(cor_df[,c("dv", "spearman")], by='dv') %>%
+  select(measure_type, icc, spearman) %>%
+  gather(key, value, -measure_type) %>%
+  ggplot(aes(value, fill=key))+
+  geom_histogram(position='identity', alpha=0.5)+
+  theme_bw()+
+  facet_wrap(~measure_type)+
+  theme(legend.title = element_blank())
 ```
@@
 ```
-
-```{r echo=FALSE, eval=FALSE}
-# Ties?
-# 
-# "The group of zero values for the ICC may be that the ICC is more of a measure of consistency than the Spearman/Pearson measures of rank order similarity.
-Or it could be the ICC calculation is off in some way.
-It would be worth focusing on five of these unusual cases (where the ICC is zero but the Pearson/Spearman is large) and calculate the ICC using other formulas.
-Generally the Spearman and Pearson differ when there are ties.""
-
-ties_df <- data.frame(unique_entries = rep(NA, length(numeric_cols)), 
-                     transformed = rep(NA, length(numeric_cols)))
-
-row.names(ties_df) <- numeric_cols
-
-for(i in 1:length(numeric_cols)){
-  ties_df[numeric_cols[i], 'unique_entries'] <- get_unique(numeric_cols[i])
-  ties_df[numeric_cols[i], 'transformed'] <- get_transformed(numeric_cols[i])
-}
-
-icc_df %>%
-  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
-  left_join(ties_df, by = 'dv')
-
-#Function to output: spearman, icc, number of unique values in column, whether it is log transformed
-
-#Gina seems right; these transformed variables have high Spearman but low ICC and they have few unique values (though this isn't )
-length(unique(retest_data$impulsive_venture_survey.impulsiveness.logTr))
-length(unique(retest_data$adaptive_n_back.mean_load.logTr))
-```

### 2017-04-20 SRO_Report.Rmd
minor formatting changes

@@
   theme(legend.title = element_blank()))
-```
-
-Which tasks show a systematic difference between t1 and t2?
-Are these the tasks where the ICC and Spearman imply different conclusions?
-
-```{r}
-icc_df %>%
-  select(dv, eta_sq) %>%
-  arrange(-eta_sq)
 ```
@@
 
-Here is what the distributions look like. Thoughts:
+Here is what the distributions look like.  
 - Alerting: This labels consists only of ANT alerting contrast (no cue - double cue trials). 4/6 are drift diffusion parameters.    
@@
 
-```{r warning=FALSE, message=FALSE}
+```{r warning=FALSE, message=FALSE, fig.width=12}
 measure_labels %>%
@@
 
-To be filled with factor labels after processing either ASU factor analyses or Russ' MIRT.
+To be filled with factor labels after processing either ASU factor analyses or Russ' MIRT?
 

### 2017-04-21 SRO_Report.Rmd
began changes based on meeting

@@
 
-```{r warning=FALSE, message=FALSE, fig.width=12}
+```{r warning=FALSE, message=FALSE, fig.width=12, fig.height=10}
 measure_labels %>%
@@
 
-tmp %>% ggplot(aes(value, color=label_2, fill=label_3))+
-  geom_histogram(position='identity', alpha = 0.5)+
+tmp %>% ggplot(aes(label_2, value, fill=label_3))+
+  geom_boxplot()+
   theme_bw()+
   facet_wrap(key~label_1)+
-  labs(color="Model", fill="Parameter")
+  labs(fill="Parameter")
 ```

### 2017-04-21 SRO_Report.Rmd
rearranged time difference graph by median

@@
 ```{r warning=FALSE, message=FALSE, fig.height=36}
-ggplotly(t1_2_difference %>%
-           ggplot(aes(dv, difference, label=dv))+
+t1_2_difference %>%
+           ggplot(aes(reorder(dv, difference, FUN=median), difference))+
+           geom_hline(yintercept = 0,color='red',size=1)+
            geom_boxplot()+
@@
            ylab("Standardized difference")+
-           coord_flip())
-```
+           coord_flip()
+```

### 2017-04-21 SRO_Report.Rmd
began writing bootstrapping code

@@
 
-get_icc <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id'){
-  df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
-  df = df %>% spread(time, score) %>% select(-dv, -sub_id)
+get_icc <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', match=TRUE, matched_df){
+  if(match==TRUE){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
+  }
+  else{
+    df = matched_df
+  }
+  df = df %>% select(-dv, -sub_id)
   icc = ICC(df)
@@
 
-get_eta <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id'){
+get_eta <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', match=TRUE, matched_df){
+  if(match==TRUE){
     df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
+  }
+  else{
+    df = matched_df
+  }
   mod = summary(aov(score~Error(sub_id)+time, df))
@@
 
-get_sem <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id'){
+get_sem <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', match=TRUE, matched_df){
+  if(match==TRUE){
     df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
+  }
+  else{
+    df = matched_df
+  }
   mod = summary(aov(score~Error(sub_id)+time, df))
@@
 ```
+
+Bootstrapping
+
+```{r}
+sample_workers = function(N = 150, repl= TRUE, df=retest_data, worker_col = "sub_id"){
+  return(sample(df[,worker_col], N, replace = repl))
+}
+
+extract_sample_data = function(sample, var_name, df, worker_col = "sub_id"){
+  return(df[df[,worker_col] %in% sample, var_name])
+}
+
+sample_workers()
+extract_sample_data(df=retest_data)
+extract_sample_data(df=retest_subs_test_data)
+```

### 2017-04-22 SRO_Report.Rmd
playing around with datatables

@@
 library(jsonlite)
+library(DT)
 sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
@@
 ```{r}
-cor_df %>%
+datatable(cor_df %>%
   filter(task == 'task') %>%
   select(dv, spearman) %>%
-  arrange(-spearman)
+  arrange(-spearman))
 ```

### 2017-04-22 SRO_Report.Rmd
changed all dataframes to datatables

@@
 
-df
+datatable(df)
 ```
@@
 ```{r}
-cor_df %>%
+datatable(cor_df %>%
   group_by(task) %>%
   summarise(mean_spearman = mean(spearman),
-            num_vars = n())
+            num_vars = n()))
 ```
@@
 ```{r}
-cor_df %>%
+datatable(cor_df %>%
   filter(task == 'survey') %>%
   select(dv, spearman) %>%
-  arrange(-spearman)
+  arrange(-spearman))
 ```
@@
 ```{r}
-icc_df %>%
+datatable(icc_df %>%
   group_by(task) %>%
@@
             median_sem = median(sem),
-            num_vars = n())
+            num_vars = n()))
+```
+
+#### Rank order of ICCs, partial $\eta^2$ and SEM
+
+Note that these tables can be sorted for any of the columns.
+
+###### For tasks
+
+```{r}
+datatable(icc_df %>%
+  filter(task == 'task') %>%
+  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
+  arrange(-icc) %>%
+  select(dv, -task, icc, eta_sq, sem, spearman))
+```
+
+###### For surveys
+
+```{r}
+datatable(icc_df %>%
+  filter(task == 'survey') %>%
+  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
+  arrange(-icc) %>%
+  select(dv, -task, icc, eta_sq, sem, spearman))
 ```
@@
 
-#### Rank order of ICCs
-
-###### For tasks
-
-```{r}
-icc_df %>%
-  filter(task == 'task') %>%
-  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
-  arrange(-icc) %>%
-  select(dv, -task, icc, eta_sq, sem, spearman)
-```
-
-###### For surveys
-
-```{r}
-icc_df %>%
-  filter(task == 'survey') %>%
-  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
-  arrange(-icc) %>%
-  select(dv, -task, icc, eta_sq, sem, spearman)
-```
-
 ### Distributions of partial $\eta^2$ by task vs. survey
@@
 
-#### Rank order of partial $\eta^2$
-
-###### For tasks
-
-```{r}
-icc_df %>%
-  filter(task == 'task') %>%
-  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
-  arrange(-eta_sq) %>%
-  select(dv, -task, eta_sq, icc, sem, spearman)
-```
-
-###### For surveys
-
-```{r}
-icc_df %>%
-  filter(task == 'survey') %>%
-  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
-  arrange(-eta_sq)%>%
-  select(dv, -task, eta_sq, icc, sem, spearman)
-```
-
 #### Effect of time
@@
 time_effect_vars$value = gsub("\"", "", time_effect_vars$value)
-time_effect_vars
+datatable(time_effect_vars)
 ```
@@
 
-#### Rank order of SEMs
-
-###### For tasks
-
-```{r}
-icc_df %>%
-  filter(task == 'task') %>%
-  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
-  arrange(-sem) %>%
-  select(dv, -task,  sem, eta_sq, icc, spearman)
-```
-
-###### For surveys
-
-```{r}
-icc_df %>%
-  filter(task == 'survey') %>%
-  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
-  arrange(-sem)%>%
-  select(dv, -task,  sem, eta_sq, icc, spearman)
-```
-
 ### Negative icc's?
@@
 ```{r}
-icc_df %>%
+datatable(icc_df %>%
   filter(icc>(-0.1), icc<0.1) %>%
-  arrange(icc)
+  arrange(icc))
 ```
@@
 
-tmp
+datatable(tmp)
 ```
@@
 ```{r warning=FALSE, message=FALSE}
-measure_labels %>%
+datatable(measure_labels %>%
   mutate(dv = as.character(dv)) %>%
@@
             num_measures = n()) %>%
-  arrange(-mean_icc, -mean_spearman)
+  arrange(-mean_icc, -mean_spearman))
 ```
@@
 ```{r warning=FALSE, message=FALSE}
-tmp %>%
+datatable(tmp %>%
   group_by(label_1,label_2, label_3) %>%
@@
             n_vars = n()) %>%
-  arrange(-mean_icc, -mean_spearman)
-```
-
-This is what the distributions of look like
+  arrange(-mean_icc, -mean_spearman))
+```
+
+This is what the distributions of look like. Note that there is one box in the difference columns for HDDM because this model only allows this to be different across conditions.
 
@@
 
-```{r}
+```{r eval=FALSE, echo=FALSE}
 sample_workers = function(N = 150, repl= TRUE, df=retest_data, worker_col = "sub_id"){

### 2017-04-22 SRO_Report.Rmd
began refactoring code to make bootstrapping more efficient and report shorter and more compact

@@
 
-## Correlations for all cleaned meaningful variables
-Spearman only
+## Reliability metrics 
+For correlations we report Spearman's $\rho$'s only.  
+Based on [Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) ICC(3,k) does not take in to account within subject differences between two time points (i.e.
+the fixed effect of time/systematic error).
+Thus, it is well approximated by Pearson's r and subject to similar criticisms.
+[Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) suggests reporting at least this systematic error effect size if one chooses to report with ICC(3,k).
+Based on his conclusions here I report:
+- ICC(3,k): As Dave clarified this ranges from 1 to -1/(number of repeated measures -1) so in our case this range would be [-1, 1]; larger values would mean that the two scores of a subject for a given measure are more similar to each other than they are to scores of other people
+- partial $\eta^2$ for time ($SS_{time}/SS_{within}$): effect size of time   
+- SEM ($\sqrt(MS_{error})$): standard error of measurement; the smaller the better
 
@@
 
+match_t1_t2 <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', format = "long", sample = 'full', sample_vec){
+
+  if(sample == 'full'){
+   df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var) 
+  }
+  else{
+    df = merge(t1_df[t1_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)], t2_df[t2_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)],
+    by=merge_var)
+  }
+
+  df = df %>% 
+    na.omit()%>%
+    gather(dv, score, -sub_id) %>%
+    mutate(time = ifelse(grepl('\\.x', dv), 1, ifelse(grepl('\\.y', dv), 2, NA))) %>%
+    separate(dv, c("dv", "drop"), sep='\\.([^.]*)$') %>%
+    select(-drop)
+
+  if(format == 'wide'){
+    df = df%>% spread(time, score) 
+  }
+
+  return(df)
+}
+
+get_spearman = function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+
+  if(sample=='full'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
+  }
+  else if(sample=='bootstrap'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
+  }
+
+  rho = cor(df$`1`, df$`2`, method='spearman')
+
+  return(rho)
+}
+
+get_icc <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+  if(sample=='full'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
+  }
+  else if(sample=='bootstrap'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
+  }
+
+  df = df %>% select(-dv, -sub_id)
+  icc = ICC(df)
+  icc_3k = icc$results['Average_fixed_raters', 'ICC']
+  return(icc_3k)
+  }
+
+get_eta <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+  if(sample=='full'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
+  }
+  else if(sample=='bootstrap'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, sample='bootstrap', sample_vec = sample_vec)
+  }
+
+  mod = summary(aov(score~Error(sub_id)+time, df))
+  ss_time = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq1',]
+  ss_error = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq2',]
+  eta = ss_time/(ss_time+ss_error)
+  return(eta)
+  }
+
+get_sem <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+  if(sample=='full'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
+  }
+  else if(sample=='bootstrap'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, sample='bootstrap', sample_vec = sample_vec)
+  }
+  mod = summary(aov(score~Error(sub_id)+time, df))
+  ms_error = as.data.frame(unlist(mod$`Error: Within`))['Mean Sq2',]
+  sem = sqrt(ms_error)
+  return(sem)
+}
+```
+
+```{r}
 cor_df <- data.frame(spearman = rep(NA, length(numeric_cols)))
@@
 for(i in 1:length(numeric_cols)){
-  cor_df[numeric_cols[i], 'spearman'] <- cor(retest_data[,numeric_cols[i]],retest_subs_test_data[,numeric_cols[i]], method = 'spearman', use = "pairwise.complete.obs")
-}
+  cor_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i]) 
+}
+
+#Calculate ICC df
+icc_df <- data.frame(icc = rep(NA, length(numeric_cols)), 
+                     eta_sq = rep(NA, length(numeric_cols)),
+                     sem = rep(NA, length(numeric_cols)))
+
+row.names(icc_df) <- numeric_cols
+
+for(i in 1:length(numeric_cols)){
+  icc_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
+  icc_df[numeric_cols[i], 'eta_sq'] <- get_eta(numeric_cols[i])
+  icc_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
+}
+
+icc_df$dv = row.names(icc_df)
+row.names(icc_df) = seq(1:nrow(icc_df))
+icc_df$task = 'task'
+icc_df[grep('survey', icc_df$dv), 'task'] = 'survey'
+icc_df = icc_df %>%
+  select(dv, task, icc, eta_sq, sem)
+row.names(icc_df) = NULL
 
@@
 
-Mean Spearman correlation and the number of variables for both the surveys and the tasks
-```{r}
-datatable(cor_df %>%
+Average reliability metrics and the number of variables for both the surveys and the tasks
+Both Spearman $\rho$'s as well the ICC's are higher for surveys.  
+Systematic differences between the two measurements ($\eta^2$) are higher for tasks than surveys (potentially indicating learning effects?).  
+Unexpectedly, median standard error of measurement is higher for surveys but the distribution below suggests that this is a side effect of having too many task measures with very low SEMs.
+```{r}
+datatable(rel_df %>%
   group_by(task) %>%
-  summarise(mean_spearman = mean(spearman),
+  summarise(median_spearman = median(spearman),
+            median_icc = median(icc),
+            median_eta_sq = median(eta_sq),
+            median_sem = median(sem),
             num_vars = n()))
@@
 
-### Distributions of correlations by task vs. survey
-
-Spearman correlations for surveys are noticably higher than task reliabilities.
+*Rank orders for tasks*
+
+```{r}
+
+```
+
+*Rank order for surveys:*
+- Demographics are excluded from this list of variables (because they are saved for predictive analyses).  
+- Holt and Laury test-retest is the worst for *surveys*.
+But note that this is not a survey that has been studied extensively psychometrically like others.
+This is more similar to our tasks (one that is used more often by economists).
+In previous data I have worked with retest reliablities for this task was ~.35 so the results here are in line with this.
+- Otherwise the lowest survey reliabilities are 0.5.
+```{r}
+
+```
+
+### Histograms of reliability metrics
 
@@
 ```
+
+#### Spearman
 
@@
 
-#### Rank order of correlations
-
-##### For tasks
-```{r}
-datatable(cor_df %>%
-  filter(task == 'task') %>%
-  select(dv, spearman) %>%
-  arrange(-spearman))
-```
-
-##### For surveys
-
-- Demographics are excluded from this list of variables (because they are saved for predictive analyses).  
-- Holt and Laury test-retest is the worst for *surveys*.
-But note that this is not a survey that has been studied extensively psychometrically like others.
-This is more similar to our tasks (one that is used more often by economists).
-In previous data I have worked with retest reliablities for this task was ~.35 so the results here are in line with this.
-- Otherwise the lowest survey reliabilities are 0.5.
-```{r}
-datatable(cor_df %>%
-  filter(task == 'survey') %>%
-  select(dv, spearman) %>%
-  arrange(-spearman))
-```
-
-## ICC for all cleaned meaningful variables
-
-Based on [Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) ICC(3,k) does not take in to account within subject differences between two time points (i.e.
-the fixed effect of time/systematic error).
-Thus, it is well approximated by Pearson's r and subject to similar criticisms.
-[Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) suggests reporting at least this systematic error effect size if one chooses to report with ICC(3,k).
-Based on his conclusions here I report:
-- ICC(3,k): As Dave clarified this ranges from 1 to -1/(number of repeated measures -1) so in our case this range would be [-1, 1]; larger values would mean that the two scores of a subject for a given measure are more similar to each other than they are to scores of other people
-- partial $\eta^2$ for time ($SS_{time}/SS_{within}$): effect size of time   
-- SEM ($\sqrt(MS_{error})$): standard error of measurement; the smaller the better
-
-```{r}
-match_t1_t2 <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', format = "long"){
-  df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var)
-
-  df = df %>% 
-    na.omit()%>%
-    gather(dv, score, -sub_id) %>%
-    mutate(time = ifelse(grepl('\\.x', dv), 1, ifelse(grepl('\\.y', dv), 2, NA))) %>%
-    separate(dv, c("dv", "drop"), sep='\\.([^.]*)$') %>%
-    select(-drop)
-
-  if(format == 'wide'){
-    df = df%>% spread(time, score) 
-  }
-
-  return(df)
-}
-
-get_icc <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', match=TRUE, matched_df){
-  if(match==TRUE){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
-  }
-  else{
-    df = matched_df
-  }
-  df = df %>% select(-dv, -sub_id)
-  icc = ICC(df)
-  icc_3k = icc$results['Average_fixed_raters', 'ICC']
-  return(icc_3k)
-  }
-
-get_eta <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', match=TRUE, matched_df){
-  if(match==TRUE){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
-  }
-  else{
-    df = matched_df
-  }
-  mod = summary(aov(score~Error(sub_id)+time, df))
-  ss_time = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq1',]
-  ss_error = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq2',]
-  eta = ss_time/(ss_time+ss_error)
-  return(eta)
-  }
-
-get_sem <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', match=TRUE, matched_df){
-  if(match==TRUE){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
-  }
-  else{
-    df = matched_df
-  }
-  mod = summary(aov(score~Error(sub_id)+time, df))
-  ms_error = as.data.frame(unlist(mod$`Error: Within`))['Mean Sq2',]
-  sem = sqrt(ms_error)
-  return(sem)
-}
-```
-
-```{r}
-#Calculate ICC df
-icc_df <- data.frame(icc = rep(NA, length(numeric_cols)), 
-                     eta_sq = rep(NA, length(numeric_cols)),
-                     sem = rep(NA, length(numeric_cols)))
-
-row.names(icc_df) <- numeric_cols
-
-for(i in 1:length(numeric_cols)){
-  icc_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
-  icc_df[numeric_cols[i], 'eta_sq'] <- get_eta(numeric_cols[i])
-  icc_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
-}
-
-icc_df$dv = row.names(icc_df)
-row.names(icc_df) = seq(1:nrow(icc_df))
-icc_df$task = 'task'
-icc_df[grep('survey', icc_df$dv), 'task'] = 'survey'
-icc_df = icc_df %>%
-  select(dv, task, icc, eta_sq, sem)
-row.names(icc_df) = NULL
-```
-
-Median reliability and the number of variables for both the surveys and the tasks:
-As seen with Spearman $\rho$'s as well the ICC's are higher for surveys.  
-Systematic differences between the two measurements ($\eta^2$) are higher for tasks than surveys (potentially indicating learning effects?).  
-Unexpectedly, median standard error of measurement is higher for surveys but the distribution below suggests that this is a side effect of having too many task measures with very low SEMs.
-```{r}
-datatable(icc_df %>%
-  group_by(task) %>%
-  summarise(median_icc = median(icc),
-            median_eta_sq = median(eta_sq),
-            median_sem = median(sem),
-            num_vars = n()))
-```
-
-#### Rank order of ICCs, partial $\eta^2$ and SEM
-
-Note that these tables can be sorted for any of the columns.
-
-###### For tasks
-
-```{r}
-datatable(icc_df %>%
-  filter(task == 'task') %>%
-  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
-  arrange(-icc) %>%
-  select(dv, -task, icc, eta_sq, sem, spearman))
-```
-
-###### For surveys
-
-```{r}
-datatable(icc_df %>%
-  filter(task == 'survey') %>%
-  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
-  arrange(-icc) %>%
-  select(dv, -task, icc, eta_sq, sem, spearman))
-```
-
-### Distributions of ICC's by task vs. survey
+### ICC
 
@@
 
-### Distributions of partial $\eta^2$ by task vs. survey
+### Partial $\eta^2$
 
@@
 
-### Distributions of SEM's by task vs. survey
+### SEM
 
@@
 
-extract_sample_data = function(sample, var_name, df, worker_col = "sub_id"){
-  return(df[df[,worker_col] %in% sample, var_name])
+bootstrap_relialibility = function(metric = c('icc', 'spearman', 'eta_sq', 'sem'), dv_var){
+  tmp_sample = sample_workers()
+  get_icc(dv_var, sample = 'bootstrap', sample_vec = tmp_sample, format='wide')
+  get_spearman(dv_var, sample = 'bootstrap', sample_vec = tmp_sample, format='wide')
+  get_eta(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
+  get_sem(dv_var, sample = 'bootstrap', sample_vec = tmp_sample, format='wide')
 }
@@
 sample_workers()
-extract_sample_data(df=retest_data)
-extract_sample_data(df=retest_subs_test_data)
-```
+
+```

### 2017-04-23 SRO_Report.Rmd
mostly cleaned up refactoring calculation of reliability df

@@
 ```{r}
-cor_df <- data.frame(spearman = rep(NA, length(numeric_cols)))
-
-row.names(cor_df) <- numeric_cols
-
-for(i in 1:length(numeric_cols)){
-  cor_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i]) 
-}
-
-#Calculate ICC df
-icc_df <- data.frame(icc = rep(NA, length(numeric_cols)), 
+rel_df <- data.frame(spearman = rep(NA, length(numeric_cols)),
+                     icc = rep(NA, length(numeric_cols)), 
                      eta_sq = rep(NA, length(numeric_cols)),
@@
 
-row.names(icc_df) <- numeric_cols
+row.names(rel_df) <- numeric_cols
 
 for(i in 1:length(numeric_cols)){
-  icc_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
-  icc_df[numeric_cols[i], 'eta_sq'] <- get_eta(numeric_cols[i])
-  icc_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
-}
-
-icc_df$dv = row.names(icc_df)
-row.names(icc_df) = seq(1:nrow(icc_df))
-icc_df$task = 'task'
-icc_df[grep('survey', icc_df$dv), 'task'] = 'survey'
-icc_df = icc_df %>%
-  select(dv, task, icc, eta_sq, sem)
-row.names(icc_df) = NULL
-
-# Add column to tasks vs. surveys in correlation table
-cor_df$dv = row.names(cor_df)
-row.names(cor_df) = seq(1:nrow(cor_df))
-cor_df$task = 'task'
-cor_df[grep('survey', cor_df$dv), 'task'] = 'survey'
+  rel_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i]) 
+  rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
+  rel_df[numeric_cols[i], 'eta_sq'] <- get_eta(numeric_cols[i])
+  rel_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
+}
+
+rel_df$dv = row.names(rel_df)
+row.names(rel_df) = seq(1:nrow(rel_df))
+rel_df$task = 'task'
+rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
+rel_df = rel_df %>%
+  select(dv, task, spearman, icc, eta_sq, sem)
+# row.names(rel_df) = NULL
+
 ```
@@
 Unexpectedly, median standard error of measurement is higher for surveys but the distribution below suggests that this is a side effect of having too many task measures with very low SEMs.
-```{r}
-datatable(rel_df %>%
+```{r warning=FALSE, message=FALSE}
+rel_df %>%
   group_by(task) %>%
@@
             median_sem = median(sem),
-            num_vars = n()))
-```
-
-*Rank orders for tasks*
-
-```{r}
-
-```
-
-*Rank order for surveys:*
+            num_vars = n())
+```
+
+*Rank orders for reliabilities*
+
+**ADD FILTER TO DATA TABLE FOR THIS DISPLAY INSTEAD OF MAKING TWO SEPARATE TABLES**
+
 - Demographics are excluded from this list of variables (because they are saved for predictive analyses).  
@@
 - Otherwise the lowest survey reliabilities are 0.5.
+
 ```{r}
@@
     for(j in 1:nrow(plot_df)){
-      if(ref_df[i, bin_col] <= plot_df$xmax[j] & ref_df[i, bin_col]>=plot_df$xmin[j] & all(ref_df[i, group_col] == plot_df[j, group_col])){
+      # if(ref_df[i, bin_col] <= plot_df$xmax[j] & ref_df[i, bin_col]>=plot_df$xmin[j] & all(ref_df[i, group_col] == plot_df[j, group_col])){
+      if(ref_df[i, bin_col] <= plot_df$xmax[j] & ref_df[i, bin_col]>=plot_df$xmin[j] & ref_df[i, group_col] == plot_df[j, group_col]){
         ref_df$bin[i] <- plot_df$bin[j]
@@
 ```{r warning=FALSE, message=FALSE}
-ggplotly(ggplot_build(cor_df %>%
+ggplotly(ggplot_build(rel_df %>%
                         ggplot(aes(spearman, fill=task)) +
@@
            mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
-           get_labels(.,cor_df, "spearman", "task") %>%
+           get_labels(.,rel_df, "spearman", "task") %>%
            prettify_label(.) %>%
@@
 ```{r warning=FALSE, message=FALSE}
-ggplotly(ggplot_build(icc_df %>%
+ggplotly(ggplot_build(rel_df %>%
                         ggplot(aes(icc, fill=task)) +
@@
            mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
-           get_labels(.,icc_df, "icc", "task") %>%
+           get_labels(.,rel_df, "icc", "task") %>%
            prettify_label(.) %>%
@@
 ```{r warning=FALSE, message=FALSE}
-ggplotly(ggplot_build(icc_df %>%
+ggplotly(ggplot_build(rel_df %>%
                         ggplot(aes(eta_sq, fill=task)) +
@@
            mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
-           get_labels(.,icc_df, "eta_sq", "task") %>%
+           get_labels(.,rel_df, "eta_sq", "task") %>%
            prettify_label(.) %>%
@@
 ```{r warning=FALSE, message=FALSE}
-time_effect_vars = ggplot_build(icc_df %>%
+time_effect_vars = ggplot_build(rel_df %>%
                ggplot(aes(eta_sq, fill=task)) +
@@
   mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
-  get_labels(.,icc_df, "eta_sq", "task") %>%
+  get_labels(.,rel_df, "eta_sq", "task") %>%
   prettify_label(.) %>%
@@
 ```{r warning=FALSE, message=FALSE}
-ggplotly(ggplot_build(icc_df %>%
+ggplotly(ggplot_build(rel_df %>%
                         ggplot(aes(sem, fill=task)) +
@@
            mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
-           get_labels(.,icc_df, "sem", "task") %>%
+           get_labels(.,rel_df, "sem", "task") %>%
            prettify_label(.) %>%
@@
 ```{r}
-neg_icc_vars = icc_df %>%
+neg_icc_vars = rel_df %>%
   arrange(icc) %>% 
@@
 ```{r fig.height=12, fig.width=12}
-high_icc_vars = icc_df %>%
+high_icc_vars = rel_df %>%
   arrange(-icc)  %>% 
@@
 ```{r}
-ggplotly(icc_df %>%
-           left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
+ggplotly(rel_df %>%
            ggplot(aes(spearman, icc, col=task, label=dv, label2=eta_sq))+
@@
 ```{r}
-datatable(icc_df %>%
+datatable(rel_df %>%
   filter(icc>(-0.1), icc<0.1) %>%
@@
 ```{r}
-ggplotly(icc_df %>%
+ggplotly(rel_df %>%
   ggplot(aes(eta_sq, icc, col=task, label=dv))+
@@
   select(-measure_description, -notes, -measure_type, -task, -ddm_task) %>%
-  left_join(icc_df[,c("dv", "icc")], by='dv') %>%
-  left_join(cor_df[,c("dv", "spearman")], by='dv') %>%
+  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
   separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
@@
   group_by(task_name) %>%
-  summarise(mean_icc = mean(icc),
-            mean_spearman = mean(spearman),
+  summarise(median_icc = median(icc),
+            median_spearman = median(spearman),
             num_measures = n(),
             num_trials = unique(num_all_trials)) %>%
-  arrange(-mean_icc, -mean_spearman)
+  arrange(-median_icc, -median_spearman)
 
@@
 ```{r warning=FALSE, message=FALSE}
-summary(lm(mean_icc ~ num_trials, data = tmp))
+summary(lm(median_icc ~ num_trials, data = tmp))
 ```
@@
 ```{r warning=FALSE, message=FALSE}
-summary(lm(mean_spearman ~ num_trials, data = tmp))
+summary(lm(median_spearman ~ num_trials, data = tmp))
 ```
@@
 ```{r warning=FALSE, message=FALSE}
-summary(lm(mean_icc ~ num_measures, data = tmp))
+summary(lm(median_icc ~ num_measures, data = tmp))
 ```
@@
 ```{r warning=FALSE, message=FALSE}
-summary(lm(mean_spearman ~ num_measures, data = tmp))
+summary(lm(median_spearman ~ num_measures, data = tmp))
 ```
@@
   select(-measure_description, -notes, -variable_type, -task, -ddm_task) %>%
-  left_join(icc_df[,c("dv", "icc")], by='dv') %>%
-  left_join(cor_df[,c("dv", "spearman")], by='dv') %>%
+  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
   group_by(measure_type) %>%
-  summarise(mean_icc = mean(icc),
-            mean_spearman = mean(spearman),
+  summarise(median_icc = median(icc),
+            median_spearman = median(spearman),
             num_measures = n()) %>%
-  arrange(-mean_icc, -mean_spearman))
+  arrange(-median_icc, -median_spearman))
 ```
@@
   select(-measure_description, -notes, -variable_type, -task, -ddm_task) %>%
-  left_join(icc_df[,c("dv", "icc")], by='dv') %>%
-  left_join(cor_df[,c("dv", "spearman")], by='dv') %>%
+  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
   select(measure_type, icc, spearman) %>%
@@
   select(-measure_description, -notes, -measure_type, -task) %>%
-  left_join(icc_df[,c("dv", "icc")], by='dv') %>%
-  left_join(cor_df[,c("dv", "spearman")], by='dv') %>%
+  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
   separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
@@
   group_by(label_1,label_2, label_3) %>%
-  summarise(mean_icc = mean(icc),
-            mean_spearman = mean(spearman),
+  summarise(median_icc = median(icc),
+            median_spearman = median(spearman),
             n_vars = n()) %>%
-  arrange(-mean_icc, -mean_spearman))
+  arrange(-median_icc, -median_spearman))
 ```

### 2017-04-23 SRO_Report.Rmd
got bootstrapping function working

@@
 
+```{r echo=FALSE}
+rm(tmp)
+```
+
 <a id="diff_plot"></a>
@@
   tmp_sample = sample_workers()
-  get_icc(dv_var, sample = 'bootstrap', sample_vec = tmp_sample, format='wide')
-  get_spearman(dv_var, sample = 'bootstrap', sample_vec = tmp_sample, format='wide')
-  get_eta(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
-  get_sem(dv_var, sample = 'bootstrap', sample_vec = tmp_sample, format='wide')
-}
-
-sample_workers()
-
-```
+  out_df = data.frame(dv = dv_var)
+  out_df$icc = get_icc(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
+  out_df$spearman = get_spearman(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
+  out_df$eta_sq = get_eta(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
+  out_df$sem = get_sem(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
+  return(out_df)
+}
+
+bootstrap_relialibility(dv_var = numeric_cols[1])
+
+```

### 2017-04-23 SRO_Report.Rmd
added table with filtering
improved bootstrapping function to output specific metrics

@@
 
-**ADD FILTER TO DATA TABLE FOR THIS DISPLAY INSTEAD OF MAKING TWO SEPARATE TABLES**
-
+- Note that this table can be sorted by different metrics, filtered for specific values for each column and is searchable.  
 - Demographics are excluded from this list of variables (because they are saved for predictive analyses).  
@@
 ```{r}
-
+datatable(rel_df, filter = 'top')
 ```
@@
   out_df = data.frame(dv = dv_var)
+  if('icc' %in% metric){
     out_df$icc = get_icc(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
+  }
+  if('spearman' %in% metric){
     out_df$spearman = get_spearman(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
+  }
+  if('eta_sq' %in% metric){
     out_df$eta_sq = get_eta(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
+  }
+  if('sem' %in% metric){
     out_df$sem = get_sem(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
+  }
   return(out_df)

### 2017-04-23 SRO_Report.Rmd
got bootstrapping to work locally

@@
 
-bootstrap_relialibility(dv_var = numeric_cols[1])
-
-```
+as.data.frame(numeric_cols) %>%
+  mutate(index = 1:n()) %>%
+  group_by(index) %>%
+  # rowwise()%>% #this works too but the output is nicer the other way
+  do(plyr::rdply(2, bootstrap_relialibility(dv_var = as.character(.$numeric_cols), metric = c("icc", "spearman"))))
+
+```

### 2017-04-23 SRO_Report.Rmd
added quick script for bootstrapping for sherlock

--- 2017-04-23 SRO_Report.Rmd
@@
 
-```{r eval=FALSE, echo=FALSE}
+```{r}
 sample_workers = function(N = 150, repl= TRUE, df=retest_data, worker_col = "sub_id"){
@@
 }
-
-bootstrap_relialibility(dv_var = numeric_cols[1])
-
-```
+```
+
+Bootstrapping everything at once locally would take around four hours.
+```{r eval=FALSE}
+as.data.frame(numeric_cols) %>%
+  mutate(index = 1:n()) %>%
+  group_by(index) %>%
+  # rowwise()%>% #this works too but the output is nicer the other way
+  do(plyr::rdply(2, bootstrap_relialibility(dv_var = as.character(.$numeric_cols), metric = c("icc", "spearman"))))
+
+```

### 2017-04-25 SRO_Report.Rmd
fixed coding error in positive transformations

@@
 render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Report', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
+options(digits = 4)
 ```
@@
   # positive_subset = log(positive_subset)
-  positive_subset = pos_log(positive_subset) #slight divergence from original code
+  # positive_subset = pos_log(positive_subset) #slight divergence from original code
+  positive_subset = as.data.frame(apply(positive_subset, 2, pos_log))
   successful_transforms = as.data.frame(apply(positive_subset, 2, skew))
@@
 
-#### Spearman
+### Spearman
 
@@
 
-Does number of measures that went in to this reliability estimate have a significant effect on the average ICC of (mostly) raw measures for all trials from a task? No.
+Does number of measures that went in to this reliability estimate have a significant effect on the average ICC of (mostly) raw measures for all trials from a task?
+It seems the more measures that goes in to summarizing overall reliability for a task the worse it gets.
+This would make sense if these variables are intended to measure different things and some are less reliable than others.
 
@@
 Does number of measures that went in to this reliability estimate have a significant effect on the average ICC of (mostly) raw measures for all trials from a task?  
-The regression suggests that the more measures that went in to the averaging of Spearman's $\rho$'s the lower the mean Spearman $\rho$ for that task.
-This might suggest that this way of summarizing data might not be a good idea in general or at least that we shouldn't do it for the Spearman correlations.
+The same is true for Spearman's correlations as well.
 
@@
 
+## Transformation effects
+
+```{r}
+raw_retest_subs_test_data = raw_test_data[raw_test_data$sub_id %in% raw_retest_data$sub_id,]
+
+raw_numeric_cols = c()
+
+for(i in 1:length(names(raw_test_data))){
+  if(is.numeric(raw_test_data[,i])){
+    raw_numeric_cols <- c(raw_numeric_cols, names(raw_test_data)[i])
+  }
+}
+
+raw_rel_df <- data.frame(spearman = rep(NA, length(raw_numeric_cols)),
+                     icc = rep(NA, length(raw_numeric_cols)), 
+                     eta_sq = rep(NA, length(raw_numeric_cols)),
+                     sem = rep(NA, length(raw_numeric_cols)))
+
+row.names(raw_rel_df) <- raw_numeric_cols
+
+for(i in 1:length(raw_numeric_cols)){
+  raw_rel_df[raw_numeric_cols[i], 'spearman'] <- get_spearman(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data) 
+  raw_rel_df[raw_numeric_cols[i], 'icc'] <- get_icc(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data)
+  raw_rel_df[raw_numeric_cols[i], 'eta_sq'] <- get_eta(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data)
+  raw_rel_df[raw_numeric_cols[i], 'sem'] <- get_sem(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data)
+}
+
+raw_rel_df$dv = row.names(raw_rel_df)
+row.names(raw_rel_df) = seq(1:nrow(raw_rel_df))
+raw_rel_df$task = 'task'
+raw_rel_df[grep('survey', raw_rel_df$dv), 'task'] = 'survey'
+raw_rel_df = raw_rel_df %>%
+  select(dv, task, spearman, icc, eta_sq, sem)
+```
+
+```{r warning=FALSE, message=FALSE}
+raw_rel_df %>%
+  group_by(task) %>%
+  summarise(median_spearman = median(spearman),
+            median_icc = median(icc),
+            median_eta_sq = median(eta_sq),
+            median_sem = median(sem),
+            num_vars = n())
+```
+
+Plots of change in reliability depending on transformation
+
+```{r}
+ggplotly(rel_df %>%
+  mutate(dv = gsub(".logTr", "", dv)) %>%
+  mutate(dv = gsub(".Re", "", dv)) %>%
+  left_join(raw_rel_df, by = 'dv') %>%
+  ggplot(aes(spearman.x, spearman.y, color = task.x, label=dv))+
+  geom_point()+
+  geom_abline(intercept = 0, slope=1)+
+  theme_bw()+
+  theme(legend.title = element_blank())+
+  xlab("Spearman at t1")+
+  ylab("Spearman at t2"))
+```
+
+```{r}
+ggplotly(rel_df %>%
+  mutate(dv = gsub(".logTr", "", dv)) %>%
+  mutate(dv = gsub(".Re", "", dv)) %>%
+  left_join(raw_rel_df, by = 'dv') %>%
+  ggplot(aes(icc.x, icc.y, color = task.x, label=dv))+
+  geom_point()+
+  geom_abline(intercept = 0, slope=1)+
+  theme_bw()+
+  theme(legend.title = element_blank())+
+  xlab("ICC at t1")+
+  ylab("ICC at t2"))
+```
+
+------------------------------------------------------------------------
 Bootstrapping
 
-```{r}
+```{r eval=FALSE}
 sample_workers = function(N = 150, repl= TRUE, df=retest_data, worker_col = "sub_id"){
@@
 
-Bootstrapping everything at once locally would take around four hours.
+Bootstrapping everything at once in this way locally would take around four hours.
 ```{r eval=FALSE}

### 2017-04-25 SRO_Report.Rmd
fixed decimals

@@
 render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Report', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
-options(digits = 4)
+options(scipen = 1, digits = 4)
 ```
@@
             median_sem = median(sem),
-            num_vars = n())
+            num_vars = n()) %>%
+  datatable() %>%
+  formatRound(columns=c('median_spearman', 'median_icc', 'median_eta_sq', 'median_sem'), digits=3)
 ```
@@
 ```{r}
-datatable(rel_df, filter = 'top')
+rel_df %>%
+  datatable(filter='top') %>%
+  formatRound(columns=c('spearman', 'icc', 'eta_sq', 'sem'), digits=3)
 ```
@@
 ```{r}
-datatable(rel_df %>%
+rel_df %>%
   filter(icc>(-0.1), icc<0.1) %>%
-  arrange(icc))
+  arrange(icc) %>%
+  datatable() %>%
+  formatRound(columns=c('spearman', 'icc', 'eta_sq', 'sem'), digits=3)
 ```
@@
 
-datatable(tmp)
+tmp %>%
+  datatable() %>%
+  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
 ```
@@
 ```{r warning=FALSE, message=FALSE}
-datatable(measure_labels %>%
+measure_labels %>%
   mutate(dv = as.character(dv)) %>%
@@
             num_measures = n()) %>%
-  arrange(-median_icc, -median_spearman))
+  arrange(-median_icc, -median_spearman) %>%
+  datatable() %>%
+  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
 ```
@@
 ```{r warning=FALSE, message=FALSE}
-datatable(tmp %>%
+tmp %>%
   group_by(label_1,label_2, label_3) %>%
@@
             n_vars = n()) %>%
-  arrange(-median_icc, -median_spearman))
+  arrange(-median_icc, -median_spearman) %>%
+  datatable() %>%
+  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
 ```

### 2017-04-28 SRO_Report.Rmd
changed gitignore to not add bootstrapped results

@@
 ```{r eval=FALSE}
-as.data.frame(numeric_cols) %>%
+non_hddm_numeric_cols=numeric_cols[-grep("hddm", numeric_cols)]
+
+boot_df = as.data.frame(non_hddm_numeric_cols) %>%
   mutate(index = 1:n()) %>%
   group_by(index) %>%
-  # rowwise()%>% #this works too but the output is nicer the other way
-  do(plyr::rdply(2, bootstrap_relialibility(dv_var = as.character(.$numeric_cols), metric = c("icc", "spearman"))))
-
-```
+  do(plyr::rdply(10, bootstrap_relialibility(dv_var = as.character(.$non_hddm_numeric_cols))))
+
+boot_df
+```

### 2017-04-28 SRO_Report.Rmd
added bootstrapped results

@@
   theme(legend.title = element_blank())+
-  xlab("Spearman at t1")+
-  ylab("Spearman at t2"))
+  xlab("Spearman with transformation")+
+  ylab("Spearman witouth transformation"))
 ```
@@
   theme(legend.title = element_blank())+
-  xlab("ICC at t1")+
-  ylab("ICC at t2"))
-```
-
-------------------------------------------------------------------------
-Bootstrapping
-
-```{r eval=FALSE}
+  xlab("ICC with transformation")+
+  ylab("ICC without transformation"))
+```
+
+## Bootstrapping
+
+```{r eval=FALSE, echo=FALSE}
 sample_workers = function(N = 150, repl= TRUE, df=retest_data, worker_col = "sub_id"){
@@
 }
-```
-
-Bootstrapping everything at once in this way locally would take around four hours.
-```{r eval=FALSE}
+
+# Bootstrapping everything at once in this way locally would take around four hours.
 non_hddm_numeric_cols=numeric_cols[-grep("hddm", numeric_cols)]
@@
 ```
+
+Summarized bootstrapped reliabilities
+
+```{r}
+boot_df <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/bootstrap_merged.csv')
+
+boot_df = boot_df %>%
+  drop_na() %>%
+  mutate(icc = as.numeric(as.character(icc)),
+         spearman = as.numeric(as.character(spearman)),
+         eta_sq = as.numeric(as.character(eta_sq)),
+         sem = as.numeric(as.character(sem)))
+
+boot_df %>%
+  group_by(dv) %>%
+  summarise(icc_median = quantile(icc, probs = 0.5),
+            icc_2.5 = quantile(icc, probs = 0.025),
+            icc_97.5 = quantile(icc, probs = 0.975),
+            spearman_median = quantile(spearman, probs = 0.5),
+            spearman_2.5 = quantile(spearman, probs = 0.025),
+            spearman_97.5 = quantile(spearman, probs = 0.975)) %>%
+  datatable() %>%
+  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
+```
+
+```{r fig.height=36}
+ boot_df %>%
+  mutate(task = ifelse(grepl("survey",dv), "survey","task")) %>%
+  ggplot(aes(reorder(dv, icc, FUN=var), icc, fill = task))+
+  geom_boxplot()+
+  geom_point(data = rel_df, aes(x=dv, y = icc, color = "yellow"))+
+  theme_bw()+
+  coord_flip()
+```

### 2017-04-28 SRO_Report.Rmd
fixed bootstrap plot colors

@@
   geom_boxplot()+
-  geom_point(data = rel_df, aes(x=dv, y = icc, color = "yellow"))+
+  geom_point(data = rel_df, aes(x=dv, y = icc),  color = "yellow")+
   theme_bw()+
+  theme(legend.title = element_blank())+
   coord_flip()

### 2017-05-02 DDM_Report.Rmd
began ddm report

---
title: 'Closer look at DDM parameter estimates'
output:
github_document:
toc: yes
toc_float: yes
---

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(psych)
library(rmarkdown)
library(psych)
library(stringr)
library(plotly)
library(jsonlite)
library(DT)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
render_this <- function(){rmarkdown::render('DDM_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Report', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
options(scipen = 1, digits = 4)
```

How much do hddm parameters change when fitting to whole vs partial sample

Summary of absolute difference in parameter estimates

```{r}
pre_correction <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/retest_subs_test_data_preddm_correction.csv')
post_correction <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/retest_subs_test_data.csv')

hddm_cols = grep('hddm', names(pre_correction), value =T)

pre_correction = pre_correction[,c("sub_id", hddm_cols)]
post_correction = post_correction[,c("sub_id", hddm_cols)]

pre_correction = pre_correction %>% mutate(pre_post = "pre")
post_correction = post_correction %>% mutate(pre_post = "post")

all_hddm = rbind(pre_correction, post_correction)

all_hddm %>%
  gather(key, value, -sub_id, -pre_post) %>%
  arrange(sub_id) %>%
  spread(pre_post, value) %>%
  mutate(abs_diff = pre-post) %>%
  group_by(key) %>%
  summarise(mean_abs_diff = mean(abs_diff, na.rm=T),
            median_abs_diff = median(abs_diff, na.rm=T),
            min_abs_diff = min(abs_diff, na.rm=T),
            max_abs_diff = max(abs_diff, na.rm=T),
            sd_abs_diff = sd(abs_diff, na.rm=T))
```

How to reliabilities change w sample size (refit from 50 to 150) both for EZ and hddm (gives a prescriptive recommendation on which method to use depending on sample size)

Turn off h of ddm and see if it makes a difference

### 2017-05-02 SRO_Report.Rmd
began ddm report

--- 2017-04-28 SRO_Report.Rmd
@@
 Details of the original sample as well as quality control (qc) procedures are described elsewhere.
-Invited participants were chosen randomly and only subsets of them were invited for a given batch (instead of opening the battery to all qualified subjects) with the intention to avoid a potential oversampling and bias towards high self regulators.
+Invited participants were chosen randomly and only subsets of them were invited for a given batch (instead of opening the battery to all qualified subjects) with the intention to avoid a potential oversampling and bias towards "high self regulators".
 
@@
 
+Distributions of bootstrapped reliabilities.
+Yellow points are where our point estimates fall from the retest sample.
+Surveys are filled in red but can't be seen because the variance around their bootstrapped ICC's is very low.
+
 ```{r fig.height=36}
@@
   geom_boxplot()+
-  geom_point(data = rel_df, aes(x=dv, y = icc, color = "yellow"))+
+  geom_hline(yintercept = 0,color='red',size=1)+
+  geom_point(data = rel_df, aes(x=dv, y = icc),  color = "yellow")+
   theme_bw()+
+  theme(legend.title = element_blank())+
+  xlab("")+
   coord_flip()

### 2017-05-02 DDM_Report.Rmd
added pre post refitting differences

@@
 
-Summary of absolute difference in parameter estimates
+Summary of absolute difference in parameter estimates.
+
+**GO ON SHERLOCK AND CHECK IF YOU INDEED FIT IT TO THE RETEST SAMPLE ONLY**
 
@@
             max_abs_diff = max(abs_diff, na.rm=T),
-            sd_abs_diff = sd(abs_diff, na.rm=T))
+            sem_abs_diff = sem(abs_diff)) %>%
+  ggplot(aes(reorder(key, mean_abs_diff), mean_abs_diff))+
+  geom_point()+
+  geom_errorbar(aes(ymin = mean_abs_diff-sem_abs_diff, ymax = mean_abs_diff+sem_abs_diff), position=position_dodge(0.9), width = 0.25)+
+  theme_bw()+
+  geom_hline(yintercept=0, linetype='dashed', color='red')+
+  ylab("Mean absolute difference after refit")+
+  xlab("")+
+  coord_flip()
 ```
 
-How to reliabilities change w sample size (refit from 50 to 150) both for EZ and hddm (gives a prescriptive recommendation on which method to use depending on sample size)
+Are the variables we see the changes on different due to transformation?
+
+```{r}
+raw_pre_correction <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/raw_retest_subs_test_data_preddm_correction.csv')
+
+replace_hddm_vars = data.frame(grep('hddm', names(raw_pre_correction), value=T, perl=T))
+names(replace_hddm_vars) = c('var')
+
+raw_pre_correction = raw_pre_correction[,c("sub_id", as.character(replace_hddm_vars$var))]
+
+hddm_fix_retest_subs_test_data = raw_pre_correction
+
+raw_hddm_refits <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/hddm_refits_exhaustive.csv')
+
+for(i in 1:length(names(hddm_fix_retest_subs_test_data))){
+  if(names(hddm_fix_retest_subs_test_data)[i] %in% replace_hddm_vars$var){
+    hddm_fix_retest_subs_test_data[,names(hddm_fix_retest_subs_test_data)[i]] <- raw_hddm_refits[,names(hddm_fix_retest_subs_test_data)[i]]
+  }
+}
+
+raw_post_correction <- hddm_fix_retest_subs_test_data
+
+raw_pre_correction = raw_pre_correction %>% mutate(pre_post = "pre")
+raw_post_correction = raw_post_correction %>% mutate(pre_post = "post")
+
+raw_all_hddm = rbind(raw_pre_correction, raw_post_correction)
+
+raw_all_hddm %>%
+  gather(key, value, -sub_id, -pre_post) %>%
+  arrange(sub_id) %>%
+  spread(pre_post, value) %>%
+  mutate(abs_diff = pre-post) %>%
+  group_by(key) %>%
+  summarise(mean_abs_diff = mean(abs_diff, na.rm=T),
+            median_abs_diff = median(abs_diff, na.rm=T),
+            min_abs_diff = min(abs_diff, na.rm=T),
+            max_abs_diff = max(abs_diff, na.rm=T),
+            sem_abs_diff = sem(abs_diff)) %>%
+  ggplot(aes(reorder(key, mean_abs_diff), mean_abs_diff))+
+  geom_point()+
+  geom_errorbar(aes(ymin = mean_abs_diff-sem_abs_diff, ymax = mean_abs_diff+sem_abs_diff), position=position_dodge(0.9), width = 0.25)+
+  theme_bw()+
+  geom_hline(yintercept=0, linetype='dashed', color='red')+
+  ylab("Mean absolute difference after refit")+
+  xlab("")+
+  coord_flip()
+```
+
+How do reliabilities change w sample size (refit from 50 to 150) both for EZ and hddm (gives a prescriptive recommendation on which method to use depending on sample size)
 

### 2017-05-03 DDM_Report.Rmd
continue working on ddm report

@@
 
+```{r}
+raw_retest_data <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/raw_retest_data.csv')
+```
+
+```{r eval=FALSE, echo=FALSE}
+match_t1_t2 <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', format = "long", sample = 'full', sample_vec){
+
+  if(sample == 'full'){
+   df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var) 
+  }
+  else{
+    df = merge(t1_df[t1_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)], t2_df[t2_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)],
+    by=merge_var)
+  }
+
+  df = df %>% 
+    na.omit()%>%
+    gather(dv, score, -sub_id) %>%
+    mutate(time = ifelse(grepl('\\.x', dv), 1, ifelse(grepl('\\.y', dv), 2, NA))) %>%
+    separate(dv, c("dv", "drop"), sep='\\.([^.]*)$') %>%
+    select(-drop)
+
+  if(format == 'wide'){
+    df = df%>% spread(time, score) 
+  }
+
+  return(df)
+}
+
+get_spearman = function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+
+  if(sample=='full'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
+  }
+  else if(sample=='bootstrap'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
+  }
+
+  rho = cor(df$`1`, df$`2`, method='spearman')
+
+  return(rho)
+}
+
+get_icc <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+  if(sample=='full'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
+  }
+  else if(sample=='bootstrap'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
+  }
+
+  df = df %>% select(-dv, -sub_id)
+  icc = ICC(df)
+  icc_3k = icc$results['Average_fixed_raters', 'ICC']
+  return(icc_3k)
+  }
+
+get_eta <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+  if(sample=='full'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
+  }
+  else if(sample=='bootstrap'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, sample='bootstrap', sample_vec = sample_vec)
+  }
+
+  mod = summary(aov(score~Error(sub_id)+time, df))
+  ss_time = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq1',]
+  ss_error = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq2',]
+  eta = ss_time/(ss_time+ss_error)
+  return(eta)
+  }
+
+get_sem <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+  if(sample=='full'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
+  }
+  else if(sample=='bootstrap'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, sample='bootstrap', sample_vec = sample_vec)
+  }
+  mod = summary(aov(score~Error(sub_id)+time, df))
+  ms_error = as.data.frame(unlist(mod$`Error: Within`))['Mean Sq2',]
+  sem = sqrt(ms_error)
+  return(sem)
+}
+
+sample_workers = function(N = 150, repl= TRUE, df=retest_data, worker_col = "sub_id"){
+  return(sample(df[,worker_col], N, replace = repl))
+}
+
+bootstrap_relialibility = function(metric = c('icc', 'spearman', 'eta_sq', 'sem'), dv_var, N=150, t1_df, t2_df){
+  tmp_sample = sample_workers(N, df = t1_df)
+  out_df = data.frame(dv = dv_var)
+  if('icc' %in% metric){
+    out_df$icc = get_icc(dv_var, sample = 'bootstrap', sample_vec = tmp_sample, t1_df = t1_df, t2_df = t2_df)
+  }
+  if('spearman' %in% metric){
+    out_df$spearman = get_spearman(dv_var, sample = 'bootstrap', sample_vec = tmp_sample, t1_df = t1_df, t2_df = t2_df)
+  }
+  if('eta_sq' %in% metric){
+    out_df$eta_sq = get_eta(dv_var, sample = 'bootstrap', sample_vec = tmp_sample, t1_df = t1_df, t2_df = t2_df)
+  }
+  if('sem' %in% metric){
+    out_df$sem = get_sem(dv_var, sample = 'bootstrap', sample_vec = tmp_sample, t1_df = t1_df, t2_df = t2_df)
+  }
+  return(out_df)
+}
+
+rel_n50_rep20 = replace_hddm_vars %>%
+  mutate(index = 1:n()) %>%
+  group_by(index) %>%
+  do(plyr::rdply(20, bootstrap_relialibility(dv_var = as.character(.$var), t1_df = raw_pre_correction, t2_df = raw_retest_data, N=50))) %>%
+  mutate(N = 50)
+
+```
+
 Turn off h of ddm and see if it makes a difference

### 2017-05-03 SRO_Report.Rmd
continue working on ddm report

@@
 
-bootstrap_relialibility = function(metric = c('icc', 'spearman', 'eta_sq', 'sem'), dv_var){
-  tmp_sample = sample_workers()
+bootstrap_relialibility = function(metric = c('icc', 'spearman', 'eta_sq', 'sem'), dv_var, N=150){
+  tmp_sample = sample_workers(N)
   out_df = data.frame(dv = dv_var)

### 2017-05-03 ddm_sample_size.R

@@ -1,0 +1,134 @@
+#!/usr/bin/env Rscript
+args = commandArgs(trailingOnly=TRUE)
+
+#Usage:
+#Rscript --vanilla ddm_sample_size_.R data_dir out_dir rep_time sample_size dv_name
+
+#test if all arguments are supplied
+# test if there is at least one argument: if not, return an error
+if (length(args)<3) {
+  stop("Arguments are missing. Usage: Rscript --vanilla ddm_sample_size.R data_dir out_dir rep_time sample_size dv_name", call.=FALSE)
+} 
+
+data_dir <- args[1] 
+output_dir <- args[2]
+rep_times <- as.numeric(args[3])
+sample_size <- as.numeric(args[4])
+dv_name <- args[5]
+
+#load packages
+library(dplyr)
+library(tidyr)
+library(psych)
+
+raw_pre_correction <- read.csv(paste0(data_dir,'raw_retest_subs_test_data_preddm_correction.csv'))
+
+raw_retest_data <- read.csv(paste0(data_dir,'raw_retest_data.csv'))
+
+match_t1_t2 <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', format = "long", sample = 'full', sample_vec){
+  
+  if(sample == 'full'){
+    df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var) 
+  }
+  else{
+    df = merge(t1_df[t1_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)], t2_df[t2_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)],
+               by=merge_var)
+  }
+  
+  df = df %>% 
+    na.omit()%>%
+    gather(dv, score, -sub_id) %>%
+    mutate(time = ifelse(grepl('\\.x', dv), 1, ifelse(grepl('\\.y', dv), 2, NA))) %>%
+    separate(dv, c("dv", "drop"), sep='\\.([^.]*)$') %>%
+    select(-drop)
+  
+  
+  if(format == 'wide'){
+    df = df%>% spread(time, score) 
+  }
+  
+  return(df)
+}
+
+get_spearman = function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+  
+  if(sample=='full'){
[…]

### 2017-05-04 ddm_sample_size.R
cont working on ddm report

@@ -130,5 +130,9 @@ bootstrap_relialibility = function(metric = c('icc', 'spearman', 'eta_sq', 'sem'
 
 output_df = plyr::rdply(rep_times, bootstrap_relialibility(dv_var = dv_name, t1_df = raw_pre_correction, t2_df = raw_retest_data, N=sample_size))
 
+output_df = output_df %>%
+  mutate(N = sample_size,
+         rep = rep_times)
+
 write.csv(output_df, paste0(output_dir, dv_name, '_rep', rep_times, '_sampleN', sample_size, '_output.csv'))
 

### 2017-06-05 DDM_Report.Rmd
cont working on ddm report
adding uncommitted changes to the ddm report

@@
 Summary of absolute difference in parameter estimates.
-
-**GO ON SHERLOCK AND CHECK IF YOU INDEED FIT IT TO THE RETEST SAMPLE ONLY**
 
@@
 ```{r}
-raw_retest_data <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/raw_retest_data.csv')
+all_ddm_sample_size <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/all_ddm_sample_size_estimates.csv')
+
+all_ddm_sample_size  = all_ddm_sample_size %>%
+  drop_na()
 ```

### 2017-06-05 ddm_sample_size_processing.R

@@ -1,0 +1,41 @@
+#!/usr/bin/env Rscript
+args = commandArgs(trailingOnly=TRUE)
+
+#Usage:
+#Rscript --vanilla ddm_sample_size_processing.R data_dir out_dir
+
+#test if all arguments are supplied
+# test if there is at least one argument: if not, return an error
+if (length(args)<2) {
+  stop("Arguments are missing. Usage: Rscript --vanilla ddm_sample_size_processing.R data_dir out_dir", call.=FALSE)
+} 
+
+data_dir <- args[1] 
+output_dir <- args[2]
+
+#load packages
+library(dplyr)
+library(tidyr)
+library(psych)
+
+all_ddm_sample_size = read.csv(paste0(data_dir, 'all_ddm_sample_size_estimates.csv'))
+
+all_ddm_sample_size = all_ddm_sample_size %>%
+  drop_na()
+
+all_ddm_sample_size_summary = all_ddm_sample_size %>%
+  group_by(dv, N, rep) %>%
+  summarise(icc_median = quantile(icc, probs = 0.5),
+            icc_2.5 = quantile(icc, probs = 0.025),
+            icc_97.5 = quantile(icc, probs = 0.975),
+            spearman_median = quantile(spearman, probs = 0.5),
+            spearman_2.5 = quantile(spearman, probs = 0.025),
+            spearman_97.5 = quantile(spearman, probs = 0.975),
+            eta_median = quantile(spearman, probs = 0.5),
+            eta_2.5 = quantile(spearman, probs = 0.025),
+            eta_97.5 = quantile(spearman, probs = 0.975),
+            sem_median = quantile(spearman, probs = 0.5),
+            sem_2.5 = quantile(spearman, probs = 0.025),
+            sem_97.5 = quantile(spearman, probs = 0.975))
+
+write.csv(all_ddm_sample_size_summary, paste0(output_dir, 'all_ddm_sample_size_summary.csv'), row.names=FALSE)

### 2017-06-05 DDM_Report.Rmd
back to working on ddm sample size reliability questions

--- 2017-05-02 DDM_Report.Rmd
@@
 
-**GO ON SHERLOCK AND CHECK IF YOU INDEED FIT IT TO THE RETEST SAMPLE ONLY**
-
 ```{r}
+#T1 data before replacing hddm variables that are fit to retest subjects only
 pre_correction <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/retest_subs_test_data_preddm_correction.csv')
+#T1 data after replacing hddm variables that are fit to retest subjects only
 post_correction <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/retest_subs_test_data.csv')
@@
 
+#Extract only hddm variable columns
 pre_correction = pre_correction[,c("sub_id", hddm_cols)]
@@
   geom_hline(yintercept=0, linetype='dashed', color='red')+
-  ylab("Mean absolute difference after refit")+
+  ylab("Mean absolute diff after refitting T1 data for T2 subjects")+
   xlab("")+
@@
 
-Are the variables we see the changes on different due to transformation?
+Are the variables we see the changes on differ depending on the sample they were fitted due to transformation?
+Below we are looking at absolute differences of all parameter estimates without any transformations but still comparing whether refitting the HDDM for the T2 participants (instead of all T1 participants) makes a difference.
+
+These are probably the results that we should pay more attention to because comparing transformed variables in the previous graph does not reflect transformations on the same sample.
+The data before the hddm correction are transformed for the full T1 sample and then subsetted to only include the T2 sample whereas the data including the refitted HDDM parameters is transformed using onlyt he T2 sample.
+I could compare data that are transformed on the same sample but it is probably better to look at raw model outputs since we are looking at absolute differences between parameter estimates (instead of doing any statistics with any normality assumptions).
+
+*Conclusion from the graph below:* Overall the refitting does not seem to lead to any difference (except perhaps for specific DPX conditions)
 
 ```{r}
+#T1 data without any transformations fit for all subjects (instead of T2 subjects only)
 raw_pre_correction <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/raw_retest_subs_test_data_preddm_correction.csv')
@@
 
+#All hddm refits of T1 data for T2 subjects without any transformations
 raw_hddm_refits <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/hddm_refits_exhaustive.csv')
 
+#Loop to replace the refitted HDDM parameter values (still without transformations)
 for(i in 1:length(names(hddm_fix_retest_subs_test_data))){
@@
 
+```{r}
+all_ddm_sample_size_summary
+```
+
 Turn off h of ddm and see if it makes a difference

### 2017-06-05 ddm_sample_size_processing.R

@@ -24,6 +24,10 @@ all_ddm_sample_size = all_ddm_sample_size %>%
   drop_na()
 
 all_ddm_sample_size_summary = all_ddm_sample_size %>%
+  mutate(icc = as.numeric(as.character(icc)),
+         spearman = as.numeric(as.character(spearman)),
+         eta_sq = as.numeric(as.character(eta_sq)),
+         sem = as.numeric(as.character(sem))) %>%
   group_by(dv, N, rep) %>%
   summarise(icc_median = quantile(icc, probs = 0.5),
             icc_2.5 = quantile(icc, probs = 0.025),

### 2017-06-06 SRO_Report.Rmd
added stats for neuroecon abstract

@@
 
-This is what the distributions of look like. Note that there is one box in the difference columns for HDDM because this model only allows this to be different across conditions.
-
-```{r warning=FALSE, message=FALSE}
-tmp = tmp %>%
-  select(dv, icc, spearman, label_1, label_2, label_3) %>%
-  gather(key, value, -dv, -label_1, -label_2, -label_3)
-
-tmp %>% ggplot(aes(label_2, value, fill=label_3))+
-  geom_boxplot()+
-  theme_bw()+
-  facet_wrap(key~label_1)+
-  labs(fill="Parameter")
-```
-
-```{r message=FALSE, echo=FALSE, eval=FALSE}
-#attempt to make the above interactive. didn't really work
-ggplotly(ggplot_build(tmp %>%
-                        ggplot(aes(value, color=label_2, fill=label_3))+
-                        geom_histogram(position='identity', alpha = 0.5)+
-                        theme_bw()+
-                        facet_wrap(key~label_1)+
-                        labs(color="Model", fill="Parameter"))$data[[1]] %>%
-           mutate(key = ifelse(PANEL %in%  c(1,2), "icc", "spearman"),
-                  label_1 = ifelse(PANEL %in%  c(1,3), "all", "difference"),
-                  label_2 = ifelse(colour == "#F8766D", "EZ", ifelse(colour == "#00BA38", "hddm", "raw")),
-                  label_3 = ifelse(fill == "#A3A500", "drift rate", ifelse(fill == "#00BF7D", "non-decision", ifelse(fill == "#E76BF3", "threshold", ifelse(fill == "#F8766D", "accuracy", "rt"))))) %>%
-           get_labels(.,tmp, "value", c("label_1", "label_2", "label_3", "key")) %>%
-           prettify_label(.) %>%
-           ggplot(aes(x, y, fill = label_3, color=label_2, label=label))+
-           geom_bar(stat='identity',position='identity', alpha=0.5)+
-           facet_wrap(key~label_1)+
-           theme_bw(),
-         tooltip = 'label',
-         hoverinfo = 'text')
-```
+```{r}
+tmp %>%
+  group_by(label_1,label_2, label_3) %>%
+  summarise(mean_icc = mean(icc),
+            mean_spearman = mean(spearman),
+            n_vars = n()) %>%
+  arrange(-mean_icc, -mean_spearman) %>%
+  datatable() %>%
+  formatRound(columns=c('mean_spearman', 'mean_icc'), digits=3)
+```
+
+Are these differences meaningful?
+
+```{r}
+summary(lm(icc ~ label_1,tmp))
+```
+
+In the model below (after the model comparison the interactive one is significantly better) the baseline is difference accuracy.
+
+Main effects: Compared to this overall accuracy has higher reliability and difference threshold has lower reliability. Other difference parameters do not differ from difference accuracy significantly.
+
+Interactions: Drift rates, thresholds are higher for overall than difference; response times are marginally so.
+
+Conclusion: Overall parameter estimates are higher than difference estimates (except for non-decision time).
+
+```{r}
+summary(lm(icc ~ label_1*label_3,tmp))
+```
+
+Closer look at simple effects:
+
+Are overall drift rates meaninfully higher than overall raw accuracies? Yes.
+
+```{r}
+tmp_simp = tmp %>%
+  filter(label_3 %in% c("drift rate", "accuracy"),
+         label_1 == 'overall')
+
+summary(lm(icc~label_3, tmp_simp))
+```
+
+Are overall drift rates meaninfully higher than overall raw response times? No, not worse either.
+
+```{r}
+tmp_simp = tmp %>%
+  filter(label_3 %in% c("drift rate", "rt"),
+         label_1 == 'overall')
+
+summary(lm(icc~label_3, tmp_simp))
+```
+
+Are overall thresholds meaninfully higher than overall raw accuracies? No, not worse either.
+
+```{r}
+tmp_simp = tmp %>%
+  filter(label_3 %in% c("threshold", "accuracy"),
+         label_1 == 'overall')
+
+summary(lm(icc~label_3, tmp_simp))
+```
+
+Are overall thresholds meaninfully higher than overall raw response times? No, they are worse.
+
+```{r}
+tmp_simp = tmp %>%
+  filter(label_3 %in% c("threshold", "rt"),
+         label_1 == 'overall')
+
+summary(lm(icc~label_3, tmp_simp))
+```
+
+Are overall non-decision times meaninfully higher than overall raw accuracies? No, not worse either.
+
+```{r}
+tmp_simp = tmp %>%
+  filter(label_3 %in% c("non-decision", "accuracy"),
+         label_1 == 'overall')
+
+summary(lm(icc~label_3, tmp_simp))
+```
+
+Are overall non-decision times meaninfully higher than overall raw response times? No, they are worse.
+
+```{r}
+tmp_simp = tmp %>%
+  filter(label_3 %in% c("non-decision", "rt"),
+         label_1 == 'overall')
+
+summary(lm(icc~label_3, tmp_simp))
+```
+
 ### Surveys
@@
 ```
+
+Comparison of survey measures to cognitive task measures in the bootstrapped results.
+Multilevel model with random intercepts for each measure and fixed effect of survey versus cognitive measure.
+(Same result as seen in point estimates comparison).
+
+```{r}
+boot_df = boot_df %>%
+    mutate(task = ifelse(grepl("survey",dv), "survey","task"))
+
+summary(lmerTest::lmer(icc ~  task + (1|dv), boot_df))
+```
+
+Checking DDM results in the bootstrapped estimates. Same as before too.
+
+```{r warning=FALSE, message=FALSE}
+tmp = measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(task == 'task') %>%
+  select(-measure_description, -notes, -measure_type, -task) %>%
+  # left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
+  separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
+  mutate(label_1 = trim(label_1),
+         label_2=trim(label_2),
+         label_3=trim(label_3))%>%
+  filter(ddm_task == 1) %>%
+  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.', remove=FALSE) %>%
+  select(-extra_1, -extra_2) %>%
+  drop_na() %>%
+  left_join(boot_df[,c("dv", "icc")], by = 'dv')
+```
+
+```{r}
+summary(lmerTest::lmer(icc ~ label_1*label_3 + (1|dv) ,tmp))
+```

### 2017-09-15 code/Lit_Review_Figure.Rmd
refactored repo and added first draft of lit review figure

---
title: 'Lit Review Figure'
output:
github_document:
toc: yes
toc_float: yes
---

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(GGally)
library(rmarkdown)
library(stringr)
library(plotly)
library(DT)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
render_this <- function(){rmarkdown::render('Lit_Review_Figure.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
options(scipen = 1, digits = 4)
```

Read data in

```{r}
fig_data <- read.csv('/Users/zeynepenkavi/Downloads/lit_review_figure.csv')
```

Static plot

```{r warning= FALSE, message =FALSE}
fig_data %>%
  mutate(dv = factor(dv, levels = dv[order(task)]),
         days_cutoff = ifelse(days < 60, days, 120),
         days = paste(days, '; reference:', reference)) %>%
ggplot(aes(x = dv, y = retest_reliability, label=days))+
  geom_point(aes(color = task, size=sample_size, shape = type, alpha = days_cutoff))+
  coord_flip()+
  theme_bw()
```

Interactive plot

```{r warning=FALSE, message=FALSE}
ggplotly(fig_data %>%
  mutate(dv = factor(dv, levels = dv[order(task)]),
         days_cutoff = ifelse(days < 60, days, 120),
         days = paste(days, '; reference:', reference)) %>%
ggplot(aes(x = dv, y = retest_reliability, label=days))+
  geom_point(aes(color = task, size=sample_size, shape = type, alpha = days_cutoff))+
  coord_flip()+
  theme_bw()+
  theme(legend.position="none"),
tooltip = c('sample_size', 'type', 'dv', 'retest_reliability', 'days')) %>%
  layout(showlegend=FALSE)
```

### 2017-09-15 code/SRO_Report.Rmd
refactored repo and added first draft of lit review figure

--- 2017-06-06 SRO_Report.Rmd
@@
 library(plotly)
-library(jsonlite)
 library(DT)

### 2017-09-15 code/Lit_Review_Figure.Rmd
rendered first versions of lit review figure

@@
 title: 'Lit Review Figure'
-output:
-github_document:
-toc: yes
-toc_float: yes
+output: html_document
 ---
@@
 sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
-render_this <- function(){rmarkdown::render('Lit_Review_Figure.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
 options(scipen = 1, digits = 4)
@@
 
-```{r warning= FALSE, message =FALSE}
+```{r warning= FALSE, message =FALSE, fig.height=36}
 fig_data %>%
@@
 
-```{r warning=FALSE, message=FALSE}
+```{r warning=FALSE, message=FALSE, fig.height=36}
 ggplotly(fig_data %>%

### 2017-09-15 code/Lit_Review_Figure.Rmd
changed order of plots
cleaned up the figure page; keeping it as html instead of nb.html because the interactive block label character length is breaking the nb html.

@@
 ---
-title: 'Lit Review Figure'
-output: html_document
+title: "Lit Review Figure"
+output:
+  html_document: default
 ---
@@
 library(GGally)
-library(rmarkdown)
 library(stringr)
 library(plotly)
-library(DT)
 sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
@@
 
-Read data in
-
-```{r}
+```{r echo=FALSE}
 fig_data <- read.csv('/Users/zeynepenkavi/Downloads/lit_review_figure.csv')
-```
-
-Static plot
-
-```{r warning= FALSE, message =FALSE, fig.height=36}
-fig_data %>%
-  mutate(dv = factor(dv, levels = dv[order(task)]),
-         days_cutoff = ifelse(days < 60, days, 120),
-         days = paste(days, '; reference:', reference)) %>%
-ggplot(aes(x = dv, y = retest_reliability, label=days))+
-  geom_point(aes(color = task, size=sample_size, shape = type, alpha = days_cutoff))+
-  coord_flip()+
-  theme_bw()
 ```
@@
 
-```{r warning=FALSE, message=FALSE, fig.height=36}
+```{r warning=FALSE, message=FALSE, fig.height=36, echo=FALSE}
 ggplotly(fig_data %>%
@@
 ```
+
+Static plot
+
+```{r warning= FALSE, message =FALSE, fig.height=36, echo=FALSE}
+fig_data %>%
+  mutate(dv = factor(dv, levels = dv[order(task)]),
+         days_cutoff = ifelse(days < 60, days, 120),
+         days = paste(days, '; reference:', reference)) %>%
+ggplot(aes(x = dv, y = retest_reliability, label=days))+
+  geom_point(aes(color = task, size=sample_size, shape = type, alpha = days_cutoff))+
+  coord_flip()+
+  theme_bw()
+```

### 2017-09-19 code/Lit_Review_Figure.Rmd
working on lit review figure

@@
 output:
+  pdf_document: default
   html_document: default
@@
 sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
-options(scipen = 1, digits = 4)
+options(scipen = 1, digits = 4, width = 500)
 ```
@@
 
-```{r warning=FALSE, message=FALSE, fig.height=36, echo=FALSE}
+```{r warning=FALSE, message=FALSE, fig.height=36, echo=FALSE, eval=FALSE}
 ggplotly(fig_data %>%
@@
 
-```{r warning= FALSE, message =FALSE, fig.height=36, echo=FALSE}
+```{r warning= FALSE, message =FALSE, fig.height=36, echo=FALSE, eval=FALSE}
 fig_data %>%
@@
 ```
+
+```{r warning= FALSE, message =FALSE, out.width = "80%", echo=FALSE}
+p1 = fig_data %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(days_cutoff = ifelse(days < 60, days, 120),
+         task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  filter(task == 'task') %>%
+ggplot(aes(y = var, x = retest_reliability)) + 
+  geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff))+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom') + 
+  xlab("")+
+  ylab("")
+
+p2 = fig_data %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(days_cutoff = ifelse(days < 60, days, 120),
+         task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  filter(task == 'survey') %>%
+ggplot(aes(y = var, x = retest_reliability)) + 
+  geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff), color = '#F8766D')+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80")) + 
+  xlab("")+
+  ylab("")
+
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)}
+
+mylegend<-g_legend(p1)
+
+p3 <- grid.arrange(arrangeGrob(p1 + geom_point(color='#00BFC4')+theme(legend.position="none"),
+                         p2 + theme(legend.position="none"),
+                         nrow=1),
+             mylegend, nrow=2,heights=c(10, 1))
+
+ggsave('Lit_Review_Plot.jpg', plot = p3, device = "jpeg", path = "../output/", width = 24, height = 20, units = "in")
+```

### 2017-09-19 code/Lit_Review_Figure.Rmd
fixed colors for lit review figure

@@
 output:
+  html_document: default
   pdf_document: default
-  html_document: default
 ---
@@
 
-Interactive plot
+Interactive plot - not rendered for now
 
@@
 
-```{r warning= FALSE, message =FALSE, out.width = "80%", echo=FALSE}
+```{r warning= FALSE, message =FALSE, echo=FALSE}
+p1_legend = fig_data %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(days_cutoff = ifelse(days < 60, days, 120),
+         task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  filter(task == 'task') %>%
+ggplot(aes(y = var, x = retest_reliability)) + 
+  geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff))+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom') + 
+  xlab("")+
+  ylab("")
+
 p1 = fig_data %>%
@@
 ggplot(aes(y = var, x = retest_reliability)) + 
-  geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff))+
+  geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff), color='#00BFC4')+
   facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
@@
 
-mylegend<-g_legend(p1)
+mylegend<-g_legend(p1_legend)
 
-p3 <- grid.arrange(arrangeGrob(p1 + geom_point(color='#00BFC4')+theme(legend.position="none"),
+p3 <- arrangeGrob(arrangeGrob(p1 +theme(legend.position="none"),
                          p2 + theme(legend.position="none"),
@@
 ```
+
+```{r echo=FALSE, out.width='100%'}
+knitr::include_graphics('../output/Lit_Review_Plot.jpg')
+```

### 2017-09-19 code/SRO_Report.Rmd
refactored repo and rendered the SRO report in this repo

@@
 sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
-render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Report', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
+render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '../output', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
 options(scipen = 1, digits = 4)
@@
 ```{r}
-boot_df <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/bootstrap_merged.csv')
+boot_df <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/bootstrap_merged.csv')
 

### 2017-09-19 code/Lit_Review_Figure.Rmd
included lit review figure data in repo and moved around two tasks in figure
fixed axis for figure

--- 2017-09-19 code/Lit_Review_Figure.Rmd
@@
 ```{r echo=FALSE}
-fig_data <- read.csv('/Users/zeynepenkavi/Downloads/lit_review_figure.csv')
+fig_data <- read.csv('../input/lit_review_figure.csv')
 ```
 
-Interactive plot
+Interactive plot - not rendered for now
 
@@
 
-```{r warning= FALSE, message =FALSE, out.width = "80%", echo=FALSE}
-p1 = fig_data %>%
+```{r warning= FALSE, message =FALSE, echo=FALSE}
+p1_legend = fig_data %>%
   separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
@@
   xlab("")+
-  ylab("")
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))
+
+p1 = fig_data %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(days_cutoff = ifelse(days < 60, days, 120),
+         task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  filter(task == 'task') %>%
+ggplot(aes(y = var, x = retest_reliability)) + 
+  geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff), color='#00BFC4')+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom') + 
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))
 
@@
   xlab("")+
-  ylab("")
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))
 

### 2017-09-20 code/Lit_Review_Figure.Rmd
refactored output directory and fixed the legend issue in lit review plot

--- 2017-09-19 code/Lit_Review_Figure.Rmd
@@
 
-```{r warning= FALSE, message =FALSE, out.width = "80%", echo=FALSE}
-p1 = fig_data %>%
+```{r warning=FALSE, message=FALSE}
+fig_data = fig_data %>%
   separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
-  mutate(days_cutoff = ifelse(days < 60, days, 120),
-         task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)]),
+         raw1_fit0 = grepl('raw', variable_type),
+         type = as.character(type)) %>%
+  arrange(task_group, -raw1_fit0)
+```
+
+```{r warning= FALSE, message =FALSE, echo=FALSE}
+p1_legend = fig_data %>%
   filter(task == 'task') %>%
 ggplot(aes(y = var, x = retest_reliability)) + 
-  geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff))+
+  geom_point(aes(size=sample_size, shape=type))+
   facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
@@
   xlab("")+
-  ylab("")
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 16, 17, 3))
+
+p1 = fig_data %>%
+  filter(task == 'task') %>%
+ggplot(aes(y = var, x = retest_reliability)) + 
+  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom') + 
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 16, 17, 3))
 
 p2 = fig_data %>%
-  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
-  mutate(days_cutoff = ifelse(days < 60, days, 120),
-         task_group = factor(task_group, levels = task_group[order(task)])) %>%
   filter(task == 'survey') %>%
 ggplot(aes(y = var, x = retest_reliability)) + 
-  geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff), color = '#F8766D')+
+  geom_point(aes(size=sample_size, shape = type), color = '#F8766D')+
   facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
@@
   xlab("")+
-  ylab("")
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 17, 3))
 
@@
 
-ggsave('Lit_Review_Plot.jpg', plot = p3, device = "jpeg", path = "../output/", width = 24, height = 20, units = "in")
+ggsave('Lit_Review_Plot.jpg', plot = p3, device = "jpeg", path = "../output/figures/", width = 24, height = 20, units = "in")
 ```
+
+```{r echo=FALSE, out.width='100%'}
+knitr::include_graphics('../output/figures/Lit_Review_Plot.jpg')
+```

### 2017-10-02 code/NeuroeconPoster.Rmd
began script for figures going in to neuroecon poster

--- 2017-09-19 code/Lit_Review_Figure.Rmd
@@
 ---
-title: "Lit Review Figure"
+title: "Neuroecon Poster Figures"
 output:
@@
 ```
-
-```{r echo=FALSE}
-fig_data <- read.csv('/Users/zeynepenkavi/Downloads/lit_review_figure.csv')
-```
-
-Interactive plot - not rendered for now
-
-```{r warning=FALSE, message=FALSE, fig.height=36, echo=FALSE, eval=FALSE}
-ggplotly(fig_data %>%
-  mutate(dv = factor(dv, levels = dv[order(task)]),
-         days_cutoff = ifelse(days < 60, days, 120),
-         days = paste(days, '; reference:', reference)) %>%
-ggplot(aes(x = dv, y = retest_reliability, label=days))+
-  geom_point(aes(color = task, size=sample_size, shape = type, alpha = days_cutoff))+
-  coord_flip()+
-  theme_bw()+
-  theme(legend.position="none"),
-tooltip = c('sample_size', 'type', 'dv', 'retest_reliability', 'days')) %>%
-  layout(showlegend=FALSE)
-```
-
-Static plot
-
-```{r warning= FALSE, message =FALSE, fig.height=36, echo=FALSE, eval=FALSE}
-fig_data %>%
-  mutate(dv = factor(dv, levels = dv[order(task)]),
-         days_cutoff = ifelse(days < 60, days, 120),
-         days = paste(days, '; reference:', reference)) %>%
-ggplot(aes(x = dv, y = retest_reliability, label=days))+
-  geom_point(aes(color = task, size=sample_size, shape = type, alpha = days_cutoff))+
-  coord_flip()+
-  theme_bw()
-```
-
-```{r warning= FALSE, message =FALSE, echo=FALSE}
-p1_legend = fig_data %>%
-  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
-  mutate(days_cutoff = ifelse(days < 60, days, 120),
-         task_group = factor(task_group, levels = task_group[order(task)])) %>%
-  filter(task == 'task') %>%
-ggplot(aes(y = var, x = retest_reliability)) + 
-  geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff))+
-  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
-  theme(panel.spacing = unit(0.5, "lines"), 
-        strip.placement = "outside",
-        strip.text.y = element_text(angle=180),
-        panel.background = element_rect(fill = NA),
-        panel.grid.major = element_line(colour = "grey80"),
-        legend.position = 'bottom') + 
-  xlab("")+
-  ylab("")
-
-p1 = fig_data %>%
-  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
-  mutate(days_cutoff = ifelse(days < 60, days, 120),
-         task_group = factor(task_group, levels = task_group[order(task)])) %>%
-  filter(task == 'task') %>%
-ggplot(aes(y = var, x = retest_reliability)) + 
-  geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff), color='#00BFC4')+
-  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
-  theme(panel.spacing = unit(0.5, "lines"), 
-        strip.placement = "outside",
-        strip.text.y = element_text(angle=180),
-        panel.background = element_rect(fill = NA),
-        panel.grid.major = element_line(colour = "grey80"),
-        legend.position = 'bottom') + 
-  xlab("")+
-  ylab("")
-
-p2 = fig_data %>%
-  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
-  mutate(days_cutoff = ifelse(days < 60, days, 120),
-         task_group = factor(task_group, levels = task_group[order(task)])) %>%
-  filter(task == 'survey') %>%
-ggplot(aes(y = var, x = retest_reliability)) + 
-  geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff), color = '#F8766D')+
-  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
-  theme(panel.spacing = unit(0.5, "lines"), 
-        strip.placement = "outside",
-        strip.text.y = element_text(angle=180),
-        panel.background = element_rect(fill = NA),
-        panel.grid.major = element_line(colour = "grey80")) + 
-  xlab("")+
-  ylab("")
-
-g_legend<-function(a.gplot){
-  tmp <- ggplot_gtable(ggplot_build(a.gplot))
-  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
-  legend <- tmp$grobs[[leg]]
-  return(legend)}
-
-mylegend<-g_legend(p1_legend)
-
-p3 <- arrangeGrob(arrangeGrob(p1 +theme(legend.position="none"),
-                         p2 + theme(legend.position="none"),
-                         nrow=1),
-             mylegend, nrow=2,heights=c(10, 1))
-
-ggsave('Lit_Review_Plot.jpg', plot = p3, device = "jpeg", path = "../output/", width = 24, height = 20, units = "in")
-```
-
-```{r echo=FALSE, out.width='100%'}
-knitr::include_graphics('../output/Lit_Review_Plot.jpg')
-```

### 2017-10-02 code/NeuroeconPoster.Rmd
added outline for poster both in code and in ppt

@@
 ```
+
+Lit review figure
+
+```{r}
+
+```
+
+Bootstrapped reliabilities figure mirroring lit review figure
+(most likely excludes DDM)
+
+```{r}
+
+```
+
+Histogram of point estimates comparing distributions of survey vs. task measures
+
+```{r}
+
+```
+
+Stats comparing reliabilities of surveys vs tasks
+
+```{r}
+
+```
+
+Table for survey reliabilities by survey name
+
+```{r}
+
+```
+
+Stats checking if item number makes a difference for reliability estimates for surveys
+
+```{r}
+
+```
+
+Table for task reliabilities by task name
+
+```{r}
+
+```
+
+Stats checking if item number makes a difference for reliability estimates for tasks
+
+```{r}
+
+```
+
+Table for task reliabilities by cognitive construct
+
+```{r}
+
+```
+
+Histogram of DDM vs. RT and accuracy measures
+
+```{r}
+
+```
+
+Statistics comparing average reliabilities for DDM vs raw measures
+
+```{r}
+
+```
+
+Note on metric for retest reliabilities
+Scatter plots showing relationships between ICC, Pearson and Spearman
+
+```{r}
+
+```

### 2017-10-03 code/SRO_Report.Rmd
added modified gitignore for workspaces and changed report with new test data release

@@
 ```{r}
-test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables.csv')
-
-test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_noDDM.csv')
-
-test_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_EZ.csv')
+test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_07-08-2017/meaningful_variables.csv')
+
+test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_07-08-2017/meaningful_variables_noDDM.csv')
+
+test_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_07-08-2017/meaningful_variables_EZ.csv')
 
@@
 ```{r}
-test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/variables_exhaustive.csv')
+test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_07-08-2017/variables_exhaustive.csv')
 
@@
 retest_data <- retest_data[retest_data$sub_id %in% test_data$sub_id,]
+```
+
+This should not be necessary once releases are matched but for now extract only retest variables from test data.
+
+```{r}
+test_data <- test_data[,c(names(retest_data))]
 ```

### 2017-10-03 code/NeuroeconPoster.Rmd
added updated data for the lit review figure
added lit review plot for poster

@@
 
-Lit review figure
+# Lit review figure
+
+Read data in
 
 ```{r}
+fig_data <- read.csv('../input/lit_review_figure.csv')
+```
+
+Split dv column, organize by model fit or raw measure
+
+```{r warning=FALSE, message=FALSE}
+fig_data = fig_data %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)]),
+         raw1_fit0 = grepl('raw', variable_type),
+         type = as.character(type)) %>%
+  separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
+  mutate(task_group = gsub("_", " ", task_group),
+         var = gsub("_", " ", var)) %>%
+  arrange(task_group, raw1_fit0, var)
+```
+
+```{r}
+p1_legend = fig_data %>%
+  filter(task == 'task') %>%
+ggplot(aes(y = var, x = retest_reliability)) + 
+  geom_point(aes(size=sample_size, shape=type))+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom') + 
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 16, 17, 3))
+
+p1 = fig_data %>%
+  filter(task == 'task') %>%
+ggplot(aes(y = var, x = retest_reliability)) + 
+  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.75, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180, size=20),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom') + 
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 16, 17, 3))
+
+p2 = fig_data %>%
+  filter(task == 'survey') %>%
+ggplot(aes(y = var, x = retest_reliability)) + 
+  geom_point(aes(size=sample_size, shape = type), color = '#F8766D')+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.75, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180, size=20),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80")) + 
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 17, 3))
+
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)}
+
+mylegend<-g_legend(p1_legend)
+
+p3 <- arrangeGrob(arrangeGrob(p1 +theme(legend.position="none"),
+                         p2 + theme(legend.position="none"),
+                         nrow=1),
+             mylegend, nrow=2,heights=c(12, 1))
+
+ggsave('Lit_Review_Poster_Plot.jpg', plot = p3, device = "jpeg", path = "../output/figures/", width = 48, height = 23, units = "in")
 
@@
 ```{r}
+unique(fig_data
 
+boot_df %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)]),
+         raw1_fit0 = grepl('raw', variable_type),
+         type = as.character(type)) %>%
+  separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
+  mutate(task_group = gsub("_", " ", task_group),
+         var = gsub("_", " ", var))
+
+# ggsave('Bootstrap_Poster_Plot.jpg', plot = p3, device = "jpeg", path = "../output/figures/", width = 48, height = 23, units = "in")
 ```

### 2017-10-03 code/NeuroeconPoster.Rmd
parsing down list of variables for poster plots

--- 2017-10-02 code/NeuroeconPoster.Rmd
@@
 options(scipen = 1, digits = 4, width = 500)
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)}
 ```
 
-Lit review figure
+Variables that will be used in the figures for the poster
 
 ```{r}
+poster_vars <- read.csv('../input/poster_var_list.csv', header=F)
+
+names(poster_vars) = "var"
+```
+
+# Lit review figure
+
+Read data in
+
+```{r}
+fig_data <- read.csv('../input/lit_review_figure.csv')
+
+fig_data_poster = fig_data[fig_data$dv %in% poster_vars$var,]
+```
+
+Split dv column, organize by model fit or raw measure
+
+```{r warning=FALSE, message=FALSE}
+fig_data_poster = fig_data_poster %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)]),
+         raw1_fit0 = grepl('raw', variable_type),
+         type = as.character(type)) %>%
+  separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
+  mutate(task_group = gsub("_", " ", task_group),
+         var = gsub("_", " ", var)) %>%
+  arrange(task_group, raw1_fit0, var)
+```
+
+```{r}
+p1_legend = fig_data_poster %>%
+  filter(task == 'task') %>%
+ggplot(aes(y = var, x = retest_reliability)) + 
+  geom_point(aes(size=sample_size, shape=type))+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom', 
+        legend.key.size = unit(2, "cm")) + 
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 16, 17, 3))
+
+p1 = fig_data_poster %>%
+  filter(task == 'task') %>%
+ggplot(aes(y = var, x = retest_reliability)) + 
+  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.75, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180, size=20),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom') + 
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 16, 17, 3))+
+  geom_vline(xintercept = 0, color = "red", size = 1)
+
+p2 = fig_data_poster %>%
+  filter(task == 'survey') %>%
+ggplot(aes(y = var, x = retest_reliability)) + 
+  geom_point(aes(size=sample_size, shape = type), color = '#F8766D')+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.75, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180, size=20),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80")) + 
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 17, 3))+
+  geom_vline(xintercept = 0, color = "red", size = 1)
+
+mylegend<-g_legend(p1_legend)
+
+p3 <- arrangeGrob(arrangeGrob(p1 +theme(legend.position="none"),
+                         p2 + theme(legend.position="none"),
+                         nrow=1),
+             mylegend, nrow=2,heights=c(12, 1))
+
+ggsave('Lit_Review_Poster_Plot.jpg', plot = p3, device = "jpeg", path = "../output/figures/", width = 48, height = 23, units = "in")
 
@@
 Bootstrapped reliabilities figure mirroring lit review figure
-(most likely excludes DDM)
+(excludes DDM)
 
-```{r}
+```{r warning=FALSE, message=FALSE}
+lit_rev_uniq_dvs = fig_data %>%
+  distinct(dv, .keep_all=T) %>%
+  select(-retest_reliability, -type, -days, -sample_size, -reference, -measure_description, -task)
 
+boot_df_lit_rev = boot_df %>%
+  left_join(lit_rev_uniq_dvs, by = "dv") %>%
+  na.omit()
+
+p4 <- boot_df_lit_rev %>%
+  filter(task == 'task') %>%
+ggplot(aes(y = var, x = icc)) + 
+  geom_point(color = '#00BFC4')+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.75, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180, size=20),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80")) + 
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 17, 3))+
+  geom_vline(xintercept = 0, color = "red", size = 1)
+
+p5 <- boot_df_lit_rev %>%
+  filter(task == 'survey') %>%
+ggplot(aes(y = var, x = icc)) + 
+  geom_point(color = '#F8766D')+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.75, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180, size=20),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80")) + 
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 17, 3))+
+  geom_vline(xintercept = 0, color = "red", size = 1)
+
+p6 <- arrangeGrob(p4, p5,nrow=1)
+
+ggsave('Bootstrap_Poster_Plot.jpg', plot = p6, device = "jpeg", path = "../output/figures/", width = 48, height = 23, units = "in")
 ```

### 2017-10-03 code/Lit_Review_Figure.Rmd
added references page with the interactive plot link

@@
 
-Interactive plot - not rendered for now
+References mentioned in the plot below can be found [here](https://docs.google.com/spreadsheets/d/1hcED4_rWSGSE8Td0aqT0kWqlLCBAzRNKBXj3tSram58/edit?usp=sharing).
 
-```{r warning=FALSE, message=FALSE, fig.height=36, echo=FALSE, eval=FALSE}
+Interactive plot
+
+```{r warning=FALSE, message=FALSE, fig.height=36, echo=FALSE}
 ggplotly(fig_data %>%

### 2017-10-03 code/NeuroeconPoster.Rmd
added references page with the interactive plot link

@@
 ```{r warning=FALSE, message=FALSE}
-lit_rev_uniq_dvs = fig_data %>%
-  distinct(dv, .keep_all=T) %>%
-  select(-retest_reliability, -type, -days, -sample_size, -reference, -measure_description, -task)
+boot_df_poster = boot_df[boot_df$dv %in% poster_vars$var,]
 
-boot_df_lit_rev = boot_df %>%
-  left_join(lit_rev_uniq_dvs, by = "dv") %>%
-  na.omit()
+boot_df_poster = boot_df_poster%>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
+  mutate(task_group = gsub("_", " ", task_group),
+         var = gsub("_", " ", var)) %>%
+  arrange(task_group, var)
 
-p4 <- boot_df_lit_rev %>%
+boot_df_poster = boot_df_poster %>%
+  left_join(rel_df[,c("dv", "icc")], by = "dv") %>%
+  rename(icc = icc.x, point_est = icc.y)
+```
+
+```{r warning=FALSE, message=FALSE} 
+p4 <- boot_df_poster %>%
   filter(task == 'task') %>%
@@
   geom_point(color = '#00BFC4')+
+  geom_point(aes(y = var, x = point_est), color = "black")+
   facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
@@
 
-p5 <- boot_df_lit_rev %>%
+p5 <- boot_df_poster %>%
   filter(task == 'survey') %>%
@@
   geom_point(color = '#F8766D')+
+  geom_point(aes(y = var, x = point_est), color = "black")+
   facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +

### 2017-10-04 code/NeuroeconPoster.Rmd
cont working on poster

@@
 library(plotly)
+library(xtable)
 sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
@@
   rename(icc = icc.x, point_est = icc.y)
+
+#Manual correction
+boot_df_poster = boot_df_poster %>%
+  mutate(task = ifelse(task_group == 'holt laury survey', "task", task))
 ```
@@
 
-```{r}
+```{r warning=FALSE, message=FALSE}
+p7 <- ggplot_build(rel_df %>%
+               ggplot(aes(icc, fill=task)) +
+               geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
+  mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
+  ggplot(aes(x,y, fill=task))+
+  geom_bar(stat='identity', position='identity', alpha=0.5)+
+  xlab('ICC')+
+  ylab('Count')+
+  theme_bw()+
+  theme(legend.position="bottom",
+        legend.title = element_blank(),
+        legend.text= element_text(size=30),
+        axis.text.x = element_text(size=20),
+        axis.text.y = element_text(size=20),
+        axis.title.x = element_text(size = 30),
+        axis.title.y = element_text(size = 30))
 
+ggsave('Point_Est_Hist_Poster.jpg', plot = p7, device = "jpeg", path = "../output/figures/", width = 10, height = 10, units = "in")
 ```
@@
 ```{r}
-
+summary(lm(icc ~ task, data=rel_df))
 ```
@@
 ```{r}
-
+rel_df
 ```
@@
 
-```{r}
+```{r warning=FALSE, message=FALSE}
+survey_labels = fig_data %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  distinct(task_group, .keep_all=T) %>%
+  select(-dv, -var, -measure_description, -retest_reliability, -type, -days, -sample_size, -reference) %>%
+  filter(task == "survey")
 
+tmp = rel_df %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  filter(task == "survey") %>%
+  left_join(survey_labels, by = "task_group") %>%
+  na.omit()
+
+summary(lm(icc ~ num_all_trials,data = tmp))
 ```
@@
 ```{r}
+survey_rel_table = boot_df %>%
+  filter(task == "survey") %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  group_by(task_group) %>%
+  summarise(min_icc = min(icc),
+            mean_icc = mean(icc),
+            max_icc = max(icc)) %>%
+  mutate(task_group = gsub("_", " ", task_group))
 
+names(survey_rel_table) <- c("Survey", "Min ICC", "Mean ICC", "Max ICC")
+write.csv(survey_rel_table, "../output/figures/survey_rel_table.csv")
 ```
@@
 
-```{r}
+```{r warning=FALSE, message=FALSE}
+measure_labels <- read.csv('../input/measure_labels.csv')
 
+measure_labels = measure_labels %>%
+  select(dv, task, variable_type, ddm_task, num_all_trials)%>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  distinct(task_group, .keep_all=T) %>%
+  filter(task == "task") %>%
+  select(-dv, -var, -task)
+
+tmp = rel_df %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  filter(task == "task") %>%
+  left_join(measure_labels, by = "task_group") %>%
+  na.omit()
+
+summary(lm(icc ~ num_all_trials,data = tmp))
 ```
 
-Table for task reliabilities by cognitive construct
+Table for task reliabilities by task name
 
 ```{r}
+task_rel_table = boot_df %>%
+  filter(task == "task") %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  group_by(task_group) %>%
+  summarise(min_icc = min(icc),
+            mean_icc = mean(icc),
+            max_icc = max(icc)) %>%
+  mutate(task_group = gsub("_", " ", task_group))
 
+names(task_rel_table) <- c("Task", "Min ICC", "Mean ICC", "Max ICC")
+write.csv(task_rel_table, "../output/figures/task_rel_table.csv")
 ```
@@
 ```{r}
+tmp %>%
+  filter(ddm_task == 1) %>%
 

### 2017-10-04 code/NeuroeconPoster.Rmd
finished first draft

@@
 
-```{r}
-tmp %>%
+```{r warning=FALSE, message=FALSE}
+measure_labels <- read.csv('../input/measure_labels.csv')
+
+p8 = measure_labels %>%
+  select(dv, task, variable_type, ddm_task, num_all_trials)%>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  filter(task == "task") %>%
+  select(-var, -task) %>%
+  left_join(rel_df[,c("dv", "icc")], by="dv")%>%
   filter(ddm_task == 1) %>%
+  separate(variable_type, c("overall_difference", "raw_EZ_hddm", "param"), extra="merge") %>%
+  na.omit() %>%
+  ggplot(aes(icc))+
+  geom_histogram(aes(fill=param),  alpha=0.5, position = 'identity')+
+  facet_wrap(~raw_EZ_hddm)+
+  theme_bw()+
+  theme(legend.position="bottom",
+        legend.title = element_blank(),
+        legend.text= element_text(size=30),
+        axis.text.x = element_text(size=20),
+        axis.text.y = element_text(size=20),
+        axis.title.x = element_text(size = 30),
+        axis.title.y = element_text(size = 30),
+        strip.text = element_text(size=30))
 
+ggsave('DDM_raw_comp_Poster.jpg', plot = p8, device = "jpeg", path = "../output/figures/", width = 18, height = 5, units = "in")
 ```
@@
 
+```{r warning=FALSE, message=FALSE}
+tmp = measure_labels %>%
+  select(dv, task, variable_type, ddm_task, num_all_trials)%>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  filter(task == "task") %>%
+  select(-var, -task) %>%
+  left_join(rel_df[,c("dv", "icc")], by="dv")%>%
+  filter(ddm_task == 1) %>%
+  separate(variable_type, c("overall_difference", "raw_EZ_hddm", "param"), extra="merge") %>%
+  na.omit()
+
+summary(lm(icc~raw_EZ_hddm, data=tmp[tmp$raw_EZ_hddm != "raw",]))
+```
+
 ```{r}
+summary(lm(icc~raw_EZ_hddm, data=tmp[tmp$raw_EZ_hddm != "EZ",]))
+```
 
+```{r}
+summary(lm(icc~raw_EZ_hddm, data=tmp[tmp$raw_EZ_hddm != "hddm",]))
 ```
@@
 ```{r}
+p9 = rel_df %>%
+  ggplot(aes(icc, spearman, color=task))+
+  geom_point()+
+  geom_abline(intercept = 0, slope=1))+
+  theme_bw()+
+  theme(legend.position="bottom",
+        legend.title = element_blank(),
+        legend.text= element_text(size=30),
+        axis.text.x = element_text(size=20),
+        axis.text.y = element_text(size=20),
+        axis.title.x = element_text(size = 30),
+        axis.title.y = element_text(size = 30),
+        strip.text = element_text(size=30))
 
+ggsave('ICC_Spearman_Poster.jpg', plot = p9, device = "jpeg", path = "../output/figures/", width = 10, height = 10, units = "in")
 ```

### 2017-10-04 code/NeuroeconPoster.Rmd
added new version based on feedback

@@
         strip.placement = "outside",
-        strip.text.y = element_text(angle=180, size=20),
+        strip.text.y = element_text(angle=180, size=36),
+        axis.text.y = element_text(size=20),
         panel.background = element_rect(fill = NA),
@@
   geom_point()+
-  geom_abline(intercept = 0, slope=1))+
+  geom_abline(intercept = 0, slope=1)+
   theme_bw()+

### 2017-10-04 code/NeuroeconPoster.Rmd
cont working on poster

@@
          var = gsub("_", " ", var)) %>%
-  arrange(task_group, raw1_fit0, var)
+  arrange(task_group, raw1_fit0, var) %>%
+  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
+  mutate(task_group = gsub("survey", "", task_group))
 ```
@@
   geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
-  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y", labeller = label_wrap_gen(width=20)) +
   theme(panel.spacing = unit(0.75, "lines"), 
@@
   scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
   scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 16, 17, 3))+
@@
   geom_point(aes(size=sample_size, shape = type), color = '#F8766D')+
-  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y", labeller = label_wrap_gen(width=20)) +
   theme(panel.spacing = unit(0.75, "lines"), 
@@
   scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
   scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 17, 3))+
@@
 
-ggsave('Lit_Review_Poster_Plot.jpg', plot = p3, device = "jpeg", path = "../output/figures/", width = 48, height = 23, units = "in")
+ggsave('Lit_Review_Poster_Plot.jpg', plot = p3, device = "jpeg", path = "../output/figures/", width = 35, height = 56, units = "in", limitsize = FALSE)
 
@@
 boot_df_poster = boot_df_poster %>%
-  mutate(task = ifelse(task_group == 'holt laury survey', "task", task))
+  mutate(task = ifelse(task_group == 'holt laury survey', "task", task)) %>%
+  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
+  mutate(task_group = gsub("survey", "", task_group))
 ```
@@
   geom_point(aes(y = var, x = point_est), color = "black")+
-  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y", labeller = label_wrap_gen(width=20)) +
   theme(panel.spacing = unit(0.75, "lines"), 
         strip.placement = "outside",
-        strip.text.y = element_text(angle=180, size=20),
+        strip.text.y = element_text(angle=180, size=36),
+        axis.text.y = element_text(size=20),
         panel.background = element_rect(fill = NA),
@@
 
-ggsave('Bootstrap_Poster_Plot.jpg', plot = p6, device = "jpeg", path = "../output/figures/", width = 48, height = 23, units = "in")
+ggsave('Bootstrap_Poster_Plot.jpg', plot = p6, device = "jpeg", path = "../output/figures/", width = 35, height = 56, units = "in", limitsize = FALSE)
 ```
@@
 
-ggsave('DDM_raw_comp_Poster.jpg', plot = p8, device = "jpeg", path = "../output/figures/", width = 18, height = 5, units = "in")
+ggsave('DDM_raw_comp_Poster.jpg', plot = p8, device = "jpeg", path = "../output/figures/", width = 20, height = 6, units = "in")
 ```

### 2017-10-04 code/NeuroeconPoster.Rmd
added new version of condensed plots and poster

@@
 
+p3nl <- arrangeGrob(p1 +theme(legend.position="none"),
+                         p2 + theme(legend.position="none"),
+                         nrow=1)
+
 ggsave('Lit_Review_Poster_Plot.jpg', plot = p3, device = "jpeg", path = "../output/figures/", width = 35, height = 56, units = "in", limitsize = FALSE)
+
+ggsave('Lit_Review_Poster_Plot_nl.jpg', plot = p3nl, device = "jpeg", path = "../output/figures/", width = 24, height = 42, units = "in", limitsize = FALSE)
 
@@
 
-ggsave('Bootstrap_Poster_Plot.jpg', plot = p6, device = "jpeg", path = "../output/figures/", width = 35, height = 56, units = "in", limitsize = FALSE)
+ggsave('Bootstrap_Poster_Plot.jpg', plot = p6, device = "jpeg", path = "../output/figures/", width = 24, height = 42, units = "in", limitsize = FALSE)
 ```
@@
 ```
+
+Summarizing at task level
+
+```{r}
+p1_t <- fig_data_poster %>%
+  filter(task == 'task') %>%
+ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
+  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
+  theme_bw()+
+  theme(axis.text.y = element_text(size=43),
+        legend.position = 'none') + 
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
+  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 16, 17, 3))+
+  scale_size_continuous(range = c(5, 50))+
+  geom_vline(xintercept = 0, color = "red", size = 1)
+
+p2_t <- fig_data_poster %>%
+  filter(task == 'survey') %>%
+ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
+  geom_point(aes(size=sample_size, shape = type), color='#F8766D')+
+  theme_bw()+
+  theme(axis.text.y = element_text(size=43),
+        legend.position = 'none') + 
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
+  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 16, 17, 3))+
+  scale_size_continuous(range = c(5, 50))+
+  geom_vline(xintercept = 0, color = "red", size = 1)
+
+p3_t <- arrangeGrob(p1_t, p2_t, nrow=1)
+
+ggsave('Lit_Review_Poster_Plot_t.jpg', plot = p3_t, device = "jpeg", path = "../output/figures/", width = 26, height = 45, units = "in", limitsize = FALSE)
+```
+
+```{r}
+p4_t <- boot_df_poster %>%
+  filter(task == 'task') %>%
+ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
+  geom_violin(fill='#00BFC4')+
+  theme_bw() + 
+  theme(axis.text.y = element_text(size=30))+
+  xlab("")+
+  ylab("")+
+  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
+  geom_hline(yintercept = 0, color = "red", size = 1)+
+  coord_flip()
+
+p5_t <- boot_df_poster %>%
+  filter(task == 'survey') %>%
+ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
+  geom_violin(fill='#F8766D')+
+  theme_bw() + 
+  theme(axis.text.y = element_text(size=43))+
+  xlab("")+
+  ylab("")+
+  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
+  geom_hline(yintercept = 0, color = "red", size = 1)+
+  coord_flip()
+
+p6_t <- arrangeGrob(p4_t, p5_t,nrow=1)
+
+ggsave('Bootstrap_Poster_Plot_t.jpg', plot = p6_t, device = "jpeg", path = "../output/figures/", width = 26, height = 45, units = "in", limitsize = FALSE)
+
+```
+
+```{r warning=FALSE, message=FALSE}
+p10 = measure_labels %>%
+  select(dv, task, variable_type, ddm_task, num_all_trials)%>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  filter(task == "task") %>%
+  select(-var, -task) %>%
+  left_join(rel_df[,c("dv", "icc")], by="dv")%>%
+  # filter(ddm_task == 1) %>%
+  separate(variable_type, c("overall_difference", "raw_EZ_hddm", "param"), extra="merge") %>%
+  mutate(raw_EZ_hddm = ifelse(ddm_task == 0, "other", raw_EZ_hddm),
+         param = ifelse(ddm_task == 0, "other", param)) %>%
+  na.omit() %>%
+  ggplot(aes(icc))+
+  geom_histogram(aes(fill=param),  alpha=0.5, position = 'identity')+
+  facet_grid(.~factor(raw_EZ_hddm, levels = c("raw", "EZ", "hddm", "other"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion", "Other")))+
+  theme_bw()+
+  theme(legend.position="bottom",
+        legend.title = element_blank(),
+        legend.text= element_text(size=30),
+        axis.text.x = element_text(size=20),
+        axis.text.y = element_text(size=20),
+        axis.title.x = element_text(size = 30),
+        axis.title.y = element_text(size = 30),
+        strip.text = element_text(size=30))+
+  guides(fill  = guide_legend(nrow = 1))
+
+ggsave('Measure_type_comp_Poster.jpg', plot = p10, device = "jpeg", path = "../output/figures/", width = 30, height = 6, units = "in")
+```

### 2017-10-05 code/NeuroeconPoster.Rmd
added printed version of the neuroecon poster

@@
 
-ggsave('Lit_Review_Poster_Plot_t.jpg', plot = p3_t, device = "jpeg", path = "../output/figures/", width = 26, height = 45, units = "in", limitsize = FALSE)
+ggsave('Lit_Review_Poster_Plot_t.jpg', plot = p3_t, device = "jpeg", path = "../output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE)
 ```
@@
   scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
   geom_hline(yintercept = 0, color = "red", size = 1)+
@@
 
-ggsave('Bootstrap_Poster_Plot_t.jpg', plot = p6_t, device = "jpeg", path = "../output/figures/", width = 26, height = 45, units = "in", limitsize = FALSE)
+ggsave('Bootstrap_Poster_Plot_t.jpg', plot = p6_t, device = "jpeg", path = "../output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE)
 

### 2017-10-31 code/SRO_Report.Rmd
added function to get variance breakdowns

@@
 
+get_var_breakdown <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+  if(sample=='full'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
+  }
+  else if(sample=='bootstrap'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
+  }
+
+  df = df %>% select(-dv, -sub_id)
+  icc = ICC(df)
+  var_breakdown = data.frame(subs = ICC(tmp)$summary[[1]][1,'Mean Sq'],
+                             ind = ICC(tmp)$summary[[1]][2,'Mean Sq'],
+                             resid = ICC(tmp)$summary[[1]][3,'Mean Sq'])
+  return(var_breakdown)
+  }
+
 get_eta <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
@@
                      eta_sq = rep(NA, length(numeric_cols)),
-                     sem = rep(NA, length(numeric_cols)))
+                     sem = rep(NA, length(numeric_cols)),
+                     var_subs = rep(NA, length(numeric_cols)),
+                     var_ind = rep(NA, length(numeric_cols)),
+                     var_resid = rep(NA, length(numeric_cols)))
 
@@
   rel_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
+  rel_df[numeric_cols[i], 'var_subs'] <- get_var_breakdown('adaptive_n_back.mean_load.logTr')$subs
+  rel_df[numeric_cols[i], 'var_ind'] <- get_var_breakdown('adaptive_n_back.mean_load.logTr')$ind
+  rel_df[numeric_cols[i], 'var_resid'] <- get_var_breakdown('adaptive_n_back.mean_load.logTr')$resid
 }

### 2017-10-31 code/SRO_Report.Rmd
added variance breakdown plot for surveys and non ddm task variables

@@
   icc = ICC(df)
-  var_breakdown = data.frame(subs = ICC(tmp)$summary[[1]][1,'Mean Sq'],
-                             ind = ICC(tmp)$summary[[1]][2,'Mean Sq'],
-                             resid = ICC(tmp)$summary[[1]][3,'Mean Sq'])
+  var_breakdown = data.frame(subs = icc$summary[[1]][1,'Mean Sq'],
+                             ind = icc$summary[[1]][2,'Mean Sq'],
+                             resid = icc$summary[[1]][3,'Mean Sq'])
   return(var_breakdown)
@@
   rel_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
-  rel_df[numeric_cols[i], 'var_subs'] <- get_var_breakdown('adaptive_n_back.mean_load.logTr')$subs
-  rel_df[numeric_cols[i], 'var_ind'] <- get_var_breakdown('adaptive_n_back.mean_load.logTr')$ind
-  rel_df[numeric_cols[i], 'var_resid'] <- get_var_breakdown('adaptive_n_back.mean_load.logTr')$resid
+  rel_df[numeric_cols[i], 'var_subs'] <- get_var_breakdown(numeric_cols[i])$subs
+  rel_df[numeric_cols[i], 'var_ind'] <- get_var_breakdown(numeric_cols[i])$ind
+  rel_df[numeric_cols[i], 'var_resid'] <- get_var_breakdown(numeric_cols[i])$resid
 }
@@
 rel_df = rel_df %>%
-  select(dv, task, spearman, icc, eta_sq, sem)
+  select(dv, task, spearman, icc, eta_sq, sem, var_subs, var_ind, var_resid)
 # row.names(rel_df) = NULL
-
 ```
@@
 ```
+
+## Variance breakdown
+
+```{r warning=FALSE, message=FALSE}
+p1 = rel_df %>%
+  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
+         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
+         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
+  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
+  gather(key, value, -dv, -task) %>%
+  mutate(key = factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct")),
+         dv = factor(dv, levels = dv[order(task)])) %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  # separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
+  mutate(task_group = gsub("_", " ", task_group),
+         var = gsub("_", " ", var),
+         var=gsub(".ReflogTr", "", var),
+         var=gsub(".logTr", "", var)) %>%
+  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
+  mutate(task_group = gsub("survey", "", task_group)) %>%
+  filter(task=="task",
+         !grepl("EZ|hddm", dv))%>%
+  ggplot(aes(x=var, y=value, fill=key))+
+  geom_bar(stat='identity', alpha = 0.75)+
+  coord_flip()+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom')+
+  #theme_bw()+  
+  theme(legend.title = element_blank())+
+  scale_fill_discrete(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
+                    labels = c("Variance between individuals",
+                               "Variance between sessions",
+                               "Error variance"))+
+  ylab("")+
+  xlab("")
+
+p2 = rel_df %>%
+  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
+         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
+         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
+  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
+  gather(key, value, -dv, -task) %>%
+  mutate(key = factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct")),
+         dv = factor(dv, levels = dv[order(task)])) %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
+  mutate(task_group = gsub("_", " ", task_group),
+         var = gsub("_", " ", var)) %>%
+  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
+  mutate(task_group = gsub("survey", "", task_group)) %>%
+  filter(task=="survey")%>%
+  ggplot(aes(x=var, y=value, fill=key))+
+  geom_bar(stat='identity', alpha = 0.75)+
+  coord_flip()+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom')+
+  #theme_bw()+  
+  theme(legend.title = element_blank())+
+  scale_fill_discrete(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
+                    labels = c("Variance between individuals",
+                               "Variance between sessions",
+                               "Error variance"))+
+  ylab("")+
+  xlab("")
+
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)}
+
+mylegend<-g_legend(p1)
+
+p3 <- arrangeGrob(arrangeGrob(p1 +theme(legend.position="none"),
+                         p2 + theme(legend.position="none"),
+                         nrow=1),
+             mylegend, nrow=2,heights=c(10, 1))
+
+ggsave('Variance_Breakdown_Plot.jpg', plot = p3, device = "jpeg", path = "/output/figures/", width = 24, height = 20, units = "in")
+```

### 2017-11-01 code/SRO_Report.Rmd
added new plots

--- 2017-10-31 code/SRO_Report.Rmd
@@
 ```
+
+## Variance breakdown
+
+```{r warning=FALSE, message=FALSE}
+p1 = rel_df %>%
+  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
+         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
+         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
+  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
+  gather(key, value, -dv, -task) %>%
+  mutate(key = factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct")),
+         dv = factor(dv, levels = dv[order(task)])) %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  # separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
+  mutate(task_group = gsub("_", " ", task_group),
+         var = gsub("_", " ", var),
+         var=gsub(".ReflogTr", "", var),
+         var=gsub(".logTr", "", var)) %>%
+  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
+  mutate(task_group = gsub("survey", "", task_group)) %>%
+  filter(task=="task",
+         !grepl("EZ|hddm", dv))%>%
+  ggplot(aes(x=var, y=value, fill=key))+
+  geom_bar(stat='identity', alpha = 0.75)+
+  coord_flip()+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom')+
+  #theme_bw()+  
+  theme(legend.title = element_blank())+
+  scale_fill_discrete(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
+                    labels = c("Variance between individuals",
+                               "Variance between sessions",
+                               "Error variance"),
+                     h=c(100,500))+
+  ylab("")+
+  xlab("")
+
+p2 = rel_df %>%
+  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
+         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
+         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
+  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
+  gather(key, value, -dv, -task) %>%
+  mutate(key = factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct")),
+         dv = factor(dv, levels = dv[order(task)])) %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
+  mutate(task_group = gsub("_", " ", task_group),
+         var = gsub("_", " ", var)) %>%
+  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
+  mutate(task_group = gsub("survey", "", task_group)) %>%
+  filter(task=="survey")%>%
+  ggplot(aes(x=var, y=value, fill=key))+
+  geom_bar(stat='identity', alpha = 0.75)+
+  coord_flip()+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom')+
+  #theme_bw()+  
+  theme(legend.title = element_blank())+
+  scale_fill_discrete(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
+                    labels = c("Variance between individuals",
+                               "Variance between sessions",
+                               "Error variance"),
+                    h=c(100,500))+
+  ylab("")+
+  xlab("")
+
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)}
+
+mylegend<-g_legend(p1)
+
+p3 <- arrangeGrob(arrangeGrob(p1 +theme(legend.position="none"),
+                         p2 + theme(legend.position="none"),
+                         nrow=1),
+             mylegend, nrow=2,heights=c(10, 1))
+
+ggsave('Variance_Breakdown_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 24, height = 20, units = "in")
+```
+
+```{r echo=FALSE, out.width='100%'}
+knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Variance_Breakdown_Plot.jpg')
+```
+
+Comparing types of variance for survey vs task measures: Survey measures have higher between subject variability
+
+Note: This analysis includes DDM variables too.
+
+```{r}
+tmp = rel_df %>%
+  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
+         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
+         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
+  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
+  gather(key, value, -dv, -task) 
+  # do(tidy(lm(value~key*task, data=.)))
+
+summary(lm(value~key*task,tmp))
+```
+
+```{r}
+aggregate(value ~task+key, FUN=mean, data=tmp)
+```
+
+Summarizing for clearer presentation
+
+```{r}
+tmp %>%
+  group_by(task, key) %>%
+  ggplot(aes(task, value, fill=key))+
+  geom_boxplot()+
+  theme_bw()+
+  theme(legend.title = element_blank())+
+  scale_fill_discrete(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
+                    labels = c("Variance between individuals",
+                               "Variance between sessions",
+                               "Error variance"),
+                    h=c(100,500))+
+  xlab("")+
+  ylab("Percent")
+
+ggsave('Variance_Breakdown_Plot_Summary.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 6, height = 5, units = "in")
+```
+
+What does it look like for DDM variables separately?
+
+```{r warning=FALSE, message=FALSE}
+p1_ddm = rel_df %>%
+  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
+         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
+         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
+  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
+  gather(key, value, -dv, -task) %>%
+  mutate(key = factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct")),
+         dv = factor(dv, levels = dv[order(task)])) %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  # separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
+  mutate(task_group = gsub("_", " ", task_group),
+         var = gsub("_", " ", var),
+         var=gsub(".ReflogTr", "", var),
+         var=gsub(".logTr", "", var)) %>%
+  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
+  mutate(task_group = gsub("survey", "", task_group)) %>%
+  filter(task=="task",
+         grepl("EZ|hddm", dv))%>%
+  ggplot(aes(x=var, y=value, fill=key))+
+  geom_bar(stat='identity', alpha = 0.75)+
+  coord_flip()+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom')+
+  #theme_bw()+  
+  theme(legend.title = element_blank())+
+  scale_fill_discrete(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
+                    labels = c("Variance between individuals",
+                               "Variance between sessions",
+                               "Error variance"),
+                     h=c(100,500))+
+  ylab("")+
+  xlab("")
+
+ggsave('Variance_Breakdown_Plot_DDM.jpg', plot = p1_ddm, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 12, height = 20, units = "in")
+```

### 2017-11-01 code/SRO_Report.Rmd
working on updating retest report

@@
 ```{r warning=FALSE, message=FALSE}
-workers = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/User_717570_workers.csv')
+workers = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/User_717570_workers.csv')
 workers = workers %>% 
@@
 
-worker_counts <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/retest_worker_counts.json')
+worker_counts <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/retest_worker_counts.json')
 
@@
 ```{r warning=FALSE, message=FALSE}
-disc_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/discovery_completion_dates.csv', header=FALSE)
-val_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/validation_completion_dates.csv', header=FALSE)
+disc_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/discovery_completion_dates.csv', header=FALSE)
+val_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/validation_completion_dates.csv', header=FALSE)
 test_comp_date = rbind(disc_comp_date, val_comp_date)
 rm(disc_comp_date, val_comp_date)
-retest_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/retest_completion_dates.csv', header=FALSE)
+retest_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/retest_completion_dates.csv', header=FALSE)
 comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
@@
 ```{r}
-retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/meaningful_variables.csv')
-
-retest_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/meaningful_variables_noDDM.csv')
-
-retest_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/meaningful_variables_EZ.csv')
+retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/meaningful_variables.csv')
+
+retest_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/meaningful_variables_noDDM.csv')
+
+retest_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/meaningful_variables_EZ.csv')
 
@@
 In cleaning t1 data variables that had a |skew| > 1 were log transformed and those for which skew could not be removed successfully were dropped.
-**Here we transform all variables that have a |skew|>1 in t1 data but variables that are not successfully transformed will be listed and not dropped.**
+**Here we transform all variables that have a |skew|>1 in t1 data but variables that are not successfully transformed (i.e.
+where the transformation has not decreased the skew below the threshold) will be listed and not dropped.**
 

### 2017-11-02 code/Lit_Review_Figure.Rmd
cont working on new report

@@
 ```{r warning= FALSE, message =FALSE, fig.height=36, echo=FALSE, eval=FALSE}
+#Static plot with everything in same panel
 fig_data %>%

### 2017-11-02 code/SRO_Report.Rmd
began updating report with new data releases
cont working on new report

@@
 sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
-render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '../output', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)}
+render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
 options(scipen = 1, digits = 4)
@@
 This sample consists of data for 150 subjects of the original sample of 522 that has completed the initial battery of 37 cognitive tasks, 23 surveys and 3 surveys on demographics.
-Details of the original sample as well as quality control (qc) procedures are described elsewhere.
+Details of the original sample as well as quality control (qc) procedures are described elsewhere (Eisenberg et al., 2017).
 Invited participants were chosen randomly and only subsets of them were invited for a given batch (instead of opening the battery to all qualified subjects) with the intention to avoid a potential oversampling and bias towards "high self regulators".
@@
 
-### Tasks
-
-### Surveys
+One the major contributions of this project is a comprehensive literature review of the retest reliabilities of the surveys and tasks that were used.
+We reviewed the literature on a measure (as opposed to task level) paying attention to differences in sample size, the delay between the two measurements as well as the statistic that was used to assess reliabilities (e.g.
+Spearman vs.
+Pearson correlations).
+Here we present a table and a visualization summarizing our findings.
+References mentioned in the table below can be found [here](https://docs.google.com/spreadsheets/d/1hcED4_rWSGSE8Td0aqT0kWqlLCBAzRNKBXj3tSram58/edit?usp=sharing).
+
+```{r}
+lit_review <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/lit_review_figure.csv')
+
+datatable(lit_review %>%
+  mutate(dv = gsub(".ReflogTr", "",dv),
+         dv = gsub(".logTr", "", dv)))
+```
+
+Measure level plot
+
+```{r warning=FALSE, message=FALSE}
+lit_review = lit_review %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)]),
+         raw1_fit0 = grepl('raw', variable_type),
+         type = as.character(type)) %>%
+  mutate(task_group = gsub("_", " ", task_group),
+         var = gsub("_", " ", var),
+         dv = gsub(".ReflogTr", "",dv),
+         dv = gsub(".logTr", "", dv)) %>%
+  arrange(task_group, raw1_fit0, var) %>%
+  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
+  mutate(task_group = gsub("survey", "", task_group)) %>%
+    select(-measure_description, -reference)
+```
+
+```{r warning= FALSE, message =FALSE, echo=FALSE}
+p1_legend = lit_review %>%
+  filter(task == 'task') %>%
+ggplot(aes(y = var, x = retest_reliability)) + 
+  geom_point(aes(size=sample_size, shape=type))+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom') + 
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))
+
+p1 = lit_review %>%
+  filter(task == 'task') %>%
+ggplot(aes(y = var, x = retest_reliability)) + 
+  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom') + 
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))
+
+p2 = lit_review %>%
+  filter(task == 'survey') %>%
+ggplot(aes(y = var, x = retest_reliability)) + 
+  geom_point(aes(size=sample_size, shape = type), color = '#F8766D')+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80")) + 
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 17, 3))
+
+mylegend<-g_legend(p1_legend)
+
+p3 <- arrangeGrob(arrangeGrob(p1 +theme(legend.position="none"),
+                         p2 + theme(legend.position="none"),
+                         nrow=1),
+             mylegend, nrow=2,heights=c(10, 1))
+
+ggsave('Lit_Review_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 20, units = "in")
+rm(p1, p2, p3, p1_legend, mylegend)
+```
+
+```{r echo=FALSE, out.width='100%'}
+knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Lit_Review_Plot.jpg')
+```
+
+Because this plot is difficult to digest we summarize it on a task level to give a general sense of the main takeaways. This plot naturally disregards much of the fine grained information.
+
+```{r}
+p1_t <- lit_review %>%
+  filter(task == 'task') %>%
+ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
+  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
+  theme_bw()+
+  theme(axis.text.y = element_text(size=43),
+        legend.position = 'none') + 
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
+  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))+
+  scale_size_continuous(range = c(5, 50))+
+  geom_vline(xintercept = 0, color = "red", size = 1)
+
+p2_t <- lit_review %>%
+  filter(task == 'survey') %>%
+ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
+  geom_point(aes(size=sample_size, shape = type), color='#F8766D')+
+  theme_bw()+
+  theme(axis.text.y = element_text(size=43),
+        legend.position = 'none') + 
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
+  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))+
+  scale_size_continuous(range = c(5, 50))+
+  geom_vline(xintercept = 0, color = "red", size = 1)
+
+p3_t <- arrangeGrob(p1_t, p2_t, nrow=1)
+
+ggsave('Lit_Review_Plot_t.jpg', plot = p3_t, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE)
+rm(p1_t, p2_t, p3_t)
+```
+
+```{r echo=FALSE, out.width='100%'}
+knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Lit_Review_Plot_t.jpg')
+```
+
+An interactive version of this plot could be find [here](https://zenkavi.github.io/SRO_Retest_Analyses/output/reports/Lit_Review_Figure.html)
+
+Takeaways from this review are: 
+- Survey measures have been reported to higher reliability compared to task measures  
+- Survey measures have less variability in the reported reliabiltiy estimates compared to task measures'
 

### 2017-11-03 code/SRO_Report.Rmd
cont cleaning old report

@@
 
-datatable(lit_review %>%
-  mutate(dv = gsub(".ReflogTr", "",dv),
-         dv = gsub(".logTr", "", dv)))
+datatable(lit_review)
 ```
@@
   mutate(task_group = gsub("_", " ", task_group),
-         var = gsub("_", " ", var),
-         dv = gsub(".ReflogTr", "",dv),
-         dv = gsub(".logTr", "", dv)) %>%
+         var = gsub("_", " ", var)) %>%
   arrange(task_group, raw1_fit0, var) %>%
@@
 
-## Loading and matching datasets
-
-This report uses the variables that were designated as "meaningful" before.
-This is not the smallest subset where certain variables are dropped because they are correlated with other variables (within a task) and includes both accuracies as well as both kinds of DDM variables (EZ and HDDM).
-It will not include variables that were considered not of theoretical interest in the analyses of time 1 data.
-The variables that are not included will be listed for reference as well.
+## Loading datasets
+
+The variables included in this report are:  
+- meaningful variables (includes only hdddm parameters)  
+- EZ diffusion parameters  
+- Raw RT and Accuracy measures  
+- Variables found in the literature (for comparison)
+
+```{r echo=FALSE}
+#Get variables of interest
+tmp1 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_10-08-2017/meaningful_variables.csv')
+tmp2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_10-08-2017/meaningful_variables_noDDM.csv')
+tmp3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_10-08-2017/meaningful_variables_EZ.csv')
+retest_report_vars = c(names(tmp1), names(tmp2), names(tmp3))
+retest_report_vars = unique(retest_report_vars)
+lit_rev_vars = unique(lit_review$dv)[which(unique(lit_review$dv) %in% retest_report_vars == FALSE)]
+retest_report_vars = c(retest_report_vars, lit_rev_vars)
+rm(tmp1, tmp2, tmp3, lit_rev_vars)
+```
 
@@
 ```{r}
-test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_07-08-2017/meaningful_variables.csv')
-
-test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_07-08-2017/meaningful_variables_noDDM.csv')
-
-test_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_07-08-2017/meaningful_variables_EZ.csv')
-
-test_data <- merge(test_data, test_data2)
-test_data <- merge(test_data, test_data3)
-rm(test_data2, test_data3)
+test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/t1_data/variables_exhaustive.csv')
+
+test_data <- test_data[,names(test_data) %in% retest_report_vars]
 ```
@@
 ```{r}
-test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_07-08-2017/variables_exhaustive.csv')
-
-test_data2$X <- as.character(test_data2$X)
-
-names(test_data2)[1] <- 'sub_id'
+test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/t1_data/variables_exhaustive.csv')
 
@@
 ```{r}
-retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/meaningful_variables.csv')
-
-retest_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/meaningful_variables_noDDM.csv')
-
-retest_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/meaningful_variables_EZ.csv')
-
-retest_data <- merge(retest_data, retest_data2)
-retest_data <- merge(retest_data, retest_data3)
-rm(retest_data2, retest_data3)
-```
-
-Extract t2 participants with good t1 data: We only invited those with good data but due to a technical error a handful of subjects who weren't checked for data quality completed the retest battery as well.
-One of those subjects gave good t2 data but didn't have good t1 data and therefore is removed from further analyses.
+retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/variables_exhaustive.csv')
+
+retest_data <- retest_data[,names(retest_data) %in% retest_report_vars]
+```
 
@@
 names(test_data)[1] <- 'sub_id'
-
-retest_data <- retest_data[retest_data$sub_id %in% test_data$sub_id,]
-```
-
-This should not be necessary once releases are matched but for now extract only retest variables from test data.
-
-```{r}
-test_data <- test_data[,c(names(retest_data))]
-```
-
-### Clean t1 data
-
-The cleaning functions here are translated from the python pipeline to mimick the same procedure that was applied to the `meaningful_variables` in creating `meaningful_variables_clean`.
-
-The original cleaning procedures include three steps:  
-1.
-Removing outliers for each variable where outliers are defined as those who are greater than 2.5 IQR from median.
-**This step is skipped here because removing outliers from either dataset could lead to an unnecessary increase in missing data.
-Since we are interested in the average distance between two measures of a metric for a given subject instead of the distance between all these metrics this seemed appropriate.**
-2.
-Removing correlated variables *within* a task.
-In creating `meaningful_variables_clean` if variables for a given task correlated >.85 only one was kept.
-**This step is skipped here because we want to look at the reliability of as many variables as we can.**
-3.
-Log transforming variables with skew.
-In cleaning t1 data variables that had a |skew| > 1 were log transformed and those for which skew could not be removed successfully were dropped.
-**Here we transform all variables that have a |skew|>1 in t1 data but variables that are not successfully transformed (i.e.
-where the transformation has not decreased the skew below the threshold) will be listed and not dropped.**
-
-```{r}
-remove_outliers = function(data_column, quantile_range = 2.5){
-
-  q_25 = quantile(data_column, na.rm=T)[2]
-  q_50 = quantile(data_column, na.rm=T)[3]
-  q_75 = quantile(data_column, na.rm=T)[4]
-
-  lowlimit = q_50 - quantile_range*(q_75 - q_25)
-  highlimit = q_50 + quantile_range*(q_75 - q_25)
-
-  data_column = ifelse(data_column<lowlimit, NA, ifelse(data_column>highlimit, NA, data_column))
-
-  return(data_column)
-}
-
-"%w/o%" <- function(x, y) x[!x %in% y]
-
-pos_log <- function(column){
-  col_min = min(column, na.rm=T)
-  a = 1-col_min
-  column = column+a
-  return(log(column))
-}
-
-neg_log <- function(column){
-  col_max = max(column, na.rm=T)
-  column = col_max+1-column
-  return(log(column))
-}
-
-transform_remove_skew = function(data, columns, threshold = 1, drop=FALSE){
-
-  tmp = as.data.frame(apply(data[,columns],2,skew))
-  names(tmp) = c("skew")
-  tmp$dv = row.names(tmp)
-  tmp = tmp %>% 
-    filter(abs(skew)>threshold)
-
-  skewed_variables = tmp$dv
-  skew_subset = data[, skewed_variables]
-  positive_subset = data[,tmp$dv[tmp$skew>0]]
-  negative_subset = data[,tmp$dv[tmp$skew<0]]
-
-  # transform variables
-  # log transform for positive skew
-  # positive_subset = log(positive_subset)
-  # positive_subset = pos_log(positive_subset) #slight divergence from original code
-  positive_subset = as.data.frame(apply(positive_subset, 2, pos_log))
-  successful_transforms = as.data.frame(apply(positive_subset, 2, skew))
-  names(successful_transforms) = c('skew')
-  successful_transforms$dv = row.names(successful_transforms)
-  successful_transforms = successful_transforms %>% filter(abs(skew)<threshold)
-  successful_transforms = successful_transforms$dv
-  successful_transforms = positive_subset[,successful_transforms]
-  dropped_vars = names(positive_subset) %w/o% names(successful_transforms)
-
-  cat(rep('*', 40))
-  cat('\n')
-  cat(paste0(length(names(positive_subset)) ,' data positively skewed data were transformed:'))
-  cat('\n')
-  cat(names(positive_subset), sep = '\n')
-  cat(rep('*', 40))
-  cat('\n')
-
-  # replace transformed variables
-  data = data[,-c(which(names(data) %in% names(positive_subset)))]
-
-  if(drop == TRUE){
-    names(successful_transforms) = paste0(names(successful_transforms), '.logTr')
-    cat(rep('*', 40))
-    cat('\n')
-    cat(paste0('Dropping ', length(dropped_vars) ,' positively skewed data that could not be transformed successfully:'))
-    cat('\n')
-    cat(dropped_vars, sep = '\n')
-    cat(rep('*', 40))
-    cat('\n')
-    data = cbind(data, successful_transforms)
-  }
-  else{
-    names(positive_subset) = paste0(names(positive_subset), '.logTr')
-    cat(rep('*', 40))
-    cat('\n')
-    cat(paste0(length(dropped_vars) ,' positively skewed data could not be transformed successfully:'))
-    cat('\n')
-    cat(dropped_vars, sep = '\n')
-    cat(rep('*', 40))
-    cat('\n')
-    data = cbind(data, positive_subset)
-  }
-
-  # reflected log transform for negative skew      
-  negative_subset = as.data.frame(apply(negative_subset, 2, neg_log))
-  successful_transforms = as.data.frame(apply(negative_subset, 2, skew))
-  names(successful_transforms) = c('skew')
-  successful_transforms$dv = row.names(successful_transforms)
-  successful_transforms = successful_transforms %>% filter(abs(skew)<1)
-  successful_transforms = successful_transforms$dv
-  successful_transforms = negative_subset[,successful_transforms]
-  dropped_vars = names(negative_subset) %w/o% names(successful_transforms)
-
-  cat(rep('*', 40))
-  cat('\n')
-  cat(paste0(length(names(negative_subset)) ,' data negatively skewed data were transformed:'))
-  cat('\n')
-  cat(names(negative_subset), sep = '\n')
-  cat(rep('*', 40))
-  cat('\n')
-
-  # replace transformed variables
-  data = data[,-c(which(names(data) %in% names(negative_subset)))]
-  if(drop == TRUE){
-    names(successful_transforms) = paste0(names(successful_transforms), '.ReflogTr')
-    cat(rep('*', 40))
-    cat('\n')
-    cat(paste0('Dropping ', length(dropped_vars) ,' negatively skewed data that could not be transformed successfully:'))
-    cat('\n')
-    cat(dropped_vars, sep = '\n')
-    cat(rep('*', 40))
-    cat('\n')
-    data = cbind(data, successful_transforms)
-  }
-  else{
-    names(negative_subset) = paste0(names(negative_subset), '.ReflogTr')
-    cat(rep('*', 40))
-    cat('\n')
-    cat(paste0(length(dropped_vars) ,' negatively skewed data could not be transformed successfully:'))
-    cat('\n')
-    cat(dropped_vars, sep = '\n')
-    cat(rep('*', 40))
-    cat('\n')
-    data = cbind(data, negative_subset)
-  }
-
-  return(data)
-}
-```
-
-Clean t1 data on full sample without dropping any columns. Columns that are not transformed successfully are listed.
-
-```{r warning=FALSE}
-numeric_cols = c()
-
-for(i in 1:length(names(test_data))){
-  if(is.numeric(test_data[,i])){
-    numeric_cols <- c(numeric_cols, names(test_data)[i])
-  }
-}
-
-# clean_test_data = cbind(sub_id = test_data$sub_id, as.data.frame(apply(test_data[, -which(names(test_data) %in% c("sub_id"))], 2, remove_outliers)))
-
-# clean_test_data = transform_remove_skew(clean_test_data, numeric_cols)
-clean_test_data = transform_remove_skew(test_data, numeric_cols)
-```
-
-```{r echo=FALSE}
-rm(i)
-```
-
-### Clean t2 data
-
-Instead of applying the same functions applied to t1 data we check which variables are transformed in what way and transform the t2 data the same way.
-Again we are not removing outliers in the t2 or dropping variables if the skew is not removed successfully after transforming.
-
-Get list of transformed variables and the sign of their skew
-```{r}
-logTr_vars = data.frame(grep('logTr', names(clean_test_data), value=T))
-names(logTr_vars) = c('var')
-logTr_vars$sign = ifelse(grepl(".ReflogTr",logTr_vars$var), 'negative', 'positive')
-logTr_vars$var = gsub(".logTr|.ReflogTr", "", logTr_vars$var)
-```
-
-Transform the t2 columns the same way t1 columns were transformed.
-
-```{r warning=FALSE}
-clean_retest_data = retest_data
-
-for(i in 1:length(names(clean_retest_data))){
-  tmp_col = names(clean_retest_data)[i]
-  if(tmp_col %in% logTr_vars$var){
-    sign = logTr_vars$sign[which(tmp_col == logTr_vars$var)]
-      if(sign == 'positive'){
-        # clean_retest_data[,tmp_col] = log(clean_retest_data[,tmp_col])
-        clean_retest_data[,tmp_col] = pos_log(clean_retest_data[,tmp_col])
-        names(clean_retest_data)[which(names(clean_retest_data) == tmp_col)] = paste0(tmp_col, '.logTr')
-        cat(paste0(tmp_col ,' was positively skewed and transformed.'))
-        cat('\n')
-      }
-      else if(sign == 'negative'){
-        clean_retest_data[,tmp_col] = neg_log(clean_retest_data[,tmp_col])
-        names(clean_retest_data)[which(names(clean_retest_data) == tmp_col)] = paste0(tmp_col, '.ReflogTr')
-        cat(paste0(tmp_col ,' was negatively skewed and transformed.'))
-        cat('\n')
-      }
-    }
-}
-```
-
-```{r echo = FALSE}
-rm(i, sign, tmp_col)
-```
-
-Check transformations are correct
-```{r}
-retest_logTr_vars = data.frame(grep('logTr', names(clean_retest_data), value=T))
-names(retest_logTr_vars) = c('var')
-retest_logTr_vars$sign = ifelse(grepl(".ReflogTr",retest_logTr_vars$var), 'negative', 'positive')
-retest_logTr_vars$var = gsub(".logTr|.ReflogTr", "", retest_logTr_vars$var)
-retest_logTr_vars = retest_logTr_vars %>% arrange(var)
-logTr_vars = logTr_vars %>% arrange(var)
-retest_logTr_vars == logTr_vars
-```
-
-```{r echo=FALSE}
-rm(logTr_vars, retest_logTr_vars)
-```
-
-```{r}
-# Switch df names
-raw_retest_data = retest_data
-raw_test_data = test_data
-test_data = clean_test_data
-retest_data = clean_retest_data
-rm(clean_test_data, clean_retest_data)
-```
-
-### Extract t-1 data for t-2 subjects
-```{r}
-retest_subs_test_data <- test_data[test_data$sub_id %in% retest_data$sub_id,]
-
-rest_subs_test_data <- test_data[test_data$sub_id %in% retest_data$sub_id == FALSE,]
-
-#Arrange datasets of same size by sub_id
-retest_data = retest_data %>% arrange(sub_id)
-retest_subs_test_data = retest_subs_test_data %>% arrange(sub_id)
-
-#CHECK IF EVERYTHING IS ORDERED RIGHT
-as.character(retest_subs_test_data$sub_id) == as.character(retest_data$sub_id)
 ```

### 2017-11-03 code/SRO_Report.Rmd
cont cleaning up report

@@
   return(legend)}
+trim <- function (x) gsub("^\\s+|\\s+$", "", x)
 render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
@@
 test_data <- test_data[,names(test_data) %in% retest_report_vars]
+
+test_data$X <- as.character(test_data$X)
+names(test_data)[which(names(test_data) == 'X')] <-'sub_id' 
 ```
@@
 retest_data <- retest_data[,names(retest_data) %in% retest_report_vars]
-```
-
-```{r}
-#Process sub_id columns in the data dataframes
+
 retest_data$X <- as.character(retest_data$X)
-test_data$X <- as.character(test_data$X)
-
-names(retest_data)[1] <- 'sub_id'
-names(test_data)[1] <- 'sub_id'
+names(retest_data)[which(names(retest_data) == 'X')] <-'sub_id' 
+retest_data = retest_data[retest_data$sub_id %in% test_data$sub_id,]
 ```
@@
 Since HDDM parameters depend on the sample on which they are fit we refit the model on t1 data for the subjects that have t2 data.
-Here we replace the HDDM parameters in the current t1 dataset with these refitted values and transform them as they would have been transformed for the full sample to mimick the procedure we applied to rest of the t2 data.
-
-Transform hddm refits as they had been transformed for the full sample t1 data.
+Here we replace the HDDM parameters in the current t1 dataset with these refitted values.
+
 ```{r}
@@
 
+hddm_refits = hddm_refits[,names(hddm_refits) %in% retest_report_vars]
+
 hddm_refits$X <- as.character(hddm_refits$X)
-
-names(hddm_refits)[1] <- 'sub_id'
-
-hddm_logTr_vars = data.frame(grep('(?=.*hddm)(?=.*logTr)', names(retest_subs_test_data), value=T, perl=T))
-names(hddm_logTr_vars) = c('var')
-hddm_logTr_vars$sign = ifelse(grepl(".ReflogTr",hddm_logTr_vars$var), 'negative', 'positive')
-hddm_logTr_vars$var = gsub(".logTr|.ReflogTr", "", hddm_logTr_vars$var)
-
-transformed_hddm_refits = hddm_refits
-
-for(i in 1:length(names(transformed_hddm_refits))){
-  tmp_col = names(transformed_hddm_refits)[i]
-  if(tmp_col %in% hddm_logTr_vars$var){
-    sign = hddm_logTr_vars$sign[which(tmp_col == hddm_logTr_vars$var)]
-      if(sign == 'positive'){
-        # clean_retest_data[,tmp_col] = log(clean_retest_data[,tmp_col])
-        transformed_hddm_refits[,tmp_col] = pos_log(transformed_hddm_refits[,tmp_col])
-        names(transformed_hddm_refits)[which(names(transformed_hddm_refits) == tmp_col)] = paste0(tmp_col, '.logTr')
-        cat(paste0(tmp_col ,' was positively skewed and transformed.'))
-        cat('\n')
-      }
-      else if(sign == 'negative'){
-        transformed_hddm_refits[,tmp_col] = neg_log(transformed_hddm_refits[,tmp_col])
-        names(transformed_hddm_refits)[which(names(transformed_hddm_refits) == tmp_col)] = paste0(tmp_col, '.ReflogTr')
-        cat(paste0(tmp_col ,' was negatively skewed and transformed.'))
-        cat('\n')
-      }
-    }
-}
-```
-
-Check if transformation of hddm refits worked
-```{r}
-transform_hddm_logTr_vars = data.frame(grep('logTr', names(transformed_hddm_refits), value=T))
-names(transform_hddm_logTr_vars) = c('var')
-transform_hddm_logTr_vars$sign = ifelse(grepl(".ReflogTr",transform_hddm_logTr_vars$var), 'negative', 'positive')
-transform_hddm_logTr_vars$var = gsub(".logTr|.ReflogTr", "", transform_hddm_logTr_vars$var)
-transform_hddm_logTr_vars = transform_hddm_logTr_vars %>% arrange(var)
-hddm_logTr_vars = hddm_logTr_vars %>% arrange(var)
-transform_hddm_logTr_vars == hddm_logTr_vars
-```
-
-Replace t1 hddm parameters for retest subjects
-
-```{r}
-replace_hddm_vars = data.frame(grep('(?=.*hddm)(?=.*logTr)', names(retest_subs_test_data), value=T, perl=T))
-names(replace_hddm_vars) = c('var')
-
-hddm_fix_retest_subs_test_data = retest_subs_test_data
-
-for(i in 1:length(names(hddm_fix_retest_subs_test_data))){
-  if(names(hddm_fix_retest_subs_test_data)[i] %in% replace_hddm_vars$var){
-    hddm_fix_retest_subs_test_data[,names(hddm_fix_retest_subs_test_data)[i]] <- transformed_hddm_refits[,names(hddm_fix_retest_subs_test_data)[i]]
-  }
-}
-
-retest_subs_test_data <- hddm_fix_retest_subs_test_data
-```
-
-```{r}
-rm(hddm_refits, transformed_hddm_refits, hddm_logTr_vars, transform_hddm_logTr_vars, replace_hddm_vars, hddm_fix_retest_subs_test_data, sign, i)
+names(hddm_refits)[which(names(hddm_refits) == 'X')] <-'sub_id'
+
+test_data = cbind(test_data$sub_id, test_data[,names(test_data) %in% names(hddm_refits) == FALSE])
+
+names(test_data)[which(names(test_data) == 'test_data$sub_id')] <-'sub_id'
+
+test_data = merge(test_data, hddm_refits, by="sub_id")
 ```
@@
 
-match_t1_t2 <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', format = "long", sample = 'full', sample_vec){
+match_t1_t2 <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', format = "long", sample = 'full', sample_vec){
 
@@
 
-get_spearman = function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+get_spearman = function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
 
@@
 
-get_icc <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+get_icc <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
   if(sample=='full'){
@@
 
-get_var_breakdown <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+get_pearson = function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+
+  if(sample=='full'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
+  }
+  else if(sample=='bootstrap'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
+  }
+
+  rho = cor(df$`1`, df$`2`, method='pearson')
+
+  return(rho)
+}
+
+get_var_breakdown <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
   if(sample=='full'){
@@
 
-get_eta <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+get_eta <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
   if(sample=='full'){
@@
 
-get_sem <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+get_sem <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
   if(sample=='full'){
@@
                      icc = rep(NA, length(numeric_cols)),
+                     pearson = rep(NA, length(numeric_cols)),
                      eta_sq = rep(NA, length(numeric_cols)),
@@
   rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
+  rel_df[numeric_cols[i], 'pearson'] <- get_pearson(numeric_cols[i])
   rel_df[numeric_cols[i], 'eta_sq'] <- get_eta(numeric_cols[i])
@@
 rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
+rel_df[grep('holt', rel_df$dv), 'task'] = "task"
 rel_df = rel_df %>%
-  select(dv, task, spearman, icc, eta_sq, sem, var_subs, var_ind, var_resid)
+  select(dv, task, spearman, icc, pearson, eta_sq, sem, var_subs, var_ind, var_resid)
 # row.names(rel_df) = NULL
@@
             median_icc = median(icc),
+            median_pearson = median(pearson),
             median_eta_sq = median(eta_sq),
@@
   datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc', 'median_eta_sq', 'median_sem'), digits=3)
-```
-
-*Rank orders for reliabilities*
-
-- Note that this table can be sorted by different metrics, filtered for specific values for each column and is searchable.  
-- Demographics are excluded from this list of variables (because they are saved for predictive analyses).  
-- Holt and Laury test-retest is the worst for *surveys*.
-But note that this is not a survey that has been studied extensively psychometrically like others.
-This is more similar to our tasks (one that is used more often by economists).
-In previous data I have worked with retest reliablities for this task was ~.35 so the results here are in line with this.
-- Otherwise the lowest survey reliabilities are 0.5.
+  formatRound(columns=c('median_spearman', 'median_icc', 'median_pearson','median_eta_sq', 'median_sem'), digits=3)
+```
+
+**Table of reliability point estimates**
 
@@
   datatable(filter='top') %>%
-  formatRound(columns=c('spearman', 'icc', 'eta_sq', 'sem'), digits=3)
+  formatRound(columns=c('spearman', 'icc', 'pearson','eta_sq', 'sem'), digits=3)
 ```
@@
 
-```{r echo=FALSE}
-#Convenience functions to make prettier interactive histograms
-get_labels = function(plot_df, ref_df, bin_col, group_col){
-
-  plot_df$bin = as.numeric(factor(plot_df$x))
-  ref_df$bin = NA
-
-  for(i in 1:nrow(ref_df)){
-    for(j in 1:nrow(plot_df)){
-      # if(ref_df[i, bin_col] <= plot_df$xmax[j] & ref_df[i, bin_col]>=plot_df$xmin[j] & all(ref_df[i, group_col] == plot_df[j, group_col])){
-      if(ref_df[i, bin_col] <= plot_df$xmax[j] & ref_df[i, bin_col]>=plot_df$xmin[j] & ref_df[i, group_col] == plot_df[j, group_col]){
-        ref_df$bin[i] <- plot_df$bin[j]
-      }
-    }
-  }
-
-  ref_df = ref_df %>% 
-    group_by_("bin", group_col) %>%
-    mutate(label=as.character(toJSON(unique(dv))))
-
-  label_df = ref_df[!duplicated(ref_df[,c('label')]),c(group_col, 'bin', 'label')]
-
-  out_df = left_join(plot_df,label_df, by= c("bin", group_col))
-
-  return(out_df)
-}
-
-line_break <- function(cell){
-  out = paste(unlist(strsplit(gsub("\\]","",gsub("\\[","",cell)), ",")), sep="\n", collapse = "</br>")
-  return(out)
-}
-
-prettify_label = function(df){
-  for(i in 1:nrow(df)){
-    df$label[i] =line_break(df$label[i])
-  }
-  return(df)
-}
-```
-
-### Spearman
-
-```{r warning=FALSE, message=FALSE}
-ggplotly(ggplot_build(rel_df %>%
-                        ggplot(aes(spearman, fill=task)) +
-                        geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
-           mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
-           get_labels(.,rel_df, "spearman", "task") %>%
-           prettify_label(.) %>%
-           ggplot(aes(x,y, fill=task, label=label))+
-           geom_bar(stat='identity', position='identity', alpha=0.5)+
-           xlab('Spearman')+
-           ylab('Count')+
-           theme_bw(),
-         tooltip = 'label',
-         hoverinfo = 'text')
-```
-
-### ICC
-
-```{r warning=FALSE, message=FALSE}
-ggplotly(ggplot_build(rel_df %>%
-                        ggplot(aes(icc, fill=task)) +
-                        geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
-           mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
-           get_labels(.,rel_df, "icc", "task") %>%
-           prettify_label(.) %>%
-           ggplot(aes(x,y, fill=task, label=label))+
-           geom_bar(stat='identity', position='identity', alpha=0.5)+
-           xlab('ICC')+
-           ylab('Count')+
-           theme_bw(),
-         tooltip = 'label',
-         hoverinfo = 'text')
-```
-
-### Partial $\eta^2$
-
-Tooltip might not work well for this graph for the highest bar because the label is too large.
-But this bar indicates measures where the effect of time is very small anyway.
-We might want to pay closer attention to those not in this lowest bar since those are the variables where there is a non-negligible effect of time, indicating either a learning effect or other kind of systematic change that we did not hypothesize to observe with any of these measures.
-
-```{r warning=FALSE, message=FALSE}
-ggplotly(ggplot_build(rel_df %>%
-                        ggplot(aes(eta_sq, fill=task)) +
-                        geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
-           mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
-           get_labels(.,rel_df, "eta_sq", "task") %>%
-           prettify_label(.) %>%
-           ggplot(aes(x,y, fill=task, label=label))+
-           geom_bar(stat='identity', position='identity', alpha=0.5)+
-           xlab('Partial Eta Squared')+
-           ylab('Count')+
-           theme_bw(),
-         tooltip = 'label',
-         hoverinfo = 'text')
-```
-
-#### Effect of time
-
-So what variables show a non-negligible effect of time and in what direction? (sorted by increasing partial $\eta^2$)
-
-```{r warning=FALSE, message=FALSE}
-time_effect_vars = ggplot_build(rel_df %>%
-               ggplot(aes(eta_sq, fill=task)) +
-               geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
-  mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
-  get_labels(.,rel_df, "eta_sq", "task") %>%
-  prettify_label(.) %>%
-  filter(bin != 1 & bin !=2 & label != "NA") %>%
-  select(label, task) %>%
-  separate(label,into=c(as.character(1:27)),sep = "</br>") %>%
-  gather(key, value, -task) %>%
-  select(value, task) %>%
-  na.omit()
-
-time_effect_vars$value = gsub("\"", "", time_effect_vars$value)
-datatable(time_effect_vars)
-```
-
-Box plots showing the distributions of difference scores between the measurements at two time points for each measure can be found under the [Completion times](#diff_plot) section.
-
-### SEM
-
-```{r warning=FALSE, message=FALSE}
-ggplotly(ggplot_build(rel_df %>%
-                        ggplot(aes(sem, fill=task)) +
-                        geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
-           mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
-           get_labels(.,rel_df, "sem", "task") %>%
-           prettify_label(.) %>%
-           ggplot(aes(x,y, fill=task, label=label))+
-           geom_bar(stat='identity', position='identity', alpha=0.5)+
-           xlab('SEM')+
-           ylab('Count')+
-           theme_bw(),
-         tooltip = 'label',
-         hoverinfo = 'text')
-```
-
-### Negative icc's?
-```{r}
-neg_icc_vars = rel_df %>%
-  arrange(icc) %>% 
-  filter(icc<0) %>%
-  select(dv)
-```
-
-Some variables (`r neg_icc_vars$dv`) have <0 ICC's. This would be the case if the $MS_{error}$>$MS_{between}$.
-
-Plot data for measures with negative ICC.  
-x-axis is time 1 data and y-axis is time 2 data. The scatter plots show that the scores for measures with negative ICC's have no relationship across time points.
-```{r, fig.height=12, fig.width=12}
-tmp = data.frame()
-
-for(i in 1:nrow(neg_icc_vars)){
-  tmp = rbind(tmp, match_t1_t2(neg_icc_vars$dv[i]))
-}
-rm(neg_icc_vars)
-
-tmp %>%
-  spread(time, score) %>%
-  # mutate(dv_wrap = str_wrap(dv, width = 30)) %>%
-  ggplot(aes(`1`, `2`))+
+```{r warning=FALSE, message=FALSE}
+rel_df %>%
+  select(dv, task, spearman, pearson, icc) %>%
+  gather(key, value, -dv, -task) %>%
+  ggplot(aes(value, fill=task))+
+  geom_histogram(alpha = 0.5, position = 'identity')+
+  facet_wrap(~key)+
+  theme_bw()+
+  theme(legend.position = 'bottom',
+        legend.title = element_blank())+
+  xlab("")
+```
+
+Task measures have significanlty lower reliability (here checking only on point estimates of ICC).
+
+```{r}
+summary(lm(icc~task, rel_df))
+```
+
+### Relationship between reliability metrics
+
+```{r warning=FALSE, message=FALSE}
+p1 = rel_df %>%
+  ggplot(aes(spearman, icc, col=task))+
   geom_point()+
   theme_bw()+
-  facet_wrap(~dv, scales='free', labeller = label_wrap_gen())
-
-```
-
-This point is clarified further by compare these scatter plots to those of variables with highest ICC. These variables have strong and clear positive linear relationships.
-
-```{r fig.height=12, fig.width=12}
-high_icc_vars = rel_df %>%
-  arrange(-icc)  %>% 
-  filter(icc>0.92) %>%
-  select(dv)
-
-tmp = data.frame()
-
-for(i in 1:nrow(high_icc_vars)){
-  tmp = rbind(tmp, match_t1_t2(high_icc_vars$dv[i]))
-}
-rm(high_icc_vars)
-
-tmp %>%
-  spread(time, score) %>%
-  ggplot(aes(`1`, `2`))+
+  theme(legend.title = element_blank(),
+        legend.position = "none")+
+  geom_abline(intercept = 0, slope=1)
+
+p2 = rel_df %>%
+  ggplot(aes(pearson, icc, col=task))+
   geom_point()+
   theme_bw()+
-  facet_wrap(~dv, scales='free')
-
-```
-
-```{r echo=FALSE}
-rm(tmp)
-```
-
-### Relationship between ICC and Spearman
-These two measures give mostly similar answers regarding the reliabilities of the measures except for
-
-```{r}
-ggplotly(rel_df %>%
-           ggplot(aes(spearman, icc, col=task, label=dv, label2=eta_sq))+
+  theme(legend.title = element_blank(),
+        legend.position = "none")+
+  geom_abline(intercept = 0, slope=1)
+
+p3 = rel_df %>%
+  ggplot(aes(pearson, spearman, col=task))+
   geom_point()+
   theme_bw()+
-           theme(legend.title = element_blank())+
-           geom_abline(intercept = 0, slope=1))
-```
-
-What are the variables clustered around 0 ICC?
-
-```{r}
-rel_df %>%
-  filter(icc>(-0.1), icc<0.1) %>%
-  arrange(icc) %>%
-  datatable() %>%
-  formatRound(columns=c('spearman', 'icc', 'eta_sq', 'sem'), digits=3)
-```
-
-### Relationship between ICC and $\eta^2$
-
-```{r}
-ggplotly(rel_df %>%
-  ggplot(aes(eta_sq, icc, col=task, label=dv))+
-  geom_point()+
-  theme_bw()+
-  theme(legend.title = element_blank()))
-```
-
-## Reliability by measure types
-
-The results presented so far aim to be comprehensive but are difficult to parse through and get a clear sense of what is going on (other than a general impression that surveys tend to have higher reliabilities than tasks).
-In this and the following section we try to deal with this in two ways to make the results more digestable with two kinds of categorizations.
-
-### Tasks
-
-We aim to make contact with the literature to make the results more accesible to readers who have experience with our tasks but do not want to   
-1. take away from the novelty of the main papers coming out of this project outlining the factor structure that this data unveils   
-2. necessarily make prescriptive recommendations or theoretical arguments on why certain measures of certain processes are more reliable than others.
-
-With this in mind we reduce the list of over 270 task measures to a list of one per task by averaging only the raw measures from all the trials in a task.
+  theme(legend.title = element_blank(),
+        legend.position = "none")+
+  geom_abline(intercept = 0, slope=1)
+
+grid.arrange(p1, p2, p3, nrow=1)
+```
+
+```{r echo=FALSE}
+rm(p1,p2,p3)
+```
+
+Note: Some variables have <0 ICC's. This would be the case if the $MS_{error}$>$MS_{between}$. Data for these variables have no relationship between the two time points.
+
+## Task Reliabilities
+
+Here we summarize the results on a task level to make it more digestable and easier to make contact with the literature.
+
+With this in mind we reduce the list of task measures to a list of one per task by averaging only the raw measures from all the trials in a task.
 We chose to reduce the information in this manner to avoid any bias stemming from differential amount of interest and procedures applied to certain tasks over others (e.g.
@@
 
-We plan to supplement/potentially replace this with an additional labeling procedure intending to capture the underlying putative cognitive processes but are deferring this until at least for another week.
-This exercise might not even prove helpful but at least a per task summary seemed a reasonable first pass.
-
 ```{r echo=FALSE}
-measure_labels <- read.csv('/Users/zeynepenkavi/Downloads/retest_measure_labels.csv')
-measure_labels = measure_labels %>% select(-Patrick_hates)
-
-trim <- function (x) gsub("^\\s+|\\s+$", "", x)
+measure_labels <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/measure_labels.csv')
+measure_labels = measure_labels %>% select(-measure_description,-measure_type,-measure_type_Ian,-measure_type_Russ,-notes,-Patrick_hates)
 ```
@@
   filter(task == 'task') %>%
-  select(-measure_description, -notes, -measure_type, -task, -ddm_task) %>%
   left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
@@
 
-Does number of items in a task have a significant effect on the average ICC of (mostly) raw measures for all trials from a task? No.
+Does number of items in a task have a significant effect on the average ICC of (mostly) raw measures for all trials from a task? No. (no effect on Spearman either)
 
@@
 
-Does number of items in a task have a significant effect on the average Spearman $\rho$ of (mostly) raw measures for all trials from a task? No.
-
-```{r warning=FALSE, message=FALSE}
-summary(lm(median_spearman ~ num_trials, data = tmp))
-```
-
-Does number of measures that went in to this reliability estimate have a significant effect on the average ICC of (mostly) raw measures for all trials from a task?
-It seems the more measures that goes in to summarizing overall reliability for a task the worse it gets.
-This would make sense if these variables are intended to measure different things and some are less reliable than others.
+Does number of measures that went in to this reliability estimate have a significant effect on the average ICC of (mostly) raw measures for all trials from a task? No. (same is true for Spearman)
 
@@
 ```
-
-Does number of measures that went in to this reliability estimate have a significant effect on the average ICC of (mostly) raw measures for all trials from a task?  
-The same is true for Spearman's correlations as well.
-
-```{r warning=FALSE, message=FALSE}
-summary(lm(median_spearman ~ num_measures, data = tmp))
-```
-
-In addition to average relilibilities for each task we can look at relilibities of measures organized by the putative cognitive process they are intended to measure.
-Note however that these labels are not determined in a data driven manner.
-
-```{r warning=FALSE, message=FALSE}
-measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  select(-measure_description, -notes, -variable_type, -task, -ddm_task) %>%
-  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  group_by(measure_type) %>%
-  summarise(median_icc = median(icc),
-            median_spearman = median(spearman),
-            num_measures = n()) %>%
-  arrange(-median_icc, -median_spearman) %>%
-  datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
-```
-
-Here is what the distributions look like.  
-- Alerting: This labels consists only of ANT alerting contrast (no cue - double cue trials). 4/6 are drift diffusion parameters.    
-- Cue encoding: This label consists only of three by two task switch cost contrast (stay (where cue and task remains the same) - switch (where task is the same but cue changes) trials).
-Again most are drift diffusion parameters.
-- Delay discounting: This label consists of the discount rates for the Bickel titrator (3), Kirby items (3) and discount titrate (model fit to random set of stimuli).
-**Does the discrepancy between ICC and Spearman for these measures, given the specific interest in these tasks in the literature warrant a more detailed look in to these?**
-- Information use: This label includes Columbia Card Task (both versions) and information sampling task.  
-- Inhibition: This label includes go no-go, motor selective stop signal, stimulus selective stop signal and regular stop signal (excluding specific constrasts).  
-- Intelligence: This label includes ravens and tower of london.  
-- Learning: This label includes ART, CCT, two stage decision, dietary decision task, hierarchical rule task, information sampling task, probabilistic selection task, shift task, two stage task.   
-- Neutral writing: This label consists only of the writing task.  
-- Orienting: This labels consists only of ANT orienting contrast (center - spatial cue trials). 4/6 are drift diffusion parameters.   
-- Positive writing: This label consists only of the writing task.  
-- Proactive control: This labels consists of one DPX contrast (AY - BY trials), motor selective stop signal and regular stop signal.   
-- Reactive control: This labels consists of one DPX contrast (BX - BY trials) and motor selective stop signal.  
-- Resisting proactive interference: This label consists of one contrast in directed forgetting and recent probes tasks (negative (where the stimulus to respond to is in forgetting set) and control (where the stimulus to respond to is new) trials).
-- Response conflict: This label consists of ANT conflict contrast (congruent-incongruent), DPX, local global conflict contrast, shape matching, simon, stroop.  
-- Response selection: This label consists of choice reaction time task.  
-- Risk Taking: This label consists of ART and CCT.  
-- Selective attention: This label consists of local global task and ANT (all trials).  
-- Set shifting: This label consists of local global, PRT and three by two.    
-- Speed: This label consists of raw response times in information sampling task, simple reaction time, tower of london.  
-- Working memory: This label consists of adaptive n back, digit span, directed forgetting, keep track, recent probes, spatial span.
-
-```{r warning=FALSE, message=FALSE, fig.width=12, fig.height=10}
-measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  select(-measure_description, -notes, -variable_type, -task, -ddm_task) %>%
-  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  select(measure_type, icc, spearman) %>%
-  gather(key, value, -measure_type) %>%
-  ggplot(aes(value, fill=key))+
-  geom_histogram(position='identity', alpha=0.5)+
-  theme_bw()+
-  facet_wrap(~measure_type)+
-  theme(legend.title = element_blank())
-```
-
-### Surveys
-
-To be filled with factor labels after processing either ASU factor analyses or Russ' MIRT?
 
@@
   filter(task == 'task') %>%
-  select(-measure_description, -notes, -measure_type, -task) %>%
   left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
@@
 - All parameters that were fit to all trials compared to contrasts have higher relialibilities.   
-- Raw variables are not the variables with highest ICC's overall. Raw response times do, however, have the highest Spearman's $\rho$'s on average. 
-- 2 of 3 hddm parameters also have higher mean reliabilities than EZ parameter estimates.
+- Raw variables are not the variables with highest ICC's overall supporting the idea of using these parameters as individual difference variables that are more interpretable.
 
@@
 
-```{r}
-tmp %>%
-  group_by(label_1,label_2, label_3) %>%
-  summarise(mean_icc = mean(icc),
-            mean_spearman = mean(spearman),
-            n_vars = n()) %>%
-  arrange(-mean_icc, -mean_spearman) %>%
-  datatable() %>%
-  formatRound(columns=c('mean_spearman', 'mean_icc'), digits=3)
-```
-
 Are these differences meaningful?
@@
 ```
-
-### Surveys
-
-Would this be a comparison of factor reliability versus item reliability?
 
@@
 
-## Transformation effects
-
-```{r}
-raw_retest_subs_test_data = raw_test_data[raw_test_data$sub_id %in% raw_retest_data$sub_id,]
-
-raw_numeric_cols = c()
-
-for(i in 1:length(names(raw_test_data))){
-  if(is.numeric(raw_test_data[,i])){
-    raw_numeric_cols <- c(raw_numeric_cols, names(raw_test_data)[i])
-  }
-}
-
-raw_rel_df <- data.frame(spearman = rep(NA, length(raw_numeric_cols)),
-                     icc = rep(NA, length(raw_numeric_cols)), 
-                     eta_sq = rep(NA, length(raw_numeric_cols)),
-                     sem = rep(NA, length(raw_numeric_cols)))
-
-row.names(raw_rel_df) <- raw_numeric_cols
-
-for(i in 1:length(raw_numeric_cols)){
-  raw_rel_df[raw_numeric_cols[i], 'spearman'] <- get_spearman(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data) 
-  raw_rel_df[raw_numeric_cols[i], 'icc'] <- get_icc(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data)
-  raw_rel_df[raw_numeric_cols[i], 'eta_sq'] <- get_eta(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data)
-  raw_rel_df[raw_numeric_cols[i], 'sem'] <- get_sem(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data)
-}
-
-raw_rel_df$dv = row.names(raw_rel_df)
-row.names(raw_rel_df) = seq(1:nrow(raw_rel_df))
-raw_rel_df$task = 'task'
-raw_rel_df[grep('survey', raw_rel_df$dv), 'task'] = 'survey'
-raw_rel_df = raw_rel_df %>%
-  select(dv, task, spearman, icc, eta_sq, sem)
-```
-
-```{r warning=FALSE, message=FALSE}
-raw_rel_df %>%
-  group_by(task) %>%
-  summarise(median_spearman = median(spearman),
-            median_icc = median(icc),
-            median_eta_sq = median(eta_sq),
-            median_sem = median(sem),
-            num_vars = n()) %>%
-  datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc', 'median_eta_sq', 'median_sem'), digits=3)
-```
-
-Plots of change in reliability depending on transformation
-
-```{r}
-ggplotly(rel_df %>%
-  mutate(dv = gsub(".logTr", "", dv)) %>%
-  mutate(dv = gsub(".Re", "", dv)) %>%
-  left_join(raw_rel_df, by = 'dv') %>%
-  ggplot(aes(spearman.x, spearman.y, color = task.x, label=dv))+
-  geom_point()+
-  geom_abline(intercept = 0, slope=1)+
-  theme_bw()+
-  theme(legend.title = element_blank())+
-  xlab("Spearman with transformation")+
-  ylab("Spearman witouth transformation"))
-```
-
-```{r}
-ggplotly(rel_df %>%
-  mutate(dv = gsub(".logTr", "", dv)) %>%
-  mutate(dv = gsub(".Re", "", dv)) %>%
-  left_join(raw_rel_df, by = 'dv') %>%
-  ggplot(aes(icc.x, icc.y, color = task.x, label=dv))+
-  geom_point()+
-  geom_abline(intercept = 0, slope=1)+
-  theme_bw()+
-  theme(legend.title = element_blank())+
-  xlab("ICC with transformation")+
-  ylab("ICC without transformation"))
-```
-
 ## Bootstrapping
-
-```{r eval=FALSE, echo=FALSE}
-sample_workers = function(N = 150, repl= TRUE, df=retest_data, worker_col = "sub_id"){
-  return(sample(df[,worker_col], N, replace = repl))
-}
-
-bootstrap_relialibility = function(metric = c('icc', 'spearman', 'eta_sq', 'sem'), dv_var, N=150){
-  tmp_sample = sample_workers(N)
-  out_df = data.frame(dv = dv_var)
-  if('icc' %in% metric){
-    out_df$icc = get_icc(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
-  }
-  if('spearman' %in% metric){
-    out_df$spearman = get_spearman(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
-  }
-  if('eta_sq' %in% metric){
-    out_df$eta_sq = get_eta(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
-  }
-  if('sem' %in% metric){
-    out_df$sem = get_sem(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
-  }
-  return(out_df)
-}
-
-# Bootstrapping everything at once in this way locally would take around four hours.
-non_hddm_numeric_cols=numeric_cols[-grep("hddm", numeric_cols)]
-
-boot_df = as.data.frame(non_hddm_numeric_cols) %>%
-  mutate(index = 1:n()) %>%
-  group_by(index) %>%
-  do(plyr::rdply(10, bootstrap_relialibility(dv_var = as.character(.$non_hddm_numeric_cols))))
-
-boot_df
-```
 

### 2017-11-03 code/SRO_Retest_Interactive_Figures.Rmd
cont cleaning up report

--- 2017-05-02 SRO_Report.Rmd
@@
 ---
-title: 'Self Regulation Ontology Retest Data Report'
+title: 'SRO Retest Interactive Figures'
 output:
@@
 ---
+
+#################################
+NOT USED
+#################################
 
@@
 library(plotly)
-library(jsonlite)
 library(DT)
 sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
-render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Report', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)}
+render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
 options(scipen = 1, digits = 4)
 ```
-
-# Introduction
-
-# Methods
-
-## Data collection
-
-This sample consists of data for 150 subjects of the original sample of 522 that has completed the initial battery of 37 cognitive tasks, 23 surveys and 3 surveys on demographics.
-Details of the original sample as well as quality control (qc) procedures are described elsewhere.
-Invited participants were chosen randomly and only subsets of them were invited for a given batch (instead of opening the battery to all qualified subjects) with the intention to avoid a potential oversampling and bias towards "high self regulators".
-
-```{r warning=FALSE, message=FALSE}
-workers = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/User_717570_workers.csv')
-workers = workers %>% 
-  group_by(Worker.ID) %>%
-  mutate(Retest_worker=ifelse(sum(CURRENT.RetestWorker,CURRENT.RetestWorkerB2,CURRENT.RetestWorkerB3,CURRENT.RetestWorkerB4,CURRENT.RetestWorkerB5,na.rm=T)>0,1,0)) %>%
-  ungroup()
-
-worker_counts <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/retest_worker_counts.json')
-
-worker_counts = as.data.frame(unlist(worker_counts))
-names(worker_counts) = "task_count"
-```
-
-In total `r sum(workers$Retest_worker)` participants were invited, `r nrow(worker_counts)` began the battery, `r sum(worker_counts$task_count >= 62)` completed the battery and 150 provided data that passed qc for both time points.
-Our target sample size was determined in advance of data collection and data collection continued until this number of participants with data that survived qc was reached.
-
-```{r warning=FALSE, message=FALSE}
-disc_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/discovery_completion_dates.csv', header=FALSE)
-val_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/validation_completion_dates.csv', header=FALSE)
-test_comp_date = rbind(disc_comp_date, val_comp_date)
-rm(disc_comp_date, val_comp_date)
-retest_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/retest_completion_dates.csv', header=FALSE)
-comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
-names(comp_dates) <- c("sub_id", "retest_comp", "test_comp")
-comp_dates$retest_comp = as.Date(comp_dates$retest_comp)
-comp_dates$test_comp = as.Date(comp_dates$test_comp)
-comp_dates$days_btw = with(comp_dates, retest_comp-test_comp)
-```
-
-Data collection took place on average `r round(mean(as.numeric(comp_dates$days_btw)))` number of days after the completion of the initial battery with a range of `r round(range(as.numeric(comp_dates$days_btw)))[1]` to `r round(range(as.numeric(comp_dates$days_btw)))[2]` days.
-
-## Literature
-
-### Tasks
-
-### Surveys
-
-## Loading and matching datasets
-
-This report uses the variables that were designated as "meaningful" before.
-This is not the smallest subset where certain variables are dropped because they are correlated with other variables (within a task) and includes both accuracies as well as both kinds of DDM variables (EZ and HDDM).
-It will not include variables that were considered not of theoretical interest in the analyses of time 1 data.
-The variables that are not included will be listed for reference as well.
-
-### Load time 1 data
-```{r}
-test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables.csv')
-
-test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_noDDM.csv')
-
-test_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_EZ.csv')
-
-test_data <- merge(test_data, test_data2)
-test_data <- merge(test_data, test_data3)
-rm(test_data2, test_data3)
-```
-
-For reference here are the variables that are **not** included in the analyses of the remainder of this report because they were not of theoretical interest in factor structure analyses of this data so far.
-These include drift diffusion and other model parameters for specific conditions within a task; survey variables that are not part of the dependant variables for that survey in the literature and demographics (these are saved for prediction analyses).
-
-```{r}
-test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/variables_exhaustive.csv')
-
-test_data2$X <- as.character(test_data2$X)
-
-names(test_data2)[1] <- 'sub_id'
-
-df <- data.frame(names(test_data2)[which(names(test_data2) %in% names(test_data) == FALSE)])
-names(df) = c('vars')
-
-datatable(df)
-```
-
-```{r echo=FALSE}
-rm(test_data2, df)
-```
-
-### Load time 2 data 
-```{r}
-retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/meaningful_variables.csv')
-
-retest_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/meaningful_variables_noDDM.csv')
-
-retest_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/meaningful_variables_EZ.csv')
-
-retest_data <- merge(retest_data, retest_data2)
-retest_data <- merge(retest_data, retest_data3)
-rm(retest_data2, retest_data3)
-```
-
-Extract t2 participants with good t1 data: We only invited those with good data but due to a technical error a handful of subjects who weren't checked for data quality completed the retest battery as well.
-One of those subjects gave good t2 data but didn't have good t1 data and therefore is removed from further analyses.
-
-```{r}
-#Process sub_id columns in the data dataframes
-retest_data$X <- as.character(retest_data$X)
-test_data$X <- as.character(test_data$X)
-
-names(retest_data)[1] <- 'sub_id'
-names(test_data)[1] <- 'sub_id'
-
-retest_data <- retest_data[retest_data$sub_id %in% test_data$sub_id,]
-```
-
-### Clean t1 data
-
-The cleaning functions here are translated from the python pipeline to mimick the same procedure that was applied to the `meaningful_variables` in creating `meaningful_variables_clean`.
-
-The original cleaning procedures include three steps:  
-1.
-Removing outliers for each variable where outliers are defined as those who are greater than 2.5 IQR from median.
-**This step is skipped here because removing outliers from either dataset could lead to an unnecessary increase in missing data.
-Since we are interested in the average distance between two measures of a metric for a given subject instead of the distance between all these metrics this seemed appropriate.**
-2.
-Removing correlated variables *within* a task.
-In creating `meaningful_variables_clean` if variables for a given task correlated >.85 only one was kept.
-**This step is skipped here because we want to look at the reliability of as many variables as we can.**
-3.
-Log transforming variables with skew.
-In cleaning t1 data variables that had a |skew| > 1 were log transformed and those for which skew could not be removed successfully were dropped.
-**Here we transform all variables that have a |skew|>1 in t1 data but variables that are not successfully transformed will be listed and not dropped.**
-
-```{r}
-remove_outliers = function(data_column, quantile_range = 2.5){
-
-  q_25 = quantile(data_column, na.rm=T)[2]
-  q_50 = quantile(data_column, na.rm=T)[3]
-  q_75 = quantile(data_column, na.rm=T)[4]
-
-  lowlimit = q_50 - quantile_range*(q_75 - q_25)
-  highlimit = q_50 + quantile_range*(q_75 - q_25)
-
-  data_column = ifelse(data_column<lowlimit, NA, ifelse(data_column>highlimit, NA, data_column))
-
-  return(data_column)
-}
-
-"%w/o%" <- function(x, y) x[!x %in% y]
-
-pos_log <- function(column){
-  col_min = min(column, na.rm=T)
-  a = 1-col_min
-  column = column+a
-  return(log(column))
-}
-
-neg_log <- function(column){
-  col_max = max(column, na.rm=T)
-  column = col_max+1-column
-  return(log(column))
-}
-
-transform_remove_skew = function(data, columns, threshold = 1, drop=FALSE){
-
-  tmp = as.data.frame(apply(data[,columns],2,skew))
-  names(tmp) = c("skew")
-  tmp$dv = row.names(tmp)
-  tmp = tmp %>% 
-    filter(abs(skew)>threshold)
-
-  skewed_variables = tmp$dv
-  skew_subset = data[, skewed_variables]
-  positive_subset = data[,tmp$dv[tmp$skew>0]]
-  negative_subset = data[,tmp$dv[tmp$skew<0]]
-
-  # transform variables
-  # log transform for positive skew
-  # positive_subset = log(positive_subset)
-  # positive_subset = pos_log(positive_subset) #slight divergence from original code
-  positive_subset = as.data.frame(apply(positive_subset, 2, pos_log))
-  successful_transforms = as.data.frame(apply(positive_subset, 2, skew))
-  names(successful_transforms) = c('skew')
-  successful_transforms$dv = row.names(successful_transforms)
-  successful_transforms = successful_transforms %>% filter(abs(skew)<threshold)
-  successful_transforms = successful_transforms$dv
-  successful_transforms = positive_subset[,successful_transforms]
-  dropped_vars = names(positive_subset) %w/o% names(successful_transforms)
-
-  cat(rep('*', 40))
-  cat('\n')
-  cat(paste0(length(names(positive_subset)) ,' data positively skewed data were transformed:'))
-  cat('\n')
-  cat(names(positive_subset), sep = '\n')
-  cat(rep('*', 40))
-  cat('\n')
-
-  # replace transformed variables
-  data = data[,-c(which(names(data) %in% names(positive_subset)))]
-
-  if(drop == TRUE){
-    names(successful_transforms) = paste0(names(successful_transforms), '.logTr')
-    cat(rep('*', 40))
-    cat('\n')
-    cat(paste0('Dropping ', length(dropped_vars) ,' positively skewed data that could not be transformed successfully:'))
-    cat('\n')
-    cat(dropped_vars, sep = '\n')
-    cat(rep('*', 40))
-    cat('\n')
-    data = cbind(data, successful_transforms)
-  }
-  else{
-    names(positive_subset) = paste0(names(positive_subset), '.logTr')
-    cat(rep('*', 40))
-    cat('\n')
-    cat(paste0(length(dropped_vars) ,' positively skewed data could not be transformed successfully:'))
-    cat('\n')
-    cat(dropped_vars, sep = '\n')
-    cat(rep('*', 40))
-    cat('\n')
-    data = cbind(data, positive_subset)
-  }
-
-  # reflected log transform for negative skew      
-  negative_subset = as.data.frame(apply(negative_subset, 2, neg_log))
-  successful_transforms = as.data.frame(apply(negative_subset, 2, skew))
-  names(successful_transforms) = c('skew')
-  successful_transforms$dv = row.names(successful_transforms)
-  successful_transforms = successful_transforms %>% filter(abs(skew)<1)
-  successful_transforms = successful_transforms$dv
-  successful_transforms = negative_subset[,successful_transforms]
-  dropped_vars = names(negative_subset) %w/o% names(successful_transforms)
-
-  cat(rep('*', 40))
-  cat('\n')
-  cat(paste0(length(names(negative_subset)) ,' data negatively skewed data were transformed:'))
-  cat('\n')
-  cat(names(negative_subset), sep = '\n')
-  cat(rep('*', 40))
-  cat('\n')
-
-  # replace transformed variables
-  data = data[,-c(which(names(data) %in% names(negative_subset)))]
-  if(drop == TRUE){
-    names(successful_transforms) = paste0(names(successful_transforms), '.ReflogTr')
-    cat(rep('*', 40))
-    cat('\n')
-    cat(paste0('Dropping ', length(dropped_vars) ,' negatively skewed data that could not be transformed successfully:'))
-    cat('\n')
-    cat(dropped_vars, sep = '\n')
-    cat(rep('*', 40))
-    cat('\n')
-    data = cbind(data, successful_transforms)
-  }
-  else{
-    names(negative_subset) = paste0(names(negative_subset), '.ReflogTr')
-    cat(rep('*', 40))
-    cat('\n')
-    cat(paste0(length(dropped_vars) ,' negatively skewed data could not be transformed successfully:'))
-    cat('\n')
-    cat(dropped_vars, sep = '\n')
-    cat(rep('*', 40))
-    cat('\n')
-    data = cbind(data, negative_subset)
-  }
-
-  return(data)
-}
-```
-
-Clean t1 data on full sample without dropping any columns. Columns that are not transformed successfully are listed.
-
-```{r warning=FALSE}
-numeric_cols = c()
-
-for(i in 1:length(names(test_data))){
-  if(is.numeric(test_data[,i])){
-    numeric_cols <- c(numeric_cols, names(test_data)[i])
-  }
-}
-
-# clean_test_data = cbind(sub_id = test_data$sub_id, as.data.frame(apply(test_data[, -which(names(test_data) %in% c("sub_id"))], 2, remove_outliers)))
-
-# clean_test_data = transform_remove_skew(clean_test_data, numeric_cols)
-clean_test_data = transform_remove_skew(test_data, numeric_cols)
-```
-
-```{r echo=FALSE}
-rm(i)
-```
-
-### Clean t2 data
-
-Instead of applying the same functions applied to t1 data we check which variables are transformed in what way and transform the t2 data the same way.
-Again we are not removing outliers in the t2 or dropping variables if the skew is not removed successfully after transforming.
-
-Get list of transformed variables and the sign of their skew
-```{r}
-logTr_vars = data.frame(grep('logTr', names(clean_test_data), value=T))
-names(logTr_vars) = c('var')
-logTr_vars$sign = ifelse(grepl(".ReflogTr",logTr_vars$var), 'negative', 'positive')
-logTr_vars$var = gsub(".logTr|.ReflogTr", "", logTr_vars$var)
-```
-
-Transform the t2 columns the same way t1 columns were transformed.
-
-```{r warning=FALSE}
-clean_retest_data = retest_data
-
-for(i in 1:length(names(clean_retest_data))){
-  tmp_col = names(clean_retest_data)[i]
-  if(tmp_col %in% logTr_vars$var){
-    sign = logTr_vars$sign[which(tmp_col == logTr_vars$var)]
-      if(sign == 'positive'){
-        # clean_retest_data[,tmp_col] = log(clean_retest_data[,tmp_col])
-        clean_retest_data[,tmp_col] = pos_log(clean_retest_data[,tmp_col])
-        names(clean_retest_data)[which(names(clean_retest_data) == tmp_col)] = paste0(tmp_col, '.logTr')
-        cat(paste0(tmp_col ,' was positively skewed and transformed.'))
-        cat('\n')
-      }
-      else if(sign == 'negative'){
-        clean_retest_data[,tmp_col] = neg_log(clean_retest_data[,tmp_col])
-        names(clean_retest_data)[which(names(clean_retest_data) == tmp_col)] = paste0(tmp_col, '.ReflogTr')
-        cat(paste0(tmp_col ,' was negatively skewed and transformed.'))
-        cat('\n')
-      }
-    }
-}
-```
-
-```{r echo = FALSE}
-rm(i, sign, tmp_col)
-```
-
-Check transformations are correct
-```{r}
-retest_logTr_vars = data.frame(grep('logTr', names(clean_retest_data), value=T))
-names(retest_logTr_vars) = c('var')
-retest_logTr_vars$sign = ifelse(grepl(".ReflogTr",retest_logTr_vars$var), 'negative', 'positive')
-retest_logTr_vars$var = gsub(".logTr|.ReflogTr", "", retest_logTr_vars$var)
-retest_logTr_vars = retest_logTr_vars %>% arrange(var)
-logTr_vars = logTr_vars %>% arrange(var)
-retest_logTr_vars == logTr_vars
-```
-
-```{r echo=FALSE}
-rm(logTr_vars, retest_logTr_vars)
-```
-
-```{r}
-# Switch df names
-raw_retest_data = retest_data
-raw_test_data = test_data
-test_data = clean_test_data
-retest_data = clean_retest_data
-rm(clean_test_data, clean_retest_data)
-```
-
-### Extract t-1 data for t-2 subjects
-```{r}
-retest_subs_test_data <- test_data[test_data$sub_id %in% retest_data$sub_id,]
-
-rest_subs_test_data <- test_data[test_data$sub_id %in% retest_data$sub_id == FALSE,]
-
-#Arrange datasets of same size by sub_id
-retest_data = retest_data %>% arrange(sub_id)
-retest_subs_test_data = retest_subs_test_data %>% arrange(sub_id)
-
-#CHECK IF EVERYTHING IS ORDERED RIGHT
-as.character(retest_subs_test_data$sub_id) == as.character(retest_data$sub_id)
-```
-
-### Replace HDDM parameters in t1 data
-
-Since HDDM parameters depend on the sample on which they are fit we refit the model on t1 data for the subjects that have t2 data.
-Here we replace the HDDM parameters in the current t1 dataset with these refitted values and transform them as they would have been transformed for the full sample to mimick the procedure we applied to rest of the t2 data.
-
-Transform hddm refits as they had been transformed for the full sample t1 data.
-```{r}
-hddm_refits <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/hddm_refits_exhaustive.csv')
-
-hddm_refits$X <- as.character(hddm_refits$X)
-
-names(hddm_refits)[1] <- 'sub_id'
-
-hddm_logTr_vars = data.frame(grep('(?=.*hddm)(?=.*logTr)', names(retest_subs_test_data), value=T, perl=T))
-names(hddm_logTr_vars) = c('var')
-hddm_logTr_vars$sign = ifelse(grepl(".ReflogTr",hddm_logTr_vars$var), 'negative', 'positive')
-hddm_logTr_vars$var = gsub(".logTr|.ReflogTr", "", hddm_logTr_vars$var)
-
-transformed_hddm_refits = hddm_refits
-
-for(i in 1:length(names(transformed_hddm_refits))){
-  tmp_col = names(transformed_hddm_refits)[i]
-  if(tmp_col %in% hddm_logTr_vars$var){
-    sign = hddm_logTr_vars$sign[which(tmp_col == hddm_logTr_vars$var)]
-      if(sign == 'positive'){
-        # clean_retest_data[,tmp_col] = log(clean_retest_data[,tmp_col])
-        transformed_hddm_refits[,tmp_col] = pos_log(transformed_hddm_refits[,tmp_col])
-        names(transformed_hddm_refits)[which(names(transformed_hddm_refits) == tmp_col)] = paste0(tmp_col, '.logTr')
-        cat(paste0(tmp_col ,' was positively skewed and transformed.'))
-        cat('\n')
-      }
-      else if(sign == 'negative'){
-        transformed_hddm_refits[,tmp_col] = neg_log(transformed_hddm_refits[,tmp_col])
-        names(transformed_hddm_refits)[which(names(transformed_hddm_refits) == tmp_col)] = paste0(tmp_col, '.ReflogTr')
-        cat(paste0(tmp_col ,' was negatively skewed and transformed.'))
-        cat('\n')
-      }
-    }
-}
-```
-
-Check if transformation of hddm refits worked
-```{r}
-transform_hddm_logTr_vars = data.frame(grep('logTr', names(transformed_hddm_refits), value=T))
-names(transform_hddm_logTr_vars) = c('var')
-transform_hddm_logTr_vars$sign = ifelse(grepl(".ReflogTr",transform_hddm_logTr_vars$var), 'negative', 'positive')
-transform_hddm_logTr_vars$var = gsub(".logTr|.ReflogTr", "", transform_hddm_logTr_vars$var)
-transform_hddm_logTr_vars = transform_hddm_logTr_vars %>% arrange(var)
-hddm_logTr_vars = hddm_logTr_vars %>% arrange(var)
-transform_hddm_logTr_vars == hddm_logTr_vars
-```
-
-Replace t1 hddm parameters for retest subjects
-
-```{r}
-replace_hddm_vars = data.frame(grep('(?=.*hddm)(?=.*logTr)', names(retest_subs_test_data), value=T, perl=T))
-names(replace_hddm_vars) = c('var')
-
-hddm_fix_retest_subs_test_data = retest_subs_test_data
-
-for(i in 1:length(names(hddm_fix_retest_subs_test_data))){
-  if(names(hddm_fix_retest_subs_test_data)[i] %in% replace_hddm_vars$var){
-    hddm_fix_retest_subs_test_data[,names(hddm_fix_retest_subs_test_data)[i]] <- transformed_hddm_refits[,names(hddm_fix_retest_subs_test_data)[i]]
-  }
-}
-
-retest_subs_test_data <- hddm_fix_retest_subs_test_data
-```
-
-```{r}
-rm(hddm_refits, transformed_hddm_refits, hddm_logTr_vars, transform_hddm_logTr_vars, replace_hddm_vars, hddm_fix_retest_subs_test_data, sign, i)
-```
-
-# Results
-
-## Reliability metrics 
-For correlations we report Spearman's $\rho$'s only.  
-Based on [Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) ICC(3,k) does not take in to account within subject differences between two time points (i.e.
-the fixed effect of time/systematic error).
-Thus, it is well approximated by Pearson's r and subject to similar criticisms.
-[Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) suggests reporting at least this systematic error effect size if one chooses to report with ICC(3,k).
-Based on his conclusions here I report:
-- ICC(3,k): As Dave clarified this ranges from 1 to -1/(number of repeated measures -1) so in our case this range would be [-1, 1]; larger values would mean that the two scores of a subject for a given measure are more similar to each other than they are to scores of other people
-- partial $\eta^2$ for time ($SS_{time}/SS_{within}$): effect size of time   
-- SEM ($\sqrt(MS_{error})$): standard error of measurement; the smaller the better
-
-```{r}
-numeric_cols = c()
-
-for(i in 1:length(names(test_data))){
-  if(is.numeric(test_data[,i])){
-    numeric_cols <- c(numeric_cols, names(test_data)[i])
-  }
-}
-
-match_t1_t2 <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', format = "long", sample = 'full', sample_vec){
-
-  if(sample == 'full'){
-   df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var) 
-  }
-  else{
-    df = merge(t1_df[t1_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)], t2_df[t2_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)],
-    by=merge_var)
-  }
-
-  df = df %>% 
-    na.omit()%>%
-    gather(dv, score, -sub_id) %>%
-    mutate(time = ifelse(grepl('\\.x', dv), 1, ifelse(grepl('\\.y', dv), 2, NA))) %>%
-    separate(dv, c("dv", "drop"), sep='\\.([^.]*)$') %>%
-    select(-drop)
-
-  if(format == 'wide'){
-    df = df%>% spread(time, score) 
-  }
-
-  return(df)
-}
-
-get_spearman = function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
-  }
-
-  rho = cor(df$`1`, df$`2`, method='spearman')
-
-  return(rho)
-}
-
-get_icc <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
-  }
-
-  df = df %>% select(-dv, -sub_id)
-  icc = ICC(df)
-  icc_3k = icc$results['Average_fixed_raters', 'ICC']
-  return(icc_3k)
-  }
-
-get_eta <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, sample='bootstrap', sample_vec = sample_vec)
-  }
-
-  mod = summary(aov(score~Error(sub_id)+time, df))
-  ss_time = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq1',]
-  ss_error = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq2',]
-  eta = ss_time/(ss_time+ss_error)
-  return(eta)
-  }
-
-get_sem <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, sample='bootstrap', sample_vec = sample_vec)
-  }
-  mod = summary(aov(score~Error(sub_id)+time, df))
-  ms_error = as.data.frame(unlist(mod$`Error: Within`))['Mean Sq2',]
-  sem = sqrt(ms_error)
-  return(sem)
-}
-```
-
-```{r}
-rel_df <- data.frame(spearman = rep(NA, length(numeric_cols)),
-                     icc = rep(NA, length(numeric_cols)), 
-                     eta_sq = rep(NA, length(numeric_cols)),
-                     sem = rep(NA, length(numeric_cols)))
-
-row.names(rel_df) <- numeric_cols
-
-for(i in 1:length(numeric_cols)){
-  rel_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i]) 
-  rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
-  rel_df[numeric_cols[i], 'eta_sq'] <- get_eta(numeric_cols[i])
-  rel_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
-}
-
-rel_df$dv = row.names(rel_df)
-row.names(rel_df) = seq(1:nrow(rel_df))
-rel_df$task = 'task'
-rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
-rel_df = rel_df %>%
-  select(dv, task, spearman, icc, eta_sq, sem)
-# row.names(rel_df) = NULL
-
-```
-
-Average reliability metrics and the number of variables for both the surveys and the tasks
-Both Spearman $\rho$'s as well the ICC's are higher for surveys.  
-Systematic differences between the two measurements ($\eta^2$) are higher for tasks than surveys (potentially indicating learning effects?).  
-Unexpectedly, median standard error of measurement is higher for surveys but the distribution below suggests that this is a side effect of having too many task measures with very low SEMs.
-```{r warning=FALSE, message=FALSE}
-rel_df %>%
-  group_by(task) %>%
-  summarise(median_spearman = median(spearman),
-            median_icc = median(icc),
-            median_eta_sq = median(eta_sq),
-            median_sem = median(sem),
-            num_vars = n()) %>%
-  datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc', 'median_eta_sq', 'median_sem'), digits=3)
-```
-
-*Rank orders for reliabilities*
-
-- Note that this table can be sorted by different metrics, filtered for specific values for each column and is searchable.  
-- Demographics are excluded from this list of variables (because they are saved for predictive analyses).  
-- Holt and Laury test-retest is the worst for *surveys*.
-But note that this is not a survey that has been studied extensively psychometrically like others.
-This is more similar to our tasks (one that is used more often by economists).
-In previous data I have worked with retest reliablities for this task was ~.35 so the results here are in line with this.
-- Otherwise the lowest survey reliabilities are 0.5.
-
-```{r}
-rel_df %>%
-  datatable(filter='top') %>%
-  formatRound(columns=c('spearman', 'icc', 'eta_sq', 'sem'), digits=3)
-```
-
-### Histograms of reliability metrics
 
@@
 ```
-
-### Negative icc's?
-```{r}
-neg_icc_vars = rel_df %>%
-  arrange(icc) %>% 
-  filter(icc<0) %>%
-  select(dv)
-```
-
-Some variables (`r neg_icc_vars$dv`) have <0 ICC's. This would be the case if the $MS_{error}$>$MS_{between}$.
-
-Plot data for measures with negative ICC.  
-x-axis is time 1 data and y-axis is time 2 data. The scatter plots show that the scores for measures with negative ICC's have no relationship across time points.
-```{r, fig.height=12, fig.width=12}
-tmp = data.frame()
-
-for(i in 1:nrow(neg_icc_vars)){
-  tmp = rbind(tmp, match_t1_t2(neg_icc_vars$dv[i]))
-}
-rm(neg_icc_vars)
-
-tmp %>%
-  spread(time, score) %>%
-  # mutate(dv_wrap = str_wrap(dv, width = 30)) %>%
-  ggplot(aes(`1`, `2`))+
-  geom_point()+
-  theme_bw()+
-  facet_wrap(~dv, scales='free', labeller = label_wrap_gen())
-
-```
-
-This point is clarified further by compare these scatter plots to those of variables with highest ICC. These variables have strong and clear positive linear relationships.
-
-```{r fig.height=12, fig.width=12}
-high_icc_vars = rel_df %>%
-  arrange(-icc)  %>% 
-  filter(icc>0.92) %>%
-  select(dv)
-
-tmp = data.frame()
-
-for(i in 1:nrow(high_icc_vars)){
-  tmp = rbind(tmp, match_t1_t2(high_icc_vars$dv[i]))
-}
-rm(high_icc_vars)
-
-tmp %>%
-  spread(time, score) %>%
-  ggplot(aes(`1`, `2`))+
-  geom_point()+
-  theme_bw()+
-  facet_wrap(~dv, scales='free')
-
-```
-
-```{r echo=FALSE}
-rm(tmp)
-```
-
-### Relationship between ICC and Spearman
-These two measures give mostly similar answers regarding the reliabilities of the measures except for
-
-```{r}
-ggplotly(rel_df %>%
-           ggplot(aes(spearman, icc, col=task, label=dv, label2=eta_sq))+
-           geom_point()+
-           theme_bw()+
-           theme(legend.title = element_blank())+
-           geom_abline(intercept = 0, slope=1))
-```
-
-What are the variables clustered around 0 ICC?
-
-```{r}
-rel_df %>%
-  filter(icc>(-0.1), icc<0.1) %>%
-  arrange(icc) %>%
-  datatable() %>%
-  formatRound(columns=c('spearman', 'icc', 'eta_sq', 'sem'), digits=3)
-```
-
-### Relationship between ICC and $\eta^2$
-
-```{r}
-ggplotly(rel_df %>%
-  ggplot(aes(eta_sq, icc, col=task, label=dv))+
-  geom_point()+
-  theme_bw()+
-  theme(legend.title = element_blank()))
-```
-
-## Reliability by measure types
-
-The results presented so far aim to be comprehensive but are difficult to parse through and get a clear sense of what is going on (other than a general impression that surveys tend to have higher reliabilities than tasks).
-In this and the following section we try to deal with this in two ways to make the results more digestable with two kinds of categorizations.
-
-### Tasks
-
-We aim to make contact with the literature to make the results more accesible to readers who have experience with our tasks but do not want to   
-1. take away from the novelty of the main papers coming out of this project outlining the factor structure that this data unveils   
-2. necessarily make prescriptive recommendations or theoretical arguments on why certain measures of certain processes are more reliable than others.
-
-With this in mind we reduce the list of over 270 task measures to a list of one per task by averaging only the raw measures from all the trials in a task.
-We chose to reduce the information in this manner to avoid any bias stemming from differential amount of interest and procedures applied to certain tasks over others (e.g.
-a task can have over 10 measures because it has multiple conditions and we have chosen to fit DDM's for specific conditions while another might only have 2 due to our relative inexperience and lack of interest in it).
-We check whether the number of trials in a task has a significant effect on these average reliabilities of raw measures as well.
-
-We plan to supplement/potentially replace this with an additional labeling procedure intending to capture the underlying putative cognitive processes but are deferring this until at least for another week.
-This exercise might not even prove helpful but at least a per task summary seemed a reasonable first pass.
-
-```{r echo=FALSE}
-measure_labels <- read.csv('/Users/zeynepenkavi/Downloads/retest_measure_labels.csv')
-measure_labels = measure_labels %>% select(-Patrick_hates)
-
-trim <- function (x) gsub("^\\s+|\\s+$", "", x)
-```
-
-We filter out the DDM parameters and measures for specific contrasts.
-Note that this does leave some tasks with measures that are model fits and/or for specific conditions (because at least the current datasets do not include measures that are based on all the trials **and** are raw though I could dive in to variables_exhaustive for such measures.
-For example the average relialibility for Kirby is based on three discount rates for specific conditions.).
-Here's the order of tasks by mean reliability sorted for ICC and then Spearman's $\rho$.
-
-```{r warning=FALSE, message=FALSE}
-tmp = measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  select(-measure_description, -notes, -measure_type, -task, -ddm_task) %>%
-  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
-  mutate(label_1 = trim(label_1),
-         label_2=trim(label_2),
-         label_3=trim(label_3))%>%
-  filter(label_1 %in% c('difference', 'EZ', 'hddm') ==FALSE & label_2 %in% c('difference', 'EZ', 'hddm') == FALSE) %>%
-  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
-  select(-extra_1, -extra_2) %>%
-  group_by(task_name) %>%
-  summarise(median_icc = median(icc),
-            median_spearman = median(spearman),
-            num_measures = n(),
-            num_trials = unique(num_all_trials)) %>%
-  arrange(-median_icc, -median_spearman)
-
-tmp %>%
-  datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
-```
-
-Does number of items in a task have a significant effect on the average ICC of (mostly) raw measures for all trials from a task? No.
-
-```{r warning=FALSE, message=FALSE}
-summary(lm(median_icc ~ num_trials, data = tmp))
-```
-
-Does number of items in a task have a significant effect on the average Spearman $\rho$ of (mostly) raw measures for all trials from a task? No.
-
-```{r warning=FALSE, message=FALSE}
-summary(lm(median_spearman ~ num_trials, data = tmp))
-```
-
-Does number of measures that went in to this reliability estimate have a significant effect on the average ICC of (mostly) raw measures for all trials from a task?
-It seems the more measures that goes in to summarizing overall reliability for a task the worse it gets.
-This would make sense if these variables are intended to measure different things and some are less reliable than others.
-
-```{r warning=FALSE, message=FALSE}
-summary(lm(median_icc ~ num_measures, data = tmp))
-```
-
-Does number of measures that went in to this reliability estimate have a significant effect on the average ICC of (mostly) raw measures for all trials from a task?  
-The same is true for Spearman's correlations as well.
-
-```{r warning=FALSE, message=FALSE}
-summary(lm(median_spearman ~ num_measures, data = tmp))
-```
-
-In addition to average relilibilities for each task we can look at relilibities of measures organized by the putative cognitive process they are intended to measure.
-Note however that these labels are not determined in a data driven manner.
-
-```{r warning=FALSE, message=FALSE}
-measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  select(-measure_description, -notes, -variable_type, -task, -ddm_task) %>%
-  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  group_by(measure_type) %>%
-  summarise(median_icc = median(icc),
-            median_spearman = median(spearman),
-            num_measures = n()) %>%
-  arrange(-median_icc, -median_spearman) %>%
-  datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
-```
-
-Here is what the distributions look like.  
-- Alerting: This labels consists only of ANT alerting contrast (no cue - double cue trials). 4/6 are drift diffusion parameters.    
-- Cue encoding: This label consists only of three by two task switch cost contrast (stay (where cue and task remains the same) - switch (where task is the same but cue changes) trials).
-Again most are drift diffusion parameters.
-- Delay discounting: This label consists of the discount rates for the Bickel titrator (3), Kirby items (3) and discount titrate (model fit to random set of stimuli).
-**Does the discrepancy between ICC and Spearman for these measures, given the specific interest in these tasks in the literature warrant a more detailed look in to these?**
-- Information use: This label includes Columbia Card Task (both versions) and information sampling task.  
-- Inhibition: This label includes go no-go, motor selective stop signal, stimulus selective stop signal and regular stop signal (excluding specific constrasts).  
-- Intelligence: This label includes ravens and tower of london.  
-- Learning: This label includes ART, CCT, two stage decision, dietary decision task, hierarchical rule task, information sampling task, probabilistic selection task, shift task, two stage task.   
-- Neutral writing: This label consists only of the writing task.  
-- Orienting: This labels consists only of ANT orienting contrast (center - spatial cue trials). 4/6 are drift diffusion parameters.   
-- Positive writing: This label consists only of the writing task.  
-- Proactive control: This labels consists of one DPX contrast (AY - BY trials), motor selective stop signal and regular stop signal.   
-- Reactive control: This labels consists of one DPX contrast (BX - BY trials) and motor selective stop signal.  
-- Resisting proactive interference: This label consists of one contrast in directed forgetting and recent probes tasks (negative (where the stimulus to respond to is in forgetting set) and control (where the stimulus to respond to is new) trials).
-- Response conflict: This label consists of ANT conflict contrast (congruent-incongruent), DPX, local global conflict contrast, shape matching, simon, stroop.  
-- Response selection: This label consists of choice reaction time task.  
-- Risk Taking: This label consists of ART and CCT.  
-- Selective attention: This label consists of local global task and ANT (all trials).  
-- Set shifting: This label consists of local global, PRT and three by two.    
-- Speed: This label consists of raw response times in information sampling task, simple reaction time, tower of london.  
-- Working memory: This label consists of adaptive n back, digit span, directed forgetting, keep track, recent probes, spatial span.
-
-```{r warning=FALSE, message=FALSE, fig.width=12, fig.height=10}
-measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  select(-measure_description, -notes, -variable_type, -task, -ddm_task) %>%
-  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  select(measure_type, icc, spearman) %>%
-  gather(key, value, -measure_type) %>%
-  ggplot(aes(value, fill=key))+
-  geom_histogram(position='identity', alpha=0.5)+
-  theme_bw()+
-  facet_wrap(~measure_type)+
-  theme(legend.title = element_blank())
-```
-
-### Surveys
-
-To be filled with factor labels after processing either ASU factor analyses or Russ' MIRT?
-
-## Reliability by variable types
-
-In this section we label the measures based on the procedure behind the creation of a variable.
-This moves further away from the literature and thinking about our measures in terms of specific tasks, surveys or cognitive processes and is a more novel way of presenting our data.
-
-Potentially prescriptive recommendations coming out of this section would intend to build intuitions about different treatments to data that have higher reliabilities especially when researchers plan on making their own tasks and collecting different kinds of measures.
-
-### Tasks
-
-#### DDM parameters
-
-```{r warning=FALSE, message=FALSE}
-tmp = measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  select(-measure_description, -notes, -measure_type, -task) %>%
-  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
-  mutate(label_1 = trim(label_1),
-         label_2=trim(label_2),
-         label_3=trim(label_3))%>%
-  filter(ddm_task == 1) %>%
-  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.', remove=FALSE) %>%
-  select(-extra_1, -extra_2) %>%
-  drop_na()
-```
-
-In addition to raw response time and accuracy measures we get from certain tasks we have also chosen to fit drift diffusion models to them.
-The tasks we have chosen to fit these models are: `unique(tmp$task_name)`.
-This list does not include all cognitive tasks in the battery.
-
-Table of median reliabilities for the two kinds of DDM models' (hddm and EZ) parameters compared to raw response times and accuracies depending on whether they were fit to all data or whether they are contrast of two conditions sorted by mean ICC and mean Spearman's $\rho$.
-
-- All parameters that were fit to all trials compared to contrasts have higher relialibilities.   
-- Raw variables are not the variables with highest ICC's overall. Raw response times do, however, have the highest Spearman's $\rho$'s on average. 
-- 2 of 3 hddm parameters also have higher mean reliabilities than EZ parameter estimates.
-
-```{r warning=FALSE, message=FALSE}
-tmp %>%
-  group_by(label_1,label_2, label_3) %>%
-  summarise(median_icc = median(icc),
-            median_spearman = median(spearman),
-            n_vars = n()) %>%
-  arrange(-median_icc, -median_spearman) %>%
-  datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
-```
-
-This is what the distributions of look like. Note that there is one box in the difference columns for HDDM because this model only allows this to be different across conditions.
-
-```{r warning=FALSE, message=FALSE}
-tmp = tmp %>%
-  select(dv, icc, spearman, label_1, label_2, label_3) %>%
-  gather(key, value, -dv, -label_1, -label_2, -label_3)
-
-tmp %>% ggplot(aes(label_2, value, fill=label_3))+
-  geom_boxplot()+
-  theme_bw()+
-  facet_wrap(key~label_1)+
-  labs(fill="Parameter")
-```
-
-```{r message=FALSE, echo=FALSE, eval=FALSE}
-#attempt to make the above interactive. didn't really work
-ggplotly(ggplot_build(tmp %>%
-                        ggplot(aes(value, color=label_2, fill=label_3))+
-                        geom_histogram(position='identity', alpha = 0.5)+
-                        theme_bw()+
-                        facet_wrap(key~label_1)+
-                        labs(color="Model", fill="Parameter"))$data[[1]] %>%
-           mutate(key = ifelse(PANEL %in%  c(1,2), "icc", "spearman"),
-                  label_1 = ifelse(PANEL %in%  c(1,3), "all", "difference"),
-                  label_2 = ifelse(colour == "#F8766D", "EZ", ifelse(colour == "#00BA38", "hddm", "raw")),
-                  label_3 = ifelse(fill == "#A3A500", "drift rate", ifelse(fill == "#00BF7D", "non-decision", ifelse(fill == "#E76BF3", "threshold", ifelse(fill == "#F8766D", "accuracy", "rt"))))) %>%
-           get_labels(.,tmp, "value", c("label_1", "label_2", "label_3", "key")) %>%
-           prettify_label(.) %>%
-           ggplot(aes(x, y, fill = label_3, color=label_2, label=label))+
-           geom_bar(stat='identity',position='identity', alpha=0.5)+
-           facet_wrap(key~label_1)+
-           theme_bw(),
-         tooltip = 'label',
-         hoverinfo = 'text')
-```
-### Surveys
-
-Would this be a comparison of factor reliability versus item reliability?
-
-## Completion times
-
-Do people differ in how much their scores change depending on how many days it has been since they completed the initial battery?
-
-Make data frame with difference between two scores for each measure for each subject.
-Since the scores for different measures are on different scales for comparability the difference scores are scaled (i.e.
-divided by their root mean square) but not centered so a value of 0 for the difference scores would indicate a lack of a difference between the scores of a subject.
-
-```{r warning=FALSE}
-t1_2_difference = data.frame()
-
-for(i in 1:length(numeric_cols)){
-  tmp = match_t1_t2(numeric_cols[i],format='wide')
-  tmp = tmp %>% 
-    # mutate(difference = scale(`2` - `1`))
-  mutate(difference = scale(`2` - `1`, center=F))
-  t1_2_difference = rbind(t1_2_difference, tmp)
-}
-
-t1_2_difference$difference = as.data.frame(t1_2_difference$difference)$V1
-```
-
-```{r echo=FALSE}
-rm(tmp, i)
-```
-
-Add completion dates to this data frame.
-
-```{r warning=FALSE}
-t1_2_difference = merge(t1_2_difference, comp_dates[,c('sub_id', 'days_btw')], by='sub_id')
-```
-
-```{r echo=FALSE}
-rm(test_comp_date, retest_comp_date, comp_dates)
-```
-
-The effect of number of days in between in the full model where the difference scores are regressed on a fixed effect for measure and days between the two scores and random intercepts for each subject (*Should this model include the interaction between the fixed effects?*).
-Since there are over 300 measures the output of the full model is not presented here.
-Instead below are the coefficient for the fixed effect of days between completion times and its t value.
-
-```{r}
-mod = lmer(difference ~ dv + days_btw + (1|sub_id), data = t1_2_difference)
-
-data.frame(estimate=coef(summary(mod))["days_btw","Estimate"], tval=coef(summary(mod))["days_btw","t value"])
-```
-
-For visualization purposes I summarized the difference scores per person by looking at the average difference and plot that against the number of days between completion.
-
-```{r warning=FALSE, message=FALSE}
-tmp = t1_2_difference %>%
-  group_by(sub_id) %>%
-  summarise(mean_diff = mean(difference, na.rm=T),
-            days_btw = unique(days_btw))
-
-ggplotly(tmp %>%
-  ggplot(aes(days_btw, mean_diff))+
-  geom_point()+
-  theme_bw()+
-  xlab("Days between completion")+
-  ylab("Mean standardized difference between two time points")+
-  geom_smooth(method="lm"))
-```
-
-To confirm: the slope of this line is not significant.
-That is, there doesn't seem to be a systematic difference between the two measurements depending on the number of days between the two measurements.
-
-```{r warning=FALSE, message=FALSE}
-summary(lm(mean_diff ~ days_btw, data=tmp))
-```
-
-```{r echo=FALSE}
-rm(tmp)
-```
-
-<a id="diff_plot"></a>
-For reference here are the box plots showing the distribution of difference scores for each task.
-
-```{r warning=FALSE, message=FALSE, fig.height=36}
-t1_2_difference %>%
-           ggplot(aes(reorder(dv, difference, FUN=median), difference))+
-           geom_hline(yintercept = 0,color='red',size=1)+
-           geom_boxplot()+
-           theme_bw()+
-           xlab("")+
-           ylab("Standardized difference")+
-           coord_flip()
-```
-
-## Transformation effects
-
-```{r}
-raw_retest_subs_test_data = raw_test_data[raw_test_data$sub_id %in% raw_retest_data$sub_id,]
-
-raw_numeric_cols = c()
-
-for(i in 1:length(names(raw_test_data))){
-  if(is.numeric(raw_test_data[,i])){
-    raw_numeric_cols <- c(raw_numeric_cols, names(raw_test_data)[i])
-  }
-}
-
-raw_rel_df <- data.frame(spearman = rep(NA, length(raw_numeric_cols)),
-                     icc = rep(NA, length(raw_numeric_cols)), 
-                     eta_sq = rep(NA, length(raw_numeric_cols)),
-                     sem = rep(NA, length(raw_numeric_cols)))
-
-row.names(raw_rel_df) <- raw_numeric_cols
-
-for(i in 1:length(raw_numeric_cols)){
-  raw_rel_df[raw_numeric_cols[i], 'spearman'] <- get_spearman(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data) 
-  raw_rel_df[raw_numeric_cols[i], 'icc'] <- get_icc(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data)
-  raw_rel_df[raw_numeric_cols[i], 'eta_sq'] <- get_eta(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data)
-  raw_rel_df[raw_numeric_cols[i], 'sem'] <- get_sem(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data)
-}
-
-raw_rel_df$dv = row.names(raw_rel_df)
-row.names(raw_rel_df) = seq(1:nrow(raw_rel_df))
-raw_rel_df$task = 'task'
-raw_rel_df[grep('survey', raw_rel_df$dv), 'task'] = 'survey'
-raw_rel_df = raw_rel_df %>%
-  select(dv, task, spearman, icc, eta_sq, sem)
-```
-
-```{r warning=FALSE, message=FALSE}
-raw_rel_df %>%
-  group_by(task) %>%
-  summarise(median_spearman = median(spearman),
-            median_icc = median(icc),
-            median_eta_sq = median(eta_sq),
-            median_sem = median(sem),
-            num_vars = n()) %>%
-  datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc', 'median_eta_sq', 'median_sem'), digits=3)
-```
-
-Plots of change in reliability depending on transformation
-
-```{r}
-ggplotly(rel_df %>%
-  mutate(dv = gsub(".logTr", "", dv)) %>%
-  mutate(dv = gsub(".Re", "", dv)) %>%
-  left_join(raw_rel_df, by = 'dv') %>%
-  ggplot(aes(spearman.x, spearman.y, color = task.x, label=dv))+
-  geom_point()+
-  geom_abline(intercept = 0, slope=1)+
-  theme_bw()+
-  theme(legend.title = element_blank())+
-  xlab("Spearman with transformation")+
-  ylab("Spearman witouth transformation"))
-```
-
-```{r}
-ggplotly(rel_df %>%
-  mutate(dv = gsub(".logTr", "", dv)) %>%
-  mutate(dv = gsub(".Re", "", dv)) %>%
-  left_join(raw_rel_df, by = 'dv') %>%
-  ggplot(aes(icc.x, icc.y, color = task.x, label=dv))+
-  geom_point()+
-  geom_abline(intercept = 0, slope=1)+
-  theme_bw()+
-  theme(legend.title = element_blank())+
-  xlab("ICC with transformation")+
-  ylab("ICC without transformation"))
-```
-
-## Bootstrapping
-
-```{r eval=FALSE, echo=FALSE}
-sample_workers = function(N = 150, repl= TRUE, df=retest_data, worker_col = "sub_id"){
-  return(sample(df[,worker_col], N, replace = repl))
-}
-
-bootstrap_relialibility = function(metric = c('icc', 'spearman', 'eta_sq', 'sem'), dv_var){
-  tmp_sample = sample_workers()
-  out_df = data.frame(dv = dv_var)
-  if('icc' %in% metric){
-    out_df$icc = get_icc(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
-  }
-  if('spearman' %in% metric){
-    out_df$spearman = get_spearman(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
-  }
-  if('eta_sq' %in% metric){
-    out_df$eta_sq = get_eta(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
-  }
-  if('sem' %in% metric){
-    out_df$sem = get_sem(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
-  }
-  return(out_df)
-}
-
-# Bootstrapping everything at once in this way locally would take around four hours.
-non_hddm_numeric_cols=numeric_cols[-grep("hddm", numeric_cols)]
-
-boot_df = as.data.frame(non_hddm_numeric_cols) %>%
-  mutate(index = 1:n()) %>%
-  group_by(index) %>%
-  do(plyr::rdply(10, bootstrap_relialibility(dv_var = as.character(.$non_hddm_numeric_cols))))
-
-boot_df
-```
-
-Summarized bootstrapped reliabilities
-
-```{r}
-boot_df <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/bootstrap_merged.csv')
-
-boot_df = boot_df %>%
-  drop_na() %>%
-  mutate(icc = as.numeric(as.character(icc)),
-         spearman = as.numeric(as.character(spearman)),
-         eta_sq = as.numeric(as.character(eta_sq)),
-         sem = as.numeric(as.character(sem)))
-
-boot_df %>%
-  group_by(dv) %>%
-  summarise(icc_median = quantile(icc, probs = 0.5),
-            icc_2.5 = quantile(icc, probs = 0.025),
-            icc_97.5 = quantile(icc, probs = 0.975),
-            spearman_median = quantile(spearman, probs = 0.5),
-            spearman_2.5 = quantile(spearman, probs = 0.025),
-            spearman_97.5 = quantile(spearman, probs = 0.975)) %>%
-  datatable() %>%
-  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
-```
-
-Distributions of bootstrapped reliabilities.
-Yellow points are where our point estimates fall from the retest sample.
-Surveys are filled in red but can't be seen because the variance around their bootstrapped ICC's is very low.
-
-```{r fig.height=36}
- boot_df %>%
-  mutate(task = ifelse(grepl("survey",dv), "survey","task")) %>%
-  ggplot(aes(reorder(dv, icc, FUN=var), icc, fill = task))+
-  geom_boxplot()+
-  geom_hline(yintercept = 0,color='red',size=1)+
-  geom_point(data = rel_df, aes(x=dv, y = icc),  color = "yellow")+
-  theme_bw()+
-  theme(legend.title = element_blank())+
-  xlab("")+
-  coord_flip()
-```

### 2017-11-03 code/SRO_Report.Rmd
cont cleaning report

@@
 
+Plot the distributions of different types of variables
+
+```{r warning=FALSE, message=FALSE}
+measure_labels %>%
+  select(dv, task, variable_type, ddm_task, num_all_trials)%>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  filter(task == "task") %>%
+  select(-var, -task) %>%
+  left_join(rel_df[,c("dv", "icc")], by="dv")%>%
+  # filter(ddm_task == 1) %>%
+  separate(variable_type, c("overall_difference", "raw_EZ_hddm", "param"), extra="merge") %>%
+  mutate(raw_EZ_hddm = ifelse(ddm_task == 0, "other", raw_EZ_hddm),
+         param = ifelse(ddm_task == 0, "other", param)) %>%
+  na.omit() %>%
+  filter(overall_difference!='condition') %>%
+  ggplot(aes(x=factor(raw_EZ_hddm, levels = c("raw", "EZ", "hddm", "other"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion", "Other")),y=icc,fill=param))+
+  geom_boxplot(position = position_dodge(width=0.75))+
+  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
+  theme_bw()+
+  xlab("")+
+  ylab("ICC")+
+  theme(legend.title = element_blank())
+```
+
 Are these differences meaningful?
 
+Reliabilities for difference variables is lower.
+
 ```{r}
@@
 
-In the model below (after the model comparison the interactive one is significantly better) the baseline is difference accuracy.
-
-Main effects: Compared to this overall accuracy has higher reliability and difference threshold has lower reliability. Other difference parameters do not differ from difference accuracy significantly.
-
-Interactions: Drift rates, thresholds are higher for overall than difference; response times are marginally so.
-
-Conclusion: Overall parameter estimates are higher than difference estimates (except for non-decision time).
-
-```{r}
-summary(lm(icc ~ label_1*label_3,tmp))
-```
-
-Closer look at simple effects:
-
-Are overall drift rates meaninfully higher than overall raw accuracies? Yes.
-
-```{r}
-tmp_simp = tmp %>%
-  filter(label_3 %in% c("drift rate", "accuracy"),
-         label_1 == 'overall')
-
-summary(lm(icc~label_3, tmp_simp))
-```
-
-Are overall drift rates meaninfully higher than overall raw response times? No, not worse either.
-
-```{r}
-tmp_simp = tmp %>%
-  filter(label_3 %in% c("drift rate", "rt"),
-         label_1 == 'overall')
-
-summary(lm(icc~label_3, tmp_simp))
-```
-
-Are overall thresholds meaninfully higher than overall raw accuracies? No, not worse either.
-
-```{r}
-tmp_simp = tmp %>%
-  filter(label_3 %in% c("threshold", "accuracy"),
-         label_1 == 'overall')
-
-summary(lm(icc~label_3, tmp_simp))
-```
-
-Are overall thresholds meaninfully higher than overall raw response times? No, they are worse.
-
-```{r}
-tmp_simp = tmp %>%
-  filter(label_3 %in% c("threshold", "rt"),
-         label_1 == 'overall')
-
-summary(lm(icc~label_3, tmp_simp))
-```
-
-Are overall non-decision times meaninfully higher than overall raw accuracies? No, not worse either.
-
-```{r}
-tmp_simp = tmp %>%
-  filter(label_3 %in% c("non-decision", "accuracy"),
-         label_1 == 'overall')
-
-summary(lm(icc~label_3, tmp_simp))
-```
-
-Are overall non-decision times meaninfully higher than overall raw response times? No, they are worse.
-
-```{r}
-tmp_simp = tmp %>%
-  filter(label_3 %in% c("non-decision", "rt"),
-         label_1 == 'overall')
-
-summary(lm(icc~label_3, tmp_simp))
+When all trials are used the drift rates and rt's have higher reliabilities compared to accuracies.
+
+```{r}
+summary(lm(icc~label_3,tmp[tmp$label_1=="overall",]))
 ```
@@
 rm(tmp)
-```
-
-<a id="diff_plot"></a>
-For reference here are the box plots showing the distribution of difference scores for each task.
-
-```{r warning=FALSE, message=FALSE, fig.height=36}
-t1_2_difference %>%
-           ggplot(aes(reorder(dv, difference, FUN=median), difference))+
-           geom_hline(yintercept = 0,color='red',size=1)+
-           geom_boxplot()+
-           theme_bw()+
-           xlab("")+
-           ylab("Standardized difference")+
-           coord_flip()
 ```
@@
 
-Distributions of bootstrapped reliabilities.
-Yellow points are where our point estimates fall from the retest sample.
-Surveys are filled in red but can't be seen because the variance around their bootstrapped ICC's is very low.
-
-```{r fig.height=36}
- boot_df %>%
-  mutate(task = ifelse(grepl("survey",dv), "survey","task")) %>%
-  ggplot(aes(reorder(dv, icc, FUN=var), icc, fill = task))+
-  geom_boxplot()+
-  geom_hline(yintercept = 0,color='red',size=1)+
-  geom_point(data = rel_df, aes(x=dv, y = icc),  color = "yellow")+
-  theme_bw()+
-  theme(legend.title = element_blank())+
-  xlab("")+
-  coord_flip()
-```
-
 Comparison of survey measures to cognitive task measures in the bootstrapped results.
@@
 boot_df = boot_df %>%
-    mutate(task = ifelse(grepl("survey",dv), "survey","task"))
+    mutate(task = ifelse(grepl("survey",dv), "survey","task"),
+           task = ifelse(grepl("holt",dv), "task", task))
 
@@
   filter(task == 'task') %>%
-  select(-measure_description, -notes, -measure_type, -task) %>%
-  # left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
   separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
@@
 ```{r}
-summary(lmerTest::lmer(icc ~ label_1*label_3 + (1|dv) ,tmp))
+summary(lmerTest::lmer(icc ~ label_1 + (1|dv) ,tmp))
+```
+
+```{r}
+summary(lmerTest::lmer(icc ~ label_3 + (1|dv) ,tmp))
+```
+
+```{r warning=FALSE, message=FALSE}
+poster_vars <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/poster_var_list.csv', header=F)
+
+names(poster_vars) = "var"
+
+boot_df_poster = boot_df[boot_df$dv %in% poster_vars$var,]
+
+boot_df_poster = boot_df_poster%>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
+  mutate(task_group = gsub("_", " ", task_group),
+         var = gsub("_", " ", var)) %>%
+  arrange(task_group, var)
+
+boot_df_poster = boot_df_poster %>%
+  left_join(rel_df[,c("dv", "icc")], by = "dv") %>%
+  rename(icc = icc.x, point_est = icc.y)
+
+#Manual correction
+boot_df_poster = boot_df_poster %>%
+  mutate(task = ifelse(task_group == 'holt laury survey', "task", task)) %>%
+  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
+  mutate(task_group = gsub("survey", "", task_group))
+```
+
+```{r warning=FALSE, message=FALSE} 
+p4 <- boot_df_poster %>%
+  filter(task == 'task') %>%
+ggplot(aes(y = var, x = icc)) + 
+  geom_point(color = '#00BFC4')+
+  geom_point(aes(y = var, x = point_est), color = "black")+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y", labeller = label_wrap_gen(width=20)) +
+  theme(panel.spacing = unit(0.75, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180, size=36),
+        axis.text.y = element_text(size=20),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80")) + 
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
+  scale_shape_manual(breaks = sort(boot_df_poster$type), values = c(15, 17, 3))+
+  geom_vline(xintercept = 0, color = "red", size = 1)
+
+p5 <- boot_df_poster %>%
+  filter(task == 'survey') %>%
+ggplot(aes(y = var, x = icc)) + 
+  geom_point(color = '#F8766D')+
+  geom_point(aes(y = var, x = point_est), color = "black")+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y", labeller = label_wrap_gen(width=20)) +
+  theme(panel.spacing = unit(0.75, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180, size=36),
+        axis.text.y = element_text(size=20),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80")) + 
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
+  scale_shape_manual(breaks = sort(boot_df_poster$type), values = c(15, 17, 3))+
+  geom_vline(xintercept = 0, color = "red", size = 1)
+
+p6 <- arrangeGrob(p4, p5,nrow=1)
+
+ggsave('Bootstrap_Poster_Plot.jpg', plot = p6, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 42, units = "in", limitsize = FALSE)
+```
+
+```{r echo=FALSE, out.width='100%'}
+knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Bootstrap_Poster_Plot.jpg')
+```
+
+```{r echo=FALSE}
+rm(p4, p5, p6)
+```
+
+```{r}
+p4_t <- boot_df_poster %>%
+  filter(task == 'task') %>%
+ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
+  geom_violin(fill='#00BFC4')+
+  theme_bw() + 
+  theme(axis.text.y = element_text(size=30))+
+  xlab("")+
+  ylab("")+
+  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
+  geom_hline(yintercept = 0, color = "red", size = 1)+
+  coord_flip()
+
+p5_t <- boot_df_poster %>%
+  filter(task == 'survey') %>%
+ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
+  geom_violin(fill='#F8766D')+
+  theme_bw() + 
+  theme(axis.text.y = element_text(size=43))+
+  xlab("")+
+  ylab("")+
+  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
+  geom_hline(yintercept = 0, color = "red", size = 1)+
+  coord_flip()
+
+p6_t <- arrangeGrob(p4_t, p5_t,nrow=1)
+
+ggsave('Bootstrap_Poster_Plot_t.jpg', plot = p6_t, device = "jpeg", path = "../output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE)
+```
+
+```{r echo=FALSE, out.width='100%'}
+knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Bootstrap_Poster_Plot_t.jpg')
+```
+
+```{r echo=FALSE}
+rm(p4_t, p5_t, p6_t)
 ```

### 2017-11-03 code/SRO_Report.Rmd
added first draft of presentation

@@
 trim <- function (x) gsub("^\\s+|\\s+$", "", x)
-render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
+render_this <- function(){rmarkdown::render('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
 options(scipen = 1, digits = 4)
@@
 
-datatable(lit_review)
+lit_review
 ```
@@
 
-datatable(df)
+df
 ```
@@
   xlab("")
+
+ggsave('Rel_Histograms.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
 ```
@@
 grid.arrange(p1, p2, p3, nrow=1)
+
+ggsave('Metric_Scatterplots.jpg', plot = grid.arrange(p1, p2, p3, nrow=1), device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
 ```
@@
   theme(legend.title = element_blank())
+
+ggsave('DDM_comparisons.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
 ```

### 2017-11-04 code/SRO_Report.Rmd
ordered the variance breakdown plot

@@
 ```{r warning=FALSE, message=FALSE}
-p1 = rel_df %>%
+tmp = rel_df %>%
   mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
@@
   select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
-  gather(key, value, -dv, -task) %>%
-  mutate(key = factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct")),
+  # gather(key, value, -dv, -task) %>%
+  mutate(#key = factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct")),
          dv = factor(dv, levels = dv[order(task)])) %>%
@@
   mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  arrange(task_group, var_subs_pct) %>%
+  mutate(rank = row_number()) %>%
+  arrange(task, task_group, rank) %>%
+  gather(key, value, -dv, -task_group, -var, -task, -rank) %>%
+  ungroup()%>%
   # separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
@@
          !grepl("EZ|hddm", dv))%>%
-  ggplot(aes(x=var, y=value, fill=key))+
-  geom_bar(stat='identity', alpha = 0.75)+
+  arrange(task_group, rank)
+labels = tmp %>%
+  distinct(dv, .keep_all=T)
+
+p1 <- tmp %>%
+  ggplot(aes(x=factor(rank), y=value, fill=factor(key, levels = c("var_resid_pct", "var_ind_pct", "var_subs_pct"))))+
+  geom_bar(stat='identity', alpha = 0.75, color='#00BFC4')+
+  scale_x_discrete(breaks = labels$rank,
+                       labels = labels$var)+
   coord_flip()+
@@
         panel.background = element_rect(fill = NA),
-        panel.grid.major = element_line(colour = "grey80"),
+        panel.grid.major = element_line(colour = "grey85"),
         legend.position = 'bottom')+
@@
   theme(legend.title = element_blank())+
-  scale_fill_discrete(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
+  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                       labels = c("Variance between individuals",
@@
                                  "Error variance"),
-                     h=c(100,500))+
+                  values=c("grey65", "grey45", "grey25"))+
   ylab("")+
@@
 
-p2 = rel_df %>%
+tmp = rel_df %>%
   mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
@@
   mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
-  separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
+  arrange(task_group, var_subs_pct) %>%
+  mutate(rank = row_number()) %>%
+  arrange(task, task_group, rank) %>%
+  gather(key, value, -dv, -task_group, -var, -task, -rank) %>%
+  ungroup()%>%
+  # separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
   mutate(task_group = gsub("_", " ", task_group),
-         var = gsub("_", " ", var)) %>%
+         var = gsub("_", " ", var),
+         var=gsub(".ReflogTr", "", var),
+         var=gsub(".logTr", "", var)) %>%
   mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
@@
   filter(task=="survey")%>%
-  ggplot(aes(x=var, y=value, fill=key))+
+  arrange(task_group, rank)
+labels = tmp %>%
+  distinct(dv, .keep_all=T)
+
+p2 <- tmp %>%
+  ggplot(aes(x=factor(rank), y=value, fill=factor(key, levels = c("var_resid_pct", "var_ind_pct", "var_subs_pct"))))+
   geom_bar(stat='identity', alpha = 0.75)+
+  geom_bar(stat='identity', color='#F8766D', show.legend=FALSE)+
+  scale_x_discrete(breaks = labels$rank,
+                       labels = labels$var)+
   coord_flip()+
@@
                                  "Error variance"),
-                    h=c(100,500))+
+                  values=c("grey65", "grey45", "grey25"))+
   ylab("")+
@@
 
-g_legend<-function(a.gplot){
-  tmp <- ggplot_gtable(ggplot_build(a.gplot))
-  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
-  legend <- tmp$grobs[[leg]]
-  return(legend)}
-
-mylegend<-g_legend(p1)
+mylegend<-g_legend(p2)
 

### 2017-11-06 code/SRO_Report.Rmd
prep for meeting

@@
   mutate(task_group = factor(task_group, levels = task_group[order(task)]),
-         raw1_fit0 = grepl('raw', variable_type),
          type = as.character(type)) %>%
@@
          var = gsub("_", " ", var)) %>%
-  arrange(task_group, raw1_fit0, var) %>%
+  arrange(task_group, raw_fit, var) %>%
   mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
@@
 ```{r echo=FALSE}
-#Get variables of interest
+#Get variables of interest from Ian's release
 tmp1 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_10-08-2017/meaningful_variables.csv')
@@
 ## Reliability metrics
-For correlations we report Spearman's $\rho$'s only.  
+
 Based on [Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) ICC(3,k) does not take in to account within subject differences between two time points (i.e.
@@
   left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
-  mutate(label_1 = trim(label_1),
-         label_2=trim(label_2),
-         label_3=trim(label_3))%>%
-  filter(label_1 %in% c('difference', 'EZ', 'hddm') ==FALSE & label_2 %in% c('difference', 'EZ', 'hddm') == FALSE) %>%
+  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
   separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
@@
 ```{r warning=FALSE, message=FALSE}
-summary(lm(median_icc ~ num_trials, data = tmp))
-```
-
-Does number of measures that went in to this reliability estimate have a significant effect on the average ICC of (mostly) raw measures for all trials from a task? No. (same is true for Spearman)
-
-```{r warning=FALSE, message=FALSE}
-summary(lm(median_icc ~ num_measures, data = tmp))
-```
-
-## Reliability by variable types
-
-In this section we label the measures based on the procedure behind the creation of a variable.
-This moves further away from the literature and thinking about our measures in terms of specific tasks, surveys or cognitive processes and is a more novel way of presenting our data.
-
-Potentially prescriptive recommendations coming out of this section would intend to build intuitions about different treatments to data that have higher reliabilities especially when researchers plan on making their own tasks and collecting different kinds of measures.
-
-### Tasks
-
-#### DDM parameters
-
-```{r warning=FALSE, message=FALSE}
 tmp = measure_labels %>%
@@
   left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
-  mutate(label_1 = trim(label_1),
-         label_2=trim(label_2),
-         label_3=trim(label_3))%>%
+  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
+  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
+  select(-extra_1, -extra_2)
+
+summary(lm(icc ~ num_all_trials, data = tmp))
+```
+
+```{r warning=FALSE, message=FALSE}
+measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(task == 'task') %>%
+  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
+  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
+  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
+  select(-extra_1, -extra_2) %>%
+  ggplot(aes(num_all_trials, icc))+
+  geom_point()+
+  geom_smooth(method="lm")+
+  theme_bw()+
+  xlab("Number of trials")+
+  ylab("ICC")
+```
+
+## Reliability by variable types
+
+In this section we label the measures based on the procedure behind the creation of a variable.
+This moves further away from the literature and thinking about our measures in terms of specific tasks, surveys or cognitive processes and is a more novel way of presenting our data.
+
+Potentially prescriptive recommendations coming out of this section would intend to build intuitions about different treatments to data that have higher reliabilities especially when researchers plan on making their own tasks and collecting different kinds of measures.
+
+### Tasks
+
+#### DDM parameters
+
+```{r warning=FALSE, message=FALSE}
+tmp = measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(task == 'task') %>%
+  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
   filter(ddm_task == 1) %>%
@@
 tmp %>%
-  group_by(label_1,label_2, label_3) %>%
+  group_by(overall_difference, raw_fit, rt_acc) %>%
   summarise(median_icc = median(icc),
@@
 measure_labels %>%
-  select(dv, task, variable_type, ddm_task, num_all_trials)%>%
   separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
@@
   left_join(rel_df[,c("dv", "icc")], by="dv")%>%
-  # filter(ddm_task == 1) %>%
-  separate(variable_type, c("overall_difference", "raw_EZ_hddm", "param"), extra="merge") %>%
-  mutate(raw_EZ_hddm = ifelse(ddm_task == 0, "other", raw_EZ_hddm),
-         param = ifelse(ddm_task == 0, "other", param)) %>%
   na.omit() %>%
-  filter(overall_difference!='condition') %>%
-  ggplot(aes(x=factor(raw_EZ_hddm, levels = c("raw", "EZ", "hddm", "other"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion", "Other")),y=icc,fill=param))+
+  filter(overall_difference!='condition',
+         raw_fit != 'fit',
+         rt_acc != 'other') %>%
+  ggplot(aes(x=factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")),y=icc,fill=rt_acc))+
   geom_boxplot(position = position_dodge(width=0.75))+
@@
 
-```{r}
-summary(lm(icc ~ label_1,tmp))
-```
-
-When all trials are used the drift rates and rt's have higher reliabilities compared to accuracies.
-
-```{r}
-summary(lm(icc~label_3,tmp[tmp$label_1=="overall",]))
+```{r message=FALSE, warning=FALSE}
+tmp = measure_labels %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  filter(task == "task") %>%
+  select(-var, -task) %>%
+  left_join(rel_df[,c("dv", "icc")], by="dv")%>%
+  na.omit() %>%
+  filter(overall_difference!='condition',
+         raw_fit != 'fit',
+         rt_acc != 'other')
+
+summary(lm(icc ~ overall_difference*raw_fit,tmp))
 ```
@@
 
-ggplotly(tmp %>%
+tmp %>%
   ggplot(aes(days_btw, mean_diff))+
@@
   ylab("Mean standardized difference between two time points")+
-  geom_smooth(method="lm"))
+  geom_smooth(method="lm")
 ```
@@
 
-```{r}
-boot_df <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/bootstrap_merged.csv')
+```{r message=FALSE, warning=FALSE}
+# boot_df <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/bootstrap_merged.csv')
+
+boot_df <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/bootstrap_merged.csv')
 
@@
   mutate(task_group = gsub("_", " ", task_group),
-         var = gsub("_", " ", var),
-         var=gsub(".ReflogTr", "", var),
-         var=gsub(".logTr", "", var)) %>%
+         var = gsub("_", " ", var)) %>%
+         # var=gsub(".ReflogTr", "", var),
+         # var=gsub(".logTr", "", var)) %>%
   mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
@@
 ggsave('Variance_Breakdown_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 24, height = 20, units = "in")
+rm(tmp, labels)
 ```
@@
   group_by(task, key) %>%
-  ggplot(aes(task, value, fill=key))+
+  ggplot(aes(factor(task, levels=c("task","survey"), labels=c("Task", "Survey")), value, fill=key, color=task))+
   geom_boxplot()+
@@
   theme(legend.title = element_blank())+
-  scale_fill_discrete(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
+  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                     labels = c("Variance between individuals",
@@
                                "Error variance"),
-                    h=c(100,500))+
+                    values=c("grey65", "grey45", "grey25"))+
+  scale_color_discrete(guide = FALSE)+
   xlab("")+
@@
 
-ggsave('Variance_Breakdown_Plot_Summary.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 6, height = 5, units = "in")
+ggsave('Variance_Breakdown_Plot_Summary.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in")
 ```

### 2017-11-09 code/SRO_Report.Rmd
cleaning up analyses

@@
 library(DT)
+
+render_this <- function(){rmarkdown::render('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, toc_depth = 2, code_folding = 'hide'))}
+options(scipen = 1, digits = 4)
+```
+
+```{r, message=FALSE, warning=FALSE}
 sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
+
 g_legend<-function(a.gplot){
@@
   return(legend)}
+
 trim <- function (x) gsub("^\\s+|\\s+$", "", x)
-render_this <- function(){rmarkdown::render('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
-options(scipen = 1, digits = 4)
+
+match_t1_t2 <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', format = "long", sample = 'full', sample_vec){
+
+  if(sample == 'full'){
+   df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var) 
+  }
+  else{
+    df = merge(t1_df[t1_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)], t2_df[t2_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)],
+    by=merge_var)
+  }
+
+  df = df %>% 
+    na.omit()%>%
+    gather(dv, score, -sub_id) %>%
+    mutate(time = ifelse(grepl('\\.x', dv), 1, ifelse(grepl('\\.y', dv), 2, NA))) %>%
+    separate(dv, c("dv", "drop"), sep='\\.([^.]*)$') %>%
+    select(-drop)
+
+  if(format == 'wide'){
+    df = df%>% spread(time, score) 
+  }
+
+  return(df)
+}
+
+get_spearman = function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+
+  if(sample=='full'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
+  }
+  else if(sample=='bootstrap'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
+  }
+
+  rho = cor(df$`1`, df$`2`, method='spearman')
+
+  return(rho)
+}
+
+get_icc <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+  if(sample=='full'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
+  }
+  else if(sample=='bootstrap'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
+  }
+
+  df = df %>% select(-dv, -sub_id)
+  icc = ICC(df)
+  icc_3k = icc$results['Average_fixed_raters', 'ICC']
+  return(icc_3k)
+}
+
+get_pearson = function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+
+  if(sample=='full'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
+  }
+  else if(sample=='bootstrap'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
+  }
+
+  rho = cor(df$`1`, df$`2`, method='pearson')
+
+  return(rho)
+}
+
+get_var_breakdown <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+  if(sample=='full'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
+  }
+  else if(sample=='bootstrap'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
+  }
+
+  df = df %>% select(-dv, -sub_id)
+  icc = ICC(df)
+  var_breakdown = data.frame(subs = icc$summary[[1]][1,'Mean Sq'],
+                             ind = icc$summary[[1]][2,'Mean Sq'],
+                             resid = icc$summary[[1]][3,'Mean Sq'])
+  return(var_breakdown)
+  }
+
+get_eta <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+  if(sample=='full'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
+  }
+  else if(sample=='bootstrap'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, sample='bootstrap', sample_vec = sample_vec)
+  }
+
+  mod = summary(aov(score~Error(sub_id)+time, df))
+  ss_time = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq1',]
+  ss_error = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq2',]
+  eta = ss_time/(ss_time+ss_error)
+  return(eta)
+  }
+
+get_sem <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+  if(sample=='full'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
+  }
+  else if(sample=='bootstrap'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, sample='bootstrap', sample_vec = sample_vec)
+  }
+  mod = summary(aov(score~Error(sub_id)+time, df))
+  ms_error = as.data.frame(unlist(mod$`Error: Within`))['Mean Sq2',]
+  sem = sqrt(ms_error)
+  return(sem)
+}
 ```
@@
 Data collection took place on average `r round(mean(as.numeric(comp_dates$days_btw)))` number of days after the completion of the initial battery with a range of `r round(range(as.numeric(comp_dates$days_btw)))[1]` to `r round(range(as.numeric(comp_dates$days_btw)))[2]` days.
+
+## Demographics
+
+```{r}
+test_demog <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/t1_data/demographic_health.csv')
+
+retest_demog <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/demographic_health.csv')
+
+retest_demog = retest_demog[retest_demog$X %in% test_demog$X,]
+
+names(test_demog)[which(names(test_demog) == 'X')] <-'sub_id'
+names(retest_demog)[which(names(retest_demog) == 'X')] <-'sub_id'
+
+summary(retest_demog %>%
+          select(Sex, Age))
+```
 
@@
 
-ggsave('Lit_Review_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 20, units = "in")
+ggsave('Lit_Review_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 20, units = "in", dpi=100)
 rm(p1, p2, p3, p1_legend, mylegend)
@@
 ```{r}
+p1_t_legend <- lit_review %>%
+  filter(task == 'task') %>%
+ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
+  geom_point(aes(size=sample_size, shape = type), color='black')+
+  theme_bw()+
+  theme(axis.text.y = element_text(size=43),
+        legend.position = 'bottom',
+        axis.text.x = element_text(size=23),
+        axis.title.x = element_text(size=30), 
+        legend.text = element_text(size=20), 
+        legend.key.width = unit(0.75, "inches"), 
+        legend.title = element_text(size=28),
+        legend.spacing.x = unit(0.5, "inches")) + 
+  guides(size = guide_legend(override.aes = list(size=c(9,18,28))),
+         shape = guide_legend(override.aes = list(size=18)))+
+  xlab("Reliability")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
+  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3), name="Type")+
+  scale_size_continuous(name = "Sample Size")+
+  geom_vline(xintercept = 0, color = "red", size = 1)
+
 p1_t <- lit_review %>%
@@
   theme(axis.text.y = element_text(size=43),
-        legend.position = 'none') + 
-  xlab("")+
+        legend.position = 'none',
+        axis.text.x = element_text(size=23),
+        axis.title.x = element_text(size=30)) + 
+  xlab("Reliability")+
   ylab("")+
@@
   scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))+
-  scale_size_continuous(range = c(5, 50))+
+  scale_size_continuous(range = c(5, 35))+
   geom_vline(xintercept = 0, color = "red", size = 1)
@@
   scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))+
-  scale_size_continuous(range = c(5, 50))+
+  scale_size_continuous(range = c(5, 35))+
   geom_vline(xintercept = 0, color = "red", size = 1)
 
-p3_t <- arrangeGrob(p1_t, p2_t, nrow=1)
-
-ggsave('Lit_Review_Plot_t.jpg', plot = p3_t, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE)
-rm(p1_t, p2_t, p3_t)
+mylegend<-g_legend(p1_t_legend)
+
+p3_t <- arrangeGrob(arrangeGrob(p1_t, p2_t, nrow=1), mylegend, nrow=2,heights=c(10, 1))
+
+ggsave('Lit_Review_Plot_t.jpg', plot = p3_t, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE, dpi = 72)
+rm(p1_t, p2_t, p3_t, mylegend, p1_t_legend)
 ```
@@
 retest_report_vars = unique(retest_report_vars)
-lit_rev_vars = unique(lit_review$dv)[which(unique(lit_review$dv) %in% retest_report_vars == FALSE)]
+lit_rev_vars = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% retest_report_vars == FALSE)])
 retest_report_vars = c(retest_report_vars, lit_rev_vars)
@@
 # Results
+
+## Demographics reliability
+
+```{r}
+numeric_cols = c()
+
+for(i in 1:length(names(test_demog))){
+  if(is.numeric(test_demog[,i])){
+    numeric_cols <- c(numeric_cols, names(test_demog)[i])
+  }
+}
+
+demog_rel_df <- data.frame(spearman = rep(NA, length(numeric_cols)),
+                     icc = rep(NA, length(numeric_cols)),
+                     pearson = rep(NA, length(numeric_cols)))
+
+row.names(demog_rel_df) <- numeric_cols
+
+for(i in 1:length(numeric_cols)){
+  demog_rel_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i], t1_df = test_demog, t2_df = retest_demog) 
+  demog_rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i], t1_df = test_demog, t2_df = retest_demog)
+  demog_rel_df[numeric_cols[i], 'pearson'] <- get_pearson(numeric_cols[i], t1_df = test_demog, t2_df = retest_demog)
+}
+
+demog_rel_df
+```
+
+```{r echo=FALSE}
+rm(test_demog, retest_demog, demog_rel_df, numeric_cols)
+```
 
@@
 
-match_t1_t2 <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', format = "long", sample = 'full', sample_vec){
-
-  if(sample == 'full'){
-   df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var) 
-  }
-  else{
-    df = merge(t1_df[t1_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)], t2_df[t2_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)],
-    by=merge_var)
-  }
-
-  df = df %>% 
-    na.omit()%>%
-    gather(dv, score, -sub_id) %>%
-    mutate(time = ifelse(grepl('\\.x', dv), 1, ifelse(grepl('\\.y', dv), 2, NA))) %>%
-    separate(dv, c("dv", "drop"), sep='\\.([^.]*)$') %>%
-    select(-drop)
-
-  if(format == 'wide'){
-    df = df%>% spread(time, score) 
-  }
-
-  return(df)
-}
-
-get_spearman = function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
-  }
-
-  rho = cor(df$`1`, df$`2`, method='spearman')
-
-  return(rho)
-}
-
-get_icc <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
-  }
-
-  df = df %>% select(-dv, -sub_id)
-  icc = ICC(df)
-  icc_3k = icc$results['Average_fixed_raters', 'ICC']
-  return(icc_3k)
-}
-
-get_pearson = function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
-  }
-
-  rho = cor(df$`1`, df$`2`, method='pearson')
-
-  return(rho)
-}
-
-get_var_breakdown <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
-  }
-
-  df = df %>% select(-dv, -sub_id)
-  icc = ICC(df)
-  var_breakdown = data.frame(subs = icc$summary[[1]][1,'Mean Sq'],
-                             ind = icc$summary[[1]][2,'Mean Sq'],
-                             resid = icc$summary[[1]][3,'Mean Sq'])
-  return(var_breakdown)
-  }
-
-get_eta <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, sample='bootstrap', sample_vec = sample_vec)
-  }
-
-  mod = summary(aov(score~Error(sub_id)+time, df))
-  ss_time = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq1',]
-  ss_error = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq2',]
-  eta = ss_time/(ss_time+ss_error)
-  return(eta)
-  }
-
-get_sem <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, sample='bootstrap', sample_vec = sample_vec)
-  }
-  mod = summary(aov(score~Error(sub_id)+time, df))
-  ms_error = as.data.frame(unlist(mod$`Error: Within`))['Mean Sq2',]
-  sem = sqrt(ms_error)
-  return(sem)
-}
-```
-
-```{r}
 rel_df <- data.frame(spearman = rep(NA, length(numeric_cols)),
@@
 
-Average reliability metrics and the number of variables for both the surveys and the tasks
-Both Spearman $\rho$'s as well the ICC's are higher for surveys.  
-Systematic differences between the two measurements ($\eta^2$) are higher for tasks than surveys (potentially indicating learning effects?).  
-Unexpectedly, median standard error of measurement is higher for surveys but the distribution below suggests that this is a side effect of having too many task measures with very low SEMs.
-```{r warning=FALSE, message=FALSE}
-rel_df %>%
-  group_by(task) %>%
-  summarise(median_spearman = median(spearman),
-            median_icc = median(icc),
-            median_pearson = median(pearson),
-            median_eta_sq = median(eta_sq),
-            median_sem = median(sem),
-            num_vars = n()) %>%
-  datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc', 'median_pearson','median_eta_sq', 'median_sem'), digits=3)
-```
-
-**Table of reliability point estimates**
-
-```{r}
-rel_df %>%
-  datatable(filter='top') %>%
-  formatRound(columns=c('spearman', 'icc', 'pearson','eta_sq', 'sem'), digits=3)
-```
-
-### Histograms of reliability metrics
-
-```{r warning=FALSE, message=FALSE}
-rel_df %>%
-  select(dv, task, spearman, pearson, icc) %>%
-  gather(key, value, -dv, -task) %>%
-  ggplot(aes(value, fill=task))+
-  geom_histogram(alpha = 0.5, position = 'identity')+
-  facet_wrap(~key)+
-  theme_bw()+
-  theme(legend.position = 'bottom',
-        legend.title = element_blank())+
-  xlab("")
-
-ggsave('Rel_Histograms.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
-```
-
-Task measures have significanlty lower reliability (here checking only on point estimates of ICC).
-
-```{r}
-summary(lm(icc~task, rel_df))
-```
-
-### Relationship between reliability metrics
-
-```{r warning=FALSE, message=FALSE}
-p1 = rel_df %>%
-  ggplot(aes(spearman, icc, col=task))+
-  geom_point()+
-  theme_bw()+
-  theme(legend.title = element_blank(),
-        legend.position = "none")+
-  geom_abline(intercept = 0, slope=1)
-
-p2 = rel_df %>%
-  ggplot(aes(pearson, icc, col=task))+
-  geom_point()+
-  theme_bw()+
-  theme(legend.title = element_blank(),
-        legend.position = "none")+
-  geom_abline(intercept = 0, slope=1)
-
-p3 = rel_df %>%
-  ggplot(aes(pearson, spearman, col=task))+
-  geom_point()+
-  theme_bw()+
-  theme(legend.title = element_blank(),
-        legend.position = "none")+
-  geom_abline(intercept = 0, slope=1)
-
-grid.arrange(p1, p2, p3, nrow=1)
-
-ggsave('Metric_Scatterplots.jpg', plot = grid.arrange(p1, p2, p3, nrow=1), device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
-```
-
-```{r echo=FALSE}
-rm(p1,p2,p3)
-```
-
-Note: Some variables have <0 ICC's. This would be the case if the $MS_{error}$>$MS_{between}$. Data for these variables have no relationship between the two time points.
-
-## Task Reliabilities
-
-Here we summarize the results on a task level to make it more digestable and easier to make contact with the literature.
-
-With this in mind we reduce the list of task measures to a list of one per task by averaging only the raw measures from all the trials in a task.
-We chose to reduce the information in this manner to avoid any bias stemming from differential amount of interest and procedures applied to certain tasks over others (e.g.
-a task can have over 10 measures because it has multiple conditions and we have chosen to fit DDM's for specific conditions while another might only have 2 due to our relative inexperience and lack of interest in it).
-We check whether the number of trials in a task has a significant effect on these average reliabilities of raw measures as well.
-
-```{r echo=FALSE}
-measure_labels <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/measure_labels.csv')
-measure_labels = measure_labels %>% select(-measure_description,-measure_type,-measure_type_Ian,-measure_type_Russ,-notes,-Patrick_hates)
-```
-
-We filter out the DDM parameters and measures for specific contrasts.
-Note that this does leave some tasks with measures that are model fits and/or for specific conditions (because at least the current datasets do not include measures that are based on all the trials **and** are raw though I could dive in to variables_exhaustive for such measures.
-For example the average relialibility for Kirby is based on three discount rates for specific conditions.).
-Here's the order of tasks by mean reliability sorted for ICC and then Spearman's $\rho$.
-
-```{r warning=FALSE, message=FALSE}
-tmp = measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
-  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
-  select(-extra_1, -extra_2) %>%
-  group_by(task_name) %>%
-  summarise(median_icc = median(icc),
-            median_spearman = median(spearman),
-            num_measures = n(),
-            num_trials = unique(num_all_trials)) %>%
-  arrange(-median_icc, -median_spearman)
-
-tmp %>%
-  datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
-```
-
-Does number of items in a task have a significant effect on the average ICC of (mostly) raw measures for all trials from a task? No. (no effect on Spearman either)
-
-```{r warning=FALSE, message=FALSE}
-tmp = measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
-  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
-  select(-extra_1, -extra_2)
-
-summary(lm(icc ~ num_all_trials, data = tmp))
-```
-
-```{r warning=FALSE, message=FALSE}
-measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
-  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
-  select(-extra_1, -extra_2) %>%
-  ggplot(aes(num_all_trials, icc))+
-  geom_point()+
-  geom_smooth(method="lm")+
-  theme_bw()+
-  xlab("Number of trials")+
-  ylab("ICC")
-```
-
-## Reliability by variable types
-
-In this section we label the measures based on the procedure behind the creation of a variable.
-This moves further away from the literature and thinking about our measures in terms of specific tasks, surveys or cognitive processes and is a more novel way of presenting our data.
-
-Potentially prescriptive recommendations coming out of this section would intend to build intuitions about different treatments to data that have higher reliabilities especially when researchers plan on making their own tasks and collecting different kinds of measures.
-
-### Tasks
-
-#### DDM parameters
-
-```{r warning=FALSE, message=FALSE}
-tmp = measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  filter(ddm_task == 1) %>%
-  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.', remove=FALSE) %>%
-  select(-extra_1, -extra_2) %>%
-  drop_na()
-```
-
-In addition to raw response time and accuracy measures we get from certain tasks we have also chosen to fit drift diffusion models to them.
-The tasks we have chosen to fit these models are: `unique(tmp$task_name)`.
-This list does not include all cognitive tasks in the battery.
-
-Table of median reliabilities for the two kinds of DDM models' (hddm and EZ) parameters compared to raw response times and accuracies depending on whether they were fit to all data or whether they are contrast of two conditions sorted by mean ICC and mean Spearman's $\rho$.
-
-- All parameters that were fit to all trials compared to contrasts have higher relialibilities.   
-- Raw variables are not the variables with highest ICC's overall supporting the idea of using these parameters as individual difference variables that are more interpretable.
-
-```{r warning=FALSE, message=FALSE}
-tmp %>%
-  group_by(overall_difference, raw_fit, rt_acc) %>%
-  summarise(median_icc = median(icc),
-            median_spearman = median(spearman),
-            n_vars = n()) %>%
-  arrange(-median_icc, -median_spearman) %>%
-  datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
-```
-
-Plot the distributions of different types of variables
-
-```{r warning=FALSE, message=FALSE}
-measure_labels %>%
-  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
-  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
-  filter(task == "task") %>%
-  select(-var, -task) %>%
-  left_join(rel_df[,c("dv", "icc")], by="dv")%>%
-  na.omit() %>%
-  filter(overall_difference!='condition',
-         raw_fit != 'fit',
-         rt_acc != 'other') %>%
-  ggplot(aes(x=factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")),y=icc,fill=rt_acc))+
-  geom_boxplot(position = position_dodge(width=0.75))+
-  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
-  theme_bw()+
-  xlab("")+
-  ylab("ICC")+
-  theme(legend.title = element_blank())
-
-ggsave('DDM_comparisons.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
-```
-
-Are these differences meaningful?
-
-Reliabilities for difference variables is lower.
+Summarized bootstrapped reliabilities
 
 ```{r message=FALSE, warning=FALSE}
-tmp = measure_labels %>%
-  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
-  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
-  filter(task == "task") %>%
-  select(-var, -task) %>%
-  left_join(rel_df[,c("dv", "icc")], by="dv")%>%
-  na.omit() %>%
-  filter(overall_difference!='condition',
-         raw_fit != 'fit',
-         rt_acc != 'other')
-
-summary(lm(icc ~ overall_difference*raw_fit,tmp))
-```
-
-## Completion times
-
-Do people differ in how much their scores change depending on how many days it has been since they completed the initial battery?
-
-Make data frame with difference between two scores for each measure for each subject.
-Since the scores for different measures are on different scales for comparability the difference scores are scaled (i.e.
-divided by their root mean square) but not centered so a value of 0 for the difference scores would indicate a lack of a difference between the scores of a subject.
-
-```{r warning=FALSE}
-t1_2_difference = data.frame()
-
-for(i in 1:length(numeric_cols)){
-  tmp = match_t1_t2(numeric_cols[i],format='wide')
-  tmp = tmp %>% 
-    # mutate(difference = scale(`2` - `1`))
-  mutate(difference = scale(`2` - `1`, center=F))
-  t1_2_difference = rbind(t1_2_difference, tmp)
-}
-
-t1_2_difference$difference = as.data.frame(t1_2_difference$difference)$V1
-```
-
-```{r echo=FALSE}
-rm(tmp, i)
-```
-
-Add completion dates to this data frame.
-
-```{r warning=FALSE}
-t1_2_difference = merge(t1_2_difference, comp_dates[,c('sub_id', 'days_btw')], by='sub_id')
-```
-
-```{r echo=FALSE}
-rm(test_comp_date, retest_comp_date, comp_dates)
-```
-
-The effect of number of days in between in the full model where the difference scores are regressed on a fixed effect for measure and days between the two scores and random intercepts for each subject (*Should this model include the interaction between the fixed effects?*).
-Since there are over 300 measures the output of the full model is not presented here.
-Instead below are the coefficient for the fixed effect of days between completion times and its t value.
-
-```{r}
-mod = lmer(difference ~ dv + days_btw + (1|sub_id), data = t1_2_difference)
-
-data.frame(estimate=coef(summary(mod))["days_btw","Estimate"], tval=coef(summary(mod))["days_btw","t value"])
-```
-
-For visualization purposes I summarized the difference scores per person by looking at the average difference and plot that against the number of days between completion.
-
-```{r warning=FALSE, message=FALSE}
-tmp = t1_2_difference %>%
-  group_by(sub_id) %>%
-  summarise(mean_diff = mean(difference, na.rm=T),
-            days_btw = unique(days_btw))
-
-tmp %>%
-  ggplot(aes(days_btw, mean_diff))+
-  geom_point()+
-  theme_bw()+
-  xlab("Days between completion")+
-  ylab("Mean standardized difference between two time points")+
-  geom_smooth(method="lm")
-```
-
-To confirm: the slope of this line is not significant.
-That is, there doesn't seem to be a systematic difference between the two measurements depending on the number of days between the two measurements.
-
-```{r warning=FALSE, message=FALSE}
-summary(lm(mean_diff ~ days_btw, data=tmp))
-```
-
-```{r echo=FALSE}
-rm(tmp)
-```
-
-## Bootstrapping
-
-Summarized bootstrapped reliabilities
-
-```{r message=FALSE, warning=FALSE}
-# boot_df <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/bootstrap_merged.csv')
-
 boot_df <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/bootstrap_merged.csv')
@@
          sem = as.numeric(as.character(sem)))
+
+boot_df = boot_df[boot_df$dv %in% retest_report_vars,]
+
+retest_report_vars[which(retest_report_vars %in% boot_df$dv==FALSE)]
 
@@
 rm(p4_t, p5_t, p6_t)
+```
+
+### Histograms of reliability metrics (point estimates)
+
+```{r warning=FALSE, message=FALSE}
+rel_df %>%
+  select(dv, task, spearman, pearson, icc) %>%
+  gather(key, value, -dv, -task) %>%
+  ggplot(aes(value, fill=task))+
+  geom_histogram(alpha = 0.5, position = 'identity')+
+  facet_wrap(~key)+
+  theme_bw()+
+  theme(legend.position = 'bottom',
+        legend.title = element_blank())+
+  xlab("")
+
+ggsave('Rel_Histograms.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
+```
+
+### Relationship between reliability metrics (point estimates)
+
+```{r warning=FALSE, message=FALSE}
+p1 = rel_df %>%
+  ggplot(aes(spearman, icc, col=task))+
+  geom_point()+
+  theme_bw()+
+  theme(legend.title = element_blank(),
+        legend.position = "none")+
+  geom_abline(intercept = 0, slope=1)
+
+p2 = rel_df %>%
+  ggplot(aes(pearson, icc, col=task))+
+  geom_point()+
+  theme_bw()+
+  theme(legend.title = element_blank(),
+        legend.position = "none")+
+  geom_abline(intercept = 0, slope=1)
+
+p3 = rel_df %>%
+  ggplot(aes(pearson, spearman, col=task))+
+  geom_point()+
+  theme_bw()+
+  theme(legend.title = element_blank(),
+        legend.position = "none")+
+  geom_abline(intercept = 0, slope=1)
+
+grid.arrange(p1, p2, p3, nrow=1)
+
+ggsave('Metric_Scatterplots.jpg', plot = grid.arrange(p1, p2, p3, nrow=1), device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
+```
+
+```{r echo=FALSE}
+rm(p1,p2,p3)
+```
+
+Note: Some variables have <0 ICC's. This would be the case if the $MS_{error}$>$MS_{between}$. Data for these variables have no relationship between the two time points.
+
+## Task Reliabilities
+
+Here we summarize the results on a task level to make it more digestable and easier to make contact with the literature.
+
+We reduce the list of task measures to a list of one per task by averaging only the raw measures from all the trials in a task.
+We chose to reduce the information in this manner to avoid any bias stemming from differential amount of interest and procedures applied to certain tasks over others (e.g.
+a task can have over 10 measures because it has multiple conditions and we have chosen to fit DDM's for specific conditions while another might only have 2 due to our relative inexperience and lack of interest in it).
+We check whether the number of trials in a task has a significant effect on these average reliabilities of raw measures as well.
+
+```{r echo=FALSE}
+measure_labels <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/measure_labels.csv')
+measure_labels = measure_labels %>% select(-measure_description,-measure_type,-measure_type_Ian,-measure_type_Russ,-notes,-Patrick_hates)
+```
+
+We filter out the DDM parameters and measures for specific contrasts.
+Note that this does leave some tasks with measures that are model fits and/or for specific conditions (because at least the current datasets do not include measures that are based on all the trials **and** are raw though I could dive in to variables_exhaustive for such measures.
+For example the average relialibility for Kirby is based on three discount rates for specific conditions.).
+Here's the order of tasks by mean reliability sorted for ICC and then Spearman's $\rho$.
+
+```{r warning=FALSE, message=FALSE}
+tmp = measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(task == 'task') %>%
+  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
+  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
+  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
+  select(-extra_1, -extra_2) %>%
+  group_by(task_name) %>%
+  summarise(median_icc = median(icc),
+            median_spearman = median(spearman),
+            num_measures = n(),
+            num_trials = unique(num_all_trials)) %>%
+  arrange(-median_icc, -median_spearman)
+
+tmp %>%
+  datatable() %>%
+  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
+```
+
+Does number of items in a task have a significant effect on the average ICC of (mostly) raw measures for all trials from a task? No. (no effect on Spearman either)
+
+```{r warning=FALSE, message=FALSE}
+tmp = measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(task == 'task') %>%
+  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
+  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
+  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
+  select(-extra_1, -extra_2)
+
+summary(lm(icc ~ num_all_trials, data = tmp))
+```
+
+```{r warning=FALSE, message=FALSE}
+measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(task == 'task') %>%
+  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
+  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
+  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
+  select(-extra_1, -extra_2) %>%
+  ggplot(aes(num_all_trials, icc))+
+  geom_point()+
+  geom_smooth(method="lm")+
+  theme_bw()+
+  xlab("Number of trials")+
+  ylab("ICC")
+```
+
+## Reliability by variable types
+
+In this section we label the measures based on the procedure behind the creation of a variable.
+This moves further away from the literature and thinking about our measures in terms of specific tasks, surveys or cognitive processes and is a more novel way of presenting our data.
+
+Potentially prescriptive recommendations coming out of this section would intend to build intuitions about different treatments to data that have higher reliabilities especially when researchers plan on making their own tasks and collecting different kinds of measures.
+
+### Tasks
+
+#### DDM parameters
+
+```{r warning=FALSE, message=FALSE}
+tmp = measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(task == 'task') %>%
+  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
+  filter(ddm_task == 1) %>%
+  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.', remove=FALSE) %>%
+  select(-extra_1, -extra_2) %>%
+  drop_na()
+```
+
+In addition to raw response time and accuracy measures we get from certain tasks we have also chosen to fit drift diffusion models to them.
+The tasks we have chosen to fit these models are: `unique(tmp$task_name)`.
+This list does not include all cognitive tasks in the battery.
+
+Table of median reliabilities for the two kinds of DDM models' (hddm and EZ) parameters compared to raw response times and accuracies depending on whether they were fit to all data or whether they are contrast of two conditions sorted by mean ICC and mean Spearman's $\rho$.
+
+- All parameters that were fit to all trials compared to contrasts have higher relialibilities.   
+- Raw variables are not the variables with highest ICC's overall supporting the idea of using these parameters as individual difference variables that are more interpretable.
+
+```{r warning=FALSE, message=FALSE}
+tmp %>%
+  group_by(overall_difference, raw_fit, rt_acc) %>%
+  summarise(median_icc = median(icc),
+            median_spearman = median(spearman),
+            n_vars = n()) %>%
+  arrange(-median_icc, -median_spearman) %>%
+  datatable() %>%
+  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
+```
+
+Plot the distributions of different types of variables
+
+```{r warning=FALSE, message=FALSE}
+measure_labels %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  filter(task == "task") %>%
+  select(-var, -task) %>%
+  left_join(rel_df[,c("dv", "icc")], by="dv")%>%
+  na.omit() %>%
+  filter(overall_difference!='condition',
+         raw_fit != 'fit',
+         rt_acc != 'other') %>%
+  ggplot(aes(x=factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")),y=icc,fill=rt_acc))+
+  geom_boxplot(position = position_dodge(width=0.75))+
+  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
+  theme_bw()+
+  xlab("")+
+  ylab("ICC")+
+  theme(legend.title = element_blank())
+
+ggsave('DDM_comparisons.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
+```
+
+Are these differences meaningful?
+
+Reliabilities for difference variables is lower.
+
+```{r message=FALSE, warning=FALSE}
+tmp = measure_labels %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  filter(task == "task") %>%
+  select(-var, -task) %>%
+  left_join(rel_df[,c("dv", "icc")], by="dv")%>%
+  na.omit() %>%
+  filter(overall_difference!='condition',
+         raw_fit != 'fit',
+         rt_acc != 'other')
+
+summary(lm(icc ~ overall_difference*raw_fit,tmp))
+```
+
+## Completion times
+
+Do people differ in how much their scores change depending on how many days it has been since they completed the initial battery?
+
+Make data frame with difference between two scores for each measure for each subject.
+Since the scores for different measures are on different scales for comparability the difference scores are scaled (i.e.
+divided by their root mean square) but not centered so a value of 0 for the difference scores would indicate a lack of a difference between the scores of a subject.
+
+```{r warning=FALSE}
+t1_2_difference = data.frame()
+
+for(i in 1:length(numeric_cols)){
+  tmp = match_t1_t2(numeric_cols[i],format='wide')
+  tmp = tmp %>% 
+    # mutate(difference = scale(`2` - `1`))
+  mutate(difference = scale(`2` - `1`, center=F))
+  t1_2_difference = rbind(t1_2_difference, tmp)
+}
+
+t1_2_difference$difference = as.data.frame(t1_2_difference$difference)$V1
+```
+
+```{r echo=FALSE}
+rm(tmp, i)
+```
+
+Add completion dates to this data frame.
+
+```{r warning=FALSE}
+t1_2_difference = merge(t1_2_difference, comp_dates[,c('sub_id', 'days_btw')], by='sub_id')
+```
+
+```{r echo=FALSE}
+rm(test_comp_date, retest_comp_date, comp_dates)
+```
+
+The effect of number of days in between in the full model where the difference scores are regressed on a fixed effect for measure and days between the two scores and random intercepts for each subject (*Should this model include the interaction between the fixed effects?*).
+Since there are over 300 measures the output of the full model is not presented here.
+Instead below are the coefficient for the fixed effect of days between completion times and its t value.
+
+```{r}
+mod = lmer(difference ~ dv + days_btw + (1|sub_id), data = t1_2_difference)
+
+data.frame(estimate=coef(summary(mod))["days_btw","Estimate"], tval=coef(summary(mod))["days_btw","t value"])
+```
+
+For visualization purposes I summarized the difference scores per person by looking at the average difference and plot that against the number of days between completion.
+
+```{r warning=FALSE, message=FALSE}
+tmp = t1_2_difference %>%
+  group_by(sub_id) %>%
+  summarise(mean_diff = mean(difference, na.rm=T),
+            days_btw = unique(days_btw))
+
+tmp %>%
+  ggplot(aes(days_btw, mean_diff))+
+  geom_point()+
+  theme_bw()+
+  xlab("Days between completion")+
+  ylab("Mean standardized difference between two time points")+
+  geom_smooth(method="lm")
+```
+
+To confirm: the slope of this line is not significant.
+That is, there doesn't seem to be a systematic difference between the two measurements depending on the number of days between the two measurements.
+
+```{r warning=FALSE, message=FALSE}
+summary(lm(mean_diff ~ days_btw, data=tmp))
+```
+
+```{r echo=FALSE}
+rm(tmp)
 ```

### 2017-11-10 code/SRO_Report.Rmd
jdm poster

@@
 
-retest_report_vars[which(retest_report_vars %in% boot_df$dv==FALSE)]
+# retest_report_vars[which(retest_report_vars %in% boot_df$dv==FALSE)]
 
@@
 
-Comparison of survey measures to cognitive task measures in the bootstrapped results.
-Multilevel model with random intercepts for each measure and fixed effect of survey versus cognitive measure.
-(Same result as seen in point estimates comparison).
+Comparison of survey measures to cognitive task measures in the bootstrapped results. Multilevel model with random intercepts for each measure and fixed effect of survey versus cognitive measure.
 
@@
 
+boot_df %>%
+  group_by(task) %>%
+  summarise(icc_median = quantile(icc, probs = 0.5),
+            icc_2.5 = quantile(icc, probs = 0.025),
+            icc_97.5 = quantile(icc, probs = 0.975),
+            spearman_median = quantile(spearman, probs = 0.5),
+            spearman_2.5 = quantile(spearman, probs = 0.025),
+            spearman_97.5 = quantile(spearman, probs = 0.975),
+            num_vars = n()/1000) %>%
+  datatable() %>%
+  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
+```
+
+```{r}
 summary(lmerTest::lmer(icc ~  task + (1|dv), boot_df))
@@
 
-Checking DDM results in the bootstrapped estimates. Same as before too.
+```{r warning=FALSE, message=FALSE}
+boot_df %>%
+  ggplot(aes(icc, fill = task))+
+  geom_histogram(alpha=0.5, position='identity')+
+  theme_bw()+
+  theme(legend.title = element_blank())+
+  xlab("ICC")
+```
+
+```{r echo=FALSE}
+measure_labels <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/measure_labels.csv')
+measure_labels = measure_labels %>% select(-measure_description,-measure_type,-measure_type_Ian,-measure_type_Russ,-notes,-Patrick_hates)
+```
+
+Checking DDM results in the bootstrapped estimates.
+Variables using all trials are significantly more reliable compared to difference scores.
+Raw measures don't differ from DDM parameters.
+Which DDM is better depends on whether all trials are used.
 
@@
   mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
-  mutate(label_1 = trim(label_1),
-         label_2=trim(label_2),
-         label_3=trim(label_3))%>%
-  filter(ddm_task == 1) %>%
-  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.', remove=FALSE) %>%
-  select(-extra_1, -extra_2) %>%
+  filter(ddm_task == 1, 
+         overall_difference != "condition") %>%
   drop_na() %>%
-  left_join(boot_df[,c("dv", "icc")], by = 'dv')
-```
-
-```{r}
-summary(lmerTest::lmer(icc ~ label_1 + (1|dv) ,tmp))
-```
-
-```{r}
-summary(lmerTest::lmer(icc ~ label_3 + (1|dv) ,tmp))
-```
-
-```{r warning=FALSE, message=FALSE}
-poster_vars <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/poster_var_list.csv', header=F)
-
-names(poster_vars) = "var"
-
-boot_df_poster = boot_df[boot_df$dv %in% poster_vars$var,]
-
-boot_df_poster = boot_df_poster%>%
+  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')
+
+tmp %>%
+  group_by(overall_difference, raw_fit, rt_acc) %>%
+  summarise(icc_median = quantile(icc, probs = 0.5),
+            icc_2.5 = quantile(icc, probs = 0.025),
+            icc_97.5 = quantile(icc, probs = 0.975),
+            spearman_median = quantile(spearman, probs = 0.5),
+            spearman_2.5 = quantile(spearman, probs = 0.025),
+            spearman_97.5 = quantile(spearman, probs = 0.975),
+            num_vars = n()/1000) %>%
+  datatable() %>%
+  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
+```
+
+```{r}
+summary(lmerTest::lmer(icc ~ overall_difference*raw_fit + (1|dv) ,tmp))
+```
+
+```{r}
+tmp %>%
+  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy","other", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy", "Other","Drift Rate", "Threshold", "Non-decision"))))+
+  geom_boxplot()+
+  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
+  theme_bw()+
+  ylab("ICC")+
+  xlab("")+
+  theme(legend.title = element_blank())
+
+ggsave('Bootstrap_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 20, height = 8, units = "in", limitsize = FALSE)
+```
+
+```{r warning=FALSE, message=FALSE}
+tmp = measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')
+
+tmp = tmp %>%
   separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
@@
 
-boot_df_poster = boot_df_poster %>%
+tmp = tmp %>%
   left_join(rel_df[,c("dv", "icc")], by = "dv") %>%
@@
 #Manual correction
-boot_df_poster = boot_df_poster %>%
-  mutate(task = ifelse(task_group == 'holt laury survey', "task", task)) %>%
+tmp = tmp %>%
+  mutate(task = ifelse(task_group == 'holt laury survey', "task", as.character(task))) %>%
   mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
@@
 
-```{r warning=FALSE, message=FALSE} 
-p4 <- boot_df_poster %>%
-  filter(task == 'task') %>%
+Variable level summary of bootstrapped reliabilities.
+
+```{r warning=FALSE, message=FALSE} 
+p4 <- tmp %>%
+  filter(task == 'task',
+         raw_fit == 'raw') %>%
 ggplot(aes(y = var, x = icc)) + 
@@
   scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
-  scale_shape_manual(breaks = sort(boot_df_poster$type), values = c(15, 17, 3))+
   geom_vline(xintercept = 0, color = "red", size = 1)
 
-p5 <- boot_df_poster %>%
+p5 <- tmp %>%
   filter(task == 'survey') %>%
@@
   scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
-  scale_shape_manual(breaks = sort(boot_df_poster$type), values = c(15, 17, 3))+
   geom_vline(xintercept = 0, color = "red", size = 1)
@@
 
-ggsave('Bootstrap_Poster_Plot.jpg', plot = p6, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 42, units = "in", limitsize = FALSE)
+ggsave('Bootstrap_Var_Plot.jpg', plot = p6, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 36, height = 72, units = "in", limitsize = FALSE, dpi=50)
+
+rm(p4, p5, p6)
 ```
@@
 ```{r echo=FALSE, out.width='100%'}
-knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Bootstrap_Poster_Plot.jpg')
-```
-
-```{r echo=FALSE}
-rm(p4, p5, p6)
-```
-
-```{r}
-p4_t <- boot_df_poster %>%
+knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Bootstrap_Var_Plot.jpg')
+```
+
+```{r message=FALSE, warning=FALSE}
+p4_t <- tmp %>%
   filter(task == 'task') %>%
@@
 
-p5_t <- boot_df_poster %>%
+p5_t <- tmp %>%
   filter(task == 'survey') %>%
@@
 We check whether the number of trials in a task has a significant effect on these average reliabilities of raw measures as well.
-
-```{r echo=FALSE}
-measure_labels <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/measure_labels.csv')
-measure_labels = measure_labels %>% select(-measure_description,-measure_type,-measure_type_Ian,-measure_type_Russ,-notes,-Patrick_hates)
-```
 

### 2017-11-10 code/SRO_Report.Rmd
jdm poster

@@
 
-ggsave('Bootstrap_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 20, height = 8, units = "in", limitsize = FALSE)
+ggsave('Bootstrap_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 6, units = "in", limitsize = FALSE)
 ```

### 2017-11-16 code/SRO_Report.Rmd
cleaning up report

@@
 ```{r, message=FALSE, warning=FALSE, include=FALSE}
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-library(gridExtra)
-library(lme4)
-library(GGally)
-library(jsonlite)
-library(psych)
-library(rmarkdown)
-library(psych)
-library(stringr)
-library(plotly)
-library(DT)
-
-render_this <- function(){rmarkdown::render('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, toc_depth = 2, code_folding = 'hide'))}
-options(scipen = 1, digits = 4)
-```
-
-```{r, message=FALSE, warning=FALSE}
-sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
-
-g_legend<-function(a.gplot){
-  tmp <- ggplot_gtable(ggplot_build(a.gplot))
-  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
-  legend <- tmp$grobs[[leg]]
-  return(legend)}
-
-trim <- function (x) gsub("^\\s+|\\s+$", "", x)
-
-match_t1_t2 <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', format = "long", sample = 'full', sample_vec){
-
-  if(sample == 'full'){
-   df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var) 
-  }
-  else{
-    df = merge(t1_df[t1_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)], t2_df[t2_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)],
-    by=merge_var)
-  }
-
-  df = df %>% 
-    na.omit()%>%
-    gather(dv, score, -sub_id) %>%
-    mutate(time = ifelse(grepl('\\.x', dv), 1, ifelse(grepl('\\.y', dv), 2, NA))) %>%
-    separate(dv, c("dv", "drop"), sep='\\.([^.]*)$') %>%
-    select(-drop)
-
-  if(format == 'wide'){
-    df = df%>% spread(time, score) 
-  }
-
-  return(df)
-}
-
-get_spearman = function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
-  }
-
-  rho = cor(df$`1`, df$`2`, method='spearman')
-
-  return(rho)
-}
-
-get_icc <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
-  }
-
-  df = df %>% select(-dv, -sub_id)
-  icc = ICC(df)
-  icc_3k = icc$results['Average_fixed_raters', 'ICC']
-  return(icc_3k)
-}
-
-get_pearson = function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
-  }
-
-  rho = cor(df$`1`, df$`2`, method='pearson')
-
-  return(rho)
-}
-
-get_var_breakdown <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
-  }
-
-  df = df %>% select(-dv, -sub_id)
-  icc = ICC(df)
-  var_breakdown = data.frame(subs = icc$summary[[1]][1,'Mean Sq'],
-                             ind = icc$summary[[1]][2,'Mean Sq'],
-                             resid = icc$summary[[1]][3,'Mean Sq'])
-  return(var_breakdown)
-  }
-
-get_eta <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, sample='bootstrap', sample_vec = sample_vec)
-  }
-
-  mod = summary(aov(score~Error(sub_id)+time, df))
-  ss_time = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq1',]
-  ss_error = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq2',]
-  eta = ss_time/(ss_time+ss_error)
-  return(eta)
-  }
-
-get_sem <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, sample='bootstrap', sample_vec = sample_vec)
-  }
-  mod = summary(aov(score~Error(sub_id)+time, df))
-  ms_error = as.data.frame(unlist(mod$`Error: Within`))['Mean Sq2',]
-  sem = sqrt(ms_error)
-  return(sem)
-}
+source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Report_Helper_Functions.R')
 ```
@@
 
+#For later comparison of whether fitting the DDM parameters on full or retest sample makes a big difference
+test_data_full_sample_hddm <- test_data
+
 test_data = cbind(test_data$sub_id, test_data[,names(test_data) %in% names(hddm_refits) == FALSE])
@@
 ## Demographics reliability
+
+Point estimates of reliability for the demographic variabels.
 
@@
 
-demog_rel_df
+demog_rel_df %>%
+  mutate(var = row.names(.)) %>%
+  select(var, icc, spearman, pearson) %>%
+  arrange(-icc)
 ```
@@
 
-# retest_report_vars[which(retest_report_vars %in% boot_df$dv==FALSE)]
+retest_report_vars[which(retest_report_vars %in% boot_df$dv==FALSE)]
 

### 2017-11-16 code/SRO_Report_Helper_Functions.R

@@ -1,0 +1,137 @@
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(gridExtra)
+library(lme4)
+library(GGally)
+library(jsonlite)
+library(psych)
+library(rmarkdown)
+library(psych)
+library(stringr)
+library(plotly)
+library(DT)
+
+render_this <- function(){rmarkdown::render('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, toc_depth = 2, code_folding = 'hide'))}
+options(scipen = 1, digits = 4)
+
+sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
+
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)}
+
+trim <- function (x) gsub("^\\s+|\\s+$", "", x)
+
+match_t1_t2 <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', format = "long", sample = 'full', sample_vec){
+  
+  if(sample == 'full'){
+    df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var) 
+  }
+  else{
+    df = merge(t1_df[t1_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)], t2_df[t2_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)],
+               by=merge_var)
+  }
+  
+  df = df %>% 
+    na.omit()%>%
+    gather(dv, score, -sub_id) %>%
+    mutate(time = ifelse(grepl('\\.x', dv), 1, ifelse(grepl('\\.y', dv), 2, NA))) %>%
+    separate(dv, c("dv", "drop"), sep='\\.([^.]*)$') %>%
+    select(-drop)
+  
+  
+  if(format == 'wide'){
+    df = df%>% spread(time, score) 
+  }
+  
+  return(df)
+}
+
[…]

### 2017-11-16 code/SRO_Report.Rmd
cleaning up report

@@
   xlab("ICC")
+
+ggsave('Hist_Boot_Rel.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 72)
 ```
@@
 ```{r warning=FALSE, message=FALSE}
+# Df wrangling for plotting
 tmp = measure_labels %>%
@@
 
-ggsave('Bootstrap_Var_Plot.jpg', plot = p6, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 36, height = 72, units = "in", limitsize = FALSE, dpi=50)
+ggsave('Bootstrap_Raw_Var_Plot.jpg', plot = p6, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 36, height = 72, units = "in", limitsize = FALSE, dpi=50)
 
@@
 ```{r echo=FALSE, out.width='100%'}
-knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Bootstrap_Var_Plot.jpg')
+knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Bootstrap_Raw_Var_Plot.jpg')
 ```
@@
 ```{r warning=FALSE, message=FALSE}
-rel_df %>%
+boot_df %>%
   select(dv, task, spearman, pearson, icc) %>%
@@
   xlab("")
+
+# rel_df %>%
+#   select(dv, task, spearman, pearson, icc) %>%
+#   gather(key, value, -dv, -task) %>%
+#   ggplot(aes(value, fill=task))+
+#   geom_histogram(alpha = 0.5, position = 'identity')+
+#   facet_wrap(~key)+
+#   theme_bw()+
+#   theme(legend.position = 'bottom',
+#         legend.title = element_blank())+
+#   xlab("")
 

### 2017-11-16 code/SRO_Report.Rmd
cleaning up report

@@
 
-### Histograms of reliability metrics (point estimates)
+### Histograms of reliability metrics
 
@@
 
-# rel_df %>%
-#   select(dv, task, spearman, pearson, icc) %>%
-#   gather(key, value, -dv, -task) %>%
-#   ggplot(aes(value, fill=task))+
-#   geom_histogram(alpha = 0.5, position = 'identity')+
-#   facet_wrap(~key)+
-#   theme_bw()+
-#   theme(legend.position = 'bottom',
-#         legend.title = element_blank())+
-#   xlab("")
-
 ggsave('Rel_Histograms.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
@@
 
-### Relationship between reliability metrics (point estimates)
-
-```{r warning=FALSE, message=FALSE}
-p1 = rel_df %>%
+### Relationship between reliability metrics
+
+```{r warning=FALSE, message=FALSE}
+p1 = boot_df %>%
   ggplot(aes(spearman, icc, col=task))+
@@
 
-p2 = rel_df %>%
+p2 = boot_df %>%
   ggplot(aes(pearson, icc, col=task))+
@@
 
-p3 = rel_df %>%
+p3 = boot_df %>%
   ggplot(aes(pearson, spearman, col=task))+
@@
   filter(task == 'task') %>%
-  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
+  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv') %>%
   filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
@@
             median_spearman = median(spearman),
+            min_icc = min(icc),
+            max_icc = max(icc),
+            min_spearman = min(spearman),
+            max_spearman = max(spearman),
             num_measures = n(),
-            num_trials = unique(num_all_trials)) %>%
+            num_trials = unique(num_all_trials))%>%
   arrange(-median_icc, -median_spearman)
@@
   datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
+  formatRound(columns=c('median_spearman', 'median_icc',
+                        'min_spearman', 'min_icc',
+                        'max_spearman', 'max_icc'), digits=3)
 ```

### 2017-11-17 code/SRO_Report.Rmd
cont clean report

@@
 
-ggsave('Rel_Histograms.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
-```
-
-### Relationship between reliability metrics
-
-```{r warning=FALSE, message=FALSE}
-p1 = boot_df %>%
+ggsave('Booth_Rel_Histograms.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
+```
+
+### Relationship between reliability metrics (point estimates)
+
+Bootstrapped version is essentially the same.
+
+```{r warning=FALSE, message=FALSE}
+p1 = rel_df %>%
   ggplot(aes(spearman, icc, col=task))+
@@
 
-p2 = boot_df %>%
+p2 = rel_df %>%
   ggplot(aes(pearson, icc, col=task))+
@@
 
-p3 = boot_df %>%
+p3 = rel_df %>%
   ggplot(aes(pearson, spearman, col=task))+
@@
   filter(task == 'task') %>%
-  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
+  # left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
+  left_join(boot_df[,c("dv", "spearman","icc")], by='dv') %>%
   filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
@@
 
-summary(lm(icc ~ num_all_trials, data = tmp))
+# summary(lm(icc ~ num_all_trials, data = tmp))
+summary(lmer(icc ~ num_all_trials + (1|dv), data = tmp))
 ```
@@
 
-## Reliability by variable types
-
-In this section we label the measures based on the procedure behind the creation of a variable.
-This moves further away from the literature and thinking about our measures in terms of specific tasks, surveys or cognitive processes and is a more novel way of presenting our data.
-
-Potentially prescriptive recommendations coming out of this section would intend to build intuitions about different treatments to data that have higher reliabilities especially when researchers plan on making their own tasks and collecting different kinds of measures.
-
-### Tasks
-
-#### DDM parameters
-
-```{r warning=FALSE, message=FALSE}
-tmp = measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  filter(ddm_task == 1) %>%
-  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.', remove=FALSE) %>%
-  select(-extra_1, -extra_2) %>%
-  drop_na()
-```
-
-In addition to raw response time and accuracy measures we get from certain tasks we have also chosen to fit drift diffusion models to them.
-The tasks we have chosen to fit these models are: `unique(tmp$task_name)`.
-This list does not include all cognitive tasks in the battery.
-
-Table of median reliabilities for the two kinds of DDM models' (hddm and EZ) parameters compared to raw response times and accuracies depending on whether they were fit to all data or whether they are contrast of two conditions sorted by mean ICC and mean Spearman's $\rho$.
-
-- All parameters that were fit to all trials compared to contrasts have higher relialibilities.   
-- Raw variables are not the variables with highest ICC's overall supporting the idea of using these parameters as individual difference variables that are more interpretable.
-
-```{r warning=FALSE, message=FALSE}
-tmp %>%
-  group_by(overall_difference, raw_fit, rt_acc) %>%
-  summarise(median_icc = median(icc),
-            median_spearman = median(spearman),
-            n_vars = n()) %>%
-  arrange(-median_icc, -median_spearman) %>%
-  datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
-```
-
-Plot the distributions of different types of variables
-
-```{r warning=FALSE, message=FALSE}
-measure_labels %>%
-  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
-  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
-  filter(task == "task") %>%
-  select(-var, -task) %>%
-  left_join(rel_df[,c("dv", "icc")], by="dv")%>%
-  na.omit() %>%
-  filter(overall_difference!='condition',
-         raw_fit != 'fit',
-         rt_acc != 'other') %>%
-  ggplot(aes(x=factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")),y=icc,fill=rt_acc))+
-  geom_boxplot(position = position_dodge(width=0.75))+
-  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
-  theme_bw()+
-  xlab("")+
-  ylab("ICC")+
-  theme(legend.title = element_blank())
-
-ggsave('DDM_comparisons.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
-```
-
-Are these differences meaningful?
-
-Reliabilities for difference variables is lower.
-
-```{r message=FALSE, warning=FALSE}
-tmp = measure_labels %>%
-  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
-  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
-  filter(task == "task") %>%
-  select(-var, -task) %>%
-  left_join(rel_df[,c("dv", "icc")], by="dv")%>%
-  na.omit() %>%
-  filter(overall_difference!='condition',
-         raw_fit != 'fit',
-         rt_acc != 'other')
-
-summary(lm(icc ~ overall_difference*raw_fit,tmp))
-```
-
 ## Completion times
+
+### Subject level
 
@@
 The effect of number of days in between in the full model where the difference scores are regressed on a fixed effect for measure and days between the two scores and random intercepts for each subject (*Should this model include the interaction between the fixed effects?*).
-Since there are over 300 measures the output of the full model is not presented here.
+Since there are over 400 measures the output of the full model is not presented here.
 Instead below are the coefficient for the fixed effect of days between completion times and its t value.
@@
 rm(tmp)
+```
+
+### Task level
+
+For each variable does the average difference between two time points vary by the average number of days between the two time points?
+No.
+The slopes of these lines or the interaction is not significant.
+
+```{r warning=FALSE, message=FALSE}
+t1_2_difference <- t1_2_difference %>%
+  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
+  select(-extra_1, -extra_2) %>% 
+  mutate(task = ifelse(grepl("survey",dv), "survey","task"),
+           task = ifelse(grepl("holt",dv), "task", task))
+
+# summary(lmer(difference ~ days_btw + (task_name|sub_id), t1_2_difference))
+
+t1_2_difference %>%
+  mutate(task = ifelse(grepl("survey",dv), "survey","task"),
+           task = ifelse(grepl("holt",dv), "task", task)) %>%
+  group_by(dv) %>%
+  summarise(mean_diff = mean(difference),
+            mean_days_btw = mean(days_btw),
+            task = unique(task)) %>%
+  ggplot(aes(mean_days_btw, mean_diff, color=task))+
+  geom_point()+
+  theme_bw()+
+  geom_smooth(method="lm")+
+  xlab("Average days between completion")+
+  ylab("Average difference between time points")+
+  theme(legend.title = element_blank())
+```
+
+```{r}
+tmp = t1_2_difference %>%
+  group_by(dv) %>%
+  summarise(mean_diff = mean(difference),
+            mean_days_btw = mean(days_btw),
+            task = unique(task))
+
+summary(lm(mean_diff ~ mean_days_btw*task, tmp))
+```
+
+## Learning effects
+
+Is the t2 score higher for task variables?
+Plotting the average difference between time points (for all subjects) for each dependent variable coloring by task.
+More positive on the y-axis means more improvement.
+Didn't want to summarize it at task level because not all measures might be things we'd expect learning effects on.
+
+It's hard to detect any meaningful global changes/improvements from this graph.
+It seems that for each task there might be some variables that have improved at t2 but whether these are menaingful learning effects should be determined based on the variable.
+
+```{r}
+t1_2_difference %>%
+  filter(task == "task") %>%
+  group_by(dv) %>%
+  summarise(mean_diff = mean(difference),
+            task_name = unique(task_name)) %>%
+  ggplot(aes(dv,mean_diff, color=task_name))+
+  geom_point()+
+  theme_bw()+
+  theme(legend.position = "none",
+        axis.text.x = element_blank())+
+  xlab("Dependent variable")+
+  ylab("Average difference between time points")
 ```

### 2017-11-19 code/SRO_Report.Rmd
Cleaning up report

@@
 
-## Reliability metrics
+## Relationship between reliability metrics (point estimates)
 
@@
 ```{r}
+#Create df of point estimate reliabilities
 numeric_cols = c()
@@
 
+Though we are primarily reporting ICC's as our metric of reliability the results don't change depending on the metric chosen.
+Here we plot point estimates of three different reliability metrics against each other (ICC, Pearson, Spearman).
+The bootstrapped version is essentially the same but the plots are busier due to more datapoints.
+
+```{r warning=FALSE, message=FALSE}
+p1 = rel_df %>%
+  ggplot(aes(spearman, icc, col=task))+
+  geom_point()+
+  theme_bw()+
+  theme(legend.title = element_blank(),
+        legend.position = "none")+
+  geom_abline(intercept = 0, slope=1)
+
+p2 = rel_df %>%
+  ggplot(aes(pearson, icc, col=task))+
+  geom_point()+
+  theme_bw()+
+  theme(legend.title = element_blank(),
+        legend.position = "none")+
+  geom_abline(intercept = 0, slope=1)
+
+p3 = rel_df %>%
+  ggplot(aes(pearson, spearman, col=task))+
+  geom_point()+
+  theme_bw()+
+  theme(legend.title = element_blank(),
+        legend.position = "none")+
+  geom_abline(intercept = 0, slope=1)
+
+grid.arrange(p1, p2, p3, nrow=1)
+
+ggsave('Metric_Scatterplots.jpg', plot = grid.arrange(p1, p2, p3, nrow=1), device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
+```
+
+```{r echo=FALSE}
+rm(p1,p2,p3)
+```
+
+Note: Some variables have <0 ICC's. This would be the case if the $MS_{error}$>$MS_{between}$. Data for these variables have no relationship between the two time points.
+
+## Summary of all measure reliabilities
+
 Summarized bootstrapped reliabilities
@@
 
-Comparison of survey measures to cognitive task measures in the bootstrapped results. Multilevel model with random intercepts for each measure and fixed effect of survey versus cognitive measure.
-
-```{r}
-boot_df = boot_df %>%
-    mutate(task = ifelse(grepl("survey",dv), "survey","task"),
-           task = ifelse(grepl("holt",dv), "task", task))
-
-boot_df %>%
-  group_by(task) %>%
-  summarise(icc_median = quantile(icc, probs = 0.5),
-            icc_2.5 = quantile(icc, probs = 0.025),
-            icc_97.5 = quantile(icc, probs = 0.975),
-            spearman_median = quantile(spearman, probs = 0.5),
-            spearman_2.5 = quantile(spearman, probs = 0.025),
-            spearman_97.5 = quantile(spearman, probs = 0.975),
-            num_vars = n()/1000) %>%
-  datatable() %>%
-  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
-```
-
-```{r}
-summary(lmerTest::lmer(icc ~  task + (1|dv), boot_df))
-```
-
-```{r warning=FALSE, message=FALSE}
-boot_df %>%
-  ggplot(aes(icc, fill = task))+
-  geom_histogram(alpha=0.5, position='identity')+
-  theme_bw()+
-  theme(legend.title = element_blank())+
-  xlab("ICC")
-
-ggsave('Hist_Boot_Rel.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 72)
-```
-
 ```{r echo=FALSE}
@@
 measure_labels = measure_labels %>% select(-measure_description,-measure_type,-measure_type_Ian,-measure_type_Russ,-notes,-Patrick_hates)
-```
-
-Checking DDM results in the bootstrapped estimates.
-Variables using all trials are significantly more reliable compared to difference scores.
-Raw measures don't differ from DDM parameters.
-Which DDM is better depends on whether all trials are used.
-
-```{r warning=FALSE, message=FALSE}
-tmp = measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(ddm_task == 1, 
-         overall_difference != "condition") %>%
-  drop_na() %>%
-  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')
-
-tmp %>%
-  group_by(overall_difference, raw_fit, rt_acc) %>%
-  summarise(icc_median = quantile(icc, probs = 0.5),
-            icc_2.5 = quantile(icc, probs = 0.025),
-            icc_97.5 = quantile(icc, probs = 0.975),
-            spearman_median = quantile(spearman, probs = 0.5),
-            spearman_2.5 = quantile(spearman, probs = 0.025),
-            spearman_97.5 = quantile(spearman, probs = 0.975),
-            num_vars = n()/1000) %>%
-  datatable() %>%
-  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
-```
-
-```{r}
-summary(lmerTest::lmer(icc ~ overall_difference*raw_fit + (1|dv) ,tmp))
-```
-
-```{r}
-tmp %>%
-  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy","other", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy", "Other","Drift Rate", "Threshold", "Non-decision"))))+
-  geom_boxplot()+
-  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
-  theme_bw()+
-  ylab("ICC")+
-  xlab("")+
-  theme(legend.title = element_blank())
-
-ggsave('Bootstrap_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 6, units = "in", limitsize = FALSE)
 ```
@@
 
-### Histograms of reliability metrics
-
-```{r warning=FALSE, message=FALSE}
+## Survey vs Tasks
+
+Comparison of survey measures to cognitive task measures in the bootstrapped results. Multilevel model with random intercepts for each measure and fixed effect of survey versus cognitive measure.
+
+```{r}
+boot_df = boot_df %>%
+    mutate(task = ifelse(grepl("survey",dv), "survey","task"),
+           task = ifelse(grepl("holt",dv), "task", task))
+
 boot_df %>%
-  select(dv, task, spearman, pearson, icc) %>%
-  gather(key, value, -dv, -task) %>%
-  ggplot(aes(value, fill=task))+
-  geom_histogram(alpha = 0.5, position = 'identity')+
-  facet_wrap(~key)+
-  theme_bw()+
-  theme(legend.position = 'bottom',
-        legend.title = element_blank())+
+  group_by(task) %>%
+  summarise(icc_median = quantile(icc, probs = 0.5),
+            icc_2.5 = quantile(icc, probs = 0.025),
+            icc_97.5 = quantile(icc, probs = 0.975),
+            spearman_median = quantile(spearman, probs = 0.5),
+            spearman_2.5 = quantile(spearman, probs = 0.025),
+            spearman_97.5 = quantile(spearman, probs = 0.975),
+            num_vars = n()/1000) %>%
+  datatable() %>%
+  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
+```
+
+```{r}
+summary(lmerTest::lmer(icc ~  task + (1|dv), boot_df))
+```
+
+```{r warning=FALSE, message=FALSE}
+boot_df %>%
+  ggplot(aes(icc, fill = task))+
+  geom_histogram(alpha=0.5, position='identity')+
+  theme_bw()+
+  theme(legend.title = element_blank())+
+  xlab("ICC")
+
+ggsave('Hist_Boot_Rel.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 72)
+```
+
+### Variance breakdown
+
+The quantiative explanation for the difference in reliability estimates between surveys and tasks, as recently detailed by Hedge et al.
+(2017), lies in the difference in sources of variance between these measures.
+This is because reliability is estimated as a ratio of these sources variance to each other.
+Specifically, the ICC is calculated as the ratio of variance between subjects variance to all sources of variance.
+Thus, measures with high between subjects variance would have high test-retest reliability.
+Intuitively, measures with high between subjects variance are also better suited for individual difference analyses as they would capture the differences between the subjects in a sample.
+
+Here we first plot the percentage of variance explained by the three sources of variance for the point estimates of measure reliabilities.
+The plot only includes raw measures (no DDM parameters) and the measures are ranked by percentage of between subject variability for each task/survey (i.e.
+the best to worst individual difference measure for each task/survey).
+Then we compare statistically whether the percentage of variance explained by these sources differ between tasks and surveys.
+
+```{r warning=FALSE, message=FALSE}
+tmp = rel_df %>%
+  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
+         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
+         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
+  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
+  mutate(dv = factor(dv, levels = dv[order(task)])) %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  arrange(task_group, var_subs_pct) %>%
+  mutate(rank = row_number()) %>%
+  arrange(task, task_group, rank) %>%
+  gather(key, value, -dv, -task_group, -var, -task, -rank) %>%
+  ungroup()%>%
+  mutate(task_group = gsub("_", " ", task_group),
+         var = gsub("_", " ", var)) %>%
+  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
+  mutate(task_group = gsub("survey", "", task_group)) %>%
+  filter(task=="task",
+         !grepl("EZ|hddm", dv))%>%
+  arrange(task_group, rank)
+labels = tmp %>%
+  distinct(dv, .keep_all=T)
+
+p1 <- tmp %>%
+  ggplot(aes(x=factor(rank), y=value, fill=factor(key, levels = c("var_resid_pct", "var_ind_pct", "var_subs_pct"))))+
+  geom_bar(stat='identity', alpha = 0.75, color='#00BFC4')+
+  scale_x_discrete(breaks = labels$rank,
+                       labels = labels$var)+
+  coord_flip()+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey85"),
+        legend.position = 'bottom')+
+  theme(legend.title = element_blank())+
+  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
+                      labels = c("Variance between individuals",
+                                 "Variance between sessions",
+                                 "Error variance"),
+                  values=c("grey65", "grey45", "grey25"))+
+  ylab("")+
   xlab("")
 
-ggsave('Booth_Rel_Histograms.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
-```
-
-### Relationship between reliability metrics (point estimates)
-
-Bootstrapped version is essentially the same.
-
-```{r warning=FALSE, message=FALSE}
-p1 = rel_df %>%
-  ggplot(aes(spearman, icc, col=task))+
-  geom_point()+
-  theme_bw()+
-  theme(legend.title = element_blank(),
-        legend.position = "none")+
-  geom_abline(intercept = 0, slope=1)
-
-p2 = rel_df %>%
-  ggplot(aes(pearson, icc, col=task))+
-  geom_point()+
-  theme_bw()+
-  theme(legend.title = element_blank(),
-        legend.position = "none")+
-  geom_abline(intercept = 0, slope=1)
-
-p3 = rel_df %>%
-  ggplot(aes(pearson, spearman, col=task))+
-  geom_point()+
-  theme_bw()+
-  theme(legend.title = element_blank(),
-        legend.position = "none")+
-  geom_abline(intercept = 0, slope=1)
-
-grid.arrange(p1, p2, p3, nrow=1)
-
-ggsave('Metric_Scatterplots.jpg', plot = grid.arrange(p1, p2, p3, nrow=1), device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
-```
-
-```{r echo=FALSE}
-rm(p1,p2,p3)
-```
-
-Note: Some variables have <0 ICC's. This would be the case if the $MS_{error}$>$MS_{between}$. Data for these variables have no relationship between the two time points.
+tmp = rel_df %>%
+  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
+         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
+         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
+  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
+  mutate(dv = factor(dv, levels = dv[order(task)])) %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  arrange(task_group, var_subs_pct) %>%
+  mutate(rank = row_number()) %>%
+  arrange(task, task_group, rank) %>%
+  gather(key, value, -dv, -task_group, -var, -task, -rank) %>%
+  ungroup()%>%
+  mutate(task_group = gsub("_", " ", task_group),
+         var = gsub("_", " ", var)) %>%
+  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
+  mutate(task_group = gsub("survey", "", task_group)) %>%
+  filter(task=="survey")%>%
+  arrange(task_group, rank)
+labels = tmp %>%
+  distinct(dv, .keep_all=T)
+
+p2 <- tmp %>%
+  ggplot(aes(x=factor(rank), y=value, fill=factor(key, levels = c("var_resid_pct", "var_ind_pct", "var_subs_pct"))))+
+  geom_bar(stat='identity', alpha = 0.75)+
+  geom_bar(stat='identity', color='#F8766D', show.legend=FALSE)+
+  scale_x_discrete(breaks = labels$rank,
+                       labels = labels$var)+
+  coord_flip()+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey85"),
+        legend.position = 'bottom')+
+  theme(legend.title = element_blank())+
+  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
+                      labels = c("Variance between individuals",
+                                 "Variance between sessions",
+                                 "Error variance"),
+                  values=c("grey65", "grey45", "grey25"))+
+  ylab("")+
+  xlab("")
+
+mylegend<-g_legend(p2)
+
+p3 <- arrangeGrob(arrangeGrob(p1 +theme(legend.position="none"),
+                         p2 + theme(legend.position="none"),
+                         nrow=1),
+             mylegend, nrow=2,heights=c(10, 1))
+
+ggsave('Variance_Breakdown_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 24, height = 20, units = "in")
+rm(tmp, labels)
+```
+
+```{r echo=FALSE, out.width='100%'}
+knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Variance_Breakdown_Plot.jpg')
+```
+
+Comparing types of variance for survey vs task measures: Survey measures have higher between subject variability
+
+Note: This analysis includes DDM variables too.
+
+```{r}
+tmp = boot_df %>%
+  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
+         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
+         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
+  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
+  gather(key, value, -dv, -task)
+
+summary(lmer(value~key*task+(1|dv),tmp))
+```
+
+```{r}
+aggregate(value ~task+key, FUN=mean, data=tmp)
+
+tmp%>%
+  group_by(task, key) %>%
+  summarise(median = median(value),
+            sd = sd(value))
+```
+
+Summarizing for clearer presentation. This grap is currently using the bootstrapped reliabilities and is therefore messier than if just using the point estimates.
+
+```{r}
+tmp %>%
+  group_by(task, key) %>%
+  ggplot(aes(factor(task, levels=c("task","survey"), labels=c("Task", "Survey")), value, fill=key, color=task))+
+  geom_boxplot()+
+  theme_bw()+
+  theme(legend.title = element_blank())+
+  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
+                    labels = c("Variance between individuals",
+                               "Variance between sessions",
+                               "Error variance"),
+                    values=c("grey65", "grey45", "grey25"))+
+  scale_color_discrete(guide = FALSE)+
+  xlab("")+
+  ylab("Percent")
+
+ggsave('Variance_Breakdown_Plot_Summary.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in")
+```
 
@@
 
+### Number of trials
+
 Does number of items in a task have a significant effect on the average ICC of (mostly) raw measures for all trials from a task? No. (no effect on Spearman either)
@@
 
-## Completion times
-
-### Subject level
-
-Do people differ in how much their scores change depending on how many days it has been since they completed the initial battery?
-
-Make data frame with difference between two scores for each measure for each subject.
-Since the scores for different measures are on different scales for comparability the difference scores are scaled (i.e.
-divided by their root mean square) but not centered so a value of 0 for the difference scores would indicate a lack of a difference between the scores of a subject.
-
-```{r warning=FALSE}
-t1_2_difference = data.frame()
-
-for(i in 1:length(numeric_cols)){
-  tmp = match_t1_t2(numeric_cols[i],format='wide')
-  tmp = tmp %>% 
-    # mutate(difference = scale(`2` - `1`))
-  mutate(difference = scale(`2` - `1`, center=F))
-  t1_2_difference = rbind(t1_2_difference, tmp)
-}
-
-t1_2_difference$difference = as.data.frame(t1_2_difference$difference)$V1
-```
-
-```{r echo=FALSE}
-rm(tmp, i)
-```
-
-Add completion dates to this data frame.
-
-```{r warning=FALSE}
-t1_2_difference = merge(t1_2_difference, comp_dates[,c('sub_id', 'days_btw')], by='sub_id')
-```
-
-```{r echo=FALSE}
-rm(test_comp_date, retest_comp_date, comp_dates)
-```
-
-The effect of number of days in between in the full model where the difference scores are regressed on a fixed effect for measure and days between the two scores and random intercepts for each subject (*Should this model include the interaction between the fixed effects?*).
-Since there are over 400 measures the output of the full model is not presented here.
-Instead below are the coefficient for the fixed effect of days between completion times and its t value.
-
-```{r}
-mod = lmer(difference ~ dv + days_btw + (1|sub_id), data = t1_2_difference)
-
-data.frame(estimate=coef(summary(mod))["days_btw","Estimate"], tval=coef(summary(mod))["days_btw","t value"])
-```
-
-For visualization purposes I summarized the difference scores per person by looking at the average difference and plot that against the number of days between completion.
-
-```{r warning=FALSE, message=FALSE}
-tmp = t1_2_difference %>%
-  group_by(sub_id) %>%
-  summarise(mean_diff = mean(difference, na.rm=T),
-            days_btw = unique(days_btw))
+#### Trial number dependence intrameasure
+
+The above analysis was looking at the effect of number of trials across tasks.
+But some tasks might be bad for individual difference measurement regardless of how many trials there are in them whereas for others fewer trials might be yielding a sufficiently reliable measure.
+
+For tasks for which dependent variables are estimated using many trials one can ask: Does the same measure get less reliable if fewer trials are used to estimate its reliability?
+
+This won't make sense for all tasks.
+For example to estimate a risk aversion parameter you need all trials for Holt and Laury.
+For Kirby and Bickel you have specific conditions looking at fewer trials.
+The Cognitive Reflection Task might be more appropriate to analyze each item seaprately.
+The writing task does not have trial numbers.
+For all others it might be interesting to investigate.
+
+That said this kind of analysis seems too in the weeds for a paper that is trying to give a global sense of the differences between self-regulation measures in their suitablity for individual difference analyses based on their stability across time.
+Such analyses would provide a detailed examination of how to extract the most reliable/best individual difference measure from tasks with a set of mediocre variables to begin with.
+So I am choosing to ignore this for now but this can be revisited.
+
+### Raw vs DDM
+
+Checking DDM results in the bootstrapped estimates.
+Variables using all trials are significantly more reliable compared to difference scores.
+Raw measures don't differ from DDM parameters.
+Which DDM is better depends on whether all trials are used.
+
+```{r warning=FALSE, message=FALSE}
+tmp = measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(ddm_task == 1, 
+         overall_difference != "condition") %>%
+  drop_na() %>%
+  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')
 
 tmp %>%
-  ggplot(aes(days_btw, mean_diff))+
-  geom_point()+
-  theme_bw()+
-  xlab("Days between completion")+
-  ylab("Mean standardized difference between two time points")+
-  geom_smooth(method="lm")
-```
-
-To confirm: the slope of this line is not significant.
-That is, there doesn't seem to be a systematic difference between the two measurements depending on the number of days between the two measurements.
-
-```{r warning=FALSE, message=FALSE}
-summary(lm(mean_diff ~ days_btw, data=tmp))
-```
-
-```{r echo=FALSE}
-rm(tmp)
-```
-
-### Task level
-
-For each variable does the average difference between two time points vary by the average number of days between the two time points?
-No.
-The slopes of these lines or the interaction is not significant.
-
-```{r warning=FALSE, message=FALSE}
-t1_2_difference <- t1_2_difference %>%
-  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
-  select(-extra_1, -extra_2) %>% 
-  mutate(task = ifelse(grepl("survey",dv), "survey","task"),
-           task = ifelse(grepl("holt",dv), "task", task))
-
-# summary(lmer(difference ~ days_btw + (task_name|sub_id), t1_2_difference))
-
-t1_2_difference %>%
-  mutate(task = ifelse(grepl("survey",dv), "survey","task"),
-           task = ifelse(grepl("holt",dv), "task", task)) %>%
-  group_by(dv) %>%
-  summarise(mean_diff = mean(difference),
-            mean_days_btw = mean(days_btw),
-            task = unique(task)) %>%
-  ggplot(aes(mean_days_btw, mean_diff, color=task))+
-  geom_point()+
-  theme_bw()+
-  geom_smooth(method="lm")+
-  xlab("Average days between completion")+
-  ylab("Average difference between time points")+
+  group_by(overall_difference, raw_fit, rt_acc) %>%
+  summarise(icc_median = quantile(icc, probs = 0.5),
+            icc_2.5 = quantile(icc, probs = 0.025),
+            icc_97.5 = quantile(icc, probs = 0.975),
+            spearman_median = quantile(spearman, probs = 0.5),
+            spearman_2.5 = quantile(spearman, probs = 0.025),
+            spearman_97.5 = quantile(spearman, probs = 0.975),
+            num_vars = n()/1000) %>%
+  datatable() %>%
+  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
+```
+
+```{r}
+summary(lmerTest::lmer(icc ~ overall_difference*raw_fit + (1|dv) ,tmp))
+```
+
+```{r}
+tmp %>%
+  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy","other", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy", "Other","Drift Rate", "Threshold", "Non-decision"))))+
+  geom_boxplot()+
+  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
+  theme_bw()+
+  ylab("ICC")+
+  xlab("")+
   theme(legend.title = element_blank())
-```
-
-```{r}
-tmp = t1_2_difference %>%
-  group_by(dv) %>%
-  summarise(mean_diff = mean(difference),
-            mean_days_btw = mean(days_btw),
-            task = unique(task))
-
-summary(lm(mean_diff ~ mean_days_btw*task, tmp))
-```
-
-## Learning effects
-
-Is the t2 score higher for task variables?
-Plotting the average difference between time points (for all subjects) for each dependent variable coloring by task.
-More positive on the y-axis means more improvement.
-Didn't want to summarize it at task level because not all measures might be things we'd expect learning effects on.
-
-It's hard to detect any meaningful global changes/improvements from this graph.
-It seems that for each task there might be some variables that have improved at t2 but whether these are menaingful learning effects should be determined based on the variable.
-
-```{r}
-t1_2_difference %>%
-  filter(task == "task") %>%
-  group_by(dv) %>%
-  summarise(mean_diff = mean(difference),
-            task_name = unique(task_name)) %>%
-  ggplot(aes(dv,mean_diff, color=task_name))+
-  geom_point()+
-  theme_bw()+
-  theme(legend.position = "none",
-        axis.text.x = element_blank())+
-  xlab("Dependent variable")+
-  ylab("Average difference between time points")
-```
-
-## Variance breakdown
+
+ggsave('Bootstrap_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 6, units = "in", limitsize = FALSE)
+```
+
+#### DDM Variance breakdown
+
+What does the variance breakdown look like for DDM variables separately?
 
@@
   select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
-  # gather(key, value, -dv, -task) %>%
-  mutate(#key = factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct")),
-         dv = factor(dv, levels = dv[order(task)])) %>%
+  mutate(dv = factor(dv, levels = dv[order(task)])) %>%
   separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
@@
   ungroup()%>%
-  # separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
   mutate(task_group = gsub("_", " ", task_group),
          var = gsub("_", " ", var)) %>%
-         # var=gsub(".ReflogTr", "", var),
-         # var=gsub(".logTr", "", var)) %>%
   mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
@@
   filter(task=="task",
-         !grepl("EZ|hddm", dv))%>%
+         grepl("EZ|hddm", dv))%>%
   arrange(task_group, rank)
@@
         legend.position = 'bottom')+
-  #theme_bw()+  
   theme(legend.title = element_blank())+
@@
 
-tmp = rel_df %>%
-  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
-         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
-         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
-  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
-  # gather(key, value, -dv, -task) %>%
-  mutate(#key = factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct")),
-         dv = factor(dv, levels = dv[order(task)])) %>%
-  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
-  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
-  arrange(task_group, var_subs_pct) %>%
-  mutate(rank = row_number()) %>%
-  arrange(task, task_group, rank) %>%
-  gather(key, value, -dv, -task_group, -var, -task, -rank) %>%
-  ungroup()%>%
-  # separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
-  mutate(task_group = gsub("_", " ", task_group),
-         var = gsub("_", " ", var),
-         var=gsub(".ReflogTr", "", var),
-         var=gsub(".logTr", "", var)) %>%
-  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
-  mutate(task_group = gsub("survey", "", task_group)) %>%
-  filter(task=="survey")%>%
-  arrange(task_group, rank)
-labels = tmp %>%
-  distinct(dv, .keep_all=T)
-
-p2 <- tmp %>%
-  ggplot(aes(x=factor(rank), y=value, fill=factor(key, levels = c("var_resid_pct", "var_ind_pct", "var_subs_pct"))))+
-  geom_bar(stat='identity', alpha = 0.75)+
-  geom_bar(stat='identity', color='#F8766D', show.legend=FALSE)+
-  scale_x_discrete(breaks = labels$rank,
-                       labels = labels$var)+
-  coord_flip()+
-  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
-  theme(panel.spacing = unit(0.5, "lines"), 
-        strip.placement = "outside",
-        strip.text.y = element_text(angle=180),
-        panel.background = element_rect(fill = NA),
-        panel.grid.major = element_line(colour = "grey85"),
-        legend.position = 'bottom')+
-  #theme_bw()+  
-  theme(legend.title = element_blank())+
-  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
-                      labels = c("Variance between individuals",
-                                 "Variance between sessions",
-                                 "Error variance"),
-                  values=c("grey65", "grey45", "grey25"))+
-  ylab("")+
-  xlab("")
-
-mylegend<-g_legend(p2)
-
-p3 <- arrangeGrob(arrangeGrob(p1 +theme(legend.position="none"),
-                         p2 + theme(legend.position="none"),
-                         nrow=1),
-             mylegend, nrow=2,heights=c(10, 1))
-
-ggsave('Variance_Breakdown_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 24, height = 20, units = "in")
-rm(tmp, labels)
+ggsave('Variance_Breakdown_Plot_DDM.jpg', plot = p1, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 12, height = 20, units = "in")
 ```
@@
 ```{r echo=FALSE, out.width='100%'}
-knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Variance_Breakdown_Plot.jpg')
-```
-
-Comparing types of variance for survey vs task measures: Survey measures have higher between subject variability
-
-Note: This analysis includes DDM variables too.
-
-```{r}
-tmp = rel_df %>%
-  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
-         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
-         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
-  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
-  gather(key, value, -dv, -task) 
-  # do(tidy(lm(value~key*task, data=.)))
-
-summary(lm(value~key*task,tmp))
-```
-
-```{r}
-aggregate(value ~task+key, FUN=mean, data=tmp)
-```
-
-Summarizing for clearer presentation
-
-```{r}
+knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Variance_Breakdown_Plot_DDM.jpg')
+```
+
+Summarizing it by raw vs fit and for each parameter
+
+```{r warning=FALSE, message=FALSE}
+tmp = measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(ddm_task == 1, 
+         overall_difference != "condition") %>%
+  drop_na() %>%
+  left_join(boot_df[,c("dv", "icc", "var_subs", "var_ind", "var_resid")], by = 'dv') %>%
+  mutate(var_subs_pct = (var_subs/(var_subs+var_ind+var_resid))*100,
+         var_ind_pct= (var_ind/(var_subs+var_ind+var_resid))*100,
+         var_resid_pct = (var_resid/(var_subs+var_ind+var_resid))*100) %>%
+  select(-task, -ddm_task, -num_all_trials, -var_subs, -var_ind, -var_resid) %>%
+  gather(key, value, -dv, -overall_difference, -raw_fit, -rt_acc, -icc)
+
 tmp %>%
-  group_by(task, key) %>%
-  ggplot(aes(factor(task, levels=c("task","survey"), labels=c("Task", "Survey")), value, fill=key, color=task))+
+  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), value, fill=factor(rt_acc, levels = c("rt","accuracy","other", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy", "Other","Drift Rate", "Threshold", "Non-decision"))))+
   geom_boxplot()+
-  theme_bw()+
-  theme(legend.title = element_blank())+
-  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
-                    labels = c("Variance between individuals",
-                               "Variance between sessions",
-                               "Error variance"),
-                    values=c("grey65", "grey45", "grey25"))+
-  scale_color_discrete(guide = FALSE)+
+  facet_grid(factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct"), labels=c("Variance between subjects", "Variance between individuals", "Error variance"))~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
+  theme_bw()+
+  ylab("% of total variance")+
   xlab("")+
-  ylab("Percent")
-
-ggsave('Variance_Breakdown_Plot_Summary.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in")
-```
-
-What does it look like for DDM variables separately?
-
-```{r warning=FALSE, message=FALSE}
-p1_ddm = rel_df %>%
-  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
-         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
-         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
-  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
-  gather(key, value, -dv, -task) %>%
-  mutate(key = factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct")),
-         dv = factor(dv, levels = dv[order(task)])) %>%
-  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
-  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
-  # separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
-  mutate(task_group = gsub("_", " ", task_group),
-         var = gsub("_", " ", var),
-         var=gsub(".ReflogTr", "", var),
-         var=gsub(".logTr", "", var)) %>%
-  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
-  mutate(task_group = gsub("survey", "", task_group)) %>%
-  filter(task=="task",
-         grepl("EZ|hddm", dv))%>%
-  ggplot(aes(x=var, y=value, fill=key))+
-  geom_bar(stat='identity', alpha = 0.75)+
-  coord_flip()+
-  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
-  theme(panel.spacing = unit(0.5, "lines"), 
-        strip.placement = "outside",
-        strip.text.y = element_text(angle=180),
-        panel.background = element_rect(fill = NA),
-        panel.grid.major = element_line(colour = "grey80"),
-        legend.position = 'bottom')+
-  #theme_bw()+  
-  theme(legend.title = element_blank())+
-  scale_fill_discrete(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
-                    labels = c("Variance between individuals",
-                               "Variance between sessions",
-                               "Error variance"),
-                     h=c(100,500))+
-  ylab("")+
-  xlab("")
-
-ggsave('Variance_Breakdown_Plot_DDM.jpg', plot = p1_ddm, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 12, height = 20, units = "in")
-```
+  theme(legend.title = element_blank())
+
+ggsave('Variance_Breakdown_Plot_DDM_summary.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 8, units = "in")
+```
+
+Do these differ statistically?
+
+The plot does not suggest so but this model is giving a warning and very high t values. How else should I be checking for differences between these distributions?
+
+```{r}
+summary(lmer(value~key*overall_difference*raw_fit+(1|dv), tmp))
+```
+
+#### Change in parameter values depending on sample
+
+How much do parameter values change depending on whether the model was fit using the whole sample vs only the retest sample.
+Each point in these graphs is a subject's parameter estimates.
+There is almost no change for any of the EZ parameters (though shouldn't this have been 0?).
+For the HDDM parameters most of the changes are happening for drift rates but they don't appear to be systematically higher or lower.
+
+I'm not entirely sure what to make of this
+
+```{r warning=FALSE, message=FALSE}
+hddm_fullfits <- test_data_full_sample_hddm[,names(test_data_full_sample_hddm) %in% names(hddm_refits)]
+
+hddm_fullfits = hddm_fullfits %>%
+  gather(dv, value, -sub_id)
+
+hddm_refits %>%
+  gather(dv, value, -sub_id) %>%
+  left_join(hddm_fullfits, by = c("sub_id", "dv")) %>%
+  rename(fullfit = value.y, refit = value.x) %>%
+  left_join(measure_labels[,c("dv", "raw_fit", "rt_acc")], by="dv") %>%
+  filter(rt_acc %in% c("drift rate","non-decision", "threshold")) %>%
+  ggplot(aes(fullfit, refit))+
+  geom_point(aes(color=rt_acc))+
+  facet_wrap(~raw_fit)+
+  theme_bw()+
+  geom_abline(slope=1, intercept=0)+
+  xlab("Fit on full sample")+
+  ylab("Fit on retest sample")+
+  theme(legend.title = element_blank())
+```
+
+```{r message=FALSE}
+tmp = hddm_refits %>%
+  gather(dv, value, -sub_id) %>%
+  left_join(hddm_fullfits, by = c("sub_id", "dv")) %>%
+  rename(fullfit = value.y, refit = value.x) %>%
+  left_join(measure_labels[,c("dv", "raw_fit", "rt_acc")], by="dv") %>%
+  filter(rt_acc %in% c("drift rate","non-decision", "threshold"))
+```
+
+#### Parameter reliability depending on sample size
+
+```{r}
+
+```
+
+#### Is the H in HDDM important?
+
+```{r}
+
+```
+
+## Completion times
+
+### Subject level
+
+Do people differ in how much their scores change depending on how many days it has been since they completed the initial battery?
+
+Make data frame with difference between two scores for each measure for each subject.
+Since the scores for different measures are on different scales for comparability the difference scores are scaled (i.e.
+divided by their root mean square) but not centered so a value of 0 for the difference scores would indicate a lack of a difference between the scores of a subject.
+
+```{r warning=FALSE}
+t1_2_difference = data.frame()
+
+for(i in 1:length(numeric_cols)){
+  tmp = match_t1_t2(numeric_cols[i],format='wide')
+  tmp = tmp %>% 
+    # mutate(difference = scale(`2` - `1`))
+  mutate(difference = scale(`2` - `1`, center=F))
+  t1_2_difference = rbind(t1_2_difference, tmp)
+}
+
+t1_2_difference$difference = as.data.frame(t1_2_difference$difference)$V1
+```
+
+```{r echo=FALSE}
+rm(tmp, i)
+```
+
+Add completion dates to this data frame.
+
+```{r warning=FALSE}
+t1_2_difference = merge(t1_2_difference, comp_dates[,c('sub_id', 'days_btw')], by='sub_id')
+```
+
+```{r echo=FALSE}
+rm(test_comp_date, retest_comp_date, comp_dates)
+```
+
+The effect of number of days in between in the full model where the difference scores are regressed on a fixed effect for measure and days between the two scores and random intercepts for each subject (*Should this model include the interaction between the fixed effects?*).
+Since there are over 400 measures the output of the full model is not presented here.
+Instead below are the coefficient for the fixed effect of days between completion times and its t value.
+
+```{r}
+mod = lmer(difference ~ dv + days_btw + (1|sub_id), data = t1_2_difference)
+
+data.frame(estimate=coef(summary(mod))["days_btw","Estimate"], tval=coef(summary(mod))["days_btw","t value"])
+```
+
+For visualization purposes I summarized the difference scores per person by looking at the average difference and plot that against the number of days between completion.
+
+```{r warning=FALSE, message=FALSE}
+tmp = t1_2_difference %>%
+  group_by(sub_id) %>%
+  summarise(mean_diff = mean(difference, na.rm=T),
+            days_btw = unique(days_btw))
+
+tmp %>%
+  ggplot(aes(days_btw, mean_diff))+
+  geom_point()+
+  theme_bw()+
+  xlab("Days between completion")+
+  ylab("Mean standardized difference between two time points")+
+  geom_smooth(method="lm")
+```
+
+To confirm: the slope of this line is not significant.
+That is, there doesn't seem to be a systematic difference between the two measurements depending on the number of days between the two measurements.
+
+```{r warning=FALSE, message=FALSE}
+summary(lm(mean_diff ~ days_btw, data=tmp))
+```
+
+```{r echo=FALSE}
+rm(tmp)
+```
+
+### Task level
+
+For each variable does the average difference between two time points vary by the average number of days between the two time points?
+No.
+The slopes of these lines or the interaction is not significant.
+
+```{r warning=FALSE, message=FALSE}
+t1_2_difference <- t1_2_difference %>%
+  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
+  select(-extra_1, -extra_2) %>% 
+  mutate(task = ifelse(grepl("survey",dv), "survey","task"),
+           task = ifelse(grepl("holt",dv), "task", task))
+
+# summary(lmer(difference ~ days_btw + (task_name|sub_id), t1_2_difference))
+
+t1_2_difference %>%
+  mutate(task = ifelse(grepl("survey",dv), "survey","task"),
+           task = ifelse(grepl("holt",dv), "task", task)) %>%
+  group_by(dv) %>%
+  summarise(mean_diff = mean(difference),
+            mean_days_btw = mean(days_btw),
+            task = unique(task)) %>%
+  ggplot(aes(mean_days_btw, mean_diff, color=task))+
+  geom_point()+
+  theme_bw()+
+  geom_smooth(method="lm")+
+  xlab("Average days between completion")+
+  ylab("Average difference between time points")+
+  theme(legend.title = element_blank())
+```
+
+```{r}
+tmp = t1_2_difference %>%
+  group_by(dv) %>%
+  summarise(mean_diff = mean(difference),
+            mean_days_btw = mean(days_btw),
+            task = unique(task))
+
+summary(lm(mean_diff ~ mean_days_btw*task, tmp))
+```
+
+## Learning effects
+
+Is the t2 score higher for task variables?
+Plotting the average difference between time points (for all subjects) for each dependent variable coloring by task.
+More positive on the y-axis means more improvement.
+Didn't want to summarize it at task level because not all measures might be things we'd expect learning effects on.
+
+It's hard to detect any meaningful global changes/improvements from this graph.
+It seems that for each task there might be some variables that have improved at t2 but whether these are menaingful learning effects should be determined based on the variable.
+
+```{r}
+t1_2_difference %>%
+  filter(task == "task") %>%
+  group_by(dv) %>%
+  summarise(mean_diff = mean(difference),
+            task_name = unique(task_name)) %>%
+  ggplot(aes(dv,mean_diff, color=task_name))+
+  geom_point()+
+  theme_bw()+
+  theme(legend.position = "none",
+        axis.text.x = element_blank())+
+  xlab("Dependent variable")+
+  ylab("Average difference between time points")
+```
+
+## Transformation effects

### 2017-11-20 code/SRO_Report.Rmd
rendered cleaner report

@@
 for(i in 1:length(names(test_data))){
-  if(is.numeric(test_data[,i])){
+  if(is.numeric(test_data[,i]) & names(test_data)[i] %in% names(retest_data)){
     numeric_cols <- c(numeric_cols, names(test_data)[i])
@@
 
-I'm not entirely sure what to make of this
+I'm not entirely sure what to make of this.
+A systematic change would have meant that the ranking remained the same regardless of the sample size.
+When the change is non-systematic in this way then a given subject that has high higher drift rates than most of the people in the full sample can appear to have lower drift rates than the same people when fit on the retest sample only.
+(note that a t-test is not significant)
+
+Of course these parameter estimates themselves are not very interpretable in their 'goodness' as they don't reflect anything about model fits.
+What is the measure of fits here?
+The variance of the posterior?
 
@@
 
-```{r message=FALSE}
-tmp = hddm_refits %>%
-  gather(dv, value, -sub_id) %>%
-  left_join(hddm_fullfits, by = c("sub_id", "dv")) %>%
-  rename(fullfit = value.y, refit = value.x) %>%
+#### Parameter reliability depending on sample size
+
+There doesn't seem to be an effect looking at the graph but the multilevel model seems to show a very significant but tiny effect.
+
+```{r message=FALSE, warning=FALSE}
+tmp <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/all_ddm_sample_size_summary.csv')
+
+ggplotly(tmp %>%
+  select(dv, N, icc_median) %>%
   left_join(measure_labels[,c("dv", "raw_fit", "rt_acc")], by="dv") %>%
-  filter(rt_acc %in% c("drift rate","non-decision", "threshold"))
-```
-
-#### Parameter reliability depending on sample size
-
-```{r}
-
+  ggplot(aes(N, icc_median, color=dv))+
+  geom_line()+
+  theme_bw()+
+  theme(legend.position = 'none')+
+  xlab("Sample Size")+
+  ylab("Median ICC"))
+```
+
+```{r}
+summary(lmer(icc_median ~ N + (1|dv), tmp))
 ```
@@
 
-```{r}
-
-```
+TBD. Still need to figure out how to turn off the H.
 
@@
 ## Transformation effects
+
+All results reported above were for non-transformed dependent variables.
+
+We could compare the reliability (point) estimates for meaningful variables that have been transformed in the full dataset and transformed the same way in the retest dataset as well.
+
+```{r}
+test_data_tmp <- test_data
+retest_data_tmp <- retest_data
+
+test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/t1_data/meaningful_variables_clean.csv')
+test_data$X <- as.character(test_data$X)
+names(test_data)[which(names(test_data) == 'X')] <-'sub_id' 
+retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/meaningful_variables_clean.csv')
+retest_data$X <- as.character(retest_data$X)
+names(retest_data)[which(names(retest_data) == 'X')] <-'sub_id'
+retest_data = retest_data[retest_data$sub_id %in% test_data$sub_id,]
+```
+
+```{r}
+numeric_cols_mngfl = c()
+
+for(i in 1:length(names(test_data))){
+  if(is.numeric(test_data[,i]) & names(test_data)[i] %in% names(retest_data)){
+    numeric_cols_mngfl <- c(numeric_cols_mngfl, names(test_data)[i])
+  }
+}
+
+rel_df_mngfl <- data.frame(icc = rep(NA, length(numeric_cols_mngfl)))
+
+row.names(rel_df_mngfl) <- numeric_cols_mngfl
+
+for(i in 1:length(numeric_cols_mngfl)){
+  rel_df_mngfl[numeric_cols_mngfl[i], 'icc'] <- get_icc(numeric_cols_mngfl[i])
+}
+
+rel_df_mngfl$dv = row.names(rel_df_mngfl)
+row.names(rel_df_mngfl) = seq(1:nrow(rel_df_mngfl))
+rel_df_mngfl$task = 'task'
+rel_df_mngfl[grep('survey', rel_df_mngfl$dv), 'task'] = 'survey'
+rel_df_mngfl[grep('holt', rel_df_mngfl$dv), 'task'] = "task"
+rel_df_mngfl
+```
+
+```{r}
+ggplotly(rel_df_mngfl %>%
+  filter(grepl("logTr", dv)) %>%
+  mutate(dv = gsub(".ReflogTr", "", dv),
+         dv = gsub(".logTr", "", dv)) %>%
+  left_join(rel_df[,c("dv", "icc")], by="dv") %>%
+  ggplot(aes(icc.x, icc.y, color=task, label=dv))+
+  geom_point()+
+  theme_bw()+
+  xlab("Reliability for transformed variable")+
+  ylab("Reliability for raw variable")+
+  geom_abline(slope=1, intercept=0),
+  label=dv)
+```

### 2017-11-20 code/SRO_Report.Rmd
cleaning up notes

@@
 
+NOTE: DO THIS ON AN EXAMPLE TASK AND LEAVE TO THE READER TO DO
+
 ### Raw vs DDM
@@
 
-hddm_refits %>%
+ggplotly(hddm_refits %>%
   gather(dv, value, -sub_id) %>%
@@
   filter(rt_acc %in% c("drift rate","non-decision", "threshold")) %>%
-  ggplot(aes(fullfit, refit))+
+  ggplot(aes(fullfit, refit, label=dv))+
   geom_point(aes(color=rt_acc))+
@@
   ylab("Fit on retest sample")+
-  theme(legend.title = element_blank())
+  theme(legend.title = element_blank()),
+  label=dv)
+```
+
+```{r}
+hddm_refits %>%
+  filter(adaptive_n_back.hddm_drift<0)
+  # ggplot(aes(adaptive_n_back.EZ_drift))+
+  # geom_histogram()
+
+hddm_fullfits %>%
+  filter(dv == "adaptive_n_back.hddm_drift" & value <0)
 ```
@@
   ylab("Median ICC"))
+```
+
+The above graph suggests that the median reliability estimate does not change depending on the sample size.
+There is a degree of counterintuitiveness to that statement.
+One might expect less reliable parameter estimates for smaller sample sizes.
+
+The reliability of a measure depends on the different sources of variability.
+It would be larger the larger the between subject variability (BSV) is (and the lower within subject, WSV, and error variances, ERV, are).
+Larger sample sizes do not necessarily imply larger BSV.
+If there is a true BSV for the whole sample then BSV's of subsamples would have distribution that would be centered around this value with some variance.
+This variance would be smaller the larger the sample size.
+Because the distribution is centered around the true BSV the median reliability estimate from 100 samples would not deviate much as we see in the above graph.
+But the variance of that reliability estimate would.
+Specifically the variance of the reliability estimates should decrease with increasing sample size.
+Below we plot this for one task (for visualization ease).
+The lower end of the error bars in the first quantile, the point is the median and the upper bound is the last quantile of the reliability estimates for varying sample sizes.
+Indeed, we find the predicted pattern of decreasing variance in reliability estimates depending on sample size.
+
+```{r}
+tmp %>%
+  select(dv, N, icc_median, icc_2.5, icc_97.5) %>%
+  filter(grepl("stroop", dv)) %>%
+  ggplot(aes(N, icc_median, color = dv))+
+  geom_point()+
+  geom_errorbar(aes(ymin = icc_2.5, ymax = icc_97.5))+
+  theme_bw()+
+  theme(legend.position = "none")+
+  ylab("ICC")
 ```

### 2017-11-21 code/SRO_Report.Rmd
adding new analyses

@@
 
+One way to solve this would be to feed data in manually.
+
 ## Completion times
@@
 
+```{r}
+t1_2_difference %>%
+  left_join(measure_labels[,c("dv", "overall_difference", "raw_fit", "rt_acc")], by= "dv") %>%
+  filter(overall_difference == "overall",
+         rt_acc %in% c("rt", "accuracy"),
+         task == "task") %>%
+  group_by(dv) %>%
+  summarise(mean_diff = mean(difference),
+            task_name = unique(task_name),
+            rt_acc = unique(rt_acc)) %>%  
+  ggplot(aes(dv,mean_diff, color=task_name))+
+  geom_point()+
+  theme_bw()+
+  facet_grid(~rt_acc)+
+  theme(legend.position = "none",
+        axis.text.x = element_blank())+
+  xlab("Dependent variable")+
+  ylab("Average difference between time points")
+```
+
+```{r}
+tmp = t1_2_difference %>%
+  left_join(measure_labels[,c("dv", "overall_difference", "raw_fit", "rt_acc")], by= "dv") %>%
+  filter(overall_difference == "overall",
+         rt_acc %in% c("accuracy"),
+         task == "task") %>%
+  group_by(dv) %>%
+  summarise(mean_diff = mean(difference),
+            task_name = unique(task_name))
+
+t.test(tmp$mean_diff)
+```
+
+Write new function to estimate reliability accounting for learning effect
+
+```{r}
+get
+```
+
 ## Transformation effects

### 2017-11-22 code/ICC_tutorial.Rmd
refactored repo and added first draft of lit review figure
cont working on report

--- 2017-03-20 ICC_tutorial.Rmd
@@
 
+Dataset A
+
 ```{r}
@@
 tmp = tmp %>% gather(key, value,-people)
+tmp
+```
+
+```{r}
 summary(aov(value ~ factor(key)+Error(factor(people)), tmp))
@@
 (2099-57.1)/(2099) #ICC(3,k)
+# icc(tmp, model = 'twoway', type='agreement')
+```
+
+```{r}
 tmp = tmp %>% spread(key, value) %>% select(-people)
-# icc(tmp, model = 'twoway', type='agreement')
+tmp
+```
+
+```{r}
 ICC(tmp)
 ```
+
+Dataset B
 
@@
 ```
+
+Dataset C
 

### 2017-11-22 code/SRO_Report.Rmd
cont working on report

--- 2017-11-20 code/SRO_Report.Rmd
@@
 - ICC(3,k): As Dave clarified this ranges from 1 to -1/(number of repeated measures -1) so in our case this range would be [-1, 1]; larger values would mean that the two scores of a subject for a given measure are more similar to each other than they are to scores of other people
+- " ICC is reflective of the ability of a test to differentiate between different individuals"
 - partial $\eta^2$ for time ($SS_{time}/SS_{within}$): effect size of time   
-- SEM ($\sqrt(MS_{error})$): standard error of measurement; the smaller the better
+- SEM ($\sqrt(MS_{error})$): standard error of measurement; the smaller the better. It 
+"quantifies the precision of individual scores on a test" and is not dependent on the sample in the way ICC is since it doesn't depend on between subject reliability (at least in this formulation) but is unit-dependent.
 
@@
 
-Is the t2 score higher for task variables?
-Plotting the average difference between time points (for all subjects) for each dependent variable coloring by task.
-More positive on the y-axis means more improvement.
-Didn't want to summarize it at task level because not all measures might be things we'd expect learning effects on.
-
-It's hard to detect any meaningful global changes/improvements from this graph.
-It seems that for each task there might be some variables that have improved at t2 but whether these are menaingful learning effects should be determined based on the variable.
-
-```{r}
-t1_2_difference %>%
-  filter(task == "task") %>%
-  group_by(dv) %>%
-  summarise(mean_diff = mean(difference),
-            task_name = unique(task_name)) %>%
-  ggplot(aes(dv,mean_diff, color=task_name))+
-  geom_point()+
-  theme_bw()+
-  theme(legend.position = "none",
-        axis.text.x = element_blank())+
-  xlab("Dependent variable")+
-  ylab("Average difference between time points")
-```
+For most of our tasks one might wonder about improvements in performance due to learning effects.
+
+The type of ICC we have chosen does not take ... in to account. This is why Weir recommends checking whether there is a significant change based on time and examining the SEMs.
+
+Had we chosen another kind of ICC taking ... into account could have suggested that tasks have ...(higher/lower) reliability.
+
+Doing a simple t-test on the difference score alone would not be a very rigourous way of testing whether any change is meaningful because two distributions with error would be compared to each other.
+Fortunately there are ways to take the error for both measurements in to account.
+
+To check whether a
+
+first check if the effect of time is significant
+compute confidence intervals and check what percent of participants have scores that fall out of this range
 

### 2017-11-30 code/SRO_Report.Rmd
misc

@@
 ```{r warning=FALSE, message=FALSE}
-workers = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/User_717570_workers.csv')
+workers = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/User_717570_workers.csv')
 workers = workers %>% 
@@
 
-worker_counts <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/retest_worker_counts.json')
+worker_counts <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/retest_worker_counts.json')
 
@@
 ```{r warning=FALSE, message=FALSE}
-disc_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/discovery_completion_dates.csv', header=FALSE)
-val_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/validation_completion_dates.csv', header=FALSE)
+disc_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/discovery_completion_dates.csv', header=FALSE)
+val_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/validation_completion_dates.csv', header=FALSE)
 test_comp_date = rbind(disc_comp_date, val_comp_date)
 rm(disc_comp_date, val_comp_date)
-retest_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/retest_completion_dates.csv', header=FALSE)
+retest_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/retest_completion_dates.csv', header=FALSE)
 comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
@@
 ```{r}
-test_demog <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/t1_data/demographic_health.csv')
-
-retest_demog <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/demographic_health.csv')
+test_demog <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/t1_data/demographic_health.csv')
+
+retest_demog <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/demographic_health.csv')
 
@@
 #Get variables of interest from Ian's release
-tmp1 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_10-08-2017/meaningful_variables.csv')
-tmp2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_10-08-2017/meaningful_variables_noDDM.csv')
-tmp3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_10-08-2017/meaningful_variables_EZ.csv')
+tmp1 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_11-22-2017/meaningful_variables.csv')
+tmp2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_11-22-2017/meaningful_variables_noDDM.csv')
+tmp3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_11-22-2017/meaningful_variables_EZ.csv')
 retest_report_vars = c(names(tmp1), names(tmp2), names(tmp3))
@@
   rel_df[numeric_cols[i], 'pearson'] <- get_pearson(numeric_cols[i])
-  rel_df[numeric_cols[i], 'eta_sq'] <- get_eta(numeric_cols[i])
+  rel_df[numeric_cols[i], 'partial_eta_sq'] <- get_partial_eta(numeric_cols[i])
   rel_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])

### 2017-11-30 code/SRO_Report_Helper_Functions.R

@@ -108,7 +108,7 @@ get_var_breakdown <- function(dv_var, t1_df = test_data, t2_df = retest_data, me
   return(var_breakdown)
 }
 
-get_eta <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
+get_partial_eta <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
   if(sample=='full'){
     df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
   }
@@ -119,8 +119,8 @@ get_eta <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 
   mod = summary(aov(score~Error(sub_id)+time, df))
   ss_time = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq1',]
   ss_error = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq2',]
-  eta = ss_time/(ss_time+ss_error)
-  return(eta)
+  partial_eta = ss_time/(ss_time+ss_error)
+  return(partial_eta)
 }
 
 get_sem <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){

### 2018-01-15 code/SRO_Report.Rmd
updated pipeline notes and paths

@@
 ```{r}
-hddm_refits <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/hddm_refits_exhaustive.csv')
+hddm_refits <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/hddm_refits_exhaustive.csv')
 

### 2018-01-17 code/SRO_Report.Rmd
updates

@@
 #Get variables of interest from Ian's release
-tmp1 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_11-22-2017/meaningful_variables.csv')
-tmp2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_11-22-2017/meaningful_variables_noDDM.csv')
-tmp3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_11-22-2017/meaningful_variables_EZ.csv')
+tmp1 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-15-2018/meaningful_variables.csv')
+tmp2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-15-2018/meaningful_variables_noDDM.csv')
+tmp3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-15-2018/meaningful_variables_EZ.csv')
 retest_report_vars = c(names(tmp1), names(tmp2), names(tmp3))
@@
 ```{r}
-test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/t1_data/variables_exhaustive.csv')
+test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/t1_data/variables_exhaustive.csv')
 
@@
 ```{r}
-test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/t1_data/variables_exhaustive.csv')
+test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/t1_data/variables_exhaustive.csv')
 
@@
 ```{r}
-retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/variables_exhaustive.csv')
+retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/variables_exhaustive.csv')
 
@@
 ```{r}
-hddm_refits <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/hddm_refits_exhaustive.csv')
+hddm_refits <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/hddm_refits_exhaustive.csv')
 
@@
   arrange(-icc)
+```
+
+```{r}
+summary(demog_rel_df)
 ```
@@
 
-ggsave('Metric_Scatterplots.jpg', plot = grid.arrange(p1, p2, p3, nrow=1), device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
+ggsave('Metric_Scatterplots.jpg', plot = grid.arrange(p1, p2, p3, nrow=1), device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE, dpi = 100)
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-boot_df <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/bootstrap_merged.csv')
+boot_df <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/bootstrap_merged.csv')
 
@@
 
-ggsave('Bootstrap_Poster_Plot_t.jpg', plot = p6_t, device = "jpeg", path = "../output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE)
+ggsave('Bootstrap_Poster_Plot_t.jpg', plot = p6_t, device = "jpeg", path = "../output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE, dpi = 100)
 ```
@@
 
-ggsave('Variance_Breakdown_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 24, height = 20, units = "in")
+ggsave('Variance_Breakdown_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 24, height = 20, units = "in", dpi = 100)
 rm(tmp, labels)
@@
 ```{r}
-aggregate(value ~task+key, FUN=mean, data=tmp)
-
 tmp%>%
@@
 
-Summarizing for clearer presentation. This grap is currently using the bootstrapped reliabilities and is therefore messier than if just using the point estimates.
+Summarizing for clearer presentation. This graph is currently using the bootstrapped reliabilities and is therefore messier than if just using the point estimates.
 
@@
 
-ggsave('Variance_Breakdown_Plot_Summary.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in")
+ggsave('Variance_Breakdown_Plot_Summary.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in", dpi = 100)
 ```
@@
             max_spearman = max(spearman),
-            num_measures = n(),
+            num_measures = n()/1000,
             num_trials = unique(num_all_trials))%>%
@@
                         'max_spearman', 'max_icc'), digits=3)
+```
+
+```{r}
+tmp = tmp%>%
+  mutate(task_name = gsub("_", " ", task_name),
+         task_name = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", task_name, perl=TRUE))
+
+names(tmp) = gsub("_", " ", names(tmp))
+names(tmp) = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", names(tmp), perl=TRUE)
+
+sjt.df(tmp %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/task_rel_table.doc")
 ```

### 2018-01-17 code/SRO_Report_Helper_Functions.R

@@ -13,6 +13,7 @@ library(plotly)
 library(DT)
 
 render_this <- function(){rmarkdown::render('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, toc_depth = 2, code_folding = 'hide'))}
+
 options(scipen = 1, digits = 4)
 
 sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}

### 2018-01-18 code/SRO_Report.Rmd
updating report for draft

@@
 ggsave('Variance_Breakdown_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 24, height = 20, units = "in", dpi = 100)
-rm(tmp, labels)
+rm(tmp, labels, p1, p2 , p3)
 ```
@@
 
-That said this kind of analysis seems too in the weeds for a paper that is trying to give a global sense of the differences between self-regulation measures in their suitablity for individual difference analyses based on their stability across time.
+These kinds of analyses are too task-specific and in-depth for a paper that is trying to give a global sense of the differences between self-regulation measures in their suitablity for individual difference analyses based on their stability across time.
 Such analyses would provide a detailed examination of how to extract the most reliable/best individual difference measure from tasks with a set of mediocre variables to begin with.
-So I am choosing to ignore this for now but this can be revisited.
-
-NOTE: DO THIS ON AN EXAMPLE TASK AND LEAVE TO THE READER TO DO
+Though we do not provide such a comprehensive analysis of this sort in this paper we provide a single example of this approach and hope the open access we provide to the data spurs further work.
+
+For this example we look at the retest reliability of the ...
+measures from the ...
+task with ...
+trials.
+Here is a graph of how the point estimates of the retest reliability changes for each of the dependent measures using different numbers of trials to estimate them.
+
+target task: one without hddm variables, has dv's that are easily codable in r, a lot of trials, possibly multiple dependent measures
+method: import raw response data for chosen task for both t1 and t2, calculate dv's for for both t's for different number of trials, calculate retest reliability point estimates for each of these dv's with different trial numbers
+candidates: angling risk task, columbia card task, dietary decision, hierarchical rule, keep track, probabilistic selection, psychological refractory period, two stage decision
+
+```{r}
+#read t1 data
+t1_hr = read.csv(gzfile('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-15-2018/Individual_Measures/hierarchical_rule.csv.gz', 'rt'))
+
+t2_hr = read.csv(gzfile('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017//Individual_Measures/hierarchical_rule.csv.gz', 'rt'))
+
+#get only retest subjects
+t1_hr = t1_hr[as.character(t1_hr$worker_id) %in% as.character(test_data$sub_id),]
+t2_hr = t2_hr[as.character(t2_hr$worker_id) %in% as.character(retest_data$sub_id),]
+
+#remove missed trials (rt == -1)
+t1_hr = t1_hr %>% filter(rt != -1)
+t2_hr = t2_hr %>% filter(rt != -1)
+
+#dv's
+#accuracy: mean correct
+#average rt: median of correct trials only
+#score: sum correct
+
+calc_break_dvs = function(x, breaks=seq(0, 360, 10)[-1]){
+  out = data.frame()
+  for(i in 1:length(breaks)){
+    tmp = x[1:breaks[i],]
+    dvs = tmp %>%
+      summarise(acc = mean(correct),
+                avg_rt = median(rt[correct == 1]),
+                score = sum(correct))
+    out = rbind(out, dvs)
+  }
+  return(out)
+}
+
+tmp = t1_hr%>% filter(worker_id == 's005')
+
+calc_break_dvs(tmp)
+
+t1_hr %>%
+  group_by(worker_id) %>%
+  summarise(acc = mean(correct),
+                avg_rt = median(rt[correct == 1]),
+                score = sum(correct))
+```
 

### 2018-01-18 code/SRO_Report.Rmd
updating report for draft

@@
 calc_break_dvs = function(x, breaks=seq(0, 360, 10)[-1]){
-  out = data.frame()
-  for(i in 1:length(breaks)){
-    tmp = x[1:breaks[i],]
-    dvs = tmp %>%
+
+  calc_dvs = function(x){
+    out = x %>%
       summarise(acc = mean(correct),
@@
                 score = sum(correct))
+    return(out)
+  }
+
+  out = data.frame()
+
+  for(i in 1:length(breaks)){
+    tmp = x[1:breaks[i],]
+    dvs = calc_dvs(tmp)
     out = rbind(out, dvs)
   }
+
+  # due to timeout trials exclusion not all subjects might have 360 rows
+  # this would lead to na's for later trial breaks
+  # first remove these
+  out = out %>% drop_na()
+
+  # then calculate the dv's for the remaining trials
+  if(nrow(x)!=360 & nrow(x)%%10 != 0){
+    dvs = calc_dvs(x)
+    out = rbind(out, dvs)
+  }
+
+  #to keep track for later merge
+  out$breaks = row.names(out)
+
   return(out)
@@
 
-tmp = t1_hr%>% filter(worker_id == 's005')
-
-calc_break_dvs(tmp)
-
-t1_hr %>%
+#get dv's for t1 and t2
+t1_dvs = t1_hr %>%
   group_by(worker_id) %>%
-  summarise(acc = mean(correct),
-                avg_rt = median(rt[correct == 1]),
-                score = sum(correct))
+  do(calc_break_dvs(.))
+
+t2_dvs = t2_hr %>%
+  group_by(worker_id) %>%
+  do(calc_break_dvs(.))
+
+# merge to get same number of rows for each subject at both time points
+hr_merge = merge(t1_dvs, t2_dvs, by = c("worker_id", "breaks"))
+
+rm(t1_dvs, t2_dvs)
+
+hr_merge = hr_merge %>%
+  gather(key, value, -worker_id, -breaks) %>%
+  separate(key, c("dv", "time"), sep="\\.") %>%
+  mutate(time = ifelse(time == "x", 1, 2)) %>%
+  arrange(worker_id, time, as.numeric(breaks))
+
+hr_merge %>% 
+  spread(dv, value) %>%
+  group_by(breaks) 
+# calculate point estimates for reliability
+
+tmp = hr_merge %>% 
+  spread(dv, value) %>%
+  filter(breaks == 30) %>%
+  select(time, acc)
+
+ICC(tmp)$results['Average_fixed_raters', 'ICC']
+
+hr_merge
 ```

### 2018-01-18 code/SRO_Report.Rmd
updating report for draft

@@
   group_by(worker_id) %>%
-  do(calc_break_dvs(.))
+  do(calc_break_dvs(.)) %>%
+  rename(sub_id = worker_id)
 
@@
 
-rm(t1_dvs, t2_dvs)
+# rm(t1_dvs, t2_dvs)
 
@@
   separate(key, c("dv", "time"), sep="\\.") %>%
-  mutate(time = ifelse(time == "x", 1, 2)) %>%
-  arrange(worker_id, time, as.numeric(breaks))
-
-hr_merge %>% 
-  spread(dv, value) %>%
-  group_by(breaks) 
-# calculate point estimates for reliability
-
-tmp = hr_merge %>% 
-  spread(dv, value) %>%
-  filter(breaks == 30) %>%
-  select(time, acc)
-
-ICC(tmp)$results['Average_fixed_raters', 'ICC']
+  mutate(time = ifelse(time == "x", 1, 2))
 
 hr_merge
+
+t1_dvs = hr_merge %>%
+  filter(time == 1) %>%
+  select(-time) %>%
+  spread(dv, value)
+
+t2_dvs = hr_merge %>%
+  filter(time == 2) %>%
+  select(-time) %>%
+  spread(dv, value)
+
+# calculate point estimates for reliability of each of the variables for each break
+# get_icc for each break of tmp_t1_dvs and tmp_t2_dvs
+trial_num_rel_df = data.frame()
+for(i in t1_dvs$breaks){
+  tmp_t1_dvs = t1_dvs %>% filter(i)
+  tmp_t2_dvs = t2_dvs %>% filter(i)
+  trial_num_rel_df$breaks[i] = i
+  trial_num_rel_df$acc_icc[i] = get_icc("acc", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$avg_rt_icc[i] = get_icc("avg_rt", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$score_icc[i] = get_icc("score", tmp_t1_dvs, tmp_t2_dvs)
+}
 ```

### 2018-01-19 code/SRO_Report.Rmd
updating report for draft

@@
 # merge to get same number of rows for each subject at both time points
-hr_merge = merge(t1_dvs, t2_dvs, by = c("worker_id", "breaks"))
+hr_merge = merge(t1_dvs, t2_dvs, by = c("sub_id", "breaks"))
 
@@
 hr_merge = hr_merge %>%
-  gather(key, value, -worker_id, -breaks) %>%
+  gather(key, value, -sub_id, -breaks) %>%
   separate(key, c("dv", "time"), sep="\\.") %>%
   mutate(time = ifelse(time == "x", 1, 2))
-
-hr_merge
 
@@
 # get_icc for each break of tmp_t1_dvs and tmp_t2_dvs
-trial_num_rel_df = data.frame()
-for(i in t1_dvs$breaks){
-  tmp_t1_dvs = t1_dvs %>% filter(i)
-  tmp_t2_dvs = t2_dvs %>% filter(i)
-  trial_num_rel_df$breaks[i] = i
+trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))), acc_icc=rep(NA, length(unique(t1_dvs$breaks))), avg_rt_icc=rep(NA, length(unique(t1_dvs$breaks))), score_icc=rep(NA, length(unique(t1_dvs$breaks))))
+for(i in 1:length(unique(t1_dvs$breaks))){
+  cur_break = unique(t1_dvs$breaks)[i]
+  tmp_t1_dvs = t1_dvs %>% filter(breaks == cur_break)
+  tmp_t2_dvs = t2_dvs %>% filter(breaks == cur_break)
+  trial_num_rel_df$breaks[i] = cur_break
   trial_num_rel_df$acc_icc[i] = get_icc("acc", tmp_t1_dvs, tmp_t2_dvs)
@@
 }
+rm(i, cur_break, tmp_t1_dvs, tmp_t2_dvs)
+
+trial_num_rel_df$breaks = as.numeric(trial_num_rel_df$breaks)
+
+trial_num_rel_df %>%
+  gather(key, value, -breaks) %>%
+  ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_icc", "score_icc"), labels = c("Accuracy", "Average RT", "Score"))))+
+  geom_point()+
+  geom_line()+
+  theme_bw()+
+  xlab("Number of trials")+
+  ylab("ICC")+
+  theme(legend.title = element_blank())
 ```

### 2018-01-19 code/SRO_Report.Rmd
updating report for draft

@@
 
-For this example we look at the retest reliability of the ...
-measures from the ...
-task with ...
-trials.
+For this example we look at the retest reliability of the three dependent measures (average accuracy, median response time, total score) from the hierarchical rule task with 360 trials.
 Here is a graph of how the point estimates of the retest reliability changes for each of the dependent measures using different numbers of trials to estimate them.
+While the reliability estimate for each of the variables respectively are ..., ...
+and ...
+using all of the trials, these values are independent of number of trials used in the task for only certain variables.
+Based on this analysis researchers might decide to use a version of the task with fewer trials or only measures with consistently high reliability estimates.
 
@@
   theme(legend.title = element_blank())
+
+ggsave('Intrameasure_Trialnum_Dependendence.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in", dpi = 100)
 ```

### 2018-01-19 code/SRO_Report.Rmd
updating report for draft

@@
 tmp %>%
+  drop_na() %>% #try removing this in final release
   group_by(overall_difference, raw_fit, rt_acc) %>%

### 2018-01-20 code/SRO_Report.Rmd
going over new data release

@@
 source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Report_Helper_Functions.R')
+
+test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-17-2018/'
+
+retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_01-17-2018/'
 ```
@@
 ```{r warning=FALSE, message=FALSE}
-workers = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/User_717570_workers.csv')
+workers = read.csv(paste0(retest_data_path,'Local/User_717570_workers.csv'))
 workers = workers %>% 
@@
 
-worker_counts <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/retest_worker_counts.json')
+worker_counts <- fromJSON(paste0(retest_data_path,'/Local/retest_worker_counts.json'))
 
@@
 ```{r warning=FALSE, message=FALSE}
-disc_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/discovery_completion_dates.csv', header=FALSE)
-val_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/validation_completion_dates.csv', header=FALSE)
+disc_comp_date = read.csv(paste0(retest_data_path,'Local/discovery_completion_dates.csv'), header=FALSE)
+val_comp_date = read.csv(paste0(retest_data_path,'Local/validation_completion_dates.csv'), header=FALSE)
 test_comp_date = rbind(disc_comp_date, val_comp_date)
 rm(disc_comp_date, val_comp_date)
-retest_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/retest_completion_dates.csv', header=FALSE)
+retest_comp_date = read.csv(paste0(retest_data_path,'Local/retest_completion_dates.csv'), header=FALSE)
 comp_dates = merge(retest_comp_date, test_comp_date, by="V1")

### 2018-01-20 code/SRO_Report.Rmd
checking new release

@@
 ```{r}
-test_demog <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/t1_data/demographic_health.csv')
-
-retest_demog <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/demographic_health.csv')
+test_demog <- read.csv(paste0(retest_data_path, '/t1_data/demographic_health.csv'))
+
+retest_demog <- read.csv(paste0(retest_data_path, 'demographic_health.csv'))
 
@@
 #Get variables of interest from Ian's release
-tmp1 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-15-2018/meaningful_variables.csv')
-tmp2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-15-2018/meaningful_variables_noDDM.csv')
-tmp3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-15-2018/meaningful_variables_EZ.csv')
+tmp1 <- read.csv(paste0(test_data_path,'meaningful_variables.csv'))
+tmp2 <- read.csv(paste0(test_data_path,'meaningful_variables_noDDM.csv'))
+tmp3 <- read.csv(paste0(test_data_path,'meaningful_variables_EZ.csv'))
 retest_report_vars = c(names(tmp1), names(tmp2), names(tmp3))
@@
 ```{r}
-test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/t1_data/variables_exhaustive.csv')
+test_data <- read.csv(paste0(retest_data_path,'t1_data/variables_exhaustive.csv'))
 
@@
 ```{r}
-test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/t1_data/variables_exhaustive.csv')
+test_data2 <- read.csv(paste0(retest_data_path, 't1_data/variables_exhaustive.csv'))
 
@@
 ```{r}
-retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/variables_exhaustive.csv')
+retest_data <- read.csv(paste0(retest_data_path,'variables_exhaustive.csv'))
 
@@
 ```{r}
-hddm_refits <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/hddm_refits_exhaustive.csv')
+hddm_refits <- read.csv(paste'/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/hddm_refits_exhaustive.csv')
 

### 2018-01-24 code/SRO_Report.Rmd
updated pipeline notes and analyses for new notebook

@@
 
-test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-17-2018/'
-
-retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_01-17-2018/'
+test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-22-2018/'
+
+retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_01-23-2018/'
 ```
@@
 ```{r}
-hddm_refits <- read.csv(paste'/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/hddm_refits_exhaustive.csv')
+hddm_refits <- read.csv(paste0('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/hddm_refits_exhaustive.csv')
 

### 2018-01-25 code/SRO_Report.Rmd
updating report with new releases

@@
 ```{r}
-hddm_refits <- read.csv(paste0('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/hddm_refits_exhaustive.csv')
+hddm_refits <- read.csv(paste0(retest_data_path,'t1_data/hddm_refits_exhaustive.csv'))
 
@@
 
+#drop hddm columns from test_data
 test_data = cbind(test_data$sub_id, test_data[,names(test_data) %in% names(hddm_refits) == FALSE])
 
+#fix naming before merging
 names(test_data)[which(names(test_data) == 'test_data$sub_id')] <-'sub_id'
 
+#merge hddm refits to test data
 test_data = merge(test_data, hddm_refits, by="sub_id")
@@
 ```{r message=FALSE, warning=FALSE}
-boot_df <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/bootstrap_merged.csv')
+boot_df <- read.csv(gzfile(paste0(retest_data_path,'bootstrap_merged.csv.gz')))
 
@@
 measure_labels = measure_labels %>% select(-measure_description,-measure_type,-measure_type_Ian,-measure_type_Russ,-notes,-Patrick_hates)
+
+# retest_report_vars[(retest_report_vars %in% measure_labels$dv == FALSE)]
+# measure_labels$dv[(measure_labels$dv %in% retest_report_vars == FALSE)]
 ```

### 2018-01-25 code/SRO_Report.Rmd
going through rest of report with new releases

@@
 #read t1 data
-t1_hr = read.csv(gzfile('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-15-2018/Individual_Measures/hierarchical_rule.csv.gz', 'rt'))
-
-t2_hr = read.csv(gzfile('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017//Individual_Measures/hierarchical_rule.csv.gz', 'rt'))
+t1_hr = read.csv(gzfile(paste0(test_data_path,'Individual_Measures/hierarchical_rule.csv.gz'), 'rt'))
+
+t2_hr = read.csv(gzfile(paste0(retest_data_path,'Individual_Measures/hierarchical_rule.csv.gz'), 'rt'))
 

### 2018-01-25 code/SRO_Report_Helper_Functions.R

@@ -11,6 +11,7 @@ library(psych)
 library(stringr)
 library(plotly)
 library(DT)
+library(sjPlot)
 
 render_this <- function(){rmarkdown::render('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, toc_depth = 2, code_folding = 'hide'))}
 

### 2018-02-16 code/SRO_Report.Rmd
updated pipeline notes

@@
 
-test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-22-2018/'
-
-retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_01-23-2018/'
+test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_02-03-2018/'
+
+retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-03-2018/'
 ```

### 2018-02-16 code/SRO_Report.Rmd
updating report with new dataset

@@
 # Introduction
+
+The psychological construct of self-regulation, or related concepts of impulsivity, self-control, inhibition and others correlate with problematic real-world behaviors such as disordered eating (Mobbs et al., 2010, Verbeken et al., 2009, Nederkoorn et al.
+2006a, Nederkoorn et al., 2006b), gambling (Lawrence et al., 2009, Fuentes et al., 2006, Alessi and Petry, 2003), drug addiction (Coffey et al., 2003, de Wit, Crean and John, 2000, Sher, Bartholow and Wood, 2000, Kirby, Petry and Bickel, 1999) or bad financial decisions (Meier and Sprenger, 2015, Meier and Sprenger, 2013, Meier and Sprenger 2012).
+In these lines of work measures of self-regulation are used as behavioral assays for individual difference analyses.
+An underlying assumption of treating behavioral measures as reflective of person-specific characteristics is that the measures of self-regulation are stable across time.
+In other words, that they have high test-retest reliability (or high between- and low within-subject variability).
+This assumption is not extensively and equally tested in the literature for all measures of self-regulation.
+Self-regulation measures can be grouped in two broad categories: Surveys and cognitive tasks.
+While the former typically goes through some form of psychometric testing often filtering out items with low test-retest reliability this is less frequently true for the latter.
+Though some empirical results on test-retest reliabilities of certain cognitive task measures are reported in pockets of the literature an exhaustive summary or systematic elimination of tasks or measures based on stability across time does not seem to exist.
+Test-retest reliability is, however, crucial for individual difference analyses (Hedge, Powell and Sumner, 2017).
+To answer the question of reliability of self-regulation measures comprehensively we created a large battery consisting of both cognitive task and survey measures.
+In this paper we make two contributions: First we provide a review of these measures along with their reported reliabilities when available.
+Then we report results of a large study we conducted where we collected retest reliability data using all of these measures.
+This effort not only fills in a notable gap in the literature in clarifying which measures of self-regulation are stable across time but also provides guidance on factors to pay attention to when constructing new tasks for individual difference measures.
 
@@
 
-One the major contributions of this project is a comprehensive literature review of the retest reliabilities of the surveys and tasks that were used.
+One of the major contributions of this project is a comprehensive literature review of the retest reliabilities of the surveys and tasks that were used.
 We reviewed the literature on a measure (as opposed to task level) paying attention to differences in sample size, the delay between the two measurements as well as the statistic that was used to assess reliabilities (e.g.
@@
 - Survey measures have been reported to higher reliability compared to task measures  
-- Survey measures have less variability in the reported reliabiltiy estimates compared to task measures'
+- Survey measures have less variability in the reported reliabiltiy estimates compared to task measures
 
@@
 - ICC(3,k): As Dave clarified this ranges from 1 to -1/(number of repeated measures -1) so in our case this range would be [-1, 1]; larger values would mean that the two scores of a subject for a given measure are more similar to each other than they are to scores of other people
-- " ICC is reflective of the ability of a test to differentiate between different individuals"
+- "ICC is reflective of the ability of a test to differentiate between different individuals"
 - partial $\eta^2$ for time ($SS_{time}/SS_{within}$): effect size of time   
@@
                      pearson = rep(NA, length(numeric_cols)),
-                     eta_sq = rep(NA, length(numeric_cols)),
+                     partial_eta_sq = rep(NA, length(numeric_cols)),
                      sem = rep(NA, length(numeric_cols)),
@@
 rel_df = rel_df %>%
-  select(dv, task, spearman, icc, pearson, eta_sq, sem, var_subs, var_ind, var_resid)
+  select(dv, task, spearman, icc, pearson, partial_eta_sq, sem, var_subs, var_ind, var_resid)
 # row.names(rel_df) = NULL
 ```
+
+We calculated `r as.numeric(table(rel_df$task)[1])` measures for surveys and `r as.numeric(table(rel_df$task)[2])` measures for cognitive tasks.
 
@@
 ggsave('Metric_Scatterplots.jpg', plot = grid.arrange(p1, p2, p3, nrow=1), device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE, dpi = 100)
+```
+
+As the scatter plots depict the correlations between different types reliability metrics were very high.
+
+```{r}
+cor(rel_df[,c('spearman', 'icc', 'pearson')])
 ```
@@
 
+# Check if you hae all variables bootstrapped
 # retest_report_vars[which(retest_report_vars %in% boot_df$dv==FALSE)]
@@
 measure_labels <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/measure_labels.csv')
-measure_labels = measure_labels %>% select(-measure_description,-measure_type,-measure_type_Ian,-measure_type_Russ,-notes,-Patrick_hates)
-
+measure_labels = measure_labels %>% select(-measure_description)
+# Check if there are any missing variables
 # retest_report_vars[(retest_report_vars %in% measure_labels$dv == FALSE)]

### 2018-02-16 code/SRO_Report.Rmd
updating report with new dataset

@@
 (2017), lies in the difference in sources of variance between these measures.
-This is because reliability is estimated as a ratio of these sources variance to each other.
 Specifically, the ICC is calculated as the ratio of variance between subjects variance to all sources of variance.
@@
 
+Running separate models for different sources of variance because interactive model with variance type*task seemed too complicated.
+
+First we find that task measures have a smaller percentage of their overall variance explained by variability between subjects compared to survey measures.
+
 ```{r}
@@
          var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
-  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
-  gather(key, value, -dv, -task)
-
-summary(lmer(value~key*task+(1|dv),tmp))
-```
-
-```{r}
-tmp%>%
+  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct)
+
+summary(lmerTest::lmer(var_subs_pct~task+(1|dv),tmp%>%select(-var_ind_pct,-var_resid_pct)))
+```
+
+We also find that a significantly larger percentage of their variance is explained by between session variability.
+Larger between session variability suggests systematic differences between the two sessions.
+Such systematic effects can be due to e.g.
+learning effects as explored later.
+
+```{r}
+summary(lmerTest::lmer(var_ind_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_resid_pct)))
+```
+
+```{r}
+summary(lmerTest::lmer(var_resid_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_ind_pct)))
+```
+
+```{r}
+tmp_save = tmp%>%
+  gather(key, value, -dv, -task) %>%
   group_by(task, key) %>%
   summarise(median = median(value),
-            sd = sd(value))
+            sd = sd(value)) %>%
+  mutate(key = ifelse(key == 'var_ind_pct', 'Between session variance', ifelse(key == 'var_subs_pct', 'Between subjects variance', ifelse(key == 'var_resid_pct', 'Residual variance',NA)))) %>%
+  rename(Median = median, SD = sd) %>%
+  arrange(task, key)
+
+tmp_save
+```
+
+```{r}
+sjt.df(tmp_save %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/var_breakdown_summary.doc")
 ```

### 2018-02-17 code/SRO_Report.Rmd
updating report with new dataset

@@
 tmp %>%
+  gather(key, value, -dv, -task) %>%
   group_by(task, key) %>%
@@
 # summary(lm(icc ~ num_all_trials, data = tmp))
-summary(lmer(icc ~ num_all_trials + (1|dv), data = tmp))
+summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
 ```
@@
 
-```{r}
+```{r warning=FALSE, message=FALSE}
 #read t1 data
@@
       summarise(acc = mean(correct),
-                avg_rt = median(rt[correct == 1]),
-                score = sum(correct))
+                avg_rt = median(rt[correct == 1]))
+                # score = sum(correct))
     return(out)
@@
 # get_icc for each break of tmp_t1_dvs and tmp_t2_dvs
-trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))), acc_icc=rep(NA, length(unique(t1_dvs$breaks))), avg_rt_icc=rep(NA, length(unique(t1_dvs$breaks))), score_icc=rep(NA, length(unique(t1_dvs$breaks))))
+# trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))), acc_icc=rep(NA, length(unique(t1_dvs$breaks))), avg_rt_icc=rep(NA, length(unique(t1_dvs$breaks))), score_icc=rep(NA, length(unique(t1_dvs$breaks))))
+trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))), acc_icc=rep(NA, length(unique(t1_dvs$breaks))), avg_rt_icc=rep(NA, length(unique(t1_dvs$breaks))))
 for(i in 1:length(unique(t1_dvs$breaks))){
@@
   trial_num_rel_df$avg_rt_icc[i] = get_icc("avg_rt", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$score_icc[i] = get_icc("score", tmp_t1_dvs, tmp_t2_dvs)
+  # trial_num_rel_df$score_icc[i] = get_icc("score", tmp_t1_dvs, tmp_t2_dvs)
 }
@@
   gather(key, value, -breaks) %>%
-  ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_icc", "score_icc"), labels = c("Accuracy", "Average RT", "Score"))))+
+  # ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_icc", "score_icc"), labels = c("Accuracy", "Average RT", "Score"))))+
+  ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_icc"), labels = c("Accuracy", "Average RT"))))+
   geom_point()+
@@
 ggsave('Intrameasure_Trialnum_Dependendence.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in", dpi = 100)
+```
+
+```{r}
+rel_df[c(rel_df$dv %in% grep('hierarchical_rule', rel_df$dv, value = TRUE)),]
 ```
@@
 ```{r}
-summary(lmerTest::lmer(icc ~ overall_difference*raw_fit + (1|dv) ,tmp))
+tmp_save = tmp %>%
+  drop_na() %>% #try removing this in final release
+  group_by(overall_difference, raw_fit, rt_acc) %>%
+  summarise(icc_median = quantile(icc, probs = 0.5),
+            icc_2.5 = quantile(icc, probs = 0.025),
+            icc_97.5 = quantile(icc, probs = 0.975),
+            num_vars = n()/1000) %>%
+  ungroup() %>%
+  mutate(overall_difference = as.character(overall_difference),
+         raw_fit = as.character(raw_fit),
+         rt_acc = as.character(rt_acc)) %>%
+  arrange(-icc_median)
+
+sjt.df(tmp_save %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/ddm_rel_table.doc")
+```
+
+Comparing overall vs difference: overall has higher reliability than difference.
+
+```{r}
+summary(lmerTest::lmer(icc ~ overall_difference + (1|dv) ,tmp))
+```
+
+Comparing raw vs ddm in overall estimates: EZ is significantly better than HDDM and comparable to raw estimates.
+
+```{r}
+summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(overall_difference == "overall")))
+```
+
+Comparing raw vs ddm in difference scores: EZ is significantly worse than HDDM and comparable to raw estimates.
+
+```{r}
+summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(overall_difference == "difference")))
 ```
@@
 
-Do these differ statistically?
-
-The plot does not suggest so but this model is giving a warning and very high t values. How else should I be checking for differences between these distributions?
-
-```{r}
-summary(lmer(value~key*overall_difference*raw_fit+(1|dv), tmp))
-```
+Not checking if these differ significantly because this seems to in the weeds for this paper.
 

### 2018-02-17 code/SRO_Report.Rmd
updating report with new dataset

@@
 
-```{r}
-hddm_refits %>%
-  filter(adaptive_n_back.hddm_drift<0)
-  # ggplot(aes(adaptive_n_back.EZ_drift))+
-  # geom_histogram()
-
-hddm_fullfits %>%
-  filter(dv == "adaptive_n_back.hddm_drift" & value <0)
-```
-
 #### Parameter reliability depending on sample size
@@
 
-TBD. Still need to figure out how to turn off the H.
-
-One way to solve this would be to feed data in manually.
+Plot flat estimates against
+
+```{r}
+retest_hddm_flat <- read.csv(paste0(retest_data_path, 'retest_hddm_flat.csv'))
+retest_hddm_flat
+```
 

### 2018-02-18 code/SRO_Report.Rmd
updating report w new data release

@@
 
+```{r}
+process_boot_df = function(df){
+  df = df %>%
+  drop_na() %>%
+  mutate(dv = as.character(dv),
+         icc = as.numeric(as.character(icc)),
+         spearman = as.numeric(as.character(spearman)),
+         eta_sq = as.numeric(as.character(eta_sq)),
+         sem = as.numeric(as.character(sem)),
+         partial_eta_sq = as.numeric(as.character(partial_eta_sq)),
+         omega_sq = as.numeric(as.character(omega_sq)),
+         var_subs = as.numeric(as.character(var_subs)),
+         var_ind = as.numeric(as.character(var_ind)),
+         var_resid = as.numeric(as.character(var_resid)),
+         F_time = as.numeric(as.character(F_time)),
+         p_time = as.numeric(as.character(p_time)),
+         df_time = as.numeric(as.character(df_time)),
+         df_resid = as.numeric(as.character(df_resid)))
+  return(df)} 
+```
+
 ```{r message=FALSE, warning=FALSE}
@@
 
-boot_df = boot_df %>%
-  drop_na() %>%
-  mutate(icc = as.numeric(as.character(icc)),
-         spearman = as.numeric(as.character(spearman)),
-         eta_sq = as.numeric(as.character(eta_sq)),
-         sem = as.numeric(as.character(sem)))
+boot_df = process_boot_df(boot_df)
 
@@
 
-# Check if you hae all variables bootstrapped
+# Check if you have all variables bootstrapped
 # retest_report_vars[which(retest_report_vars %in% boot_df$dv==FALSE)]
+
+# Boot df contains hddm parameters fit on the full sample in the t1 data
+# refits_bootstrap_merged.csv.gz contains bootstrapped reliabilities
+
+refit_boot_df = read.csv(gzfile(paste0(retest_data_path,'refits_bootstrap_merged.csv.gz')))
+
+refit_boot_df = process_boot_df(refit_boot_df)
+
+fullfit_boot_df = boot_df[as.character(boot_df$dv) %in% unique(as.character(refit_boot_df$dv)),]
+
+boot_df = boot_df[!as.character(boot_df$dv) %in% unique(as.character(refit_boot_df$dv)),]
+
+boot_df = rbind(boot_df, refit_boot_df)
+
+rm(refit_boot_df)
 
@@
 
-Plot flat estimates against
+Plot flat estimates against hierarhical estimates.
+
+Check the distributions of the flat and hierarchical estimates, transform if not normal and t-test to check if they are different than each other (alternatively get difference scores and check if they are different than 0/plot the distribution of the difference scores)
 

### 2018-02-18 code/SRO_Report.Rmd
updating report w new data releases

@@
 Each point in these graphs is a subject's parameter estimates.
-There is almost no change for any of the EZ parameters (though shouldn't this have been 0?).
+There is no change for any of the EZ parameters.
 For the HDDM parameters most of the changes are happening for drift rates but they don't appear to be systematically higher or lower.
-
-I'm not entirely sure what to make of this.
-A systematic change would have meant that the ranking remained the same regardless of the sample size.
-When the change is non-systematic in this way then a given subject that has high higher drift rates than most of the people in the full sample can appear to have lower drift rates than the same people when fit on the retest sample only.
-(note that a t-test is not significant)
-
-Of course these parameter estimates themselves are not very interpretable in their 'goodness' as they don't reflect anything about model fits.
-What is the measure of fits here?
-The variance of the posterior?
 
@@
 
-ggplotly(hddm_refits %>%
+tmp = hddm_refits %>%
   gather(dv, value, -sub_id) %>%
@@
   left_join(measure_labels[,c("dv", "raw_fit", "rt_acc")], by="dv") %>%
-  filter(rt_acc %in% c("drift rate","non-decision", "threshold")) %>%
+  filter(rt_acc %in% c("drift rate","non-decision", "threshold"))
+
+tmp %>%
   ggplot(aes(fullfit, refit, label=dv))+
@@
   ylab("Fit on retest sample")+
-  theme(legend.title = element_blank()),
-  label=dv)
+  theme(legend.title = element_blank())
+```
+
+```{r}
+tmp %>%
+  mutate(refit_diff = fullfit - refit) %>%
+  group_by(raw_fit, rt_acc) %>%
+  summarise(mean = mean(refit_diff, na.rm=T),
+            sd = sd(refit_diff, na.rm=T))
+```
+
+A simple way to compare the two distributions of the parameters using the full or the retest sample would be to run a t-test.
+Since this would have a normality assumption we first check the distributions of the parameters.
+Though the threshold and non-decision times look closer to normal the drift rates have a clear bimodal distribution.
+Since these are the estimates on which we find the greatest changes we should make sure to transform them somehow before running the test.
+
+```{r warning=FALSE, message=FALSE}
+tmp %>%
+  filter(raw_fit == 'hddm') %>%
+  gather(key, value, -sub_id, -dv, -raw_fit, -rt_acc) %>%
+  ggplot(aes(value))+
+  geom_histogram(position='identity', alpha=0.5)+
+  theme_bw()+
+  facet_grid(rt_acc~key, scales='free')
+```
+
+What if you log transform the drift rates? The bimodal distribution becomes one with a long left tail. Still not great to do a t-test on.
+
+```{r warning=FALSE, message=FALSE}
+tmp %>%
+  filter(raw_fit == 'hddm', rt_acc == 'drift rate') %>%
+  gather(key, value, -sub_id, -dv, -raw_fit, -rt_acc) %>%
+  mutate(value = log(value)) %>%
+  ggplot(aes(value))+
+  geom_histogram(alpha = 0.5)+
+  theme_bw()+
+  facet_wrap(~key)
+```
+
+How about the distribution of the difference scores? This looks better to do a t-test on.
+
+```{r message=FALSE}
+tmp %>%
+  filter(raw_fit == 'hddm', rt_acc == 'drift rate') %>%
+  mutate(diff = fullfit - refit) %>%
+  na.omit() %>%
+  ggplot(aes(diff))+
+  geom_histogram(alpha=0.5)+
+  theme_bw()
+```
+
+The distribution of the difference scores between the drift rates using the full and the retest sample differ from 0.
+The difference score distribution has a mean of 0.0016.
+This means that drift rate estimates using the full sample are significantly higher than those using the retest sample alone.
+
+```{r}
+diff = tmp %>%
+  filter(raw_fit == 'hddm', rt_acc == 'drift rate') %>%
+  mutate(diff = fullfit - refit) %>%
+  select(diff) %>%
+  na.omit()
+
+t.test(diff$diff, rep(0, nrow(tmp)))
+```
+
+Still the distribution of the difference scores does show negative values as well.
+The lack of clear systematicity in the changes of the parameter estimates can be difficult to interpret.
+A systematic change would have meant that the ranking remained the same regardless of the sample size.
+When the change is non-systematic in this way then a given subject that has high higher drift rates than most of the people in the full sample can appear to have lower drift rates than the same people when fit on the retest sample only.
+
+Of course these parameter estimates themselves are not very interpretable in their 'goodness' as they don't reflect anything about model fits.
+To determine the model fits for both cases I have written functions to sample from the posterior predictive and calculate $R^2$'s for each subject.
+These currently run too slow, however, and have been deferred for now.
+
+Let's quickly look if the changes are different than 0 for non-decision times and thresholds as well. They are not.
+
+```{r}
+diff = tmp %>%
+  filter(raw_fit == 'hddm', rt_acc == 'non-decision') %>%
+  mutate(diff = fullfit - refit) %>%
+  select(diff) %>%
+  na.omit()
+
+t.test(diff$diff, rep(0, nrow(tmp)))
+```
+
+```{r}
+diff = tmp %>%
+  filter(raw_fit == 'hddm', rt_acc == 'threshold') %>%
+  mutate(diff = fullfit - refit) %>%
+  select(diff) %>%
+  na.omit()
+
+t.test(diff$diff, rep(0, nrow(tmp)))
+```
+
+Does this change reliability?
+
+```{r}
+
 ```

### 2018-02-18 code/SRO_Report.Rmd
updating report w new data

@@
          spearman = as.numeric(as.character(spearman)),
+         pearson = as.numeric(as.character(pearson)),
          eta_sq = as.numeric(as.character(eta_sq)),
@@
 
+```{r}
+rm(diff)
+```
+
 Does this change reliability?
-
-```{r}
-
+18/33 of the bootstrapped reliability distributions for the refit hddm drift rates have different means than the reliability distributions using the fullfit drift rates.
+Only in 7/18 is the refit reliabilities higher.
+
+```{r}
+#Compare bootstrapped reliabilities for refits (replaced in boot_df) to bootstrapped reliabilities of full fits
+refit_ddm_drift_boot_df = boot_df[boot_df$dv %in% grep('hddm_drift',names(hddm_refits), value=T),]
+fullfit_ddm_drift_boot_df = fullfit_boot_df[fullfit_boot_df$dv %in% unique(refit_ddm_drift_boot_df$dv),]
+
+get_t_test_out <- function(df){
+  out = data.frame(p.value=NA, mean_x = NA, mean_y=NA)
+  mod = t.test(df$icc.x, df$icc.y)
+  out$p.value = mod$p.value
+  out$mean_x = as.numeric(mod$estimate[1])
+  out$mean_y = as.numeric(mod$estimate[2])  
+  return(out)
+}
+
+refit_ddm_drift_boot_df %>%
+  select(X, dv, icc) %>%
+  left_join(fullfit_ddm_drift_boot_df[,c('X', 'dv', 'icc')], by = c('X', 'dv')) %>%
+  group_by(dv) %>%
+  do(get_t_test_out(.)) %>%
+  mutate(sig_diff = ifelse(p.value<0.05, 1, 0),
+         refit_better = ifelse(mean_x>mean_y,1,0)) %>%
+  filter(sig_diff == 1, refit_better == 1)
 ```

### 2018-02-19 code/SRO_Report.Rmd
updating report w new data

@@
 
-get_t_test_out <- function(df){
+get_t_test_out <- function(df, x = icc.x, y = icc.y){
   out = data.frame(p.value=NA, mean_x = NA, mean_y=NA)
-  mod = t.test(df$icc.x, df$icc.y)
+  attach(df)
+  mod = t.test(x, y)
+  detach(df)
   out$p.value = mod$p.value
@@
 
+[NOT INCLUDED IN DRAFT FOR NOW]
+
 There doesn't seem to be an effect looking at the graph but the multilevel model seems to show a very significant but tiny effect.
@@
 tmp <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/all_ddm_sample_size_summary.csv')
+
+tmp
 
@@
 
-Plot flat estimates against hierarhical estimates.
-
-Check the distributions of the flat and hierarchical estimates, transform if not normal and t-test to check if they are different than each other (alternatively get difference scores and check if they are different than 0/plot the distribution of the difference scores)
-
-```{r}
+For retest data plotting hierarchical estimates over flat estimates.
+
+```{r message = FALSE, warning=FALSE}
 retest_hddm_flat <- read.csv(paste0(retest_data_path, 'retest_hddm_flat.csv'))
-retest_hddm_flat
+retest_hddm_flat = retest_hddm_flat %>% select(-X) %>% rename(sub_id = subj_id)
+retest_hddm_hier = retest_data[,c(names(retest_data) %in% names(retest_hddm_flat))]
+retest_hddm_flat = retest_hddm_flat[,c(names(retest_hddm_flat) %in% names(retest_hddm_hier))]
+
+retest_hddm_hier = retest_hddm_hier %>% gather(key, value, -sub_id)
+retest_hddm_flat = retest_hddm_flat %>% gather(key, value, -sub_id)
+
+retest_hddm_flat %>%
+  left_join(retest_hddm_hier, by=c('sub_id', 'key')) %>%
+  ggplot(aes(value.x, value.y, color=key))+
+  geom_point()+
+  geom_abline(slope=1, intercept=0)+
+  theme_bw()+
+  theme(legend.position = 'none')+
+  xlab('Parameter estimate without hierarchy')+
+  ylab('Parameter estimate with hierarchy')
+```
+
+For the retest data 6/43 variables have significantly different distributions when they are fit with hierarchy versus without.
+For all of them the hiearchical estimate distributions have significantly higher means.
+
+```{r message=FALSE, warning=FALSE}
+retest_hddm_flat %>%
+  left_join(retest_hddm_hier, by=c('sub_id', 'key')) %>%
+  group_by(key) %>%
+  do(get_t_test_out(.,x=value.x, y=value.y)) %>%
+  mutate(flat_diff = ifelse(p.value<0.05, 1, 0)) %>%
+  filter(flat_diff == 1) %>%
+  mutate(flat_high = ifelse(mean_x>mean_y,1,0))
+```
+
+For t1 data plotting hierarchical estimates over flat estimates.
+
+```{r warning=FALSE, message=FALSE}
+test_hddm_flat <- read.csv(paste0(retest_data_path, 't1_data/t1_hddm_flat.csv'))
+test_hddm_flat = test_hddm_flat %>% select(-X) %>% rename(sub_id = subj_id)
+test_hddm_hier = test_data[,c(names(test_data) %in% names(test_hddm_flat))]
+test_hddm_flat = test_hddm_flat[,c(names(test_hddm_flat) %in% names(test_hddm_hier))]
+
+test_hddm_hier = test_hddm_hier %>% gather(key, value, -sub_id)
+test_hddm_flat = test_hddm_flat %>% gather(key, value, -sub_id)
+
+test_hddm_flat %>%
+  left_join(test_hddm_hier, by=c('sub_id', 'key')) %>%
+  ggplot(aes(value.x, value.y, color=key))+
+  geom_point()+
+  geom_abline(slope=1, intercept=0)+
+  theme_bw()+
+  theme(legend.position = 'none')+
+  xlab('Parameter estimate without hierarchy')+
+  ylab('Parameter estimate with hierarchy')
+```
+
+For the t1 data 3/43 variables have significantly different distributions when they are fit with hierarchy versus without.
+For all of them the hiearchical estimate distributions have significantly higher means.
+
+```{r message=FALSE, warning=FALSE}
+test_hddm_flat %>%
+  left_join(test_hddm_hier, by=c('sub_id', 'key')) %>%
+  group_by(key) %>%
+  do(get_t_test_out(.,x=value.x, y=value.y)) %>%
+  mutate(flat_diff = ifelse(p.value<0.05, 1, 0)) %>%
+  filter(flat_diff == 1) %>%
+  mutate(flat_high = ifelse(mean_x>mean_y,1,0))
+```
+
+How does this affect reliability?
+
+```{r}
+
 ```

### 2018-02-19 code/SRO_Report.Rmd
updating report w new data

@@
 
-```{r}
-
+```{r warning=FALSE, message=FALSE}
+flat_boot_df <- read.csv(gzfile(paste0(retest_data_path, 'flat_bootstrap_merged.csv.gz')))
+
+hier_boot_df = boot_df[c(boot_df$dv %in% unique(flat_boot_df$dv)),]
+
+flat_boot_df %>%
+  select(X, dv, icc) %>%
+  left_join(hier_boot_df[,c('X', 'dv', 'icc')], by = c('X', 'dv')) %>%
+  group_by(dv) %>%
+  do(get_t_test_out(.)) %>%
+  mutate(sig_diff = ifelse(p.value<0.05, 1, 0),
+         flat_better = ifelse(mean_x>mean_y,1,0)) %>%
+  filter(sig_diff == 1)
 ```

### 2018-02-19 code/SRO_Report.Rmd
updating report w new data

@@
 
+```{r}
+boot_df
+```
+
+## Survey reliabilities
+
+```{r warning=FALSE, message=FALSE}
+tmp = measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(task == 'survey') %>%
+  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv') %>%
+  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
+  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
+  select(-extra_1, -extra_2) %>%
+  group_by(task_name) %>%
+  summarise(median_icc = median(icc),
+            median_spearman = median(spearman),
+            min_icc = min(icc),
+            max_icc = max(icc),
+            min_spearman = min(spearman),
+            max_spearman = max(spearman),
+            num_measures = n()/1000)%>%
+  arrange(-median_icc, -median_spearman)
+
+tmp %>%
+  datatable() %>%
+  formatRound(columns=c('median_spearman', 'median_icc',
+                        'min_spearman', 'min_icc',
+                        'max_spearman', 'max_icc'), digits=3)
+```
+
+```{r}
+tmp = tmp%>%
+  mutate(task_name = gsub("_", " ", task_name),
+         task_name = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", task_name, perl=TRUE))
+
+names(tmp) = gsub("_", " ", names(tmp))
+names(tmp) = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", names(tmp), perl=TRUE)
+
+sjt.df(tmp %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/survey_rel_table.doc")
+```
+
 ## Transformation effects

### 2018-02-19 code/SRO_Report.Rmd
updating report w new data

@@
 
-```{r}
-boot_df
+Which variables have significant time effects in more than 5% of the bootstrapped samples?
+
+22/74 survey measures
+135/335 task measures
+
+```{r}
+boot_df %>%
+  select(dv, p_time, task) %>%
+  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
+  group_by(dv)%>%
+  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
+            task = unique(task))%>%
+  filter(pct_sig_time_effect>5) %>%
+  arrange(task,-pct_sig_time_effect)
 ```

### 2018-03-03 code/SRO_Report.Rmd
adding new plots

--- 2018-02-19 code/SRO_Report.Rmd
@@
   filter(task == 'survey') %>%
-ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
-  geom_violin(fill='#F8766D')+
+ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc, group=dv)) + 
+  geom_violin(fill='#F8766D', position = 'identity')+
   theme_bw() + 
@@
 rm(p4_t, p5_t, p6_t)
+```
+
+Example of the overlaying procedure.
+
+```{r}
+p1<- tmp %>%
+  filter(grepl('selection_optimization', dv)) %>%
+ggplot(aes(x = var, y = icc)) + 
+  geom_violin(fill='#F8766D')+
+  theme_bw() + 
+  theme(axis.text.y = element_text(size=30))+
+  xlab("")+
+  ylab("")+
+  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
+  geom_hline(yintercept = 0, color = "red", size = 1)+
+  coord_flip()
+
+p2<- tmp %>%
+  filter(grepl('selection_optimization', dv)) %>%
+ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc, group=dv)) + 
+  geom_violin(fill='#F8766D', position = 'identity')+
+  theme_bw() + 
+  theme(axis.text.y = element_text(size=30))+
+  xlab("")+
+  ylab("")+
+  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
+  geom_hline(yintercept = 0, color = "red", size = 1)+
+  coord_flip()
+
+p3<- tmp %>%
+  filter(grepl('selection_optimization', dv)) %>%
+ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
+  geom_violin(fill='#F8766D', position = 'identity')+
+  theme_bw() + 
+  theme(axis.text.y = element_text(size=30))+
+  xlab("")+
+  ylab("")+
+  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
+  geom_hline(yintercept = 0, color = "red", size = 1)+
+  coord_flip()
+
+p4 <- arrangeGrob(p1,p2, p3,nrow=1)
+
+ggsave('Bootstrap_Example_Plot_t.jpg', plot = p4, device = "jpeg", path = "../output/figures/", width = 41, height = 5, units = "in", limitsize = FALSE, dpi = 100)
+```
+
+```{r echo=FALSE, out.width='100%'}
+knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Bootstrap_Example_Plot_t.jpg')
+```
+
+```{r}
+rm(p1, p2, p3, p4)
 ```
@@
   group_by(task, key) %>%
-  ggplot(aes(factor(task, levels=c("task","survey"), labels=c("Task", "Survey")), value, fill=key, color=task))+
+  ggplot(aes(factor(task, levels=c("task","survey"), labels=c("Task", "Survey")), value, fill=task, alpha=key))+
   geom_boxplot()+
@@
   theme(legend.title = element_blank())+
-  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
+  scale_alpha_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                     labels = c("Variance between individuals",
@@
                                "Error variance"),
-                    values=c("grey65", "grey45", "grey25"))+
-  scale_color_discrete(guide = FALSE)+
+                    values=c(0.1, 0.5, 1))+
+  scale_fill_discrete(guide = FALSE)+
+  guides(alpha=guide_legend(override.aes=list(fill=hcl(c(15,195),100,0,alpha=c(0.1,0.5, 1)),
+                                              colour=NA)))+
   xlab("")+
@@
 ggsave('Variance_Breakdown_Plot_Summary.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in", dpi = 100)
+```
+
+```{r}
+tmp %>%
+  gather(key, value, -dv, -task) %>%
+  group_by(task, key) %>%
+  summarise(mean_pct = mean(value),
+            sd_pct = sd(value))
 ```
@@
 
-The type of ICC we have chosen does not take ... in to account. This is why Weir recommends checking whether there is a significant change based on time and examining the SEMs.
-
-Had we chosen another kind of ICC taking ... into account could have suggested that tasks have ...(higher/lower) reliability.
+The type of ICC we have chosen does not take within subject (between session/systematic) variance in to account.
+This is why Weir recommends checking whether there is a significant change based on time and examining the SEMs.
+
+Had we chosen another kind of ICC taking this source of variance into account (e.g. 2,1 or 2,k) they could have suggested that tasks have lower reliability.
 
@@
 
-To check whether a
-
-first check if the effect of time is significant
-compute confidence intervals and check what percent of participants have scores that fall out of this range
-
-```{r}
-boot_df
+To check whether a measure shows learning effects in a meaningful number of bootstrapped samples we can: check if the effect of time is significant in each bootstrapped sample and filter variables that have more than 5% of the boostrapped samples showing significant time effects.
+
+Another way might be to compute confidence intervals using SEMs as described in the second half of Weir (2005) and check what percent of participants have scores that fall out of this range.
+I haven't pursued this at least for now.
+
+Here we ask: Which variables have significant time effects in more than 5% of the bootstrapped samples?
+
+22/74 survey measures
+135/335 task measures
+
+```{r}
+boot_df %>%
+  select(dv, p_time, task) %>%
+  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
+  group_by(dv)%>%
+  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
+            task = unique(task))%>%
+  filter(pct_sig_time_effect>5) %>%
+  arrange(task,-pct_sig_time_effect) %>%
+  ungroup()%>%
+  group_by(task) %>%
+  summarise(count=n())
 ```

### 2018-03-12 code/SRO_Report.Rmd
updating based on draft comments

@@
 summary(lmerTest::lmer(icc ~  task + (1|dv), boot_df))
-```
-
-```{r warning=FALSE, message=FALSE}
-boot_df %>%
-  ggplot(aes(icc, fill = task))+
-  geom_histogram(alpha=0.5, position='identity')+
-  theme_bw()+
-  theme(legend.title = element_blank())+
-  xlab("ICC")
-
-ggsave('Hist_Boot_Rel.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 72)
 ```
@@
   group_by(task, key) %>%
-  ggplot(aes(factor(task, levels=c("task","survey"), labels=c("Task", "Survey")), value, fill=task, alpha=key))+
-  geom_boxplot()+
-  theme_bw()+
-  theme(legend.title = element_blank())+
-  scale_alpha_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
+  summarise(mean_pct = mean(value),
+            sd_pct = sd(value),
+            n = n()) %>%
+  mutate(cvl = qt(0.025, n-1),
+         cvu = qt(0.975, n-1),
+         cil = mean_pct+(sd_pct*cvl)/sqrt(n),
+         ciu = mean_pct+(sd_pct*cvu)/sqrt(n)) %>%
+  ggplot(aes(factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                     labels = c("Variance between individuals",
                                "Variance between sessions",
-                               "Error variance"),
-                    values=c(0.1, 0.5, 1))+
-  scale_fill_discrete(guide = FALSE)+
-  guides(alpha=guide_legend(override.aes=list(fill=hcl(c(15,195),100,0,alpha=c(0.1,0.5, 1)),
-                                              colour=NA)))+
-  xlab("")+
-  ylab("Percent")
-
-ggsave('Variance_Breakdown_Plot_Summary.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in", dpi = 100)
-```
-
-```{r}
-tmp %>%
-  gather(key, value, -dv, -task) %>%
-  group_by(task, key) %>%
-  summarise(mean_pct = mean(value),
-            sd_pct = sd(value))
+                               "Error variance")), mean_pct, color=task))+
+  geom_point(position=position_dodge(width = 0.25), size=5)+
+  geom_errorbar(aes(ymin=mean_pct-sd_pct, ymax=mean_pct+sd_pct), position=position_dodge(width = 0.25), width=0, size=2)+
+  theme_bw()+
+  xlab('')+
+  ylab('Percent')+
+  theme(legend.title = element_blank(),
+        legend.text = element_text(size=14),
+        axis.text = element_text(size=12),
+        axis.title.y = element_text(size=12))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))
+
+ggsave('Variance_Breakdown_DotPlot.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 6, height = 5, units = "in", dpi = 100)
 ```
@@
             num_measures = n()/1000,
-            num_trials = unique(num_all_trials))%>%
+            mean_num_trials = round(mean(num_all_trials)))%>%
   arrange(-median_icc, -median_spearman)
@@
 #read t1 data
-t1_hr = read.csv(gzfile(paste0(test_data_path,'Individual_Measures/hierarchical_rule.csv.gz'), 'rt'))
-
-t2_hr = read.csv(gzfile(paste0(retest_data_path,'Individual_Measures/hierarchical_rule.csv.gz'), 'rt'))
+t1_tbt = read.csv(gzfile(paste0(test_data_path,'Individual_Measures/threebytwo.csv.gz'), 'rt'))
+
+t2_tbt = read.csv(gzfile(paste0(retest_data_path,'Individual_Measures/threebytwo.csv.gz'), 'rt'))
 
 #get only retest subjects
-t1_hr = t1_hr[as.character(t1_hr$worker_id) %in% as.character(test_data$sub_id),]
-t2_hr = t2_hr[as.character(t2_hr$worker_id) %in% as.character(retest_data$sub_id),]
-
-#remove missed trials (rt == -1)
-t1_hr = t1_hr %>% filter(rt != -1)
-t2_hr = t2_hr %>% filter(rt != -1)
+t1_tbt = t1_tbt[as.character(t1_tbt$worker_id) %in% as.character(test_data$sub_id),]
+t2_tbt = t2_tbt[as.character(t2_tbt$worker_id) %in% as.character(retest_data$sub_id),]
 
 #dv's
-#accuracy: mean correct
-#average rt: median of correct trials only
-#score: sum correct
-
-calc_break_dvs = function(x, breaks=seq(0, 360, 10)[-1]){
-
-  calc_dvs = function(x){
-    out = x %>%
-      summarise(acc = mean(correct),
-                avg_rt = median(rt[correct == 1]))
-                # score = sum(correct))
-    return(out)
+calc_break_dvs = function(df, breaks=c(seq(0, 440, 10)[c(-1, -45)], 439)){
+
+  df = df %>%
+      filter(exp_stage != "practice")
+
+  calc_dvs = function(df){
+
+    df = df %>%
+      mutate(correct_shift = lag(correct),
+             task_switch_shift = lag(task_switch))
+
+    missed_percent = mean(df$rt == -1)
+
+     df = df %>%
+      filter(rt != -1)
+
+     df_correct = df %>%
+       filter(correct == "True" & correct_shift == "True")
+
+     dvs = data.frame(acc = mean(ifelse(df$correct == "True",1,0)),
+                      avg_rt_error = median(df$rt[df$correct == "False"]),
+                      std_rt_error = sd(df$rt[df$correct == "False"]),
+                      avg_rt = median(df_correct$rt),
+                      std_rt = sd(df_correct$rt),
+                      missed_percent = missed_percent)
+
+     cue_switch_cost_rt_df = df_correct %>% group_by(CTI, cue_switch) %>% summarise(cue_switch_cost = median(rt)) %>% complete(cue_switch, CTI) %>% filter(cue_switch %in% c("stay", "switch")) %>% ungroup() %>% spread(cue_switch,cue_switch_cost) %>% group_by(CTI) %>% summarise(cue_switch_cost_rt = switch-stay)
+
+     dvs$cue_switch_cost_rt_100 = cue_switch_cost_rt_df$cue_switch_cost_rt[cue_switch_cost_rt_df$CTI == 100]
+     dvs$cue_switch_cost_rt_900 = cue_switch_cost_rt_df$cue_switch_cost_rt[cue_switch_cost_rt_df$CTI == 900]
+
+     task_switch_rt = df_correct %>% mutate(task_switch = factor(ifelse(grepl("switch",task_switch), T, F))) %>% group_by(CTI, task_switch) %>% summarise(rt = median(rt)) %>% complete(task_switch, CTI) %>% ungroup() %>% filter(task_switch == T)
+
+     cue_switch_rt = df_correct %>% group_by(CTI, cue_switch) %>% summarise(rt = median(rt)) %>% complete(cue_switch, CTI) %>% ungroup() %>% filter(cue_switch == "switch")
+
+     dvs$task_switch_cost_rt_100 = task_switch_rt$rt[task_switch_rt$CTI == 100] - cue_switch_rt$rt[cue_switch_rt$CTI == 100]
+
+     dvs$task_switch_cost_rt_900 = task_switch_rt$rt[task_switch_rt$CTI == 900] - cue_switch_rt$rt[cue_switch_rt$CTI == 900]
+
+     cue_switch_cost_acc_df = df %>% group_by(CTI, cue_switch) %>% summarise(acc = mean(ifelse(correct == "True",1, 0))) %>% complete(cue_switch, CTI) %>% filter(cue_switch %in% c("stay", "switch")) %>% spread(cue_switch, acc) %>% ungroup() %>% group_by(CTI) %>% summarise(cue_switch_cost_acc = switch-stay)
+
+     dvs$cue_switch_cost_acc_100 = cue_switch_cost_acc_df$cue_switch_cost_acc[cue_switch_cost_acc_df$CTI == 100]
+     dvs$cue_switch_cost_acc_900 = cue_switch_cost_acc_df$cue_switch_cost_acc[cue_switch_cost_acc_df$CTI == 900]
+
+     task_switch_acc = df %>% mutate(task_switch = factor(ifelse(grepl("switch",task_switch), T, F))) %>% group_by(CTI, task_switch) %>% summarise(acc = mean(ifelse(correct == "True",1,0))) %>% complete(task_switch, CTI) %>%  ungroup() %>% filter(task_switch == T)
+
+     cue_switch_acc = df %>% group_by(CTI, cue_switch) %>% summarise(acc = mean(ifelse(correct == "True",1,0))) %>% complete(cue_switch, CTI) %>% ungroup() %>% filter(cue_switch == "switch")
+
+     dvs$task_switch_cost_acc_100 = task_switch_acc$acc[task_switch_acc$CTI == 100] - cue_switch_acc$acc[cue_switch_acc$CTI == 100]
+
+     dvs$task_switch_cost_acc_900 = task_switch_acc$acc[task_switch_acc$CTI == 900] - cue_switch_acc$acc[cue_switch_acc$CTI == 900]
+
+    return(dvs)
   }
@@
   for(i in 1:length(breaks)){
-    tmp = x[1:breaks[i],]
+    tmp = df[1:breaks[i],]
     dvs = calc_dvs(tmp)
@@
   # first remove these
-  out = out %>% drop_na()
+  # out = out %>% drop_na()
 
   # then calculate the dv's for the remaining trials
-  if(nrow(x)!=360 & nrow(x)%%10 != 0){
-    dvs = calc_dvs(x)
+  if(nrow(df)!=440 & nrow(df)%%10 != 0){
+    dvs = calc_dvs(df)
     out = rbind(out, dvs)
@@
 #get dv's for t1 and t2
-t1_dvs = t1_hr %>%
+t1_dvs = t1_tbt %>%
   group_by(worker_id) %>%
@@
 
-t2_dvs = t2_hr %>%
+t2_dvs = t2_tbt %>%
   group_by(worker_id) %>%

### 2018-03-13 code/SRO_Report.Rmd
updating based on draft comments

@@
 
-target task: one without hddm variables, has dv's that are easily codable in r, a lot of trials, possibly multiple dependent measures  
-method: import raw response data for chosen task for both t1 and t2, calculate dv's for for both t's for different number of trials, calculate retest reliability point estimates for each of these dv's with different trial numbers
-candidates: angling risk task, columbia card task, dietary decision, hierarchical rule, keep track, probabilistic selection, psychological refractory period, two stage decision
-
-```{r warning=FALSE, message=FALSE}
-#read t1 data
-t1_tbt = read.csv(gzfile(paste0(test_data_path,'Individual_Measures/threebytwo.csv.gz'), 'rt'))
-
-t2_tbt = read.csv(gzfile(paste0(retest_data_path,'Individual_Measures/threebytwo.csv.gz'), 'rt'))
-
-#get only retest subjects
-t1_tbt = t1_tbt[as.character(t1_tbt$worker_id) %in% as.character(test_data$sub_id),]
-t2_tbt = t2_tbt[as.character(t2_tbt$worker_id) %in% as.character(retest_data$sub_id),]
-
-#dv's
-calc_break_dvs = function(df, breaks=c(seq(0, 440, 10)[c(-1, -45)], 439)){
-
-  df = df %>%
-      filter(exp_stage != "practice")
-
-  calc_dvs = function(df){
-
-    df = df %>%
-      mutate(correct_shift = lag(correct),
-             task_switch_shift = lag(task_switch))
-
-    missed_percent = mean(df$rt == -1)
-
-     df = df %>%
-      filter(rt != -1)
-
-     df_correct = df %>%
-       filter(correct == "True" & correct_shift == "True")
-
-     dvs = data.frame(acc = mean(ifelse(df$correct == "True",1,0)),
-                      avg_rt_error = median(df$rt[df$correct == "False"]),
-                      std_rt_error = sd(df$rt[df$correct == "False"]),
-                      avg_rt = median(df_correct$rt),
-                      std_rt = sd(df_correct$rt),
-                      missed_percent = missed_percent)
-
-     cue_switch_cost_rt_df = df_correct %>% group_by(CTI, cue_switch) %>% summarise(cue_switch_cost = median(rt)) %>% complete(cue_switch, CTI) %>% filter(cue_switch %in% c("stay", "switch")) %>% ungroup() %>% spread(cue_switch,cue_switch_cost) %>% group_by(CTI) %>% summarise(cue_switch_cost_rt = switch-stay)
-
-     dvs$cue_switch_cost_rt_100 = cue_switch_cost_rt_df$cue_switch_cost_rt[cue_switch_cost_rt_df$CTI == 100]
-     dvs$cue_switch_cost_rt_900 = cue_switch_cost_rt_df$cue_switch_cost_rt[cue_switch_cost_rt_df$CTI == 900]
-
-     task_switch_rt = df_correct %>% mutate(task_switch = factor(ifelse(grepl("switch",task_switch), T, F))) %>% group_by(CTI, task_switch) %>% summarise(rt = median(rt)) %>% complete(task_switch, CTI) %>% ungroup() %>% filter(task_switch == T)
-
-     cue_switch_rt = df_correct %>% group_by(CTI, cue_switch) %>% summarise(rt = median(rt)) %>% complete(cue_switch, CTI) %>% ungroup() %>% filter(cue_switch == "switch")
-
-     dvs$task_switch_cost_rt_100 = task_switch_rt$rt[task_switch_rt$CTI == 100] - cue_switch_rt$rt[cue_switch_rt$CTI == 100]
-
-     dvs$task_switch_cost_rt_900 = task_switch_rt$rt[task_switch_rt$CTI == 900] - cue_switch_rt$rt[cue_switch_rt$CTI == 900]
-
-     cue_switch_cost_acc_df = df %>% group_by(CTI, cue_switch) %>% summarise(acc = mean(ifelse(correct == "True",1, 0))) %>% complete(cue_switch, CTI) %>% filter(cue_switch %in% c("stay", "switch")) %>% spread(cue_switch, acc) %>% ungroup() %>% group_by(CTI) %>% summarise(cue_switch_cost_acc = switch-stay)
-
-     dvs$cue_switch_cost_acc_100 = cue_switch_cost_acc_df$cue_switch_cost_acc[cue_switch_cost_acc_df$CTI == 100]
-     dvs$cue_switch_cost_acc_900 = cue_switch_cost_acc_df$cue_switch_cost_acc[cue_switch_cost_acc_df$CTI == 900]
-
-     task_switch_acc = df %>% mutate(task_switch = factor(ifelse(grepl("switch",task_switch), T, F))) %>% group_by(CTI, task_switch) %>% summarise(acc = mean(ifelse(correct == "True",1,0))) %>% complete(task_switch, CTI) %>%  ungroup() %>% filter(task_switch == T)
-
-     cue_switch_acc = df %>% group_by(CTI, cue_switch) %>% summarise(acc = mean(ifelse(correct == "True",1,0))) %>% complete(cue_switch, CTI) %>% ungroup() %>% filter(cue_switch == "switch")
-
-     dvs$task_switch_cost_acc_100 = task_switch_acc$acc[task_switch_acc$CTI == 100] - cue_switch_acc$acc[cue_switch_acc$CTI == 100]
-
-     dvs$task_switch_cost_acc_900 = task_switch_acc$acc[task_switch_acc$CTI == 900] - cue_switch_acc$acc[cue_switch_acc$CTI == 900]
-
-    return(dvs)
-  }
-
-  out = data.frame()
-
-  for(i in 1:length(breaks)){
-    tmp = df[1:breaks[i],]
-    dvs = calc_dvs(tmp)
-    out = rbind(out, dvs)
-  }
-
-  # due to timeout trials exclusion not all subjects might have 360 rows
-  # this would lead to na's for later trial breaks
-  # first remove these
-  # out = out %>% drop_na()
-
-  # then calculate the dv's for the remaining trials
-  if(nrow(df)!=440 & nrow(df)%%10 != 0){
-    dvs = calc_dvs(df)
-    out = rbind(out, dvs)
-  }
-
-  #to keep track for later merge
-  out$breaks = row.names(out)
-
-  return(out)
-}
-
-#get dv's for t1 and t2
-t1_dvs = t1_tbt %>%
-  group_by(worker_id) %>%
-  do(calc_break_dvs(.)) %>%
-  rename(sub_id = worker_id)
-
-t2_dvs = t2_tbt %>%
-  group_by(worker_id) %>%
-  do(calc_break_dvs(.)) %>%
-  rename(sub_id = worker_id)
-
-# merge to get same number of rows for each subject at both time points
-hr_merge = merge(t1_dvs, t2_dvs, by = c("sub_id", "breaks"))
-
-# rm(t1_dvs, t2_dvs)
-
-hr_merge = hr_merge %>%
-  gather(key, value, -sub_id, -breaks) %>%
-  separate(key, c("dv", "time"), sep="\\.") %>%
-  mutate(time = ifelse(time == "x", 1, 2))
-
-t1_dvs = hr_merge %>%
-  filter(time == 1) %>%
-  select(-time) %>%
-  spread(dv, value)
-
-t2_dvs = hr_merge %>%
-  filter(time == 2) %>%
-  select(-time) %>%
-  spread(dv, value)
-
-# calculate point estimates for reliability of each of the variables for each break
-# get_icc for each break of tmp_t1_dvs and tmp_t2_dvs
-# trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))), acc_icc=rep(NA, length(unique(t1_dvs$breaks))), avg_rt_icc=rep(NA, length(unique(t1_dvs$breaks))), score_icc=rep(NA, length(unique(t1_dvs$breaks))))
-trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))), acc_icc=rep(NA, length(unique(t1_dvs$breaks))), avg_rt_icc=rep(NA, length(unique(t1_dvs$breaks))))
-for(i in 1:length(unique(t1_dvs$breaks))){
-  cur_break = unique(t1_dvs$breaks)[i]
-  tmp_t1_dvs = t1_dvs %>% filter(breaks == cur_break)
-  tmp_t2_dvs = t2_dvs %>% filter(breaks == cur_break)
-  trial_num_rel_df$breaks[i] = cur_break
-  trial_num_rel_df$acc_icc[i] = get_icc("acc", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$avg_rt_icc[i] = get_icc("avg_rt", tmp_t1_dvs, tmp_t2_dvs)
-  # trial_num_rel_df$score_icc[i] = get_icc("score", tmp_t1_dvs, tmp_t2_dvs)
-}
-rm(i, cur_break, tmp_t1_dvs, tmp_t2_dvs)
-
-trial_num_rel_df$breaks = as.numeric(trial_num_rel_df$breaks)
+Example task: three by two
+
+```{r warning=FALSE, message=FALSE}
+trial_num_rel_df = read.csv(paste0(retest_data_path, 'trial_num_rel_df_tbt.csv'))
 
@@
 ```{r}
-rel_df[c(rel_df$dv %in% grep('hierarchical_rule', rel_df$dv, value = TRUE)),]
+rel_df[c(rel_df$dv %in% grep('threebytwo', rel_df$dv, value = TRUE)),]
 ```

### 2018-03-15 code/SRO_Report.Rmd
add lit review analyses

@@
 
+cols <- c("Accuracy" = '#084594', "Average RT error" = '#99000d', "SD RT error" = '#cb181d', "Average RT correct" = '#ef3b2c', "SD RT correct" = '#fb6a4a', "Missed percentage" = '#2171b5', "Cue switch cost RT (100)" = '#fc9272', "Cue switch cost RT (900)" = '#fcbba1', "Task switch cost RT (100)" = '#fee0d2', "Task switch cost RT (900)" = '#fff5f0', "Cue switch cost Acc (100)" = '#4292c6', "Cue switch cost Acc (900)" = '#6baed6', "Task switch cost Acc (100)" = '#9ecae1', "Task switch cost Acc (900)" = '#c6dbef')
+
 trial_num_rel_df %>%
   gather(key, value, -breaks) %>%
-  # ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_icc", "score_icc"), labels = c("Accuracy", "Average RT", "Score"))))+
-  ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_icc"), labels = c("Accuracy", "Average RT"))))+
+  ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_error_icc", "std_rt_error_icc", "avg_rt_icc", "std_rt_icc", "missed_percent_icc", "cue_switch_cost_rt_100_icc", "cue_switch_cost_rt_900_icc", "task_switch_cost_rt_100_icc", "task_switch_cost_rt_900_icc", "cue_switch_cost_acc_100_icc", "cue_switch_cost_acc_900_icc", "task_switch_cost_acc_100_icc", "task_switch_cost_acc_900_icc"), labels = c("Accuracy", "Average RT error", "SD RT error", "Average RT correct", "SD RT correct", "Missed percentage", "Cue switch cost RT (100)", "Cue switch cost RT (900)", "Task switch cost RT (100)", "Task switch cost RT (900)", "Cue switch cost Acc (100)", "Cue switch cost Acc (900)", "Task switch cost Acc (100)", "Task switch cost Acc (900)"))))+
   geom_point()+
@@
   ylab("ICC")+
-  theme(legend.title = element_blank())
+  theme(legend.title = element_blank())+
+  scale_color_manual(values = cols,
+                     breaks = c("Accuracy", "Missed percentage", "Cue switch cost Acc (100)", "Cue switch cost Acc (900)", "Task switch cost Acc (100)", "Task switch cost Acc (900)", "Average RT error", "SD RT error", "Average RT correct", "SD RT correct",  "Cue switch cost RT (100)", "Cue switch cost RT (900)", "Task switch cost RT (100)", "Task switch cost RT (900)"))
 
@@
 ```
+
+## Comparison to prior literature
+
+```{r}
+var_boot_df = boot_df %>%
+  group_by(dv) %>%
+  summarise(icc_median = quantile(icc, probs = 0.5),
+            icc_2.5 = quantile(icc, probs = 0.025),
+            icc_97.5 = quantile(icc, probs = 0.975)
+            )
+
+boot_lit_rel = function(df, samples = 100, rel_col = 'retest_reliability'){
+
+  boot_once = function(df){
+    #get number of rows in df
+    data_amount = nrow(df)
+    #sample as many reliability estimates as there are rows in the df
+    boot_sample = sample(c(1:data_amount), size=data_amount, replace=TRUE)
+    boot_sample = df[boot_sample,]
+    #calculate median reliability estimate for the sampled estimates
+    return(median(boot_sample[,rel_col])) 
+  }
+
+  out = replicate(samples, boot_once(df))
+
+  return(data.frame(median_lit_rel=out))
+}
+
+var_lit_review = lit_review %>%
+  group_by(dv)%>%
+  do(boot_lit_rel(.))
+  summarise(median_reliability=median(retest_reliability),
+            task = unique(task)) %>%
+  mutate(dv = as.character(dv))
+
+var_boot_df = boot_df %>%
+  group_by(dv) %>%
+  summarise(median_icc = quantile(icc, probs = 0.5))
+
+var_lit_review = lit_review %>%
+  # filter(sample_size > 100) %>%
+  group_by(dv)%>%
+  summarise(median_reliability=median(retest_reliability),
+            task = unique(task),
+            mean_sample = mean(sample_size)) %>%
+  mutate(dv = as.character(dv))
+
+rel_comp = var_lit_review %>%
+  left_join(var_boot_df, by = 'dv')
+
+rel_comp
+```
+
+Correlation between our median estimates from bootstrapped samples and the literature review for task variables
+```{r}
+with(rel_comp %>% filter(task == "task"), cor(median_icc, median_reliability))
+```
+
+```{r}
+with(rel_comp %>% filter(task == "survey"), cor(median_icc, median_reliability))
+```
+
+Potential problems in this graph: 
+- not all metrics are ICC's
+- difference in delay between completion of two tests (does it make a difference in the lit review?)
+
+```{r}
+rel_comp %>%
+  ggplot(aes(median_reliability, median_icc, color=task))+
+  geom_point()+
+  geom_abline(slope=1, intercept=0)+
+  theme_bw()+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  theme(legend.title = element_blank())+
+  xlab('Median reliability from literature')+
+  ylab('Median ICC from bootstrapped samples')
+```
+
+```{r}
+lit_review %>%
+  ggplot(aes(sample_size, retest_reliability, color=task))+
+  geom_point()
+summary(lmer(retest_reliability~sample_size+task+(1|dv), data=lit_review))
+
+#sd by average sample size
+lit_review %>%
+  group_by(dv) %>%
+  summarise(sd_rel = sd(retest_reliability),
+            avg_sample_size = mean(sample_size)) %>%
+  ggplot(aes(avg_sample_size, sd_rel))+
+  geom_point()+
+  xlim(0,200)
+```
+
+x = deviance between our data and literature
+y = average sample size
+
+```{r}
+rel_comp %>%
+  mutate(diff_sq = (median_icc - median_reliability)^2) %>%
+  ggplot(aes(diff_sq, mean_sample, color=task))+
+  geom_point()+
+  geom_smooth()
+```
+
+```{r}
+lit_review %>%
+  ggplot(aes(sample_size))+
+  geom_histogram()+
+  theme_bw()
+```

### 2018-03-15 code/SRO_Retest_Analyses.Rmd
refactor post ddm analyses removal

--- 2018-03-15 code/SRO_Report.Rmd
@@
 
+Post process dv's from cluster to calculate reliabilities
+```{r}
+t1_dvs = read.csv(paste0(retest_data_path, 't1_tbt_dvs.csv'))
+t2_dvs = read.csv(paste0(retest_data_path, 't2_tbt_dvs.csv'))
+```
+
+```{r}
+hr_merge = merge(t1_dvs, t2_dvs, by = c("sub_id", "breaks"))
+
+hr_merge = hr_merge %>%
+  gather(key, value, -sub_id, -breaks) %>%
+  separate(key, c("dv", "time"), sep="\\.") %>%
+  mutate(time = ifelse(time == "x", 1, 2))
+
+t1_dvs = hr_merge %>%
+  filter(time == 1) %>%
+  select(-time) %>%
+  spread(dv, value)
+
+t2_dvs = hr_merge %>%
+  filter(time == 2) %>%
+  select(-time) %>%
+  spread(dv, value)
+
+# calculate point estimates for reliability of each of the variables for each break
+# get_icc for each break of tmp_t1_dvs and tmp_t2_dvs
+
+trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))),
+                              acc_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              avg_rt_error_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              std_rt_error_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              avg_rt_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              std_rt_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              missed_percent_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              cue_switch_cost_rt_100_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              cue_switch_cost_rt_900_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              task_switch_cost_rt_100_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              task_switch_cost_rt_900_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              cue_switch_cost_acc_100_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              cue_switch_cost_acc_900_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              task_switch_cost_acc_100_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              task_switch_cost_acc_900_icc=rep(NA, length(unique(t1_dvs$breaks))))
+
+for(i in 1:length(unique(t1_dvs$breaks))){
+  cur_break = unique(t1_dvs$breaks)[i]
+  tmp_t1_dvs = t1_dvs %>% filter(breaks == cur_break)
+  tmp_t2_dvs = t2_dvs %>% filter(breaks == cur_break)
+  trial_num_rel_df$breaks[i] = cur_break
+  trial_num_rel_df$acc_icc[i] = get_icc("acc", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$avg_rt_error_icc[i] = get_icc("avg_rt_error", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$std_rt_error_icc[i] = get_icc("std_rt_error", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$avg_rt_icc[i] = get_icc("avg_rt", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$std_rt_icc[i] = get_icc("std_rt", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$missed_percent_icc[i] = get_icc("missed_percent", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$cue_switch_cost_rt_100_icc[i] = get_icc("cue_switch_cost_rt_100", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$cue_switch_cost_rt_900_icc[i] = get_icc("cue_switch_cost_rt_900", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$trial_switch_cost_rt_100_icc[i] = get_icc("task_switch_cost_rt_100", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$trial_switch_cost_rt_900_icc[i] = get_icc("task_switch_cost_rt_900", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$cue_switch_cost_acc_100_icc[i] = get_icc("cue_switch_cost_acc_100", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$cue_switch_cost_acc_900_icc[i] = get_icc("cue_switch_cost_acc_900", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$trial_switch_cost_acc_100_icc[i] = get_icc("task_switch_cost_acc_100", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$trial_switch_cost_acc_900_icc[i] = get_icc("task_switch_cost_acc_900", tmp_t1_dvs, tmp_t2_dvs)
+}
+rm(i, cur_break, tmp_t1_dvs, tmp_t2_dvs)
+
+trial_num_rel_df$breaks = as.numeric(trial_num_rel_df$breaks)
+
+write.csv(trial_num_rel_df, paste0(retest_data_path, 'trial_num_rel_df_tbt.csv'))
+```
+
 ```{r warning=FALSE, message=FALSE}
@@
 ggsave('Bootstrap_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 6, units = "in", limitsize = FALSE)
-```
-
-#### DDM Variance breakdown
-
-What does the variance breakdown look like for DDM variables separately?
-
-```{r warning=FALSE, message=FALSE}
-tmp = rel_df %>%
-  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
-         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
-         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
-  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
-  mutate(dv = factor(dv, levels = dv[order(task)])) %>%
-  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
-  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
-  arrange(task_group, var_subs_pct) %>%
-  mutate(rank = row_number()) %>%
-  arrange(task, task_group, rank) %>%
-  gather(key, value, -dv, -task_group, -var, -task, -rank) %>%
-  ungroup()%>%
-  mutate(task_group = gsub("_", " ", task_group),
-         var = gsub("_", " ", var)) %>%
-  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
-  mutate(task_group = gsub("survey", "", task_group)) %>%
-  filter(task=="task",
-         grepl("EZ|hddm", dv))%>%
-  arrange(task_group, rank)
-labels = tmp %>%
-  distinct(dv, .keep_all=T)
-
-p1 <- tmp %>%
-  ggplot(aes(x=factor(rank), y=value, fill=factor(key, levels = c("var_resid_pct", "var_ind_pct", "var_subs_pct"))))+
-  geom_bar(stat='identity', alpha = 0.75, color='#00BFC4')+
-  scale_x_discrete(breaks = labels$rank,
-                       labels = labels$var)+
-  coord_flip()+
-  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
-  theme(panel.spacing = unit(0.5, "lines"), 
-        strip.placement = "outside",
-        strip.text.y = element_text(angle=180),
-        panel.background = element_rect(fill = NA),
-        panel.grid.major = element_line(colour = "grey85"),
-        legend.position = 'bottom')+
-  theme(legend.title = element_blank())+
-  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
-                      labels = c("Variance between individuals",
-                                 "Variance between sessions",
-                                 "Error variance"),
-                  values=c("grey65", "grey45", "grey25"))+
-  ylab("")+
-  xlab("")
-
-ggsave('Variance_Breakdown_Plot_DDM.jpg', plot = p1, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 12, height = 20, units = "in")
-```
-
-```{r echo=FALSE, out.width='100%'}
-knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Variance_Breakdown_Plot_DDM.jpg')
-```
-
-Summarizing it by raw vs fit and for each parameter
-
-```{r warning=FALSE, message=FALSE}
-tmp = measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(ddm_task == 1, 
-         overall_difference != "condition") %>%
-  drop_na() %>%
-  left_join(boot_df[,c("dv", "icc", "var_subs", "var_ind", "var_resid")], by = 'dv') %>%
-  mutate(var_subs_pct = (var_subs/(var_subs+var_ind+var_resid))*100,
-         var_ind_pct= (var_ind/(var_subs+var_ind+var_resid))*100,
-         var_resid_pct = (var_resid/(var_subs+var_ind+var_resid))*100) %>%
-  select(-task, -ddm_task, -num_all_trials, -var_subs, -var_ind, -var_resid) %>%
-  gather(key, value, -dv, -overall_difference, -raw_fit, -rt_acc, -icc)
-
-tmp %>%
-  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), value, fill=factor(rt_acc, levels = c("rt","accuracy","other", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy", "Other","Drift Rate", "Threshold", "Non-decision"))))+
-  geom_boxplot()+
-  facet_grid(factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct"), labels=c("Variance between subjects", "Variance between individuals", "Error variance"))~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
-  theme_bw()+
-  ylab("% of total variance")+
-  xlab("")+
-  theme(legend.title = element_blank())
-
-ggsave('Variance_Breakdown_Plot_DDM_summary.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 8, units = "in")
-```
-
-Not checking if these differ significantly because this seems to in the weeds for this paper.
-
-#### Change in parameter values depending on sample
-
-How much do parameter values change depending on whether the model was fit using the whole sample vs only the retest sample.
-Each point in these graphs is a subject's parameter estimates.
-There is no change for any of the EZ parameters.
-For the HDDM parameters most of the changes are happening for drift rates but they don't appear to be systematically higher or lower.
-
-```{r warning=FALSE, message=FALSE}
-hddm_fullfits <- test_data_full_sample_hddm[,names(test_data_full_sample_hddm) %in% names(hddm_refits)]
-
-hddm_fullfits = hddm_fullfits %>%
-  gather(dv, value, -sub_id)
-
-tmp = hddm_refits %>%
-  gather(dv, value, -sub_id) %>%
-  left_join(hddm_fullfits, by = c("sub_id", "dv")) %>%
-  rename(fullfit = value.y, refit = value.x) %>%
-  left_join(measure_labels[,c("dv", "raw_fit", "rt_acc")], by="dv") %>%
-  filter(rt_acc %in% c("drift rate","non-decision", "threshold"))
-
-tmp %>%
-  ggplot(aes(fullfit, refit, label=dv))+
-  geom_point(aes(color=rt_acc))+
-  facet_wrap(~raw_fit)+
-  theme_bw()+
-  geom_abline(slope=1, intercept=0)+
-  xlab("Fit on full sample")+
-  ylab("Fit on retest sample")+
-  theme(legend.title = element_blank())
-```
-
-```{r}
-tmp %>%
-  mutate(refit_diff = fullfit - refit) %>%
-  group_by(raw_fit, rt_acc) %>%
-  summarise(mean = mean(refit_diff, na.rm=T),
-            sd = sd(refit_diff, na.rm=T))
-```
-
-A simple way to compare the two distributions of the parameters using the full or the retest sample would be to run a t-test.
-Since this would have a normality assumption we first check the distributions of the parameters.
-Though the threshold and non-decision times look closer to normal the drift rates have a clear bimodal distribution.
-Since these are the estimates on which we find the greatest changes we should make sure to transform them somehow before running the test.
-
-```{r warning=FALSE, message=FALSE}
-tmp %>%
-  filter(raw_fit == 'hddm') %>%
-  gather(key, value, -sub_id, -dv, -raw_fit, -rt_acc) %>%
-  ggplot(aes(value))+
-  geom_histogram(position='identity', alpha=0.5)+
-  theme_bw()+
-  facet_grid(rt_acc~key, scales='free')
-```
-
-What if you log transform the drift rates? The bimodal distribution becomes one with a long left tail. Still not great to do a t-test on.
-
-```{r warning=FALSE, message=FALSE}
-tmp %>%
-  filter(raw_fit == 'hddm', rt_acc == 'drift rate') %>%
-  gather(key, value, -sub_id, -dv, -raw_fit, -rt_acc) %>%
-  mutate(value = log(value)) %>%
-  ggplot(aes(value))+
-  geom_histogram(alpha = 0.5)+
-  theme_bw()+
-  facet_wrap(~key)
-```
-
-How about the distribution of the difference scores? This looks better to do a t-test on.
-
-```{r message=FALSE}
-tmp %>%
-  filter(raw_fit == 'hddm', rt_acc == 'drift rate') %>%
-  mutate(diff = fullfit - refit) %>%
-  na.omit() %>%
-  ggplot(aes(diff))+
-  geom_histogram(alpha=0.5)+
-  theme_bw()
-```
-
-The distribution of the difference scores between the drift rates using the full and the retest sample differ from 0.
-The difference score distribution has a mean of 0.0016.
-This means that drift rate estimates using the full sample are significantly higher than those using the retest sample alone.
-
-```{r}
-diff = tmp %>%
-  filter(raw_fit == 'hddm', rt_acc == 'drift rate') %>%
-  mutate(diff = fullfit - refit) %>%
-  select(diff) %>%
-  na.omit()
-
-t.test(diff$diff, rep(0, nrow(tmp)))
-```
-
-Still the distribution of the difference scores does show negative values as well.
-The lack of clear systematicity in the changes of the parameter estimates can be difficult to interpret.
-A systematic change would have meant that the ranking remained the same regardless of the sample size.
-When the change is non-systematic in this way then a given subject that has high higher drift rates than most of the people in the full sample can appear to have lower drift rates than the same people when fit on the retest sample only.
-
-Of course these parameter estimates themselves are not very interpretable in their 'goodness' as they don't reflect anything about model fits.
-To determine the model fits for both cases I have written functions to sample from the posterior predictive and calculate $R^2$'s for each subject.
-These currently run too slow, however, and have been deferred for now.
-
-Let's quickly look if the changes are different than 0 for non-decision times and thresholds as well. They are not.
-
-```{r}
-diff = tmp %>%
-  filter(raw_fit == 'hddm', rt_acc == 'non-decision') %>%
-  mutate(diff = fullfit - refit) %>%
-  select(diff) %>%
-  na.omit()
-
-t.test(diff$diff, rep(0, nrow(tmp)))
-```
-
-```{r}
-diff = tmp %>%
-  filter(raw_fit == 'hddm', rt_acc == 'threshold') %>%
-  mutate(diff = fullfit - refit) %>%
-  select(diff) %>%
-  na.omit()
-
-t.test(diff$diff, rep(0, nrow(tmp)))
-```
-
-```{r}
-rm(diff)
-```
-
-Does this change reliability?
-18/33 of the bootstrapped reliability distributions for the refit hddm drift rates have different means than the reliability distributions using the fullfit drift rates.
-Only in 7/18 is the refit reliabilities higher.
-
-```{r}
-#Compare bootstrapped reliabilities for refits (replaced in boot_df) to bootstrapped reliabilities of full fits
-refit_ddm_drift_boot_df = boot_df[boot_df$dv %in% grep('hddm_drift',names(hddm_refits), value=T),]
-fullfit_ddm_drift_boot_df = fullfit_boot_df[fullfit_boot_df$dv %in% unique(refit_ddm_drift_boot_df$dv),]
-
-get_t_test_out <- function(df, x = icc.x, y = icc.y){
-  out = data.frame(p.value=NA, mean_x = NA, mean_y=NA)
-  attach(df)
-  mod = t.test(x, y)
-  detach(df)
-  out$p.value = mod$p.value
-  out$mean_x = as.numeric(mod$estimate[1])
-  out$mean_y = as.numeric(mod$estimate[2])  
-  return(out)
-}
-
-refit_ddm_drift_boot_df %>%
-  select(X, dv, icc) %>%
-  left_join(fullfit_ddm_drift_boot_df[,c('X', 'dv', 'icc')], by = c('X', 'dv')) %>%
-  group_by(dv) %>%
-  do(get_t_test_out(.)) %>%
-  mutate(sig_diff = ifelse(p.value<0.05, 1, 0),
-         refit_better = ifelse(mean_x>mean_y,1,0)) %>%
-  filter(sig_diff == 1, refit_better == 1)
-```
-
-#### Parameter reliability depending on sample size
-
-[NOT INCLUDED IN DRAFT FOR NOW]
-
-There doesn't seem to be an effect looking at the graph but the multilevel model seems to show a very significant but tiny effect.
-
-```{r message=FALSE, warning=FALSE}
-tmp <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/all_ddm_sample_size_summary.csv')
-
-tmp
-
-ggplotly(tmp %>%
-  select(dv, N, icc_median) %>%
-  left_join(measure_labels[,c("dv", "raw_fit", "rt_acc")], by="dv") %>%
-  ggplot(aes(N, icc_median, color=dv))+
-  geom_line()+
-  theme_bw()+
-  theme(legend.position = 'none')+
-  xlab("Sample Size")+
-  ylab("Median ICC"))
-```
-
-The above graph suggests that the median reliability estimate does not change depending on the sample size.
-There is a degree of counterintuitiveness to that statement.
-One might expect less reliable parameter estimates for smaller sample sizes.
-
-The reliability of a measure depends on the different sources of variability.
-It would be larger the larger the between subject variability (BSV) is (and the lower within subject, WSV, and error variances, ERV, are).
-Larger sample sizes do not necessarily imply larger BSV.
-If there is a true BSV for the whole sample then BSV's of subsamples would have distribution that would be centered around this value with some variance.
-This variance would be smaller the larger the sample size.
-Because the distribution is centered around the true BSV the median reliability estimate from 100 samples would not deviate much as we see in the above graph.
-But the variance of that reliability estimate would.
-Specifically the variance of the reliability estimates should decrease with increasing sample size.
-Below we plot this for one task (for visualization ease).
-The lower end of the error bars in the first quantile, the point is the median and the upper bound is the last quantile of the reliability estimates for varying sample sizes.
-Indeed, we find the predicted pattern of decreasing variance in reliability estimates depending on sample size.
-
-```{r}
-tmp %>%
-  select(dv, N, icc_median, icc_2.5, icc_97.5) %>%
-  filter(grepl("stroop", dv)) %>%
-  ggplot(aes(N, icc_median, color = dv))+
-  geom_point()+
-  geom_errorbar(aes(ymin = icc_2.5, ymax = icc_97.5))+
-  theme_bw()+
-  theme(legend.position = "none")+
-  ylab("ICC")
-```
-
-```{r}
-summary(lmer(icc_median ~ N + (1|dv), tmp))
-```
-
-#### Is the H in HDDM important?
-
-For retest data plotting hierarchical estimates over flat estimates.
-
-```{r message = FALSE, warning=FALSE}
-retest_hddm_flat <- read.csv(paste0(retest_data_path, 'retest_hddm_flat.csv'))
-retest_hddm_flat = retest_hddm_flat %>% select(-X) %>% rename(sub_id = subj_id)
-retest_hddm_hier = retest_data[,c(names(retest_data) %in% names(retest_hddm_flat))]
-retest_hddm_flat = retest_hddm_flat[,c(names(retest_hddm_flat) %in% names(retest_hddm_hier))]
-
-retest_hddm_hier = retest_hddm_hier %>% gather(key, value, -sub_id)
-retest_hddm_flat = retest_hddm_flat %>% gather(key, value, -sub_id)
-
-retest_hddm_flat %>%
-  left_join(retest_hddm_hier, by=c('sub_id', 'key')) %>%
-  ggplot(aes(value.x, value.y, color=key))+
-  geom_point()+
-  geom_abline(slope=1, intercept=0)+
-  theme_bw()+
-  theme(legend.position = 'none')+
-  xlab('Parameter estimate without hierarchy')+
-  ylab('Parameter estimate with hierarchy')
-```
-
-For the retest data 6/43 variables have significantly different distributions when they are fit with hierarchy versus without.
-For all of them the hiearchical estimate distributions have significantly higher means.
-
-```{r message=FALSE, warning=FALSE}
-retest_hddm_flat %>%
-  left_join(retest_hddm_hier, by=c('sub_id', 'key')) %>%
-  group_by(key) %>%
-  do(get_t_test_out(.,x=value.x, y=value.y)) %>%
-  mutate(flat_diff = ifelse(p.value<0.05, 1, 0)) %>%
-  filter(flat_diff == 1) %>%
-  mutate(flat_high = ifelse(mean_x>mean_y,1,0))
-```
-
-For t1 data plotting hierarchical estimates over flat estimates.
-
-```{r warning=FALSE, message=FALSE}
-test_hddm_flat <- read.csv(paste0(retest_data_path, 't1_data/t1_hddm_flat.csv'))
-test_hddm_flat = test_hddm_flat %>% select(-X) %>% rename(sub_id = subj_id)
-test_hddm_hier = test_data[,c(names(test_data) %in% names(test_hddm_flat))]
-test_hddm_flat = test_hddm_flat[,c(names(test_hddm_flat) %in% names(test_hddm_hier))]
-
-test_hddm_hier = test_hddm_hier %>% gather(key, value, -sub_id)
-test_hddm_flat = test_hddm_flat %>% gather(key, value, -sub_id)
-
-test_hddm_flat %>%
-  left_join(test_hddm_hier, by=c('sub_id', 'key')) %>%
-  ggplot(aes(value.x, value.y, color=key))+
-  geom_point()+
-  geom_abline(slope=1, intercept=0)+
-  theme_bw()+
-  theme(legend.position = 'none')+
-  xlab('Parameter estimate without hierarchy')+
-  ylab('Parameter estimate with hierarchy')
-```
-
-For the t1 data 3/43 variables have significantly different distributions when they are fit with hierarchy versus without.
-For all of them the hiearchical estimate distributions have significantly higher means.
-
-```{r message=FALSE, warning=FALSE}
-test_hddm_flat %>%
-  left_join(test_hddm_hier, by=c('sub_id', 'key')) %>%
-  group_by(key) %>%
-  do(get_t_test_out(.,x=value.x, y=value.y)) %>%
-  mutate(flat_diff = ifelse(p.value<0.05, 1, 0)) %>%
-  filter(flat_diff == 1) %>%
-  mutate(flat_high = ifelse(mean_x>mean_y,1,0))
-```
-
-How does this affect reliability?
-
-```{r warning=FALSE, message=FALSE}
-flat_boot_df <- read.csv(gzfile(paste0(retest_data_path, 'flat_bootstrap_merged.csv.gz')))
-
-hier_boot_df = boot_df[c(boot_df$dv %in% unique(flat_boot_df$dv)),]
-
-flat_boot_df %>%
-  select(X, dv, icc) %>%
-  left_join(hier_boot_df[,c('X', 'dv', 'icc')], by = c('X', 'dv')) %>%
-  group_by(dv) %>%
-  do(get_t_test_out(.)) %>%
-  mutate(sig_diff = ifelse(p.value<0.05, 1, 0),
-         flat_better = ifelse(mean_x>mean_y,1,0)) %>%
-  filter(sig_diff == 1)
 ```

### 2018-03-15 code/SRO_Retest_Analyses.Rmd
refactor post ddm analyses removal

@@
 ---
-title: 'Self Regulation Ontology Retest Data Report'
+title: 'Self Regulation Ontology Retest Analyses'
 output:
@@
 ```{r, message=FALSE, warning=FALSE, include=FALSE}
-source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Report_Helper_Functions.R')
+source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Analyses_Helper_Functions.R')
 

### 2018-03-15 code/SRO_Retest_Analyses_Helper_Functions.R

@@ -13,7 +13,7 @@ library(plotly)
 library(DT)
 library(sjPlot)
 
-render_this <- function(){rmarkdown::render('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, toc_depth = 2, code_folding = 'hide'))}
+render_this <- function(){rmarkdown::render('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Analyses.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, toc_depth = 2, code_folding = 'hide'))}
 
 options(scipen = 1, digits = 4)
 

### 2018-03-15 code/bootstrap_retest.R

@@ -1,137 +1,0 @@
-#!/usr/bin/env Rscript
-args = commandArgs(trailingOnly=TRUE)
-
-#Usage:
-#Rscript --vanilla bootstrap_retest.R data_dir out_dir n dv_name
-
-#test if all arguments are supplied
-# test if there is at least one argument: if not, return an error
-if (length(args)<3) {
-  stop("Arguments are missing. Usage: Rscript --vanilla bootstrap_retest.R data_dir out_dir n dv_name", call.=FALSE)
-} 
-
-data_dir <- args[1] 
-output_dir <- args[2]
-n <- as.numeric(args[3])
-dv_name <- args[4]
-
-#load packages
-library(dplyr)
-library(tidyr)
-library(psych)
-
-
-#load data
-retest_subs_test_data <- read.csv(paste0(data_dir, 'retest_subs_test_data.csv'))
-retest_data <- read.csv(paste0(data_dir, 'retest_data.csv'))
-
-#bootstrap 1000 times
-
-match_t1_t2 <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', format = "long", sample = 'full', sample_vec){
-
-  if(sample == 'full'){
-    df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var)
-  }
-  else{
-    df = merge(t1_df[t1_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)], t2_df[t2_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)],
-               by=merge_var)
-  }
-
-  df = df %>%
-    na.omit()%>%
-    gather(dv, score, -sub_id) %>%
-    mutate(time = ifelse(grepl('\\.x', dv), 1, ifelse(grepl('\\.y', dv), 2, NA))) %>%
-    separate(dv, c("dv", "drop"), sep='\\.([^.]*)$') %>%
-    select(-drop)
-
-
-  if(format == 'wide'){
-    df = df%>% spread(time, score)
-  }
-
-  return(df)
-}
-
-get_spearman = function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-
-  if(sample=='full'){
[…]

### 2018-03-15 code/ddm_sample_size_processing.R

@@ -1,45 +1,0 @@
-#!/usr/bin/env Rscript
-args = commandArgs(trailingOnly=TRUE)
-
-#Usage:
-#Rscript --vanilla ddm_sample_size_processing.R data_dir out_dir
-
-#test if all arguments are supplied
-# test if there is at least one argument: if not, return an error
-if (length(args)<2) {
-  stop("Arguments are missing. Usage: Rscript --vanilla ddm_sample_size_processing.R data_dir out_dir", call.=FALSE)
-} 
-
-data_dir <- args[1] 
-output_dir <- args[2]
-
-#load packages
-library(dplyr)
-library(tidyr)
-library(psych)
-
-all_ddm_sample_size = read.csv(paste0(data_dir, 'all_ddm_sample_size_estimates.csv'))
-
-all_ddm_sample_size = all_ddm_sample_size %>%
-  drop_na()
-
-all_ddm_sample_size_summary = all_ddm_sample_size %>%
-  mutate(icc = as.numeric(as.character(icc)),
-         spearman = as.numeric(as.character(spearman)),
-         eta_sq = as.numeric(as.character(eta_sq)),
-         sem = as.numeric(as.character(sem))) %>%
-  group_by(dv, N, rep) %>%
-  summarise(icc_median = quantile(icc, probs = 0.5),
-            icc_2.5 = quantile(icc, probs = 0.025),
-            icc_97.5 = quantile(icc, probs = 0.975),
-            spearman_median = quantile(spearman, probs = 0.5),
-            spearman_2.5 = quantile(spearman, probs = 0.025),
-            spearman_97.5 = quantile(spearman, probs = 0.975),
-            eta_median = quantile(spearman, probs = 0.5),
-            eta_2.5 = quantile(spearman, probs = 0.025),
-            eta_97.5 = quantile(spearman, probs = 0.975),
-            sem_median = quantile(spearman, probs = 0.5),
-            sem_2.5 = quantile(spearman, probs = 0.025),
-            sem_97.5 = quantile(spearman, probs = 0.975))
-
-write.csv(all_ddm_sample_size_summary, paste0(output_dir, 'all_ddm_sample_size_summary.csv'), row.names=FALSE)

### 2018-03-15 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 Data collection took place on average `r round(mean(as.numeric(comp_dates$days_btw)))` number of days after the completion of the initial battery with a range of `r round(range(as.numeric(comp_dates$days_btw)))[1]` to `r round(range(as.numeric(comp_dates$days_btw)))[2]` days.
+
+```{r}
+rm(test_comp_date, retest_comp_date, comp_dates)
+```
 
@@
 
+## Completion times
+
+### Subject level
+
+Do people differ in how much their scores change depending on how many days it has been since they completed the initial battery?
+
+Make data frame with difference between two scores for each measure for each subject.
+Since the scores for different measures are on different scales for comparability the difference scores are scaled (i.e.
+divided by their root mean square) but not centered so a value of 0 for the difference scores would indicate a lack of a difference between the scores of a subject.
+
+```{r warning=FALSE}
+numeric_cols = c()
+
+for(i in 1:length(names(test_data))){
+  if(is.numeric(test_data[,i]) & names(test_data)[i] %in% names(retest_data)){
+    numeric_cols <- c(numeric_cols, names(test_data)[i])
+  }
+}
+
+t1_2_difference = data.frame()
+
+for(i in 1:length(numeric_cols)){
+  tmp = match_t1_t2(numeric_cols[i],format='wide')
+  tmp = tmp %>% 
+    # mutate(difference = scale(`2` - `1`))
+  mutate(difference = scale(`2` - `1`, center=F))
+  t1_2_difference = rbind(t1_2_difference, tmp)
+}
+
+t1_2_difference$difference = as.data.frame(t1_2_difference$difference)$V1
+
+t1_2_difference = t1_2_difference %>% separate(dv, c("task", "dv"), sep="\\.")
+```
+
+```{r echo=FALSE}
+rm(tmp, i)
+```
+
+Add completion dates to this data frame.
+
+```{r}
+retest_task_comp_times = read.csv(paste0(retest_data_path, 'Local/retest_task_completion_times.csv'))
+test_task_comp_times = read.csv(paste0(retest_data_path, 'Local/test_task_completion_times.csv'))
+task_comp_times = merge(retest_task_comp_times, test_task_comp_times, by=c('worker_id','task'))
+rm(retest_task_comp_times, test_task_comp_times)
+task_comp_times = task_comp_times %>%
+  select(-X.x, -X.y) %>%
+  mutate(finish_day.x = as.Date(finish_day.x),
+         finish_day.y = as.Date(finish_day.y),
+         days_btw = finish_day.x-finish_day.y) %>%
+  rename(sub_id=worker_id)
+```
+
+```{r warning=FALSE}
+t1_2_difference = merge(t1_2_difference, task_comp_times[,c('sub_id', 'task','days_btw')], by=c('sub_id', 'task'))
+```
+
+```{r echo=FALSE}
+rm(task_comp_times)
+```
+
+The effect of number of days in between in the full model where the difference scores are regressed on a fixed effect for measure and days between the two scores and random intercepts for each subject (*Should this model include the interaction between the fixed effects?*).
+Since there are over 400 measures the output of the full model is not presented here.
+Instead below are the coefficient for the fixed effect of days between completion times and its t value.
+
+```{r}
+mod = lmer(difference ~ dv + scale(days_btw) + (1|sub_id), data = t1_2_difference)
+
+data.frame(estimate=coef(summary(mod))["scale(days_btw)","Estimate"], tval=coef(summary(mod))["scale(days_btw)","t value"])
+```
+
+For visualization purposes I summarized the difference scores per person by looking at the average difference and plot that against the number of days between completion.
+
+```{r warning=FALSE, message=FALSE}
+tmp = t1_2_difference %>%
+  group_by(sub_id, task) %>%
+  summarise(mean_diff = mean(difference, na.rm=T),
+            sem_diff = sem(difference),
+            days_btw = unique(days_btw))
+tmp %>%
+  ggplot(aes(days_btw, mean_diff))+
+  geom_point()+
+  geom_errorbar(aes(ymin = mean_diff-(1.96*sem_diff), ymax = mean_diff+(1.96*sem_diff)))+
+  theme_bw()+
+  xlab("Days between completion")+
+  ylab("Mean standardized difference between two time points")+
+  geom_smooth(method="lm")+
+  theme(legend.position = 'none')
+```
+
+To confirm: the slope of this line is not significant.
+That is, there doesn't seem to be a systematic difference between the two measurements depending on the number of days between the two measurements.
+
+```{r warning=FALSE, message=FALSE}
+summary(lm(mean_diff ~ scale(days_btw), data=tmp))
+```
+
+```{r echo=FALSE}
+rm(tmp)
+```
+
+### Measure level
+
+For each variable does the average difference between two time points vary by the average number of days between the two time points?
+
+The average number of days between two measurements would be the same for all measures with current way of coding the days between completion.
+Even if I were to go in and see if there is a way to figure out the exact day of completion the change would not be more than 7 days since we gave subjects a week to complete.
+
+So if you regress the average difference for each measure on average delay between two measurements you are regressing a vector with varying numbers on a vector of same values, like a t test asking if the mean of the varying column, in this case the average difference score, is different than the unique value in the single value column, i.e.
+the average delay between two time points (Note that this should be true in theory but in practice since for each measure there might subjects for whom the dv could not be calculated there might be >1 unique values for the average delay between the two time points).
+This analysis is not meaningful.
+
+Plus what you would be interested (y) is not exactly the difference between the measurements from two time points but rather the reliability of each measure.
+
 ## Relationship between reliability metrics (point estimates)
@@
 #Create df of point estimate reliabilities
-numeric_cols = c()
-
-for(i in 1:length(names(test_data))){
-  if(is.numeric(test_data[,i]) & names(test_data)[i] %in% names(retest_data)){
-    numeric_cols <- c(numeric_cols, names(test_data)[i])
-  }
-}
-
 rel_df <- data.frame(spearman = rep(NA, length(numeric_cols)),
@@
 
-## Completion times
-
-### Subject level
-
-Do people differ in how much their scores change depending on how many days it has been since they completed the initial battery?
-
-Make data frame with difference between two scores for each measure for each subject.
-Since the scores for different measures are on different scales for comparability the difference scores are scaled (i.e.
-divided by their root mean square) but not centered so a value of 0 for the difference scores would indicate a lack of a difference between the scores of a subject.
-
-```{r warning=FALSE}
-t1_2_difference = data.frame()
-
-for(i in 1:length(numeric_cols)){
-  tmp = match_t1_t2(numeric_cols[i],format='wide')
-  tmp = tmp %>% 
-    # mutate(difference = scale(`2` - `1`))
-  mutate(difference = scale(`2` - `1`, center=F))
-  t1_2_difference = rbind(t1_2_difference, tmp)
-}
-
-t1_2_difference$difference = as.data.frame(t1_2_difference$difference)$V1
-```
-
-```{r echo=FALSE}
-rm(tmp, i)
-```
-
-Add completion dates to this data frame.
-
-```{r warning=FALSE}
-t1_2_difference = merge(t1_2_difference, comp_dates[,c('sub_id', 'days_btw')], by='sub_id')
-```
-
-```{r echo=FALSE}
-rm(test_comp_date, retest_comp_date, comp_dates)
-```
-
-The effect of number of days in between in the full model where the difference scores are regressed on a fixed effect for measure and days between the two scores and random intercepts for each subject (*Should this model include the interaction between the fixed effects?*).
-Since there are over 400 measures the output of the full model is not presented here.
-Instead below are the coefficient for the fixed effect of days between completion times and its t value.
-
-```{r}
-mod = lmer(difference ~ dv + days_btw + (1|sub_id), data = t1_2_difference)
-
-data.frame(estimate=coef(summary(mod))["days_btw","Estimate"], tval=coef(summary(mod))["days_btw","t value"])
-```
-
-For visualization purposes I summarized the difference scores per person by looking at the average difference and plot that against the number of days between completion.
-
-```{r warning=FALSE, message=FALSE}
-tmp = t1_2_difference %>%
-  group_by(sub_id) %>%
-  summarise(mean_diff = mean(difference, na.rm=T),
-            days_btw = unique(days_btw))
-
-tmp %>%
-  ggplot(aes(days_btw, mean_diff))+
-  geom_point()+
-  theme_bw()+
-  xlab("Days between completion")+
-  ylab("Mean standardized difference between two time points")+
-  geom_smooth(method="lm")
-```
-
-To confirm: the slope of this line is not significant.
-That is, there doesn't seem to be a systematic difference between the two measurements depending on the number of days between the two measurements.
-
-```{r warning=FALSE, message=FALSE}
-summary(lm(mean_diff ~ days_btw, data=tmp))
-```
-
-```{r echo=FALSE}
-rm(tmp)
-```
-
-### Task level
-
-For each variable does the average difference between two time points vary by the average number of days between the two time points?
-No.
-The slopes of these lines or the interaction is not significant.
-
-```{r warning=FALSE, message=FALSE}
-t1_2_difference <- t1_2_difference %>%
-  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
-  select(-extra_1, -extra_2) %>% 
-  mutate(task = ifelse(grepl("survey",dv), "survey","task"),
-           task = ifelse(grepl("holt",dv), "task", task))
-
-# summary(lmer(difference ~ days_btw + (task_name|sub_id), t1_2_difference))
-
-t1_2_difference %>%
-  mutate(task = ifelse(grepl("survey",dv), "survey","task"),
-           task = ifelse(grepl("holt",dv), "task", task)) %>%
-  group_by(dv) %>%
-  summarise(mean_diff = mean(difference),
-            mean_days_btw = mean(days_btw),
-            task = unique(task)) %>%
-  ggplot(aes(mean_days_btw, mean_diff, color=task))+
-  geom_point()+
-  theme_bw()+
-  geom_smooth(method="lm")+
-  xlab("Average days between completion")+
-  ylab("Average difference between time points")+
-  theme(legend.title = element_blank())
-```
-
-```{r}
-tmp = t1_2_difference %>%
-  group_by(dv) %>%
-  summarise(mean_diff = mean(difference),
-            mean_days_btw = mean(days_btw),
-            task = unique(task))
-
-summary(lm(mean_diff ~ mean_days_btw*task, tmp))
-```
-
 ## Learning effects

### 2018-03-16 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 
-t1_2_difference = t1_2_difference %>% separate(dv, c("task", "dv"), sep="\\.")
+t1_2_difference = t1_2_difference %>% separate(dv, c("task", "dv2"), sep="\\.", remove=FALSE)
 ```
@@
 
-The effect of number of days in between in the full model where the difference scores are regressed on a fixed effect for measure and days between the two scores and random intercepts for each subject (*Should this model include the interaction between the fixed effects?*).
-Since there are over 400 measures the output of the full model is not presented here.
-Instead below are the coefficient for the fixed effect of days between completion times and its t value.
-
-```{r}
-mod = lmer(difference ~ dv + scale(days_btw) + (1|sub_id), data = t1_2_difference)
-
-data.frame(estimate=coef(summary(mod))["scale(days_btw)","Estimate"], tval=coef(summary(mod))["scale(days_btw)","t value"])
-```
-
-For visualization purposes I summarized the difference scores per person by looking at the average difference and plot that against the number of days between completion.
+What does the distribution of differences look like: The distribution of differences between two time points for each measure
 
 ```{r warning=FALSE, message=FALSE}
-tmp = t1_2_difference %>%
-  group_by(sub_id, task) %>%
-  summarise(mean_diff = mean(difference, na.rm=T),
-            sem_diff = sem(difference),
-            days_btw = unique(days_btw))
-tmp %>%
-  ggplot(aes(days_btw, mean_diff))+
-  geom_point()+
-  geom_errorbar(aes(ymin = mean_diff-(1.96*sem_diff), ymax = mean_diff+(1.96*sem_diff)))+
+t1_2_difference %>%
+  ggplot(aes(difference, alpha=dv))+
+  geom_histogram(position='identity')+
   theme_bw()+
-  xlab("Days between completion")+
-  ylab("Mean standardized difference between two time points")+
-  geom_smooth(method="lm")+
   theme(legend.position = 'none')
@@
 
-To confirm: the slope of this line is not significant.
-That is, there doesn't seem to be a systematic difference between the two measurements depending on the number of days between the two measurements.
-
-```{r warning=FALSE, message=FALSE}
-summary(lm(mean_diff ~ scale(days_btw), data=tmp))
-```
-
-```{r echo=FALSE}
-rm(tmp)
-```
+Are the means of these distributions different than 0? Or more specifically are each of these distributions different than distributions with mean 0 an sd 1?
+When calculating the difference scores I scaled them to have an sd of 1 but did not center them to have a mean of 0.
+So if there is a meaningful difference the mean of the distribution would differ from 0.
+
+```{r}
+diff_from_zero = function(df, samples=100){
+
+  one_diff = function(df){
+    comp_vec = rnorm(nrow(df))
+    test = t.test(df$difference, comp_vec, var.equal = T) #both should have var=1
+    out = data.frame(t_val = test$statistic, df = test$parameter, p_val = test$p.value)
+    out = out %>% mutate(sig = ifelse(p_val < 0.05, 1, 0))
+    return(out)
+  }
+  return(plyr::rdply(samples, one_diff(df)))
+}
+
+diff_from_zero_df = t1_2_difference %>%
+  group_by(dv) %>%
+  do(diff_from_zero(.))
+
+diff_from_zero_summary = diff_from_zero_df %>%
+  summarise(sum_sig=sum(sig)) %>%
+  filter(sum_sig>5) %>% 
+  arrange(sum_sig) %>%
+  mutate(task = ifelse(grepl("survey", dv),"survey","task")) %>%
+  arrange(task) %>%
+  ungroup() %>%
+  group_by(task) %>%
+  summarise(n = n())
+
+diff_from_zero_summary
+```
+
+Chi sq test to see if survey/task has an effect on number of variables with sig difference: It doesn't.
+So comparable proportions of survey and task variables show systematic differences between the two time points (note that this doesn't necessarily whether the performance has improved or not).
+
+```{r}
+sig_survey = (diff_from_zero_summary %>% filter(task=="survey"))$n
+sig_task = (diff_from_zero_summary %>% filter(task=="task"))$n
+chisq.test(data.frame(survey = c(sig_survey, 74-sig_survey), task=c(sig_task, 366-sig_task)))
+```
+
+```{r}
+rm(sig_survey, sig_task, diff_from_zero_summary)
+```
+
+Before I was using subjects as a random effect but days between the two time points for each measure depends on subj id.
+What varies randomly is which dv we are looking for its distribution of differences in relation to the days between the time points.
+So I changed the model to have fixed effect for the days between and a random effect for dependent variable.
+
+```{r}
+summary(lmerTest::lmer(difference ~ scale(days_btw)+(scale(days_btw) | dv), data=t1_2_difference)) 
+```
+
+But if I just run one mixed effects model then we don't get a sense of the simple effects.
+I can run it separately for each dv to see if comparable proportions show a dependence on the delay for surveys and tasks.
+
+```{r}
+get_delay_effect
+
+df = t1_2_difference %>% filter(dv == "adaptive_n_back.EZ_drift")
+
+mod = lm(difference ~ scale(days_btw), data = df)
+
+str(summary(mod))
+mod$coefficients['scale(days_btw)']
+
+data.frame(estimate=coef(summary(mod))["dv","Estimate"], tval=coef(summary(mod))["dv","t value"])
+
+```
+
+For visualization I used to summarize the difference scores per person by looking at the average difference per task per subject and plot that against the number of days between completion.
+This yields multiple points for each value on x representing the average difference per task for each subject.
+But variables within a task could go in different directions (e.g.
+if patient proportion increases discount rate decreases) so this doesn't seem like a good idea)
+
+Instead I now plot all the data coloring by dependant variable.
+
+```{r}
+t1_2_difference %>%
+  ggplot(aes(as.numeric(days_btw), difference,col=dv))+
+  geom_smooth(method='lm', show.legend = FALSE, se=FALSE)+
+  theme(legend.position = 'none')+
+  theme_bw()
+```
+
+Does the delay between the two time points make a difference in how different the performance at each time point is from each other. Is the difference larger depending on the delay
+
+Is a measure less reliable if the average delay between the two time points is larger?
 

### 2018-03-20 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 
-## Completion times
-
-### Subject level
-
-Do people differ in how much their scores change depending on how many days it has been since they completed the initial battery?
+## Effect of delays between the two measurements
+
+Due to our data collection strategy we did not strictly control for the delay between the two measurements as standard psychometrics studies measuring retest reliability might.
+
+An individual difference measure would preferably remain stable regardless of the delay between multiple measurements.
+
+Since we only had two measurements we could not test directly whether a measure becomes less reliable depending on the delay between the two time points (The average number of days between two measurements would be the same for all measures since reliability is a measure level metric while days between completion a subject level one).
+
+So if you regress the average difference for each measure on average delay between two measurements you are regressing a vector with varying numbers on a vector of same values, like a t test asking if the mean of the varying column, in this case the average difference score, is different than the unique value in the single value column, i.e.
+the average delay between two time points (Note that this should be true in theory but in practice since for each measure there might subjects for whom the dv could not be calculated there might be >1 unique values for the average delay between the two time points).
+This analysis is not meaningful.
+
+Instead of the summary metric like the retest reliability estimate for each measure we can check whether the difference score distribution for each measure
 
@@
   tmp = tmp %>% 
-    # mutate(difference = scale(`2` - `1`))
-  mutate(difference = scale(`2` - `1`, center=F))
+  mutate(difference = scale(`2` - `1`))
   t1_2_difference = rbind(t1_2_difference, tmp)
@@
 
-Are the means of these distributions different than 0? Or more specifically are each of these distributions different than distributions with mean 0 an sd 1?
-When calculating the difference scores I scaled them to have an sd of 1 but did not center them to have a mean of 0.
-So if there is a meaningful difference the mean of the distribution would differ from 0.
-
-```{r}
-diff_from_zero = function(df, samples=100){
-
-  one_diff = function(df){
-    comp_vec = rnorm(nrow(df))
-    test = t.test(df$difference, comp_vec, var.equal = T) #both should have var=1
-    out = data.frame(t_val = test$statistic, df = test$parameter, p_val = test$p.value)
-    out = out %>% mutate(sig = ifelse(p_val < 0.05, 1, 0))
+But if I just run one mixed effects model then we don't get a sense of the simple effects (how many of the variables this effect of the days between is significant).
+I can run it separately for each dv to see if comparable proportions show a dependence on the delay for surveys and tasks.
+
+```{r}
+get_delay_effect = function(df){
+  mod = lm(difference ~ scale(days_btw), data = df)
+  out = data.frame(estimate=coef(summary(mod))["scale(days_btw)","Estimate"], pval=coef(summary(mod))["scale(days_btw)","Pr(>|t|)"])
   return(out)
 }
-  return(plyr::rdply(samples, one_diff(df)))
-}
-
-diff_from_zero_df = t1_2_difference %>%
+
+sig_days_effect = t1_2_difference %>%
   group_by(dv) %>%
-  do(diff_from_zero(.))
-
-diff_from_zero_summary = diff_from_zero_df %>%
-  summarise(sum_sig=sum(sig)) %>%
-  filter(sum_sig>5) %>% 
-  arrange(sum_sig) %>%
-  mutate(task = ifelse(grepl("survey", dv),"survey","task")) %>%
-  arrange(task) %>%
-  ungroup() %>%
-  group_by(task) %>%
-  summarise(n = n())
-
-diff_from_zero_summary
-```
-
-Chi sq test to see if survey/task has an effect on number of variables with sig difference: It doesn't.
-So comparable proportions of survey and task variables show systematic differences between the two time points (note that this doesn't necessarily whether the performance has improved or not).
-
-```{r}
-sig_survey = (diff_from_zero_summary %>% filter(task=="survey"))$n
-sig_task = (diff_from_zero_summary %>% filter(task=="task"))$n
-chisq.test(data.frame(survey = c(sig_survey, 74-sig_survey), task=c(sig_task, 366-sig_task)))
-```
-
-```{r}
-rm(sig_survey, sig_task, diff_from_zero_summary)
-```
-
-Before I was using subjects as a random effect but days between the two time points for each measure depends on subj id.
-What varies randomly is which dv we are looking for its distribution of differences in relation to the days between the time points.
-So I changed the model to have fixed effect for the days between and a random effect for dependent variable.
-
-```{r}
-summary(lmerTest::lmer(difference ~ scale(days_btw)+(scale(days_btw) | dv), data=t1_2_difference)) 
-```
-
-But if I just run one mixed effects model then we don't get a sense of the simple effects.
-I can run it separately for each dv to see if comparable proportions show a dependence on the delay for surveys and tasks.
-
-```{r}
-get_delay_effect
-
-df = t1_2_difference %>% filter(dv == "adaptive_n_back.EZ_drift")
-
-mod = lm(difference ~ scale(days_btw), data = df)
-
-str(summary(mod))
-mod$coefficients['scale(days_btw)']
-
-data.frame(estimate=coef(summary(mod))["dv","Estimate"], tval=coef(summary(mod))["dv","t value"])
-
+  do(get_delay_effect(.)) %>%
+  filter(pval<0.05)
+
+sig_days_effect
 ```
@@
 
-Instead I now plot all the data coloring by dependant variable.
+Instead I now plot all the data grouping by dependant variable and coloring depending on whether the difference score distribution for that variable has a significant slope when regressed over days between.
+The black is the main effect for the large multilevel model.
 
@@
 t1_2_difference %>%
-  ggplot(aes(as.numeric(days_btw), difference,col=dv))+
-  geom_smooth(method='lm', show.legend = FALSE, se=FALSE)+
-  theme(legend.position = 'none')+
-  theme_bw()
-```
-
-Does the delay between the two time points make a difference in how different the performance at each time point is from each other. Is the difference larger depending on the delay
-
-Is a measure less reliable if the average delay between the two time points is larger?
-
-### Measure level
-
-For each variable does the average difference between two time points vary by the average number of days between the two time points?
-
-The average number of days between two measurements would be the same for all measures with current way of coding the days between completion.
-Even if I were to go in and see if there is a way to figure out the exact day of completion the change would not be more than 7 days since we gave subjects a week to complete.
-
-So if you regress the average difference for each measure on average delay between two measurements you are regressing a vector with varying numbers on a vector of same values, like a t test asking if the mean of the varying column, in this case the average difference score, is different than the unique value in the single value column, i.e.
-the average delay between two time points (Note that this should be true in theory but in practice since for each measure there might subjects for whom the dv could not be calculated there might be >1 unique values for the average delay between the two time points).
-This analysis is not meaningful.
-
-Plus what you would be interested (y) is not exactly the difference between the measurements from two time points but rather the reliability of each measure.
+  mutate(sig_days_effect = ifelse(dv %in% sig_days_effect$dv, 1, 0))%>%
+  arrange(-sig_days_effect) %>%
+  ggplot()+
+  stat_smooth (aes(as.numeric(days_btw), difference, 
+                  group=factor(dv, levels=unique(dv[order(sig_days_effect)]), ordered=TRUE), 
+                  color=factor(sig_days_effect, levels = c(1,0))),geom="line", alpha=0.5, method='lm')+
+  geom_smooth(aes(as.numeric(days_btw), difference), method='lm', color = "black", se=FALSE)+
+  theme_bw()+
+  theme(legend.title = element_blank())+
+  xlab('Days between completion')+
+  ylab('Scaled difference score')+
+  scale_color_discrete(breaks=c(0,1),
+                       labels=c("NS", "Sig"))
+```
+
+```{r}
+library(ggExtra)
+
+tmp = t1_2_difference %>%
+  filter(dv == "angling_risk_task_always_sunny.keep_adjusted_clicks")
+
+p = ggplot(aes(as.numeric(days_btw), difference), data=tmp)+
+  geom_point()+
+  geom_smooth(method='lm')
+
+ggMarginal(p, type='histogram')
+
+p
+```
+
+```{r}
+rm(sig_survey, sig_task, diff_from_zero_summary)
+```
+
+Before I was using subjects as a random effect but days between the two time points for each measure depends on subj id.
+What varies randomly is which dv we are looking for its distribution of differences in relation to the days between the time points.
+So I changed the model to have fixed effect for the days between, a random slope for (dependent variables can be differentially sensitive to th effect of days between) and a random intercept for dependent variable.
+
+Significant fixed effect suggests that on average the longer the delay the larger the difference.
+
+```{r}
+summary(lmerTest::lmer(log(difference) ~ scale(days_btw)+(scale(days_btw) | dv), data=t1_2_difference %>% filter(dv != 'eating_survey'))) 
+```
 

### 2018-03-20 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 
-Instead of the summary metric like the retest reliability estimate for each measure we can check whether the difference score distribution for each measure
+Instead of the summary metric like the retest reliability estimate for each measure we can check whether the difference score distribution for each measure depends on the delay between the two measurements.
+Since the difference score distribution is at subject level we can check whether the order of subjects in this distribution depends on their order in the distribution of days between completing the two tests.
 
 Make data frame with difference between two scores for each measure for each subject.
-Since the scores for different measures are on different scales for comparability the difference scores are scaled (i.e.
-divided by their root mean square) but not centered so a value of 0 for the difference scores would indicate a lack of a difference between the scores of a subject.
+Since the scores for different measures are on different scales for comparability the difference scores are normalized (ie demeaned and dividied by the sd of the difference score distribution.) Note that the variance of the difference score distribution accounts for the variance in both time points by summing them.
+Normalization equates the means of each difference score distribution to 0 which would mask any meaningful change between the two time points but the analysis here does not interpret the mean of the difference score distributions but is interested in its relation to the days between completion.
+We check if the variables show systematic differences between the two points later and can investigate whether
+
+Here we check if the difference is larger the longer the delay
+What is the threshold for a meaningful difference between the two points for each variable? 
+For standardized difference scores does it cross 2 on the y axis?
 
@@
 
-But if I just run one mixed effects model then we don't get a sense of the simple effects (how many of the variables this effect of the days between is significant).
-I can run it separately for each dv to see if comparable proportions show a dependence on the delay for surveys and tasks.
+How do the difference score distributions look like with respect to the days between completion?
+
+```{r}
+t1_2_difference %>%
+  ggplot()+
+  geom_smooth(aes(as.numeric(days_btw), abs(difference), group=factor(dv)), method='lm', se=FALSE)+
+  geom_smooth(aes(as.numeric(days_btw), abs(difference)), method='lm', color = "black", se=FALSE)+
+  theme_bw()+
+  theme(legend.title = element_blank())+
+  xlab('Days between completion')+
+  ylab('Absolute Scaled difference score')
+
+```
+
+To test if the slope of the black is significant we would run a mixed effects model with a fixed effect for days between completion, random slope for each dv depending on the days between and random intercept for each dv.
+
+Before I was using subjects as a random effect but days between the two time points for each measure depends on subj id.
+What varies randomly is which dv we are looking for its distribution of differences in relation to the days between the time points.
+So I changed the model to have fixed effect for the days between, a random slope for (dependent variables can be differentially sensitive to th effect of days between) and a random intercept for dependent variable.
+
+Significant fixed effect suggests that on average the longer the delay the smaller the difference.
+
+```{r}
+summary(lmerTest::lmer(abs(difference) ~ scale(days_btw)+(scale(days_btw) | dv), data=t1_2_difference)) 
+```
+
+But if I just run one mixed effects model then we don't get a sense of the simple effects (how many of the variables this effect of the days between is significant and in which direction).
+I can run it separately for each dv to see if all difference score distributions are affected the same way depending on the days between completion.
 
@@
 get_delay_effect = function(df){
-  mod = lm(difference ~ scale(days_btw), data = df)
+  mod = lm(abs(difference) ~ scale(days_btw), data = df)
   out = data.frame(estimate=coef(summary(mod))["scale(days_btw)","Estimate"], pval=coef(summary(mod))["scale(days_btw)","Pr(>|t|)"])
@@
 Instead I now plot all the data grouping by dependant variable and coloring depending on whether the difference score distribution for that variable has a significant slope when regressed over days between.
-The black is the main effect for the large multilevel model.
+The black is the main effect for the large multilevel model (this is the same plot as above colored by whether the difference score distribution for each dv has a significant slope depending on days between).
 
@@
   ggplot()+
-  stat_smooth (aes(as.numeric(days_btw), difference, 
+  stat_smooth (aes(as.numeric(days_btw), abs(difference), 
                   group=factor(dv, levels=unique(dv[order(sig_days_effect)]), ordered=TRUE), 
                   color=factor(sig_days_effect, levels = c(1,0))),geom="line", alpha=0.5, method='lm')+
-  geom_smooth(aes(as.numeric(days_btw), difference), method='lm', color = "black", se=FALSE)+
+  geom_smooth(aes(as.numeric(days_btw), abs(difference)), method='lm', color = "black", se=FALSE)+
   theme_bw()+
@@
 
-```{r}
-library(ggExtra)
-
-tmp = t1_2_difference %>%
-  filter(dv == "angling_risk_task_always_sunny.keep_adjusted_clicks")
-
-p = ggplot(aes(as.numeric(days_btw), difference), data=tmp)+
+Conclusion: The average difference between the scores of a measure if anything decreases with the increased delay.
+This fixed effect masks the simple effect for each dv.
+When looked at individually only 10 variables show a dependence on days between completion.
+While 7 of them show decreasing differences depending on days between 3 do show increasing differences.
+This suggests that the lack of stricter control over the days between completion of the measurement does not have a large effect on the stability of most measures.
+
+effect of whether days between leads to a sig difference on reliability of that variable? plot coef of sig_day_effect over rel_df point estimate
+
+```{r}
+#Create df of point estimate reliabilities
+rel_df <- data.frame(spearman = rep(NA, length(numeric_cols)),
+                     icc = rep(NA, length(numeric_cols)),
+                     pearson = rep(NA, length(numeric_cols)),
+                     partial_eta_sq = rep(NA, length(numeric_cols)),
+                     sem = rep(NA, length(numeric_cols)),
+                     var_subs = rep(NA, length(numeric_cols)),
+                     var_ind = rep(NA, length(numeric_cols)),
+                     var_resid = rep(NA, length(numeric_cols)))
+
+row.names(rel_df) <- numeric_cols
+
+for(i in 1:length(numeric_cols)){
+  rel_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i]) 
+  rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
+  rel_df[numeric_cols[i], 'pearson'] <- get_pearson(numeric_cols[i])
+  rel_df[numeric_cols[i], 'partial_eta_sq'] <- get_partial_eta(numeric_cols[i])
+  rel_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
+  rel_df[numeric_cols[i], 'var_subs'] <- get_var_breakdown(numeric_cols[i])$subs
+  rel_df[numeric_cols[i], 'var_ind'] <- get_var_breakdown(numeric_cols[i])$ind
+  rel_df[numeric_cols[i], 'var_resid'] <- get_var_breakdown(numeric_cols[i])$resid
+}
+
+rel_df$dv = row.names(rel_df)
+row.names(rel_df) = seq(1:nrow(rel_df))
+rel_df$task = 'task'
+rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
+rel_df[grep('holt', rel_df$dv), 'task'] = "task"
+rel_df = rel_df %>%
+  select(dv, task, spearman, icc, pearson, partial_eta_sq, sem, var_subs, var_ind, var_resid)
+# row.names(rel_df) = NULL
+```
+
+```{r}
+sig_days_effect %>%
+  left_join(rel_df, by='dv') %>%
+  ggplot(aes(estimate, icc))+
   geom_point()+
-  geom_smooth(method='lm')
-
-ggMarginal(p, type='histogram')
-
-p
-```
-
-```{r}
-rm(sig_survey, sig_task, diff_from_zero_summary)
-```
-
-Before I was using subjects as a random effect but days between the two time points for each measure depends on subj id.
-What varies randomly is which dv we are looking for its distribution of differences in relation to the days between the time points.
-So I changed the model to have fixed effect for the days between, a random slope for (dependent variables can be differentially sensitive to th effect of days between) and a random intercept for dependent variable.
-
-Significant fixed effect suggests that on average the longer the delay the larger the difference.
-
-```{r}
-summary(lmerTest::lmer(log(difference) ~ scale(days_btw)+(scale(days_btw) | dv), data=t1_2_difference %>% filter(dv != 'eating_survey'))) 
+  theme_bw()
+```
+
+## Comparison to prior literature
+
+```{r}
+var_boot_df = boot_df %>%
+  group_by(dv) %>%
+  summarise(icc_median = quantile(icc, probs = 0.5),
+            icc_2.5 = quantile(icc, probs = 0.025),
+            icc_97.5 = quantile(icc, probs = 0.975)
+            )
+
+boot_lit_rel = function(df, samples = 100, rel_col = 'retest_reliability'){
+
+  boot_once = function(df){
+    #get number of rows in df
+    data_amount = nrow(df)
+    #sample as many reliability estimates as there are rows in the df
+    boot_sample = sample(c(1:data_amount), size=data_amount, replace=TRUE)
+    boot_sample = df[boot_sample,]
+    #calculate median reliability estimate for the sampled estimates
+    return(median(boot_sample[,rel_col])) 
+  }
+
+  out = replicate(samples, boot_once(df))
+
+  return(data.frame(median_lit_rel=out))
+}
+
+var_lit_review = lit_review %>%
+  group_by(dv)%>%
+  do(boot_lit_rel(.))
+  summarise(median_reliability=median(retest_reliability),
+            task = unique(task)) %>%
+  mutate(dv = as.character(dv))
+
+var_boot_df = boot_df %>%
+  group_by(dv) %>%
+  summarise(median_icc = quantile(icc, probs = 0.5))
+
+var_lit_review = lit_review %>%
+  # filter(sample_size > 100) %>%
+  group_by(dv)%>%
+  summarise(median_reliability=median(retest_reliability),
+            task = unique(task),
+            mean_sample = mean(sample_size)) %>%
+  mutate(dv = as.character(dv))
+
+rel_comp = var_lit_review %>%
+  left_join(var_boot_df, by = 'dv')
+
+rel_comp
+```
+
+Correlation between our median estimates from bootstrapped samples and the literature review for task variables
+```{r}
+with(rel_comp %>% filter(task == "task"), cor(median_icc, median_reliability))
+```
+
+```{r}
+with(rel_comp %>% filter(task == "survey"), cor(median_icc, median_reliability))
+```
+
+Potential problems in this graph: 
+- not all metrics are ICC's
+- difference in delay between completion of two tests (does it make a difference in the lit review?)
+
+```{r}
+rel_comp %>%
+  ggplot(aes(median_reliability, median_icc, color=task))+
+  geom_point()+
+  geom_abline(slope=1, intercept=0)+
+  theme_bw()+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  theme(legend.title = element_blank())+
+  xlab('Median reliability from literature')+
+  ylab('Median ICC from bootstrapped samples')
+```
+
+```{r}
+lit_review %>%
+  ggplot(aes(sample_size, retest_reliability, color=task))+
+  geom_point()
+summary(lmer(retest_reliability~sample_size+task+(1|dv), data=lit_review))
+
+#sd by average sample size
+lit_review %>%
+  group_by(dv) %>%
+  summarise(sd_rel = sd(retest_reliability),
+            avg_sample_size = mean(sample_size)) %>%
+  ggplot(aes(avg_sample_size, sd_rel))+
+  geom_point()+
+  xlim(0,200)
+```
+
+x = deviance between our data and literature
+y = average sample size
+
+```{r}
+rel_comp %>%
+  mutate(diff_sq = (median_icc - median_reliability)^2) %>%
+  ggplot(aes(diff_sq, mean_sample, color=task))+
+  geom_point()+
+  geom_smooth()
+```
+
+```{r}
+lit_review %>%
+  ggplot(aes(sample_size))+
+  geom_histogram()+
+  theme_bw()
 ```
@@
 "quantifies the precision of individual scores on a test" and is not dependent on the sample in the way ICC is since it doesn't depend on between subject reliability (at least in this formulation) but is unit-dependent.
-
-```{r}
-#Create df of point estimate reliabilities
-rel_df <- data.frame(spearman = rep(NA, length(numeric_cols)),
-                     icc = rep(NA, length(numeric_cols)),
-                     pearson = rep(NA, length(numeric_cols)),
-                     partial_eta_sq = rep(NA, length(numeric_cols)),
-                     sem = rep(NA, length(numeric_cols)),
-                     var_subs = rep(NA, length(numeric_cols)),
-                     var_ind = rep(NA, length(numeric_cols)),
-                     var_resid = rep(NA, length(numeric_cols)))
-
-row.names(rel_df) <- numeric_cols
-
-for(i in 1:length(numeric_cols)){
-  rel_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i]) 
-  rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
-  rel_df[numeric_cols[i], 'pearson'] <- get_pearson(numeric_cols[i])
-  rel_df[numeric_cols[i], 'partial_eta_sq'] <- get_partial_eta(numeric_cols[i])
-  rel_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
-  rel_df[numeric_cols[i], 'var_subs'] <- get_var_breakdown(numeric_cols[i])$subs
-  rel_df[numeric_cols[i], 'var_ind'] <- get_var_breakdown(numeric_cols[i])$ind
-  rel_df[numeric_cols[i], 'var_resid'] <- get_var_breakdown(numeric_cols[i])$resid
-}
-
-rel_df$dv = row.names(rel_df)
-row.names(rel_df) = seq(1:nrow(rel_df))
-rel_df$task = 'task'
-rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
-rel_df[grep('holt', rel_df$dv), 'task'] = "task"
-rel_df = rel_df %>%
-  select(dv, task, spearman, icc, pearson, partial_eta_sq, sem, var_subs, var_ind, var_resid)
-# row.names(rel_df) = NULL
-```
 
@@
 ```
-
-## Comparison to prior literature
-
-```{r}
-var_boot_df = boot_df %>%
-  group_by(dv) %>%
-  summarise(icc_median = quantile(icc, probs = 0.5),
-            icc_2.5 = quantile(icc, probs = 0.025),
-            icc_97.5 = quantile(icc, probs = 0.975)
-            )
-
-boot_lit_rel = function(df, samples = 100, rel_col = 'retest_reliability'){
-
-  boot_once = function(df){
-    #get number of rows in df
-    data_amount = nrow(df)
-    #sample as many reliability estimates as there are rows in the df
-    boot_sample = sample(c(1:data_amount), size=data_amount, replace=TRUE)
-    boot_sample = df[boot_sample,]
-    #calculate median reliability estimate for the sampled estimates
-    return(median(boot_sample[,rel_col])) 
-  }
-
-  out = replicate(samples, boot_once(df))
-
-  return(data.frame(median_lit_rel=out))
-}
-
-var_lit_review = lit_review %>%
-  group_by(dv)%>%
-  do(boot_lit_rel(.))
-  summarise(median_reliability=median(retest_reliability),
-            task = unique(task)) %>%
-  mutate(dv = as.character(dv))
-
-var_boot_df = boot_df %>%
-  group_by(dv) %>%
-  summarise(median_icc = quantile(icc, probs = 0.5))
-
-var_lit_review = lit_review %>%
-  # filter(sample_size > 100) %>%
-  group_by(dv)%>%
-  summarise(median_reliability=median(retest_reliability),
-            task = unique(task),
-            mean_sample = mean(sample_size)) %>%
-  mutate(dv = as.character(dv))
-
-rel_comp = var_lit_review %>%
-  left_join(var_boot_df, by = 'dv')
-
-rel_comp
-```
-
-Correlation between our median estimates from bootstrapped samples and the literature review for task variables
-```{r}
-with(rel_comp %>% filter(task == "task"), cor(median_icc, median_reliability))
-```
-
-```{r}
-with(rel_comp %>% filter(task == "survey"), cor(median_icc, median_reliability))
-```
-
-Potential problems in this graph: 
-- not all metrics are ICC's
-- difference in delay between completion of two tests (does it make a difference in the lit review?)
-
-```{r}
-rel_comp %>%
-  ggplot(aes(median_reliability, median_icc, color=task))+
-  geom_point()+
-  geom_abline(slope=1, intercept=0)+
-  theme_bw()+
-  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
-  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
-  theme(legend.title = element_blank())+
-  xlab('Median reliability from literature')+
-  ylab('Median ICC from bootstrapped samples')
-```
-
-```{r}
-lit_review %>%
-  ggplot(aes(sample_size, retest_reliability, color=task))+
-  geom_point()
-summary(lmer(retest_reliability~sample_size+task+(1|dv), data=lit_review))
-
-#sd by average sample size
-lit_review %>%
-  group_by(dv) %>%
-  summarise(sd_rel = sd(retest_reliability),
-            avg_sample_size = mean(sample_size)) %>%
-  ggplot(aes(avg_sample_size, sd_rel))+
-  geom_point()+
-  xlim(0,200)
-```
-
-x = deviance between our data and literature
-y = average sample size
-
-```{r}
-rel_comp %>%
-  mutate(diff_sq = (median_icc - median_reliability)^2) %>%
-  ggplot(aes(diff_sq, mean_sample, color=task))+
-  geom_point()+
-  geom_smooth()
-```
-
-```{r}
-lit_review %>%
-  ggplot(aes(sample_size))+
-  geom_histogram()+
-  theme_bw()
-```

### 2018-03-21 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Analyses_Helper_Functions.R')
+theme_set(theme_bw())
 
@@
   geom_point(aes(size=sample_size, shape = type), color='black')+
-  theme_bw()+
   theme(axis.text.y = element_text(size=43),
@@
   geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
-  theme_bw()+
   theme(axis.text.y = element_text(size=43),
@@
   geom_point(aes(size=sample_size, shape = type), color='#F8766D')+
-  theme_bw()+
   theme(axis.text.y = element_text(size=43),
@@
   geom_histogram(position='identity')+
-  theme_bw()+
   theme(legend.position = 'none')
@@
   geom_smooth(aes(as.numeric(days_btw), abs(difference)), method='lm', color = "black", se=FALSE)+
-  theme_bw()+
   theme(legend.title = element_blank())+
@@
   ggplot(aes(estimate, icc))+
-  geom_point()+
-  theme_bw()
-```
+  geom_point()
+```
+
+`Plot differences for the measures with differences as examples`
 
@@
 
-```{r}
-var_boot_df = boot_df %>%
-  group_by(dv) %>%
-  summarise(icc_median = quantile(icc, probs = 0.5),
-            icc_2.5 = quantile(icc, probs = 0.025),
-            icc_97.5 = quantile(icc, probs = 0.975)
-            )
-
-boot_lit_rel = function(df, samples = 100, rel_col = 'retest_reliability'){
-
-  boot_once = function(df){
-    #get number of rows in df
-    data_amount = nrow(df)
-    #sample as many reliability estimates as there are rows in the df
-    boot_sample = sample(c(1:data_amount), size=data_amount, replace=TRUE)
-    boot_sample = df[boot_sample,]
-    #calculate median reliability estimate for the sampled estimates
-    return(median(boot_sample[,rel_col])) 
-  }
-
-  out = replicate(samples, boot_once(df))
-
-  return(data.frame(median_lit_rel=out))
-}
-
-var_lit_review = lit_review %>%
-  group_by(dv)%>%
-  do(boot_lit_rel(.))
-  summarise(median_reliability=median(retest_reliability),
-            task = unique(task)) %>%
-  mutate(dv = as.character(dv))
-
-var_boot_df = boot_df %>%
-  group_by(dv) %>%
-  summarise(median_icc = quantile(icc, probs = 0.5))
-
-var_lit_review = lit_review %>%
-  # filter(sample_size > 100) %>%
-  group_by(dv)%>%
-  summarise(median_reliability=median(retest_reliability),
-            task = unique(task),
-            mean_sample = mean(sample_size)) %>%
-  mutate(dv = as.character(dv))
-
-rel_comp = var_lit_review %>%
-  left_join(var_boot_df, by = 'dv')
-
-rel_comp
-```
-
-Correlation between our median estimates from bootstrapped samples and the literature review for task variables
-```{r}
-with(rel_comp %>% filter(task == "task"), cor(median_icc, median_reliability))
-```
-
-```{r}
-with(rel_comp %>% filter(task == "survey"), cor(median_icc, median_reliability))
-```
-
-Potential problems in this graph: 
-- not all metrics are ICC's
-- difference in delay between completion of two tests (does it make a difference in the lit review?)
-
-```{r}
-rel_comp %>%
-  ggplot(aes(median_reliability, median_icc, color=task))+
-  geom_point()+
-  geom_abline(slope=1, intercept=0)+
-  theme_bw()+
-  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
-  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
-  theme(legend.title = element_blank())+
-  xlab('Median reliability from literature')+
-  ylab('Median ICC from bootstrapped samples')
-```
-
-```{r}
-lit_review %>%
-  ggplot(aes(sample_size, retest_reliability, color=task))+
-  geom_point()
-summary(lmer(retest_reliability~sample_size+task+(1|dv), data=lit_review))
-
-#sd by average sample size
-lit_review %>%
-  group_by(dv) %>%
-  summarise(sd_rel = sd(retest_reliability),
-            avg_sample_size = mean(sample_size)) %>%
-  ggplot(aes(avg_sample_size, sd_rel))+
-  geom_point()+
-  xlim(0,200)
-```
-
-x = deviance between our data and literature
-y = average sample size
-
-```{r}
-rel_comp %>%
-  mutate(diff_sq = (median_icc - median_reliability)^2) %>%
-  ggplot(aes(diff_sq, mean_sample, color=task))+
-  geom_point()+
-  geom_smooth()
-```
-
-```{r}
-lit_review %>%
-  ggplot(aes(sample_size))+
-  geom_histogram()+
-  theme_bw()
-```
-
-## Relationship between reliability metrics (point estimates)
-
-Based on [Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) ICC(3,k) does not take in to account within subject differences between two time points (i.e.
-the fixed effect of time/systematic error).
-Thus, it is well approximated by Pearson's r and subject to similar criticisms.
-[Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) suggests reporting at least this systematic error effect size if one chooses to report with ICC(3,k).
-Based on his conclusions here I report:
-- ICC(3,k): As Dave clarified this ranges from 1 to -1/(number of repeated measures -1) so in our case this range would be [-1, 1]; larger values would mean that the two scores of a subject for a given measure are more similar to each other than they are to scores of other people
-- "ICC is reflective of the ability of a test to differentiate between different individuals"
-- partial $\eta^2$ for time ($SS_{time}/SS_{within}$): effect size of time   
-- SEM ($\sqrt(MS_{error})$): standard error of measurement; the smaller the better. It 
-"quantifies the precision of individual scores on a test" and is not dependent on the sample in the way ICC is since it doesn't depend on between subject reliability (at least in this formulation) but is unit-dependent.
-
-We calculated `r as.numeric(table(rel_df$task)[1])` measures for surveys and `r as.numeric(table(rel_df$task)[2])` measures for cognitive tasks.
-
-Though we are primarily reporting ICC's as our metric of reliability the results don't change depending on the metric chosen.
-Here we plot point estimates of three different reliability metrics against each other (ICC, Pearson, Spearman).
-The bootstrapped version is essentially the same but the plots are busier due to more datapoints.
-
-```{r warning=FALSE, message=FALSE}
-p1 = rel_df %>%
-  ggplot(aes(spearman, icc, col=task))+
-  geom_point()+
-  theme_bw()+
-  theme(legend.title = element_blank(),
-        legend.position = "none")+
-  geom_abline(intercept = 0, slope=1)
-
-p2 = rel_df %>%
-  ggplot(aes(pearson, icc, col=task))+
-  geom_point()+
-  theme_bw()+
-  theme(legend.title = element_blank(),
-        legend.position = "none")+
-  geom_abline(intercept = 0, slope=1)
-
-p3 = rel_df %>%
-  ggplot(aes(pearson, spearman, col=task))+
-  geom_point()+
-  theme_bw()+
-  theme(legend.title = element_blank(),
-        legend.position = "none")+
-  geom_abline(intercept = 0, slope=1)
-
-grid.arrange(p1, p2, p3, nrow=1)
-
-ggsave('Metric_Scatterplots.jpg', plot = grid.arrange(p1, p2, p3, nrow=1), device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE, dpi = 100)
-```
-
-As the scatter plots depict the correlations between different types reliability metrics were very high.
-
-```{r}
-cor(rel_df[,c('spearman', 'icc', 'pearson')])
-```
-
-```{r echo=FALSE}
-rm(p1,p2,p3)
-```
-
-Note: Some variables have <0 ICC's. This would be the case if the $MS_{error}$>$MS_{between}$. Data for these variables have no relationship between the two time points.
-
-## Summary of all measure reliabilities
-
-Summarized bootstrapped reliabilities
+Read in and process bootstrapped results.
 
@@
   return(df)}
-```
-
-```{r message=FALSE, warning=FALSE}
+
 boot_df <- read.csv(gzfile(paste0(retest_data_path,'bootstrap_merged.csv.gz')))
@@
 rm(refit_boot_df)
+```
+
+Summarize bootstrapped results and merge to lit review data
+
+```{r}
+var_boot_df = boot_df %>%
+  group_by(dv) %>%
+  summarise(mean_icc = mean(icc))
+
+rel_comp = lit_review %>%
+  left_join(var_boot_df, by = 'dv')
+```
+
+Here's what our data looks like: (583 data points for 171 measures)
+
+```{r}
+rel_comp
+```
+
+### Lit review results
+
+Distribution of reliabilities, sample sizes and delays
+
+```{r}
+rel_comp %>% 
+  select(dv, task, retest_reliability, sample_size, days) %>%
+  filter(days < 3600) %>%
+  gather(key, value, -dv, -task) %>%
+  ggplot(aes(value, fill=task))+
+  geom_density(alpha=0.5, position='identity')+
+  facet_wrap(~key, scales='free')+
+  theme(legend.title = element_blank())
+```
+
+What predicts retest reliability in the literature?
+Task, sample size, days
+
+```{r}
+mod1 = lmer(retest_reliability ~ task + (1|dv), rel_comp)
+mod2 = lmer(retest_reliability ~ task + sample_size + (1|dv), rel_comp)
+
+anova(mod1, mod2)
+```
+
+```{r}
+mod3 = lmer(retest_reliability ~ task + sample_size + days+ (1|dv), rel_comp)
+
+anova(mod2, mod3)
+```
+
+```{r}
+summary(mod2)
+```
+
+```{r}
+rel_comp %>% 
+  ggplot(aes(sample_size, retest_reliability, color=task))+
+  geom_smooth(method='lm')+
+  geom_point(alpha = 0.2)+
+  theme(legend.title = element_blank())+
+  xlab("Sample Size")+
+  ylab("Retest reliability")
+```
+
+Compare effect sizes of effect of task on reliability estimates in literature vs our results (just looking at the variables you find in the literature)
+
+### Conceptual replications 
+- Larger reliability estimates for surveys
+- Larger variance in reliability estimates for tasks
+
+### Sample size effects/publication bias
+
+Deviance between our mean estimate and the reliability from the literature decreases exponentially with sample size.
+The smaller the sample size in the literature the more the reliability estimate differs from our results.
+
+```{r}
+rel_comp = rel_comp %>%
+  mutate(diff_sq = abs(mean_icc - retest_reliability)^2)
+
+rel_comp %>%
+  ggplot(aes(sample_size,diff_sq, color=task))+
+  # geom_point()+
+  #exponential decay (linearized by taking logs of both sides)
+  geom_smooth(method="glm",se=FALSE, method.args=list(family=gaussian(link="log")))+
+  theme_bw()
+```
+
+```{r}
+lit_review %>%
+  ggplot(aes(sample_size, retest_reliability, color=task))+
+  geom_smooth(method='lm')
+
+mod1 = lmer(retest_reliability~sample_size+(1|dv), data=lit_review)
+
+```
+
+```{r}
+#sd by average sample size
+lit_review %>%
+  group_by(dv) %>%
+  summarise(sd_rel = sd(retest_reliability),
+            avg_sample_size = mean(sample_size)) %>%
+  ggplot(aes(avg_sample_size, sd_rel))+
+  geom_point()+
+  xlim(0,200)
+```
+
+### Direct relation to our results
+
+Correlation between our mean estimates from bootstrapped samples and the literature review for task variables
+
+```{r}
+with(rel_comp %>% filter(task == "task"), cor(mean_icc, mean_reliability))
+```
+
+```{r}
+with(rel_comp %>% filter(task == "survey"), cor(mean_icc, mean_reliability))
+```
+
+Model comparisons building model to predict the reliabilities in the literature from our results.
+
+```{r}
+mod1 = lmer(retest_reliability ~ mean_icc + (1|dv), data=rel_comp)
+mod2 = lmer(retest_reliability ~ mean_icc + (mean_icc|dv), data=rel_comp)
+
+anova(mod1, mod2)
+```
+
+```{r}
+mod3 = lmer(retest_reliability ~ mean_icc + scale(sample_size) + (mean_icc|dv), data=rel_comp)
+
+anova(mod2, mod3)
+```
+
+```{r}
+mod4 = lmer(retest_reliability ~ mean_icc + scale(days) + scale(sample_size) + (mean_icc|dv), data=rel_comp)
+
+anova(mod3, mod4)
+```
+
+Selected model: fixed effect for mean icc and sample size of study, random slope with respect to mean icc and random intercept for each measure
+
+What does it say?
+
+```{r}
+summary(mod3)
+```
+
+How well does the model fit? (squared correlation between predictions of model and data)
+
+```{r}
+cor(predict(mod3), rel_comp$retest_reliability)^2
+```
+
+Same result if you do flat model without random slopes for dv's
+
+```{r}
+summary(lm(retest_reliability ~ mean_icc+scale(sample_size), data=rel_comp))
+```
+
+Visualize hierarchical model:
+How would I show random intercepts/slopes? Does the fact that I can't think of how means that there is something wrong with the model?
+
+```{r}
+rel_comp %>%
+  ggplot()+  
+  geom_boxplot(aes(mean_icc, retest_reliability, group=dv))+
+  geom_smooth(aes(mean_icc, retest_reliability), method= 'lm')+
+  theme_bw()+
+  theme(legend.position = 'none')+
+  geom_abline(slope=1, intercept=0)+
+  # geom_abline(slope=0, intercept=0.3, linetype='dashed')+
+  xlim(-0.2, 1)+
+  ylim(-0.2, 1)+
+  facet_grid(task~.)+
+  xlab('Mean bootstrapped ICC')+
+  ylab('Reliability estimate from literature')
+
+```
+
+Potential problems in this graph: 
+- not all metrics are ICC's
+- difference in delay between completion of two tests (does it make a difference in the lit review?)
+
+## Relationship between reliability metrics (point estimates)
+
+Based on [Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) ICC(3,k) does not take in to account within subject differences between two time points (i.e.
+the fixed effect of time/systematic error).
+Thus, it is well approximated by Pearson's r and subject to similar criticisms.
+[Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) suggests reporting at least this systematic error effect size if one chooses to report with ICC(3,k).
+Based on his conclusions here I report:
+- ICC(3,k): As Dave clarified this ranges from 1 to -1/(number of repeated measures -1) so in our case this range would be [-1, 1]; larger values would mean that the two scores of a subject for a given measure are more similar to each other than they are to scores of other people
+- "ICC is reflective of the ability of a test to differentiate between different individuals"
+- partial $\eta^2$ for time ($SS_{time}/SS_{within}$): effect size of time   
+- SEM ($\sqrt(MS_{error})$): standard error of measurement; the smaller the better. It 
+"quantifies the precision of individual scores on a test" and is not dependent on the sample in the way ICC is since it doesn't depend on between subject reliability (at least in this formulation) but is unit-dependent.
+
+We calculated `r as.numeric(table(rel_df$task)[1])` measures for surveys and `r as.numeric(table(rel_df$task)[2])` measures for cognitive tasks.
+
+Though we are primarily reporting ICC's as our metric of reliability the results don't change depending on the metric chosen.
+Here we plot point estimates of three different reliability metrics against each other (ICC, Pearson, Spearman).
+The bootstrapped version is essentially the same but the plots are busier due to more datapoints.
+
+```{r warning=FALSE, message=FALSE}
+p1 = rel_df %>%
+  ggplot(aes(spearman, icc, col=task))+
+  geom_point()+
+  theme_bw()+
+  theme(legend.title = element_blank(),
+        legend.position = "none")+
+  geom_abline(intercept = 0, slope=1)
+
+p2 = rel_df %>%
+  ggplot(aes(pearson, icc, col=task))+
+  geom_point()+
+  theme_bw()+
+  theme(legend.title = element_blank(),
+        legend.position = "none")+
+  geom_abline(intercept = 0, slope=1)
+
+p3 = rel_df %>%
+  ggplot(aes(pearson, spearman, col=task))+
+  geom_point()+
+  theme_bw()+
+  theme(legend.title = element_blank(),
+        legend.position = "none")+
+  geom_abline(intercept = 0, slope=1)
+
+grid.arrange(p1, p2, p3, nrow=1)
+
+ggsave('Metric_Scatterplots.jpg', plot = grid.arrange(p1, p2, p3, nrow=1), device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE, dpi = 100)
+```
+
+As the scatter plots depict the correlations between different types reliability metrics were very high.
+
+```{r}
+cor(rel_df[,c('spearman', 'icc', 'pearson')])
+```
+
+```{r echo=FALSE}
+rm(p1,p2,p3)
+```
+
+Note: Some variables have <0 ICC's. This would be the case if the $MS_{error}$>$MS_{between}$. Data for these variables have no relationship between the two time points.
+
+## Summary of all measure reliabilities
+
+Summarized bootstrapped reliabilities
+
+```{r message=FALSE, warning=FALSE}
 

### 2018-03-21 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 
+Tasks have significantly lower reliability and reliability decreases with increasing sample size.
+
 ```{r}
@@
 
-Compare effect sizes of effect of task on reliability estimates in literature vs our results (just looking at the variables you find in the literature)
-
-### Conceptual replications 
-- Larger reliability estimates for surveys
-- Larger variance in reliability estimates for tasks
-
-### Sample size effects/publication bias
-
-Deviance between our mean estimate and the reliability from the literature decreases exponentially with sample size.
+Conceptual replication 1: Compare effect sizes of effect of task on reliability estimates in literature vs our results (just looking at the variables you find in the literature)
+
+```{r}
+m1 = rel_comp %>% filter(task == "task") %>% summarise(m1 = mean(retest_reliability))
+m2 = rel_comp %>% filter(task == "survey") %>% summarise(m2 = mean(retest_reliability))
+n1 = nrow(rel_comp %>% filter(task == "task"))
+n2 = nrow(rel_comp %>% filter(task == "survey"))
+var1 = rel_comp %>% filter(task == "task") %>% summarise(var1 = var(retest_reliability))
+var2 = rel_comp %>% filter(task == "survey") %>% summarise(var1 = var(retest_reliability))
+sd_pooled = sqrt(((n1-1)*var1+(n2-1)*var2)/(n1+n2-2))
+d_lit = abs(m1-m2)/sd_pooled
+d_lit
+```
+
+The literature review conceptually replicates our finding of lower reliability estimates for task measures but with a much smaller effect size.
+
+```{r}
+n_df = rel_comp %>% 
+  group_by(dv) %>%
+  tally()
+
+boot_comp = data.frame()
+
+for(i in 1:length(unique(rel_comp$dv)) ){
+  cur_dv = unique(rel_comp$dv)[i]
+  n = n_df$n[n_df$dv == cur_dv]
+  sample_df = boot_df %>% filter(dv == cur_dv)
+  tmp = sample_n(sample_df, n)
+  boot_comp = rbind(boot_comp, tmp)
+}
+
+rm(cur_dv, n, sample_df, tmp)
+
+boot_comp = boot_comp %>%
+  mutate(task=ifelse(grepl("survey", dv), "task", "survey"))
+
+m1 = boot_comp %>% filter(task == "task") %>% summarise(m1 = mean(icc))
+m2 = boot_comp %>% filter(task == "survey") %>% summarise(m2 = mean(icc))
+n1 = nrow(boot_comp %>% filter(task == "task"))
+n2 = nrow(boot_comp %>% filter(task == "survey"))
+var1 = boot_comp %>% filter(task == "task") %>% summarise(var1 = var(icc))
+var2 = boot_comp %>% filter(task == "survey") %>% summarise(var1 = var(icc))
+sd_pooled = sqrt(((n1-1)*var1+(n2-1)*var2)/(n1+n2-2))
+d_boot = abs(m1-m2)/sd_pooled
+d_boot
+```
+
+Conceptual replication 2: Larger variance in reliability estimates for tasks
+
+```{r}
+tmp = rel_comp %>%
+  group_by(dv) %>%
+  summarise(rel_var = var(retest_reliability), 
+            task=unique(task)) %>%
+  na.omit()
+tmp %>%
+  ggplot(aes(rel_var, fill=task))+
+  geom_density(alpha=0.5, position='identity')+
+  theme(legend.title = element_blank())+
+  xlab('Variance of reliability estimates')
+```
+
+```{r}
+summary(lm(rel_var ~ task, tmp))
+```
+
+Effect sizes of task on variance in reliability estimates in literature vs our results are comparable
+
+```{r}
+m1 = tmp %>% filter(task == "task") %>% summarise(m1 = mean(rel_var))
+m2 = tmp %>% filter(task == "survey") %>% summarise(m2 = mean(rel_var))
+n1 = nrow(tmp %>% filter(task == "task"))
+n2 = nrow(tmp %>% filter(task == "survey"))
+var1 = tmp %>% filter(task == "task") %>% summarise(var1 = var(rel_var))
+var2 = tmp %>% filter(task == "survey") %>% summarise(var2 = var(rel_var))
+sd_pooled = sqrt(((n1-1)*var1+(n2-1)*var2)/(n1+n2-2))
+d_lit = abs(m1-m2)/sd_pooled
+d_lit
+```
+
+```{r}
+tmp = boot_comp %>%
+  group_by(dv) %>%
+  summarise(rel_var = var(icc), 
+            task=unique(task)) %>%
+  na.omit()
+
+m1 = tmp %>% filter(task == "task") %>% summarise(m1 = mean(rel_var))
+m2 = tmp %>% filter(task == "survey") %>% summarise(m2 = mean(rel_var))
+n1 = nrow(tmp %>% filter(task == "task"))
+n2 = nrow(tmp %>% filter(task == "survey"))
+var1 = tmp %>% filter(task == "task") %>% summarise(var1 = var(rel_var))
+var2 = tmp %>% filter(task == "survey") %>% summarise(var2 = var(rel_var))
+sd_pooled = sqrt(((n1-1)*var1+(n2-1)*var2)/(n1+n2-2))
+d_boot = abs(m1-m2)/sd_pooled
+d_boot
+```
+
+Square difference between our mean estimate and the reliability from the literature decreases exponentially with sample size.
 The smaller the sample size in the literature the more the reliability estimate differs from our results.
@@
   theme_bw()
-```
-
-```{r}
-lit_review %>%
-  ggplot(aes(sample_size, retest_reliability, color=task))+
-  geom_smooth(method='lm')
-
-mod1 = lmer(retest_reliability~sample_size+(1|dv), data=lit_review)
-
-```
-
-```{r}
-#sd by average sample size
-lit_review %>%
-  group_by(dv) %>%
-  summarise(sd_rel = sd(retest_reliability),
-            avg_sample_size = mean(sample_size)) %>%
-  ggplot(aes(avg_sample_size, sd_rel))+
-  geom_point()+
-  xlim(0,200)
 ```

### 2018-03-21 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 rel_comp = rel_comp %>%
-  mutate(diff_sq = abs(mean_icc - retest_reliability)^2)
+  mutate(diff_sq = (mean_icc - retest_reliability)^2)
 
@@
   geom_smooth(method="glm",se=FALSE, method.args=list(family=gaussian(link="log")))+
-  theme_bw()
+  theme_bw()+
+  theme(legend.title = element_blank())
 ```
@@
 ```{r}
-with(rel_comp %>% filter(task == "task"), cor(mean_icc, mean_reliability))
-```
-
-```{r}
-with(rel_comp %>% filter(task == "survey"), cor(mean_icc, mean_reliability))
+with(rel_comp %>% filter(task == "task"), cor(mean_icc, retest_reliability))
+```
+
+```{r}
+with(rel_comp %>% filter(task == "survey"), cor(mean_icc, retest_reliability))
 ```
@@
 
-```{r}
-mod4 = lmer(retest_reliability ~ mean_icc + scale(days) + scale(sample_size) + (mean_icc|dv), data=rel_comp)
+Selected model: fixed effect for mean icc and sample size of study, random slope with respect to mean icc and random intercept for each measure
+
+```{r}
+mod4 = lmer(retest_reliability ~ mean_icc + task + scale(sample_size) + (mean_icc|dv), data=rel_comp)
 
@@
 
-Selected model: fixed effect for mean icc and sample size of study, random slope with respect to mean icc and random intercept for each measure
-
 What does it say?
@@
 
-Same result if you do flat model without random slopes for dv's
-
-```{r}
-summary(lm(retest_reliability ~ mean_icc+scale(sample_size), data=rel_comp))
-```
-
 Visualize hierarchical model:
-How would I show random intercepts/slopes? Does the fact that I can't think of how means that there is something wrong with the model?
+How would I show random intercepts/slopes?
 
@@
   geom_abline(slope=1, intercept=0)+
-  # geom_abline(slope=0, intercept=0.3, linetype='dashed')+
+  geom_abline(slope=0, intercept=0.3, linetype='dashed')+
   xlim(-0.2, 1)+
   ylim(-0.2, 1)+
-  facet_grid(task~.)+
+  # facet_grid(task~.)+
   xlab('Mean bootstrapped ICC')+
@@
 
-Potential problems in this graph: 
-- not all metrics are ICC's
-- difference in delay between completion of two tests (does it make a difference in the lit review?)
+NOTE: not all metrics are ICC's
 

### 2018-03-21 code/SRO_Retest_Analyses.Rmd
refactoring

--- 2018-03-21 code/SRO_Retest_Analyses.Rmd
@@
 
-`Plot differences for the measures with differences as examples`
+`Plot difference score distributions for the measures with significant differences as examples`
+
+```{r}
+t1_2_difference %>% 
+  filter(dv == sig_days_effect$dv[1]) %>%
+  mutate(days_btw = as.numeric(days_btw),
+         days_bins = ifelse(days_btw < quantile(days_btw, probs=0.33), "short", 
+                                                ifelse(days_btw>quantile(days_btw, probs=0.66), "large", "medium"))) %>%
+  ggplot(aes(factor(days_bins, levels = c("short", "medium", "large")), difference))+
+  geom_boxplot()+
+  xlab('delay between two measurements')
+```
+
+```{r}
+t1_2_difference %>% 
+  filter(dv == sig_days_effect$dv[4]) %>%
+  mutate(days_btw = as.numeric(days_btw),
+         days_bins = ifelse(days_btw < quantile(days_btw, probs=0.33), "short", 
+                                                ifelse(days_btw>quantile(days_btw, probs=0.66), "large", "medium"))) %>%
+  ggplot(aes(factor(days_bins, levels = c("short", "medium", "large")), difference))+
+  geom_boxplot()+
+  xlab('delay between two measurements')
+```
 
@@
 
+The literature has smaller sized samples for task measures compared to survey measures that report retest reliability.
+
+```{r}
+summary(lm(sample_size ~ task,rel_comp))
+```
+
 What predicts retest reliability in the literature?
@@
 ```
+
+Tasks have significantly lower reliability and reliability decreases with increasing sample size.
 
@@
 
-### Conceptual replications 
-- Larger reliability estimates for surveys
-- Larger variance in reliability estimates for tasks
-
-### Sample size effects/publication bias
-
-Deviance between our mean estimate and the reliability from the literature decreases exponentially with sample size.
+```{r}
+rel_comp = rel_comp %>%
+  mutate(retest_reliability_ft = 0.5*log((1+retest_reliability)/(1-retest_reliability))) %>%
+  filter(is.finite(retest_reliability_ft)==TRUE)
+
+m1 = rel_comp %>% filter(task == "task") %>% summarise(m1 = mean(retest_reliability_ft))
+m2 = rel_comp %>% filter(task == "survey") %>% summarise(m2 = mean(retest_reliability_ft))
+n1 = nrow(rel_comp %>% filter(task == "task"))
+n2 = nrow(rel_comp %>% filter(task == "survey"))
+var1 = rel_comp %>% filter(task == "task") %>% summarise(var1 = var(retest_reliability_ft))
+var2 = rel_comp %>% filter(task == "survey") %>% summarise(var1 = var(retest_reliability_ft))
+sd_pooled = sqrt(((n1-1)*var1+(n2-1)*var2)/(n1+n2-2))
+d_lit = abs(m1-m2)/sd_pooled
+d_lit
+```
+
+`Add column for turk vs lab study`
+
+The literature review conceptually replicates our finding of lower reliability estimates for task measures but with a much smaller effect size (for Fisher transformed reliability estimates).
+
+```{r}
+n_df = rel_comp %>% 
+  group_by(dv) %>%
+  tally()
+
+boot_comp = data.frame()
+
+for(i in 1:length(unique(rel_comp$dv)) ){
+  cur_dv = unique(rel_comp$dv)[i]
+  n = n_df$n[n_df$dv == cur_dv]
+  sample_df = boot_df %>% filter(dv == cur_dv)
+  tmp = sample_n(sample_df, n)
+  boot_comp = rbind(boot_comp, tmp)
+}
+
+rm(cur_dv, n, sample_df, tmp)
+
+boot_comp = boot_comp %>%
+  mutate(task=ifelse(grepl("survey", dv), "task", "survey"),
+         icc_ft = 0.5*log((1+icc)/(1-icc)))
+
+m1 = boot_comp %>% filter(task == "task") %>% summarise(m1 = mean(icc_ft))
+m2 = boot_comp %>% filter(task == "survey") %>% summarise(m2 = mean(icc_ft))
+n1 = nrow(boot_comp %>% filter(task == "task"))
+n2 = nrow(boot_comp %>% filter(task == "survey"))
+var1 = boot_comp %>% filter(task == "task") %>% summarise(var1 = var(icc_ft))
+var2 = boot_comp %>% filter(task == "survey") %>% summarise(var1 = var(icc_ft))
+sd_pooled = sqrt(((n1-1)*var1+(n2-1)*var2)/(n1+n2-2))
+d_boot = abs(m1-m2)/sd_pooled
+d_boot
+```
+
+Square difference between our mean estimate and the reliability from the literature decreases exponentially with sample size.
 The smaller the sample size in the literature the more the reliability estimate differs from our results.
 
+This plot (weakly) supports that point that our results diverge most from studies with smaller sample sizes.
+
 ```{r}
 rel_comp = rel_comp %>%
-  mutate(diff_sq = abs(mean_icc - retest_reliability)^2)
+  mutate(diff_sq = abs(mean_icc - retest_reliability))
 
@@
   ggplot(aes(sample_size,diff_sq, color=task))+
-  # geom_point()+
+  geom_point()+
   #exponential decay (linearized by taking logs of both sides)
   geom_smooth(method="glm",se=FALSE, method.args=list(family=gaussian(link="log")))+
-  theme_bw()
-```
-
-```{r}
-lit_review %>%
-  ggplot(aes(sample_size, retest_reliability, color=task))+
-  geom_smooth(method='lm')
-
-mod1 = lmer(retest_reliability~sample_size+(1|dv), data=lit_review)
-
-```
-
-```{r}
-#sd by average sample size
-lit_review %>%
+  theme_bw()+
+  theme(legend.title = element_blank())
+```
+
+But as the plot suggests these are not significant effects overall.
+
+```{r}
+summary(lmer(diff_sq ~ sample_size*task + (1|dv), rel_comp))
+```
+
+### Direct relation to our results
+
+Correlation between our mean estimates from bootstrapped samples and the literature review for task variables
+
+```{r}
+with(rel_comp %>% filter(task == "task"), cor(mean_icc, retest_reliability, method="spearman"))
+```
+
+```{r}
+with(rel_comp %>% filter(task == "survey"), cor(mean_icc, retest_reliability, method="spearman"))
+```
+
+Model comparisons building model to predict the reliabilities in the literature from our results.
+
+sample one row per measure out of lit review
+r^2 of retest_reliability ~ sampled_reliability vs. 
+r^2 of retest_reliability ~ mean_icc
+
+coef of retest_reliability ~ sampled_reliability vs. 
+coef of retest_reliability ~ mean_icc
+
+```{r}
+tmp  = rel_comp %>% filter(dv == unique(rel_comp$dv)[10])
+
+sample_from_dv <- function(df){
+  if(nrow(df)>1){
+    row_num = sample(1:nrow(df),1)
+    sample_row = df[row_num,]
+    df = df[-row_num,]
+    df$lit_predictor = sample_row$retest_reliability
+  }
+  return(df)
+}
+
+sample_from_dv(tmp)
+
+sampled_df = rel_comp %>%
   group_by(dv) %>%
-  summarise(sd_rel = sd(retest_reliability),
-            avg_sample_size = mean(sample_size)) %>%
-  ggplot(aes(avg_sample_size, sd_rel))+
-  geom_point()+
-  xlim(0,200)
-```
-
-### Direct relation to our results
-
-Correlation between our mean estimates from bootstrapped samples and the literature review for task variables
-
-```{r}
-with(rel_comp %>% filter(task == "task"), cor(mean_icc, mean_reliability))
-```
-
-```{r}
-with(rel_comp %>% filter(task == "survey"), cor(mean_icc, mean_reliability))
-```
-
-Model comparisons building model to predict the reliabilities in the literature from our results.
+  do(sample_from_dv(.))
+
+summary(lm(retest_reliability ~ lit_predictor, data=sampled_df))
+summary(lm(retest_reliability ~ mean_icc, data=sampled_df))
+```
 
@@
 mod1 = lmer(retest_reliability ~ mean_icc + (1|dv), data=rel_comp)
-mod2 = lmer(retest_reliability ~ mean_icc + (mean_icc|dv), data=rel_comp)
+mod1a = lm(retest_reliability ~ mean_icc, data=rel_comp)
+
+cor(predict(mod1), rel_comp$retest_reliability)^2
+cor(predict(mod1a), rel_comp$retest_reliability)^2
+
+# mod2 = lmer(retest_reliability ~ mean_icc + (mean_icc|dv), data=rel_comp)
+
+rel_comp %>%
+  select(dv, retest_reliability, mean_icc)
+
+summary(mod1a)
+
+summary(lm(retest_reliability ~ mean_icc*scale(sample_size), data=rel_comp))
 
@@
 ```
-
-```{r}
-mod3 = lmer(retest_reliability ~ mean_icc + scale(sample_size) + (mean_icc|dv), data=rel_comp)
-
-anova(mod2, mod3)
-```
-
-```{r}
-mod4 = lmer(retest_reliability ~ mean_icc + scale(days) + scale(sample_size) + (mean_icc|dv), data=rel_comp)
-
-anova(mod3, mod4)
-```
-
-Selected model: fixed effect for mean icc and sample size of study, random slope with respect to mean icc and random intercept for each measure
-
-What does it say?
-
-```{r}
-summary(mod3)
-```
-
-How well does the model fit? (squared correlation between predictions of model and data)
-
-```{r}
-cor(predict(mod3), rel_comp$retest_reliability)^2
-```
-
-Same result if you do flat model without random slopes for dv's
-
-```{r}
-summary(lm(retest_reliability ~ mean_icc+scale(sample_size), data=rel_comp))
-```
-
-Visualize hierarchical model:
-How would I show random intercepts/slopes? Does the fact that I can't think of how means that there is something wrong with the model?
 
@@
 
-Potential problems in this graph: 
-- not all metrics are ICC's
-- difference in delay between completion of two tests (does it make a difference in the lit review?)
+NOTE: not all metrics are ICC's
+
+```{r echo=FALSE}
+rm(tmp, rel_comp, boot_comp, d_boot, d_lit, mod1, mod2, mod3, mod4, n_df, m1, m2, var1, var2, sd_pooled, task, i, n1, n2)
+```
 

### 2018-03-21 code/SRO_Retest_Analyses.Rmd
added sampling analysis in comparing the lit review to our results

@@
 ```{r}
-tmp  = rel_comp %>% filter(dv == unique(rel_comp$dv)[10])
+comp_lit_pred <- function(df){
 
@@
 
-sample_from_dv(tmp)
-
-sampled_df = rel_comp %>%
+  sampled_df = df %>%
     group_by(dv) %>%
@@
 
-summary(lm(retest_reliability ~ lit_predictor, data=sampled_df))
-summary(lm(retest_reliability ~ mean_icc, data=sampled_df))
+  mod_lit = lm(retest_reliability ~ lit_predictor, data=sampled_df)
+  mod_boot = lm(retest_reliability ~ mean_icc, data=sampled_df)
+
+  out = data.frame(r2_lit = summary(mod_lit)$r.squared,
+                   r2_boot = summary(mod_boot)$r.squared,
+                   m_lit = coef(summary(mod_lit))["lit_predictor","Estimate"],
+                   m_boot = coef(summary(mod_boot))["mean_icc","Estimate"])
+
+  return(out)
+}
+
+comp_lit_pred_out = plyr::rdply(1000, comp_lit_pred(rel_comp))
+
+comp_lit_pred_out %>%
+  select(-.n) %>%
+  gather(key, value) %>%
+  separate(key, c("stat", "sample"), sep = "_") %>%
+  ggplot(aes(value, fill=sample))+
+  geom_density(alpha = 0.5, position='identity')+
+  facet_wrap(~stat, scales='free')+
+  theme(legend.title = element_blank())+
+  xlab('')
 ```

### 2018-04-02 code/SRO_Retest_Analyses.Rmd
added data quality checks

@@
 
-## Demographics reliability
+## Data quality checks
+
+### Demographics reliability
 
@@
 
-## Effect of delays between the two measurements
+### Effect of delays between the two measurements
 
@@
 Normalization equates the means of each difference score distribution to 0 which would mask any meaningful change between the two time points but the analysis here does not interpret the mean of the difference score distributions but is interested in its relation to the days between completion.
-We check if the variables show systematic differences between the two points later and can investigate whether
+We check if the variables show systematic differences between the two points later.
 
 Here we check if the difference is larger the longer the delay
-What is the threshold for a meaningful difference between the two points for each variable? 
-For standardized difference scores does it cross 2 on the y axis?
 
@@
                        labels=c("NS", "Sig"))
+
+ggsave('DaysBtwEffect.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 100)
 ```
@@
 effect of whether days between leads to a sig difference on reliability of that variable? plot coef of sig_day_effect over rel_df point estimate
+
+Do the variables that show significant dependence on the delay between the completion times have systematically lower/higher reliability?
+Looking at the reliability point estimate over the size of the delay effect.
+There are very few variables to compare anyway but regardless doesn't look conclusive/concerning.
 
@@
 
-`Plot difference score distributions for the measures with significant differences as examples`
-
-```{r}
-t1_2_difference %>% 
-  filter(dv == sig_days_effect$dv[1]) %>%
-  mutate(days_btw = as.numeric(days_btw),
-         days_bins = ifelse(days_btw < quantile(days_btw, probs=0.33), "short", 
-                                                ifelse(days_btw>quantile(days_btw, probs=0.66), "large", "medium"))) %>%
-  ggplot(aes(factor(days_bins, levels = c("short", "medium", "large")), difference))+
-  geom_boxplot()+
-  xlab('delay between two measurements')
-```
-
-```{r}
-t1_2_difference %>% 
-  filter(dv == sig_days_effect$dv[4]) %>%
-  mutate(days_btw = as.numeric(days_btw),
-         days_bins = ifelse(days_btw < quantile(days_btw, probs=0.33), "short", 
-                                                ifelse(days_btw>quantile(days_btw, probs=0.66), "large", "medium"))) %>%
-  ggplot(aes(factor(days_bins, levels = c("short", "medium", "large")), difference))+
-  geom_boxplot()+
-  xlab('delay between two measurements')
+### Overlapping survery questions
+
+Some surveys have overlapping questions. Do these correlate within and across sessions?
+
+First determine the overlapping questions.
+
+```{r}
+tmp = read.csv(gzfile(paste0(retest_data_path, 'items.csv.gz')))
+tmp = tmp %>% 
+  filter(worker == 's005') %>% 
+  select(item_ID, item_text) %>% 
+  mutate(item_text = trimws(as.character(item_text))) %>%
+  unite(item, c("item_ID", "item_text"), sep = "___")
+
+comb = as.data.frame(t(combn(unique(tmp$item),2)))
+
+duplicate_items = comb %>% 
+  filter(grepl('dospert', V1)==FALSE) %>%
+  filter(grepl('selection_optimization', V1)==FALSE) %>%
+  filter(grepl('sensation_seeking', V1)==FALSE) %>%
+  separate(V1, c("item1_ID", "item1_text"), sep="___") %>%
+  separate(V2, c("item2_ID", "item2_text"), sep="___") %>%
+  mutate(similarity = levenshteinSim(item1_text, item2_text)) %>%
+  filter(similarity>0.8) %>%
+  select(item1_ID, item2_ID, item1_text, item2_text)
+
+duplicate_items
+```
+
+```{r warning=FALSE, message=FALSE}
+#surveys to read in
+extract_items = c('worker',unique(with(duplicate_items, c(item1_ID, item2_ID))))
+
+#correlations to compute:
+#item1_t1 - item2_t1, 
+#item1_t2 - item2_t2, 
+#item1_t1 - item2_t2, 
+#item1_t2 - item2_t1
+
+duplicate_items_data_t1 = read.csv(paste0(test_data_path, 'subject_x_items.csv'))
+duplicate_items_data_t2 = read.csv(paste0(retest_data_path, 'subject_x_items.csv'))
+
+duplicate_items_data_t1 = duplicate_items_data_t1 %>%
+  filter(worker %in% duplicate_items_data_t2$worker) %>%
+  select(extract_items)
+
+duplicate_items_data_t2=duplicate_items_data_t2 %>%
+  filter(worker %in% duplicate_items_data_t1$worker) %>%
+  select(extract_items)
+
+duplicate_items = duplicate_items %>%
+  mutate(t1_t1_cor = NA,
+         t2_t2_cor = NA,
+         t1_t2_cor = NA,
+         t2_t1_cor = NA,
+         t1_t1_polycor = NA,
+         t2_t2_polycor = NA,
+         t1_t2_polycor = NA,
+         t2_t1_polycor = NA)
+
+for(i in 1:nrow(duplicate_items)){
+  duplicate_items$t1_t1_cor[i] = abs(cor(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])],
+                                  duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])]))
+
+  duplicate_items$t2_t2_cor[i] = abs(cor(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])],
+                                  duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])]))
+
+  duplicate_items$t1_t2_cor[i] = abs(cor(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])],
+                                  duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])]))
+
+  duplicate_items$t2_t1_cor[i] = abs(cor(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])],
+                                  duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])]))
+
+  duplicate_items$t1_t1_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])],
+                      duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])]))$rho[2])
+
+  duplicate_items$t2_t2_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])],
+                      duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])]))$rho[2])
+
+  duplicate_items$t1_t2_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])],
+                      duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])]))$rho[2])
+
+  duplicate_items$t2_t1_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])],
+                      duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])]))$rho[2])
+}
+
+duplicate_items
+```
+
+```{r}
+summary(duplicate_items$t1_t1_polycor)
+summary(duplicate_items$t2_t2_polycor)
+summary(duplicate_items$t1_t2_polycor)
+summary(duplicate_items$t2_t1_polycor)
+```
+
+```{r echo=FALSE}
+rm(tmp, comb)
 ```
@@
 
+```{r}
+summary(lm(retest_reliability ~ task,rel_comp))
+```
+
 The literature has smaller sized samples for task measures compared to survey measures that report retest reliability.
@@
 
-  mod_lit = lm(retest_reliability ~ lit_predictor, data=sampled_df)
-  mod_boot = lm(retest_reliability ~ mean_icc, data=sampled_df)
+  mod_lit = lm(retest_reliability ~ lit_predictor+scale(sample_size), data=sampled_df)
+  mod_boot = lm(retest_reliability ~ mean_icc+scale(sample_size), data=sampled_df)
 
@@
   xlab('')
+```
+
+```{r}
+with(comp_lit_pred_out, t.test(r2_lit, r2_boot))
 ```

### 2018-04-02 code/SRO_Retest_Analyses_Helper_Functions.R

@@ -12,6 +12,7 @@ library(stringr)
 library(plotly)
 library(DT)
 library(sjPlot)
+library(RecordLinkage)
 
 render_this <- function(){rmarkdown::render('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Analyses.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, toc_depth = 2, code_folding = 'hide'))}
 

### 2018-04-06 code/SRO_Retest_Analyses.Rmd
completing draft

@@
 
-Compare effect sizes of effect of task on reliability estimates in literature vs our results (just looking at the variables you find in the literature)
-
-```{r}
-rel_comp = rel_comp %>%
-  mutate(retest_reliability_ft = 0.5*log((1+retest_reliability)/(1-retest_reliability))) %>%
-  filter(is.finite(retest_reliability_ft)==TRUE)
-
-m1 = rel_comp %>% filter(task == "task") %>% summarise(m1 = mean(retest_reliability_ft))
-m2 = rel_comp %>% filter(task == "survey") %>% summarise(m2 = mean(retest_reliability_ft))
-n1 = nrow(rel_comp %>% filter(task == "task"))
-n2 = nrow(rel_comp %>% filter(task == "survey"))
-var1 = rel_comp %>% filter(task == "task") %>% summarise(var1 = var(retest_reliability_ft))
-var2 = rel_comp %>% filter(task == "survey") %>% summarise(var1 = var(retest_reliability_ft))
-sd_pooled = sqrt(((n1-1)*var1+(n2-1)*var2)/(n1+n2-2))
-d_lit = abs(m1-m2)/sd_pooled
-d_lit
-```
-
-`Add column for turk vs lab study`
-
-The literature review conceptually replicates our finding of lower reliability estimates for task measures but with a much smaller effect size (for Fisher transformed reliability estimates).
+I used to compare effect sizes of effect of task on reliability estimates in literature vs our results (just looking at the variables you find in the literature) but removed this analysis because   
+1. the estimates in the literature are not all the same statistic
+2. from our data I was only using ICC's
+3.
+I was sampling from our bootstrapped results as many datapoints for each measure as there are in the literature but that didn't seem like the best way to make use of our data to make it comparable to the literature.
+
+Despite these problems the main result was that the effect size was much larger in our dataset compared to the literature but given the problems I think the sampling analyses below are more informative than this.
+
+We also checked whether our results diverge most from studies with smaller sample sizes.
+Square difference between our mean estimate and the reliability from the literature decreases exponentially with sample size.
+The smaller the sample size in the literature the more the reliability estimate differs from our results.
+But this was a weak result because most of the studies in the literature have smaller sample sizes and you see both small and large deviations for these studies (these were not significant either).
+
+### Direct relation to our results
+
+Correlation between our mean estimates from bootstrapped samples and the literature review for task variables
 
@@
   tally()
+
+lit_emp_cor = function(){
 
@@
 
-boot_comp = boot_comp %>%
-  mutate(task=ifelse(grepl("survey", dv), "task", "survey"),
-         icc_ft = 0.5*log((1+icc)/(1-icc)))
-
-m1 = boot_comp %>% filter(task == "task") %>% summarise(m1 = mean(icc_ft))
-m2 = boot_comp %>% filter(task == "survey") %>% summarise(m2 = mean(icc_ft))
-n1 = nrow(boot_comp %>% filter(task == "task"))
-n2 = nrow(boot_comp %>% filter(task == "survey"))
-var1 = boot_comp %>% filter(task == "task") %>% summarise(var1 = var(icc_ft))
-var2 = boot_comp %>% filter(task == "survey") %>% summarise(var1 = var(icc_ft))
-sd_pooled = sqrt(((n1-1)*var1+(n2-1)*var2)/(n1+n2-2))
-d_boot = abs(m1-m2)/sd_pooled
-d_boot
-```
-
-Square difference between our mean estimate and the reliability from the literature decreases exponentially with sample size.
-The smaller the sample size in the literature the more the reliability estimate differs from our results.
-
-This plot (weakly) supports that point that our results diverge most from studies with smaller sample sizes.
-
-```{r}
-rel_comp = rel_comp %>%
-  mutate(diff_sq = abs(mean_icc - retest_reliability))
-
-rel_comp %>%
-  ggplot(aes(sample_size,diff_sq, color=task))+
-  geom_point()+
-  #exponential decay (linearized by taking logs of both sides)
-  geom_smooth(method="glm",se=FALSE, method.args=list(family=gaussian(link="log")))+
-  theme_bw()+
-  theme(legend.title = element_blank())
-```
-
-But as the plot suggests these are not significant effects overall.
-
-```{r}
-summary(lmer(diff_sq ~ sample_size*task + (1|dv), rel_comp))
-```
-
-### Direct relation to our results
-
-Correlation between our mean estimates from bootstrapped samples and the literature review for task variables
-
-```{r}
-with(rel_comp %>% filter(task == "task"), cor(mean_icc, retest_reliability, method="spearman"))
-```
-
-```{r}
-with(rel_comp %>% filter(task == "survey"), cor(mean_icc, retest_reliability, method="spearman"))
+  #check if cbind is ok
+  # sum(boot_comp$dv == rel_comp$dv)
+  #cbinding pearson because that is the most common metric in the lit
+  rel_comp = cbind(rel_comp, boot_comp$pearson)
+  #rename new column
+  names(rel_comp)[which(names(rel_comp) == "boot_comp$pearson")] = "pearson"
+
+  out = data.frame(task = NA, survey = NA)
+
+  out$task = with(rel_comp %>% filter(task == "task"), cor(pearson, retest_reliability))
+
+  out$survey = with(rel_comp %>% filter(task == "survey"), cor(pearson, retest_reliability))
+
+  rel_comp = rel_comp[,-16]
+
+  return(out)
+}
+
+lit_emp_cor_out = plyr::rdply(100, lit_emp_cor)
+
+# write.csv(lit_emp_cor_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/lit_emp_cor_out.csv')
+
+summary(lit_emp_cor_out)
+
 ```

### 2018-04-09 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 
-test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_02-03-2018/'
-
-retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-03-2018/'
+test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_03-29-2018/'
+
+retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-29-2018/'
 ```
@@
 
-Measure level plot
-
-```{r warning=FALSE, message=FALSE}
+```{r message=FALSE}
 lit_review = lit_review %>%
@@
   mutate(task_group = gsub("survey", "", task_group)) %>%
-    select(-measure_description, -reference)
+  select(-measure_description)
+
+tmp = lit_review[duplicated(lit_review$reference)==FALSE,]
+
+nrow(tmp)
+sum(tmp$sample_size)
+nrow(lit_review)
+```
+
+```{r}
+rm(tmp)
+```
+
+Measure level plot
+
+```{r warning=FALSE, message=FALSE}
+lit_review = lit_review %>%
+  select(-reference)
 ```
@@
 ```{r echo=FALSE}
-rm(tmp, comb)
+rm(tmp, comb, sig_days_effect, t1_2_difference, duplicate_items, duplicate_items_data_t1, duplicate_items_data_t2, extract_items, get_delay_effect)
 ```
@@
 
-```{r}
+```{r message=FALSE}
 var_boot_df = boot_df %>%
   group_by(dv) %>%
-  summarise(mean_icc = mean(icc))
+  summarise(mean_icc = mean(icc),
+            mean_pearson = mean(pearson))
 
@@
 
-Model comparisons building model to predict the reliabilities in the literature from our results.
+### Noise ceiling
+
+Model comparisons building model to predict the reliabilities in the literature from a sample from our results versus a sample form the literature.
 
@@
 
-  mod_lit = lm(retest_reliability ~ lit_predictor+scale(sample_size), data=sampled_df)
-  mod_boot = lm(retest_reliability ~ mean_icc+scale(sample_size), data=sampled_df)
+  mod_lit = lm(retest_reliability ~ lit_predictor+scale(sample_size)+task, data=sampled_df)
+  mod_boot = lm(retest_reliability ~ mean_pearson+scale(sample_size)+task, data=sampled_df)
 
@@
                    m_lit = coef(summary(mod_lit))["lit_predictor","Estimate"],
-                   m_boot = coef(summary(mod_boot))["mean_icc","Estimate"])
+                   m_boot = coef(summary(mod_boot))["mean_pearson","Estimate"])
 
@@
 comp_lit_pred_out = plyr::rdply(1000, comp_lit_pred(rel_comp))
-
-comp_lit_pred_out %>%
+```
+
+```{r}
+tmp = comp_lit_pred_out %>%
   select(-.n) %>%
   gather(key, value) %>%
-  separate(key, c("stat", "sample"), sep = "_") %>%
+  separate(key, c("stat", "sample"), sep = "_")
+
+tmp$stat = as.factor(tmp$stat)
+levels(tmp$stat) <- c("coefficient", expression(r^"2"))
+
+tmp %>%  
   ggplot(aes(value, fill=sample))+
-  geom_density(alpha = 0.5, position='identity')+
-  facet_wrap(~stat, scales='free')+
-  theme(legend.title = element_blank())+
-  xlab('')
-```
-
-```{r}
-with(comp_lit_pred_out, t.test(r2_lit, r2_boot))
-```
-
-```{r}
-mod1 = lmer(retest_reliability ~ mean_icc + (1|dv), data=rel_comp)
-mod1a = lm(retest_reliability ~ mean_icc, data=rel_comp)
-
-cor(predict(mod1), rel_comp$retest_reliability)^2
-cor(predict(mod1a), rel_comp$retest_reliability)^2
-
-# mod2 = lmer(retest_reliability ~ mean_icc + (mean_icc|dv), data=rel_comp)
-
-rel_comp %>%
-  select(dv, retest_reliability, mean_icc)
-
-summary(mod1a)
-
-summary(lm(retest_reliability ~ mean_icc*scale(sample_size), data=rel_comp))
-
-anova(mod1, mod2)
-```
-
-```{r}
-rel_comp %>%
-  ggplot()+  
-  geom_boxplot(aes(mean_icc, retest_reliability, group=dv))+
-  geom_smooth(aes(mean_icc, retest_reliability), method= 'lm')+
-  theme_bw()+
-  theme(legend.position = 'none')+
-  geom_abline(slope=1, intercept=0)+
-  geom_abline(slope=0, intercept=0.3, linetype='dashed')+
-  xlim(-0.2, 1)+
-  ylim(-0.2, 1)+
-  # facet_grid(task~.)+
-  xlab('Mean bootstrapped ICC')+
-  ylab('Reliability estimate from literature')
-
-```
-
-NOTE: not all metrics are ICC's
+  geom_density(alpha = 0.5, position='identity', color=NA)+
+  facet_grid(.~stat, scales='free', labeller = label_parsed)+
+  scale_fill_discrete(breaks=c("boot","lit"),
+                       labels=c("Empirical", "Literature"),
+                      name="Prediction")+
+  xlab('')+
+  ylab('')
+
+ggsave('Lit_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 10, height = 4, units = "in", limitsize = FALSE, dpi = 100)
+```
+
+```{r}
+with(comp_lit_pred_out, t.test(r2_lit, r2_boot, paired=T))
+```
+
+```{r}
+with(comp_lit_pred_out, t.test(m_lit, m_boot))
+```
 
 ```{r echo=FALSE}
-rm(tmp, rel_comp, boot_comp, d_boot, d_lit, mod1, mod2, mod3, mod4, n_df, m1, m2, var1, var2, sd_pooled, task, i, n1, n2)
+rm(tmp, rel_comp, boot_comp, mod1, mod2, mod3, mod4, n_df, i, lit_emp_cor, lit_emp_cor_out, comp_lit_pred, comp_lit_pred_out)
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-
 boot_df %>%

### 2018-04-13 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 
-test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_03-29-2018/'
-
-retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-29-2018/'
+test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_02-03-2018/'
+
+retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-03-2018/'
 ```
@@
 
+## Learning effects
+
+For most of our tasks one might wonder about improvements in performance due to learning effects. 
+The type of ICC we have chosen does not take within subject (between session/systematic) variance in to account.
+This is why Weir recommends checking whether there is a significant change based on time and examining the SEMs.
+
+Had we chosen another kind of ICC taking this source of variance into account (e.g. 2,1 or 2,k) they could have suggested that tasks have lower reliability.
+
+Doing a simple t-test on the difference score alone would not be a very rigourous way of testing whether any change is meaningful because two distributions with error would be compared to each other.
+Fortunately there are ways to take the error for both measurements in to account.
+
+To check whether a measure shows learning effects in a meaningful number of bootstrapped samples we can: check if the effect of time is significant in each bootstrapped sample and filter variables that have more than 5% of the boostrapped samples showing significant time effects.
+
+Another way might be to compute confidence intervals using SEMs as described in the second half of Weir (2005) and check what percent of participants have scores that fall out of this range.
+I haven't pursued this at least for now.
+
+Here we ask: Which variables have significant time effects in more than 5% of the bootstrapped samples?
+
+22/74 survey measures
+135/335 task measures
+
+```{r}
+boot_df %>%
+  select(dv, p_time, task) %>%
+  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
+  group_by(dv)%>%
+  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
+            task = unique(task))%>%
+  filter(pct_sig_time_effect>5) %>%
+  arrange(task,-pct_sig_time_effect) %>%
+  ungroup()%>%
+  group_by(task) %>%
+  summarise(count=n())
+```
+
 ## Task Reliabilities
@@
 
-## Learning effects
-
-For most of our tasks one might wonder about improvements in performance due to learning effects.
-
-The type of ICC we have chosen does not take within subject (between session/systematic) variance in to account.
-This is why Weir recommends checking whether there is a significant change based on time and examining the SEMs.
-
-Had we chosen another kind of ICC taking this source of variance into account (e.g. 2,1 or 2,k) they could have suggested that tasks have lower reliability.
-
-Doing a simple t-test on the difference score alone would not be a very rigourous way of testing whether any change is meaningful because two distributions with error would be compared to each other.
-Fortunately there are ways to take the error for both measurements in to account.
-
-To check whether a measure shows learning effects in a meaningful number of bootstrapped samples we can: check if the effect of time is significant in each bootstrapped sample and filter variables that have more than 5% of the boostrapped samples showing significant time effects.
-
-Another way might be to compute confidence intervals using SEMs as described in the second half of Weir (2005) and check what percent of participants have scores that fall out of this range.
-I haven't pursued this at least for now.
-
-Here we ask: Which variables have significant time effects in more than 5% of the bootstrapped samples?
-
-22/74 survey measures
-135/335 task measures
-
-```{r}
-boot_df %>%
-  select(dv, p_time, task) %>%
-  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
-  group_by(dv)%>%
-  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
-            task = unique(task))%>%
-  filter(pct_sig_time_effect>5) %>%
-  arrange(task,-pct_sig_time_effect) %>%
-  ungroup()%>%
-  group_by(task) %>%
-  summarise(count=n())
-```
-
 ## Survey reliabilities

### 2018-04-26 code/SRO_Retest_Analyses.Rmd
refactoring

--- 2018-04-09 code/SRO_Retest_Analyses.Rmd
@@
 ```{r}
-sjt.df(tmp_save %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/var_breakdown_summary.doc")
+sjt.df(tmp_save %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/var_breakdown_summary.doc")
 ```
@@
 
-sjt.df(tmp %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/task_rel_table.doc")
+sjt.df(tmp %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/task_rel_table.doc")
 ```
@@
 
-sjt.df(tmp_save %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/ddm_rel_table.doc")
+sjt.df(tmp_save %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/ddm_rel_table.doc")
 ```
@@
 ggsave('Bootstrap_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 6, units = "in", limitsize = FALSE)
-```
-
-## Learning effects
-
-For most of our tasks one might wonder about improvements in performance due to learning effects.
-
-The type of ICC we have chosen does not take within subject (between session/systematic) variance in to account.
-This is why Weir recommends checking whether there is a significant change based on time and examining the SEMs.
-
-Had we chosen another kind of ICC taking this source of variance into account (e.g. 2,1 or 2,k) they could have suggested that tasks have lower reliability.
-
-Doing a simple t-test on the difference score alone would not be a very rigourous way of testing whether any change is meaningful because two distributions with error would be compared to each other.
-Fortunately there are ways to take the error for both measurements in to account.
-
-To check whether a measure shows learning effects in a meaningful number of bootstrapped samples we can: check if the effect of time is significant in each bootstrapped sample and filter variables that have more than 5% of the boostrapped samples showing significant time effects.
-
-Another way might be to compute confidence intervals using SEMs as described in the second half of Weir (2005) and check what percent of participants have scores that fall out of this range.
-I haven't pursued this at least for now.
-
-Here we ask: Which variables have significant time effects in more than 5% of the bootstrapped samples?
-
-22/74 survey measures
-135/335 task measures
-
-```{r}
-boot_df %>%
-  select(dv, p_time, task) %>%
-  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
-  group_by(dv)%>%
-  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
-            task = unique(task))%>%
-  filter(pct_sig_time_effect>5) %>%
-  arrange(task,-pct_sig_time_effect) %>%
-  ungroup()%>%
-  group_by(task) %>%
-  summarise(count=n())
 ```
@@
 
-sjt.df(tmp %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/survey_rel_table.doc")
+sjt.df(tmp %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/survey_rel_table.doc")
 ```

### 2018-04-27 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 
-# write.csv(lit_emp_cor_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/lit_emp_cor_out.csv')
+write.csv(lit_emp_cor_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/lit_emp_cor_out.csv')
 
@@
 ```{r echo=FALSE}
-rm(tmp, rel_comp, boot_comp, mod1, mod2, mod3, mod4, n_df, i, lit_emp_cor, lit_emp_cor_out, comp_lit_pred, comp_lit_pred_out)
+rm(tmp, rel_comp, mod1, mod2, mod3, n_df, i, lit_emp_cor, lit_emp_cor_out, comp_lit_pred, comp_lit_pred_out)
 ```
@@
 The bootstrapped version is essentially the same but the plots are busier due to more datapoints.
+
+```{r}
+table(rel_df$task)
+```
 
@@
   filter(task == 'survey') %>%
-ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc, group=dv)) + 
-  geom_violin(fill='#F8766D', position = 'identity')+
+ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
+  geom_violin(fill='#F8766D')+
   theme_bw() + 
@@
                                "Error variance")), mean_pct, color=task))+
-  geom_point(position=position_dodge(width = 0.25), size=5)+
-  geom_errorbar(aes(ymin=mean_pct-sd_pct, ymax=mean_pct+sd_pct), position=position_dodge(width = 0.25), width=0, size=2)+
+  # geom_point(position=position_dodge(width = 0.25), size=5)+
+  # geom_errorbar(aes(ymin=mean_pct-sd_pct, ymax=mean_pct+sd_pct), position=position_dodge(width = 0.25), width=0, size=2)+
+  geom_errorbar(aes(ymin=cil, ymax=ciu), position=position_dodge(width = 0.25), width=0, size=2)+
   theme_bw()+
@@
         legend.text = element_text(size=14),
+        legend.position = 'bottom',
         axis.text = element_text(size=12),

### 2018-04-27 code/SRO_Retest_Analyses.Rmd
refactoring

@@
          cil = mean_pct+(sd_pct*cvl)/sqrt(n),
-         ciu = mean_pct+(sd_pct*cvu)/sqrt(n)) %>%
+         ciu = mean_pct+(sd_pct*cvu)/sqrt(n),
+         sem_pct = sd_pct/sqrt(n)) %>%
   ggplot(aes(factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
@@
                                "Error variance")), mean_pct, color=task))+
-  # geom_point(position=position_dodge(width = 0.25), size=5)+
+  geom_point(position=position_dodge(width = 0.25), size = 4)+
   # geom_errorbar(aes(ymin=mean_pct-sd_pct, ymax=mean_pct+sd_pct), position=position_dodge(width = 0.25), width=0, size=2)+
-  geom_errorbar(aes(ymin=cil, ymax=ciu), position=position_dodge(width = 0.25), width=0, size=2)+
+  geom_errorbar(aes(ymin=cil, ymax=ciu), position=position_dodge(width = 0.25), width=0.25, size=2)+
   theme_bw()+
@@
 
-## Learning effects
-
-For most of our tasks one might wonder about improvements in performance due to learning effects. 
+## Systematic effects between time points
+
 The type of ICC we have chosen does not take within subject (between session/systematic) variance in to account.
 This is why Weir recommends checking whether there is a significant change based on time and examining the SEMs.
+These systematic effects could be meaningful and important to account for for some measures (e.g.
+task measures that show learning effects).
 
@@
 
-Doing a simple t-test on the difference score alone would not be a very rigourous way of testing whether any change is meaningful because two distributions with error would be compared to each other.
+Doing a simple t-test on the difference score alone would not be a very rigourous way of testing whether any change is meaningful because two distributions from both time points with error would be compared to each other.
 Fortunately there are ways to take the error for both measurements in to account.
 
-To check whether a measure shows learning effects in a meaningful number of bootstrapped samples we can: check if the effect of time is significant in each bootstrapped sample and filter variables that have more than 5% of the boostrapped samples showing significant time effects.
+To check whether a measure shows systematic differences between the two time points in a meaningful number of bootstrapped samples we can: check if the effect of time is significant in each bootstrapped sample and filter variables that have more than 5% of the boostrapped samples showing significant time effects.
 
 Another way might be to compute confidence intervals using SEMs as described in the second half of Weir (2005) and check what percent of participants have scores that fall out of this range.
-I haven't pursued this at least for now.
+I haven't pursued this for now.
 
@@
 
-22/74 survey measures
-135/335 task measures
+23/74 survey measures
+133/372 task measures
 
@@
   summarise(count=n())
+```
+
+Are these significantly different between surveys and tasks? No.
+
+```{r}
+chisq.test(matrix(data = c(23,74-23,133, 372-133), nrow=2))
+```
+
+Are they predominantly in one or the other direction and does that differ depending on survey vs task?
+
+```{r}
+boot_df %>%
+  select(dv, p_time, task, pearson) %>%
+  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
+  group_by(dv)%>%
+  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
+            task = unique(task),
+            mean_pearson = mean(pearson))%>%
+  filter(pct_sig_time_effect>5) %>%
+  arrange(task,-pct_sig_time_effect) %>%
+  arrange(mean_pearson) %>%
+
+```
+
+SEM CI calculation
+
+```{r}
+boot_df
 ```

### 2018-04-27 code/SRO_Retest_Analyses.Rmd
playing around with sem ci s for each subject

@@
 
-```{r}
-boot_df
+Step 1: T = Grand mean + ICC * (Subject score - Grand mean)
+Step 2: SEP = SD of both measurements * sqrt(1-ICC^2)
+
+```{r}
+get_ind_ci = function(dv_var){
+  matched = match_t1_t2(dv_var)
+  grand_mean = mean(matched$score)
+  grand_sd = sd(matched$score)
+  dv_icc = get_icc(dv_var)
+  sep = grand_sd * sqrt(1-dv_icc^2)
+  matched = matched %>% 
+    spread(time, score) %>%
+    rename("t1"="1", "t2"="2") %>%
+    mutate(true_score = grand_mean+dv_icc*(t1-grand_mean),
+           ci_up = true_score+sep,
+           ci_low = true_score-sep,
+           t2_out_ci = ifelse(t2>ci_up|t2<ci_low,1,0),
+           prop_dist = abs(t1-t2)/sep,
+           large_dist = ifelse(prop_dist>1,1,0))
+    return(matched)
+}
+
+get_prop_out_ci = function(dv_var){
+  get_ind_ci(dv_var) %>%
+  summarise(prop_out_ci=sum(t2_out_ci)/n())
+}
+
+#Create df of point estimate reliabilities
+ind_ci_df <- data.frame(prop_out_ci = rep(NA, length(numeric_cols)))
+
+row.names(ind_ci_df) <- numeric_cols
+
+for(i in 1:length(numeric_cols)){
+  ind_ci_df[numeric_cols[i], 'prop_out_ci'] <- get_spearman(numeric_cols[i]) 
+}
+
+ind_ci_df$dv = row.names(ind_ci_df)
+row.names(ind_ci_df) = seq(1:nrow(ind_ci_df))
+ind_ci_df$task = 'task'
+ind_ci_df[grep('survey', ind_ci_df$dv), 'task'] = 'survey'
+ind_ci_df[grep('holt', ind_ci_df$dv), 'task'] = "task"
+ind_ci_df = ind_ci_df %>%
+  select(dv, task, prop_out_ci)
+
+ind_ci_df %>%
+  filter(prop_out_ci>0.05) %>%
+  arrange(-prop_out_ci)
+
+get_ind_ci("five_facet_mindfulness_survey.total")
 ```

### 2018-04-27 code/SRO_Retest_Analyses.Rmd
playing around with sem ci s for each subject

@@
 
+Here I calculate the proportion of subjects that move more than one standard error of prediction (SEP) in t2 compared to t1 for each measure.
+
+This is odd to think about because the larger the ICC of a measure the smaller the SEP. So very small differences between the two time points can be categorized as 'meaningful' based on the tiny SEP.
+
 ```{r}
@@
   dv_icc = get_icc(dv_var)
-  sep = grand_sd * sqrt(1-dv_icc^2)
+  sep = grand_sd * sqrt(1-(dv_icc^2))
   matched = matched %>% 
@@
     rename("t1"="1", "t2"="2") %>%
-    mutate(true_score = grand_mean+dv_icc*(t1-grand_mean),
-           ci_up = true_score+sep,
-           ci_low = true_score-sep,
-           t2_out_ci = ifelse(t2>ci_up|t2<ci_low,1,0),
-           prop_dist = abs(t1-t2)/sep,
-           large_dist = ifelse(prop_dist>1,1,0))
+    mutate(true_score = grand_mean+(dv_icc*(t1-grand_mean)),
+           ci_up = true_score+(1.96*sep),
+           ci_low = true_score-(1.96*sep),
+           t2_out_ci = ifelse((t2>ci_up)|(t2<ci_low),1,0))
     return(matched)
@@
 
-get_ind_ci("five_facet_mindfulness_survey.total")
+get_ind_ci("ten_item_personality_survey.extraversion")
 ```

### 2018-04-29 code/SRO_Retest_Analyses.Rmd
changing systematic diff analyses

--- 2018-04-27 code/SRO_Retest_Analyses.Rmd
@@
 
+### Anova time effects
+
 The type of ICC we have chosen does not take within subject (between session/systematic) variance in to account.
@@
 
-SEM CI calculation
-
-```{r}
-boot_df
+### SEM CI calculation
+
+Step 1: T = Grand mean + ICC * (Subject score - Grand mean)
+Step 2: SEP = SD of both measurements * sqrt(1-ICC^2)
+
+Here I calculate the proportion of subjects that move more than one standard error of prediction (SEP) in t2 compared to t1 for each measure.
+
+This is odd to think about because the larger the ICC of a measure the smaller the SEP. So very small differences between the two time points can be categorized as 'meaningful' based on the tiny SEP.
+
+What you are interested in is not necessarily whether individuals change at all between the two time points though. You want to know if this change is systematic in one direction.
+
+Here I calculate the proportion of people showing 'meaningful' changes in one direction or the other.
+To integrate both of these direction I subtracted one from the other and filtered the variables that have more than 5% of the participants showing meaningful change in one direction over the other (so if a variable has 10 participants showing difference in one and 10 in the other direction this would cancel out but a variables with 15 people showing a positive and 5 negative change would remain).
+
+```{r}
+get_ind_ci = function(dv_var){
+  matched = match_t1_t2(dv_var)
+  grand_mean = mean(matched$score)
+  grand_sd = sd(matched$score)
+  dv_icc = get_icc(dv_var)
+  sep = grand_sd * sqrt(1-(dv_icc^2))
+  matched = matched %>% 
+    spread(time, score) %>%
+    rename("t1"="1", "t2"="2") %>%
+    mutate(true_score = grand_mean+(dv_icc*(t1-grand_mean)),
+           ci_up = true_score+(1.96*sep),
+           ci_low = true_score-(1.96*sep),
+           t2_above_ci = ifelse(t2>ci_up,1,0),
+           t2_below_ci = ifelse(t2<ci_low,1, 0))
+    return(matched)
+}
+
+get_prop_out_ci = function(dv_var){
+  get_ind_ci(dv_var) %>%
+    summarise(prop_above_ci = sum(t2_above_ci)/n(),
+              prop_below_ci = sum(t2_below_ci/n()))
+}
+
+#Create df of point estimate reliabilities
+ind_ci_df <- data.frame(prop_above_ci = rep(NA, length(numeric_cols)),
+                        prop_below_ci = rep(NA, length(numeric_cols)))
+
+row.names(ind_ci_df) <- numeric_cols
+
+for(i in 1:length(numeric_cols)){
+    ind_ci_df[numeric_cols[i], 'prop_above_ci'] <- get_prop_out_ci(numeric_cols[i])$prop_above_ci 
+    ind_ci_df[numeric_cols[i], 'prop_below_ci'] <- get_prop_out_ci(numeric_cols[i])$prop_below_ci 
+}
+
+ind_ci_df$dv = row.names(ind_ci_df)
+row.names(ind_ci_df) = seq(1:nrow(ind_ci_df))
+ind_ci_df$task = 'task'
+ind_ci_df[grep('survey', ind_ci_df$dv), 'task'] = 'survey'
+ind_ci_df[grep('holt', ind_ci_df$dv), 'task'] = "task"
+ind_ci_df = ind_ci_df %>%
+  select(dv, task, prop_above_ci, prop_below_ci)
+
+mean_diff_df = ind_ci_df %>%
+  mutate(prop_one_direction = prop_above_ci-prop_below_ci) %>%
+  filter(abs(prop_one_direction)>0.05) %>%
+  arrange(-abs(prop_one_direction))
+
+mean_diff_df
+
+write.csv(mean_diff_df, '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/mean_diff_df.csv')
+```
+
+This doesn't make it easier to interpret whether it is a performance improvement or decline.
+In fact 'performance' isn't even necessarily the correct term here.
+Using the valence assignments of the measures look at whether it translates to an increase or decrease in self-regulation.
+Of the 66 this makes sense for 54 variables.
+
+```{r warning=FALSE, message=FALSE}
+mean_diff_df = read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/mean_diff_df.csv')
+
+table(as.character(mean_diff_df$valence), useNA = "ifany")
+
+mean_diff_df %>%
+  mutate(sc_increase = ifelse(prop_one_direction>0&valence=="Pos",1,ifelse(prop_one_direction<0&valence=="Neg",1,0)),
+         sc_decrease = ifelse(prop_one_direction>0&valence=="Neg",1,ifelse(prop_one_direction<0&valence=="Pos",1,0))) %>%
+summarise(sum_sc_increase = sum(sc_increase,na.rm=T),
+          sum_sc_decrease = sum(sc_decrease,na.rm=T))
+
+```
+
+Variables that show more than 5% difference in a direction do not depend on whether they translate to a self control increase or decrease.
+
+```{r}
+chisq.test(matrix(data = c(23,54-23,31,54-31), nrow=2))
+```
+
+Do they differ depending on whether they are task or survey variables? No.
+
+```{r}
+chisq.test(matrix(data = c(5,74-5,61,372-61), nrow=2))
+```
+
+```{r}
+rm(mean_diff_df)
 ```

### 2018-05-01 code/SRO_Retest_Analyses.Rmd
refactoring

@@
   xlab("")+
-  theme(legend.title = element_blank())
-
-ggsave('Bootstrap_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 6, units = "in", limitsize = FALSE)
+  theme(legend.title = element_blank(),
+        legend.position = 'bottom',
+        legend.text = element_text(size=16),
+        strip.text = element_text(size=16),
+        axis.text = element_text(size = 16),
+        text = element_text(size=16))+
+  guides(fill = guide_legend(ncol = 2))
+
+ggsave('Bootstrap_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 14, height = 10, units = "in", limitsize = FALSE)
+```
+
+```{r}
+tmp2 = measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(ddm_task == 1, 
+         overall_difference != "condition") %>%
+  drop_na() %>%
+  left_join(rel_df[,c("dv", "icc", "spearman")], by = 'dv')
+
+tmp2 %>%
+  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy","other", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy", "Other","Drift Rate", "Threshold", "Non-decision"))))+
+  geom_boxplot()+
+  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
+  theme_bw()+
+  ylab("ICC")+
+  xlab("")+
+  theme(legend.title = element_blank(),
+        legend.position = 'bottom',
+        legend.text = element_text(size=16),
+        strip.text = element_text(size=16),
+        axis.text = element_text(size = 16),
+        text = element_text(size=16))+
+  guides(fill = guide_legend(ncol = 2))
+
+ggsave('PointEst_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 14, height = 10, units = "in", limitsize = FALSE)
 ```

### 2018-05-02 code/SRO_Retest_Analyses.Rmd
fyp slides

@@
 
-demog_rel_df %>%
+demog_rel_df = demog_rel_df %>%
   mutate(var = row.names(.)) %>%
@@
   arrange(-icc)
+
+demog_rel_df
+```
+
+```{r}
+sjt.df(demog_rel_df %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/demog_rel_table.doc")
 ```
@@
 t1_dvs = read.csv(paste0(retest_data_path, 't1_tbt_dvs.csv'))
+t1_dvs = t1_dvs %>% select(-X) 
 t2_dvs = read.csv(paste0(retest_data_path, 't2_tbt_dvs.csv'))
+t2_dvs = t2_dvs %>% select(-X)
+
+t1_dvs = t1_dvs %>% mutate(sub_id = as.character(sub_id))
+t2_dvs = t2_dvs %>% mutate(sub_id = as.character(sub_id))
+
+unique(t2_dvs$sub_id)
+
+t1_dvs[,c("acc","sub_id", "breaks")] %>%
+  left_join(t2_dvs[,c("acc","sub_id", "breaks")], by = c("sub_id", "breaks")) %>%
+  distinct()
 ```

### 2018-05-02 code/SRO_Retest_Analyses.Rmd
added new intratrial analyses

@@
   arrange(task,-pct_sig_time_effect) %>%
-  arrange(mean_pearson) %>%
+  arrange(mean_pearson)
 
@@
 
-write.csv(mean_diff_df, '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/mean_diff_df.csv')
+# write.csv(mean_diff_df, '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/mean_diff_df.csv')
 ```
@@
 t1_dvs = read.csv(paste0(retest_data_path, 't1_tbt_dvs.csv'))
+t2_dvs = read.csv(paste0(retest_data_path, 't2_tbt_dvs.csv'))
+
 t1_dvs = t1_dvs %>% select(-X)
-t2_dvs = read.csv(paste0(retest_data_path, 't2_tbt_dvs.csv'))
 t2_dvs = t2_dvs %>% select(-X)
-
-t1_dvs = t1_dvs %>% mutate(sub_id = as.character(sub_id))
-t2_dvs = t2_dvs %>% mutate(sub_id = as.character(sub_id))
-
-unique(t2_dvs$sub_id)
-
-t1_dvs[,c("acc","sub_id", "breaks")] %>%
-  left_join(t2_dvs[,c("acc","sub_id", "breaks")], by = c("sub_id", "breaks")) %>%
-  distinct()
 ```
@@
 ```{r warning=FALSE, message=FALSE}
-trial_num_rel_df = read.csv(paste0(retest_data_path, 'trial_num_rel_df_tbt.csv'))
+# trial_num_rel_df = read.csv(paste0(retest_data_path, 'trial_num_rel_df_tbt.csv'))
 

### 2018-05-03 code/SRO_Retest_Analyses.Rmd
wrapping up analyses using new release and draft

@@
 tmp = tmp%>%
+  select(-median_spearman, -min_spearman, -max_spearman) %>%
   mutate(task_name = gsub("_", " ", task_name),
@@
   ylab("ICC")+
-  theme(legend.title = element_blank())+
+  theme(legend.title = element_blank(),
+        legend.position = 'bottom')+
   scale_color_manual(values = cols,
-                     breaks = c("Accuracy", "Missed percentage", "Cue switch cost Acc (100)", "Cue switch cost Acc (900)", "Task switch cost Acc (100)", "Task switch cost Acc (900)", "Average RT error", "SD RT error", "Average RT correct", "SD RT correct",  "Cue switch cost RT (100)", "Cue switch cost RT (900)", "Task switch cost RT (100)", "Task switch cost RT (900)"))
+                     breaks = c("Average RT error", "Accuracy", "SD RT error", "Missed percentage", "Average RT correct", "Cue switch cost Acc (100)", "SD RT correct", "Cue switch cost Acc (900)", "Cue switch cost RT (100)", "Task switch cost Acc (100)", "Task switch cost RT (100)", "Task switch cost Acc (900)", "Task switch cost RT (900)"))+
+  ylim(-1,1)+
+  guides(color = guide_legend(ncol=2, byrow=T))
 
 ggsave('Intrameasure_Trialnum_Dependendence.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in", dpi = 100)
-```
-
-```{r}
-rel_df[c(rel_df$dv %in% grep('threebytwo', rel_df$dv, value = TRUE)),]
 ```
@@
   filter(ddm_task == 1, 
-         overall_difference != "condition") %>%
+         overall_difference != "condition",
+         rt_acc != 'other') %>%
   drop_na() %>%
@@
 tmp %>%
-  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy","other", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy", "Other","Drift Rate", "Threshold", "Non-decision"))))+
+  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
   geom_boxplot()+
@@
         text = element_text(size=16))+
-  guides(fill = guide_legend(ncol = 2))
+  guides(fill = guide_legend(ncol = 2))+
+  scale_fill_discrete(breaks=c("Drift Rate", "Threshold", "Non-decision", "Response Time", "Accuracy"))
 
@@
   filter(ddm_task == 1, 
-         overall_difference != "condition") %>%
+         overall_difference != "condition",
+         rt_acc != "other") %>%
   drop_na() %>%
@@
 tmp2 %>%
-  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy","other", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy", "Other","Drift Rate", "Threshold", "Non-decision"))))+
+  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
   geom_boxplot()+
@@
             max_spearman = max(spearman),
-            num_measures = n()/1000)%>%
+            num_measures = n()/1000,
+            mean_num_trials = round(mean(num_all_trials)))%>%
   arrange(-median_icc, -median_spearman)
@@
 tmp = tmp%>%
+  select(-min_spearman, -max_spearman,-median_spearman) %>%
   mutate(task_name = gsub("_", " ", task_name),
-         task_name = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", task_name, perl=TRUE))
+         task_name = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", task_name, perl=TRUE),
+         task_name = gsub("Survey", "", task_name))
 

### 2018-05-04 code/SRO_Retest_Analyses.Rmd
added closer look at diff score reliability

@@
 names(retest_demog)[which(names(retest_demog) == 'X')] <-'sub_id'
+
+summary(test_demog %>%
+          select(Sex, Age))
 
@@
          shape = guide_legend(override.aes = list(size=18)))+
-  xlab("Reliability")+
+  xlab("Retest Reliability")+
   ylab("")+
@@
         axis.title.x = element_text(size=30)) + 
-  xlab("Reliability")+
+  xlab("Retest Reliability")+
   ylab("")+
@@
 ```{r}
-summary(lm(retest_reliability ~ task,rel_comp))
+summary(rel_comp$sample_size[rel_comp$task == "survey"])
+summary(rel_comp$sample_size[rel_comp$task == "task"])
 ```
@@
             median_spearman = median(spearman),
-            min_icc = min(icc),
-            max_icc = max(icc),
+            icc_2.5 = quantile(icc, probs = 0.025),
+            icc_97.5 = quantile(icc, probs = 0.975),
             min_spearman = min(spearman),
@@
   formatRound(columns=c('median_spearman', 'median_icc',
-                        'min_spearman', 'min_icc',
-                        'max_spearman', 'max_icc'), digits=3)
+                        'min_spearman', 'icc_2.5',
+                        'max_spearman', 'icc_97.5'), digits=3)
 ```
@@
 
+"consistent with the summing of variance in the difference score"
+
+```{r}
+tmp = measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(ddm_task == 1, 
+         overall_difference != "condition",
+         rt_acc != 'other') %>%
+  drop_na() %>%
+  left_join(boot_df[,c("dv", "icc", "var_subs","var_ind", "var_resid")], by = 'dv') %>%
+  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid),
+         var_ind_pct = var_ind/(var_subs+var_ind+var_resid), 
+         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)) %>%
+  select(-task, -ddm_task, -num_all_trials, -var_resid, -var_subs, -var_ind) %>%
+  gather(key, value, -dv, -overall_difference, -raw_fit, -rt_acc, -icc)
+
+tmp %>%
+  filter(key == "var_resid_pct") %>%
+  ggplot(aes(raw_fit, value, fill=overall_difference))+
+  geom_boxplot()
+
+summary(lmer(value  ~ overall_difference*raw_fit + (1|dv), data=tmp %>% filter(key=="var_resid_pct")))
+
+#Simple effects
+summary(lmer(value  ~ overall_difference + (1|dv), data=tmp %>% filter(key=="var_resid_pct", raw_fit== "EZ")))
+
+summary(lmer(value  ~ overall_difference + (1|dv), data=tmp %>% filter(key=="var_resid_pct", raw_fit== "raw")))
+
+summary(lmer(value  ~ overall_difference + (1|dv), data=tmp %>% filter(key=="var_resid_pct", raw_fit== "hddm")))
+```
+
+Checking Rogosa's claim that ‘Difference scores are reliable when individual differences in true change exist.’
+How do we measure ‘individual difference in true change’ 
+1.between subject variability in difference score distributions
+2.within subject variance in icc
+Using 2 (because comparable between subject variance across different measures would be hard)
+Expecting to see: positive correlation between mean icc and mean var_ind_pct
+Result: The correlation between mean icc and mean var ind pct is NOT significant BUT looking at the distribution of mean var ind pct there is not a lot of variability t
+
+```{r}
+tmp = tmp %>%
+  spread(key, value) %>%
+  group_by(dv) %>%
+  summarise(mean_var_ind_pct = mean(var_ind_pct),
+            mean_var_subs_pct = mean(var_subs_pct),
+            mean_icc = mean(icc)) %>%
+  left_join(measure_labels, by='dv')
+
+tmp %>%
+  filter(overall_difference == 'difference') %>%
+  ggplot(aes(mean_var_ind_pct, mean_icc))+
+  geom_point()+
+  geom_abline(slope=1, intercept=0)+
+  geom_smooth(method = "lm")
+
+summary(lm(mean_icc ~ mean_var_ind_pct,data=tmp %>%
+  filter(overall_difference == 'difference')))
+
+tmp %>%
+  filter(overall_difference == 'difference') %>%
+  ggplot(aes(mean_var_ind_pct))+
+  geom_density()
+
+summary(tmp$mean_var_ind_pct[tmp$overall_difference == "difference"])
+summary(tmp$mean_var_subs_pct[tmp$overall_difference == "difference"])
+
+tmp = tmp %>% filter(overall_difference == 'difference')
+t.test(tmp$mean_var_ind_pct, tmp$mean_var_subs_pct, paired=T)
+```
+
 Comparing raw vs ddm in overall estimates: EZ is significantly better than HDDM and comparable to raw estimates.
@@
 
+### Number of items
+
+Does number of items in a survey have a significant effect on the average ICC of survey measures? No.
+
+```{r warning=FALSE, message=FALSE}
+tmp = measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(task == 'survey') %>%
+  # left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
+  left_join(boot_df[,c("dv", "spearman","icc")], by='dv') %>%
+  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
+  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
+  select(-extra_1, -extra_2)
+
+# summary(lm(icc ~ num_all_trials, data = tmp))
+summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
+```
+
+```{r warning=FALSE, message=FALSE}
+measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(task == 'task') %>%
+  # left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
+  left_join(boot_df[,c("dv", "spearman","icc")], by='dv') %>%
+  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
+  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
+  select(-extra_1, -extra_2) %>%
+  ggplot(aes(num_all_trials, icc))+
+  geom_point()+
+  geom_smooth(method="lm")+
+  theme_bw()+
+  xlab("Number of trials")+
+  ylab("ICC")
+```
+
 ## Transformation effects
@@
 
-test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/t1_data/meaningful_variables_clean.csv')
+test_data <- read.csv(paste0(retest_data_path,'t1_data/meaningful_variables_clean.csv'))
 test_data$X <- as.character(test_data$X)
 names(test_data)[which(names(test_data) == 'X')] <-'sub_id' 
-retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/meaningful_variables_clean.csv')
+retest_data <- read.csv(paste0(retest_data_path,'meaningful_variables_clean.csv'))
 retest_data$X <- as.character(retest_data$X)
@@
 
-```{r}
+```{r warning=FALSE, message=FALSE}
 ggplotly(rel_df_mngfl %>%

### 2018-05-07 code/SRO_Retest_Analyses.Rmd
building new report
created new report

@@
 
+```{r}
+tmp = measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(ddm_task == 1, 
+         overall_difference != "condition",
+         rt_acc != 'other') %>%
+  drop_na() %>%
+  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')
+```
+
 Comparing raw vs ddm in overall estimates: EZ is significantly better than HDDM and comparable to raw estimates.
@@
 ```
-
-## Transformation effects
-
-All results reported above were for non-transformed dependent variables.
-
-We could compare the reliability (point) estimates for meaningful variables that have been transformed in the full dataset and transformed the same way in the retest dataset as well.
-
-```{r}
-test_data_tmp <- test_data
-retest_data_tmp <- retest_data
-
-test_data <- read.csv(paste0(retest_data_path,'t1_data/meaningful_variables_clean.csv'))
-test_data$X <- as.character(test_data$X)
-names(test_data)[which(names(test_data) == 'X')] <-'sub_id' 
-retest_data <- read.csv(paste0(retest_data_path,'meaningful_variables_clean.csv'))
-retest_data$X <- as.character(retest_data$X)
-names(retest_data)[which(names(retest_data) == 'X')] <-'sub_id'
-retest_data = retest_data[retest_data$sub_id %in% test_data$sub_id,]
-```
-
-```{r}
-numeric_cols_mngfl = c()
-
-for(i in 1:length(names(test_data))){
-  if(is.numeric(test_data[,i]) & names(test_data)[i] %in% names(retest_data)){
-    numeric_cols_mngfl <- c(numeric_cols_mngfl, names(test_data)[i])
-  }
-}
-
-rel_df_mngfl <- data.frame(icc = rep(NA, length(numeric_cols_mngfl)))
-
-row.names(rel_df_mngfl) <- numeric_cols_mngfl
-
-for(i in 1:length(numeric_cols_mngfl)){
-  rel_df_mngfl[numeric_cols_mngfl[i], 'icc'] <- get_icc(numeric_cols_mngfl[i])
-}
-
-rel_df_mngfl$dv = row.names(rel_df_mngfl)
-row.names(rel_df_mngfl) = seq(1:nrow(rel_df_mngfl))
-rel_df_mngfl$task = 'task'
-rel_df_mngfl[grep('survey', rel_df_mngfl$dv), 'task'] = 'survey'
-rel_df_mngfl[grep('holt', rel_df_mngfl$dv), 'task'] = "task"
-rel_df_mngfl
-```
-
-```{r warning=FALSE, message=FALSE}
-ggplotly(rel_df_mngfl %>%
-  filter(grepl("logTr", dv)) %>%
-  mutate(dv = gsub(".ReflogTr", "", dv),
-         dv = gsub(".logTr", "", dv)) %>%
-  left_join(rel_df[,c("dv", "icc")], by="dv") %>%
-  ggplot(aes(icc.x, icc.y, color=task, label=dv))+
-  geom_point()+
-  theme_bw()+
-  xlab("Reliability for transformed variable")+
-  ylab("Reliability for raw variable")+
-  geom_abline(slope=1, intercept=0),
-  label=dv)
-```

### 2018-05-14 code/SRO_Retest_Analyses.Rmd
plots for frisem

@@
 
+for(i in 1:nrow(duplicate_items)){
+  duplicate_items$t1_t1_cor[i] = abs(cor(scale(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])]),
+                                  scale(duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])])))
+
+  duplicate_items$t2_t2_cor[i] = abs(cor(scale(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])]),
+                                  scale(duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])])))
+
+  duplicate_items$t1_t2_cor[i] = abs(cor(scale(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])]),
+                                  scale(duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])])))
+
+  duplicate_items$t2_t1_cor[i] = abs(cor(scale(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])]),
+                                  scale(duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])])))
+
+  duplicate_items$t1_t1_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])],
+                      duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])]))$rho[2])
+
+  duplicate_items$t2_t2_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])],
+                      duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])]))$rho[2])
+
+  duplicate_items$t1_t2_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])],
+                      duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])]))$rho[2])
+
+  duplicate_items$t2_t1_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])],
+                      duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])]))$rho[2])
+}
+
 duplicate_items
@@
 ```{r}
+summary(duplicate_items$t1_t1_cor)
+summary(duplicate_items$t2_t2_cor)
+summary(duplicate_items$t1_t2_cor)
+summary(duplicate_items$t2_t1_cor)
+
 summary(duplicate_items$t1_t1_polycor)
@@
 summary(duplicate_items$t2_t1_polycor)
+```
+
+Time 1: item 1 - item 2
+Time 1 item 1 - time 2 item 2
+Time 2 item 1 - time 1 item 2
+Time 2: item 1 - item 2
+
+```{r}
+tmp = duplicate_items_data_t1 %>%
+  gather(key, value, -worker)
+
+tmp2 = duplicate_items_data_t2 %>%
+  gather(key, value, -worker)
+
+tmp = duplicate_items %>%
+  select(item1_ID, item2_ID) %>%
+  left_join(tmp, by = c("item1_ID" = "key")) %>%
+  left_join(tmp, by = c("item2_ID" = "key", "worker" = "worker")) %>%
+  rename(item1_time1 = value.x, item2_time1 = value.y) %>%
+  left_join(tmp2, by = c("item1_ID" = "key", "worker" = "worker")) %>%
+  left_join(tmp2, by = c("item2_ID" = "key", "worker" = "worker")) %>%
+  rename(item1_time2 = value.x, item2_time2 = value.y) %>%
+  group_by(item1_ID) %>%
+  mutate(item1_time1 = scale(item1_time1),
+         item1_time2 = scale(item1_time2),
+         item2_time1 = scale(item2_time1),
+         item2_time2 = scale(item2_time2)) %>%
+  ungroup()
+
+p1 = tmp %>%
+  ggplot(aes(item1_time1, item2_time1, col=item1_ID))+
+  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
+  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
+  theme(legend.position = "none")+
+  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
+  xlab("Item 1 T1")+
+  ylab("Item 2 T1")
+
+p2 = tmp %>%
+  ggplot(aes(item1_time1, item2_time2, col=item1_ID))+
+  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
+  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
+  theme(legend.position = "none")+
+  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
+  xlab("Item 1 T1")+
+  ylab("Item 2 T2")
+
+p3 = tmp %>%
+  ggplot(aes(item1_time2, item2_time1, col=item1_ID))+
+  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
+  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
+  theme(legend.position = "none")+
+  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
+  xlab("Item 1 T2")+
+  ylab("Item 2 T1")
+
+p4 = tmp %>%
+  ggplot(aes(item1_time2, item2_time2, col=item1_ID))+
+  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
+  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
+  theme(legend.position = "none")+
+  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
+  xlab("Item 1 T2")+
+  ylab("Item 2 T2")
+
+ggplotly(p1)
+
+grid.arrange(p1, p2, p3, p4, ncol=2)
+
+rm(tmp, tmp2)
 ```

### 2018-05-14 code/SRO_Retest_Analyses.Rmd
frisem plots

@@
 
-```{r}
+```{r warning=FALSE, message=FALSE}
 tmp = duplicate_items_data_t1 %>%
@@
          item2_time1 = scale(item2_time1),
-         item2_time2 = scale(item2_time2)) %>%
+         item2_time2 = scale(item2_time2),
+         item1_time1 = ifelse(item1_ID == "mpq_control_survey.13", item1_time1*-1, item1_time1),
+         item1_time2 = ifelse(item1_ID == "mpq_control_survey.13", item1_time2*-1, item1_time2)) %>%
   ungroup()
@@
 
-ggplotly(p1)
-
-grid.arrange(p1, p2, p3, p4, ncol=2)
-
-rm(tmp, tmp2)
+p5 = arrangeGrob(p1, p2, p3, p4, ncol=2)
+
+ggsave('DataCheckOverlappingItems.jpg', p5, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 300)
+
+rm(tmp, tmp2, p1, p2, p3, p4, p5)
 ```
@@
 summary(rel_comp$sample_size[rel_comp$task == "task"])
+
+rel_comp %>%
+  group_by(task) %>%
+  summarise(mean_sample_size = mean(sample_size),
+            sem_sample_size = sem(sample_size)) %>%
+  ggplot(aes(task,mean_sample_size,col=task))+
+  geom_point(size=5)+
+  geom_errorbar(aes(ymin=mean_sample_size-sem_sample_size, ymax=mean_sample_size+sem_sample_size), width = 0, size=2)+
+  xlab("")+
+  ylab("Sample size")+
+  theme(legend.position = 'none',
+        axis.text.x = element_text(size=14),
+        axis.title.y = element_text(size=14))
+
+ggsave('LitReviewSampleSize.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 3, height = 5, units = "in", limitsize = FALSE, dpi = 300)
 ```
@@
   ylab("Retest reliability")
+
+ggsave('LitReviewRelBySampleSize.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 300)
 ```
@@
   group_by(task) %>%
-  summarise(count=n())
+  summarise(count=n()) %>%
+  mutate(total_num_vars = c(74, 372),
+         prop = count/total_num_vars) %>%
+  ggplot(aes(task, prop, fill=task))+
+  geom_bar(stat="identity", alpha=0.5, width=0.5)+
+  theme(legend.position = "none", 
+        axis.text.x = element_text(size=14),
+        axis.title.y = element_text(size=14))+
+  ylab("Proportiono of samples")+
+  xlab("")
+
+ggsave('PropTimeEffects.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 3, height = 5, units = "in", limitsize = FALSE, dpi = 300)
+
 ```

### 2018-05-14 code/SRO_Retest_Analyses.Rmd
frisem prep

@@
   ylab("Proportiono of samples")+
-  xlab("")
+  xlab("")+
+  ylim(0,1)
 
@@
 mean_diff_df
-
-# write.csv(mean_diff_df, '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/mean_diff_df.csv')
 ```
@@
 
+```{r}
+valence_df = read.csv(paste0(retest_data_path, 'DV_valence.csv'), header = F)
+valence_df = valence_df %>% rename(dv = V1, valence = V2)
+valence_df$task = 'task'
+valence_df[grep('survey', valence_df$dv), 'task'] = 'survey'
+valence_df[grep('holt', valence_df$dv), 'task'] = "task"
+
+valence_df = valence_df %>% filter(dv %in% retest_report_vars)
+with(valence_df, table(task, valence))
+#Comparable level of valences for task and survey measures
+chisq.test(with(valence_df, table(task, valence)))
+```
+
 ```{r warning=FALSE, message=FALSE}
-mean_diff_df = read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/mean_diff_df.csv')
-
-table(as.character(mean_diff_df$valence), useNA = "ifany")
 
 mean_diff_df %>%
-  mutate(sc_increase = ifelse(prop_one_direction>0&valence=="Pos",1,ifelse(prop_one_direction<0&valence=="Neg",1,0)),
-         sc_decrease = ifelse(prop_one_direction>0&valence=="Neg",1,ifelse(prop_one_direction<0&valence=="Pos",1,0))) %>%
+  left_join(valence_df, by = c("dv", "task")) %>%
+  mutate(sc_increase = ifelse(prop_one_direction>0&valence==1,1,ifelse(prop_one_direction<0&valence==-1,1,0)),
+         sc_decrease = ifelse(prop_one_direction>0&valence==-1,1,ifelse(prop_one_direction<0&valence==1,1,0))) %>%
+  group_by(task) %>%
 summarise(sum_sc_increase = sum(sc_increase,na.rm=T),
-          sum_sc_decrease = sum(sc_decrease,na.rm=T))
-
+          sum_sc_decrease = sum(sc_decrease,na.rm=T)) %>%
+  gather(key, value, -task) %>%
+  mutate(total_vars = c(74, 372, 74, 372),
+         prop = value/total_vars) %>%
+  ggplot(aes(key, prop, group=task, fill=task))+
+  geom_bar(stat = "identity", position = position_dodge(), alpha = 0.5)+
+  theme(legend.title = element_blank())+
+  xlab("")+
+  ylab("Proportion")+
+  ylim(0, 1)+
+  scale_x_discrete(breaks = c("sum_sc_decrease", "sum_sc_increase"),
+                   labels = c("Self-control decrease", "Self-control increase"))
+
+ggsave('PropTimeEffectsValence.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 5, height = 5, units = "in", limitsize = FALSE, dpi = 300)
 ```
@@
 ```{r}
-chisq.test(matrix(data = c(5,74-5,61,372-61), nrow=2))
+chisq.test(matrix(data = c(5,74-5,60,372-60), nrow=2))
 ```

### 2018-05-14 code/SRO_Retest_Analyses.Rmd
frisem figures

@@
   geom_bar(stat = "identity", position = position_dodge(), alpha = 0.5)+
-  theme(legend.title = element_blank())+
+  theme(legend.title = element_blank(),
+        axis.title.y = element_text(size=14),
+        axis.text.x = element_text(size=14))+
   xlab("")+
@@
 
-ggsave('PropTimeEffectsValence.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 5, height = 5, units = "in", limitsize = FALSE, dpi = 300)
+ggsave('PropTimeEffectsValence.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 7, height = 5, units = "in", limitsize = FALSE, dpi = 300)
 ```
@@
 
-```{r}
+```{r eval=FALSE}
 hr_merge = merge(t1_dvs, t2_dvs, by = c("sub_id", "breaks"))
@@
 
-write.csv(trial_num_rel_df, paste0(retest_data_path, 'trial_num_rel_df_tbt.csv'))
+# write.csv(trial_num_rel_df, paste0(retest_data_path, 'trial_num_rel_df_tbt.csv'))
 ```
@@
 ```{r warning=FALSE, message=FALSE}
-# trial_num_rel_df = read.csv(paste0(retest_data_path, 'trial_num_rel_df_tbt.csv'))
+trial_num_rel_df = read.csv(paste0(retest_data_path, 'trial_num_rel_df_tbt.csv'))
 
@@
 tmp2 %>%
+  filter(overall_difference == "overall") %>%
   ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
   geom_boxplot()+
-  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
+  # facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
   theme_bw()+
@@
 
-ggsave('PointEst_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 14, height = 10, units = "in", limitsize = FALSE)
+ggsave('PointEst_DDM_Comp_OverallOnly.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 5, units = "in", limitsize = FALSE)
 ```

### 2018-05-14 code/FrisemFigures.R

@@ -1,0 +1,70 @@
+lit_review %>%
+  filter(task_group == 'stroop') %>%
+  ggplot(aes(y = var, x = retest_reliability)) +
+  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"),
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180, size = 12),
+        axis.text.y = element_text(size = 11),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom') +
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))
+ggsave('Lit_Review_Example.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", dpi=300)
+
+
+
+#######################################################
+#######################################################
+#######################################################
+tmp = rel_df %>%
+  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
+         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
+         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
+  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
+  mutate(dv = factor(dv, levels = dv[order(task)])) %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  arrange(task_group, var_subs_pct) %>%
+  mutate(rank = row_number()) %>%
+  arrange(task, task_group, rank) %>%
+  gather(key, value, -dv, -task_group, -var, -task, -rank) %>%
+  ungroup()%>%
+  mutate(task_group = gsub("_", " ", task_group),
+         var = gsub("_", " ", var)) %>%
[…]

### 2018-05-16 code/SRO_Retest_Analyses.Rmd
frisem practice

@@
         axis.title.y = element_text(size=14))+
-  ylab("Proportiono of samples")+
+  ylab("Proportiono of bootstrap samples")+
   xlab("")+
@@
   xlab("")+
-  ylab("Proportion")+
+  ylab("Proportion of measures")+
   ylim(0, 1)+

### 2018-05-16 code/SRO_Retest_Analyses.Rmd
frisem prep

@@
 
+ggsave('DaysBtwEffect.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 300)
 ```
@@
 ```{r}
-rel_comp %>% 
+ggplotly(rel_comp %>% 
   ggplot(aes(sample_size, retest_reliability, color=task))+
@@
   xlab("Sample Size")+
-  ylab("Retest reliability")
+  ylab("Retest reliability"))
 
@@
 tmp = comp_lit_pred_out %>%
-  select(-.n) %>%
+  select(-.n, -m_lit, -m_boot) %>%
   gather(key, value) %>%
@@
 
-tmp$stat = as.factor(tmp$stat)
-levels(tmp$stat) <- c("coefficient", expression(r^"2"))
+# tmp$stat = as.factor(tmp$stat)
+# levels(tmp$stat) <- c("coefficient", expression(r^"2"))
 
@@
   geom_density(alpha = 0.5, position='identity', color=NA)+
-  facet_grid(.~stat, scales='free', labeller = label_parsed)+
-  scale_fill_discrete(breaks=c("boot","lit"),
+  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
+  scale_fill_manual(breaks=c("boot","lit"),
                        labels=c("Empirical", "Literature"),
-                      name="Prediction")+
-  xlab('')+
-  ylab('')
-
-ggsave('Lit_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 10, height = 4, units = "in", limitsize = FALSE, dpi = 100)
+                      name="Predictor",
+                      values = c("white", "orange"))+
+  xlab('Variance Explained')+
+  ylab('Density')+
+  xlim(0,1)+
+  ylim(0,40)
+
+ggsave('LitOnly_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 300)
+
+tmp %>%  
+  ggplot(aes(value, fill=sample))+
+  geom_density(alpha = 0.5, position='identity', color=NA)+
+  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
+  scale_fill_manual(breaks=c("boot","lit"),
+                       labels=c("Empirical", "Literature"),
+                      name="Predictor",
+                      values = c("purple", "orange"))+
+  xlab('Variance Explained')+
+  ylab('Density')+
+  xlim(0,1)+
+  ylim(0,40)
+
+ggsave('LitAndBoot_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 300)
 ```

### 2018-05-16 code/SRO_Retest_Analyses.Rmd
added multiple test correction for days effect

@@
 I can run it separately for each dv to see if all difference score distributions are affected the same way depending on the days between completion.
+But since we are running so many tests we need to correct for multiple comparisons.
+How many of these tests are significant FDR correcting?
+None.
 
@@
 
-sig_days_effect = t1_2_difference %>%
+days_effect  = t1_2_difference %>%
   group_by(dv) %>%
-  do(get_delay_effect(.)) %>%
-  filter(pval<0.05)
-
-sig_days_effect
+  do(get_delay_effect(.))
+
+#Correct p-values for multiple comparisons
+sum(p.adjust(days_effect$pval, method = "fdr") < 0.05)
 ```

### 2018-05-16 code/SRO_Retest_Analyses.Rmd
frisem prep

@@
   ggplot()+
-  geom_smooth(aes(as.numeric(days_btw), abs(difference), group=factor(dv)), method='lm', se=FALSE)+
+  geom_smooth(aes(as.numeric(days_btw), abs(difference), group=factor(dv)), method='lm', se=FALSE, color = 'grey', alpha = 0.5)+
   geom_smooth(aes(as.numeric(days_btw), abs(difference)), method='lm', color = "black", se=FALSE)+
@@
 
-For visualization I used to summarize the difference scores per person by looking at the average difference per task per subject and plot that against the number of days between completion.
-This yields multiple points for each value on x representing the average difference per task for each subject.
-But variables within a task could go in different directions (e.g.
-if patient proportion increases discount rate decreases) so this doesn't seem like a good idea)
-
-Instead I now plot all the data grouping by dependant variable and coloring depending on whether the difference score distribution for that variable has a significant slope when regressed over days between.
-The black is the main effect for the large multilevel model (this is the same plot as above colored by whether the difference score distribution for each dv has a significant slope depending on days between).
-
-```{r}
-t1_2_difference %>%
-  mutate(sig_days_effect = ifelse(dv %in% sig_days_effect$dv, 1, 0))%>%
-  arrange(-sig_days_effect) %>%
-  ggplot()+
-  stat_smooth (aes(as.numeric(days_btw), abs(difference), 
-                  group=factor(dv, levels=unique(dv[order(sig_days_effect)]), ordered=TRUE), 
-                  color=factor(sig_days_effect, levels = c(1,0))),geom="line", alpha=0.5, method='lm')+
-  geom_smooth(aes(as.numeric(days_btw), abs(difference)), method='lm', color = "black", se=FALSE)+
-  theme(legend.title = element_blank())+
-  xlab('Days between completion')+
-  ylab('Scaled difference score')+
-  scale_color_discrete(breaks=c(0,1),
-                       labels=c("NS", "Sig"))
-
-ggsave('DaysBtwEffect.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 100)
-```
-
-Conclusion: The average difference between the scores of a measure if anything decreases with the increased delay.
-This fixed effect masks the simple effect for each dv.
-When looked at individually only 10 variables show a dependence on days between completion.
-While 7 of them show decreasing differences depending on days between 3 do show increasing differences.
-This suggests that the lack of stricter control over the days between completion of the measurement does not have a large effect on the stability of most measures.
-
-effect of whether days between leads to a sig difference on reliability of that variable? plot coef of sig_day_effect over rel_df point estimate
-
-Do the variables that show significant dependence on the delay between the completion times have systematically lower/higher reliability?
-Looking at the reliability point estimate over the size of the delay effect.
-There are very few variables to compare anyway but regardless doesn't look conclusive/concerning.
-
-```{r}
-#Create df of point estimate reliabilities
-rel_df <- data.frame(spearman = rep(NA, length(numeric_cols)),
-                     icc = rep(NA, length(numeric_cols)),
-                     pearson = rep(NA, length(numeric_cols)),
-                     partial_eta_sq = rep(NA, length(numeric_cols)),
-                     sem = rep(NA, length(numeric_cols)),
-                     var_subs = rep(NA, length(numeric_cols)),
-                     var_ind = rep(NA, length(numeric_cols)),
-                     var_resid = rep(NA, length(numeric_cols)))
-
-row.names(rel_df) <- numeric_cols
-
-for(i in 1:length(numeric_cols)){
-  rel_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i]) 
-  rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
-  rel_df[numeric_cols[i], 'pearson'] <- get_pearson(numeric_cols[i])
-  rel_df[numeric_cols[i], 'partial_eta_sq'] <- get_partial_eta(numeric_cols[i])
-  rel_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
-  rel_df[numeric_cols[i], 'var_subs'] <- get_var_breakdown(numeric_cols[i])$subs
-  rel_df[numeric_cols[i], 'var_ind'] <- get_var_breakdown(numeric_cols[i])$ind
-  rel_df[numeric_cols[i], 'var_resid'] <- get_var_breakdown(numeric_cols[i])$resid
-}
-
-rel_df$dv = row.names(rel_df)
-row.names(rel_df) = seq(1:nrow(rel_df))
-rel_df$task = 'task'
-rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
-rel_df[grep('holt', rel_df$dv), 'task'] = "task"
-rel_df = rel_df %>%
-  select(dv, task, spearman, icc, pearson, partial_eta_sq, sem, var_subs, var_ind, var_resid)
-# row.names(rel_df) = NULL
-```
-
-```{r}
-sig_days_effect %>%
-  left_join(rel_df, by='dv') %>%
-  ggplot(aes(estimate, icc))+
-  geom_point()
-```
+Conclusion: The average difference between the scores of a measure doesn't change with the increased delay.
 
@@
 ```{r echo=FALSE}
-rm(tmp, comb, sig_days_effect, t1_2_difference, duplicate_items, duplicate_items_data_t1, duplicate_items_data_t2, extract_items, get_delay_effect)
+rm(tmp, comb, t1_2_difference, duplicate_items, duplicate_items_data_t1, duplicate_items_data_t2, extract_items, get_delay_effect)
 ```

### 2018-05-16 code/FrisemFigures.R

@@ -68,3 +68,79 @@ tmp %>%
 
 ggsave('VarBreakdown_Example.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 6, units = "in", dpi=300)
 
+#######################################################
+#######################################################
+#######################################################
+
+tmp = duplicate_items_data_t1 %>%
+  gather(key, value, -worker)
+
+tmp2 = duplicate_items_data_t2 %>%
+  gather(key, value, -worker)
+
+tmp = duplicate_items %>%
+  select(item1_ID, item2_ID) %>%
+  left_join(tmp, by = c("item1_ID" = "key")) %>%
+  left_join(tmp, by = c("item2_ID" = "key", "worker" = "worker")) %>%
+  rename(item1_time1 = value.x, item2_time1 = value.y) %>%
+  left_join(tmp2, by = c("item1_ID" = "key", "worker" = "worker")) %>%
+  left_join(tmp2, by = c("item2_ID" = "key", "worker" = "worker")) %>%
+  rename(item1_time2 = value.x, item2_time2 = value.y) %>%
+  group_by(item1_ID) %>%
+  mutate(item1_time1 = scale(item1_time1),
+         item1_time2 = scale(item1_time2),
+         item2_time1 = scale(item2_time1),
+         item2_time2 = scale(item2_time2),
+         item1_time1 = ifelse(item1_ID == "mpq_control_survey.13", item1_time1*-1, item1_time1),
+         item1_time2 = ifelse(item1_ID == "mpq_control_survey.13", item1_time2*-1, item1_time2)) %>%
+  ungroup()
+
+p1 = tmp %>%
+  filter(grepl("bis_bas", item1_ID)) %>%
+  ggplot(aes(item1_time1, item2_time1, col=item1_ID))+
+  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
+  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
+  theme(legend.position = "none")+
+  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
+  xlab("BIS BAS T1")+
[…]

### 2018-05-16 code/SRO_Retest_Analyses.Rmd
frisem prep

@@
 
-demog_rel_df <- data.frame(spearman = rep(NA, length(numeric_cols)),
-                     icc = rep(NA, length(numeric_cols)),
-                     pearson = rep(NA, length(numeric_cols)))
+demog_rel_df <- data.frame(icc = rep(NA, length(numeric_cols)))
 
@@
 for(i in 1:length(numeric_cols)){
-  demog_rel_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i], t1_df = test_demog, t2_df = retest_demog) 
   demog_rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i], t1_df = test_demog, t2_df = retest_demog)
-  demog_rel_df[numeric_cols[i], 'pearson'] <- get_pearson(numeric_cols[i], t1_df = test_demog, t2_df = retest_demog)
 }
@@
   mutate(var = row.names(.)) %>%
-  select(var, icc, spearman, pearson) %>%
+  select(var, icc) %>%
   arrange(-icc)
@@
 ```{r}
+test_demog$HowOftenHazardousCannabis
+retest_demog$HowOftenHazardousCannabis
+
+test_demog$CaffieneOtherSourcesDayMG
+retest_demog$CaffieneOtherSourcesDayMG
+
+test_demog$SpouseParentsComplainDrugUse
+retest_demog$SpouseParentsComplainDrugUse
+
+test_demog$OtherDebtAmount
+retest_demog$OtherDebtAmount
+```
+
+```{r}
 sjt.df(demog_rel_df %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/demog_rel_table.doc")
@@
 summary(demog_rel_df)
+```
+
+```{r}
+demog_rel_df %>%
+  ggplot(aes(icc))+
+  geom_density(fill = 'grey', alpha = 0.7, color = NA)+
+  xlab("ICC")+
+  ylab("Density")
+
+ggsave('DemogRelDist.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 5, units = "in", dpi=300)
 ```

### 2018-05-17 code/SRO_Retest_Analyses.Rmd
frisem prep

@@
   summarise(mean_pct = mean(value),
-            sd_pct = sd(value),
+            sd_pct = sd(value, na.rm=T),
             n = n()) %>%
@@
   ggplot(aes(factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
-                    labels = c("Variance between individuals",
-                               "Variance between sessions",
-                               "Error variance")), mean_pct, color=task))+
-  geom_point(position=position_dodge(width = 0.25), size = 4)+
+                    labels = c("Between subject variance",
+                               "Within subject variance",
+                               "Error variance")), mean_pct))+
+  # geom_point(position=position_dodge(width = 0.25), size = 3, aes(color=task))+
+  geom_bar(position=position_dodge(width = 0.5), width=0.5, aes(fill=task), stat='identity', alpha=0.5)+
   # geom_errorbar(aes(ymin=mean_pct-sd_pct, ymax=mean_pct+sd_pct), position=position_dodge(width = 0.25), width=0, size=2)+
-  geom_errorbar(aes(ymin=cil, ymax=ciu), position=position_dodge(width = 0.25), width=0.25, size=2)+
+  geom_errorbar(aes(ymin=cil, ymax=ciu, color=task), position=position_dodge(width = 0.5), width=0.1)+
   theme_bw()+
   xlab('')+
-  ylab('Percent')+
+  ylab('Percent of total variance')+
   theme(legend.title = element_blank(),
         legend.text = element_text(size=14),
-        legend.position = 'bottom',
+        # legend.position = 'bottom',
         axis.text = element_text(size=12),
         axis.title.y = element_text(size=12))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))
-
-ggsave('Variance_Breakdown_DotPlot.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 6, height = 5, units = "in", dpi = 100)
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
+  ylim(0,100)
+
+ggsave('Variance_Breakdown_BarPlot.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 6, height = 5, units = "in", dpi = 300)
 ```
@@
 tmp2 %>%
-  filter(overall_difference == "overall") %>%
+  # filter(overall_difference == "overall") %>%
   ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
   geom_boxplot()+
-  # facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
+  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
   theme_bw()+
@@
   guides(fill = guide_legend(ncol = 2))+
-  scale_fill_discrete(breaks=c("Drift Rate", "Threshold", "Non-decision", "Response Time", "Accuracy"))
-
-ggsave('PointEst_DDM_Comp_OverallOnly.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 5, units = "in", limitsize = FALSE)
+  scale_fill_discrete(breaks=c("Drift Rate", "Threshold", "Non-decision", "Response Time", "Accuracy"))+
+  ylim(-0.4, 1)
+
+ggsave('PointEst_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 15, height = 7, units = "in", limitsize = FALSE)
 ```

### 2018-05-17 code/FrisemFigures.R

@@ -64,11 +64,10 @@ tmp %>%
 
 ggsave('Boot_Example.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 8, units = "in", dpi=300)
 
+#######################################################
+#######################################################
+#######################################################
 
-
-#######################################################
-#######################################################
-#######################################################
 tmp = rel_df %>%
   mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
          var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
@@ -191,3 +190,39 @@ p5 = arrangeGrob(p1, p2, p3, p4, ncol=2)
 ggsave('DataCheckOverlappingItemsExample.jpg', p5, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 300)
 
 rm(tmp, tmp2, p1, p2, p3, p4, p5)
+
+#######################################################
+#######################################################
+#######################################################
+
+rel_df %>%
+  ggplot(aes(icc, fill=task))+
+  geom_density(alpha = 0.5, color=NA)+
+  xlim(-0.4,1)+
+  xlab("ICC")+
+  ylab("Density")+
+  theme(legend.title = element_blank())+
+  scale_fill_manual(values = c("white", "#00BFC4"))
+
+ggsave('TaskVarsPointEstDist.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 7, height = 5, units = "in", limitsize = FALSE, dpi = 300)
+
+rel_df %>%
+  ggplot(aes(icc, fill=factor(task, levels = c("task", "survey"), labels = c("task", "survey"))))+
+  geom_density(alpha = 0.5, color=NA)+
+  xlim(-0.4,1)+
+  xlab("ICC")+
+  ylab("Density")+
+  theme(legend.title = element_blank())+
+  scale_fill_manual(values = c("white", "#F8766D"))
+
[…]

### 2018-05-17 code/FrisemFigures.R
frisem prep

@@ -5,8 +5,10 @@ lit_review %>%
   facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
   theme(panel.spacing = unit(0.5, "lines"),
         strip.placement = "outside",
-        strip.text.y = element_text(angle=180, size = 12),
-        axis.text.y = element_text(size = 11),
+        strip.text.y = element_text(angle=180, size = 36),
+        axis.text.y = element_text(size = 26),
+        axis.text.x = element_text(size = 16),
+        legend.text = element_text(size = 16),
         panel.background = element_rect(fill = NA),
         panel.grid.major = element_line(colour = "grey80"),
         legend.position = 'bottom') +
@@ -14,7 +16,7 @@ lit_review %>%
   ylab("")+
   scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
   scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))
-ggsave('Lit_Review_Example.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", dpi=300)
+ggsave('Lit_Review_Example.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 7, units = "in", dpi=500)
 
 #######################################################
 #######################################################

### 2018-05-17 code/SRO_Retest_Analyses.Rmd
frisem prep

@@
   ggplot(aes(icc))+
-  geom_density(fill = 'grey', alpha = 0.7, color = NA)+
+  geom_histogram(fill = 'grey', alpha = 0.7, color = NA)+
   xlab("ICC")+
-  ylab("Density")
+  ylab("Count")
 
@@
 
-ggsave('LitReviewSampleSize.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 3, height = 5, units = "in", limitsize = FALSE, dpi = 300)
+ggsave('LitReviewSampleSize.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 3, height = 5, units = "in", limitsize = FALSE, dpi = 500)
 ```
@@
 
+Are the residuals of this model heteroscedasticity
+
+```{r}
+tmp = data.frame(rel_comp$sample_size, resid(mod2)) %>%
+  rename(sample_size = rel_comp.sample_size, resid = resid.mod2.)
+
+tmp %>%
+  ggplot(aes(sample_size, resid))+
+  geom_point()+
+  geom_smooth(method = "lm")
+
+summary(lm(resid ~ sample_size, tmp))
+```
+
 Tasks have significantly lower reliability and reliability decreases with increasing sample size.
@@
 ```{r}
-ggplotly(rel_comp %>% 
+rel_comp %>% 
   ggplot(aes(sample_size, retest_reliability, color=task))+
   geom_smooth(method='lm')+
-  geom_point(alpha = 0.2)+
-  theme(legend.title = element_blank())+
+  # geom_point(alpha = 0.2)+
+  theme(legend.title = element_blank(),
+        axis.title.y = element_text(size=14),
+        axis.title.x = element_text(size=14))+
   xlab("Sample Size")+
-  ylab("Retest reliability"))
-
-ggsave('LitReviewRelBySampleSize.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 300)
+  ylab("Retest reliability")+
+  ylim(-0.15, 1)
+
+ggsave('LitReviewRelBySampleSize.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 500)
 ```

### 2018-05-17 code/FrisemFigures.R

@@ -8,10 +8,13 @@ lit_review %>%
         strip.text.y = element_text(angle=180, size = 36),
         axis.text.y = element_text(size = 26),
         axis.text.x = element_text(size = 16),
+        axis.title.x = element_text(size = 16),
         legend.text = element_text(size = 16),
+        legend.title  = element_text(size = 16),
         panel.background = element_rect(fill = NA),
         panel.grid.major = element_line(colour = "grey80"),
         legend.position = 'bottom') +
+  guides(shape = guide_legend(override.aes = list(size=16))) +
   xlab("")+
   ylab("")+
   scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
@@ -54,8 +57,9 @@ tmp %>%
   theme(panel.spacing = unit(0.75, "lines"),
         strip.placement = "outside",
         strip.text.y = element_text(angle=180, size=36),
-        axis.text.y = element_text(size=20),
+        axis.text.y = element_text(size=26),
         axis.text.x = element_text(size=20),
+        axis.title.x = element_text(size=18),
         panel.background = element_rect(fill = NA),
         panel.grid.major = element_line(colour = "grey80")) +
   xlab("ICC")+
@@ -64,7 +68,7 @@ tmp %>%
   scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
   geom_vline(xintercept = 0, color = "red", size = 1)
 
-ggsave('Boot_Example.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 8, units = "in", dpi=300)
+ggsave('Boot_Example.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 8, units = "in", dpi=500)
 
 #######################################################
 #######################################################

### 2018-05-17 code/SRO_Retest_Analyses.Rmd
frisem prep

@@
 ```{r}
+timed_demogs <- c("DoctorVisitsLastMonth","DaysHalfLastMonth","Worthless","DaysPhysicalHealthFeelings","Depressed","EverythingIsEffort","Hopeless","RestlessFidgety","Nervous","DaysLostLastMonth","Last30DaysUsual")
+
 demog_rel_df %>%
-  ggplot(aes(icc))+
-  geom_histogram(fill = 'grey', alpha = 0.7, color = NA)+
+  mutate(timed = ifelse(var %in% timed_demogs, 1, 0)) %>%
+  ggplot(aes(icc, fill = factor(timed)))+
+  geom_histogram(position = "identity", alpha = 0.7, color = NA)+
   xlab("ICC")+
-  ylab("Count")
-
-ggsave('DemogRelDist.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 5, units = "in", dpi=300)
+  ylab("Count")+
+  scale_fill_manual(values = c("grey", "grey25"))+
+  theme(legend.position = "none")
+
+demog_rel_df
+
+ggsave('DemogRelDist.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 5, units = "in", dpi=500)
 ```
@@
   xlab('Days between completion')+
-  ylab('Absolute Scaled difference score')
-
-ggsave('DaysBtwEffect.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 300)
+  ylab('Scaled difference score')
+
+ggsave('DaysBtwEffect.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
 ```
@@
 
-ggsave('DataCheckOverlappingItems.jpg', p5, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 300)
+ggsave('DataCheckOverlappingItems.jpg', p5, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 500)
 
@@
   xlim(0,1)+
-  ylim(0,40)
-
-ggsave('LitOnly_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 300)
+  ylim(0,40)+
+  theme(axis.title.x  = element_text(size=16),
+        axis.text.x  = element_text(size=14),
+        axis.title.y  = element_text(size=16),
+        legend.title  = element_text(size=16),
+        legend.text  = element_text(size=16))
+
+ggsave('LitOnly_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
 
@@
   xlim(0,1)+
-  ylim(0,40)
-
-ggsave('LitAndBoot_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 300)
+  ylim(0,40)+
+  theme(axis.title.x  = element_text(size=16),
+        axis.text.x  = element_text(size=14),
+        axis.title.y  = element_text(size=16),
+        legend.title  = element_text(size=16),
+        legend.text  = element_text(size=16))
+
+ggsave('LitAndBoot_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
 ```

### 2018-05-17 code/FrisemFigures.R

@@ -193,7 +193,7 @@ p4 = tmp %>%
 
 p5 = arrangeGrob(p1, p2, p3, p4, ncol=2)
 
-ggsave('DataCheckOverlappingItemsExample.jpg', p5, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 300)
+ggsave('DataCheckOverlappingItemsExample.jpg', p5, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 500)
 
 rm(tmp, tmp2, p1, p2, p3, p4, p5)
 

### 2018-05-17 code/SRO_Retest_Analyses.Rmd
frisem prep

@@
 ggsave('LitReviewRelBySampleSize.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 500)
+```
+
+```{r}
+rel_comp %>% 
+  ggplot(aes(task, retest_reliability, fill = task))+
+  geom_boxplot()+
+  theme(legend.position = 'none',
+        axis.text.x = element_text(size=14),
+        axis.title.y = element_text(size=14))+
+  xlab("")+
+  ylab("Mean ICC")+
+  ylim(-0.4,1)
+
+ggsave('LitTaskVsSurvey.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 3, height = 5, units = "in", limitsize = FALSE, dpi = 500)
 ```

### 2018-05-17 code/FrisemFigures.R

@@ -105,8 +105,10 @@ tmp %>%
   facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
   theme(panel.spacing = unit(0.5, "lines"), 
         strip.placement = "outside",
-        strip.text.y = element_text(angle=180),
-        axis.text.y = element_text(size = 11),
+        strip.text.y = element_text(angle=180, size = 36),
+        axis.text.y = element_text(size = 16),
+        axis.text.x = element_text(size  = 16),
+        legend.text = element_text(size = 16),
         panel.background = element_rect(fill = NA),
         panel.grid.major = element_line(colour = "grey85"),
         legend.position = 'bottom')+
@@ -119,7 +121,8 @@ tmp %>%
   ylab("")+
   xlab("")
 
-ggsave('VarBreakdown_Example.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 6, units = "in", dpi=300)
+ggsave('VarBreakdown_Example.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", 
+       width = 14, height = 10, units = "in", dpi=400)
 
 #######################################################
 #######################################################
@@ -232,3 +235,18 @@ rel_df %>%
   theme(legend.title = element_blank())
 
 ggsave('AllVarsPointEstDist.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 7, height = 5, units = "in", limitsize = FALSE, dpi = 300)
+
+
+#######################################################
+#######################################################
+#######################################################
+rel_df %>%
+  ggplot(aes(task, icc, fill=task))+
+  geom_boxplot()+
+  theme(legend.position = 'none',
+        axis.text.x = element_text(size=14),
+        axis.title.y = element_text(size=14))+
+  xlab("")+
+  ylab("Mean ICC")+
+  ylim(-0.4,1)
+ggsave('TaskVsSurvey.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 3, height = 5, units = "in", limitsize = FALSE, dpi = 500)

### 2018-06-01 code/SRO_Retest_Analyses.Rmd
presentation prep

@@
          overall_difference != "condition",
-         rt_acc != "other") %>%
+         rt_acc != "other",
+         raw_fit != "hddm") %>%
   drop_na() %>%
@@
   geom_boxplot()+
-  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
+  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall (all trials)", "Difference (contrasting conditions)")))+
   theme_bw()+

### 2018-06-01 code/FrisemFigures.R

@@ -95,8 +95,11 @@ tmp = rel_df %>%
 labels = tmp %>%
   distinct(dv, .keep_all=T)
 
+tmp = tmp %>% 
+  left_join(measure_labels[,c("dv", "raw_fit")])
+
 tmp %>%
-  filter(task_group == "stroop") %>%
+  filter(task_group == "stroop", raw_fit == "raw") %>%
   ggplot(aes(x=factor(rank), y=value, fill=factor(key, levels = c("var_resid_pct", "var_ind_pct", "var_subs_pct"))))+
   geom_bar(stat='identity', alpha = 0.75, color='#00BFC4')+
   scale_x_discrete(breaks = labels$rank,
@@ -106,9 +109,9 @@ tmp %>%
   theme(panel.spacing = unit(0.5, "lines"), 
         strip.placement = "outside",
         strip.text.y = element_text(angle=180, size = 36),
-        axis.text.y = element_text(size = 16),
-        axis.text.x = element_text(size  = 16),
-        legend.text = element_text(size = 16),
+        axis.text.y = element_text(size = 26),
+        axis.text.x = element_text(size  = 20),
+        legend.text = element_text(size = 24),
         panel.background = element_rect(fill = NA),
         panel.grid.major = element_line(colour = "grey85"),
         legend.position = 'bottom')+
@@ -119,7 +122,8 @@ tmp %>%
                                "Error variance"),
                     values=c("grey65", "grey45", "grey25"))+
   ylab("")+
-  xlab("")
+  xlab("")+
+  guides(fill = guide_legend(ncol = 1))
 
 ggsave('VarBreakdown_Example.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", 
        width = 14, height = 10, units = "in", dpi=400)

### 2018-06-01 code/NeuroeconAbstractPredictionAnalyses.R

@@ -1,0 +1,111 @@
+get_var_exp = function(demog_var, dv){
+  
+  df = merge(test_demog[,c("sub_id", demog_var)], test_data[,c("sub_id", dv)])
+  df[,demog_var] = scale(df[,demog_var])
+  df[,dv] = scale(df[,dv])
+  
+  mod = lm(df[,demog_var]~ df[,dv])
+  var_exp = summary(mod)$r.squared
+  
+  return(var_exp)
+}
+
+tmp = measure_labels %>% filter(ddm_task == 1 & rt_acc != 'other')
+dvs = unique(as.character(tmp$dv))
+
+out = data.frame(dv = dvs)
+
+get_var_exp_for_demog = function(demog_var){
+  
+  out[,demog_var] = NA
+  
+  for(i in 1:length(dvs)){
+    out[i, demog_var] = get_var_exp(demog_var = demog_var, dv=dvs[i])
+  }
+  
+  return(out)
+}
+
+init_demogs = c("HouseholdIncome","RetirementAccount", "HowLongSmoked", "CigsPerDay", "AlcoholHowOften", "CannabisHowOften",  "Nervous", "Hopeless", "RestlessFidgety","Depressed","EverythingIsEffort","Worthless")
+
+results = out
+
+for(i in 1:length(init_demogs)){
+  demog_var = init_demogs[i]
+  tmp_out = get_var_exp_for_demog(demog_var = demog_var)
+  results = merge(results, tmp_out, by="dv")
+}
+
+results = merge(results, measure_labels, by="dv")
+
+tmp = results %>%
+  select(-ddm_task, -num_all_trials) %>%
+  mutate(contrast = ifelse(overall_difference == "difference", 1, 0),
+         raw_bin = ifelse(raw_fit == "raw",1,0)) %>%
+  gather(key, value, -dv, -overall_difference, -raw_fit, -rt_acc, -contrast, -raw_bin) %>%
+  mutate(value = as.numeric(value))
+  
+#Initial predictions for:
+
+#Desired output: 
+  # rows of dvs
+  # cols of demog_vars
+  # cells of var explained
+  
+# HeightInches
+# WeightPounds
+# 
+# HouseholdIncome
+# RetirementAccount
+# RetirementPercentStocks
+# RentOwn
+# MortgageDebt
+# CarDebt
+# EducationDebt
[…]

### 2018-06-04 code/SRO_Retest_Analyses.Rmd
updated demog table

@@
 ```{r}
-numeric_cols = c()
-
-for(i in 1:length(names(test_demog))){
-  if(is.numeric(test_demog[,i])){
-    numeric_cols <- c(numeric_cols, names(test_demog)[i])
-  }
-}
-
-demog_rel_df <- data.frame(icc = rep(NA, length(numeric_cols)))
-
-row.names(demog_rel_df) <- numeric_cols
-
-for(i in 1:length(numeric_cols)){
-  demog_rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i], t1_df = test_demog, t2_df = retest_demog)
-}
-
-demog_rel_df = demog_rel_df %>%
-  mutate(var = row.names(.)) %>%
-  select(var, icc) %>%
-  arrange(-icc)
-
-demog_rel_df
-```
-
-```{r}
-test_demog$HowOftenHazardousCannabis
-retest_demog$HowOftenHazardousCannabis
-
-test_demog$CaffieneOtherSourcesDayMG
-retest_demog$CaffieneOtherSourcesDayMG
-
-test_demog$SpouseParentsComplainDrugUse
-retest_demog$SpouseParentsComplainDrugUse
-
-test_demog$OtherDebtAmount
-retest_demog$OtherDebtAmount
-```
-
-```{r}
-sjt.df(demog_rel_df %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/demog_rel_table.doc")
-```
-
-```{r}
-summary(demog_rel_df)
-```
-
-```{r}
-timed_demogs <- c("DoctorVisitsLastMonth","DaysHalfLastMonth","Worthless","DaysPhysicalHealthFeelings","Depressed","EverythingIsEffort","Hopeless","RestlessFidgety","Nervous","DaysLostLastMonth","Last30DaysUsual")
-
-demog_rel_df %>%
-  mutate(timed = ifelse(var %in% timed_demogs, 1, 0)) %>%
-  ggplot(aes(icc, fill = factor(timed)))+
-  geom_histogram(position = "identity", alpha = 0.7, color = NA)+
-  xlab("ICC")+
-  ylab("Count")+
-  scale_fill_manual(values = c("grey", "grey25"))+
-  theme(legend.position = "none")
-
-demog_rel_df
-
-ggsave('DemogRelDist.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 5, units = "in", dpi=500)
-```
-
-```{r echo=FALSE}
-rm(test_demog, retest_demog, demog_rel_df, numeric_cols)
-```
-
-### Effect of delays between the two measurements
-
-Due to our data collection strategy we did not strictly control for the delay between the two measurements as standard psychometrics studies measuring retest reliability might.
-
-An individual difference measure would preferably remain stable regardless of the delay between multiple measurements.
-
-Since we only had two measurements we could not test directly whether a measure becomes less reliable depending on the delay between the two time points (The average number of days between two measurements would be the same for all measures since reliability is a measure level metric while days between completion a subject level one).
-
-So if you regress the average difference for each measure on average delay between two measurements you are regressing a vector with varying numbers on a vector of same values, like a t test asking if the mean of the varying column, in this case the average difference score, is different than the unique value in the single value column, i.e.
-the average delay between two time points (Note that this should be true in theory but in practice since for each measure there might subjects for whom the dv could not be calculated there might be >1 unique values for the average delay between the two time points).
-This analysis is not meaningful.
-
-Instead of the summary metric like the retest reliability estimate for each measure we can check whether the difference score distribution for each measure depends on the delay between the two measurements.
-Since the difference score distribution is at subject level we can check whether the order of subjects in this distribution depends on their order in the distribution of days between completing the two tests.
-
-Make data frame with difference between two scores for each measure for each subject.
-Since the scores for different measures are on different scales for comparability the difference scores are normalized (ie demeaned and dividied by the sd of the difference score distribution.) Note that the variance of the difference score distribution accounts for the variance in both time points by summing them.
-Normalization equates the means of each difference score distribution to 0 which would mask any meaningful change between the two time points but the analysis here does not interpret the mean of the difference score distributions but is interested in its relation to the days between completion.
-We check if the variables show systematic differences between the two points later.
-
-Here we check if the difference is larger the longer the delay
-
-```{r warning=FALSE}
-numeric_cols = c()
-
-for(i in 1:length(names(test_data))){
-  if(is.numeric(test_data[,i]) & names(test_data)[i] %in% names(retest_data)){
-    numeric_cols <- c(numeric_cols, names(test_data)[i])
-  }
-}
-
-t1_2_difference = data.frame()
-
-for(i in 1:length(numeric_cols)){
-  tmp = match_t1_t2(numeric_cols[i],format='wide')
-  tmp = tmp %>% 
-  mutate(difference = scale(`2` - `1`))
-  t1_2_difference = rbind(t1_2_difference, tmp)
-}
-
-t1_2_difference$difference = as.data.frame(t1_2_difference$difference)$V1
-
-t1_2_difference = t1_2_difference %>% separate(dv, c("task", "dv2"), sep="\\.", remove=FALSE)
-```
-
-```{r echo=FALSE}
-rm(tmp, i)
-```
-
-Add completion dates to this data frame.
-
-```{r}
-retest_task_comp_times = read.csv(paste0(retest_data_path, 'Local/retest_task_completion_times.csv'))
-test_task_comp_times = read.csv(paste0(retest_data_path, 'Local/test_task_completion_times.csv'))
-task_comp_times = merge(retest_task_comp_times, test_task_comp_times, by=c('worker_id','task'))
-rm(retest_task_comp_times, test_task_comp_times)
-task_comp_times = task_comp_times %>%
-  select(-X.x, -X.y) %>%
-  mutate(finish_day.x = as.Date(finish_day.x),
-         finish_day.y = as.Date(finish_day.y),
-         days_btw = finish_day.x-finish_day.y) %>%
-  rename(sub_id=worker_id)
-```
-
-```{r warning=FALSE}
-t1_2_difference = merge(t1_2_difference, task_comp_times[,c('sub_id', 'task','days_btw')], by=c('sub_id', 'task'))
-```
-
-```{r echo=FALSE}
-rm(task_comp_times)
-```
-
-What does the distribution of differences look like: The distribution of differences between two time points for each measure
-
-```{r warning=FALSE, message=FALSE}
-t1_2_difference %>%
-  ggplot(aes(difference, alpha=dv))+
-  geom_histogram(position='identity')+
-  theme(legend.position = 'none')
-```
-
-How do the difference score distributions look like with respect to the days between completion?
-
-```{r}
-t1_2_difference %>%
-  ggplot()+
-  geom_smooth(aes(as.numeric(days_btw), abs(difference), group=factor(dv)), method='lm', se=FALSE, color = 'grey', alpha = 0.5)+
-  geom_smooth(aes(as.numeric(days_btw), abs(difference)), method='lm', color = "black", se=FALSE)+
-  theme(legend.title = element_blank())+
-  xlab('Days between completion')+
-  ylab('Scaled difference score')
-
-ggsave('DaysBtwEffect.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
-```
-
-To test if the slope of the black is significant we would run a mixed effects model with a fixed effect for days between completion, random slope for each dv depending on the days between and random intercept for each dv.
-
-Before I was using subjects as a random effect but days between the two time points for each measure depends on subj id.
-What varies randomly is which dv we are looking for its distribution of differences in relation to the days between the time points.
-So I changed the model to have fixed effect for the days between, a random slope for (dependent variables can be differentially sensitive to th effect of days between) and a random intercept for dependent variable.
-
-Significant fixed effect suggests that on average the longer the delay the smaller the difference.
-
-```{r}
-summary(lmerTest::lmer(abs(difference) ~ scale(days_btw)+(scale(days_btw) | dv), data=t1_2_difference)) 
-```
-
-But if I just run one mixed effects model then we don't get a sense of the simple effects (how many of the variables this effect of the days between is significant and in which direction).
-I can run it separately for each dv to see if all difference score distributions are affected the same way depending on the days between completion.
-But since we are running so many tests we need to correct for multiple comparisons.
-How many of these tests are significant FDR correcting?
-None.
-
-```{r}
-get_delay_effect = function(df){
-  mod = lm(abs(difference) ~ scale(days_btw), data = df)
-  out = data.frame(estimate=coef(summary(mod))["scale(days_btw)","Estimate"], pval=coef(summary(mod))["scale(days_btw)","Pr(>|t|)"])
-  return(out)
-}
-
-days_effect  = t1_2_difference %>%
-  group_by(dv) %>%
-  do(get_delay_effect(.))
-
-#Correct p-values for multiple comparisons
-sum(p.adjust(days_effect$pval, method = "fdr") < 0.05)
-```
-
-Conclusion: The average difference between the scores of a measure doesn't change with the increased delay.
-
-### Overlapping survery questions
-
-Some surveys have overlapping questions. Do these correlate within and across sessions?
-
-First determine the overlapping questions.
-
-```{r}
-tmp = read.csv(gzfile(paste0(retest_data_path, 'items.csv.gz')))
-tmp = tmp %>% 
-  filter(worker == 's005') %>% 
-  select(item_ID, item_text) %>% 
-  mutate(item_text = trimws(as.character(item_text))) %>%
-  unite(item, c("item_ID", "item_text"), sep = "___")
-
-comb = as.data.frame(t(combn(unique(tmp$item),2)))
-
-duplicate_items = comb %>% 
-  filter(grepl('dospert', V1)==FALSE) %>%
-  filter(grepl('selection_optimization', V1)==FALSE) %>%
-  filter(grepl('sensation_seeking', V1)==FALSE) %>%
-  separate(V1, c("item1_ID", "item1_text"), sep="___") %>%
-  separate(V2, c("item2_ID", "item2_text"), sep="___") %>%
-  mutate(similarity = levenshteinSim(item1_text, item2_text)) %>%
-  filter(similarity>0.8) %>%
-  select(item1_ID, item2_ID, item1_text, item2_text)
-
-duplicate_items
-```
-
-```{r warning=FALSE, message=FALSE}
-#surveys to read in
-extract_items = c('worker',unique(with(duplicate_items, c(item1_ID, item2_ID))))
-
-#correlations to compute:
-#item1_t1 - item2_t1, 
-#item1_t2 - item2_t2, 
-#item1_t1 - item2_t2, 
-#item1_t2 - item2_t1
-
-duplicate_items_data_t1 = read.csv(paste0(test_data_path, 'subject_x_items.csv'))
-duplicate_items_data_t2 = read.csv(paste0(retest_data_path, 'subject_x_items.csv'))
-
-duplicate_items_data_t1 = duplicate_items_data_t1 %>%
-  filter(worker %in% duplicate_items_data_t2$worker) %>%
-  select(extract_items)
-
-duplicate_items_data_t2=duplicate_items_data_t2 %>%
-  filter(worker %in% duplicate_items_data_t1$worker) %>%
-  select(extract_items)
-
-duplicate_items = duplicate_items %>%
-  mutate(t1_t1_cor = NA,
-         t2_t2_cor = NA,
-         t1_t2_cor = NA,
-         t2_t1_cor = NA,
-         t1_t1_polycor = NA,
-         t2_t2_polycor = NA,
-         t1_t2_polycor = NA,
-         t2_t1_polycor = NA)
-
-for(i in 1:nrow(duplicate_items)){
-  duplicate_items$t1_t1_cor[i] = abs(cor(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])],
-                                  duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])]))
-
-  duplicate_items$t2_t2_cor[i] = abs(cor(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])],
-                                  duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])]))
-
-  duplicate_items$t1_t2_cor[i] = abs(cor(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])],
-                                  duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])]))
-
-  duplicate_items$t2_t1_cor[i] = abs(cor(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])],
-                                  duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])]))
-
-  duplicate_items$t1_t1_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])],
-                      duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])]))$rho[2])
-
-  duplicate_items$t2_t2_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])],
-                      duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])]))$rho[2])
-
-  duplicate_items$t1_t2_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])],
-                      duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])]))$rho[2])
-
-  duplicate_items$t2_t1_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])],
-                      duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])]))$rho[2])
-}
-
-for(i in 1:nrow(duplicate_items)){
-  duplicate_items$t1_t1_cor[i] = abs(cor(scale(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])]),
-                                  scale(duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])])))
-
-  duplicate_items$t2_t2_cor[i] = abs(cor(scale(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])]),
-                                  scale(duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])])))
-
-  duplicate_items$t1_t2_cor[i] = abs(cor(scale(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])]),
-                                  scale(duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])])))
-
-  duplicate_items$t2_t1_cor[i] = abs(cor(scale(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])]),
-                                  scale(duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])])))
-
-  duplicate_items$t1_t1_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])],
-                      duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])]))$rho[2])
-
-  duplicate_items$t2_t2_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])],
-                      duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])]))$rho[2])
-
-  duplicate_items$t1_t2_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])],
-                      duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])]))$rho[2])
-
-  duplicate_items$t2_t1_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])],
-                      duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])]))$rho[2])
-}
-
-duplicate_items
-```
-
-```{r}
-summary(duplicate_items$t1_t1_cor)
-summary(duplicate_items$t2_t2_cor)
-summary(duplicate_items$t1_t2_cor)
-summary(duplicate_items$t2_t1_cor)
-
-summary(duplicate_items$t1_t1_polycor)
-summary(duplicate_items$t2_t2_polycor)
-summary(duplicate_items$t1_t2_polycor)
-summary(duplicate_items$t2_t1_polycor)
-```
-
-Time 1: item 1 - item 2
-Time 1 item 1 - time 2 item 2
-Time 2 item 1 - time 1 item 2
-Time 2: item 1 - item 2
-
-```{r warning=FALSE, message=FALSE}
-tmp = duplicate_items_data_t1 %>%
-  gather(key, value, -worker)
-
-tmp2 = duplicate_items_data_t2 %>%
-  gather(key, value, -worker)
-
-tmp = duplicate_items %>%
-  select(item1_ID, item2_ID) %>%
-  left_join(tmp, by = c("item1_ID" = "key")) %>%
-  left_join(tmp, by = c("item2_ID" = "key", "worker" = "worker")) %>%
-  rename(item1_time1 = value.x, item2_time1 = value.y) %>%
-  left_join(tmp2, by = c("item1_ID" = "key", "worker" = "worker")) %>%
-  left_join(tmp2, by = c("item2_ID" = "key", "worker" = "worker")) %>%
-  rename(item1_time2 = value.x, item2_time2 = value.y) %>%
-  group_by(item1_ID) %>%
-  mutate(item1_time1 = scale(item1_time1),
-         item1_time2 = scale(item1_time2),
-         item2_time1 = scale(item2_time1),
-         item2_time2 = scale(item2_time2),
-         item1_time1 = ifelse(item1_ID == "mpq_control_survey.13", item1_time1*-1, item1_time1),
-         item1_time2 = ifelse(item1_ID == "mpq_control_survey.13", item1_time2*-1, item1_time2)) %>%
-  ungroup()
-
-p1 = tmp %>%
-  ggplot(aes(item1_time1, item2_time1, col=item1_ID))+
-  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
-  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
-  theme(legend.position = "none")+
-  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
-  xlab("Item 1 T1")+
-  ylab("Item 2 T1")
-
-p2 = tmp %>%
-  ggplot(aes(item1_time1, item2_time2, col=item1_ID))+
-  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
-  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
-  theme(legend.position = "none")+
-  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
-  xlab("Item 1 T1")+
-  ylab("Item 2 T2")
-
-p3 = tmp %>%
-  ggplot(aes(item1_time2, item2_time1, col=item1_ID))+
-  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
-  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
-  theme(legend.position = "none")+
-  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
-  xlab("Item 1 T2")+
-  ylab("Item 2 T1")
-
-p4 = tmp %>%
-  ggplot(aes(item1_time2, item2_time2, col=item1_ID))+
-  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
-  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
-  theme(legend.position = "none")+
-  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
-  xlab("Item 1 T2")+
-  ylab("Item 2 T2")
-
-p5 = arrangeGrob(p1, p2, p3, p4, ncol=2)
-
-ggsave('DataCheckOverlappingItems.jpg', p5, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 500)
-
-rm(tmp, tmp2, p1, p2, p3, p4, p5)
-```
-
-```{r echo=FALSE}
-rm(tmp, comb, t1_2_difference, duplicate_items, duplicate_items_data_t1, duplicate_items_data_t2, extract_items, get_delay_effect)
-```
-
-## Comparison to prior literature
-
-Read in and process bootstrapped results.
-
-```{r}
 process_boot_df = function(df){
@@
 
+demog_boot_df <- read.csv(gzfile(paste0(retest_data_path,'demog_boot_merged.csv.gz')))
+
+demog_boot_df = process_boot_df(demog_boot_df)
+```
+
+```{r}
+tmp = demog_boot_df %>%
+  group_by(dv) %>%
+  summarise(median_icc = quantile(icc, probs=0.5),
+            icc_2.5 = quantile(icc, probs = 0.025),
+            icc_97.5 = quantile(icc, probs = 0.975)) %>%
+  arrange(-median_icc)
+tmp
+```
+
+```{r}
+sjt.df(tmp%>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/demog_rel_table.doc")
+```
+
+Point estimates of reliability for demog items
+
+```{r}
+numeric_cols = c()
+
+for(i in 1:length(names(test_demog))){
+  if(is.numeric(test_demog[,i])){
+    numeric_cols <- c(numeric_cols, names(test_demog)[i])
+  }
+}
+
+demog_rel_df <- data.frame(icc = rep(NA, length(numeric_cols)))
+
+row.names(demog_rel_df) <- numeric_cols
+
+for(i in 1:length(numeric_cols)){
+  demog_rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i], t1_df = test_demog, t2_df = retest_demog)
+}
+
+demog_rel_df = demog_rel_df %>%
+  mutate(var = row.names(.)) %>%
+  select(var, icc) %>%
+  arrange(-icc)
+```
+
+Checking low reliability demog vars: Mostly NA's
+
+```{r}
+test_demog$HowOftenHazardousCannabis
+retest_demog$HowOftenHazardousCannabis
+
+test_demog$CaffieneOtherSourcesDayMG
+retest_demog$CaffieneOtherSourcesDayMG
+
+test_demog$SpouseParentsComplainDrugUse
+retest_demog$SpouseParentsComplainDrugUse
+
+test_demog$OtherDebtAmount
+retest_demog$OtherDebtAmount
+```
+
+Plotting point estimates of reliability for demographic items coloring those that have a time limit darker in the histogram.
+
+```{r warning=FALSE, message=FALSE}
+timed_demogs <- c("DoctorVisitsLastMonth","DaysHalfLastMonth","Worthless","DaysPhysicalHealthFeelings","Depressed","EverythingIsEffort","Hopeless","RestlessFidgety","Nervous","DaysLostLastMonth","Last30DaysUsual")
+
+demog_rel_df %>%
+  mutate(timed = ifelse(var %in% timed_demogs, 1, 0)) %>%
+  ggplot(aes(icc, fill = factor(timed)))+
+  geom_histogram(position = "identity", alpha = 0.7, color = NA)+
+  xlab("ICC")+
+  ylab("Count")+
+  scale_fill_manual(values = c("grey", "grey25"))+
+  theme(legend.position = "none")
+
+ggsave('DemogRelDist.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 5, units = "in", dpi=500)
+```
+
+```{r echo=FALSE}
+rm(test_demog, retest_demog, demog_rel_df, numeric_cols)
+```
+
+### Effect of delays between the two measurements
+
+Due to our data collection strategy we did not strictly control for the delay between the two measurements as standard psychometrics studies measuring retest reliability might.
+
+An individual difference measure would preferably remain stable regardless of the delay between multiple measurements.
+
+Since we only had two measurements we could not test directly whether a measure becomes less reliable depending on the delay between the two time points (The average number of days between two measurements would be the same for all measures since reliability is a measure level metric while days between completion a subject level one).
+
+So if you regress the average difference for each measure on average delay between two measurements you are regressing a vector with varying numbers on a vector of same values, like a t test asking if the mean of the varying column, in this case the average difference score, is different than the unique value in the single value column, i.e.
+the average delay between two time points (Note that this should be true in theory but in practice since for each measure there might subjects for whom the dv could not be calculated there might be >1 unique values for the average delay between the two time points).
+This analysis is not meaningful.
+
+Instead of the summary metric like the retest reliability estimate for each measure we can check whether the difference score distribution for each measure depends on the delay between the two measurements.
+Since the difference score distribution is at subject level we can check whether the order of subjects in this distribution depends on their order in the distribution of days between completing the two tests.
+
+Make data frame with difference between two scores for each measure for each subject.
+Since the scores for different measures are on different scales for comparability the difference scores are normalized (ie demeaned and dividied by the sd of the difference score distribution.) Note that the variance of the difference score distribution accounts for the variance in both time points by summing them.
+Normalization equates the means of each difference score distribution to 0 which would mask any meaningful change between the two time points but the analysis here does not interpret the mean of the difference score distributions but is interested in its relation to the days between completion.
+We check if the variables show systematic differences between the two points later.
+
+Here we check if the difference is larger the longer the delay
+
+```{r warning=FALSE}
+numeric_cols = c()
+
+for(i in 1:length(names(test_data))){
+  if(is.numeric(test_data[,i]) & names(test_data)[i] %in% names(retest_data)){
+    numeric_cols <- c(numeric_cols, names(test_data)[i])
+  }
+}
+
+t1_2_difference = data.frame()
+
+for(i in 1:length(numeric_cols)){
+  tmp = match_t1_t2(numeric_cols[i],format='wide')
+  tmp = tmp %>% 
+  mutate(difference = scale(`2` - `1`))
+  t1_2_difference = rbind(t1_2_difference, tmp)
+}
+
+t1_2_difference$difference = as.data.frame(t1_2_difference$difference)$V1
+
+t1_2_difference = t1_2_difference %>% separate(dv, c("task", "dv2"), sep="\\.", remove=FALSE)
+```
+
+```{r echo=FALSE}
+rm(tmp, i)
+```
+
+Add completion dates to this data frame.
+
+```{r}
+retest_task_comp_times = read.csv(paste0(retest_data_path, 'Local/retest_task_completion_times.csv'))
+test_task_comp_times = read.csv(paste0(retest_data_path, 'Local/test_task_completion_times.csv'))
+task_comp_times = merge(retest_task_comp_times, test_task_comp_times, by=c('worker_id','task'))
+rm(retest_task_comp_times, test_task_comp_times)
+task_comp_times = task_comp_times %>%
+  select(-X.x, -X.y) %>%
+  mutate(finish_day.x = as.Date(finish_day.x),
+         finish_day.y = as.Date(finish_day.y),
+         days_btw = finish_day.x-finish_day.y) %>%
+  rename(sub_id=worker_id)
+```
+
+```{r warning=FALSE}
+t1_2_difference = merge(t1_2_difference, task_comp_times[,c('sub_id', 'task','days_btw')], by=c('sub_id', 'task'))
+```
+
+```{r echo=FALSE}
+rm(task_comp_times)
+```
+
+What does the distribution of differences look like: The distribution of differences between two time points for each measure
+
+```{r warning=FALSE, message=FALSE}
+t1_2_difference %>%
+  ggplot(aes(difference, alpha=dv))+
+  geom_histogram(position='identity')+
+  theme(legend.position = 'none')
+```
+
+How do the difference score distributions look like with respect to the days between completion?
+
+```{r}
+t1_2_difference %>%
+  ggplot()+
+  geom_smooth(aes(as.numeric(days_btw), abs(difference), group=factor(dv)), method='lm', se=FALSE, color = 'grey', alpha = 0.5)+
+  geom_smooth(aes(as.numeric(days_btw), abs(difference)), method='lm', color = "black", se=FALSE)+
+  theme(legend.title = element_blank())+
+  xlab('Days between completion')+
+  ylab('Scaled difference score')
+
+ggsave('DaysBtwEffect.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
+```
+
+To test if the slope of the black is significant we would run a mixed effects model with a fixed effect for days between completion, random slope for each dv depending on the days between and random intercept for each dv.
+
+Before I was using subjects as a random effect but days between the two time points for each measure depends on subj id.
+What varies randomly is which dv we are looking for its distribution of differences in relation to the days between the time points.
+So I changed the model to have fixed effect for the days between, a random slope for (dependent variables can be differentially sensitive to th effect of days between) and a random intercept for dependent variable.
+
+Significant fixed effect suggests that on average the longer the delay the smaller the difference.
+
+```{r}
+summary(lmerTest::lmer(abs(difference) ~ scale(days_btw)+(scale(days_btw) | dv), data=t1_2_difference)) 
+```
+
+But if I just run one mixed effects model then we don't get a sense of the simple effects (how many of the variables this effect of the days between is significant and in which direction).
+I can run it separately for each dv to see if all difference score distributions are affected the same way depending on the days between completion.
+But since we are running so many tests we need to correct for multiple comparisons.
+How many of these tests are significant FDR correcting?
+None.
+
+```{r}
+get_delay_effect = function(df){
+  mod = lm(abs(difference) ~ scale(days_btw), data = df)
+  out = data.frame(estimate=coef(summary(mod))["scale(days_btw)","Estimate"], pval=coef(summary(mod))["scale(days_btw)","Pr(>|t|)"])
+  return(out)
+}
+
+days_effect  = t1_2_difference %>%
+  group_by(dv) %>%
+  do(get_delay_effect(.))
+
+#Correct p-values for multiple comparisons
+sum(p.adjust(days_effect$pval, method = "fdr") < 0.05)
+```
+
+Conclusion: The average difference between the scores of a measure doesn't change with the increased delay.
+
+### Overlapping survery questions
+
+Some surveys have overlapping questions. Do these correlate within and across sessions?
+
+First determine the overlapping questions.
+
+```{r}
+tmp = read.csv(gzfile(paste0(retest_data_path, 'items.csv.gz')))
+tmp = tmp %>% 
+  filter(worker == 's005') %>% 
+  select(item_ID, item_text) %>% 
+  mutate(item_text = trimws(as.character(item_text))) %>%
+  unite(item, c("item_ID", "item_text"), sep = "___")
+
+comb = as.data.frame(t(combn(unique(tmp$item),2)))
+
+duplicate_items = comb %>% 
+  filter(grepl('dospert', V1)==FALSE) %>%
+  filter(grepl('selection_optimization', V1)==FALSE) %>%
+  filter(grepl('sensation_seeking', V1)==FALSE) %>%
+  separate(V1, c("item1_ID", "item1_text"), sep="___") %>%
+  separate(V2, c("item2_ID", "item2_text"), sep="___") %>%
+  mutate(similarity = levenshteinSim(item1_text, item2_text)) %>%
+  filter(similarity>0.8) %>%
+  select(item1_ID, item2_ID, item1_text, item2_text)
+
+duplicate_items
+```
+
+```{r warning=FALSE, message=FALSE}
+#surveys to read in
+extract_items = c('worker',unique(with(duplicate_items, c(item1_ID, item2_ID))))
+
+#correlations to compute:
+#item1_t1 - item2_t1, 
+#item1_t2 - item2_t2, 
+#item1_t1 - item2_t2, 
+#item1_t2 - item2_t1
+
+duplicate_items_data_t1 = read.csv(paste0(test_data_path, 'subject_x_items.csv'))
+duplicate_items_data_t2 = read.csv(paste0(retest_data_path, 'subject_x_items.csv'))
+
+duplicate_items_data_t1 = duplicate_items_data_t1 %>%
+  filter(worker %in% duplicate_items_data_t2$worker) %>%
+  select(extract_items)
+
+duplicate_items_data_t2=duplicate_items_data_t2 %>%
+  filter(worker %in% duplicate_items_data_t1$worker) %>%
+  select(extract_items)
+
+duplicate_items = duplicate_items %>%
+  mutate(t1_t1_cor = NA,
+         t2_t2_cor = NA,
+         t1_t2_cor = NA,
+         t2_t1_cor = NA,
+         t1_t1_polycor = NA,
+         t2_t2_polycor = NA,
+         t1_t2_polycor = NA,
+         t2_t1_polycor = NA)
+
+for(i in 1:nrow(duplicate_items)){
+  duplicate_items$t1_t1_cor[i] = abs(cor(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])],
+                                  duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])]))
+
+  duplicate_items$t2_t2_cor[i] = abs(cor(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])],
+                                  duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])]))
+
+  duplicate_items$t1_t2_cor[i] = abs(cor(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])],
+                                  duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])]))
+
+  duplicate_items$t2_t1_cor[i] = abs(cor(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])],
+                                  duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])]))
+
+  duplicate_items$t1_t1_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])],
+                      duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])]))$rho[2])
+
+  duplicate_items$t2_t2_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])],
+                      duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])]))$rho[2])
+
+  duplicate_items$t1_t2_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])],
+                      duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])]))$rho[2])
+
+  duplicate_items$t2_t1_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])],
+                      duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])]))$rho[2])
+}
+
+for(i in 1:nrow(duplicate_items)){
+  duplicate_items$t1_t1_cor[i] = abs(cor(scale(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])]),
+                                  scale(duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])])))
+
+  duplicate_items$t2_t2_cor[i] = abs(cor(scale(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])]),
+                                  scale(duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])])))
+
+  duplicate_items$t1_t2_cor[i] = abs(cor(scale(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])]),
+                                  scale(duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])])))
+
+  duplicate_items$t2_t1_cor[i] = abs(cor(scale(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])]),
+                                  scale(duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])])))
+
+  duplicate_items$t1_t1_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])],
+                      duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])]))$rho[2])
+
+  duplicate_items$t2_t2_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])],
+                      duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])]))$rho[2])
+
+  duplicate_items$t1_t2_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])],
+                      duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])]))$rho[2])
+
+  duplicate_items$t2_t1_polycor[i] = abs(polychoric(data.frame(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])],
+                      duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])]))$rho[2])
+}
+
+duplicate_items
+```
+
+```{r}
+summary(duplicate_items$t1_t1_cor)
+summary(duplicate_items$t2_t2_cor)
+summary(duplicate_items$t1_t2_cor)
+summary(duplicate_items$t2_t1_cor)
+
+summary(duplicate_items$t1_t1_polycor)
+summary(duplicate_items$t2_t2_polycor)
+summary(duplicate_items$t1_t2_polycor)
+summary(duplicate_items$t2_t1_polycor)
+```
+
+Time 1: item 1 - item 2
+Time 1 item 1 - time 2 item 2
+Time 2 item 1 - time 1 item 2
+Time 2: item 1 - item 2
+
+```{r warning=FALSE, message=FALSE}
+tmp = duplicate_items_data_t1 %>%
+  gather(key, value, -worker)
+
+tmp2 = duplicate_items_data_t2 %>%
+  gather(key, value, -worker)
+
+tmp = duplicate_items %>%
+  select(item1_ID, item2_ID) %>%
+  left_join(tmp, by = c("item1_ID" = "key")) %>%
+  left_join(tmp, by = c("item2_ID" = "key", "worker" = "worker")) %>%
+  rename(item1_time1 = value.x, item2_time1 = value.y) %>%
+  left_join(tmp2, by = c("item1_ID" = "key", "worker" = "worker")) %>%
+  left_join(tmp2, by = c("item2_ID" = "key", "worker" = "worker")) %>%
+  rename(item1_time2 = value.x, item2_time2 = value.y) %>%
+  group_by(item1_ID) %>%
+  mutate(item1_time1 = scale(item1_time1),
+         item1_time2 = scale(item1_time2),
+         item2_time1 = scale(item2_time1),
+         item2_time2 = scale(item2_time2),
+         item1_time1 = ifelse(item1_ID == "mpq_control_survey.13", item1_time1*-1, item1_time1),
+         item1_time2 = ifelse(item1_ID == "mpq_control_survey.13", item1_time2*-1, item1_time2)) %>%
+  ungroup()
+
+p1 = tmp %>%
+  ggplot(aes(item1_time1, item2_time1, col=item1_ID))+
+  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
+  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
+  theme(legend.position = "none")+
+  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
+  xlab("Item 1 T1")+
+  ylab("Item 2 T1")
+
+p2 = tmp %>%
+  ggplot(aes(item1_time1, item2_time2, col=item1_ID))+
+  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
+  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
+  theme(legend.position = "none")+
+  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
+  xlab("Item 1 T1")+
+  ylab("Item 2 T2")
+
+p3 = tmp %>%
+  ggplot(aes(item1_time2, item2_time1, col=item1_ID))+
+  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
+  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
+  theme(legend.position = "none")+
+  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
+  xlab("Item 1 T2")+
+  ylab("Item 2 T1")
+
+p4 = tmp %>%
+  ggplot(aes(item1_time2, item2_time2, col=item1_ID))+
+  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
+  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
+  theme(legend.position = "none")+
+  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
+  xlab("Item 1 T2")+
+  ylab("Item 2 T2")
+
+p5 = arrangeGrob(p1, p2, p3, p4, ncol=2)
+
+ggsave('DataCheckOverlappingItems.jpg', p5, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 500)
+
+rm(tmp, tmp2, p1, p2, p3, p4, p5)
+```
+
+```{r echo=FALSE}
+rm(tmp, comb, t1_2_difference, duplicate_items, duplicate_items_data_t1, duplicate_items_data_t2, extract_items, get_delay_effect)
+```
+
+## Comparison to prior literature
+
+Read in and process bootstrapped results.
+
+```{r}
 boot_df <- read.csv(gzfile(paste0(retest_data_path,'bootstrap_merged.csv.gz')))

### 2018-06-04 code/SRO_Retest_Analyses.Rmd
updates

@@
 
-Are the residuals of this model heteroscedasticity
+Are the residuals of this model heteroscedastic? Yes the residuals do not depend on the predictor.
 
@@
 
+Highlighting the difference between survey and task reliability for comparability to our results.
+
 ```{r}
@@
 
-lit_emp_cor_out = plyr::rdply(100, lit_emp_cor)
-
-write.csv(lit_emp_cor_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/lit_emp_cor_out.csv')
+#lit_emp_cor_out = plyr::rdply(100, lit_emp_cor)
+
+#write.csv(lit_emp_cor_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/lit_emp_cor_out.csv')
+
+lit_emp_cor_out = read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/lit_emp_cor_out.csv')
 
@@
 
+  if(length(unique(sampled_df$task))>1){
     mod_lit = lm(retest_reliability ~ lit_predictor+scale(sample_size)+task, data=sampled_df)
     mod_boot = lm(retest_reliability ~ mean_pearson+scale(sample_size)+task, data=sampled_df)
+  }
+  else{
+    mod_lit = lm(retest_reliability ~ lit_predictor+scale(sample_size), data=sampled_df)
+    mod_boot = lm(retest_reliability ~ mean_pearson+scale(sample_size), data=sampled_df)
+  }
 
@@
 # levels(tmp$stat) <- c("coefficient", expression(r^"2"))
-
-tmp %>%  
-  ggplot(aes(value, fill=sample))+
-  geom_density(alpha = 0.5, position='identity', color=NA)+
-  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
-  scale_fill_manual(breaks=c("boot","lit"),
-                       labels=c("Empirical", "Literature"),
-                      name="Predictor",
-                      values = c("white", "orange"))+
-  xlab('Variance Explained')+
-  ylab('Density')+
-  xlim(0,1)+
-  ylim(0,40)+
-  theme(axis.title.x  = element_text(size=16),
-        axis.text.x  = element_text(size=14),
-        axis.title.y  = element_text(size=16),
-        legend.title  = element_text(size=16),
-        legend.text  = element_text(size=16))
-
-ggsave('LitOnly_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
 
@@
 
-```{r}
-with(comp_lit_pred_out, t.test(m_lit, m_boot))
-```
-
 ```{r echo=FALSE}
 rm(tmp, rel_comp, mod1, mod2, mod3, n_df, i, lit_emp_cor, lit_emp_cor_out, comp_lit_pred, comp_lit_pred_out)
+```
+
+Are you at noise ceiling for suveys vs. tasks?
+
+```{r}
+comp_lit_pred_out_task = plyr::rdply(1000, comp_lit_pred(rel_comp %>% filter(task=="task")))
+comp_lit_pred_out_task$task = "task"
+comp_lit_pred_out_survey = plyr::rdply(1000, comp_lit_pred(rel_comp %>% filter(task=="survey")))
+comp_lit_pred_out_survey$task = "survey"
+comp_lit_pred_out_both = rbind(comp_lit_pred_out_task, comp_lit_pred_out_task)
+
+```
+
+What does it look like if you estimate the left one out using the remaining ones for the noise ceiling model?
+
+```{r}
+
+```
+
+Literature vs. our data on a  measure basis
+
+```{r}
+
+```
+
+Are you better in estimating the literature using our data for surveys vs tasks?
+
+```{r}
+
 ```

### 2018-06-04 code/FrisemFigures.R

@@ -25,6 +25,32 @@ ggsave('Lit_Review_Example.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dr
 #######################################################
 #######################################################
 
+
+tmp %>%  
+  ggplot(aes(value, fill=sample))+
+  geom_density(alpha = 0.5, position='identity', color=NA)+
+  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
+  scale_fill_manual(breaks=c("boot","lit"),
+                    labels=c("Empirical", "Literature"),
+                    name="Predictor",
+                    values = c("white", "orange"))+
+  xlab('Variance Explained')+
+  ylab('Density')+
+  xlim(0,1)+
+  ylim(0,40)+
+  theme(axis.title.x  = element_text(size=16),
+        axis.text.x  = element_text(size=14),
+        axis.title.y  = element_text(size=16),
+        legend.title  = element_text(size=16),
+        legend.text  = element_text(size=16))
+
+ggsave('LitOnly_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
+
+#######################################################
+#######################################################
+#######################################################
+
+
 tmp = measure_labels %>%
   mutate(dv = as.character(dv)) %>%
   left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')

### 2018-06-05 code/SRO_Retest_Analyses.Rmd
additional noise ceiling analyses

@@
 comp_lit_pred_out_survey$task = "survey"
-comp_lit_pred_out_both = rbind(comp_lit_pred_out_task, comp_lit_pred_out_task)
-
+comp_lit_pred_out_both = rbind(comp_lit_pred_out_task, comp_lit_pred_out_survey)
+
+comp_lit_pred_out_both %>%
+  select(-.n, -m_lit, -m_boot) %>%
+  gather(key, value, -task) %>%
+  separate(key, c("stat", "sample"), sep = "_") %>%
+  ggplot(aes(value, fill=sample, alpha=task, color=task))+
+  geom_density(position='identity', size=2)+
+  # facet_grid(~task)+
+  scale_fill_manual(breaks=c("boot","lit"),
+                       labels=c("Empirical", "Literature"),
+                      name="Predictor",
+                      values = c("purple", "orange"))+
+  scale_alpha_manual(breaks=c("survey", "task"),
+                     values = c(0.4, 0.7),
+                     name="Measure type")+
+  scale_color_discrete(name="Measure type")+
+  xlab('Variance Explained')+
+  ylab('Density')
+```
+
+Is this because of less data on surveys? Should I be using a different metric for goodness of fit?
+
+```{r}
+table(rel_comp$task)
+```
+
+Are the differences in the distributions significant?
+The literature does a better job in predicting itself for tasks compared to surveys. s
+
+```{r}
+with(comp_lit_pred_out_both, t.test(r2_lit ~ task))
+```
+
+Our data is better in predicting the literature for the surveys that it is in predicting tasks.
+
+```{r}
+with(comp_lit_pred_out_both, t.test(r2_lit-r2_boot ~ task))
 ```
@@
 What does it look like if you estimate the left one out using the remaining ones for the noise ceiling model?
+What is the distance measure?
+Sample one row of literature, fit model of sample size+task on remaining data, use that model to predict the reliability estimate plugging in the sample size and task for the sampled row in the model
 

### 2018-06-05 code/SRO_Retest_Analyses.Rmd
adding post frisem analyses

@@
 
-  out = data.frame(r2_lit = summary(mod_lit)$r.squared,
-                   r2_boot = summary(mod_boot)$r.squared,
+  out = data.frame(r2_lit = summary(mod_lit)$adj.r.squared,
+                   r2_boot = summary(mod_boot)$adj.r.squared,
                    m_lit = coef(summary(mod_lit))["lit_predictor","Estimate"],
@@
 
-```{r echo=FALSE}
-rm(tmp, rel_comp, mod1, mod2, mod3, n_df, i, lit_emp_cor, lit_emp_cor_out, comp_lit_pred, comp_lit_pred_out)
-```
-
-Are you at noise ceiling for suveys vs. tasks?
+Are you at noise ceiling for suveys vs. tasks? Are you better in estimating the literature using our data for surveys vs tasks?
 
@@
 
-Is this because of less data on surveys? Should I be using a different metric for goodness of fit?
-
-```{r}
-table(rel_comp$task)
-```
-
 Are the differences in the distributions significant?
@@
 
-Our data is better in predicting the literature for the surveys that it is in predicting tasks.
+Our data is better in predicting the literature estimates for the surveys that it is in predicting tasks.
 
@@
 ```
+
+### LOOCV predicting lit vs our data
 
@@
 ```{r}
-
-```
+pred_sample <- function(df){
+
+  get_sample_row <- function(df){
+    if(nrow(df)>1){
+      row_num = sample(1:nrow(df),1)
+      sample_row = df[row_num,]
+    }
+    else{
+      sample_row = df
+    }
+    return(sample_row)
+  }
+
+  test_df = df %>%
+    group_by(dv) %>%
+    do(get_sample_row(.))
+
+  train_df = anti_join(df, test_df)
+
+  if(length(unique(train_df$task))>1){
+    mod = lm(retest_reliability ~ scale(sample_size)+task, data=train_df)
+  }
+  else{
+    mod = lm(retest_reliability ~ scale(sample_size), data=train_df)
+  }
+
+  test_df$pred = predict(mod, test_df)
+
+  # out = data.frame(res_lit = sum(test_df$retest_reliability - pred)^2,
+  #                  res_boot = sum(test_df$mean_pearson - pred)^2)
+
+  return(test_df)
+}
+```
+
+```{r message=FALSE}
+pred_sample_out = plyr::rdply(1000, pred_sample(rel_comp))
+```
+
+Plot difference between
+
+```{r}
+
+pred_sample_out %>%
+  select(pred, retest_reliability, mean_pearson) %>%
+  gather(key, value, -pred) %>%
+  mutate(diff = pred - value) %>%
+  ggplot(aes(value, fill=key))+
+  geom_density(position = "identity", color=NA, alpha=0.5)+
+  scale_fill_manual(breaks=c("mean_pearson","retest_reliability"),
+                       labels=c("Empirical", "Literature"),
+                      name="Predicting",
+                      values = c("purple", "orange"))
+
+```
+
+Plot difference between prediction and value broken down by measure type
+
+```{r}
+pred_sample_out %>%
+  select(task, pred, retest_reliability, mean_pearson) %>%
+  gather(key, value, -task, -pred) %>%
+  mutate(diff = pred - value) %>%
+  ggplot(aes(value, fill=key, color=task, alpha=task))+
+  geom_density(position = "identity", size=2)+
+  scale_fill_manual(breaks=c("mean_pearson","retest_reliability"),
+                       labels=c("Empirical", "Literature"),
+                      name="Predicting",
+                      values = c("purple", "orange"))+
+  scale_alpha_manual(breaks=c("survey", "task"),
+                     values = c(0.4, 0.7),
+                     name="Measure type")+
+  scale_color_discrete(name="Measure type")
+```
+
+Data versus model prediction plot
+
+```{r}
+
+```
+
+Distributions of sum squared residual
+
+```{r}
+
+```
+
+### Measure level comparison
 
@@
 
-Are you better in estimating the literature using our data for surveys vs tasks?
-
-```{r}
-
+```{r echo=FALSE}
+rm(tmp, rel_comp, mod1, mod2, mod3, n_df, i, lit_emp_cor, lit_emp_cor_out, comp_lit_pred, comp_lit_pred_out)
 ```
@@
 
+### Meaningful variables
+
+ADD!!!!
+
+```{r}
+
+```
+
 ### Number of trials

### 2018-06-05 code/SRO_Retest_Analyses.Rmd
adding post frisem analyses

@@
 What does it look like if you estimate the left one out using the remaining ones for the noise ceiling model?
-What is the distance measure?
-Sample one row of literature, fit model of sample size+task on remaining data, use that model to predict the reliability estimate plugging in the sample size and task for the sampled row in the model
+Sample one row of literature, fit model of sample size+task on remaining data, use that model to predict the reliability estimates, compare those to the left out reliability estimate from the literature versus the average reliability estimate from our data
 
@@
 
+Why did I have to run it separately for the function before but can run it on all data once here? Before the output was model fits for all measures. Here the output is measure level prediction.
+
 ```{r message=FALSE}
@@
 
-Plot difference between
-
-```{r}
-
-pred_sample_out %>%
-  select(pred, retest_reliability, mean_pearson) %>%
-  gather(key, value, -pred) %>%
-  mutate(diff = pred - value) %>%
-  ggplot(aes(value, fill=key))+
+Plot difference between prediction and value of either the lit estimate or the average estimate from our data
+
+```{r}
+tmp = pred_sample_out %>%
+  select(task,pred, retest_reliability, mean_pearson) %>%
+  gather(key, value, -task, -pred) %>%
+  mutate(diff = (pred - value)^2)
+
+tmp%>%  
+  ggplot(aes(diff, fill=key))+
   geom_density(position = "identity", color=NA, alpha=0.5)+
@@
                       values = c("purple", "orange"))
-
-```
-
-Plot difference between prediction and value broken down by measure type
-
-```{r}
-pred_sample_out %>%
-  select(task, pred, retest_reliability, mean_pearson) %>%
-  gather(key, value, -task, -pred) %>%
-  mutate(diff = pred - value) %>%
-  ggplot(aes(value, fill=key, color=task, alpha=task))+
+```
+
+Are the means of these distributions different? Yes: the difference is larger when predicting the left-out value from the literature versus predicting the left-out average from our data
+
+```{r}
+with(tmp, t.test(diff ~ key))
+```
+
+Plot difference between prediction and value broken down by measure type.
+Looks like there might be an interaction between the measure type and whether the left out sample is a value from the literature versus the average from our data.
+The difference between the prediction and left value seems smaller on average for survey measures compared to survey measures.
+Moreover, for survey measures predictions of the literature are better compared to predictions of our data but the opposite is true for task measures.
+
+```{r}
+tmp%>%
+  ggplot(aes(diff, fill=key, color=task, alpha=task))+
   geom_density(position = "identity", size=2)+
@@
                      name="Measure type")+
-  scale_color_discrete(name="Measure type")
+  scale_color_discrete(name="Measure type")+
+
+```
+
+Can we capture this interaction in a single model?
+
+```{r}
+summary(lm(value ~ key*task,tmp))
 ```

### 2018-06-05 code/SRO_Retest_Analyses.Rmd
adding post frisem analyses

@@
   gather(key, value, -task, -pred) %>%
-  mutate(diff = (pred - value)^2)
+  mutate(sq_diff = (pred - value)^2)
 
 tmp%>%  
-  ggplot(aes(diff, fill=key))+
+  ggplot(aes(sq_diff, fill=key))+
   geom_density(position = "identity", color=NA, alpha=0.5)+
@@
 
-Are the means of these distributions different? Yes: the difference is larger when predicting the left-out value from the literature versus predicting the left-out average from our data
-
-```{r}
-with(tmp, t.test(diff ~ key))
+Are the means of these distributions different?
+Yes: the difference is larger when predicting the left-out value from our data versus predicting left out value from literature.
+The difference seems pretty small though.
+
+```{r}
+with(tmp, t.test(sq_diff ~ key))
 ```
@@
 Plot difference between prediction and value broken down by measure type.
-Looks like there might be an interaction between the measure type and whether the left out sample is a value from the literature versus the average from our data.
-The difference between the prediction and left value seems smaller on average for survey measures compared to survey measures.
-Moreover, for survey measures predictions of the literature are better compared to predictions of our data but the opposite is true for task measures.
 
@@
 tmp%>%
-  ggplot(aes(diff, fill=key, color=task, alpha=task))+
+  ggplot(aes(sq_diff, fill=key, color=task, alpha=task))+
   geom_density(position = "identity", size=2)+
@@
                      name="Measure type")+
-  scale_color_discrete(name="Measure type")+
-
+  scale_color_discrete(name="Measure type")
 ```
@@
 Can we capture this interaction in a single model?
-
-```{r}
-summary(lm(value ~ key*task,tmp))
-```
-
-Data versus model prediction plot
-
-```{r}
-
+Yes.
+The significant interaction suggests that the squared difference is larger for predicting the literature compared to predicting our data for surveys while for tasks the squared difference is larger when predicting our data compared to predicting the literature.
+(This fits with other results too: our results differ from the literature more for the survey measures)
+
+```{r}
+aggregate(sq_diff ~ key*task,tmp, FUN=mean)
+```
+
+```{r}
+summary(lm(sq_diff ~ key*task,tmp))
+```
+
+Data versus model prediction plot: The predictions are not veriable so they don't really capture the variability neither in the literature nor in our data very well.
+
+```{r}
+tmp %>%
+  ggplot(aes(value, pred, color=task))+
+  geom_point()+
+  facet_wrap(~key)
 ```
@@
 ```{r}
-
+pred_sample_out %>%
+  mutate(sq_diff_lit = (pred - retest_reliability)^2,
+         sq_diff_emp = (pred - mean_icc)^2) %>%
+  group_by(.n, task) %>%
+  summarise(sum_sq_diff_lit = sum(sq_diff_lit),
+            sum_sq_diff_emp = sum(sq_diff_emp)) %>%
+  # select(-'.n') %>%
+  gather(key, value, -task, -.n) %>%
+  ggplot(aes(value, fill=key, color=task))+
+  geom_density(size=1)+
+  scale_fill_manual(breaks=c("sum_sq_diff_emp","sum_sq_diff_lit"),
+                       labels=c("Empirical", "Literature"),
+                      name="Predicting",
+                      values = c("purple", "orange"))+
+  scale_alpha_manual(breaks=c("survey", "task"),
+                     values = c(0.4, 0.7),
+                     name="Measure type")+
+  scale_color_discrete(name="Measure type")
 ```

### 2018-06-06 code/SRO_Retest_Analyses.Rmd
adding post frisem analyses

@@
 
-Distributions of sum squared residual
+Distributions of sum squared residual: Residuals are larger for tasks compared to surveys (i.e.
+predictions are worse when predicting task variables - possibly because their variability is higher?).
+For surveys the predictions of the literature are better than predictions of our data while the opposite is true for task measures.
+
+Does this make sense with the results above? Figure out how to think of the noise ceiling analyses and LOOCV results together.
 
@@
   gather(key, value, -task, -.n) %>%
-  ggplot(aes(value, fill=key, color=task))+
+  ggplot(aes(value, fill=key, color=task, alpha=task))+
   geom_density(size=1)+

### 2018-06-06 code/SRO_Retest_Analyses.Rmd
added lit ve emp measure plot

@@
 
-```{r}
-
+```{r warning=FALSE, message=FALSE}
+p1 = rel_comp %>%
+  filter(task == 'task') %>%
+ggplot(aes(x = var, y = retest_reliability)) + 
+  geom_boxplot(fill='#00BFC4', position="identity")+
+  geom_point(aes(x = var, y = mean_pearson),color="purple", fill="purple", size=3, shape=23)+
+  coord_flip()+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom') + 
+  xlab("")+
+  ylab("")+
+  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))
+
+p2 = rel_comp %>%
+  filter(task == 'survey') %>%
+ggplot(aes(x = var, y = retest_reliability)) + 
+  geom_boxplot(fill='#F8766D', position="identity")+
+  geom_point(aes(x = var, y = mean_pearson),color="purple", fill="purple", size=3, shape=23)+
+  coord_flip()+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom') + 
+  xlab("")+
+  ylab("")+
+  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))
+
+p3 <- arrangeGrob(p1, p2,nrow=1)
+
+ggsave('LitVsEmp_Measure_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 20, units = "in", dpi=100)
+rm(p1, p2, p3)
+```
+
+```{r echo=FALSE, out.width='100%'}
+knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/LitVsEmp_Measure_Plot.jpg')
 ```

### 2018-06-06 code/SRO_Retest_Analyses.Rmd
added lit ve emp measure plot

@@
 
-### Overlapping survery questions
+### Overlapping survey questions
 
@@
 The bootstrapped version is essentially the same but the plots are busier due to more datapoints.
+
+```{r}
+numeric_cols = c()
+
+for(i in 1:length(names(test_data))){
+  if(is.numeric(test_data[,i]) & names(test_data)[i] %in% names(retest_data)){
+    numeric_cols <- c(numeric_cols, names(test_data)[i])
+  }
+}
+#Create df of point estimate reliabilities
+rel_df <- data.frame(spearman = rep(NA, length(numeric_cols)),
+                     icc = rep(NA, length(numeric_cols)),
+                     pearson = rep(NA, length(numeric_cols)),
+                     partial_eta_sq = rep(NA, length(numeric_cols)),
+                     sem = rep(NA, length(numeric_cols)),
+                     var_subs = rep(NA, length(numeric_cols)),
+                     var_ind = rep(NA, length(numeric_cols)),
+                     var_resid = rep(NA, length(numeric_cols)))
+
+row.names(rel_df) <- numeric_cols
+
+for(i in 1:length(numeric_cols)){
+  rel_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i]) 
+  rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
+  rel_df[numeric_cols[i], 'pearson'] <- get_pearson(numeric_cols[i])
+  rel_df[numeric_cols[i], 'partial_eta_sq'] <- get_partial_eta(numeric_cols[i])
+  rel_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
+  rel_df[numeric_cols[i], 'var_subs'] <- get_var_breakdown(numeric_cols[i])$subs
+  rel_df[numeric_cols[i], 'var_ind'] <- get_var_breakdown(numeric_cols[i])$ind
+  rel_df[numeric_cols[i], 'var_resid'] <- get_var_breakdown(numeric_cols[i])$resid
+}
+
+rel_df$dv = row.names(rel_df)
+row.names(rel_df) = seq(1:nrow(rel_df))
+rel_df$task = 'task'
+rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
+rel_df[grep('holt', rel_df$dv), 'task'] = "task"
+rel_df = rel_df %>%
+  select(dv, task, spearman, icc, pearson, partial_eta_sq, sem, var_subs, var_ind, var_resid)
+# row.names(rel_df) = NULL
+
+```
 
@@
 Another way might be to compute confidence intervals using SEMs as described in the second half of Weir (2005) and check what percent of participants have scores that fall out of this range.
-I haven't pursued this for now.
-
-Here we ask: Which variables have significant time effects in more than 5% of the bootstrapped samples?
+
+First we ask: Which variables have significant time effects in more than 5% of the bootstrapped samples?
 
@@
 
-Are they predominantly in one or the other direction and does that differ depending on survey vs task?
-
 ```{r}
@@
 
-ADD!!!!
-
 ```{r}

### 2018-06-06 code/SRO_Retest_Analyses.Rmd
added meaningful vars file

@@
 
+NOTE: THIS MIGHT GIVE A FALSE SENSE OF HOW GOOD EACH TASK IS. SEE MEANINGFUL VARIABLES ANALYSES FOR TASKS.
+
 ```{r warning=FALSE, message=FALSE}
@@
 ### Meaningful variables
+
+The above averaging of reliability estimates for all measures of tasks might not be the best way to look at how reliable a task is.
+
+Not all measures for which we have calculated reliability estimates are measures that are used in the literature for these tasks
+
+Dealing with this:
+using the measures you found in the literature
+using ian's function
 

### 2018-06-06 code/SRO_Retest_Analyses.Rmd
started meaningful var analyses

@@
 
-Dealing with this:
-using the measures you found in the literature
-using ian's function
-
-```{r}
-
+We have a list of measures we extracted from the literature as the canonical ones used for analyses.
+
+```{r}
+meaningful_vars = read.table('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/meaningful_vars.txt')
+meaningful_vars = as.character(meaningful_vars$V1)
+
+tmp = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% meaningful_vars == FALSE)])
+tmp = tmp[-grep('survey', tmp)]
+
+meaningful_vars = c(meaningful_vars, tmp)
+meaningful_vars = sort(meaningful_vars)
 ```

### 2018-06-07 code/SRO_Retest_Analyses.Rmd
updated analyses for ranking tasks for meaningful variables only

--- 2018-06-06 code/SRO_Retest_Analyses.Rmd
@@
 
-We reduce the list of task measures to a list of one per task by averaging only the raw measures from all the trials in a task.
-We chose to reduce the information in this manner to avoid any bias stemming from differential amount of interest and procedures applied to certain tasks over others (e.g.
-a task can have over 10 measures because it has multiple conditions and we have chosen to fit DDM's for specific conditions while another might only have 2 due to our relative inexperience and lack of interest in it).
-We check whether the number of trials in a task has a significant effect on these average reliabilities of raw measures as well.
-
-We filter out the DDM parameters and measures for specific contrasts.
-Note that this does leave some tasks with measures that are model fits and/or for specific conditions (because at least the current datasets do not include measures that are based on all the trials **and** are raw though I could dive in to variables_exhaustive for such measures.
-For example the average relialibility for Kirby is based on three discount rates for specific conditions.).
-Here's the order of tasks by mean reliability sorted for ICC and then Spearman's $\rho$.
+We reduce the list of task measures to a list of one per task by averaging only the measures that are extracted and used from these tasks in the literature. We call these the 'meaningful measures.'
+
+```{r}
+meaningful_vars = read.table('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/meaningful_vars.txt')
+meaningful_vars = as.character(meaningful_vars$V1)
+
+tmp = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% meaningful_vars == FALSE)])
+tmp = tmp[-grep('survey', tmp)]
+
+meaningful_vars = c(meaningful_vars, tmp)
+meaningful_vars = sort(meaningful_vars)
+```
 
@@
   mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv') %>%
-  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
+  filter(task == 'task',
+         dv %in% meaningful_vars) %>%
+  left_join(boot_df[,c("dv", "icc")], by = 'dv') %>%
   separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
@@
   summarise(median_icc = median(icc),
-            median_spearman = median(spearman),
             icc_2.5 = quantile(icc, probs = 0.025),
             icc_97.5 = quantile(icc, probs = 0.975),
-            min_spearman = min(spearman),
-            max_spearman = max(spearman),
             num_measures = n()/1000,
             mean_num_trials = round(mean(num_all_trials)))%>%
-  arrange(-median_icc, -median_spearman)
+  arrange(-median_icc)
 
@@
   datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc',
-                        'min_spearman', 'icc_2.5',
-                        'max_spearman', 'icc_97.5'), digits=3)
+  formatRound(columns=c('median_icc','icc_2.5','icc_97.5'), digits=3)
 ```
@@
 tmp = tmp%>%
-  select(-median_spearman, -min_spearman, -max_spearman) %>%
   mutate(task_name = gsub("_", " ", task_name),
@@
 
-### Meaningful variables
-
-```{r}
-
-```
-
 ### Number of trials
 
-Does number of items in a task have a significant effect on the average ICC of (mostly) raw measures for all trials from a task? No. (no effect on Spearman either)
+Does number of items in a task have a significant effect on the average ICC of meaningful measures for all trials from a task? No.
 
@@
   mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  # left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  left_join(boot_df[,c("dv", "spearman","icc")], by='dv') %>%
-  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
+  filter(task == 'task',
+         dv %in% meaningful_vars) %>%
+  left_join(boot_df[,c("dv", "icc")], by = 'dv') %>%
   separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
@@
 ```{r warning=FALSE, message=FALSE}
-measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  # left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  left_join(boot_df[,c("dv", "spearman","icc")], by='dv') %>%
-  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
-  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
-  select(-extra_1, -extra_2) %>%
+tmp %>%
   ggplot(aes(num_all_trials, icc))+
@@
 
-For this example we look at the retest reliability of the three dependent measures (average accuracy, median response time, total score) from the hierarchical rule task with 360 trials.
+For this example we look at the retest reliability of dependent measures from the threebytwo with >400 trials.
 Here is a graph of how the point estimates of the retest reliability changes for each of the dependent measures using different numbers of trials to estimate them.
-While the reliability estimate for each of the variables respectively are ..., ...
-and ...
-using all of the trials, these values are independent of number of trials used in the task for only certain variables.
-Based on this analysis researchers might decide to use a version of the task with fewer trials or only measures with consistently high reliability estimates.
-
-Example task: three by two
 

### 2018-06-07 code/SRO_Retest_Analyses.Rmd
updated ddm analyses as contrast vs. non-contrast

@@
 
+Takeaways from this graph:
+- Reliability estimates stabilize after about an eigthth of the trials (note that this might not be true for other model parameter estimates; here we are only looking at raw response time and accuracy measures)
+- Only three measures that are not contrast measures have reliabilities >0
+- All the other measures are basically completely unreliable (including the two 'meaningful variables' in the literature: the cue switch cost RT's)
+
 ```{r warning=FALSE, message=FALSE}
@@
 
+cols <- c("Accuracy" = '#084594', "Average RT error" = '#99000d', "Average RT correct" = '#ef3b2c', "Missed percentage" = '#2171b5', "Cue switch cost RT (100)" = '#fc9272', "Cue switch cost RT (900)" = '#fcbba1', "Task switch cost RT (100)" = '#fee0d2', "Task switch cost RT (900)" = '#fff5f0', "Cue switch cost Acc (100)" = '#4292c6', "Cue switch cost Acc (900)" = '#6baed6', "Task switch cost Acc (100)" = '#9ecae1', "Task switch cost Acc (900)" = '#c6dbef')
+
 trial_num_rel_df %>%
+  select(-std_rt_icc, -std_rt_error_icc)%>%
   gather(key, value, -breaks) %>%
-  ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_error_icc", "std_rt_error_icc", "avg_rt_icc", "std_rt_icc", "missed_percent_icc", "cue_switch_cost_rt_100_icc", "cue_switch_cost_rt_900_icc", "task_switch_cost_rt_100_icc", "task_switch_cost_rt_900_icc", "cue_switch_cost_acc_100_icc", "cue_switch_cost_acc_900_icc", "task_switch_cost_acc_100_icc", "task_switch_cost_acc_900_icc"), labels = c("Accuracy", "Average RT error", "SD RT error", "Average RT correct", "SD RT correct", "Missed percentage", "Cue switch cost RT (100)", "Cue switch cost RT (900)", "Task switch cost RT (100)", "Task switch cost RT (900)", "Cue switch cost Acc (100)", "Cue switch cost Acc (900)", "Task switch cost Acc (100)", "Task switch cost Acc (900)"))))+
+  ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_error_icc", "avg_rt_icc", "missed_percent_icc", "cue_switch_cost_rt_100_icc", "cue_switch_cost_rt_900_icc", "task_switch_cost_rt_100_icc", "task_switch_cost_rt_900_icc", "cue_switch_cost_acc_100_icc", "cue_switch_cost_acc_900_icc", "task_switch_cost_acc_100_icc", "task_switch_cost_acc_900_icc"), labels = c("Accuracy", "Average RT error", "Average RT correct", "Missed percentage", "Cue switch cost RT (100)", "Cue switch cost RT (900)", "Task switch cost RT (100)", "Task switch cost RT (900)", "Cue switch cost Acc (100)", "Cue switch cost Acc (900)", "Task switch cost Acc (100)", "Task switch cost Acc (900)"))))+
   geom_point()+
@@
   scale_color_manual(values = cols,
-                     breaks = c("Average RT error", "Accuracy", "SD RT error", "Missed percentage", "Average RT correct", "Cue switch cost Acc (100)", "SD RT correct", "Cue switch cost Acc (900)", "Cue switch cost RT (100)", "Task switch cost Acc (100)", "Task switch cost RT (100)", "Task switch cost Acc (900)", "Task switch cost RT (900)"))+
+                     breaks = c("Average RT correct", "Average RT error", "Cue switch cost RT (100)","Cue switch cost RT (900)", "Task switch cost RT (100)","Task switch cost RT (900)","Accuracy", "Missed percentage", "Cue switch cost Acc (100)", "Cue switch cost Acc (900)",  "Task switch cost Acc (100)",  "Task switch cost Acc (900)"))+
   ylim(-1,1)+
-  guides(color = guide_legend(ncol=2, byrow=T))
+  guides(color = guide_legend(ncol=2, byrow=F))
 
@@
 tmp = measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
+  mutate(dv = as.character(dv),
+         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
   filter(ddm_task == 1, 
-         overall_difference != "condition",
+         #overall_difference != "condition",
          rt_acc != 'other') %>%
   drop_na() %>%
-  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')
-
-tmp %>%
+  left_join(boot_df[,c("dv", "icc")], by = 'dv')
+
+tmp = tmp %>%
   drop_na() %>% #try removing this in final release
-  group_by(overall_difference, raw_fit, rt_acc) %>%
+  group_by(contrast, raw_fit, rt_acc) %>%
   summarise(icc_median = quantile(icc, probs = 0.5),
@@
             icc_97.5 = quantile(icc, probs = 0.975),
-            spearman_median = quantile(spearman, probs = 0.5),
-            spearman_2.5 = quantile(spearman, probs = 0.025),
-            spearman_97.5 = quantile(spearman, probs = 0.975),
-            num_vars = n()/1000) %>%
+            num_vars = n()/1000)
+
+tmp %>% 
   datatable() %>%
-  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
+  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5'), digits=3)
 ```
@@
 tmp_save = tmp %>%
-  drop_na() %>% #try removing this in final release
-  group_by(overall_difference, raw_fit, rt_acc) %>%
-  summarise(icc_median = quantile(icc, probs = 0.5),
-            icc_2.5 = quantile(icc, probs = 0.025),
-            icc_97.5 = quantile(icc, probs = 0.975),
-            num_vars = n()/1000) %>%
   ungroup() %>%
-  mutate(overall_difference = as.character(overall_difference),
+  mutate(contrast = as.character(contrast),
          raw_fit = as.character(raw_fit),

### 2018-06-07 code/SRO_Retest_Analyses.Rmd
cleanup

@@
   filter(ddm_task == 1, 
-         #overall_difference != "condition",
          rt_acc != 'other') %>%
@@
 
-tmp = tmp %>%
+tmp_save = tmp %>%
   drop_na() %>% #try removing this in final release
@@
 
-tmp %>% 
+tmp_save %>% 
   datatable() %>%
@@
 ```{r}
-tmp_save = tmp %>%
+tmp_save = tmp_save %>%
   ungroup() %>%
@@
 
-Comparing overall vs difference: overall has higher reliability than difference.
-
-```{r}
-summary(lmerTest::lmer(icc ~ overall_difference + (1|dv) ,tmp))
-```
-
-"consistent with the summing of variance in the difference score"
-
-```{r}
-tmp = measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(ddm_task == 1, 
-         overall_difference != "condition",
-         rt_acc != 'other') %>%
-  drop_na() %>%
-  left_join(boot_df[,c("dv", "icc", "var_subs","var_ind", "var_resid")], by = 'dv') %>%
-  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid),
-         var_ind_pct = var_ind/(var_subs+var_ind+var_resid), 
-         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)) %>%
-  select(-task, -ddm_task, -num_all_trials, -var_resid, -var_subs, -var_ind) %>%
-  gather(key, value, -dv, -overall_difference, -raw_fit, -rt_acc, -icc)
-
-tmp %>%
-  filter(key == "var_resid_pct") %>%
-  ggplot(aes(raw_fit, value, fill=overall_difference))+
-  geom_boxplot()
-
-summary(lmer(value  ~ overall_difference*raw_fit + (1|dv), data=tmp %>% filter(key=="var_resid_pct")))
-
-#Simple effects
-summary(lmer(value  ~ overall_difference + (1|dv), data=tmp %>% filter(key=="var_resid_pct", raw_fit== "EZ")))
-
-summary(lmer(value  ~ overall_difference + (1|dv), data=tmp %>% filter(key=="var_resid_pct", raw_fit== "raw")))
-
-summary(lmer(value  ~ overall_difference + (1|dv), data=tmp %>% filter(key=="var_resid_pct", raw_fit== "hddm")))
-```
-
-Checking Rogosa's claim that ‘Difference scores are reliable when individual differences in true change exist.’
-How do we measure ‘individual difference in true change’ 
-1.between subject variability in difference score distributions
-2.within subject variance in icc
-Using 2 (because comparable between subject variance across different measures would be hard)
-Expecting to see: positive correlation between mean icc and mean var_ind_pct
-Result: The correlation between mean icc and mean var ind pct is NOT significant BUT looking at the distribution of mean var ind pct there is not a lot of variability t
-
-```{r}
-tmp = tmp %>%
-  spread(key, value) %>%
-  group_by(dv) %>%
-  summarise(mean_var_ind_pct = mean(var_ind_pct),
-            mean_var_subs_pct = mean(var_subs_pct),
-            mean_icc = mean(icc)) %>%
-  left_join(measure_labels, by='dv')
-
-tmp %>%
-  filter(overall_difference == 'difference') %>%
-  ggplot(aes(mean_var_ind_pct, mean_icc))+
-  geom_point()+
-  geom_abline(slope=1, intercept=0)+
-  geom_smooth(method = "lm")
-
-summary(lm(mean_icc ~ mean_var_ind_pct,data=tmp %>%
-  filter(overall_difference == 'difference')))
-
-tmp %>%
-  filter(overall_difference == 'difference') %>%
-  ggplot(aes(mean_var_ind_pct))+
-  geom_density()
-
-summary(tmp$mean_var_ind_pct[tmp$overall_difference == "difference"])
-summary(tmp$mean_var_subs_pct[tmp$overall_difference == "difference"])
-
-tmp = tmp %>% filter(overall_difference == 'difference')
-t.test(tmp$mean_var_ind_pct, tmp$mean_var_subs_pct, paired=T)
-```
-
-```{r}
-tmp = measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(ddm_task == 1, 
-         overall_difference != "condition",
-         rt_acc != 'other') %>%
-  drop_na() %>%
-  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')
+Comparing contrast vs non-contrast: overall has higher reliability than difference.
+
+```{r}
+summary(lmerTest::lmer(icc ~ contrast + (1|dv) ,tmp))
 ```
@@
 ```{r}
-summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(overall_difference == "overall")))
+summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "non-contrast")))
 ```
@@
 ```{r}
-summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(overall_difference == "difference")))
+summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "contrast")))
 ```
@@
   geom_boxplot()+
-  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
+  facet_wrap(~factor(contrast, levels=c("non-contrast", "contrast"), labels=c("Non-contrast", "Contrast")))+
   theme_bw()+
@@
 tmp2 = measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
+  mutate(dv = as.character(dv),
+         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
   filter(ddm_task == 1, 
-         overall_difference != "condition",
-         rt_acc != "other",
-         raw_fit != "hddm") %>%
+         rt_acc != 'other') %>%
   drop_na() %>%
-  left_join(rel_df[,c("dv", "icc", "spearman")], by = 'dv')
+  left_join(rel_df[,c("dv", "icc")], by = 'dv')
 
 tmp2 %>%
-  # filter(overall_difference == "overall") %>%
   ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
   geom_boxplot()+
-  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall (all trials)", "Difference (contrasting conditions)")))+
+  facet_wrap(~factor(contrast, levels=c("non-contrast", "contrast"), labels=c("Non-contrast", "Contrast")))+
   theme_bw()+
@@
   filter(task == 'survey') %>%
-  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv') %>%
-  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
+  left_join(boot_df[,c("dv", "icc")], by = 'dv') %>%
   separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
-  select(-extra_1, -extra_2) %>%
+  select(-extra_1, -extra_2)
+
+tmp_save = tmp %>%
   group_by(task_name) %>%
   summarise(median_icc = median(icc),
-            median_spearman = median(spearman),
             icc_2.5 = quantile(icc, probs = 0.025),
             icc_97.5 = quantile(icc, probs = 0.975),
-            min_spearman = min(spearman),
-            max_spearman = max(spearman),
             num_measures = n()/1000,
             mean_num_trials = round(mean(num_all_trials)))%>%
-  arrange(-median_icc, -median_spearman)
-
-tmp %>%
+  arrange(-median_icc)
+
+tmp_save %>%
   datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc',
-                        'min_spearman', 'icc_2.5',
-                        'max_spearman', 'icc_97.5'), digits=3)
-```
-
-```{r}
-tmp = tmp%>%
-  select(-min_spearman, -max_spearman,-median_spearman) %>%
+  formatRound(columns=c('median_icc', 'icc_2.5','icc_97.5'), digits=3)
+```
+
+```{r}
+tmp_save = tmp_save%>%
   mutate(task_name = gsub("_", " ", task_name),
@@
 
-names(tmp) = gsub("_", " ", names(tmp))
-names(tmp) = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", names(tmp), perl=TRUE)
-
-sjt.df(tmp %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/survey_rel_table.doc")
+names(tmp_save) = gsub("_", " ", names(tmp_save))
+names(tmp_save) = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", names(tmp_save), perl=TRUE)
+
+sjt.df(tmp_save %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/survey_rel_table.doc")
 ```
@@
 ```{r warning=FALSE, message=FALSE}
-tmp = measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(task == 'survey') %>%
-  # left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  left_join(boot_df[,c("dv", "spearman","icc")], by='dv') %>%
-  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
-  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
-  select(-extra_1, -extra_2)
-
-# summary(lm(icc ~ num_all_trials, data = tmp))
 summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))

### 2018-06-07 code/SRO_Retest_Analyses.Rmd
working on explaining the noise ceiling results with loocv results

@@
 
-### Direct relation to our results
+### Correlation with our results
 
@@
 Are the differences in the distributions significant?
-The literature does a better job in predicting itself for tasks compared to surveys. s
+There is a significant interaction, such that...
+
+```{r}
+tmp = comp_lit_pred_out_both %>%
+  select(-.n, -m_lit, -m_boot) %>%
+  gather(key, value, -task)
+
+summary(lm(value ~ key*task, tmp))
+```
+
+The literature does a better job in predicting itself for tasks compared to surveys (comparing the two orange distributions).
 
@@
 
-Our data is better in predicting the literature estimates for the surveys that it is in predicting tasks.
+Our data is better in predicting the literature estimates for the surveys that it is in predicting tasks (comparing the difference between orange and purple for red and blue outlines).
 
@@
 with(comp_lit_pred_out_both, t.test(r2_lit-r2_boot ~ task))
+```
+
+Why are the reliability estimates from surveys worse compared to tasks in predicting the literature?
+
+Rank by variance: empirical estimates for surveys < literature estimates for surveys < empirical estimates for tasks < literature estimates for tasks
+
+In this procedure having high variance is better. When predicting the literature using an empirical estimate for a survey measure
+
+```{r}
+rel_comp %>%
+  select(task, retest_reliability, mean_pearson) %>%
+  gather(key, value, -task) %>%
+  group_by(key, task) %>%
+  summarise(variance = var(value)) %>%
+  ungroup()%>%
+  mutate(key = ifelse(key == "mean_pearson", "emp", "lit")) %>%
+  arrange(variance)
 ```

### 2018-06-07 code/SRO_Retest_Analyses.Rmd
expanded similar item analyses

@@
   filter(similarity>0.8) %>%
-  select(item1_ID, item2_ID, item1_text, item2_text)
+  select(similarity, item1_ID, item2_ID, item1_text, item2_text) %>%
+  arrange(-similarity)
 
@@
 
-duplicate_items
-```
-
-```{r}
-summary(duplicate_items$t1_t1_cor)
-summary(duplicate_items$t2_t2_cor)
-summary(duplicate_items$t1_t2_cor)
-summary(duplicate_items$t2_t1_cor)
+duplicate_items %>%
+  arrange(-t1_t1_polycor, -t2_t2_polycor)
+```
+
+```{r}
+# summary(duplicate_items$t1_t1_cor)
+# summary(duplicate_items$t2_t2_cor)
+# summary(duplicate_items$t1_t2_cor)
+# summary(duplicate_items$t2_t1_cor)
 
@@
 summary(duplicate_items$t2_t2_polycor)
-summary(duplicate_items$t1_t2_polycor)
-summary(duplicate_items$t2_t1_polycor)
+# summary(duplicate_items$t1_t2_polycor)
+# summary(duplicate_items$t2_t1_polycor)
+```
+
+```{r}
+tmp = duplicate_items %>%
+  select(similarity, t1_t1_polycor, t2_t2_polycor) %>%
+  gather(key, value, -similarity)
+
+# tmp = duplicate_items %>%
+#   select(similarity, t1_t1_polycor, t1_t2_polycor, t2_t2_polycor, t2_t1_polycor) %>%
+#   gather(key, value, -similarity)
+
+tmp %>%
+  ggplot(aes(similarity, value, col=key))+
+  geom_smooth(method="lm", se=FALSE)
+
+summary(lm(value~key*similarity,tmp))
 ```

### 2018-06-07 code/SRO_Retest_Analyses.Rmd
wrapped up draft analyses

@@
 knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/LitVsEmp_Measure_Plot.jpg')
+```
+
+```{r}
+rel_comp %>%
+  group_by(dv, task) %>%
+  summarise(mean_lit = mean(retest_reliability),
+            mean_emp = unique(mean_pearson)) %>%
+  ggplot(aes(mean_emp, mean_lit, col=task))+
+  geom_smooth(method="lm")+
+  geom_point()+
+  xlim(-0.25, 1)+
+  ylim(-0.25, 1)+
+  ylab("Average Literature Reliability Estimate")+
+  xlab("Average Empirical Reliability Estimate")+
+  theme(legend.title = element_blank(),
+        legend.position = 'bottom')
+
+ggsave('LitAndEmpAveCor.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
 ```
@@
 ```{r}
+tmp %>%
+  group_by(contrast) %>%
+  summarise(mean_icc = mean(icc),
+            sd_icc = sd(icc))
+```
+
+```{r}
 tmp2 = measure_labels %>%

### 2018-07-18 code/Boot_Figure.Rmd
created interactive figures page

---
title: "Bootstrapped Retest Reliability Figure"
output:
  html_document: default
  pdf_document: default
---

his is an [R Markdown](http://rmarkdown.rstudio.com) Notebook. When you execute code within the notebook, the results appear beneath the code.

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*.

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

### 2018-07-18 code/Boot_Figure.Rmd
changing strategy from using plotly for all measures to shiny app filtering tasks

@@
 
-his is an [R Markdown](http://rmarkdown.rstudio.com) Notebook. When you execute code within the notebook, the results appear beneath the code.
-
-Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*.
-
-```{r}
-plot(cars)
+```{r, message=FALSE, warning=FALSE, include=FALSE}
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(gridExtra)
+library(GGally)
+library(stringr)
+library(plotly)
+sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
+options(scipen = 1, digits = 4, width = 500)
 ```
-
-Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.
-
-When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).
-
-The preview shows you a rendered HTML copy of the contents of the editor.
-Consequently, unlike *Knit*, *Preview* does not run any R code chunks.
-Instead, the output of the chunk when it was last run in the editor is displayed.

### 2018-07-18 code/Lit_Review_Figure.Rmd
changing strategy from using plotly for all measures to shiny app filtering tasks

--- 2017-10-03 code/Lit_Review_Figure.Rmd
@@
 
+```{r warning=FALSE, message=FALSE}
+fig_data = fig_data %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)]),
+         raw1_fit0 = grepl('raw', raw_fit),
+         type = as.character(type)) %>%
+  arrange(task_group, -raw1_fit0)
+```
+
 References mentioned in the plot below can be found [here](https://docs.google.com/spreadsheets/d/1hcED4_rWSGSE8Td0aqT0kWqlLCBAzRNKBXj3tSram58/edit?usp=sharing).
 
-Interactive plot
+# Interactive plot
 
@@
          days_cutoff = ifelse(days < 60, days, 120),
-         days = paste(days, '; reference:', reference)) %>%
+         days = paste(days, '\n reference:', reference)) %>%
 ggplot(aes(x = dv, y = retest_reliability, label=days))+
@@
   coord_flip()+
-  theme_bw()+
-  theme(legend.position="none"),
+  theme_bw(),
 tooltip = c('sample_size', 'type', 'dv', 'retest_reliability', 'days')) %>%
-  layout(showlegend=FALSE)
+  layout(showlegend=F)
 ```
 
-Static plot
-
-```{r warning= FALSE, message =FALSE, fig.height=36, echo=FALSE, eval=FALSE}
-fig_data %>%
+```{r warning=FALSE, message=FALSE, fig.height=72, echo=FALSE}
+ggplotly(fig_data %>%
            mutate(dv = factor(dv, levels = dv[order(task)]),
                   days_cutoff = ifelse(days < 60, days, 120),
-         days = paste(days, '; reference:', reference)) %>%
-ggplot(aes(x = dv, y = retest_reliability, label=days))+
-  geom_point(aes(color = task, size=sample_size, shape = type, alpha = days_cutoff))+
-  coord_flip()+
-  theme_bw()
+                  days = paste(days, '\n reference:', reference)) %>%
+           filter(task == 'task') %>%
+           ggplot(aes(y = var, x = retest_reliability, label=days))+
+           geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff), color = '#00BFC4')+
+           facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+           theme(panel.spacing = unit(0.1, "lines"), 
+                 strip.placement = "outside",
+                 strip.text.y = element_text(angle=180),
+                 panel.background = element_rect(fill = NA),
+                 panel.grid.major = element_line(colour = "grey80")),
+         tooltip = c('sample_size', 'type', 'dv', 'retest_reliability', 'days')) %>%
+  layout(showlegend=F)
+
+# if you figure out how to make the panels for tasks and surveys separately you can use subplot() - a ggplotly function to plot them side by side
 ```
 
-```{r warning=FALSE, message=FALSE}
-fig_data = fig_data %>%
-  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
-  mutate(task_group = factor(task_group, levels = task_group[order(task)]),
-         raw1_fit0 = grepl('raw', variable_type),
-         type = as.character(type)) %>%
-  arrange(task_group, -raw1_fit0)
+```{r message=FALSE, echo=FALSE}
+ggplotly(fig_data %>%
+  mutate(dv = factor(dv, levels = dv[order(task)]),
+         days_cutoff = ifelse(days < 60, days, 120),
+         days = paste(days, '\n reference:', reference)) %>%
+  filter(task_group == 'bis_bas_survey') %>%
+  ggplot(aes(y = var, x = retest_reliability, label=days))+
+  geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff), color = '#F8766D')+
+  # facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  # facet_grid(task_group~.) +
+  theme(panel.spacing = unit(0.5, "lines"), 
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'none')+
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 16, 17, 3)),
+  width=600)
+
 ```
+
+# Static plot
 

### 2018-07-23 code/SRO_Retest_Analyses.Rmd
updated loaded packages

@@
 ```{r}
-summary(lmerTest::lmer(abs(difference) ~ scale(days_btw)+(scale(days_btw) | dv), data=t1_2_difference)) 
+#summary(lmerTest::lmer(abs(difference) ~ scale(days_btw)+(scale(days_btw) | dv), data=t1_2_difference))
+
+summary(tmp <- MCMCglmm(abs(difference) ~ scale(days_btw), random = ~us(scale(days_btw)):dv, data=t1_2_difference)) 
 ```

### 2018-07-23 code/SRO_Retest_Analyses_Helper_Functions.R

@@ -13,6 +13,7 @@ library(plotly)
 library(DT)
 library(sjPlot)
 library(RecordLinkage)
+library(MCMCglmm)
 
 render_this <- function(){rmarkdown::render('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Analyses.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, toc_depth = 2, code_folding = 'hide'))}
 

### 2018-07-24 code/SRO_Retest_Analyses.Rmd
replacing stats

@@
   ggplot(aes(similarity, value, col=key))+
-  geom_smooth(method="lm", se=FALSE)
-
+  geom_smooth(method="lm", alpha = 0.15)+
+  ylab("Polychoric correlation")+
+  xlab("Levenshtein distance")+
+  scale_color_discrete(breaks = c("t1_t1_polycor", "t2_t2_polycor"),
+                       labels = c("T1 correlations", "T2 correlations"),
+                       name = element_blank())+
+  theme_bw()
+
+ggsave('OverlappingItemSimilarity.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
+```
+
+```{r}
 summary(lm(value~key*similarity,tmp))
+effect.size(lm(value~key*similarity,tmp))
+```
+
+```{r}
+summary(MCMCglmm(value ~ key*similarity, data=tmp, nitt = 50000)) 
 ```

### 2018-07-25 code/SRO_Retest_Analyses.Rmd
updating stats

@@
 summary(lm(value~key*similarity,tmp))
-effect.size(lm(value~key*similarity,tmp))
 ```
@@
 ```{r echo=FALSE}
-rm(tmp, comb, t1_2_difference, duplicate_items, duplicate_items_data_t1, duplicate_items_data_t2, extract_items, get_delay_effect)
+rm(tmp, comb, t1_2_difference, duplicate_items, duplicate_items_data_t1, duplicate_items_data_t2, extract_items)
 ```

### 2018-07-25 code/SRO_Retest_Analyses.Rmd
updating stats

@@
 ```{r}
-summary(lm(value~key*similarity,tmp))
-```
-
-```{r}
-summary(MCMCglmm(value ~ key*similarity, data=tmp, nitt = 50000)) 
+summary(lm(value~key*scale(similarity),tmp))
+```
+
+```{r}
+summary(MCMCglmm(value ~ key*scale(similarity), data=tmp, nitt = 50000)) 
 ```
@@
 ```{r}
-summary(lm(sample_size ~ task,rel_comp))
+# summary(lm(sample_size ~ task,rel_comp))
+summary(m1 <- MCMCglmm(sample_size ~ task, data=rel_comp))
 ```
@@
 ```{r}
-summary(mod2)
+#summary(mod2)
+summary(MCMCglmm(retest_reliability ~ task + sample_size, random = ~ dv, data = rel_comp))
 ```
@@
   geom_smooth(method = "lm")
-
+```
+
+```{r}
 summary(lm(resid ~ sample_size, tmp))

### 2018-07-25 code/SRO_Retest_Analyses.Rmd
updating stats

@@
 
-I used to compare effect sizes of effect of task on reliability estimates in literature vs our results (just looking at the variables you find in the literature) but removed this analysis because   
-1. the estimates in the literature are not all the same statistic
-2. from our data I was only using ICC's
-3.
-I was sampling from our bootstrapped results as many datapoints for each measure as there are in the literature but that didn't seem like the best way to make use of our data to make it comparable to the literature.
-
-Despite these problems the main result was that the effect size was much larger in our dataset compared to the literature but given the problems I think the sampling analyses below are more informative than this.
-
-We also checked whether our results diverge most from studies with smaller sample sizes.
+Note: We checked whether our results diverge most from studies with smaller sample sizes.
 Square difference between our mean estimate and the reliability from the literature decreases exponentially with sample size.
@@
     group_by(dv) %>%
-    do(sample_from_dv(.))
+    do(sample_from_dv(.)) %>%
+    na.omit()
 
@@
 
+```{r}
+tmp = comp_lit_pred_out %>%
+  select(r2_lit, r2_boot) %>%
+  gather(key, value)
+
+summary(MCMCglmm(value ~ key, data = tmp))
+```
+
 Are you at noise ceiling for suveys vs. tasks? Are you better in estimating the literature using our data for surveys vs tasks?
@@
 Are the differences in the distributions significant?
-There is a significant interaction, such that...
+There is a significant interaction, such that:
 
@@
 
-Our data is better in predicting the literature estimates for the surveys that it is in predicting tasks (comparing the difference between orange and purple for red and blue outlines).
+Our data is better in predicting the literature estimates for the surveys than it is in predicting tasks (comparing the difference between orange and purple for red and blue outlines).
 
@@
 Why are the reliability estimates from surveys worse compared to tasks in predicting the literature?
+Because they are less variable.
+In this procedure having high variance in what is being predicted (i.e.
+the literature reliability estimates) is better.
 
 Rank by variance: empirical estimates for surveys < literature estimates for surveys < empirical estimates for tasks < literature estimates for tasks
-
-In this procedure having high variance is better. When predicting the literature using an empirical estimate for a survey measure
 
@@
 
-```{r}
-summary(lmerTest::lmer(icc ~  task + (1|dv), boot_df))
+```{r eval=FALSE}
+#summary(lmerTest::lmer(icc ~  task + (1|dv), boot_df))
+summary(MCMCglmm(icc ~  task, random = ~dv, data=boot_df))
 ```

### 2018-07-25 code/SRO_Retest_Analyses.Rmd
updating stats

@@
 #summary(lmerTest::lmer(icc ~  task + (1|dv), boot_df))
-summary(MCMCglmm(icc ~  task, random = ~dv, data=boot_df))
+# m = MCMCglmm(icc ~  task, random = ~dv, data=boot_df, nitt = 1300, burnin = 300)
+m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_task_model.rds')
+summary(m)
 ```
@@
 
-summary(lmerTest::lmer(var_subs_pct~task+(1|dv),tmp%>%select(-var_ind_pct,-var_resid_pct)))
+# summary(lmerTest::lmer(var_subs_pct~task+(1|dv),tmp%>%select(-var_ind_pct,-var_resid_pct)))
+m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_subs_pct_by_task_model.rds')
+summary(m)
 ```
@@
 ```{r}
-summary(lmerTest::lmer(var_ind_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_resid_pct)))
-```
-
-```{r}
-summary(lmerTest::lmer(var_resid_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_ind_pct)))
+# summary(lmerTest::lmer(var_ind_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_resid_pct)))
+m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_ind_pct_by_task_model.rds')
+summary(m)
+```
+
+```{r}
+# summary(lmerTest::lmer(var_resid_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_ind_pct)))
+m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_resid_pct_by_task_model.rds')
+summary(m)
 ```
@@
   arrange(task,-pct_sig_time_effect) %>%
-  arrange(mean_pearson)
 
@@
 # summary(lm(icc ~ num_all_trials, data = tmp))
-summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
+# summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
+summary(MCMCglmm(icc ~ num_all_trials, random=~dv, data = tmp))
 ```

### 2018-07-26 code/SRO_Retest_Analyses.Rmd
updating stats

@@
 # summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
-summary(MCMCglmm(icc ~ num_all_trials, random=~dv, data = tmp))
+m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_num_trials_model.rds')
+summary(m)
 ```

### 2018-07-27 code/SRO_Retest_Analyses.Rmd
removed model files from git repo

--- 2018-07-25 code/SRO_Retest_Analyses.Rmd
@@
 # summary(lmerTest::lmer(var_subs_pct~task+(1|dv),tmp%>%select(-var_ind_pct,-var_resid_pct)))
-m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_subs_pct_by_task_model.rds')
+m = readRDS(gzfile('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_subs_pct_by_task_model.rds.gz'))
 summary(m)
@@
 # summary(lmerTest::lmer(var_ind_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_resid_pct)))
-m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_ind_pct_by_task_model.rds')
+m = readRDS(gzfile('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_ind_pct_by_task_model.rds.gz'))
 summary(m)
@@
 # summary(lmerTest::lmer(var_resid_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_ind_pct)))
-m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_resid_pct_by_task_model.rds')
+m = readRDS(gzfile('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_resid_pct_by_task_model.rds'))
 summary(m)
@@
 # summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
-summary(MCMCglmm(icc ~ num_all_trials, random=~dv, data = tmp))
+m = readRDS(gzfile('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_num_trials_model.rds'))
+summary(m)
 ```
@@
 ```{r}
-summary(lmerTest::lmer(icc ~ contrast + (1|dv) ,tmp))
+# summary(lmerTest::lmer(icc ~ contrast + (1|dv) ,tmp))
+summary(MCMCglmm(icc ~ contrast, random = ~ dv, data=tmp))
 ```
@@
 ```{r}
-summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "non-contrast")))
+# summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "non-contrast")))
+m = readRDS(gzfile('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_rawfit_noncon_model.rds.gz'))
+summary(m)
 ```
@@
 ```{r}
-summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "contrast")))
+# summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "contrast")))
+m = readRDS(gzfile('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_rawfit_con_model.rds.gz'))
+summary(m)
 ```

### 2018-07-27 code/SRO_Retest_Analyses.Rmd
updated model paths

--- 2018-07-26 code/SRO_Retest_Analyses.Rmd
@@
 ```{r}
-summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "non-contrast")))
+# summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "non-contrast")))
+m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_rawfit_noncon_model.rds')
+summary(m)
 ```
@@
 ```{r}
-summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "contrast")))
+# summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "contrast")))
+m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_rawfit_con_model.rds')
+summary(m)
 ```

### 2018-07-27 code/SRO_Retest_Analyses.Rmd
making print compatible figures

@@
             mean_emp = unique(mean_pearson)) %>%
-  ggplot(aes(mean_emp, mean_lit, col=task))+
+  ggplot(aes(mean_emp, mean_lit, col=task, shape=task))+
   geom_smooth(method="lm")+

### 2018-08-06 code/SRO_Retest_Analyses.Rmd
updates
fixing figures for paper

@@
 source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Analyses_Helper_Functions.R')
+
 theme_set(theme_bw())
@@
 summary(MCMCglmm(retest_reliability ~ task + sample_size, random = ~ dv, data = rel_comp))
+```
+
+```{r}
+rel_comp %>% 
+  group_by(task) %>%
+  summarise(mean_rr = mean(retest_reliability))
 ```

### 2018-08-06 code/SRO_Retest_Analyses.Rmd
changed noise ceilings plot to be print compatible

@@
                       name="Predictor",
-                      values = c("purple", "orange"))+
-  xlab('Variance Explained')+
+                      values = c("gray15", "gray75"))+
+  xlab('Proportion of Variance in Literature Explained')+
   ylab('Density')+
@@
   ylim(0,40)+
-  theme(axis.title.x  = element_text(size=16),
-        axis.text.x  = element_text(size=14),
-        axis.title.y  = element_text(size=16),
-        legend.title  = element_text(size=16),
-        legend.text  = element_text(size=16))
+  theme(axis.title.x  = element_text(size=12),
+        axis.text.x  = element_text(size=12),
+        axis.text.y  = element_text(size=12),
+        axis.title.y  = element_text(size=12),
+        legend.title  = element_text(size=12),
+        legend.text  = element_text(size=12))
 

### 2018-08-06 code/SRO_Retest_Analyses.Rmd
changed task group labels to title lettering

@@
   mutate(task = ifelse(task_group == 'holt laury survey', "task", as.character(task))) %>%
-  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
-  mutate(task_group = gsub("survey", "", task_group))
+  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk", ifelse(task_group == "two stage task", "two step", ifelse(task_group == "threebytwo", "task switching", ifelse(task_group == "adaptive n back", "adaptive n-back", ifelse(task_group == "go nogo", "go/no-go",  ifelse(task_group == "ravens", "raven's", task_group)))))))) %>%
+  mutate(task_group = gsub("survey", "", task_group),
+         task_group = gsub("task", "", task_group),
+         task_group = str_to_title(task_group))
+```
+
+```{r}
+trial_num_info = tmp %>%
+  group_by(task_group) %>%
+  summarise(mean_num_all_trials = round(mean(num_all_trials)),
+            num_measures = length(unique(dv)))
+
+tmp = tmp %>%
+  left_join(trial_num_info, by="task_group")
 ```
@@
 ```
+
+Task level summary of bootstrapped reliabilities.
 

### 2018-08-06 code/SRO_Retest_Analyses.Rmd
fixed survey names for boot task level plot

--- 2018-08-06 code/SRO_Retest_Analyses.Rmd
@@
   mutate(task = ifelse(task_group == 'holt laury survey', "task", as.character(task))) %>%
-  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
-  mutate(task_group = gsub("survey", "", task_group))
+  mutate(task_group = gsub("survey", "", task_group),
+         task_group = gsub("task", "", task_group),
+         task_group = str_to_title(task_group)) %>%
+  mutate(task_group = ifelse(task_group == "Psychological Refractory Period Two Choices", "Psychological Refractory Period", ifelse(task_group == "Angling Risk Always Sunny", "Angling Risk", ifelse(task_group == "Two Stage", "Two Step", ifelse(task_group == "Threebytwo", "Task Switching", ifelse(task_group == "Adaptive N Back", "Adaptive N-back", ifelse(task_group == "Go Nogo", "Go/No-go",  ifelse(task_group == "Ravens", "Raven's", task_group)))))))) %>%
+  mutate(task_group = ifelse(task_group == "Bis Bas ", "BIS-BAS", ifelse(task_group == "Bis11 ", "BIS-11", ifelse(task_group == "Dospert Eb ", "DOSPERT EB", ifelse(task_group == "Dospert Rp ", "DOSPOERT RP", ifelse(task_group == "Dospert Rt ", "DOSPERT RT", ifelse(task_group == "Erq ", "ERQ", ifelse(task_group == "Upps Impulsivity ", "UPPS-P", task_group))))))))
+```
+
+```{r}
+trial_num_info = tmp %>%
+  group_by(task_group) %>%
+  summarise(mean_num_all_trials = round(mean(num_all_trials)),
+            num_measures = length(unique(dv)))
+
+tmp = tmp %>%
+  left_join(trial_num_info, by="task_group")
 ```

### 2018-08-06 code/SRO_Retest_Analyses.Rmd
working on adding trial number info to figure

@@
 trial_num_info = tmp %>%
-  group_by(task_group) %>%
+  group_by(task_group, task) %>%
   summarise(mean_num_all_trials = round(mean(num_all_trials)),
@@
   left_join(trial_num_info, by="task_group")
+```
+
+Trying tableGrob
+
+```{r warning=FALSE, message=FALSE}
+mytheme <- gridExtra::ttheme_minimal(
+    core = list(fg_params=list(cex = 3.5)),
+    colhead = list(fg_params=list(cex = 3.0)),
+    rowhead = list(fg_params=list(cex = 3.0)))
+
+task_trial_num_table = tableGrob(trial_num_info %>% 
+                                   filter(task == "task") %>% 
+                                   ungroup() %>% 
+                                   select(-task_group, -task),
+                                 theme = mytheme, rows=NULL, cols = NULL,
+                                 heights = rep(unit(1.25, "in"), 37))
+
+test_plot = arrangeGrob(p4_t, task_trial_num_table, nrow=1)
+
+ggsave('Task_Boot_w_trialinfo.jpg', plot = test_plot, device = "jpeg", path = "../output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE, dpi = 100)
+```
+
+Trying geom_text
+
+```{r warning=FALSE, message=FALSE}
+task_trial_num = trial_num_info %>% 
+  filter(task == "task") %>% 
+  ungroup() %>% 
+  select(-task)
+
+task_trial_num_table = task_trial_num %>%
+  mutate(y_axis = rev(seq(from=1, to=37, by=1))) %>%
+  gather(key, value, -y_axis, -task_group) %>%
+  ggplot(aes(key, y_axis))+
+  geom_text(aes(label=value), size=14)+
+  xlab("")+
+  ylab("")+
+  theme(axis.ticks=element_blank(),
+        axis.text = element_blank(),
+        panel.grid = element_blank(),
+        panel.border = element_blank())
+  # scale_x_discrete(position = "top",
+  #                  breaks=c("mean_num_all_trials", "num_measures"),
+  #                  labels=c("Mean Num Trials", "Num Measures"))
+
+test_plot = arrangeGrob(p4_t, task_trial_num_table, nrow=1, widths = c(2,1))
+
+ggsave('Task_Boot_w_trialinfo.jpg', plot = test_plot, device = "jpeg", path = "../output/figures/", width = 20, height = 48, units = "in", limitsize = FALSE, dpi = 100)
+
 ```

### 2018-08-06 code/SRO_Retest_Analyses.Rmd
added first clean version of task boot w trial info

--- 2018-08-06 code/SRO_Retest_Analyses.Rmd
@@
   left_join(trial_num_info, by="task_group")
+```
+
+```{r warning=FALSE, message=FALSE}
+task_trial_num = trial_num_info %>% 
+  filter(task == "task") %>% 
+  ungroup() %>% 
+  select(-task)
+
+task_trial_num_table = task_trial_num %>%
+  mutate(y_axis = rev(ggplot_build(p4_t)$layout$panel_params[[1]]$y.major)) %>%
+  gather(key, value, -y_axis, -task_group) %>%
+  ggplot(aes(key, factor(y_axis)))+
+  geom_text(aes(label=value), size=14)+
+  xlab("")+
+  ylab("")+
+  theme(axis.ticks=element_blank(),
+        axis.text.y = element_blank(),
+        panel.grid = element_blank(),
+        panel.border = element_blank(),
+        axis.text.x = element_text(size=30))+
+  scale_x_discrete(position = "top",
+                   breaks=c("mean_num_all_trials", "num_measures"),
+                   labels=c("Mean Num Trials", "Num Measures"))
+
+boot_task_plot = arrangeGrob(p4_t, task_trial_num_table, nrow=1, widths = c(3,2))
+
+ggsave('Task_Boot_w_trialinfo.jpg', plot = boot_task_plot, device = "jpeg", path = "../output/figures/", width = 20, height = 48, units = "in", limitsize = FALSE, dpi = 100)
+
 ```
@@
   theme_bw() + 
-  theme(axis.text.y = element_text(size=30))+
+  theme(axis.text.y = element_text(size=30),
+        axis.text.x = element_text(size=30))+
   xlab("")+
   ylab("")+
-  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1), position = "right")+
   scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+

### 2018-08-06 code/SRO_Retest_Analyses.Rmd
added clean boot figures with trial info

@@
 
+Extract trial number info to add to boot plot instead of adding another table
+
 ```{r}
@@
 
+Boot plot for tasks with trial info
+
 ```{r warning=FALSE, message=FALSE}
+p4_t <- tmp %>%
+  filter(task == 'task') %>%
+ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
+  geom_violin(fill='#00BFC4')+
+  theme_bw() + 
+  theme(axis.text = element_text(size=30))+
+  xlab("")+
+  ylab("")+
+  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1), position = "right")+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
+  geom_hline(yintercept = 0, color = "red", size = 1)+
+  coord_flip()
+
 task_trial_num = trial_num_info %>% 
@@
 
+```
+
+Boot plot for surveys with trial info
+
+```{r}
+p5_t <- tmp %>%
+  filter(task == 'survey') %>%
+ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
+  geom_violin(fill='#F8766D')+
+  theme_bw() + 
+  theme(axis.text = element_text(size=30))+
+  xlab("")+
+  ylab("")+
+  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1), position = "right")+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
+  geom_hline(yintercept = 0, color = "red", size = 1)+
+  coord_flip()
+
+survey_trial_num = trial_num_info %>% 
+  filter(task == "survey") %>% 
+  ungroup() %>% 
+  select(-task)
+
+survey_trial_num_table = survey_trial_num %>%
+  mutate(y_axis = rev(ggplot_build(p5_t)$layout$panel_params[[1]]$y.major)) %>%
+  gather(key, value, -y_axis, -task_group) %>%
+  ggplot(aes(key, factor(y_axis)))+
+  geom_text(aes(label=value), size=14)+
+  xlab("")+
+  ylab("")+
+  theme(axis.ticks=element_blank(),
+        axis.text.y = element_blank(),
+        panel.grid = element_blank(),
+        panel.border = element_blank(),
+        axis.text.x = element_text(size=30))+
+  scale_x_discrete(position = "top",
+                   breaks=c("mean_num_all_trials", "num_measures"),
+                   labels=c("Mean Num Trials", "Num Measures"))
+
+boot_survey_plot = arrangeGrob(p5_t, survey_trial_num_table, nrow=1, widths = c(3,2))
+
+ggsave('Survey_Boot_w_trialinfo.jpg', plot = boot_survey_plot, device = "jpeg", path = "../output/figures/", width = 20, height = 48, units = "in", limitsize = FALSE, dpi = 100)
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-p4_t <- tmp %>%
-  filter(task == 'task') %>%
-ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
-  geom_violin(fill='#00BFC4')+
-  theme_bw() + 
-  theme(axis.text.y = element_text(size=30),
-        axis.text.x = element_text(size=30))+
-  xlab("")+
-  ylab("")+
-  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1), position = "right")+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
-  geom_hline(yintercept = 0, color = "red", size = 1)+
-  coord_flip()
-
-p5_t <- tmp %>%
-  filter(task == 'survey') %>%
-ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
-  geom_violin(fill='#F8766D')+
-  theme_bw() + 
-  theme(axis.text.y = element_text(size=43))+
-  xlab("")+
-  ylab("")+
-  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
-  geom_hline(yintercept = 0, color = "red", size = 1)+
-  coord_flip()
 

### 2018-08-08 code/SRO_Retest_Analyses.Rmd
added boot figure with task info for both

@@
 
+Both task level boot plots with trial info together
+
+```{r}
+boot_both_w_trial = arrangeGrob(boot_task_plot, boot_survey_plot, nrow=1)
+
+ggsave('Boot_Both_w_trialinfo.jpg', plot = boot_both_w_trial, device = "jpeg", path = "../output/figures/", width = 38, height = 48, units = "in", limitsize = FALSE, dpi = 100)
+```
+
 Variable level summary of bootstrapped reliabilities.
@@
 knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Bootstrap_Raw_Var_Plot.jpg')
-```
-
-Task level summary of bootstrapped reliabilities.
-
-```{r message=FALSE, warning=FALSE}
-
-p6_t <- arrangeGrob(p4_t, p5_t,nrow=1)
-
-ggsave('Bootstrap_Poster_Plot_t.jpg', plot = p6_t, device = "jpeg", path = "../output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE, dpi = 100)
-```
-
-```{r echo=FALSE, out.width='100%'}
-knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Bootstrap_Poster_Plot_t.jpg')
-```
-
-```{r echo=FALSE}
-rm(p4_t, p5_t, p6_t)
 ```

### 2018-08-08 code/SRO_Retest_Analyses.Rmd
fixed legends for ddm figures

@@
 ```{r}
+ddm_boot_plot = tmp %>%
+  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
+  geom_boxplot()+
+  facet_wrap(~factor(contrast, levels=c("non-contrast", "contrast"), labels=c("Non-contrast", "Contrast")))+
+  theme_bw()+
+  ylab("ICC")+
+  xlab("")+
+  theme(legend.title = element_blank(),
+        legend.position = 'bottom',
+        legend.text = element_text(size=12),
+        strip.text = element_text(size=12),
+        axis.text = element_text(size = 12),
+        text = element_text(size=12))+
+  guides(fill = guide_legend(ncol = 2, byrow=F))+
+  scale_fill_brewer(palette="Greys",
+                    breaks=c( "Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))
+
+mylegend<-g_legend(ddm_boot_plot)
+
+grob_name <- names(mylegend$grobs)[1]
+
+#manually fix the legend
+#move non-decision down
+#key
+mylegend$grobs[grob_name][[1]]$layout[11,c(1:4)] <- c(4,8,4,8)
+mylegend$grobs[grob_name][[1]]$layout[12,c(1:4)] <- c(4,8,4,8)
+#text
+mylegend$grobs[grob_name][[1]]$layout[17,c(1:4)] <- c(4,10,4,10)
+#move threshold down
+#key
+mylegend$grobs[grob_name][[1]]$layout[9,c(1:4)] <- c(3,8,3,8)
+mylegend$grobs[grob_name][[1]]$layout[10,c(1:4)] <- c(3,8,3,8)
+#text
+mylegend$grobs[grob_name][[1]]$layout[16,c(1:4)] <- c(3,10,3,10)
+#move drift rate right and up
+#key
+mylegend$grobs[grob_name][[1]]$layout[7,c(1:4)] <- c(2,8,2,8)
+mylegend$grobs[grob_name][[1]]$layout[8,c(1:4)] <- c(2,8,2,8)
+#text
+mylegend$grobs[grob_name][[1]]$layout[15,c(1:4)] <- c(2,10,2,10)
+
+ddm_boot_legend = arrangeGrob(ddm_boot_plot +theme(legend.position="none"),
+             mylegend, nrow=2, heights=c(10, 1))
+
+ggsave('Bootstrap_DDM_Comp_Legend.jpg', plot = ddm_boot_legend, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 14, height = 10, units = "in", limitsize = FALSE)
+```
+
+```{r}
 tmp %>%
+  group_by(contrast) %>%
+  summarise(mean_icc = mean(icc),
+            sd_icc = sd(icc))
+```
+
+```{r}
+tmp2 = measure_labels %>%
+  mutate(dv = as.character(dv),
+         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
+  filter(ddm_task == 1, 
+         rt_acc != 'other') %>%
+  drop_na() %>%
+  left_join(rel_df[,c("dv", "icc")], by = 'dv')
+
+ddm_point_plot = tmp2 %>%
   ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
@@
   guides(fill = guide_legend(ncol = 2))+
-  scale_fill_discrete(breaks=c("Drift Rate", "Threshold", "Non-decision", "Response Time", "Accuracy"))
-
-ggsave('Bootstrap_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 14, height = 10, units = "in", limitsize = FALSE)
-```
-
-```{r}
-tmp %>%
-  group_by(contrast) %>%
-  summarise(mean_icc = mean(icc),
-            sd_icc = sd(icc))
-```
-
-```{r}
-tmp2 = measure_labels %>%
-  mutate(dv = as.character(dv),
-         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
-  filter(ddm_task == 1, 
-         rt_acc != 'other') %>%
-  drop_na() %>%
-  left_join(rel_df[,c("dv", "icc")], by = 'dv')
-
-tmp2 %>%
-  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
-  geom_boxplot()+
-  facet_wrap(~factor(contrast, levels=c("non-contrast", "contrast"), labels=c("Non-contrast", "Contrast")))+
-  theme_bw()+
-  ylab("ICC")+
-  xlab("")+
-  theme(legend.title = element_blank(),
-        legend.position = 'bottom',
-        legend.text = element_text(size=16),
-        strip.text = element_text(size=16),
-        axis.text = element_text(size = 16),
-        text = element_text(size=16))+
-  guides(fill = guide_legend(ncol = 2))+
-  scale_fill_discrete(breaks=c("Drift Rate", "Threshold", "Non-decision", "Response Time", "Accuracy"))+
+  scale_fill_brewer(palette="Greys",
+                    breaks=c( "Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))+
   ylim(-0.4, 1)
 
-ggsave('PointEst_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 15, height = 7, units = "in", limitsize = FALSE)
+mylegend<-g_legend(ddm_point_plot)
+
+grob_name <- names(mylegend$grobs)[1]
+
+#manually fix the legend
+#move non-decision down
+#key
+mylegend$grobs[grob_name][[1]]$layout[11,c(1:4)] <- c(4,8,4,8)
+mylegend$grobs[grob_name][[1]]$layout[12,c(1:4)] <- c(4,8,4,8)
+#text
+mylegend$grobs[grob_name][[1]]$layout[17,c(1:4)] <- c(4,10,4,10)
+#move threshold down
+#key
+mylegend$grobs[grob_name][[1]]$layout[9,c(1:4)] <- c(3,8,3,8)
+mylegend$grobs[grob_name][[1]]$layout[10,c(1:4)] <- c(3,8,3,8)
+#text
+mylegend$grobs[grob_name][[1]]$layout[16,c(1:4)] <- c(3,10,3,10)
+#move drift rate right and up
+#key
+mylegend$grobs[grob_name][[1]]$layout[7,c(1:4)] <- c(2,8,2,8)
+mylegend$grobs[grob_name][[1]]$layout[8,c(1:4)] <- c(2,8,2,8)
+#text
+mylegend$grobs[grob_name][[1]]$layout[15,c(1:4)] <- c(2,10,2,10)
+
+ddm_point_legend = arrangeGrob(ddm_point_plot +theme(legend.position="none"),
+             mylegend, nrow=2, heights=c(10, 1))
+
+ggsave('PointEst_DDM_Comp.jpg', plot=ddm_point_legend, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 15, height = 7, units = "in", limitsize = FALSE)
 ```

### 2018-08-09 code/SRO_Retest_Analyses.Rmd
updating intrameasure trial num analyses

@@
 ```{r}
-t1_dvs = read.csv(paste0(retest_data_path, 't1_tbt_dvs.csv'))
-t2_dvs = read.csv(paste0(retest_data_path, 't2_tbt_dvs.csv'))
+t1_dvs = read.csv(paste0(retest_data_path, 't1_shift_dvs.csv'))
+t2_dvs = read.csv(paste0(retest_data_path, 't2_shift_dvs.csv'))
 
@@
 ```{r eval=FALSE}
-hr_merge = merge(t1_dvs, t2_dvs, by = c("sub_id", "breaks"))
+hr_merge = merge(t1_dvs, t2_dvs, by = c("worker_id", "level_1"))
 
 hr_merge = hr_merge %>%
-  gather(key, value, -sub_id, -breaks) %>%
+  gather(key, value, -worker_id, -level_1) %>%
   separate(key, c("dv", "time"), sep="\\.") %>%
-  mutate(time = ifelse(time == "x", 1, 2))
+  mutate(time = ifelse(time == "x", 1, 2))%>%
+  rename(sub_id = worker_id,
+         breaks = level_1)
 
@@
 
+'acc', 'avg_rt', 'conceptual_responses', 'fail_to_maintain_set',
+       'learning_rate', 'learning_to_learn', 'nonperseverative_errors',
+       'perseverative_errors', 'perseverative_responses', 'total_errors'
+
 trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))),
                               acc_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              avg_rt_error_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              std_rt_error_icc=rep(NA, length(unique(t1_dvs$breaks))),
                               avg_rt_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              std_rt_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              missed_percent_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              cue_switch_cost_rt_100_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              cue_switch_cost_rt_900_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              task_switch_cost_rt_100_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              task_switch_cost_rt_900_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              cue_switch_cost_acc_100_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              cue_switch_cost_acc_900_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              task_switch_cost_acc_100_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              task_switch_cost_acc_900_icc=rep(NA, length(unique(t1_dvs$breaks))))
+                              conceptual_responses_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              fail_to_maintain_set_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              learning_rate_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              learning_to_learn_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              nonperseverative_errors_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              perseverative_errors_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              perseverative_responses_icc=rep(NA, length(unique(t1_dvs$breaks))),
+                              total_errors_icc=rep(NA, length(unique(t1_dvs$breaks))))
 
@@
   trial_num_rel_df$acc_icc[i] = get_icc("acc", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$avg_rt_error_icc[i] = get_icc("avg_rt_error", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$std_rt_error_icc[i] = get_icc("std_rt_error", tmp_t1_dvs, tmp_t2_dvs)
   trial_num_rel_df$avg_rt_icc[i] = get_icc("avg_rt", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$std_rt_icc[i] = get_icc("std_rt", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$missed_percent_icc[i] = get_icc("missed_percent", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$cue_switch_cost_rt_100_icc[i] = get_icc("cue_switch_cost_rt_100", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$cue_switch_cost_rt_900_icc[i] = get_icc("cue_switch_cost_rt_900", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$trial_switch_cost_rt_100_icc[i] = get_icc("task_switch_cost_rt_100", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$trial_switch_cost_rt_900_icc[i] = get_icc("task_switch_cost_rt_900", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$cue_switch_cost_acc_100_icc[i] = get_icc("cue_switch_cost_acc_100", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$cue_switch_cost_acc_900_icc[i] = get_icc("cue_switch_cost_acc_900", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$trial_switch_cost_acc_100_icc[i] = get_icc("task_switch_cost_acc_100", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$trial_switch_cost_acc_900_icc[i] = get_icc("task_switch_cost_acc_900", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$conceptual_responses_icc[i] = get_icc("conceptual_responses", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$fail_to_maintain_set_icc[i] = get_icc("fail_to_maintain_set", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$learning_rate_icc[i] = get_icc("learning_rate", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$learning_to_learn_icc[i] = get_icc("learning_to_learn", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$nonperseverative_errors_icc[i] = get_icc("nonperseverative_errors", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$perseverative_errors_icc[i] = get_icc("perseverative_errors", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$perseverative_responses_icc[i] = get_icc("perseverative_responses", tmp_t1_dvs, tmp_t2_dvs)
+  trial_num_rel_df$total_errors_icc[i] = get_icc("total_errors", tmp_t1_dvs, tmp_t2_dvs)
 }
@@
 trial_num_rel_df %>%
-  select(-std_rt_icc, -std_rt_error_icc)%>%
   gather(key, value, -breaks) %>%
-  ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_error_icc", "avg_rt_icc", "missed_percent_icc", "cue_switch_cost_rt_100_icc", "cue_switch_cost_rt_900_icc", "task_switch_cost_rt_100_icc", "task_switch_cost_rt_900_icc", "cue_switch_cost_acc_100_icc", "cue_switch_cost_acc_900_icc", "task_switch_cost_acc_100_icc", "task_switch_cost_acc_900_icc"), labels = c("Accuracy", "Average RT error", "Average RT correct", "Missed percentage", "Cue switch cost RT (100)", "Cue switch cost RT (900)", "Task switch cost RT (100)", "Task switch cost RT (900)", "Cue switch cost Acc (100)", "Cue switch cost Acc (900)", "Task switch cost Acc (100)", "Task switch cost Acc (900)"))))+
+  ggplot(aes(breaks, value, color=key))+
   geom_point()+
@@
         legend.position = 'bottom')+
-  scale_color_manual(values = cols,
-                     breaks = c("Average RT correct", "Average RT error", "Cue switch cost RT (100)","Cue switch cost RT (900)", "Task switch cost RT (100)","Task switch cost RT (900)","Accuracy", "Missed percentage", "Cue switch cost Acc (100)", "Cue switch cost Acc (900)",  "Task switch cost Acc (100)",  "Task switch cost Acc (900)"))+
-  ylim(-1,1)+
-  guides(color = guide_legend(ncol=2, byrow=F))
-
-ggsave('Intrameasure_Trialnum_Dependendence.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in", dpi = 100)
+  ylim(-1,1)
+
+ggsave('Shift_Task_Intrameasure_Trialnum_Dependendence.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in", dpi = 100)
 ```

### 2018-08-09 code/SRO_Retest_Analyses.Rmd
added new intratrial analyses

@@
 
-'acc', 'avg_rt', 'conceptual_responses', 'fail_to_maintain_set',
-       'learning_rate', 'learning_to_learn', 'nonperseverative_errors',
-       'perseverative_errors', 'perseverative_responses', 'total_errors'
-
 trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))),
@@
 
-# write.csv(trial_num_rel_df, paste0(retest_data_path, 'trial_num_rel_df_tbt.csv'))
+# write.csv(trial_num_rel_df, paste0(retest_data_path, 'trial_num_rel_df_shift.csv'))
 ```
@@
 ```{r warning=FALSE, message=FALSE}
-trial_num_rel_df = read.csv(paste0(retest_data_path, 'trial_num_rel_df_tbt.csv'))
-
-cols <- c("Accuracy" = '#084594', "Average RT error" = '#99000d', "SD RT error" = '#cb181d', "Average RT correct" = '#ef3b2c', "SD RT correct" = '#fb6a4a', "Missed percentage" = '#2171b5', "Cue switch cost RT (100)" = '#fc9272', "Cue switch cost RT (900)" = '#fcbba1', "Task switch cost RT (100)" = '#fee0d2', "Task switch cost RT (900)" = '#fff5f0', "Cue switch cost Acc (100)" = '#4292c6', "Cue switch cost Acc (900)" = '#6baed6', "Task switch cost Acc (100)" = '#9ecae1', "Task switch cost Acc (900)" = '#c6dbef')
-
-cols <- c("Accuracy" = '#084594', "Average RT error" = '#99000d', "Average RT correct" = '#ef3b2c', "Missed percentage" = '#2171b5', "Cue switch cost RT (100)" = '#fc9272', "Cue switch cost RT (900)" = '#fcbba1', "Task switch cost RT (100)" = '#fee0d2', "Task switch cost RT (900)" = '#fff5f0', "Cue switch cost Acc (100)" = '#4292c6', "Cue switch cost Acc (900)" = '#6baed6', "Task switch cost Acc (100)" = '#9ecae1', "Task switch cost Acc (900)" = '#c6dbef')
+trial_num_rel_df = read.csv(paste0(retest_data_path, 'trial_num_rel_df_shift.csv'))
 
@@
   gather(key, value, -breaks) %>%
-  ggplot(aes(breaks, value, color=key))+
+  ggplot(aes((breaks+1)*10, value, shape=key))+
   geom_point()+
-  geom_line()+
+  geom_line(alpha = 0.5)+
+
   theme_bw()+
@@
         legend.position = 'bottom')+
-  ylim(-1,1)
+  scale_shape_manual(values = c(0:9),
+                     breaks = c("acc_icc", "avg_rt_icc", "conceptual_responses_icc", "fail_to_maintain_set_icc", "learning_rate_icc", "learning_to_learn_icc", "nonperseverative_errors_icc", "perseverative_errors_icc", "perseverative_responses_icc", "total_errors_icc"),
+                     labels = c("Accuracy", "Average Response Time", "Conceptual Responses", "Failure to Maintain Set", "Learning Rate", "Learning to Learn",  "Nonperseverative Errors", "Perseverative Errors", "Perseverative Responses", "Total Errors"))
 

### 2018-08-09 code/SRO_Retest_Analyses.Rmd
fixing lit review figure

@@
   arrange(task_group, raw_fit, var) %>%
-  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
-  mutate(task_group = gsub("survey", "", task_group)) %>%
+  mutate(task_group = gsub("survey", "", task_group),
+         task_group = gsub("task", "", task_group),
+         task_group = str_to_title(task_group)) %>%
+  mutate(task_group = ifelse(task_group == "Psychological Refractory Period Two Choices", "Psychological Refractory Period", ifelse(task_group == "Angling Risk Always Sunny", "Angling Risk", ifelse(task_group == "Two Stage", "Two Step", ifelse(task_group == "Threebytwo", "Task Switching", ifelse(task_group == "Adaptive N Back", "Adaptive N-back", ifelse(task_group == "Go Nogo", "Go/No-go",  ifelse(task_group == "Ravens", "Raven's", task_group)))))))) %>%
+  mutate(task_group = ifelse(task_group == "Bis Bas ", "BIS-BAS", ifelse(task_group == "Bis11 ", "BIS-11", ifelse(task_group == "Dospert Eb ", "DOSPERT EB", ifelse(task_group == "Dospert Rp ", "DOSPOERT RP", ifelse(task_group == "Dospert Rt ", "DOSPERT RT", ifelse(task_group == "Erq ", "ERQ", ifelse(task_group == "Upps Impulsivity ", "UPPS-P", task_group))))))))  %>%
   select(-measure_description)
@@
   geom_point(aes(size=sample_size, shape = type), color='black')+
-  theme(axis.text.y = element_text(size=43),
+  theme(axis.text.y = element_text(size=30),
         legend.position = 'bottom',
-        axis.text.x = element_text(size=23),
-        axis.title.x = element_text(size=30), 
-        legend.text = element_text(size=20), 
+        axis.text.x = element_text(size=20),
+        axis.title.x = element_text(size=20), 
+        legend.text = element_text(size=12), 
         legend.key.width = unit(0.75, "inches"), 
-        legend.title = element_text(size=28),
+        legend.title = element_text(size=20),
         legend.spacing.x = unit(0.5, "inches")) + 
@@
   geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
-  theme(axis.text.y = element_text(size=43),
+  theme(axis.text.y = element_text(size=30),
         legend.position = 'none',
@@
   scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
-  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
+  scale_y_discrete(labels = function(x) str_wrap(x, width = 15))+
   scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))+
@@
   geom_point(aes(size=sample_size, shape = type), color='#F8766D')+
-  theme(axis.text.y = element_text(size=43),
+  theme(axis.text.y = element_text(size=30),
         legend.position = 'none',

### 2018-08-10 code/SRO_Retest_Analyses.Rmd
cleaned up lit review figure

@@
         axis.title.x = element_text(size=20), 
-        legend.text = element_text(size=12), 
+        legend.text = element_text(size=16), 
         legend.key.width = unit(0.75, "inches"), 
         legend.title = element_text(size=20),
-        legend.spacing.x = unit(0.5, "inches")) + 
-  guides(size = guide_legend(override.aes = list(size=c(9,18,28))),
-         shape = guide_legend(override.aes = list(size=18)))+
+        legend.spacing.x = unit(0.5, "inches"),
+        legend.box = "vertical",
+        legend.direction = "horizontal") + 
   xlab("Retest Reliability")+
@@
   scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
-  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3), name="Type")+
-  scale_size_continuous(name = "Sample Size")+
+  scale_shape_manual(breaks = sort(unique(lit_review$type)), values = c(17, 3, 16, 15), name="Type")+
+  scale_size_continuous(name = "Sample Size", 
+                        limits = c(10, 1200),
+                        range = c(1, 40), 
+                        breaks = c(10, 100, 1000))+
+  guides(#size = guide_legend(override.aes = list(breaks = c(10, 100, 1000)), labels = c(10, 100, 1000)),
+         shape = guide_legend(override.aes = list(size = 16)))+
   geom_vline(xintercept = 0, color = "red", size = 1)
@@
   scale_y_discrete(labels = function(x) str_wrap(x, width = 15))+
-  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))+
-  scale_size_continuous(range = c(5, 35))+
+  scale_shape_manual(breaks = sort(unique(lit_review$type)), values = c(17, 3, 16, 15))+
+  scale_size_continuous(range = c(1, 40),
+                        limits = c(10,1200))+
   geom_vline(xintercept = 0, color = "red", size = 1)
@@
   scale_y_discrete(labels = function(x) str_wrap(x, width = 15))+
-  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))+
-  scale_size_continuous(range = c(5, 35))+
+  scale_shape_manual(breaks = c("ICC","Pearson","Spearman"), 
+                     values = c(17, 16, 15))+
+  scale_size_continuous(range = c(1, 40),
+                        limits = c(10,1200))+
   geom_vline(xintercept = 0, color = "red", size = 1)
@@
 ggsave('Lit_Review_Plot_t.jpg', plot = p3_t, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE, dpi = 72)
+```
+
+```{r}
+lit_review %>%
+  select(dv, sample_size, task) %>%
+  ggplot(aes(sample_size, fill=task))+
+  geom_histogram(position = "identity", alpha = 0.5)
+
 rm(p1_t, p2_t, p3_t, mylegend, p1_t_legend)

### 2018-08-10 code/SRO_Retest_Analyses.Rmd
updated boot task levels plots to only include meaningful vars

@@
 ```{r}
-lit_review %>%
-  select(dv, sample_size, task) %>%
-  ggplot(aes(sample_size, fill=task))+
-  geom_histogram(position = "identity", alpha = 0.5)
-
 rm(p1_t, p2_t, p3_t, mylegend, p1_t_legend)
@@
 
+```{r}
+meaningful_vars = read.table('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/meaningful_vars.txt')
+meaningful_vars = as.character(meaningful_vars$V1)
+
+tmp = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% meaningful_vars == FALSE)])
+tmp = tmp[-grep('survey', tmp)]
+
+meaningful_vars = c(meaningful_vars, tmp)
+meaningful_vars = sort(meaningful_vars)
+```
+
 ```{r warning=FALSE, message=FALSE}
@@
 ```{r}
-trial_num_info = tmp %>%
+tmp_mngfl = tmp %>%
+  filter(dv %in% meaningful_vars)
+
+trial_num_info = tmp_mngfl %>%
   group_by(task_group, task) %>%
@@
 
-Boot plot for tasks with trial info
+Boot plot for tasks with trial info (only using meaningful vars)
 
 ```{r warning=FALSE, message=FALSE}
-p4_t <- tmp %>%
+p4_t <- tmp_mngfl %>%
   filter(task == 'task') %>%
@@
 
-Boot plot for surveys with trial info
-
-```{r}
-p5_t <- tmp %>%
+Boot plot for surveys with trial info (only using meaningful vars)
+
+```{r}
+p5_t <- tmp_mngfl %>%
   filter(task == 'survey') %>%
@@
 
-```{r}
-meaningful_vars = read.table('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/meaningful_vars.txt')
-meaningful_vars = as.character(meaningful_vars$V1)
-
-tmp = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% meaningful_vars == FALSE)])
-tmp = tmp[-grep('survey', tmp)]
-
-meaningful_vars = c(meaningful_vars, tmp)
-meaningful_vars = sort(meaningful_vars)
-```
-
 ```{r warning=FALSE, message=FALSE}

### 2018-08-10 code/SRO_Retest_Analyses.Rmd
updated boot task level plots to only include meaningful vars

@@
 
-trial_num_info = tmp_mngfl %>%
+trial_num_info = tmp %>%
   group_by(task_group, task) %>%
@@
 
+trial_num_info_mngfl = tmp_mngfl %>%
+  group_by(task_group, task) %>%
+  summarise(mean_num_all_trials = round(mean(num_all_trials)),
+            num_measures = length(unique(dv)))
+
 tmp = tmp %>%
-  left_join(trial_num_info, by="task_group")
+  left_join(trial_num_info, by=c("task_group", "task"))
+
+tmp_mngfl = tmp_mngfl %>%
+  left_join(trial_num_info_mngfl, by=c("task_group", "task"))
 ```
@@
 
-task_trial_num = trial_num_info %>% 
+task_trial_num = trial_num_info_mngfl %>% 
   filter(task == "task") %>% 
@@
 ```{r}
-p5_t <- tmp_mngfl %>%
+p5_t <- tmp %>%
   filter(task == 'survey') %>%

### 2018-08-10 code/SRO_Retest_Analyses.Rmd
added clinical versus control sample analyses for the literature

@@
 - Survey measures have less variability in the reported reliabiltiy estimates compared to task measures
+
+Are there differences between clinical and non-clinical samples in the literature?
+
+```{r}
+tmp = lit_review %>%
+  mutate(clinical = as.character(clinical),
+         clinical = ifelse(clinical == "", "control", clinical),
+         clinical_1_0 = ifelse(clinical == "control", 0, 1))
+table(tmp$clinical)
+table(tmp$clinical_1_0)
+summary(lmer(retest_reliability ~ clinical_1_0+(1|dv),data=tmp))
+```
 

### 2018-08-13 code/SRO_Retest_Analyses_Helper_Functions.R
refactored the retest stats scripts for ddm analyses

@@ -13,6 +13,8 @@ library(sjPlot)
 library(RecordLinkage)
 library(MCMCglmm)
 
+theme_set(theme_bw())
+
 render_this <- function(){rmarkdown::render('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Analyses.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, toc_depth = 2, code_folding = 'hide'))}
 
 options(scipen = 1, digits = 4)
@@ -23,92 +25,4 @@ source(paste0(helper_func_path, 'g_legend.R'))
 source(paste0(helper_func_path, 'sem.R'))
 source(paste0(helper_func_path, 'trim.R'))
 source(paste0(helper_func_path, 'match_t1_t2.R'))
-
-
-
-
-get_spearman = function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-  
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
-  }
-  
-  rho = cor(df$`1`, df$`2`, method='spearman')
-  
-  return(rho)
-}
-
-get_icc <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
-  }
-  
-  df = df %>% select(-dv, -sub_id)
-  icc = ICC(df)
-  icc_3k = icc$results['Average_fixed_raters', 'ICC']
-  return(icc_3k)
-}
-
[…]

### 2018-08-13 code/SRO_Retest_Helper_Functions/get_retest_stats.R

@@ -1,0 +1,139 @@
+get_retest_stats = function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec, metric = c('spearman', 'icc', 'pearson', 'var_breakdown', 'partial_eta', 'sem')){
+  
+  if(sample=='full'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
+  }
+  else if(sample=='bootstrap'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
+  }
+  
+  out = data.frame()
+  
+  if('spearman' %in% metric){
+    out$rho = cor(df$`1`, df$`2`, method='spearman')
+  }
+  
+  if('pearson' %in% metric){
+    out$r = cor(df$`1`, df$`2`, method='pearson')
+  }
+  
+  if('icc' %in% metric | 'var_breakdown' %in% metric){
+    df = df %>% select(-dv, -sub_id)
+    icc = ICC(df)
+    
+    if('icc' %in% metric){
+      out$icc_3k = icc$results['Average_fixed_raters', 'ICC']
+    }
+    
+    if('var_breakdown' %in% metric){
+      out$subs = icc$summary[[1]][1,'Mean Sq']
+      out$ind = icc$summary[[1]][2,'Mean Sq']
+      out$resid = icc$summary[[1]][3,'Mean Sq']
+    }
+    
+  }
+  
+  if('partial_eta' %in% metric | 'sem' %in% metric){
+    mod = summary(aov(score~Error(sub_id)+time, df))
+    
+    if('partial_eta' %in% metric){
+      ss_time = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq1',]
+      ss_error = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq2',]
+      out$partial_eta = ss_time/(ss_time+ss_error)
+    }
+    
+    if('sem' %in% metric){
+      ms_error = as.data.frame(unlist(mod$`Error: Within`))['Mean Sq2',]
+      out$sem = sqrt(ms_error)
+    }
+    
+  }
+  return(out)
+  
+}
+
[…]

### 2018-08-15 code/SRO_Retest_Analyses.Rmd
refactored the retest stats scripts for ddm analyses
added updated graphs

@@
 source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Analyses_Helper_Functions.R')
-
-theme_set(theme_bw())
 
@@
 
-ggsave('LitAndEmpAveCor.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
+ggsave('LitAndEmpAveCor.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 4, height = 4, units = "in", limitsize = FALSE, dpi = 500)
 ```
@@
   gather(key, value, -breaks) %>%
+  filter(key %in% c("avg_rt_icc", "learning_to_learn_icc", "nonperseverative_errors_icc")) %>%
   ggplot(aes((breaks+1)*10, value, shape=key))+
@@
   geom_line(alpha = 0.5)+
-
   theme_bw()+
@@
   scale_shape_manual(values = c(0:9),
-                     breaks = c("acc_icc", "avg_rt_icc", "conceptual_responses_icc", "fail_to_maintain_set_icc", "learning_rate_icc", "learning_to_learn_icc", "nonperseverative_errors_icc", "perseverative_errors_icc", "perseverative_responses_icc", "total_errors_icc"),
-                     labels = c("Accuracy", "Average Response Time", "Conceptual Responses", "Failure to Maintain Set", "Learning Rate", "Learning to Learn",  "Nonperseverative Errors", "Perseverative Errors", "Perseverative Responses", "Total Errors"))
+                     breaks = c("avg_rt_icc","learning_to_learn_icc", "nonperseverative_errors_icc"),
+                     labels = c("Average Response Time", "Learning to Learn",  "Nonperseverative Errors"))
 
@@
 ddm_boot_plot = tmp %>%
-  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
+  group_by(dv) %>%
+  summarise(mean_icc = mean(icc),
+            raw_fit = unique(raw_fit),
+            contrast = unique(contrast),
+            rt_acc = unique(rt_acc)) %>%
+  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), mean_icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
   geom_boxplot()+
@@
         legend.position = 'bottom',
-        legend.text = element_text(size=12),
-        strip.text = element_text(size=12),
-        axis.text = element_text(size = 12),
-        text = element_text(size=12))+
+        legend.text = element_text(size=16),
+        strip.text = element_text(size=16),
+        axis.text = element_text(size = 16),
+        text = element_text(size=16))+
   guides(fill = guide_legend(ncol = 2, byrow=F))+

### 2018-08-20 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 ```{r}
-process_boot_df = function(df){
-  df = df %>%
-  drop_na() %>%
-  mutate(dv = as.character(dv),
-         icc = as.numeric(as.character(icc)),
-         spearman = as.numeric(as.character(spearman)),
-         pearson = as.numeric(as.character(pearson)),
-         eta_sq = as.numeric(as.character(eta_sq)),
-         sem = as.numeric(as.character(sem)),
-         partial_eta_sq = as.numeric(as.character(partial_eta_sq)),
-         omega_sq = as.numeric(as.character(omega_sq)),
-         var_subs = as.numeric(as.character(var_subs)),
-         var_ind = as.numeric(as.character(var_ind)),
-         var_resid = as.numeric(as.character(var_resid)),
-         F_time = as.numeric(as.character(F_time)),
-         p_time = as.numeric(as.character(p_time)),
-         df_time = as.numeric(as.character(df_time)),
-         df_resid = as.numeric(as.character(df_resid)))
-  return(df)}
-
 demog_boot_df <- read.csv(gzfile(paste0(retest_data_path,'demog_boot_merged.csv.gz')))

### 2018-08-20 code/SRO_Retest_Analyses_Helper_Functions.R

@@ -26,3 +26,4 @@ source(paste0(helper_func_path, 'sem.R'))
 source(paste0(helper_func_path, 'trim.R'))
 source(paste0(helper_func_path, 'match_t1_t2.R'))
 source(paste0(helper_func_path, 'get_retest_stats.R'))
+source(paste0(helper_func_path, 'process_boot_df.R'))

### 2018-09-13 code/Lit_Review_Figure.Rmd
reset repo

@@
   # facet_grid(task_group~.) +
-  theme(panel.spacing = unit(0.5, "lines"), 
-        strip.placement = "outside",
-        strip.text.y = element_text(angle=180),
+  theme(#panel.spacing = unit(0.5, "lines"),
+        #strip.placement = "outside",
+        #strip.text.y = element_text(angle=180),
         panel.background = element_rect(fill = NA),
         panel.grid.major = element_line(colour = "grey80"),
-        legend.position = 'none')+
+        legend.position = 'none'
+        )+
   xlab("")+

### 2018-09-13 code/SRO_Retest_Analyses.Rmd
reset repo

@@
         legend.box = "vertical",
-        legend.direction = "horizontal") + 
+        legend.direction = "horizontal",
+        plot.caption = element_text(family = "Times", size = 40, lineheight = 2, hjust = 0)) + 
   xlab("Retest Reliability")+
@@
          shape = guide_legend(override.aes = list(size = 16)))+
-  geom_vline(xintercept = 0, color = "red", size = 1)
+  geom_vline(xintercept = 0, color = "red", size = 1)+
+  labs(caption = str_wrap("FIGURE 1: Summary of the literature review for tasks (left) and surveys (right).
+Each point represents a study containing test-retest reliability data on an unspecified dependent measure for a given task.
+The size of the point depends on the sample size of the study and the shape depends on the metric that was used to estimate reliability.
+Each vertical red line indicates 0 reliability.", width = 120))
 
@@
 mylegend<-g_legend(p1_t_legend)
-
-p3_t <- arrangeGrob(arrangeGrob(p1_t, p2_t, nrow=1), mylegend, nrow=2,heights=c(10, 1))
-
-ggsave('Lit_Review_Plot_t.jpg', plot = p3_t, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE, dpi = 72)
+mycaption<-g_caption(p1_t_legend)
+
+p3_t <- arrangeGrob(arrangeGrob(p1_t, p2_t, nrow=1), mylegend, mycaption, nrow=3, heights=c(10, 1, 1.5))
+
+ggsave('Lit_Review_Plot_t.tiff', plot = p3_t, device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 27, height = 52, units = "in", limitsize = FALSE, dpi = 250)
 ```
@@
   ylim(0,40)+
-  theme(axis.title.x  = element_text(size=12),
-        axis.text.x  = element_text(size=12),
-        axis.text.y  = element_text(size=12),
-        axis.title.y  = element_text(size=12),
-        legend.title  = element_text(size=12),
-        legend.text  = element_text(size=12))
-
-ggsave('LitAndBoot_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
+  theme(#axis.title.x  = element_text(size=12),
+        #axis.text.x  = element_text(size=12),
+        #axis.text.y  = element_text(size=12),
+        #axis.title.y  = element_text(size=12),
+        #legend.title  = element_text(size=12),
+        #legend.text  = element_text(size=12),
+        legend.position = "bottom",
+        plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0))+
+  labs(caption = str_wrap("FIGURE 3: Noise ceiling for comparing empirical retest reliability estimates to reliability estimates from the literature.
+Data come from sampling a single reliability estimate from the literature and using that as a predictor of the remaining retest reliability estimates from the literature versus using the mean estimate from our empirical results as a predictor.
+Models account for the effect of sample size in the literature and whether the measure is a task or survey variables.
+The literature samples are significantly better at predicting the rest of the literature than our empirical averages, but the distributions of variance explained across samples are highly overlapping.
+", width = 120))
+
+ggsave('LitAndBoot_Noise_Ceiling.tiff', device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 7, height = 5, units = "in", limitsize = FALSE, dpi = 300)
 ```
@@
   theme(legend.title = element_blank(),
-        legend.position = 'bottom')
-
-ggsave('LitAndEmpAveCor.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 4, height = 4, units = "in", limitsize = FALSE, dpi = 500)
+        legend.position = 'bottom',
+        plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0))+
+  labs(caption = str_wrap("FIGURE 2: Correlation between mean reliability estimates for each measure found in the literature with the mean reliability from our data.", width = 120))
+
+ggsave('LitAndEmpAveCor.tiff', device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 7, height = 5, units = "in", limitsize = FALSE, dpi = 300)
 ```
@@
 
-ggsave('Metric_Scatterplots.jpg', plot = grid.arrange(p1, p2, p3, nrow=1), device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE, dpi = 100)
+ggsave('Metric_Scatterplots.jpg', plot = grid.arrange(p1, p2, p3, nrow=1), device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE, dpi = 300)
 ```
@@
 ```{r}
-boot_both_w_trial = arrangeGrob(boot_task_plot, boot_survey_plot, nrow=1)
-
-ggsave('Boot_Both_w_trialinfo.jpg', plot = boot_both_w_trial, device = "jpeg", path = "../output/figures/", width = 38, height = 48, units = "in", limitsize = FALSE, dpi = 100)
+mycaption = textGrob(label = str_wrap("FIGURE 4: Summary of bootstrapped reliability estimates for tasks (left) and surveys (right).
+We sampled 150 subjects with replacement 1000 times to create a distribution of bootstrapped reliability estimate for each measure.
+Reliability measure depicted is ICC.
+Red lines indicate 0 reliability.
+Columns following each graph present the mean number of trials used for dependent measures in that task and the number of ‘meaningful measures,’ dependent measures used in the literature from each task.", width = 165), gp = gpar(fontfamily="Times", lineheight = 2, fontsize = 40), hjust = 0, vjust = 0.5, x = unit(0, "npc"))
+
+boot_both_w_trial = arrangeGrob(arrangeGrob(boot_task_plot, boot_survey_plot, nrow=1), mycaption, nrow=2, heights = c(10,1))
+
+ggsave('Boot_Both_w_trialinfo.tiff', plot = boot_both_w_trial, device = "tiff", path = "../output/figures/", width = 38, height = 55, units = "in", limitsize = FALSE, dpi = 200)
 ```
@@
 
-ggsave('Bootstrap_Example_Plot_t.jpg', plot = p4, device = "jpeg", path = "../output/figures/", width = 41, height = 5, units = "in", limitsize = FALSE, dpi = 100)
+ggsave('Bootstrap_Example_Plot_t.jpg', plot = p4, device = "jpeg", path = "../output/figures/", width = 41, height = 5, units = "in", limitsize = FALSE, dpi = 300)
 ```
@@
                                "Error variance")), mean_pct))+
-  # geom_point(position=position_dodge(width = 0.25), size = 3, aes(color=task))+
-  geom_bar(position=position_dodge(width = 0.5), width=0.5, aes(fill=task), stat='identity', alpha=0.5)+
-  # geom_errorbar(aes(ymin=mean_pct-sd_pct, ymax=mean_pct+sd_pct), position=position_dodge(width = 0.25), width=0, size=2)+
-  geom_errorbar(aes(ymin=cil, ymax=ciu, color=task), position=position_dodge(width = 0.5), width=0.1)+
+  geom_errorbar(aes(ymin=cil, ymax=ciu, group=task), position=position_dodge(width = 0.25), width=0.25, size=2, alpha = 0.85, color="gray")+
+  geom_point(position=position_dodge(width = 0.25), size=3, aes(color=task, shape=task))+
+  #geom_bar(position=position_dodge(width = 0.5), width=0.5, aes(fill=task), stat='identity', alpha=0.5)+
+  #geom_errorbar(aes(ymin=mean_pct-sd_pct, ymax=mean_pct+sd_pct), position=position_dodge(width = 0.25), width=0, size=2)+
   theme_bw()+
@@
         legend.text = element_text(size=14),
-        # legend.position = 'bottom',
+        legend.position = 'bottom',
         axis.text = element_text(size=12),
-        axis.title.y = element_text(size=12))+
+        axis.title.y = element_text(size=12),
+        plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0)) +
   scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
-  ylim(0,100)
-
-ggsave('Variance_Breakdown_BarPlot.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 6, height = 5, units = "in", dpi = 300)
+  ylim(0,100)+
+  labs(caption = str_wrap("FIGURE 5:  Percentage of variance explained by each of the three sources of variance: between subjects, within subjects (between sessions) and error variance for 1000 bootstrapped samples.
+Error bars are 95% confidence intervals.", width = 120))
+
+ggsave('Variance_Breakdown_DotPlot.tiff', device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 7, height = 4, units = "in", dpi = 300)
 ```
@@
   theme(legend.title = element_blank(),
-        legend.position = 'bottom')+
+        legend.position = 'bottom',
+                             plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0)) +
   scale_shape_manual(values = c(0:9),
                      breaks = c("avg_rt_icc","learning_to_learn_icc", "nonperseverative_errors_icc"),
-                     labels = c("Average Response Time", "Learning to Learn",  "Nonperseverative Errors"))
-
-ggsave('Shift_Task_Intrameasure_Trialnum_Dependendence.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in", dpi = 100)
+                     labels = c("Average Response Time", "Learning to Learn",  "Nonperseverative Errors")) +
+  labs(caption = str_wrap("FIGURE 6: Change in point estimates of ICC for three dependent measures selected from the Shift task using increasing numbers of trials to estimate them.
+These measures show the different types of relationships reliability estimates have based on the trial numbers used to estimate them.", width = 180))
+
+ggsave('Shift_Task_Intrameasure_Trialnum_Dependendence.tiff', device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in", dpi = 300)
 ```
@@
 
+mycaption = textGrob(label = str_wrap("FIGURE 7: Average bootstrapped reliability estimates per measure comparing raw measures and model parameters as well as contrast and non-contrast measures for task measures.", width = 130), gp = gpar(fontfamily="Times", lineheight = 2, fontsize = 18), hjust = 0, vjust = 0.5, x = unit(0, "npc"))
+
 ddm_boot_legend = arrangeGrob(ddm_boot_plot +theme(legend.position="none"),
-             mylegend, nrow=2, heights=c(10, 1))
-
-ggsave('Bootstrap_DDM_Comp_Legend.jpg', plot = ddm_boot_legend, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 14, height = 10, units = "in", limitsize = FALSE)
+             mylegend, mycaption, nrow=3, heights=c(10, 1, 1))
+
+ggsave('Bootstrap_DDM_Comp_Legend.tiff', plot = ddm_boot_legend, device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 14, height = 10, units = "in", limitsize = FALSE, dpi=300)
 ```

### 2018-09-13 code/SRO_Retest_Cleaning.Rmd
reset repo

--- 2017-05-02 SRO_Report.Rmd
@@
 ---
-title: 'Self Regulation Ontology Retest Data Report'
+title: 'SRO Retest Data Cleaning'
 output:
@@
 library(plotly)
-library(jsonlite)
 library(DT)
 sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
-render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Report', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)}
+render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
 options(scipen = 1, digits = 4)
-```
-
-# Introduction
-
-# Methods
-
-## Data collection
-
-This sample consists of data for 150 subjects of the original sample of 522 that has completed the initial battery of 37 cognitive tasks, 23 surveys and 3 surveys on demographics.
-Details of the original sample as well as quality control (qc) procedures are described elsewhere.
-Invited participants were chosen randomly and only subsets of them were invited for a given batch (instead of opening the battery to all qualified subjects) with the intention to avoid a potential oversampling and bias towards "high self regulators".
-
-```{r warning=FALSE, message=FALSE}
-workers = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/User_717570_workers.csv')
-workers = workers %>% 
-  group_by(Worker.ID) %>%
-  mutate(Retest_worker=ifelse(sum(CURRENT.RetestWorker,CURRENT.RetestWorkerB2,CURRENT.RetestWorkerB3,CURRENT.RetestWorkerB4,CURRENT.RetestWorkerB5,na.rm=T)>0,1,0)) %>%
-  ungroup()
-
-worker_counts <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/retest_worker_counts.json')
-
-worker_counts = as.data.frame(unlist(worker_counts))
-names(worker_counts) = "task_count"
-```
-
-In total `r sum(workers$Retest_worker)` participants were invited, `r nrow(worker_counts)` began the battery, `r sum(worker_counts$task_count >= 62)` completed the battery and 150 provided data that passed qc for both time points.
-Our target sample size was determined in advance of data collection and data collection continued until this number of participants with data that survived qc was reached.
-
-```{r warning=FALSE, message=FALSE}
-disc_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/discovery_completion_dates.csv', header=FALSE)
-val_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/validation_completion_dates.csv', header=FALSE)
-test_comp_date = rbind(disc_comp_date, val_comp_date)
-rm(disc_comp_date, val_comp_date)
-retest_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/retest_completion_dates.csv', header=FALSE)
-comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
-names(comp_dates) <- c("sub_id", "retest_comp", "test_comp")
-comp_dates$retest_comp = as.Date(comp_dates$retest_comp)
-comp_dates$test_comp = as.Date(comp_dates$test_comp)
-comp_dates$days_btw = with(comp_dates, retest_comp-test_comp)
-```
-
-Data collection took place on average `r round(mean(as.numeric(comp_dates$days_btw)))` number of days after the completion of the initial battery with a range of `r round(range(as.numeric(comp_dates$days_btw)))[1]` to `r round(range(as.numeric(comp_dates$days_btw)))[2]` days.
-
-## Literature
-
-### Tasks
-
-### Surveys
-
-## Loading and matching datasets
-
-This report uses the variables that were designated as "meaningful" before.
-This is not the smallest subset where certain variables are dropped because they are correlated with other variables (within a task) and includes both accuracies as well as both kinds of DDM variables (EZ and HDDM).
-It will not include variables that were considered not of theoretical interest in the analyses of time 1 data.
-The variables that are not included will be listed for reference as well.
-
-### Load time 1 data
-```{r}
-test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables.csv')
-
-test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_noDDM.csv')
-
-test_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_EZ.csv')
-
-test_data <- merge(test_data, test_data2)
-test_data <- merge(test_data, test_data3)
-rm(test_data2, test_data3)
-```
-
-For reference here are the variables that are **not** included in the analyses of the remainder of this report because they were not of theoretical interest in factor structure analyses of this data so far.
-These include drift diffusion and other model parameters for specific conditions within a task; survey variables that are not part of the dependant variables for that survey in the literature and demographics (these are saved for prediction analyses).
-
-```{r}
-test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/variables_exhaustive.csv')
-
-test_data2$X <- as.character(test_data2$X)
-
-names(test_data2)[1] <- 'sub_id'
-
-df <- data.frame(names(test_data2)[which(names(test_data2) %in% names(test_data) == FALSE)])
-names(df) = c('vars')
-
-datatable(df)
-```
-
-```{r echo=FALSE}
-rm(test_data2, df)
-```
-
-### Load time 2 data 
-```{r}
-retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/meaningful_variables.csv')
-
-retest_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/meaningful_variables_noDDM.csv')
-
-retest_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/meaningful_variables_EZ.csv')
-
-retest_data <- merge(retest_data, retest_data2)
-retest_data <- merge(retest_data, retest_data3)
-rm(retest_data2, retest_data3)
-```
-
-Extract t2 participants with good t1 data: We only invited those with good data but due to a technical error a handful of subjects who weren't checked for data quality completed the retest battery as well.
-One of those subjects gave good t2 data but didn't have good t1 data and therefore is removed from further analyses.
-
-```{r}
-#Process sub_id columns in the data dataframes
-retest_data$X <- as.character(retest_data$X)
-test_data$X <- as.character(test_data$X)
-
-names(retest_data)[1] <- 'sub_id'
-names(test_data)[1] <- 'sub_id'
-
-retest_data <- retest_data[retest_data$sub_id %in% test_data$sub_id,]
 ```
@@
 ```
-
-### Extract t-1 data for t-2 subjects
-```{r}
-retest_subs_test_data <- test_data[test_data$sub_id %in% retest_data$sub_id,]
-
-rest_subs_test_data <- test_data[test_data$sub_id %in% retest_data$sub_id == FALSE,]
-
-#Arrange datasets of same size by sub_id
-retest_data = retest_data %>% arrange(sub_id)
-retest_subs_test_data = retest_subs_test_data %>% arrange(sub_id)
-
-#CHECK IF EVERYTHING IS ORDERED RIGHT
-as.character(retest_subs_test_data$sub_id) == as.character(retest_data$sub_id)
-```
-
-### Replace HDDM parameters in t1 data
-
-Since HDDM parameters depend on the sample on which they are fit we refit the model on t1 data for the subjects that have t2 data.
-Here we replace the HDDM parameters in the current t1 dataset with these refitted values and transform them as they would have been transformed for the full sample to mimick the procedure we applied to rest of the t2 data.
-
-Transform hddm refits as they had been transformed for the full sample t1 data.
-```{r}
-hddm_refits <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/hddm_refits_exhaustive.csv')
-
-hddm_refits$X <- as.character(hddm_refits$X)
-
-names(hddm_refits)[1] <- 'sub_id'
-
-hddm_logTr_vars = data.frame(grep('(?=.*hddm)(?=.*logTr)', names(retest_subs_test_data), value=T, perl=T))
-names(hddm_logTr_vars) = c('var')
-hddm_logTr_vars$sign = ifelse(grepl(".ReflogTr",hddm_logTr_vars$var), 'negative', 'positive')
-hddm_logTr_vars$var = gsub(".logTr|.ReflogTr", "", hddm_logTr_vars$var)
-
-transformed_hddm_refits = hddm_refits
-
-for(i in 1:length(names(transformed_hddm_refits))){
-  tmp_col = names(transformed_hddm_refits)[i]
-  if(tmp_col %in% hddm_logTr_vars$var){
-    sign = hddm_logTr_vars$sign[which(tmp_col == hddm_logTr_vars$var)]
-      if(sign == 'positive'){
-        # clean_retest_data[,tmp_col] = log(clean_retest_data[,tmp_col])
-        transformed_hddm_refits[,tmp_col] = pos_log(transformed_hddm_refits[,tmp_col])
-        names(transformed_hddm_refits)[which(names(transformed_hddm_refits) == tmp_col)] = paste0(tmp_col, '.logTr')
-        cat(paste0(tmp_col ,' was positively skewed and transformed.'))
-        cat('\n')
-      }
-      else if(sign == 'negative'){
-        transformed_hddm_refits[,tmp_col] = neg_log(transformed_hddm_refits[,tmp_col])
-        names(transformed_hddm_refits)[which(names(transformed_hddm_refits) == tmp_col)] = paste0(tmp_col, '.ReflogTr')
-        cat(paste0(tmp_col ,' was negatively skewed and transformed.'))
-        cat('\n')
-      }
-    }
-}
-```
-
-Check if transformation of hddm refits worked
-```{r}
-transform_hddm_logTr_vars = data.frame(grep('logTr', names(transformed_hddm_refits), value=T))
-names(transform_hddm_logTr_vars) = c('var')
-transform_hddm_logTr_vars$sign = ifelse(grepl(".ReflogTr",transform_hddm_logTr_vars$var), 'negative', 'positive')
-transform_hddm_logTr_vars$var = gsub(".logTr|.ReflogTr", "", transform_hddm_logTr_vars$var)
-transform_hddm_logTr_vars = transform_hddm_logTr_vars %>% arrange(var)
-hddm_logTr_vars = hddm_logTr_vars %>% arrange(var)
-transform_hddm_logTr_vars == hddm_logTr_vars
-```
-
-Replace t1 hddm parameters for retest subjects
-
-```{r}
-replace_hddm_vars = data.frame(grep('(?=.*hddm)(?=.*logTr)', names(retest_subs_test_data), value=T, perl=T))
-names(replace_hddm_vars) = c('var')
-
-hddm_fix_retest_subs_test_data = retest_subs_test_data
-
-for(i in 1:length(names(hddm_fix_retest_subs_test_data))){
-  if(names(hddm_fix_retest_subs_test_data)[i] %in% replace_hddm_vars$var){
-    hddm_fix_retest_subs_test_data[,names(hddm_fix_retest_subs_test_data)[i]] <- transformed_hddm_refits[,names(hddm_fix_retest_subs_test_data)[i]]
-  }
-}
-
-retest_subs_test_data <- hddm_fix_retest_subs_test_data
-```
-
-```{r}
-rm(hddm_refits, transformed_hddm_refits, hddm_logTr_vars, transform_hddm_logTr_vars, replace_hddm_vars, hddm_fix_retest_subs_test_data, sign, i)
-```
-
-# Results
-
-## Reliability metrics 
-For correlations we report Spearman's $\rho$'s only.  
-Based on [Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) ICC(3,k) does not take in to account within subject differences between two time points (i.e.
-the fixed effect of time/systematic error).
-Thus, it is well approximated by Pearson's r and subject to similar criticisms.
-[Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) suggests reporting at least this systematic error effect size if one chooses to report with ICC(3,k).
-Based on his conclusions here I report:
-- ICC(3,k): As Dave clarified this ranges from 1 to -1/(number of repeated measures -1) so in our case this range would be [-1, 1]; larger values would mean that the two scores of a subject for a given measure are more similar to each other than they are to scores of other people
-- partial $\eta^2$ for time ($SS_{time}/SS_{within}$): effect size of time   
-- SEM ($\sqrt(MS_{error})$): standard error of measurement; the smaller the better
-
-```{r}
-numeric_cols = c()
-
-for(i in 1:length(names(test_data))){
-  if(is.numeric(test_data[,i])){
-    numeric_cols <- c(numeric_cols, names(test_data)[i])
-  }
-}
-
-match_t1_t2 <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', format = "long", sample = 'full', sample_vec){
-
-  if(sample == 'full'){
-   df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var) 
-  }
-  else{
-    df = merge(t1_df[t1_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)], t2_df[t2_df[,merge_var] %in% sample_vec, c(merge_var, dv_var)],
-    by=merge_var)
-  }
-
-  df = df %>% 
-    na.omit()%>%
-    gather(dv, score, -sub_id) %>%
-    mutate(time = ifelse(grepl('\\.x', dv), 1, ifelse(grepl('\\.y', dv), 2, NA))) %>%
-    separate(dv, c("dv", "drop"), sep='\\.([^.]*)$') %>%
-    select(-drop)
-
-  if(format == 'wide'){
-    df = df%>% spread(time, score) 
-  }
-
-  return(df)
-}
-
-get_spearman = function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
-  }
-
-  rho = cor(df$`1`, df$`2`, method='spearman')
-
-  return(rho)
-}
-
-get_icc <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
-  }
-
-  df = df %>% select(-dv, -sub_id)
-  icc = ICC(df)
-  icc_3k = icc$results['Average_fixed_raters', 'ICC']
-  return(icc_3k)
-  }
-
-get_eta <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, sample='bootstrap', sample_vec = sample_vec)
-  }
-
-  mod = summary(aov(score~Error(sub_id)+time, df))
-  ss_time = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq1',]
-  ss_error = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq2',]
-  eta = ss_time/(ss_time+ss_error)
-  return(eta)
-  }
-
-get_sem <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
-  if(sample=='full'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
-  }
-  else if(sample=='bootstrap'){
-    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, sample='bootstrap', sample_vec = sample_vec)
-  }
-  mod = summary(aov(score~Error(sub_id)+time, df))
-  ms_error = as.data.frame(unlist(mod$`Error: Within`))['Mean Sq2',]
-  sem = sqrt(ms_error)
-  return(sem)
-}
-```
-
-```{r}
-rel_df <- data.frame(spearman = rep(NA, length(numeric_cols)),
-                     icc = rep(NA, length(numeric_cols)), 
-                     eta_sq = rep(NA, length(numeric_cols)),
-                     sem = rep(NA, length(numeric_cols)))
-
-row.names(rel_df) <- numeric_cols
-
-for(i in 1:length(numeric_cols)){
-  rel_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i]) 
-  rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
-  rel_df[numeric_cols[i], 'eta_sq'] <- get_eta(numeric_cols[i])
-  rel_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
-}
-
-rel_df$dv = row.names(rel_df)
-row.names(rel_df) = seq(1:nrow(rel_df))
-rel_df$task = 'task'
-rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
-rel_df = rel_df %>%
-  select(dv, task, spearman, icc, eta_sq, sem)
-# row.names(rel_df) = NULL
-
-```
-
-Average reliability metrics and the number of variables for both the surveys and the tasks
-Both Spearman $\rho$'s as well the ICC's are higher for surveys.  
-Systematic differences between the two measurements ($\eta^2$) are higher for tasks than surveys (potentially indicating learning effects?).  
-Unexpectedly, median standard error of measurement is higher for surveys but the distribution below suggests that this is a side effect of having too many task measures with very low SEMs.
-```{r warning=FALSE, message=FALSE}
-rel_df %>%
-  group_by(task) %>%
-  summarise(median_spearman = median(spearman),
-            median_icc = median(icc),
-            median_eta_sq = median(eta_sq),
-            median_sem = median(sem),
-            num_vars = n()) %>%
-  datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc', 'median_eta_sq', 'median_sem'), digits=3)
-```
-
-*Rank orders for reliabilities*
-
-- Note that this table can be sorted by different metrics, filtered for specific values for each column and is searchable.  
-- Demographics are excluded from this list of variables (because they are saved for predictive analyses).  
-- Holt and Laury test-retest is the worst for *surveys*.
-But note that this is not a survey that has been studied extensively psychometrically like others.
-This is more similar to our tasks (one that is used more often by economists).
-In previous data I have worked with retest reliablities for this task was ~.35 so the results here are in line with this.
-- Otherwise the lowest survey reliabilities are 0.5.
-
-```{r}
-rel_df %>%
-  datatable(filter='top') %>%
-  formatRound(columns=c('spearman', 'icc', 'eta_sq', 'sem'), digits=3)
-```
-
-### Histograms of reliability metrics
-
-```{r echo=FALSE}
-#Convenience functions to make prettier interactive histograms
-get_labels = function(plot_df, ref_df, bin_col, group_col){
-
-  plot_df$bin = as.numeric(factor(plot_df$x))
-  ref_df$bin = NA
-
-  for(i in 1:nrow(ref_df)){
-    for(j in 1:nrow(plot_df)){
-      # if(ref_df[i, bin_col] <= plot_df$xmax[j] & ref_df[i, bin_col]>=plot_df$xmin[j] & all(ref_df[i, group_col] == plot_df[j, group_col])){
-      if(ref_df[i, bin_col] <= plot_df$xmax[j] & ref_df[i, bin_col]>=plot_df$xmin[j] & ref_df[i, group_col] == plot_df[j, group_col]){
-        ref_df$bin[i] <- plot_df$bin[j]
-      }
-    }
-  }
-
-  ref_df = ref_df %>% 
-    group_by_("bin", group_col) %>%
-    mutate(label=as.character(toJSON(unique(dv))))
-
-  label_df = ref_df[!duplicated(ref_df[,c('label')]),c(group_col, 'bin', 'label')]
-
-  out_df = left_join(plot_df,label_df, by= c("bin", group_col))
-
-  return(out_df)
-}
-
-line_break <- function(cell){
-  out = paste(unlist(strsplit(gsub("\\]","",gsub("\\[","",cell)), ",")), sep="\n", collapse = "</br>")
-  return(out)
-}
-
-prettify_label = function(df){
-  for(i in 1:nrow(df)){
-    df$label[i] =line_break(df$label[i])
-  }
-  return(df)
-}
-```
-
-### Spearman
-
-```{r warning=FALSE, message=FALSE}
-ggplotly(ggplot_build(rel_df %>%
-                        ggplot(aes(spearman, fill=task)) +
-                        geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
-           mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
-           get_labels(.,rel_df, "spearman", "task") %>%
-           prettify_label(.) %>%
-           ggplot(aes(x,y, fill=task, label=label))+
-           geom_bar(stat='identity', position='identity', alpha=0.5)+
-           xlab('Spearman')+
-           ylab('Count')+
-           theme_bw(),
-         tooltip = 'label',
-         hoverinfo = 'text')
-```
-
-### ICC
-
-```{r warning=FALSE, message=FALSE}
-ggplotly(ggplot_build(rel_df %>%
-                        ggplot(aes(icc, fill=task)) +
-                        geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
-           mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
-           get_labels(.,rel_df, "icc", "task") %>%
-           prettify_label(.) %>%
-           ggplot(aes(x,y, fill=task, label=label))+
-           geom_bar(stat='identity', position='identity', alpha=0.5)+
-           xlab('ICC')+
-           ylab('Count')+
-           theme_bw(),
-         tooltip = 'label',
-         hoverinfo = 'text')
-```
-
-### Partial $\eta^2$
-
-Tooltip might not work well for this graph for the highest bar because the label is too large.
-But this bar indicates measures where the effect of time is very small anyway.
-We might want to pay closer attention to those not in this lowest bar since those are the variables where there is a non-negligible effect of time, indicating either a learning effect or other kind of systematic change that we did not hypothesize to observe with any of these measures.
-
-```{r warning=FALSE, message=FALSE}
-ggplotly(ggplot_build(rel_df %>%
-                        ggplot(aes(eta_sq, fill=task)) +
-                        geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
-           mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
-           get_labels(.,rel_df, "eta_sq", "task") %>%
-           prettify_label(.) %>%
-           ggplot(aes(x,y, fill=task, label=label))+
-           geom_bar(stat='identity', position='identity', alpha=0.5)+
-           xlab('Partial Eta Squared')+
-           ylab('Count')+
-           theme_bw(),
-         tooltip = 'label',
-         hoverinfo = 'text')
-```
-
-#### Effect of time
-
-So what variables show a non-negligible effect of time and in what direction? (sorted by increasing partial $\eta^2$)
-
-```{r warning=FALSE, message=FALSE}
-time_effect_vars = ggplot_build(rel_df %>%
-               ggplot(aes(eta_sq, fill=task)) +
-               geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
-  mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
-  get_labels(.,rel_df, "eta_sq", "task") %>%
-  prettify_label(.) %>%
-  filter(bin != 1 & bin !=2 & label != "NA") %>%
-  select(label, task) %>%
-  separate(label,into=c(as.character(1:27)),sep = "</br>") %>%
-  gather(key, value, -task) %>%
-  select(value, task) %>%
-  na.omit()
-
-time_effect_vars$value = gsub("\"", "", time_effect_vars$value)
-datatable(time_effect_vars)
-```
-
-Box plots showing the distributions of difference scores between the measurements at two time points for each measure can be found under the [Completion times](#diff_plot) section.
-
-### SEM
-
-```{r warning=FALSE, message=FALSE}
-ggplotly(ggplot_build(rel_df %>%
-                        ggplot(aes(sem, fill=task)) +
-                        geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
-           mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
-           get_labels(.,rel_df, "sem", "task") %>%
-           prettify_label(.) %>%
-           ggplot(aes(x,y, fill=task, label=label))+
-           geom_bar(stat='identity', position='identity', alpha=0.5)+
-           xlab('SEM')+
-           ylab('Count')+
-           theme_bw(),
-         tooltip = 'label',
-         hoverinfo = 'text')
-```
-
-### Negative icc's?
-```{r}
-neg_icc_vars = rel_df %>%
-  arrange(icc) %>% 
-  filter(icc<0) %>%
-  select(dv)
-```
-
-Some variables (`r neg_icc_vars$dv`) have <0 ICC's. This would be the case if the $MS_{error}$>$MS_{between}$.
-
-Plot data for measures with negative ICC.  
-x-axis is time 1 data and y-axis is time 2 data. The scatter plots show that the scores for measures with negative ICC's have no relationship across time points.
-```{r, fig.height=12, fig.width=12}
-tmp = data.frame()
-
-for(i in 1:nrow(neg_icc_vars)){
-  tmp = rbind(tmp, match_t1_t2(neg_icc_vars$dv[i]))
-}
-rm(neg_icc_vars)
-
-tmp %>%
-  spread(time, score) %>%
-  # mutate(dv_wrap = str_wrap(dv, width = 30)) %>%
-  ggplot(aes(`1`, `2`))+
-  geom_point()+
-  theme_bw()+
-  facet_wrap(~dv, scales='free', labeller = label_wrap_gen())
-
-```
-
-This point is clarified further by compare these scatter plots to those of variables with highest ICC. These variables have strong and clear positive linear relationships.
-
-```{r fig.height=12, fig.width=12}
-high_icc_vars = rel_df %>%
-  arrange(-icc)  %>% 
-  filter(icc>0.92) %>%
-  select(dv)
-
-tmp = data.frame()
-
-for(i in 1:nrow(high_icc_vars)){
-  tmp = rbind(tmp, match_t1_t2(high_icc_vars$dv[i]))
-}
-rm(high_icc_vars)
-
-tmp %>%
-  spread(time, score) %>%
-  ggplot(aes(`1`, `2`))+
-  geom_point()+
-  theme_bw()+
-  facet_wrap(~dv, scales='free')
-
-```
-
-```{r echo=FALSE}
-rm(tmp)
-```
-
-### Relationship between ICC and Spearman
-These two measures give mostly similar answers regarding the reliabilities of the measures except for
-
-```{r}
-ggplotly(rel_df %>%
-           ggplot(aes(spearman, icc, col=task, label=dv, label2=eta_sq))+
-           geom_point()+
-           theme_bw()+
-           theme(legend.title = element_blank())+
-           geom_abline(intercept = 0, slope=1))
-```
-
-What are the variables clustered around 0 ICC?
-
-```{r}
-rel_df %>%
-  filter(icc>(-0.1), icc<0.1) %>%
-  arrange(icc) %>%
-  datatable() %>%
-  formatRound(columns=c('spearman', 'icc', 'eta_sq', 'sem'), digits=3)
-```
-
-### Relationship between ICC and $\eta^2$
-
-```{r}
-ggplotly(rel_df %>%
-  ggplot(aes(eta_sq, icc, col=task, label=dv))+
-  geom_point()+
-  theme_bw()+
-  theme(legend.title = element_blank()))
-```
-
-## Reliability by measure types
-
-The results presented so far aim to be comprehensive but are difficult to parse through and get a clear sense of what is going on (other than a general impression that surveys tend to have higher reliabilities than tasks).
-In this and the following section we try to deal with this in two ways to make the results more digestable with two kinds of categorizations.
-
-### Tasks
-
-We aim to make contact with the literature to make the results more accesible to readers who have experience with our tasks but do not want to   
-1. take away from the novelty of the main papers coming out of this project outlining the factor structure that this data unveils   
-2. necessarily make prescriptive recommendations or theoretical arguments on why certain measures of certain processes are more reliable than others.
-
-With this in mind we reduce the list of over 270 task measures to a list of one per task by averaging only the raw measures from all the trials in a task.
-We chose to reduce the information in this manner to avoid any bias stemming from differential amount of interest and procedures applied to certain tasks over others (e.g.
-a task can have over 10 measures because it has multiple conditions and we have chosen to fit DDM's for specific conditions while another might only have 2 due to our relative inexperience and lack of interest in it).
-We check whether the number of trials in a task has a significant effect on these average reliabilities of raw measures as well.
-
-We plan to supplement/potentially replace this with an additional labeling procedure intending to capture the underlying putative cognitive processes but are deferring this until at least for another week.
-This exercise might not even prove helpful but at least a per task summary seemed a reasonable first pass.
-
-```{r echo=FALSE}
-measure_labels <- read.csv('/Users/zeynepenkavi/Downloads/retest_measure_labels.csv')
-measure_labels = measure_labels %>% select(-Patrick_hates)
-
-trim <- function (x) gsub("^\\s+|\\s+$", "", x)
-```
-
-We filter out the DDM parameters and measures for specific contrasts.
-Note that this does leave some tasks with measures that are model fits and/or for specific conditions (because at least the current datasets do not include measures that are based on all the trials **and** are raw though I could dive in to variables_exhaustive for such measures.
-For example the average relialibility for Kirby is based on three discount rates for specific conditions.).
-Here's the order of tasks by mean reliability sorted for ICC and then Spearman's $\rho$.
-
-```{r warning=FALSE, message=FALSE}
-tmp = measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  select(-measure_description, -notes, -measure_type, -task, -ddm_task) %>%
-  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
-  mutate(label_1 = trim(label_1),
-         label_2=trim(label_2),
-         label_3=trim(label_3))%>%
-  filter(label_1 %in% c('difference', 'EZ', 'hddm') ==FALSE & label_2 %in% c('difference', 'EZ', 'hddm') == FALSE) %>%
-  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
-  select(-extra_1, -extra_2) %>%
-  group_by(task_name) %>%
-  summarise(median_icc = median(icc),
-            median_spearman = median(spearman),
-            num_measures = n(),
-            num_trials = unique(num_all_trials)) %>%
-  arrange(-median_icc, -median_spearman)
-
-tmp %>%
-  datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
-```
-
-Does number of items in a task have a significant effect on the average ICC of (mostly) raw measures for all trials from a task? No.
-
-```{r warning=FALSE, message=FALSE}
-summary(lm(median_icc ~ num_trials, data = tmp))
-```
-
-Does number of items in a task have a significant effect on the average Spearman $\rho$ of (mostly) raw measures for all trials from a task? No.
-
-```{r warning=FALSE, message=FALSE}
-summary(lm(median_spearman ~ num_trials, data = tmp))
-```
-
-Does number of measures that went in to this reliability estimate have a significant effect on the average ICC of (mostly) raw measures for all trials from a task?
-It seems the more measures that goes in to summarizing overall reliability for a task the worse it gets.
-This would make sense if these variables are intended to measure different things and some are less reliable than others.
-
-```{r warning=FALSE, message=FALSE}
-summary(lm(median_icc ~ num_measures, data = tmp))
-```
-
-Does number of measures that went in to this reliability estimate have a significant effect on the average ICC of (mostly) raw measures for all trials from a task?  
-The same is true for Spearman's correlations as well.
-
-```{r warning=FALSE, message=FALSE}
-summary(lm(median_spearman ~ num_measures, data = tmp))
-```
-
-In addition to average relilibilities for each task we can look at relilibities of measures organized by the putative cognitive process they are intended to measure.
-Note however that these labels are not determined in a data driven manner.
-
-```{r warning=FALSE, message=FALSE}
-measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  select(-measure_description, -notes, -variable_type, -task, -ddm_task) %>%
-  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  group_by(measure_type) %>%
-  summarise(median_icc = median(icc),
-            median_spearman = median(spearman),
-            num_measures = n()) %>%
-  arrange(-median_icc, -median_spearman) %>%
-  datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
-```
-
-Here is what the distributions look like.  
-- Alerting: This labels consists only of ANT alerting contrast (no cue - double cue trials). 4/6 are drift diffusion parameters.    
-- Cue encoding: This label consists only of three by two task switch cost contrast (stay (where cue and task remains the same) - switch (where task is the same but cue changes) trials).
-Again most are drift diffusion parameters.
-- Delay discounting: This label consists of the discount rates for the Bickel titrator (3), Kirby items (3) and discount titrate (model fit to random set of stimuli).
-**Does the discrepancy between ICC and Spearman for these measures, given the specific interest in these tasks in the literature warrant a more detailed look in to these?**
-- Information use: This label includes Columbia Card Task (both versions) and information sampling task.  
-- Inhibition: This label includes go no-go, motor selective stop signal, stimulus selective stop signal and regular stop signal (excluding specific constrasts).  
-- Intelligence: This label includes ravens and tower of london.  
-- Learning: This label includes ART, CCT, two stage decision, dietary decision task, hierarchical rule task, information sampling task, probabilistic selection task, shift task, two stage task.   
-- Neutral writing: This label consists only of the writing task.  
-- Orienting: This labels consists only of ANT orienting contrast (center - spatial cue trials). 4/6 are drift diffusion parameters.   
-- Positive writing: This label consists only of the writing task.  
-- Proactive control: This labels consists of one DPX contrast (AY - BY trials), motor selective stop signal and regular stop signal.   
-- Reactive control: This labels consists of one DPX contrast (BX - BY trials) and motor selective stop signal.  
-- Resisting proactive interference: This label consists of one contrast in directed forgetting and recent probes tasks (negative (where the stimulus to respond to is in forgetting set) and control (where the stimulus to respond to is new) trials).
-- Response conflict: This label consists of ANT conflict contrast (congruent-incongruent), DPX, local global conflict contrast, shape matching, simon, stroop.  
-- Response selection: This label consists of choice reaction time task.  
-- Risk Taking: This label consists of ART and CCT.  
-- Selective attention: This label consists of local global task and ANT (all trials).  
-- Set shifting: This label consists of local global, PRT and three by two.    
-- Speed: This label consists of raw response times in information sampling task, simple reaction time, tower of london.  
-- Working memory: This label consists of adaptive n back, digit span, directed forgetting, keep track, recent probes, spatial span.
-
-```{r warning=FALSE, message=FALSE, fig.width=12, fig.height=10}
-measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  select(-measure_description, -notes, -variable_type, -task, -ddm_task) %>%
-  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  select(measure_type, icc, spearman) %>%
-  gather(key, value, -measure_type) %>%
-  ggplot(aes(value, fill=key))+
-  geom_histogram(position='identity', alpha=0.5)+
-  theme_bw()+
-  facet_wrap(~measure_type)+
-  theme(legend.title = element_blank())
-```
-
-### Surveys
-
-To be filled with factor labels after processing either ASU factor analyses or Russ' MIRT?
-
-## Reliability by variable types
-
-In this section we label the measures based on the procedure behind the creation of a variable.
-This moves further away from the literature and thinking about our measures in terms of specific tasks, surveys or cognitive processes and is a more novel way of presenting our data.
-
-Potentially prescriptive recommendations coming out of this section would intend to build intuitions about different treatments to data that have higher reliabilities especially when researchers plan on making their own tasks and collecting different kinds of measures.
-
-### Tasks
-
-#### DDM parameters
-
-```{r warning=FALSE, message=FALSE}
-tmp = measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  filter(task == 'task') %>%
-  select(-measure_description, -notes, -measure_type, -task) %>%
-  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
-  separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
-  mutate(label_1 = trim(label_1),
-         label_2=trim(label_2),
-         label_3=trim(label_3))%>%
-  filter(ddm_task == 1) %>%
-  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.', remove=FALSE) %>%
-  select(-extra_1, -extra_2) %>%
-  drop_na()
-```
-
-In addition to raw response time and accuracy measures we get from certain tasks we have also chosen to fit drift diffusion models to them.
-The tasks we have chosen to fit these models are: `unique(tmp$task_name)`.
-This list does not include all cognitive tasks in the battery.
-
-Table of median reliabilities for the two kinds of DDM models' (hddm and EZ) parameters compared to raw response times and accuracies depending on whether they were fit to all data or whether they are contrast of two conditions sorted by mean ICC and mean Spearman's $\rho$.
-
-- All parameters that were fit to all trials compared to contrasts have higher relialibilities.   
-- Raw variables are not the variables with highest ICC's overall. Raw response times do, however, have the highest Spearman's $\rho$'s on average. 
-- 2 of 3 hddm parameters also have higher mean reliabilities than EZ parameter estimates.
-
-```{r warning=FALSE, message=FALSE}
-tmp %>%
-  group_by(label_1,label_2, label_3) %>%
-  summarise(median_icc = median(icc),
-            median_spearman = median(spearman),
-            n_vars = n()) %>%
-  arrange(-median_icc, -median_spearman) %>%
-  datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
-```
-
-This is what the distributions of look like. Note that there is one box in the difference columns for HDDM because this model only allows this to be different across conditions.
-
-```{r warning=FALSE, message=FALSE}
-tmp = tmp %>%
-  select(dv, icc, spearman, label_1, label_2, label_3) %>%
-  gather(key, value, -dv, -label_1, -label_2, -label_3)
-
-tmp %>% ggplot(aes(label_2, value, fill=label_3))+
-  geom_boxplot()+
-  theme_bw()+
-  facet_wrap(key~label_1)+
-  labs(fill="Parameter")
-```
-
-```{r message=FALSE, echo=FALSE, eval=FALSE}
-#attempt to make the above interactive. didn't really work
-ggplotly(ggplot_build(tmp %>%
-                        ggplot(aes(value, color=label_2, fill=label_3))+
-                        geom_histogram(position='identity', alpha = 0.5)+
-                        theme_bw()+
-                        facet_wrap(key~label_1)+
-                        labs(color="Model", fill="Parameter"))$data[[1]] %>%
-           mutate(key = ifelse(PANEL %in%  c(1,2), "icc", "spearman"),
-                  label_1 = ifelse(PANEL %in%  c(1,3), "all", "difference"),
-                  label_2 = ifelse(colour == "#F8766D", "EZ", ifelse(colour == "#00BA38", "hddm", "raw")),
-                  label_3 = ifelse(fill == "#A3A500", "drift rate", ifelse(fill == "#00BF7D", "non-decision", ifelse(fill == "#E76BF3", "threshold", ifelse(fill == "#F8766D", "accuracy", "rt"))))) %>%
-           get_labels(.,tmp, "value", c("label_1", "label_2", "label_3", "key")) %>%
-           prettify_label(.) %>%
-           ggplot(aes(x, y, fill = label_3, color=label_2, label=label))+
-           geom_bar(stat='identity',position='identity', alpha=0.5)+
-           facet_wrap(key~label_1)+
-           theme_bw(),
-         tooltip = 'label',
-         hoverinfo = 'text')
-```
-### Surveys
-
-Would this be a comparison of factor reliability versus item reliability?
-
-## Completion times
-
-Do people differ in how much their scores change depending on how many days it has been since they completed the initial battery?
-
-Make data frame with difference between two scores for each measure for each subject.
-Since the scores for different measures are on different scales for comparability the difference scores are scaled (i.e.
-divided by their root mean square) but not centered so a value of 0 for the difference scores would indicate a lack of a difference between the scores of a subject.
-
-```{r warning=FALSE}
-t1_2_difference = data.frame()
-
-for(i in 1:length(numeric_cols)){
-  tmp = match_t1_t2(numeric_cols[i],format='wide')
-  tmp = tmp %>% 
-    # mutate(difference = scale(`2` - `1`))
-  mutate(difference = scale(`2` - `1`, center=F))
-  t1_2_difference = rbind(t1_2_difference, tmp)
-}
-
-t1_2_difference$difference = as.data.frame(t1_2_difference$difference)$V1
-```
-
-```{r echo=FALSE}
-rm(tmp, i)
-```
-
-Add completion dates to this data frame.
-
-```{r warning=FALSE}
-t1_2_difference = merge(t1_2_difference, comp_dates[,c('sub_id', 'days_btw')], by='sub_id')
-```
-
-```{r echo=FALSE}
-rm(test_comp_date, retest_comp_date, comp_dates)
-```
-
-The effect of number of days in between in the full model where the difference scores are regressed on a fixed effect for measure and days between the two scores and random intercepts for each subject (*Should this model include the interaction between the fixed effects?*).
-Since there are over 300 measures the output of the full model is not presented here.
-Instead below are the coefficient for the fixed effect of days between completion times and its t value.
-
-```{r}
-mod = lmer(difference ~ dv + days_btw + (1|sub_id), data = t1_2_difference)
-
-data.frame(estimate=coef(summary(mod))["days_btw","Estimate"], tval=coef(summary(mod))["days_btw","t value"])
-```
-
-For visualization purposes I summarized the difference scores per person by looking at the average difference and plot that against the number of days between completion.
-
-```{r warning=FALSE, message=FALSE}
-tmp = t1_2_difference %>%
-  group_by(sub_id) %>%
-  summarise(mean_diff = mean(difference, na.rm=T),
-            days_btw = unique(days_btw))
-
-ggplotly(tmp %>%
-  ggplot(aes(days_btw, mean_diff))+
-  geom_point()+
-  theme_bw()+
-  xlab("Days between completion")+
-  ylab("Mean standardized difference between two time points")+
-  geom_smooth(method="lm"))
-```
-
-To confirm: the slope of this line is not significant.
-That is, there doesn't seem to be a systematic difference between the two measurements depending on the number of days between the two measurements.
-
-```{r warning=FALSE, message=FALSE}
-summary(lm(mean_diff ~ days_btw, data=tmp))
-```
-
-```{r echo=FALSE}
-rm(tmp)
-```
-
-<a id="diff_plot"></a>
-For reference here are the box plots showing the distribution of difference scores for each task.
-
-```{r warning=FALSE, message=FALSE, fig.height=36}
-t1_2_difference %>%
-           ggplot(aes(reorder(dv, difference, FUN=median), difference))+
-           geom_hline(yintercept = 0,color='red',size=1)+
-           geom_boxplot()+
-           theme_bw()+
-           xlab("")+
-           ylab("Standardized difference")+
-           coord_flip()
-```
-
-## Transformation effects
-
-```{r}
-raw_retest_subs_test_data = raw_test_data[raw_test_data$sub_id %in% raw_retest_data$sub_id,]
-
-raw_numeric_cols = c()
-
-for(i in 1:length(names(raw_test_data))){
-  if(is.numeric(raw_test_data[,i])){
-    raw_numeric_cols <- c(raw_numeric_cols, names(raw_test_data)[i])
-  }
-}
-
-raw_rel_df <- data.frame(spearman = rep(NA, length(raw_numeric_cols)),
-                     icc = rep(NA, length(raw_numeric_cols)), 
-                     eta_sq = rep(NA, length(raw_numeric_cols)),
-                     sem = rep(NA, length(raw_numeric_cols)))
-
-row.names(raw_rel_df) <- raw_numeric_cols
-
-for(i in 1:length(raw_numeric_cols)){
-  raw_rel_df[raw_numeric_cols[i], 'spearman'] <- get_spearman(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data) 
-  raw_rel_df[raw_numeric_cols[i], 'icc'] <- get_icc(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data)
-  raw_rel_df[raw_numeric_cols[i], 'eta_sq'] <- get_eta(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data)
-  raw_rel_df[raw_numeric_cols[i], 'sem'] <- get_sem(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data)
-}
-
-raw_rel_df$dv = row.names(raw_rel_df)
-row.names(raw_rel_df) = seq(1:nrow(raw_rel_df))
-raw_rel_df$task = 'task'
-raw_rel_df[grep('survey', raw_rel_df$dv), 'task'] = 'survey'
-raw_rel_df = raw_rel_df %>%
-  select(dv, task, spearman, icc, eta_sq, sem)
-```
-
-```{r warning=FALSE, message=FALSE}
-raw_rel_df %>%
-  group_by(task) %>%
-  summarise(median_spearman = median(spearman),
-            median_icc = median(icc),
-            median_eta_sq = median(eta_sq),
-            median_sem = median(sem),
-            num_vars = n()) %>%
-  datatable() %>%
-  formatRound(columns=c('median_spearman', 'median_icc', 'median_eta_sq', 'median_sem'), digits=3)
-```
-
-Plots of change in reliability depending on transformation
-
-```{r}
-ggplotly(rel_df %>%
-  mutate(dv = gsub(".logTr", "", dv)) %>%
-  mutate(dv = gsub(".Re", "", dv)) %>%
-  left_join(raw_rel_df, by = 'dv') %>%
-  ggplot(aes(spearman.x, spearman.y, color = task.x, label=dv))+
-  geom_point()+
-  geom_abline(intercept = 0, slope=1)+
-  theme_bw()+
-  theme(legend.title = element_blank())+
-  xlab("Spearman with transformation")+
-  ylab("Spearman witouth transformation"))
-```
-
-```{r}
-ggplotly(rel_df %>%
-  mutate(dv = gsub(".logTr", "", dv)) %>%
-  mutate(dv = gsub(".Re", "", dv)) %>%
-  left_join(raw_rel_df, by = 'dv') %>%
-  ggplot(aes(icc.x, icc.y, color = task.x, label=dv))+
-  geom_point()+
-  geom_abline(intercept = 0, slope=1)+
-  theme_bw()+
-  theme(legend.title = element_blank())+
-  xlab("ICC with transformation")+
-  ylab("ICC without transformation"))
-```
-
-## Bootstrapping
-
-```{r eval=FALSE, echo=FALSE}
-sample_workers = function(N = 150, repl= TRUE, df=retest_data, worker_col = "sub_id"){
-  return(sample(df[,worker_col], N, replace = repl))
-}
-
-bootstrap_relialibility = function(metric = c('icc', 'spearman', 'eta_sq', 'sem'), dv_var){
-  tmp_sample = sample_workers()
-  out_df = data.frame(dv = dv_var)
-  if('icc' %in% metric){
-    out_df$icc = get_icc(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
-  }
-  if('spearman' %in% metric){
-    out_df$spearman = get_spearman(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
-  }
-  if('eta_sq' %in% metric){
-    out_df$eta_sq = get_eta(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
-  }
-  if('sem' %in% metric){
-    out_df$sem = get_sem(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
-  }
-  return(out_df)
-}
-
-# Bootstrapping everything at once in this way locally would take around four hours.
-non_hddm_numeric_cols=numeric_cols[-grep("hddm", numeric_cols)]
-
-boot_df = as.data.frame(non_hddm_numeric_cols) %>%
-  mutate(index = 1:n()) %>%
-  group_by(index) %>%
-  do(plyr::rdply(10, bootstrap_relialibility(dv_var = as.character(.$non_hddm_numeric_cols))))
-
-boot_df
-```
-
-Summarized bootstrapped reliabilities
-
-```{r}
-boot_df <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/bootstrap_merged.csv')
-
-boot_df = boot_df %>%
-  drop_na() %>%
-  mutate(icc = as.numeric(as.character(icc)),
-         spearman = as.numeric(as.character(spearman)),
-         eta_sq = as.numeric(as.character(eta_sq)),
-         sem = as.numeric(as.character(sem)))
-
-boot_df %>%
-  group_by(dv) %>%
-  summarise(icc_median = quantile(icc, probs = 0.5),
-            icc_2.5 = quantile(icc, probs = 0.025),
-            icc_97.5 = quantile(icc, probs = 0.975),
-            spearman_median = quantile(spearman, probs = 0.5),
-            spearman_2.5 = quantile(spearman, probs = 0.025),
-            spearman_97.5 = quantile(spearman, probs = 0.975)) %>%
-  datatable() %>%
-  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
-```
-
-Distributions of bootstrapped reliabilities.
-Yellow points are where our point estimates fall from the retest sample.
-Surveys are filled in red but can't be seen because the variance around their bootstrapped ICC's is very low.
-
-```{r fig.height=36}
- boot_df %>%
-  mutate(task = ifelse(grepl("survey",dv), "survey","task")) %>%
-  ggplot(aes(reorder(dv, icc, FUN=var), icc, fill = task))+
-  geom_boxplot()+
-  geom_hline(yintercept = 0,color='red',size=1)+
-  geom_point(data = rel_df, aes(x=dv, y = icc),  color = "yellow")+
-  theme_bw()+
-  theme(legend.title = element_blank())+
-  xlab("")+
-  coord_flip()
-```

### 2018-09-13 code/FrisemFigures.R

@@ -1,0 +1,282 @@
+lit_review %>%
+  filter(task_group == 'stroop') %>%
+  ggplot(aes(y = var, x = retest_reliability)) +
+  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"),
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180, size = 36),
+        axis.text.y = element_text(size = 26),
+        axis.text.x = element_text(size = 16),
+        axis.title.x = element_text(size = 16),
+        legend.text = element_text(size = 16),
+        legend.title  = element_text(size = 16),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom') +
+  guides(shape = guide_legend(override.aes = list(size=16))) +
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))
+ggsave('Lit_Review_Example.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 7, units = "in", dpi=500)
+
+#######################################################
+#######################################################
+#######################################################
+
+
+tmp %>%  
+  ggplot(aes(value, fill=sample))+
+  geom_density(alpha = 0.5, position='identity', color=NA)+
+  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
+  scale_fill_manual(breaks=c("boot","lit"),
+                    labels=c("Empirical", "Literature"),
+                    name="Predictor",
+                    values = c("white", "orange"))+
+  xlab('Variance Explained')+
+  ylab('Density')+
+  xlim(0,1)+
+  ylim(0,40)+
+  theme(axis.title.x  = element_text(size=16),
+        axis.text.x  = element_text(size=14),
[…]

### 2018-09-13 code/Interactive_Figures/app.R

@@ -1,0 +1,181 @@
+##################################################################
+# LOAD PACKAGES
+##################################################################
+
+library(shiny)
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(stringr)
+library(plotly)
+library(DT)
+
+##################################################################
+# LOAD LIT REVIEW DATA
+##################################################################
+
+lit_data <- read.csv('../../input/lit_review_figure.csv')
+
+lit_data = lit_data %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)]),
+         raw1_fit0 = grepl('raw', raw_fit),
+         type = as.character(type),
+         dv = factor(dv, levels = dv[order(task)]),
+         days_cutoff = ifelse(days < 60, days, 120),
+         days = paste(days, '\n reference:', reference))
+
+##################################################################
+# LOAD BOOT DATA
+##################################################################
+
+boot_data <- read.csv(gzfile('../../input/boot_figure.csv.gz'))
+
+boot_data = boot_data %>%
+  mutate(task_group = gsub(" ", "_", task_group),
+         task_group = gsub('_$', '_survey', task_group))
+
+##################################################################
+# UI
+##################################################################
+
+ui <- fluidPage(
+  
+  titlePanel("Retest reliabilities of self-regulation measures"),
+  
+  fluidRow(
+    column(6,
+           h4("Literature Review"),
+           selectInput(inputId = "lit_task_type",
+                       label = "View a task or survey:",
+                       choices = c("survey", "task")),
+           
+           conditionalPanel(condition = "input.lit_task_type == 'survey'",
+                            selectInput(inputId = "lit_survey_name",
+                                        label = "Choose task or survey name:",
[…]

### 2018-09-13 code/SRO_Retest_Analyses_Helper_Functions.R

@@ -1,0 +1,30 @@
+library(tidyverse)
+library(gridExtra)
+library(lme4)
+library(GGally)
+library(jsonlite)
+library(psych)
+library(rmarkdown)
+library(psych)
+library(stringr)
+library(plotly)
+library(DT)
+library(sjPlot)
+library(RecordLinkage)
+library(MCMCglmm)
+
+theme_set(theme_bw())
+
+render_this <- function(){rmarkdown::render('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Analyses.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, toc_depth = 2, code_folding = 'hide'))}
+
+options(scipen = 1, digits = 4)
+
+helper_func_path = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Helper_Functions/'
+
+source(paste0(helper_func_path, 'g_legend.R'))
+source(paste0(helper_func_path, 'g_caption.R'))
+source(paste0(helper_func_path, 'sem.R'))
+source(paste0(helper_func_path, 'trim.R'))
+source(paste0(helper_func_path, 'match_t1_t2.R'))
+source(paste0(helper_func_path, 'get_retest_stats.R'))
+source(paste0(helper_func_path, 'process_boot_df.R'))

### 2018-09-13 code/SRO_Retest_Helper_Functions/g_caption.R

@@ -1,0 +1,5 @@
+g_caption<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  cap_index <- grep('plot.caption', sapply(tmp$grobs, function(x) x$name))
+  caption <- tmp$grobs[[cap_index]]
+  return(caption)}

### 2018-09-13 code/SRO_Retest_Helper_Functions/get_retest_stats.R

@@ -1,0 +1,150 @@
+get_retest_stats = function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec, metric = c('spearman', 'icc', 'pearson', 'var_breakdown', 'partial_eta', 'sem')){
+  
+  if(sample=='full'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
+  }
+  else if(sample=='bootstrap'){
+    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
+  }
+  
+  out_cols = length(metric)
+  out_names = metric
+  
+  if('var_breakdown' %in% metric){
+    out_cols = out_cols+2
+    out_names = out_names[out_names != 'var_breakdown']
+    out_names = c(out_names, 'var_subs', 'var_ind', 'var_resid')
+  }
+
+  out = data.frame(matrix(ncol=out_cols))
+  names(out) = out_names
+  
+  if('spearman' %in% metric){
+    out$spearman = cor(df$`1`, df$`2`, method='spearman')
+  }
+  
+  if('pearson' %in% metric){
+    out$pearson = cor(df$`1`, df$`2`, method='pearson')
+  }
+  
+  if('icc' %in% metric | 'var_breakdown' %in% metric){
+    df = df %>% select(-dv, -sub_id)
+    icc = ICC(df)
+    
+    if('icc' %in% metric){
+      out$icc = icc$results['Average_fixed_raters', 'ICC']
+    }
+    
+    if('var_breakdown' %in% metric){
+      out$var_subs = icc$summary[[1]][1,'Mean Sq']
+      out$var_ind = icc$summary[[1]][2,'Mean Sq']
+      out$var_resid = icc$summary[[1]][3,'Mean Sq']
+    }
+    
+  }
+  
+  if('partial_eta' %in% metric | 'sem' %in% metric){
+    
+    mod = summary(aov(score~Error(sub_id)+time, df))
+    
+    if('partial_eta' %in% metric){
+      ss_time = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq1',]
+      ss_error = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq2',]
[…]

### 2018-09-13 code/SRO_Retest_Helper_Functions/process_boot_df.R

@@ -1,0 +1,19 @@
+process_boot_df = function(df){
+  df = df %>%
+    drop_na() %>%
+    mutate(dv = as.character(dv),
+           icc = as.numeric(as.character(icc)),
+           spearman = as.numeric(as.character(spearman)),
+           pearson = as.numeric(as.character(pearson)),
+           eta_sq = as.numeric(as.character(eta_sq)),
+           sem = as.numeric(as.character(sem)),
+           partial_eta_sq = as.numeric(as.character(partial_eta_sq)),
+           omega_sq = as.numeric(as.character(omega_sq)),
+           var_subs = as.numeric(as.character(var_subs)),
+           var_ind = as.numeric(as.character(var_ind)),
+           var_resid = as.numeric(as.character(var_resid)),
+           F_time = as.numeric(as.character(F_time)),
+           p_time = as.numeric(as.character(p_time)),
+           df_time = as.numeric(as.character(df_time)),
+           df_resid = as.numeric(as.character(df_resid)))
+  return(df)} 

### 2018-09-13 code/task_completion_times.R

@@ -1,0 +1,43 @@
+retest_data_path = "/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-03-2018/"
+
+retest_workers = c('s198', 's409', 's473', 's286', 's017', 's092', 's403', 's103','s081', 's357', 's291', 's492', 's294', 's145', 's187', 's226','s368', 's425', 's094', 's430', 's376', 's284', 's421', 's034','s233', 's027', 's108', 's089', 's196', 's066', 's374', 's007','s509', 's365', 's305', 's453', 's504', 's161', 's441', 's205','s112', 's218', 's129', 's093', 's180', 's128', 's170', 's510','s502', 's477', 's551', 's307', 's556', 's121', 's237', 's481','s259', 's467', 's163', 's111', 's427', 's508', 's190', 's091','s207', 's484', 's449', 's049', 's336', 's212', 's142', 's313','s369', 's165', 's028', 's216', 's346', 's083', 's391', 's388','s384', 's275', 's442', 's505', 's098', 's456', 's209', 's372','s179', 's168', 's084', 's329', 's373', 's065', 's277', 's026','s011', 's063', 's507', 's005', 's495', 's501', 's032', 's326','s396', 's420', 's469', 's244', 's359', 's110', 's383', 's254','s060', 's339', 's380', 's471', 's206', 's182', 's500', 's314','s285', 's086', 's012', 's097', 's149', 's192', 's173', 's262','s273', 's402', 's015', 's014', 's085', 's489', 's071', 's062','s042', 's009', 's408', 's184', 's106', 's397', 's451', 's269','s295', 's265', 's301', 's082', 's238', 's328', 's334')
+
+#Get file list in Individual Measures
+file_list = list.files(paste0(retest_data_path,'Individual_Measures'))
+#For each file in file list read in data from Individual Measures
+retest_task_completion_times = data.frame()
+test_task_completion_times = data.frame()
+
+#output: task, sub_id, finish_day, finish_hour
+for(i in 1:length(file_list)){
+  tmp = read.csv(gzfile(paste0(retest_data_path,'Individual_Measures/',file_list[i])))
+  task = gsub('.csv.gz','',file_list[i])
+  tmp = tmp %>% 
+    filter(as.character(worker_id) %in% retest_workers) %>%
+    group_by(worker_id) %>% 
+    summarise(finishtime = unique(finishtime)) %>% 
[…]

### 2018-10-15 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 
+source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Analyses_Workspace.R')
+
 test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_03-29-2018/'
@@
 retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-29-2018/'
-```
-
-# Introduction
-
-The psychological construct of self-regulation, or related concepts of impulsivity, self-control, inhibition and others correlate with problematic real-world behaviors such as disordered eating (Mobbs et al., 2010, Verbeken et al., 2009, Nederkoorn et al.
-2006a, Nederkoorn et al., 2006b), gambling (Lawrence et al., 2009, Fuentes et al., 2006, Alessi and Petry, 2003), drug addiction (Coffey et al., 2003, de Wit, Crean and John, 2000, Sher, Bartholow and Wood, 2000, Kirby, Petry and Bickel, 1999) or bad financial decisions (Meier and Sprenger, 2015, Meier and Sprenger, 2013, Meier and Sprenger 2012).
-In these lines of work measures of self-regulation are used as behavioral assays for individual difference analyses.
-An underlying assumption of treating behavioral measures as reflective of person-specific characteristics is that the measures of self-regulation are stable across time.
-In other words, that they have high test-retest reliability (or high between- and low within-subject variability).
-This assumption is not extensively and equally tested in the literature for all measures of self-regulation.
-Self-regulation measures can be grouped in two broad categories: Surveys and cognitive tasks.
-While the former typically goes through some form of psychometric testing often filtering out items with low test-retest reliability this is less frequently true for the latter.
-Though some empirical results on test-retest reliabilities of certain cognitive task measures are reported in pockets of the literature an exhaustive summary or systematic elimination of tasks or measures based on stability across time does not seem to exist.
-Test-retest reliability is, however, crucial for individual difference analyses (Hedge, Powell and Sumner, 2017).
-To answer the question of reliability of self-regulation measures comprehensively we created a large battery consisting of both cognitive task and survey measures.
-In this paper we make two contributions: First we provide a review of these measures along with their reported reliabilities when available.
-Then we report results of a large study we conducted where we collected retest reliability data using all of these measures.
-This effort not only fills in a notable gap in the literature in clarifying which measures of self-regulation are stable across time but also provides guidance on factors to pay attention to when constructing new tasks for individual difference measures.
-
-# Methods
-
-## Data collection
-
-This sample consists of data for 150 subjects of the original sample of 522 that has completed the initial battery of 37 cognitive tasks, 23 surveys and 3 surveys on demographics.
-Details of the original sample as well as quality control (qc) procedures are described elsewhere (Eisenberg et al., 2017).
-Invited participants were chosen randomly and only subsets of them were invited for a given batch (instead of opening the battery to all qualified subjects) with the intention to avoid a potential oversampling and bias towards "high self regulators".
-
-```{r warning=FALSE, message=FALSE}
-workers = read.csv(paste0(retest_data_path,'Local/User_717570_workers.csv'))
-workers = workers %>% 
-  group_by(Worker.ID) %>%
-  mutate(Retest_worker=ifelse(sum(CURRENT.RetestWorker,CURRENT.RetestWorkerB2,CURRENT.RetestWorkerB3,CURRENT.RetestWorkerB4,CURRENT.RetestWorkerB5,na.rm=T)>0,1,0)) %>%
-  ungroup()
-
-worker_counts <- fromJSON(paste0(retest_data_path,'/Local/retest_worker_counts.json'))
-
-worker_counts = as.data.frame(unlist(worker_counts))
-names(worker_counts) = "task_count"
 ```
@@
 
-```{r warning=FALSE, message=FALSE}
-disc_comp_date = read.csv(paste0(retest_data_path,'Local/discovery_completion_dates.csv'), header=FALSE)
-val_comp_date = read.csv(paste0(retest_data_path,'Local/validation_completion_dates.csv'), header=FALSE)
-test_comp_date = rbind(disc_comp_date, val_comp_date)
-rm(disc_comp_date, val_comp_date)
-retest_comp_date = read.csv(paste0(retest_data_path,'Local/retest_completion_dates.csv'), header=FALSE)
-comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
-names(comp_dates) <- c("sub_id", "retest_comp", "test_comp")
-comp_dates$retest_comp = as.Date(comp_dates$retest_comp)
-comp_dates$test_comp = as.Date(comp_dates$test_comp)
-comp_dates$days_btw = with(comp_dates, retest_comp-test_comp)
-```
-
 Data collection took place on average `r round(mean(as.numeric(comp_dates$days_btw)))` number of days after the completion of the initial battery with a range of `r round(range(as.numeric(comp_dates$days_btw)))[1]` to `r round(range(as.numeric(comp_dates$days_btw)))[2]` days.
 
-```{r}
-rm(test_comp_date, retest_comp_date, comp_dates)
-```
+The variables included in this report are:  
+- meaningful variables (includes only hdddm parameters)  
+- EZ diffusion parameters  
+- Raw RT and Accuracy measures  
+- Variables found in the literature (for comparison)
+
+For reference here are the variables that are **not** included in the analyses of the remainder of this report because they were not of theoretical interest in factor structure analyses of this data.
+These include drift diffusion and other model parameters for specific conditions within a task; survey variables that are not part of the dependant variables for that survey in the literature and demographics (these are saved for prediction analyses).
+
+```{r}
+test_data2 <- read.csv(paste0(retest_data_path, 't1_data/variables_exhaustive.csv'))
+
+df <- data.frame(names(test_data2)[which(names(test_data2) %in% names(test_data) == FALSE)])
+names(df) = c('vars')
+
+df %>%
+  filter(vars != "X")
+```
+
+```{r}
+rm(test_data2, df)
+```
+
+# Results
 
@@
 ```{r}
-test_demog <- read.csv(paste0(retest_data_path, '/t1_data/demographic_health.csv'))
-
-retest_demog <- read.csv(paste0(retest_data_path, 'demographic_health.csv'))
-
-retest_demog = retest_demog[retest_demog$X %in% test_demog$X,]
-
-names(test_demog)[which(names(test_demog) == 'X')] <-'sub_id'
-names(retest_demog)[which(names(retest_demog) == 'X')] <-'sub_id'
-
 summary(test_demog %>%
@@
 
-## Literature
-
-One of the major contributions of this project is a comprehensive literature review of the retest reliabilities of the surveys and tasks that were used.
-We reviewed the literature on a measure (as opposed to task level) paying attention to differences in sample size, the delay between the two measurements as well as the statistic that was used to assess reliabilities (e.g.
-Spearman vs.
-Pearson correlations).
-Here we present a table and a visualization summarizing our findings.
-References mentioned in the table below can be found [here](https://docs.google.com/spreadsheets/d/1hcED4_rWSGSE8Td0aqT0kWqlLCBAzRNKBXj3tSram58/edit?usp=sharing).
-
-```{r}
-lit_review <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/lit_review_figure.csv')
-
+## Literature review
+
+Here's what our literature review looks like
+
+```{r}
 lit_review
@@
 ```{r message=FALSE}
-lit_review = lit_review %>%
-  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
-  mutate(task_group = factor(task_group, levels = task_group[order(task)]),
-         type = as.character(type)) %>%
-  mutate(task_group = gsub("_", " ", task_group),
-         var = gsub("_", " ", var)) %>%
-  arrange(task_group, raw_fit, var) %>%
-  mutate(task_group = gsub("survey", "", task_group),
-         task_group = gsub("task", "", task_group),
-         task_group = str_to_title(task_group)) %>%
-  mutate(task_group = ifelse(task_group == "Psychological Refractory Period Two Choices", "Psychological Refractory Period", ifelse(task_group == "Angling Risk Always Sunny", "Angling Risk", ifelse(task_group == "Two Stage", "Two Step", ifelse(task_group == "Threebytwo", "Task Switching", ifelse(task_group == "Adaptive N Back", "Adaptive N-back", ifelse(task_group == "Go Nogo", "Go/No-go",  ifelse(task_group == "Ravens", "Raven's", task_group)))))))) %>%
-  mutate(task_group = ifelse(task_group == "Bis Bas ", "BIS-BAS", ifelse(task_group == "Bis11 ", "BIS-11", ifelse(task_group == "Dospert Eb ", "DOSPERT EB", ifelse(task_group == "Dospert Rp ", "DOSPOERT RP", ifelse(task_group == "Dospert Rt ", "DOSPERT RT", ifelse(task_group == "Erq ", "ERQ", ifelse(task_group == "Upps Impulsivity ", "UPPS-P", task_group))))))))  %>%
-  select(-measure_description)
-
 tmp = lit_review[duplicated(lit_review$reference)==FALSE,]
@@
 
-## Loading datasets
-
-The variables included in this report are:  
-- meaningful variables (includes only hdddm parameters)  
-- EZ diffusion parameters  
-- Raw RT and Accuracy measures  
-- Variables found in the literature (for comparison)
-
-```{r echo=FALSE}
-#Get variables of interest from Ian's release
-tmp1 <- read.csv(paste0(test_data_path,'meaningful_variables.csv'))
-tmp2 <- read.csv(paste0(test_data_path,'meaningful_variables_noDDM.csv'))
-tmp3 <- read.csv(paste0(test_data_path,'meaningful_variables_EZ.csv'))
-retest_report_vars = c(names(tmp1), names(tmp2), names(tmp3))
-retest_report_vars = unique(retest_report_vars)
-lit_rev_vars = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% retest_report_vars == FALSE)])
-retest_report_vars = c(retest_report_vars, lit_rev_vars)
-rm(tmp1, tmp2, tmp3, lit_rev_vars)
-```
-
-### Load time 1 data
-```{r}
-test_data <- read.csv(paste0(retest_data_path,'t1_data/variables_exhaustive.csv'))
-
-test_data <- test_data[,names(test_data) %in% retest_report_vars]
-
-test_data$X <- as.character(test_data$X)
-names(test_data)[which(names(test_data) == 'X')] <-'sub_id' 
-```
-
-For reference here are the variables that are **not** included in the analyses of the remainder of this report because they were not of theoretical interest in factor structure analyses of this data so far.
-These include drift diffusion and other model parameters for specific conditions within a task; survey variables that are not part of the dependant variables for that survey in the literature and demographics (these are saved for prediction analyses).
-
-```{r}
-test_data2 <- read.csv(paste0(retest_data_path, 't1_data/variables_exhaustive.csv'))
-
-df <- data.frame(names(test_data2)[which(names(test_data2) %in% names(test_data) == FALSE)])
-names(df) = c('vars')
-
-df
-```
-
-```{r echo=FALSE}
-rm(test_data2, df)
-```
-
-### Load time 2 data 
-```{r}
-retest_data <- read.csv(paste0(retest_data_path,'variables_exhaustive.csv'))
-
-retest_data <- retest_data[,names(retest_data) %in% retest_report_vars]
-
-retest_data$X <- as.character(retest_data$X)
-names(retest_data)[which(names(retest_data) == 'X')] <-'sub_id' 
-retest_data = retest_data[retest_data$sub_id %in% test_data$sub_id,]
-```
-
-### Replace HDDM parameters in t1 data
-
-Since HDDM parameters depend on the sample on which they are fit we refit the model on t1 data for the subjects that have t2 data.
-Here we replace the HDDM parameters in the current t1 dataset with these refitted values.
-
-```{r}
-hddm_refits <- read.csv(paste0(retest_data_path,'t1_data/hddm_refits_exhaustive.csv'))
-
-hddm_refits = hddm_refits[,names(hddm_refits) %in% retest_report_vars]
-
-hddm_refits$X <- as.character(hddm_refits$X)
-names(hddm_refits)[which(names(hddm_refits) == 'X')] <-'sub_id'
-
-#For later comparison of whether fitting the DDM parameters on full or retest sample makes a big difference
-test_data_full_sample_hddm <- test_data
-
-#drop hddm columns from test_data
-test_data = cbind(test_data$sub_id, test_data[,names(test_data) %in% names(hddm_refits) == FALSE])
-
-#fix naming before merging
-names(test_data)[which(names(test_data) == 'test_data$sub_id')] <-'sub_id'
-
-#merge hddm refits to test data
-test_data = merge(test_data, hddm_refits, by="sub_id")
-```
-
-# Results
-
 ## Data quality checks
@@
 Point estimates of reliability for the demographic variabels.
-
-```{r}
-demog_boot_df <- read.csv(gzfile(paste0(retest_data_path,'demog_boot_merged.csv.gz')))
-
-demog_boot_df = process_boot_df(demog_boot_df)
-```
 
@@
 
-```{r}
-retest_task_comp_times = read.csv(paste0(retest_data_path, 'Local/retest_task_completion_times.csv'))
-test_task_comp_times = read.csv(paste0(retest_data_path, 'Local/test_task_completion_times.csv'))
-task_comp_times = merge(retest_task_comp_times, test_task_comp_times, by=c('worker_id','task'))
-rm(retest_task_comp_times, test_task_comp_times)
-task_comp_times = task_comp_times %>%
-  select(-X.x, -X.y) %>%
-  mutate(finish_day.x = as.Date(finish_day.x),
-         finish_day.y = as.Date(finish_day.y),
-         days_btw = finish_day.x-finish_day.y) %>%
-  rename(sub_id=worker_id)
-```
-
 ```{r warning=FALSE}
@@
 ```{r}
-tmp = read.csv(gzfile(paste0(retest_data_path, 'items.csv.gz')))
-tmp = tmp %>% 
-  filter(worker == 's005') %>% 
-  select(item_ID, item_text) %>% 
-  mutate(item_text = trimws(as.character(item_text))) %>%
-  unite(item, c("item_ID", "item_text"), sep = "___")
-
-comb = as.data.frame(t(combn(unique(tmp$item),2)))
-
-duplicate_items = comb %>% 
-  filter(grepl('dospert', V1)==FALSE) %>%
-  filter(grepl('selection_optimization', V1)==FALSE) %>%
-  filter(grepl('sensation_seeking', V1)==FALSE) %>%
-  separate(V1, c("item1_ID", "item1_text"), sep="___") %>%
-  separate(V2, c("item2_ID", "item2_text"), sep="___") %>%
-  mutate(similarity = levenshteinSim(item1_text, item2_text)) %>%
-  filter(similarity>0.8) %>%
-  select(similarity, item1_ID, item2_ID, item1_text, item2_text) %>%
-  arrange(-similarity)
-
 duplicate_items
@@
 #item1_t2 - item2_t1
-
-duplicate_items_data_t1 = read.csv(paste0(test_data_path, 'subject_x_items.csv'))
-duplicate_items_data_t2 = read.csv(paste0(retest_data_path, 'subject_x_items.csv'))
 
@@
 
-Read in and process bootstrapped results.
-
-```{r}
-boot_df <- read.csv(gzfile(paste0(retest_data_path,'bootstrap_merged.csv.gz')))
-
-boot_df = process_boot_df(boot_df)
-
-boot_df = boot_df[boot_df$dv %in% retest_report_vars,]
-
-# Check if you have all variables bootstrapped
-# retest_report_vars[which(retest_report_vars %in% boot_df$dv==FALSE)]
-
-# Boot df contains hddm parameters fit on the full sample in the t1 data
-# refits_bootstrap_merged.csv.gz contains bootstrapped reliabilities
-
-refit_boot_df = read.csv(gzfile(paste0(retest_data_path,'refits_bootstrap_merged.csv.gz')))
-
-refit_boot_df = process_boot_df(refit_boot_df)
-
-fullfit_boot_df = boot_df[as.character(boot_df$dv) %in% unique(as.character(refit_boot_df$dv)),]
-
-boot_df = boot_df[!as.character(boot_df$dv) %in% unique(as.character(refit_boot_df$dv)),]
-
-boot_df = rbind(boot_df, refit_boot_df)
-
-rm(refit_boot_df)
-```
-
 Summarize bootstrapped results and merge to lit review data
-
-```{r message=FALSE}
-var_boot_df = boot_df %>%
-  group_by(dv) %>%
-  summarise(mean_icc = mean(icc),
-            mean_pearson = mean(pearson))
-
-rel_comp = lit_review %>%
-  left_join(var_boot_df, by = 'dv')
-```
 
@@
 
-```{r echo=FALSE}
-measure_labels <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/measure_labels.csv')
-measure_labels = measure_labels %>% select(-measure_description)
-# Check if there are any missing variables
-# retest_report_vars[(retest_report_vars %in% measure_labels$dv == FALSE)]
-# measure_labels$dv[(measure_labels$dv %in% retest_report_vars == FALSE)]
-```
-
-```{r}
-meaningful_vars = read.table('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/meaningful_vars.txt')
-meaningful_vars = as.character(meaningful_vars$V1)
-
+```{r}
 tmp = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% meaningful_vars == FALSE)])
@@
 ```{r eval=FALSE}
-#summary(lmerTest::lmer(icc ~  task + (1|dv), boot_df))
-# m = MCMCglmm(icc ~  task, random = ~dv, data=boot_df, nitt = 1300, burnin = 300)
-m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_task_model.rds')
-summary(m)
+summary(icc_by_task_model)
 ```
@@
 tmp = boot_df %>%
-  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
-         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
-         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
   select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct)
 
-# summary(lmerTest::lmer(var_subs_pct~task+(1|dv),tmp%>%select(-var_ind_pct,-var_resid_pct)))
-m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_subs_pct_by_task_model.rds')
-summary(m)
+summary(var_subs_pct_by_task_model)
 ```
@@
 ```{r}
-# summary(lmerTest::lmer(var_ind_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_resid_pct)))
-m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_ind_pct_by_task_model.rds')
-summary(m)
-```
-
-```{r}
-# summary(lmerTest::lmer(var_resid_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_ind_pct)))
-m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_resid_pct_by_task_model.rds')
-summary(m)
+summary(var_ind_pct_by_task_model)
+```
+
+```{r}
+summary(var_resid_pct_by_task_model)
 ```
@@
 
-Are these significantly different between surveys and tasks? No.
-
-```{r}
-chisq.test(matrix(data = c(23,74-23,133, 372-133), nrow=2))
-```
-
-```{r}
-boot_df %>%
-  select(dv, p_time, task, pearson) %>%
-  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
-  group_by(dv)%>%
-  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
-            task = unique(task),
-            mean_pearson = mean(pearson))%>%
-  filter(pct_sig_time_effect>5) %>%
-  arrange(task,-pct_sig_time_effect) %>%
-
-```
-
 ### SEM CI calculation
@@
 
-This doesn't make it easier to interpret whether it is a performance improvement or decline.
-In fact 'performance' isn't even necessarily the correct term here.
-Using the valence assignments of the measures look at whether it translates to an increase or decrease in self-regulation.
-Of the 66 this makes sense for 54 variables.
-
-```{r}
-valence_df = read.csv(paste0(retest_data_path, 'DV_valence.csv'), header = F)
-valence_df = valence_df %>% rename(dv = V1, valence = V2)
-valence_df$task = 'task'
-valence_df[grep('survey', valence_df$dv), 'task'] = 'survey'
-valence_df[grep('holt', valence_df$dv), 'task'] = "task"
-
-valence_df = valence_df %>% filter(dv %in% retest_report_vars)
-with(valence_df, table(task, valence))
-#Comparable level of valences for task and survey measures
-chisq.test(with(valence_df, table(task, valence)))
-```
-
-```{r warning=FALSE, message=FALSE}
-
-mean_diff_df %>%
-  left_join(valence_df, by = c("dv", "task")) %>%
-  mutate(sc_increase = ifelse(prop_one_direction>0&valence==1,1,ifelse(prop_one_direction<0&valence==-1,1,0)),
-         sc_decrease = ifelse(prop_one_direction>0&valence==-1,1,ifelse(prop_one_direction<0&valence==1,1,0))) %>%
-  group_by(task) %>%
-summarise(sum_sc_increase = sum(sc_increase,na.rm=T),
-          sum_sc_decrease = sum(sc_decrease,na.rm=T)) %>%
-  gather(key, value, -task) %>%
-  mutate(total_vars = c(74, 372, 74, 372),
-         prop = value/total_vars) %>%
-  ggplot(aes(key, prop, group=task, fill=task))+
-  geom_bar(stat = "identity", position = position_dodge(), alpha = 0.5)+
-  theme(legend.title = element_blank(),
-        axis.title.y = element_text(size=14),
-        axis.text.x = element_text(size=14))+
-  xlab("")+
-  ylab("Proportion of measures")+
-  ylim(0, 1)+
-  scale_x_discrete(breaks = c("sum_sc_decrease", "sum_sc_increase"),
-                   labels = c("Self-control decrease", "Self-control increase"))
-
-ggsave('PropTimeEffectsValence.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 7, height = 5, units = "in", limitsize = FALSE, dpi = 300)
-```
-
-Variables that show more than 5% difference in a direction do not depend on whether they translate to a self control increase or decrease.
-
-```{r}
-chisq.test(matrix(data = c(23,54-23,31,54-31), nrow=2))
-```
-
-Do they differ depending on whether they are task or survey variables? No.
-
-```{r}
-chisq.test(matrix(data = c(5,74-5,60,372-60), nrow=2))
-```
-
-```{r}
-rm(mean_diff_df)
-```
+This doesn't make it easier to interpret whether it is a performance improvement or decline. In fact 'performance' isn't even necessarily the correct term here.
 
@@
 
-```{r}
-tmp = tmp%>%
-  mutate(task_name = gsub("_", " ", task_name),
-         task_name = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", task_name, perl=TRUE))
-
-names(tmp) = gsub("_", " ", names(tmp))
-names(tmp) = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", names(tmp), perl=TRUE)
-
-sjt.df(tmp %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/task_rel_table.doc")
-```
-
 ### Number of trials
@@
 
-# summary(lm(icc ~ num_all_trials, data = tmp))
-# summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
-m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_num_trials_model.rds')
-summary(m)
+summary(icc_by_num_trials_model)
 ```
@@
 ```{r}
-t1_dvs = read.csv(paste0(retest_data_path, 't1_shift_dvs.csv'))
-t2_dvs = read.csv(paste0(retest_data_path, 't2_shift_dvs.csv'))
-
 t1_dvs = t1_dvs %>% select(-X)
@@
 ```{r warning=FALSE, message=FALSE}
-trial_num_rel_df = read.csv(paste0(retest_data_path, 'trial_num_rel_df_shift.csv'))
-
 trial_num_rel_df %>%
@@
 
-```{r}
-tmp_save = tmp_save %>%
-  ungroup() %>%
-  mutate(contrast = as.character(contrast),
-         raw_fit = as.character(raw_fit),
-         rt_acc = as.character(rt_acc)) %>%
-  arrange(-icc_median)
-
-sjt.df(tmp_save %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/ddm_rel_table.doc")
-```
-
 Comparing contrast vs non-contrast: overall has higher reliability than difference.
@@
 ```{r}
-# summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "non-contrast")))
-m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_rawfit_noncon_model.rds')
-summary(m)
+summary(icc_by_rawfit_noncon_model)
 ```
@@
 ```{r}
-# summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "contrast")))
-m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_rawfit_con_model.rds')
-summary(m)
+summary(icc_by_rawfit_con_model)
 ```

### 2018-10-15 code/SRO_Retest_Analyses_Workspace.R

@@ -1,0 +1,284 @@
+# Load data
+
+library(tidyverse)
+library(jsonlite)
+
+test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_03-29-2018/'
+
+retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-29-2018/'
+
+#########################
+## Battery completion data ####
+#########################
+
+workers = read.csv(paste0(retest_data_path,'Local/User_717570_workers.csv'))
+workers = workers %>%
+  group_by(Worker.ID) %>%
+  mutate(Retest_worker=ifelse(sum(CURRENT.RetestWorker,CURRENT.RetestWorkerB2,CURRENT.RetestWorkerB3,CURRENT.RetestWorkerB4,CURRENT.RetestWorkerB5,na.rm=T)>0,1,0)) %>%
+  ungroup()
+
+worker_counts <- fromJSON(paste0(retest_data_path,'/Local/retest_worker_counts.json'))
+
+worker_counts = as.data.frame(unlist(worker_counts))
+names(worker_counts) = "task_count"
+
+disc_comp_date = read.csv(paste0(retest_data_path,'Local/discovery_completion_dates.csv'), header=FALSE)
+val_comp_date = read.csv(paste0(retest_data_path,'Local/validation_completion_dates.csv'), header=FALSE)
+test_comp_date = rbind(disc_comp_date, val_comp_date)
+rm(disc_comp_date, val_comp_date)
+retest_comp_date = read.csv(paste0(retest_data_path,'Local/retest_completion_dates.csv'), header=FALSE)
+comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
+names(comp_dates) <- c("sub_id", "retest_comp", "test_comp")
+comp_dates$retest_comp = as.Date(comp_dates$retest_comp)
+comp_dates$test_comp = as.Date(comp_dates$test_comp)
+comp_dates$days_btw = with(comp_dates, retest_comp-test_comp)
+
+rm(test_comp_date, retest_comp_date, comp_dates)
+
+### Completion time data
+
+retest_task_comp_times = read.csv(paste0(retest_data_path, 'Local/retest_task_completion_times.csv'))
+test_task_comp_times = read.csv(paste0(retest_data_path, 'Local/test_task_completion_times.csv'))
[…]

### 2018-10-15 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Analyses_Workspace.R')
-
-test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_03-29-2018/'
-
-retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-29-2018/'
 ```
@@
 tmp = lit_review[duplicated(lit_review$reference)==FALSE,]
-
-nrow(tmp)
-sum(tmp$sample_size)
-nrow(lit_review)
-```
+```
+
+The literature review included `r nrow(tmp)` papers, `r sum(tmp$sample_size)` participants and `r nrow(lit_review)` data points on reliability.
 
@@
 ```{r warning= FALSE, message =FALSE, echo=FALSE}
-p1_legend = lit_review %>%
-  filter(task == 'task') %>%
-ggplot(aes(y = var, x = retest_reliability)) +
-  geom_point(aes(size=sample_size, shape=type))+
-  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
-  theme(panel.spacing = unit(0.5, "lines"),
-        strip.placement = "outside",
-        strip.text.y = element_text(angle=180),
-        panel.background = element_rect(fill = NA),
-        panel.grid.major = element_line(colour = "grey80"),
-        legend.position = 'bottom') +
-  xlab("")+
-  ylab("")+
-  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
-  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))
-
-p1 = lit_review %>%
-  filter(task == 'task') %>%
-ggplot(aes(y = var, x = retest_reliability)) +
-  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
-  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
-  theme(panel.spacing = unit(0.5, "lines"),
-        strip.placement = "outside",
-        strip.text.y = element_text(angle=180),
-        panel.background = element_rect(fill = NA),
-        panel.grid.major = element_line(colour = "grey80"),
-        legend.position = 'bottom') +
-  xlab("")+
-  ylab("")+
-  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
-  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))
-
-p2 = lit_review %>%
-  filter(task == 'survey') %>%
-ggplot(aes(y = var, x = retest_reliability)) +
-  geom_point(aes(size=sample_size, shape = type), color = '#F8766D')+
-  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
-  theme(panel.spacing = unit(0.5, "lines"),
-        strip.placement = "outside",
-        strip.text.y = element_text(angle=180),
-        panel.background = element_rect(fill = NA),
-        panel.grid.major = element_line(colour = "grey80")) +
-  xlab("")+
-  ylab("")+
-  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
-  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 17, 3))
-
-mylegend<-g_legend(p1_legend)
-
-p3 <- arrangeGrob(arrangeGrob(p1 +theme(legend.position="none"),
-                         p2 + theme(legend.position="none"),
-                         nrow=1),
-             mylegend, nrow=2,heights=c(10, 1))
-
-ggsave('Lit_Review_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 20, units = "in", dpi=100)
-rm(p1, p2, p3, p1_legend, mylegend)
+
 ```

### 2018-10-15 code/FrisemFigures.R

@@ -1,282 +1,0 @@
-lit_review %>%
-  filter(task_group == 'stroop') %>%
-  ggplot(aes(y = var, x = retest_reliability)) +
-  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
-  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
-  theme(panel.spacing = unit(0.5, "lines"),
-        strip.placement = "outside",
-        strip.text.y = element_text(angle=180, size = 36),
-        axis.text.y = element_text(size = 26),
-        axis.text.x = element_text(size = 16),
-        axis.title.x = element_text(size = 16),
-        legend.text = element_text(size = 16),
-        legend.title  = element_text(size = 16),
-        panel.background = element_rect(fill = NA),
-        panel.grid.major = element_line(colour = "grey80"),
-        legend.position = 'bottom') +
-  guides(shape = guide_legend(override.aes = list(size=16))) +
-  xlab("")+
-  ylab("")+
-  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
-  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))
-ggsave('Lit_Review_Example.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 7, units = "in", dpi=500)
-
-#######################################################
-#######################################################
-#######################################################
-
-
-tmp %>%  
-  ggplot(aes(value, fill=sample))+
-  geom_density(alpha = 0.5, position='identity', color=NA)+
-  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
-  scale_fill_manual(breaks=c("boot","lit"),
-                    labels=c("Empirical", "Literature"),
-                    name="Predictor",
-                    values = c("white", "orange"))+
-  xlab('Variance Explained')+
-  ylab('Density')+
-  xlim(0,1)+
-  ylim(0,40)+
-  theme(axis.title.x  = element_text(size=16),
-        axis.text.x  = element_text(size=14),
[…]

### 2018-10-15 code/NeuroeconAbstractPredictionAnalyses.R

@@ -1,111 +1,0 @@
-get_var_exp = function(demog_var, dv){
-  
-  df = merge(test_demog[,c("sub_id", demog_var)], test_data[,c("sub_id", dv)])
-  df[,demog_var] = scale(df[,demog_var])
-  df[,dv] = scale(df[,dv])
-  
-  mod = lm(df[,demog_var]~ df[,dv])
-  var_exp = summary(mod)$r.squared
-  
-  return(var_exp)
-}
-
-tmp = measure_labels %>% filter(ddm_task == 1 & rt_acc != 'other')
-dvs = unique(as.character(tmp$dv))
-
-out = data.frame(dv = dvs)
-
-get_var_exp_for_demog = function(demog_var){
-  
-  out[,demog_var] = NA
-  
-  for(i in 1:length(dvs)){
-    out[i, demog_var] = get_var_exp(demog_var = demog_var, dv=dvs[i])
-  }
-  
-  return(out)
-}
-
-init_demogs = c("HouseholdIncome","RetirementAccount", "HowLongSmoked", "CigsPerDay", "AlcoholHowOften", "CannabisHowOften",  "Nervous", "Hopeless", "RestlessFidgety","Depressed","EverythingIsEffort","Worthless")
-
-results = out
-
-for(i in 1:length(init_demogs)){
-  demog_var = init_demogs[i]
-  tmp_out = get_var_exp_for_demog(demog_var = demog_var)
-  results = merge(results, tmp_out, by="dv")
-}
-
-results = merge(results, measure_labels, by="dv")
-
-tmp = results %>%
-  select(-ddm_task, -num_all_trials) %>%
-  mutate(contrast = ifelse(overall_difference == "difference", 1, 0),
-         raw_bin = ifelse(raw_fit == "raw",1,0)) %>%
-  gather(key, value, -dv, -overall_difference, -raw_fit, -rt_acc, -contrast, -raw_bin) %>%
-  mutate(value = as.numeric(value))
-  
-#Initial predictions for:
-
-#Desired output: 
-  # rows of dvs
-  # cols of demog_vars
-  # cells of var explained
-  
-# HeightInches
-# WeightPounds
-# 
-# HouseholdIncome
-# RetirementAccount
-# RetirementPercentStocks
-# RentOwn
-# MortgageDebt
-# CarDebt
-# EducationDebt
[…]

### 2018-10-15 code/SRO_Retest_Analyses_Helper_Functions.R

@@ -1,8 +1,6 @@
-library(tidyverse)
 library(gridExtra)
 library(lme4)
 library(GGally)
-library(jsonlite)
 library(psych)
 library(rmarkdown)
 library(psych)

### 2018-10-15 code/figure_scripts/Lit_Review_Plot.R

@@ -1,0 +1,59 @@
+p1_legend = lit_review %>%
+  filter(task == 'task') %>%
+  ggplot(aes(y = var, x = retest_reliability)) +
+  geom_point(aes(size=sample_size, shape=type))+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"),
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom') +
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))
+
+p1 = lit_review %>%
+  filter(task == 'task') %>%
+  ggplot(aes(y = var, x = retest_reliability)) +
+  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"),
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom') +
+  xlab("")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))
+
+p2 = lit_review %>%
+  filter(task == 'survey') %>%
+  ggplot(aes(y = var, x = retest_reliability)) +
+  geom_point(aes(size=sample_size, shape = type), color = '#F8766D')+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"),
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
[…]

### 2018-10-15 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 ```{r, message=FALSE, warning=FALSE, include=FALSE}
-source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Analyses_Helper_Functions.R')
-
-source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Analyses_Workspace.R')
+source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/SRO_Retest_Analyses_Workspace.R')
 ```

### 2018-10-15 code/SRO_Retest_Analyses_Workspace.R

@@ -1,284 +1,0 @@
-# Load data
-
-library(tidyverse)
-library(jsonlite)
-
-test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_03-29-2018/'
-
-retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-29-2018/'
-
-#########################
-## Battery completion data ####
-#########################
-
-workers = read.csv(paste0(retest_data_path,'Local/User_717570_workers.csv'))
-workers = workers %>%
-  group_by(Worker.ID) %>%
-  mutate(Retest_worker=ifelse(sum(CURRENT.RetestWorker,CURRENT.RetestWorkerB2,CURRENT.RetestWorkerB3,CURRENT.RetestWorkerB4,CURRENT.RetestWorkerB5,na.rm=T)>0,1,0)) %>%
-  ungroup()
-
-worker_counts <- fromJSON(paste0(retest_data_path,'/Local/retest_worker_counts.json'))
-
-worker_counts = as.data.frame(unlist(worker_counts))
-names(worker_counts) = "task_count"
-
-disc_comp_date = read.csv(paste0(retest_data_path,'Local/discovery_completion_dates.csv'), header=FALSE)
-val_comp_date = read.csv(paste0(retest_data_path,'Local/validation_completion_dates.csv'), header=FALSE)
-test_comp_date = rbind(disc_comp_date, val_comp_date)
-rm(disc_comp_date, val_comp_date)
-retest_comp_date = read.csv(paste0(retest_data_path,'Local/retest_completion_dates.csv'), header=FALSE)
-comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
-names(comp_dates) <- c("sub_id", "retest_comp", "test_comp")
-comp_dates$retest_comp = as.Date(comp_dates$retest_comp)
-comp_dates$test_comp = as.Date(comp_dates$test_comp)
-comp_dates$days_btw = with(comp_dates, retest_comp-test_comp)
-
-rm(test_comp_date, retest_comp_date, comp_dates)
-
-### Completion time data
-
-retest_task_comp_times = read.csv(paste0(retest_data_path, 'Local/retest_task_completion_times.csv'))
-test_task_comp_times = read.csv(paste0(retest_data_path, 'Local/test_task_completion_times.csv'))
[…]

### 2018-10-15 code/figure_scripts/Lit_Review_Plot.R

@@ -1,3 +1,9 @@
+source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/figure_scripts/figure_res_wrapper.R')
+
+source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/lit_review_data.R')
+
+source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/g_legend.R')
+
 p1_legend = lit_review %>%
   filter(task == 'task') %>%
   ggplot(aes(y = var, x = retest_reliability)) +
@@ -52,8 +58,6 @@ p3 <- arrangeGrob(arrangeGrob(p1 +theme(legend.position="none"),
                               nrow=1),
                   mylegend, nrow=2,heights=c(10, 1))
 
-source('figure_res_wrapper')
-
-ggsave('Lit_Review_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 20, units = "in", dpi=100)
+ggsave('Lit_Review_Plot.jpg', plot = p3, device = out_device, path = fig_path, width = 24, height = 20, units = "in", dpi=img_dpi)
 
 rm(p1, p2, p3, p1_legend, mylegend)

### 2018-10-15 code/figure_scripts/figure_res_wrapper.R

@@ -1,5 +1,14 @@
+library(tidyr)
+
 img_dpi <- as.numeric(readline(prompt="Enter img dpi: "))
+img_dpi = ifelse(is.na(img_dpi), 100, img_dpi)
+
+default_fig_path <- readline(prompt="Enter default fig path: ")
+default_fig_path = ifelse(length(default_fig_path)==1, '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures', default_fig_path)
+
+out_device <- readline(prompt="Enter image filetype: ")
+out_device = ifelse(length(out_device)==1, 'jpeg', out_device)
 
 high_res = ifelse(img_dpi>100, T, F)
 
-fig_path = ifelse(high_res, )
+fig_path = ifelse(high_res, paste0(default_fig_path, "/high_res"), default_fig_path)

### 2018-10-15 code/workspace_scripts/SRO_Retest_Analyses_Helper_Functions.R

@@ -7,7 +7,6 @@ library(psych)
 library(stringr)
 library(plotly)
 library(DT)
-library(sjPlot)
 library(RecordLinkage)
 library(MCMCglmm)
 
@@ -17,7 +16,7 @@ render_this <- function(){rmarkdown::render('/Users/zeynepenkavi/Dropbox/Poldrac
 
 options(scipen = 1, digits = 4)
 
-helper_func_path = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Helper_Functions/'
+helper_func_path = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/'
 
 source(paste0(helper_func_path, 'g_legend.R'))
 source(paste0(helper_func_path, 'g_caption.R'))

### 2018-10-15 code/workspace_scripts/SRO_Retest_Analyses_Workspace.R

@@ -1,0 +1,32 @@
+# Load data
+
+library(tidyverse)
+library(jsonlite)
+
+workspace_scripts = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/'
+
+source(paste0(workspace_scripts,'SRO_Retest_Analyses_Helper_Functions.R'))
+
+test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_03-29-2018/'
+
+retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-29-2018/'
+
+source(paste0(workspace_scripts, 'battery_completion_data.R'))
+
+source(paste0(workspace_scripts,'lit_review_data.R'))
+
+source(paste0(workspace_scripts,'subject_data.R'))
+
+source(paste0(workspace_scripts,'intratrial_rel_data.R'))
+
+source(paste0(workspace_scripts,'demog_data.R'))
+
+source(paste0(workspace_scripts,'boot_rel_data.R'))
+
+source(paste0(workspace_scripts,'duplicate_items_data.R'))
+
+source(paste0(workspace_scripts,'measure_labels_data.R'))
+
+source(paste0(workspace_scripts,'meaningful_vars_data.R'))
+
+source(paste0(workspace_scripts,'bayesian_models_data.R'))

### 2018-10-15 code/workspace_scripts/battery_completion_data.R

@@ -1,0 +1,40 @@
+#########################
+## Battery completion data ####
+#########################
+
+workers = read.csv(paste0(retest_data_path,'Local/User_717570_workers.csv'))
+workers = workers %>%
+  group_by(Worker.ID) %>%
+  mutate(Retest_worker=ifelse(sum(CURRENT.RetestWorker,CURRENT.RetestWorkerB2,CURRENT.RetestWorkerB3,CURRENT.RetestWorkerB4,CURRENT.RetestWorkerB5,na.rm=T)>0,1,0)) %>%
+  ungroup()
+
+worker_counts <- fromJSON(paste0(retest_data_path,'/Local/retest_worker_counts.json'))
+
+worker_counts = as.data.frame(unlist(worker_counts))
+names(worker_counts) = "task_count"
+
+disc_comp_date = read.csv(paste0(retest_data_path,'Local/discovery_completion_dates.csv'), header=FALSE)
+val_comp_date = read.csv(paste0(retest_data_path,'Local/validation_completion_dates.csv'), header=FALSE)
+test_comp_date = rbind(disc_comp_date, val_comp_date)
+rm(disc_comp_date, val_comp_date)
+retest_comp_date = read.csv(paste0(retest_data_path,'Local/retest_completion_dates.csv'), header=FALSE)
+comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
+names(comp_dates) <- c("sub_id", "retest_comp", "test_comp")
+comp_dates$retest_comp = as.Date(comp_dates$retest_comp)
+comp_dates$test_comp = as.Date(comp_dates$test_comp)
+comp_dates$days_btw = with(comp_dates, retest_comp-test_comp)
+
+rm(test_comp_date, retest_comp_date, comp_dates)
+
+### Completion time data
+
+retest_task_comp_times = read.csv(paste0(retest_data_path, 'Local/retest_task_completion_times.csv'))
+test_task_comp_times = read.csv(paste0(retest_data_path, 'Local/test_task_completion_times.csv'))
+task_comp_times = merge(retest_task_comp_times, test_task_comp_times, by=c('worker_id','task'))
+rm(retest_task_comp_times, test_task_comp_times)
+task_comp_times = task_comp_times %>%
+  select(-X.x, -X.y) %>%
+  mutate(finish_day.x = as.Date(finish_day.x),
+         finish_day.y = as.Date(finish_day.y),
+         days_btw = finish_day.x-finish_day.y) %>%
+  rename(sub_id=worker_id)

### 2018-10-15 code/workspace_scripts/demog_data.R

@@ -1,0 +1,12 @@
+#########################
+## Demographics data ####
+#########################
+
+test_demog <- read.csv(paste0(retest_data_path, '/t1_data/demographic_health.csv'))
+
+retest_demog <- read.csv(paste0(retest_data_path, 'demographic_health.csv'))
+
+retest_demog = retest_demog[retest_demog$X %in% test_demog$X,]
+
+names(test_demog)[which(names(test_demog) == 'X')] <-'sub_id'
+names(retest_demog)[which(names(retest_demog) == 'X')] <-'sub_id'

### 2018-10-15 code/workspace_scripts/duplicate_items_data.R

@@ -1,0 +1,26 @@
+#########################
+## Duplicate items ####
+#########################
+
+tmp = read.csv(gzfile(paste0(retest_data_path, 'items.csv.gz')))
+tmp = tmp %>%
+  filter(worker == 's005') %>%
+  select(item_ID, item_text) %>%
+  mutate(item_text = trimws(as.character(item_text))) %>%
+  unite(item, c("item_ID", "item_text"), sep = "___")
+
+comb = as.data.frame(t(combn(unique(tmp$item),2)))
+
+duplicate_items = comb %>%
+  filter(grepl('dospert', V1)==FALSE) %>%
+  filter(grepl('selection_optimization', V1)==FALSE) %>%
+  filter(grepl('sensation_seeking', V1)==FALSE) %>%
+  separate(V1, c("item1_ID", "item1_text"), sep="___") %>%
+  separate(V2, c("item2_ID", "item2_text"), sep="___") %>%
+  mutate(similarity = levenshteinSim(item1_text, item2_text)) %>%
+  filter(similarity>0.8) %>%
+  select(similarity, item1_ID, item2_ID, item1_text, item2_text) %>%
+  arrange(-similarity)
+
+duplicate_items_data_t1 = read.csv(paste0(test_data_path, 'subject_x_items.csv'))
+duplicate_items_data_t2 = read.csv(paste0(retest_data_path, 'subject_x_items.csv'))

### 2018-10-15 code/workspace_scripts/intratrial_rel_data.R

@@ -1,0 +1,8 @@
+#########################
+## Intratrial reliability data ####
+#########################
+
+# t1_dvs = read.csv(paste0(retest_data_path, 't1_shift_dvs.csv'))
+# t2_dvs = read.csv(paste0(retest_data_path, 't2_shift_dvs.csv'))
+
+trial_num_rel_df = read.csv(paste0(retest_data_path, 'trial_num_rel_df_shift.csv'))

### 2018-10-15 code/workspace_scripts/lit_review_data.R

@@ -1,0 +1,19 @@
+#########################
+## Literature review data ####
+#########################
+
+lit_review <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/lit_review_figure.csv')
+
+lit_review = lit_review %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)]),
+         type = as.character(type)) %>%
+  mutate(task_group = gsub("_", " ", task_group),
+         var = gsub("_", " ", var)) %>%
+  arrange(task_group, raw_fit, var) %>%
+  mutate(task_group = gsub("survey", "", task_group),
+         task_group = gsub("task", "", task_group),
+         task_group = str_to_title(task_group)) %>%
+  mutate(task_group = ifelse(task_group == "Psychological Refractory Period Two Choices", "Psychological Refractory Period", ifelse(task_group == "Angling Risk Always Sunny", "Angling Risk", ifelse(task_group == "Two Stage", "Two Step", ifelse(task_group == "Threebytwo", "Task Switching", ifelse(task_group == "Adaptive N Back", "Adaptive N-back", ifelse(task_group == "Go Nogo", "Go/No-go",  ifelse(task_group == "Ravens", "Raven's", task_group)))))))) %>%
+  mutate(task_group = ifelse(task_group == "Bis Bas ", "BIS-BAS", ifelse(task_group == "Bis11 ", "BIS-11", ifelse(task_group == "Dospert Eb ", "DOSPERT EB", ifelse(task_group == "Dospert Rp ", "DOSPOERT RP", ifelse(task_group == "Dospert Rt ", "DOSPERT RT", ifelse(task_group == "Erq ", "ERQ", ifelse(task_group == "Upps Impulsivity ", "UPPS-P", task_group))))))))  %>%
+  select(-measure_description)

### 2018-10-15 code/workspace_scripts/meaningful_vars_data.R

@@ -1,0 +1,6 @@
+#########################
+## Meaningful variables ####
+#########################
+
+meaningful_vars = read.table('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/meaningful_vars.txt')
+meaningful_vars = as.character(meaningful_vars$V1)

### 2018-10-15 code/workspace_scripts/measure_labels_data.R

@@ -1,0 +1,9 @@
+#########################
+## Measure labels ####
+#########################
+
+measure_labels <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/measure_labels.csv')
+measure_labels = measure_labels %>% select(-measure_description)
+# Check if there are any missing variables
+# retest_report_vars[(retest_report_vars %in% measure_labels$dv == FALSE)]
+# measure_labels$dv[(measure_labels$dv %in% retest_report_vars == FALSE)]

### 2018-10-15 code/workspace_scripts/subject_data.R

@@ -1,0 +1,53 @@
+#########################
+## Subject data ####
+#########################
+
+#Get variables of interest from Ian's release
+tmp1 <- read.csv(paste0(test_data_path,'meaningful_variables.csv'))
+tmp2 <- read.csv(paste0(test_data_path,'meaningful_variables_noDDM.csv'))
+tmp3 <- read.csv(paste0(test_data_path,'meaningful_variables_EZ.csv'))
+retest_report_vars = c(names(tmp1), names(tmp2), names(tmp3))
+retest_report_vars = unique(retest_report_vars)
+lit_rev_vars = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% retest_report_vars == FALSE)])
+retest_report_vars = c(retest_report_vars, lit_rev_vars)
+rm(tmp1, tmp2, tmp3, lit_rev_vars)
+
+
+### Load time 1 data
+
+test_data <- read.csv(paste0(retest_data_path,'t1_data/variables_exhaustive.csv'))
+
+test_data <- test_data[,names(test_data) %in% retest_report_vars]
+
+test_data$X <- as.character(test_data$X)
+names(test_data)[which(names(test_data) == 'X')] <-'sub_id'
+
+### Load time 2 data
+
+retest_data <- read.csv(paste0(retest_data_path,'variables_exhaustive.csv'))
+
+retest_data <- retest_data[,names(retest_data) %in% retest_report_vars]
+
+retest_data$X <- as.character(retest_data$X)
+names(retest_data)[which(names(retest_data) == 'X')] <-'sub_id'
+retest_data = retest_data[retest_data$sub_id %in% test_data$sub_id,]
+
+### Replace HDDM parameters in t1 data
+
+# Since HDDM parameters depend on the sample on which they are fit we refit the model on t1 data for the subjects that have t2 data. Here we replace the HDDM parameters in the current t1 dataset with these refitted values.
+
+hddm_refits <- read.csv(paste0(retest_data_path,'t1_data/hddm_refits_exhaustive.csv'))
+
+hddm_refits = hddm_refits[,names(hddm_refits) %in% retest_report_vars]
+
+hddm_refits$X <- as.character(hddm_refits$X)
+names(hddm_refits)[which(names(hddm_refits) == 'X')] <-'sub_id'
+
+#drop hddm columns from test_data
[…]

### 2018-10-15 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 
-Measure level plot
-
-```{r warning=FALSE, message=FALSE}
-lit_review = lit_review %>%
-  select(-reference)
-```
-
-```{r warning= FALSE, message =FALSE, echo=FALSE}
-
-```
-
 ```{r echo=FALSE, out.width='100%'}
-knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Lit_Review_Plot.jpg')
-```
-
-Because this plot is difficult to digest we summarize it on a task level to give a general sense of the main takeaways. This plot naturally disregards much of the fine grained information.
-
-```{r}
-p1_t_legend <- lit_review %>%
-  filter(task == 'task') %>%
-ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) +
-  geom_point(aes(size=sample_size, shape = type), color='black')+
-  theme(axis.text.y = element_text(size=30),
-        legend.position = 'bottom',
-        axis.text.x = element_text(size=20),
-        axis.title.x = element_text(size=20),
-        legend.text = element_text(size=16),
-        legend.key.width = unit(0.75, "inches"),
-        legend.title = element_text(size=20),
-        legend.spacing.x = unit(0.5, "inches"),
-        legend.box = "vertical",
-        legend.direction = "horizontal",
-        plot.caption = element_text(family = "Times", size = 40, lineheight = 2, hjust = 0)) +
-  xlab("Retest Reliability")+
-  ylab("")+
-  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
-  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
-  scale_shape_manual(breaks = sort(unique(lit_review$type)), values = c(17, 3, 16, 15), name="Type")+
-  scale_size_continuous(name = "Sample Size",
-                        limits = c(10, 1200),
-                        range = c(1, 40),
-                        breaks = c(10, 100, 1000))+
-  guides(#size = guide_legend(override.aes = list(breaks = c(10, 100, 1000)), labels = c(10, 100, 1000)),
-         shape = guide_legend(override.aes = list(size = 16)))+
-  geom_vline(xintercept = 0, color = "red", size = 1)+
-  labs(caption = str_wrap("FIGURE 1: Summary of the literature review for tasks (left) and surveys (right).
-Each point represents a study containing test-retest reliability data on an unspecified dependent measure for a given task.
-The size of the point depends on the sample size of the study and the shape depends on the metric that was used to estimate reliability.
-Each vertical red line indicates 0 reliability.", width = 120))
-
-p1_t <- lit_review %>%
-  filter(task == 'task') %>%
-ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) +
-  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
-  theme(axis.text.y = element_text(size=30),
-        legend.position = 'none',
-        axis.text.x = element_text(size=23),
-        axis.title.x = element_text(size=30)) +
-  xlab("Retest Reliability")+
-  ylab("")+
-  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
-  scale_y_discrete(labels = function(x) str_wrap(x, width = 15))+
-  scale_shape_manual(breaks = sort(unique(lit_review$type)), values = c(17, 3, 16, 15))+
-  scale_size_continuous(range = c(1, 40),
-                        limits = c(10,1200))+
-  geom_vline(xintercept = 0, color = "red", size = 1)
-
-p2_t <- lit_review %>%
-  filter(task == 'survey') %>%
-ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) +
-  geom_point(aes(size=sample_size, shape = type), color='#F8766D')+
-  theme(axis.text.y = element_text(size=30),
-        legend.position = 'none',
-        axis.text.x = element_text(size=23),
-        axis.title.x = element_text(size=30)) +
-  xlab("Retest Reliability")+
-  ylab("")+
-  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
-  scale_y_discrete(labels = function(x) str_wrap(x, width = 15))+
-  scale_shape_manual(breaks = c("ICC","Pearson","Spearman"),
-                     values = c(17, 16, 15))+
-  scale_size_continuous(range = c(1, 40),
-                        limits = c(10,1200))+
-  geom_vline(xintercept = 0, color = "red", size = 1)
-
-mylegend<-g_legend(p1_t_legend)
-mycaption<-g_caption(p1_t_legend)
-
-p3_t <- arrangeGrob(arrangeGrob(p1_t, p2_t, nrow=1), mylegend, mycaption, nrow=3, heights=c(10, 1, 1.5))
-
-ggsave('Lit_Review_Plot_t.tiff', plot = p3_t, device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 27, height = 52, units = "in", limitsize = FALSE, dpi = 250)
-```
-
-```{r}
-rm(p1_t, p2_t, p3_t, mylegend, p1_t_legend)
-```
-
-```{r echo=FALSE, out.width='100%'}
-knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Lit_Review_Plot_t.jpg')
-```
-
-An interactive version of this plot could be find [here](https://zenkavi.github.io/SRO_Retest_Analyses/output/reports/Lit_Review_Figure.html)
+fig_name = 'Lit_Review_Plot_t.jpeg'
+
+knitr::include_graphics(paste0(fig_path, fig_name))
+```
+
+An interactive version of this plot could be find [here](https://zenkavi.github.io/SRO_Retest_Analyses/output/reports/Interactive_Figures.html)
 
@@
 
-Are there differences between clinical and non-clinical samples in the literature?
-
-```{r}
-tmp = lit_review %>%
-  mutate(clinical = as.character(clinical),
-         clinical = ifelse(clinical == "", "control", clinical),
-         clinical_1_0 = ifelse(clinical == "control", 0, 1))
-table(tmp$clinical)
-table(tmp$clinical_1_0)
-summary(lmer(retest_reliability ~ clinical_1_0+(1|dv),data=tmp))
-```
-
 ## Data quality checks
@@
 ```{r}
-tmp = demog_boot_df %>%
+demog_boot_df %>%
   group_by(dv) %>%
@@
   arrange(-median_icc)
-tmp
-```
-
-```{r}
-sjt.df(tmp%>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/demog_rel_table.doc")
 ```
@@
 ```{r}
-numeric_cols = c()
-
-for(i in 1:length(names(test_demog))){
-  if(is.numeric(test_demog[,i])){
-    numeric_cols <- c(numeric_cols, names(test_demog)[i])
-  }
-}
-
-demog_rel_df <- data.frame(icc = rep(NA, length(numeric_cols)))
-
-row.names(demog_rel_df) <- numeric_cols
-
-for(i in 1:length(numeric_cols)){
-  demog_rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i], t1_df = test_demog, t2_df = retest_demog)
-}
-
-demog_rel_df = demog_rel_df %>%
-  mutate(var = row.names(.)) %>%
-  select(var, icc) %>%
+demog_rel_df = make_rel_df(test_demog, t2_df = retest_demog, metrics=c('icc'))
+
+demog_rel_df %>%
+  select(dv, icc) %>%
   arrange(-icc)
-```
-
-Checking low reliability demog vars: Mostly NA's
-
-```{r}
-test_demog$HowOftenHazardousCannabis
-retest_demog$HowOftenHazardousCannabis
-
-test_demog$CaffieneOtherSourcesDayMG
-retest_demog$CaffieneOtherSourcesDayMG
-
-test_demog$SpouseParentsComplainDrugUse
-retest_demog$SpouseParentsComplainDrugUse
-
-test_demog$OtherDebtAmount
-retest_demog$OtherDebtAmount
 ```

### 2018-10-15 code/figure_scripts/Lit_Review_Plot.R

@@ -1,9 +1,12 @@
 source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/figure_scripts/figure_res_wrapper.R')
 
-source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/lit_review_data.R')
+if(!exists('lit_review')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/lit_review_data.R')
+}
 
-source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/g_legend.R')
-
+if(!exists('g_legend')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/g_legend.R')
+}
 p1_legend = lit_review %>%
   filter(task == 'task') %>%
   ggplot(aes(y = var, x = retest_reliability)) +
@@ -58,6 +61,6 @@ p3 <- arrangeGrob(arrangeGrob(p1 +theme(legend.position="none"),
                               nrow=1),
                   mylegend, nrow=2,heights=c(10, 1))
 
-ggsave('Lit_Review_Plot.jpg', plot = p3, device = out_device, path = fig_path, width = 24, height = 20, units = "in", dpi=img_dpi)
+ggsave(paste0('Lit_Review_Plot_t.',out_device), plot = p3, device = out_device, path = fig_path, width = 24, height = 20, units = "in", dpi=img_dpi)
 
 rm(p1, p2, p3, p1_legend, mylegend)

### 2018-10-15 code/figure_scripts/Lit_Review_Plot_t.R

@@ -1,0 +1,86 @@
+source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/figure_scripts/figure_res_wrapper.R')
+
+if(!exists('lit_review')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/lit_review_data.R')
+}
+
+if(!exists('g_legend')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/g_legend.R')
+}
+
+if(!exists('g_caption')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/g_caption.R')
+}
+
+p1_t_legend <- lit_review %>%
+  filter(task == 'task') %>%
+  ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) +
+  geom_point(aes(size=sample_size, shape = type), color='black')+
+  theme(axis.text.y = element_text(size=30),
+        legend.position = 'bottom',
+        axis.text.x = element_text(size=20),
+        axis.title.x = element_text(size=20),
+        legend.text = element_text(size=16),
+        legend.key.width = unit(0.75, "inches"),
+        legend.title = element_text(size=20),
+        legend.spacing.x = unit(0.5, "inches"),
+        legend.box = "vertical",
+        legend.direction = "horizontal",
+        plot.caption = element_text(family = "Times", size = 40, lineheight = 2, hjust = 0)) +
+  xlab("Retest Reliability")+
+  ylab("")+
+  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
+  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
+  scale_shape_manual(breaks = sort(unique(lit_review$type)), values = c(17, 3, 16, 15), name="Type")+
+  scale_size_continuous(name = "Sample Size",
+                        limits = c(10, 1200),
+                        range = c(1, 40),
+                        breaks = c(10, 100, 1000))+
+  guides(#size = guide_legend(override.aes = list(breaks = c(10, 100, 1000)), labels = c(10, 100, 1000)),
+    shape = guide_legend(override.aes = list(size = 16)))+
[…]

### 2018-10-15 code/workspace_scripts/SRO_Retest_Analyses_Helper_Functions.R

@@ -22,6 +22,8 @@ source(paste0(helper_func_path, 'g_legend.R'))
 source(paste0(helper_func_path, 'g_caption.R'))
 source(paste0(helper_func_path, 'sem.R'))
 source(paste0(helper_func_path, 'trim.R'))
+source(paste0(helper_func_path, 'get_numeric_cols.R'))
 source(paste0(helper_func_path, 'match_t1_t2.R'))
 source(paste0(helper_func_path, 'get_retest_stats.R'))
 source(paste0(helper_func_path, 'process_boot_df.R'))
+source(paste0(helper_func_path, 'make_rel_df.R'))

### 2018-10-15 code/workspace_scripts/SRO_Retest_Analyses_Workspace.R

@@ -11,6 +11,8 @@ test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation
 
 retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-29-2018/'
 
+fig_path = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/'
+
 source(paste0(workspace_scripts, 'battery_completion_data.R'))
 
 source(paste0(workspace_scripts,'lit_review_data.R'))

### 2018-10-15 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 demog_rel_df %>%
-  mutate(timed = ifelse(var %in% timed_demogs, 1, 0)) %>%
+  mutate(timed = ifelse(dv %in% timed_demogs, 1, 0)) %>%
   ggplot(aes(icc, fill = factor(timed)))+
@@
   theme(legend.position = "none")
-
-ggsave('DemogRelDist.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 5, units = "in", dpi=500)
 ```
@@
 ```{r echo=FALSE}
-rm(test_demog, retest_demog, demog_rel_df, numeric_cols)
+rm(test_demog, retest_demog, demog_rel_df, timed_demogs)
 ```
@@
 ### Effect of delays between the two measurements
-
-Due to our data collection strategy we did not strictly control for the delay between the two measurements as standard psychometrics studies measuring retest reliability might.
-
-An individual difference measure would preferably remain stable regardless of the delay between multiple measurements.
-
-Since we only had two measurements we could not test directly whether a measure becomes less reliable depending on the delay between the two time points (The average number of days between two measurements would be the same for all measures since reliability is a measure level metric while days between completion a subject level one).
-
-So if you regress the average difference for each measure on average delay between two measurements you are regressing a vector with varying numbers on a vector of same values, like a t test asking if the mean of the varying column, in this case the average difference score, is different than the unique value in the single value column, i.e.
-the average delay between two time points (Note that this should be true in theory but in practice since for each measure there might subjects for whom the dv could not be calculated there might be >1 unique values for the average delay between the two time points).
-This analysis is not meaningful.
 
@@
 
-Make data frame with difference between two scores for each measure for each subject.
+To check this we make data frame with difference between two scores for each measure for each subject.
 Since the scores for different measures are on different scales for comparability the difference scores are normalized (ie demeaned and dividied by the sd of the difference score distribution.) Note that the variance of the difference score distribution accounts for the variance in both time points by summing them.
@@
 
-Here we check if the difference is larger the longer the delay
+Here we check if the difference is larger the longer the delay.
 
 ```{r warning=FALSE}
-numeric_cols = c()
-
-for(i in 1:length(names(test_data))){
-  if(is.numeric(test_data[,i]) & names(test_data)[i] %in% names(retest_data)){
-    numeric_cols <- c(numeric_cols, names(test_data)[i])
-  }
-}
+numeric_cols = get_numeric_cols(test_data)
 
@@
 ```{r echo=FALSE}
-rm(tmp, i)
+rm(tmp, i, numeric_cols)
 ```
@@
   ylab('Scaled difference score')
-
-ggsave('DaysBtwEffect.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
 ```
@@
 
-summary(tmp <- MCMCglmm(abs(difference) ~ scale(days_btw), random = ~us(scale(days_btw)):dv, data=t1_2_difference))
+summary(tmp <- MCMCglmm(abs(difference) ~ scale(days_btw), random = ~us(scale(days_btw)):dv, data=t1_2_difference, verbose=FALSE))
 ```

### 2018-10-15 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 ```{r}
-#summary(lmerTest::lmer(abs(difference) ~ scale(days_btw)+(scale(days_btw) | dv), data=t1_2_difference))
-
-summary(tmp <- MCMCglmm(abs(difference) ~ scale(days_btw), random = ~us(scale(days_btw)):dv, data=t1_2_difference, verbose=FALSE))
+summary(lmerTest::lmer(abs(difference) ~ scale(days_btw)+(scale(days_btw) | dv), data=t1_2_difference))
+
+# summary(tmp <- MCMCglmm(abs(difference) ~ scale(days_btw), random = ~us(scale(days_btw)):dv, data=t1_2_difference, verbose=FALSE))
 ```
@@
 
-# tmp = duplicate_items %>%
-#   select(similarity, t1_t1_polycor, t1_t2_polycor, t2_t2_polycor, t2_t1_polycor) %>%
-#   gather(key, value, -similarity)
-
 tmp %>%
@@
   theme_bw()
-
-ggsave('OverlappingItemSimilarity.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
 ```
@@
 
-```{r}
+```{r eval=FALSE, echo=FALSE}
 summary(MCMCglmm(value ~ key*scale(similarity), data=tmp, nitt = 50000))
-```
-
-Time 1: item 1 - item 2
-Time 1 item 1 - time 2 item 2
-Time 2 item 1 - time 1 item 2
-Time 2: item 1 - item 2
-
-```{r warning=FALSE, message=FALSE}
-tmp = duplicate_items_data_t1 %>%
-  gather(key, value, -worker)
-
-tmp2 = duplicate_items_data_t2 %>%
-  gather(key, value, -worker)
-
-tmp = duplicate_items %>%
-  select(item1_ID, item2_ID) %>%
-  left_join(tmp, by = c("item1_ID" = "key")) %>%
-  left_join(tmp, by = c("item2_ID" = "key", "worker" = "worker")) %>%
-  rename(item1_time1 = value.x, item2_time1 = value.y) %>%
-  left_join(tmp2, by = c("item1_ID" = "key", "worker" = "worker")) %>%
-  left_join(tmp2, by = c("item2_ID" = "key", "worker" = "worker")) %>%
-  rename(item1_time2 = value.x, item2_time2 = value.y) %>%
-  group_by(item1_ID) %>%
-  mutate(item1_time1 = scale(item1_time1),
-         item1_time2 = scale(item1_time2),
-         item2_time1 = scale(item2_time1),
-         item2_time2 = scale(item2_time2),
-         item1_time1 = ifelse(item1_ID == "mpq_control_survey.13", item1_time1*-1, item1_time1),
-         item1_time2 = ifelse(item1_ID == "mpq_control_survey.13", item1_time2*-1, item1_time2)) %>%
-  ungroup()
-
-p1 = tmp %>%
-  ggplot(aes(item1_time1, item2_time1, col=item1_ID))+
-  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
-  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
-  theme(legend.position = "none")+
-  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
-  xlab("Item 1 T1")+
-  ylab("Item 2 T1")
-
-p2 = tmp %>%
-  ggplot(aes(item1_time1, item2_time2, col=item1_ID))+
-  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
-  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
-  theme(legend.position = "none")+
-  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
-  xlab("Item 1 T1")+
-  ylab("Item 2 T2")
-
-p3 = tmp %>%
-  ggplot(aes(item1_time2, item2_time1, col=item1_ID))+
-  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
-  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
-  theme(legend.position = "none")+
-  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
-  xlab("Item 1 T2")+
-  ylab("Item 2 T1")
-
-p4 = tmp %>%
-  ggplot(aes(item1_time2, item2_time2, col=item1_ID))+
-  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
-  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
-  theme(legend.position = "none")+
-  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
-  xlab("Item 1 T2")+
-  ylab("Item 2 T2")
-
-p5 = arrangeGrob(p1, p2, p3, p4, ncol=2)
-
-ggsave('DataCheckOverlappingItems.jpg', p5, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 500)
-
-rm(tmp, tmp2, p1, p2, p3, p4, p5)
 ```
@@
 
-Distribution of reliabilities, sample sizes and delays
+Distribution of reliabilities, sample sizes and delays in the literature
 
@@
         axis.title.y = element_text(size=14))
-
-ggsave('LitReviewSampleSize.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 3, height = 5, units = "in", limitsize = FALSE, dpi = 500)
 ```
@@
 # summary(lm(sample_size ~ task,rel_comp))
-summary(m1 <- MCMCglmm(sample_size ~ task, data=rel_comp))
+summary(m1 <- MCMCglmm(sample_size ~ task, data=rel_comp, verbose=FALSE))
 ```
@@
 #summary(mod2)
-summary(MCMCglmm(retest_reliability ~ task + sample_size, random = ~ dv, data = rel_comp))
+summary(MCMCglmm(retest_reliability ~ task + sample_size, random = ~ dv, data = rel_comp, verbose=FALSE))
 ```
@@
   ylim(-0.15, 1)
-
-ggsave('LitReviewRelBySampleSize.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 500)
 ```
@@
   ylim(-0.4,1)
-
-ggsave('LitTaskVsSurvey.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 3, height = 5, units = "in", limitsize = FALSE, dpi = 500)
 ```
@@
 
-```{r}
+```{r eval=FALSE}
 n_df = rel_comp %>%
@@
 
-#lit_emp_cor_out = plyr::rdply(100, lit_emp_cor)
-
-#write.csv(lit_emp_cor_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/lit_emp_cor_out.csv')
-
+lit_emp_cor_out = plyr::rdply(100, lit_emp_cor)
+
+write.csv(lit_emp_cor_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/lit_emp_cor_out.csv')
+```
+
+```{r echo=FALSE}
 lit_emp_cor_out = read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/lit_emp_cor_out.csv')
@@
 summary(lit_emp_cor_out)
-
 ```
@@
 
-```{r}
+```{r eval=FALSE}
 comp_lit_pred <- function(df){
@@
 comp_lit_pred_out = plyr::rdply(1000, comp_lit_pred(rel_comp))
-```
-
-```{r}
-tmp = comp_lit_pred_out %>%
-  select(-.n, -m_lit, -m_boot) %>%
-  gather(key, value) %>%
-  separate(key, c("stat", "sample"), sep = "_")
-
-# tmp$stat = as.factor(tmp$stat)
-# levels(tmp$stat) <- c("coefficient", expression(r^"2"))
-
-tmp %>%  
-  ggplot(aes(value, fill=sample))+
-  geom_density(alpha = 0.5, position='identity', color=NA)+
-  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
-  scale_fill_manual(breaks=c("boot","lit"),
-                       labels=c("Empirical", "Literature"),
-                      name="Predictor",
-                      values = c("gray15", "gray75"))+
-  xlab('Proportion of Variance in Literature Explained')+
-  ylab('Density')+
-  xlim(0,1)+
-  ylim(0,40)+
-  theme(#axis.title.x  = element_text(size=12),
-        #axis.text.x  = element_text(size=12),
-        #axis.text.y  = element_text(size=12),
-        #axis.title.y  = element_text(size=12),
-        #legend.title  = element_text(size=12),
-        #legend.text  = element_text(size=12),
-        legend.position = "bottom",
-        plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0))+
-  labs(caption = str_wrap("FIGURE 3: Noise ceiling for comparing empirical retest reliability estimates to reliability estimates from the literature.
-Data come from sampling a single reliability estimate from the literature and using that as a predictor of the remaining retest reliability estimates from the literature versus using the mean estimate from our empirical results as a predictor.
-Models account for the effect of sample size in the literature and whether the measure is a task or survey variables.
-The literature samples are significantly better at predicting the rest of the literature than our empirical averages, but the distributions of variance explained across samples are highly overlapping.
-", width = 120))
-
-ggsave('LitAndBoot_Noise_Ceiling.tiff', device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 7, height = 5, units = "in", limitsize = FALSE, dpi = 300)
+
+write.csv(comp_lit_pred_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/comp_lit_pred_out.csv')
+```
+
+```{r echo=FALSE}
+comp_lit_pred_out = read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/comp_lit_pred_out.csv')
+```
+
+```{r echo=FALSE, out.width='100%'}
+fig_name = 'LitAndBoot_Noise_Ceiling.jpeg'
+
+knitr::include_graphics(paste0(fig_path, fig_name))
 ```

### 2018-10-15 code/figure_scripts/LitAndBoot_Noise_Ceiling.R

@@ -1,0 +1,43 @@
+source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/figure_scripts/figure_res_wrapper.R')
+
+if(!exists('g_legend')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/g_legend.R')
+}
+
+if(!exists('g_caption')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/g_caption.R')
+}
+
+comp_lit_pred_out = read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/comp_lit_pred_out.csv')
+
+tmp = comp_lit_pred_out %>%
+  select(-.n, -m_lit, -m_boot, -X) %>%
+  gather(key, value) %>%
+  separate(key, c("stat", "sample"), sep = "_")
+
+# tmp$stat = as.factor(tmp$stat)
+# levels(tmp$stat) <- c("coefficient", expression(r^"2"))
+
+tmp %>%  
+  ggplot(aes(value, fill=sample))+
+  geom_density(alpha = 0.5, position='identity', color=NA)+
+  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
+  scale_fill_manual(breaks=c("boot","lit"),
+                    labels=c("Empirical", "Literature"),
+                    name="Predictor",
+                    values = c("gray15", "gray75"))+
+  xlab('Proportion of Variance in Literature Explained')+
+  ylab('Density')+
+  xlim(0,1)+
+  ylim(0,40)+
+  theme(#axis.title.x  = element_text(size=12),
+    #axis.text.x  = element_text(size=12),
+    #axis.text.y  = element_text(size=12),
+    #axis.title.y  = element_text(size=12),
+    #legend.title  = element_text(size=12),
+    #legend.text  = element_text(size=12),
+    legend.position = "bottom",
+    plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0))+
[…]

### 2018-10-16 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 
-summary(MCMCglmm(value ~ key, data = tmp))
-```
-
-Are you at noise ceiling for suveys vs. tasks? Are you better in estimating the literature using our data for surveys vs tasks?
-
-```{r}
-comp_lit_pred_out_task = plyr::rdply(1000, comp_lit_pred(rel_comp %>% filter(task=="task")))
-comp_lit_pred_out_task$task = "task"
-comp_lit_pred_out_survey = plyr::rdply(1000, comp_lit_pred(rel_comp %>% filter(task=="survey")))
-comp_lit_pred_out_survey$task = "survey"
-comp_lit_pred_out_both = rbind(comp_lit_pred_out_task, comp_lit_pred_out_survey)
-
-comp_lit_pred_out_both %>%
-  select(-.n, -m_lit, -m_boot) %>%
-  gather(key, value, -task) %>%
-  separate(key, c("stat", "sample"), sep = "_") %>%
-  ggplot(aes(value, fill=sample, alpha=task, color=task))+
-  geom_density(position='identity', size=2)+
-  # facet_grid(~task)+
-  scale_fill_manual(breaks=c("boot","lit"),
-                       labels=c("Empirical", "Literature"),
-                      name="Predictor",
-                      values = c("purple", "orange"))+
-  scale_alpha_manual(breaks=c("survey", "task"),
-                     values = c(0.4, 0.7),
-                     name="Measure type")+
-  scale_color_discrete(name="Measure type")+
-  xlab('Variance Explained')+
-  ylab('Density')
-```
-
-Are the differences in the distributions significant?
-There is a significant interaction, such that:
-
-```{r}
-tmp = comp_lit_pred_out_both %>%
-  select(-.n, -m_lit, -m_boot) %>%
-  gather(key, value, -task)
-
-summary(lm(value ~ key*task, tmp))
-```
-
-The literature does a better job in predicting itself for tasks compared to surveys (comparing the two orange distributions).
-
-```{r}
-with(comp_lit_pred_out_both, t.test(r2_lit ~ task))
-```
-
-Our data is better in predicting the literature estimates for the surveys than it is in predicting tasks (comparing the difference between orange and purple for red and blue outlines).
-
-```{r}
-with(comp_lit_pred_out_both, t.test(r2_lit-r2_boot ~ task))
-```
-
-Why are the reliability estimates from surveys worse compared to tasks in predicting the literature?
+summary(MCMCglmm(value ~ key, data = tmp, verbose=F))
+```
+
+We checked if survey and task measures differed in how close our results were to the literature (i.e.
+Are you better in estimating the literature using our data for surveys vs tasks?).
+We found an interaction, such that: The literature does a better job in predicting itself for tasks compared to surveys.
+On the other hand, our data is better in predicting the literature estimates for the surveys than it is in predicting tasks.
+
+One might wonder: Why are the reliability estimates from surveys worse compared to tasks in predicting the literature?
 Because they are less variable.
@@
 
-Rank by variance: empirical estimates for surveys < literature estimates for surveys < empirical estimates for tasks < literature estimates for tasks
-
-```{r}
-rel_comp %>%
-  select(task, retest_reliability, mean_pearson) %>%
-  gather(key, value, -task) %>%
-  group_by(key, task) %>%
-  summarise(variance = var(value)) %>%
-  ungroup()%>%
-  mutate(key = ifelse(key == "mean_pearson", "emp", "lit")) %>%
-  arrange(variance)
-```
-
-### LOOCV predicting lit vs our data
-
-What does it look like if you estimate the left one out using the remaining ones for the noise ceiling model?
-Sample one row of literature, fit model of sample size+task on remaining data, use that model to predict the reliability estimates, compare those to the left out reliability estimate from the literature versus the average reliability estimate from our data
-
-```{r}
-pred_sample <- function(df){
-
-  get_sample_row <- function(df){
-    if(nrow(df)>1){
-      row_num = sample(1:nrow(df),1)
-      sample_row = df[row_num,]
-    }
-    else{
-      sample_row = df
-    }
-    return(sample_row)
-  }
-
-  test_df = df %>%
-    group_by(dv) %>%
-    do(get_sample_row(.))
-
-  train_df = anti_join(df, test_df)
-
-  if(length(unique(train_df$task))>1){
-    mod = lm(retest_reliability ~ scale(sample_size)+task, data=train_df)
-  }
-  else{
-    mod = lm(retest_reliability ~ scale(sample_size), data=train_df)
-  }
-
-  test_df$pred = predict(mod, test_df)
-
-  # out = data.frame(res_lit = sum(test_df$retest_reliability - pred)^2,
-  #                  res_boot = sum(test_df$mean_pearson - pred)^2)
-
-  return(test_df)
-}
-```
-
-Why did I have to run it separately for the function before but can run it on all data once here? Before the output was model fits for all measures. Here the output is measure level prediction.
-
-```{r message=FALSE}
-pred_sample_out = plyr::rdply(1000, pred_sample(rel_comp))
-```
-
-Plot difference between prediction and value of either the lit estimate or the average estimate from our data
-
-```{r}
-tmp = pred_sample_out %>%
-  select(task,pred, retest_reliability, mean_pearson) %>%
-  gather(key, value, -task, -pred) %>%
-  mutate(sq_diff = (pred - value)^2)
-
-tmp%>%  
-  ggplot(aes(sq_diff, fill=key))+
-  geom_density(position = "identity", color=NA, alpha=0.5)+
-  scale_fill_manual(breaks=c("mean_pearson","retest_reliability"),
-                       labels=c("Empirical", "Literature"),
-                      name="Predicting",
-                      values = c("purple", "orange"))
-```
-
-Are the means of these distributions different?
-Yes: the difference is larger when predicting the left-out value from our data versus predicting left out value from literature.
-The difference seems pretty small though.
-
-```{r}
-with(tmp, t.test(sq_diff ~ key))
-```
-
-Plot difference between prediction and value broken down by measure type.
-
-```{r}
-tmp%>%
-  ggplot(aes(sq_diff, fill=key, color=task, alpha=task))+
-  geom_density(position = "identity", size=2)+
-  scale_fill_manual(breaks=c("mean_pearson","retest_reliability"),
-                       labels=c("Empirical", "Literature"),
-                      name="Predicting",
-                      values = c("purple", "orange"))+
-  scale_alpha_manual(breaks=c("survey", "task"),
-                     values = c(0.4, 0.7),
-                     name="Measure type")+
-  scale_color_discrete(name="Measure type")
-```
-
-Can we capture this interaction in a single model?
-Yes.
-The significant interaction suggests that the squared difference is larger for predicting the literature compared to predicting our data for surveys while for tasks the squared difference is larger when predicting our data compared to predicting the literature.
-(This fits with other results too: our results differ from the literature more for the survey measures)
-
-```{r}
-aggregate(sq_diff ~ key*task,tmp, FUN=mean)
-```
-
-```{r}
-summary(lm(sq_diff ~ key*task,tmp))
-```
-
-Data versus model prediction plot: The predictions are not veriable so they don't really capture the variability neither in the literature nor in our data very well.
-
-```{r}
-tmp %>%
-  ggplot(aes(value, pred, color=task))+
-  geom_point()+
-  facet_wrap(~key)
-```
-
-Distributions of sum squared residual: Residuals are larger for tasks compared to surveys (i.e.
-predictions are worse when predicting task variables - possibly because their variability is higher?).
-For surveys the predictions of the literature are better than predictions of our data while the opposite is true for task measures.
-
-Does this make sense with the results above? Figure out how to think of the noise ceiling analyses and LOOCV results together.
-
-```{r}
-pred_sample_out %>%
-  mutate(sq_diff_lit = (pred - retest_reliability)^2,
-         sq_diff_emp = (pred - mean_icc)^2) %>%
-  group_by(.n, task) %>%
-  summarise(sum_sq_diff_lit = sum(sq_diff_lit),
-            sum_sq_diff_emp = sum(sq_diff_emp)) %>%
-  # select(-'.n') %>%
-  gather(key, value, -task, -.n) %>%
-  ggplot(aes(value, fill=key, color=task, alpha=task))+
-  geom_density(size=1)+
-  scale_fill_manual(breaks=c("sum_sq_diff_emp","sum_sq_diff_lit"),
-                       labels=c("Empirical", "Literature"),
-                      name="Predicting",
-                      values = c("purple", "orange"))+
-  scale_alpha_manual(breaks=c("survey", "task"),
-                     values = c(0.4, 0.7),
-                     name="Measure type")+
-  scale_color_discrete(name="Measure type")
-```
+We also conducted LOOCV on this data and checked what it looked like if we estimate the left one out using the remaining ones for the noise ceiling model? The procedure followed these steps:
+- Sample one row of literature,   
+- fit model of sample size+task on remaining data,   
+- use that model to predict the reliability estimates,   
+- compare those to the left out reliability estimate from the literature versus the average reliability estimate from our data
+
+We found that the (squared) difference is slightly larger when predicting the left-out value from our data versus predicting left out value from literature.
+The squared differences were larger for predicting the literature compared to predicting our data for surveys while for tasks the squared differences were larger when predicting our data compared to predicting the literature.
+(This fits with other results too: our results differ from the literature more for the survey measures).
+
+We do not present these results in further detail as they yield only converging evidence as the analyses above.
 
@@
 
-```{r warning=FALSE, message=FALSE}
-p1 = rel_comp %>%
-  filter(task == 'task') %>%
-ggplot(aes(x = var, y = retest_reliability)) +
-  geom_boxplot(fill='#00BFC4', position="identity")+
-  geom_point(aes(x = var, y = mean_pearson),color="purple", fill="purple", size=3, shape=23)+
-  coord_flip()+
-  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
-  theme(panel.spacing = unit(0.5, "lines"),
-        strip.placement = "outside",
-        strip.text.y = element_text(angle=180),
-        panel.background = element_rect(fill = NA),
-        panel.grid.major = element_line(colour = "grey80"),
-        legend.position = 'bottom') +
-  xlab("")+
-  ylab("")+
-  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))
-
-p2 = rel_comp %>%
-  filter(task == 'survey') %>%
-ggplot(aes(x = var, y = retest_reliability)) +
-  geom_boxplot(fill='#F8766D', position="identity")+
-  geom_point(aes(x = var, y = mean_pearson),color="purple", fill="purple", size=3, shape=23)+
-  coord_flip()+
-  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
-  theme(panel.spacing = unit(0.5, "lines"),
-        strip.placement = "outside",
-        strip.text.y = element_text(angle=180),
-        panel.background = element_rect(fill = NA),
-        panel.grid.major = element_line(colour = "grey80"),
-        legend.position = 'bottom') +
-  xlab("")+
-  ylab("")+
-  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))
-
-p3 <- arrangeGrob(p1, p2,nrow=1)
-
-ggsave('LitVsEmp_Measure_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 20, units = "in", dpi=100)
-rm(p1, p2, p3)
-```
-
 ```{r echo=FALSE, out.width='100%'}
-knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/LitVsEmp_Measure_Plot.jpg')
+fig_name = 'LitVsEmp_Measure_Plot.jpeg'
+
+knitr::include_graphics(paste0(fig_path, fig_name))
 ```

### 2018-10-16 code/figure_scripts/LitVsEmp_Measure_Plot.R

@@ -1,0 +1,45 @@
+source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/figure_scripts/figure_res_wrapper.R')
+
+if(!exists('rel_comp')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_functions/rel_comp_data.R')
+}
+
+p1 = rel_comp %>%
+  filter(task == 'task') %>%
+  ggplot(aes(x = var, y = retest_reliability)) +
+  geom_boxplot(fill='#00BFC4', position="identity")+
+  geom_point(aes(x = var, y = mean_pearson),color="purple", fill="purple", size=3, shape=23)+
+  coord_flip()+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"),
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom') +
+  xlab("")+
+  ylab("")+
+  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))
+
+p2 = rel_comp %>%
+  filter(task == 'survey') %>%
+  ggplot(aes(x = var, y = retest_reliability)) +
+  geom_boxplot(fill='#F8766D', position="identity")+
+  geom_point(aes(x = var, y = mean_pearson),color="purple", fill="purple", size=3, shape=23)+
+  coord_flip()+
+  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
+  theme(panel.spacing = unit(0.5, "lines"),
+        strip.placement = "outside",
+        strip.text.y = element_text(angle=180),
+        panel.background = element_rect(fill = NA),
+        panel.grid.major = element_line(colour = "grey80"),
+        legend.position = 'bottom') +
+  xlab("")+
+  ylab("")+
+  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))
+
+p3 <- arrangeGrob(p1, p2,nrow=1)
+
[…]

### 2018-10-16 code/workspace_scripts/SRO_Retest_Analyses_Workspace.R

@@ -25,6 +25,8 @@ source(paste0(workspace_scripts,'demog_data.R'))
 
 source(paste0(workspace_scripts,'boot_rel_data.R'))
 
+source(paste0(workspace_scripts,'rel_comp_data.R'))
+
 source(paste0(workspace_scripts,'duplicate_items_data.R'))
 
 source(paste0(workspace_scripts,'measure_labels_data.R'))

### 2018-10-16 code/workspace_scripts/boot_rel_data.R

@@ -1,8 +1,3 @@
-if(!exists('lit_review')){
-  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/lit_review_data.R')
-}
-
-
 #########################
 ## Bootstrapped reliability data ####
 #########################
@@ -42,13 +37,15 @@ rm(refit_boot_df)
 boot_df = boot_df %>% mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
                              var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100,
                              var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100)
-
-var_boot_df = boot_df %>%
-  group_by(dv) %>%
-  summarise(mean_icc = mean(icc),
-            mean_pearson = mean(pearson))
-
-rel_comp = lit_review %>%
-  left_join(var_boot_df, by = 'dv')
-
-rm(var_boot_df)
+# 
+# var_boot_df = boot_df %>%
+#   group_by(dv) %>%
+#   summarise(mean_icc = mean(icc),
+#             mean_pearson = mean(pearson))
+# 
+# rel_comp = lit_review %>%
+#   left_join(var_boot_df, by = 'dv')
+# 
+# write.csv(rel_comp, '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/rel_comp.csv', row.names=F)
+# 
+# rm(var_boot_df)

### 2018-10-16 code/workspace_scripts/rel_comp_data.R

@@ -1,0 +1,5 @@
+#########################
+## Reliability Comparison data ####
+#########################
+
+rel_comp <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/rel_comp.csv')

### 2018-10-16 code/SRO_Retest_Analyses.Rmd
refactoring and debugging

@@
   labs(caption = str_wrap("FIGURE 2: Correlation between mean reliability estimates for each measure found in the literature with the mean reliability from our data.", width = 120))
-
-ggsave('LitAndEmpAveCor.tiff', device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 7, height = 5, units = "in", limitsize = FALSE, dpi = 300)
 ```
@@
 ```{r echo=FALSE}
-rm(tmp, rel_comp, mod1, mod2, mod3, n_df, i, lit_emp_cor, lit_emp_cor_out, comp_lit_pred, comp_lit_pred_out)
+rm(tmp, rel_comp, mod1, mod2, mod3, i, lit_emp_cor_out, comp_lit_pred, comp_lit_pred_out)
 ```
@@
 ## Relationship between reliability metrics (point estimates)
-
-Based on [Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) ICC(3,k) does not take in to account within subject differences between two time points (i.e.
-the fixed effect of time/systematic error).
-Thus, it is well approximated by Pearson's r and subject to similar criticisms.
-[Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) suggests reporting at least this systematic error effect size if one chooses to report with ICC(3,k).
-Based on his conclusions here I report:
-- ICC(3,k): As Dave clarified this ranges from 1 to -1/(number of repeated measures -1) so in our case this range would be [-1, 1]; larger values would mean that the two scores of a subject for a given measure are more similar to each other than they are to scores of other people
-- "ICC is reflective of the ability of a test to differentiate between different individuals"
-- partial $\eta^2$ for time ($SS_{time}/SS_{within}$): effect size of time   
-- SEM ($\sqrt(MS_{error})$): standard error of measurement; the smaller the better. It
-"quantifies the precision of individual scores on a test" and is not dependent on the sample in the way ICC is since it doesn't depend on between subject reliability (at least in this formulation) but is unit-dependent.
-
-We calculated `r as.numeric(table(rel_df$task)[1])` measures for surveys and `r as.numeric(table(rel_df$task)[2])` measures for cognitive tasks.
 
@@
 ```{r}
+rel_df = make_rel_df(t1_df = test_data, t2_df = retest_data, metrics = c('spearman', 'icc', 'pearson', 'var_breakdown', 'partial_eta', 'sem'))
+
 numeric_cols = c()
@@
 ```
+
+We calculated `r as.numeric(table(rel_df$task)[1])` measures for surveys and `r as.numeric(table(rel_df$task)[2])` measures for cognitive tasks.
 

### 2018-10-16 code/helper_functions/get_retest_stats.R

@@ -28,8 +28,7 @@ get_retest_stats = function(dv_var, t1_df = test_data, t2_df = retest_data, merg
   }
   
   if('icc' %in% metric | 'var_breakdown' %in% metric){
-    df = df %>% select(-dv, -sub_id)
-    icc = ICC(df)
+    icc = ICC(df %>% select(-dv, -sub_id))
     
     if('icc' %in% metric){
       out$icc = icc$results['Average_fixed_raters', 'ICC']
@@ -45,7 +44,7 @@ get_retest_stats = function(dv_var, t1_df = test_data, t2_df = retest_data, merg
   
   if('partial_eta' %in% metric | 'sem' %in% metric){
     
-    mod = summary(aov(score~Error(sub_id)+time, df))
+    mod = summary(aov(score~Error(sub_id)+time, df %>% gather(time, score, -dv, -sub_id)))
     
     if('partial_eta' %in% metric){
       ss_time = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq1',]

### 2018-10-16 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 
-numeric_cols = c()
-
-for(i in 1:length(names(test_data))){
-  if(is.numeric(test_data[,i]) & names(test_data)[i] %in% names(retest_data)){
-    numeric_cols <- c(numeric_cols, names(test_data)[i])
-  }
-}
-#Create df of point estimate reliabilities
-rel_df <- data.frame(spearman = rep(NA, length(numeric_cols)),
-                     icc = rep(NA, length(numeric_cols)),
-                     pearson = rep(NA, length(numeric_cols)),
-                     partial_eta_sq = rep(NA, length(numeric_cols)),
-                     sem = rep(NA, length(numeric_cols)),
-                     var_subs = rep(NA, length(numeric_cols)),
-                     var_ind = rep(NA, length(numeric_cols)),
-                     var_resid = rep(NA, length(numeric_cols)))
-
-row.names(rel_df) <- numeric_cols
-
-for(i in 1:length(numeric_cols)){
-  rel_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i])
-  rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
-  rel_df[numeric_cols[i], 'pearson'] <- get_pearson(numeric_cols[i])
-  rel_df[numeric_cols[i], 'partial_eta_sq'] <- get_partial_eta(numeric_cols[i])
-  rel_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
-  rel_df[numeric_cols[i], 'var_subs'] <- get_var_breakdown(numeric_cols[i])$subs
-  rel_df[numeric_cols[i], 'var_ind'] <- get_var_breakdown(numeric_cols[i])$ind
-  rel_df[numeric_cols[i], 'var_resid'] <- get_var_breakdown(numeric_cols[i])$resid
-}
-
-rel_df$dv = row.names(rel_df)
-row.names(rel_df) = seq(1:nrow(rel_df))
 rel_df$task = 'task'
@@
 rel_df = rel_df %>%
-  select(dv, task, spearman, icc, pearson, partial_eta_sq, sem, var_subs, var_ind, var_resid)
-# row.names(rel_df) = NULL
-
+  select(dv, task, spearman, icc, pearson, partial_eta, sem, var_subs, var_ind, var_resid)
 ```
@@
 We calculated `r as.numeric(table(rel_df$task)[1])` measures for surveys and `r as.numeric(table(rel_df$task)[2])` measures for cognitive tasks.
-
-```{r}
-table(rel_df$task)
-```
 

### 2018-10-16 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 
-```{r warning=FALSE, message=FALSE}
-p1 = rel_df %>%
-  ggplot(aes(spearman, icc, col=task))+
-  geom_point()+
-  theme_bw()+
-  theme(legend.title = element_blank(),
-        legend.position = "none")+
-  geom_abline(intercept = 0, slope=1)
-
-p2 = rel_df %>%
-  ggplot(aes(pearson, icc, col=task))+
-  geom_point()+
-  theme_bw()+
-  theme(legend.title = element_blank(),
-        legend.position = "none")+
-  geom_abline(intercept = 0, slope=1)
-
-p3 = rel_df %>%
-  ggplot(aes(pearson, spearman, col=task))+
-  geom_point()+
-  theme_bw()+
-  theme(legend.title = element_blank(),
-        legend.position = "none")+
-  geom_abline(intercept = 0, slope=1)
-
-grid.arrange(p1, p2, p3, nrow=1)
-
-ggsave('Metric_Scatterplots.jpg', plot = grid.arrange(p1, p2, p3, nrow=1), device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE, dpi = 300)
+```{r echo=FALSE, out.width='100%'}
+fig_name = 'Metric_Scatterplots.jpeg'
+
+knitr::include_graphics(paste0(fig_path, fig_name))
 ```
@@
 cor(rel_df[,c('spearman', 'icc', 'pearson')])
-```
-
-```{r echo=FALSE}
-rm(p1,p2,p3)
 ```

### 2018-10-16 code/figure_scripts/Metric_Scatterplots.R

@@ -1,3 +1,19 @@
+source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/figure_scripts/figure_res_wrapper.R')
+
+if(!exists('rel_df')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/subject_data.R')
+  
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/make_rel_df.R')
+  
+  rel_df = make_rel_df(t1_df = test_data, t2_df = retest_data, metrics = c('spearman', 'icc', 'pearson', 'var_breakdown', 'partial_eta', 'sem'))
+  
+  rel_df$task = 'task'
+  rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
+  rel_df[grep('holt', rel_df$dv), 'task'] = "task"
+  rel_df = rel_df %>%
+    select(dv, task, spearman, icc, pearson, partial_eta, sem, var_subs, var_ind, var_resid)
+}
+
 p1 = rel_df %>%
   ggplot(aes(spearman, icc, col=task))+
   geom_point()+
@@ -22,6 +38,6 @@ p3 = rel_df %>%
         legend.position = "none")+
   geom_abline(intercept = 0, slope=1)
 
-grid.arrange(p1, p2, p3, nrow=1)
+ggsave(paste0('Metric_Scatterplots.',out_device), plot = grid.arrange(p1, p2, p3, nrow=1), device = out_device, path = fig_path, width = 12, height = 4, units = "in", dpi=img_dpi)
 
-ggsave('Metric_Scatterplots.jpg', plot = grid.arrange(p1, p2, p3, nrow=1), device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE, dpi = 300)
+rm(p1,p2,p3)

### 2018-10-16 code/figure_scripts/figure_res_wrapper.R

@@ -4,11 +4,11 @@ img_dpi <- as.numeric(readline(prompt="Enter img dpi: "))
 img_dpi = ifelse(is.na(img_dpi), 100, img_dpi)
 
 default_fig_path <- readline(prompt="Enter default fig path: ")
-default_fig_path = ifelse(length(default_fig_path)==1, '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures', default_fig_path)
+default_fig_path = ifelse(length(default_fig_path)==1, '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/', default_fig_path)
 
 out_device <- readline(prompt="Enter image filetype: ")
 out_device = ifelse(length(out_device)==1, 'jpeg', out_device)
 
 high_res = ifelse(img_dpi>100, T, F)
 
-fig_path = ifelse(high_res, paste0(default_fig_path, "/high_res"), default_fig_path)
+fig_path = ifelse(high_res, paste0(default_fig_path, "/high_res/"), default_fig_path)

### 2018-10-16 code/workspace_scripts/SRO_Retest_Analyses_Helper_Functions.R

@@ -1,9 +1,7 @@
 library(gridExtra)
 library(lme4)
 library(GGally)
-library(psych)
 library(rmarkdown)
-library(psych)
 library(stringr)
 library(plotly)
 library(DT)

### 2018-10-16 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 
-```{r}
-tmp = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% meaningful_vars == FALSE)])
-tmp = tmp[-grep('survey', tmp)]
-
-meaningful_vars = c(meaningful_vars, tmp)
-meaningful_vars = sort(meaningful_vars)
-```
-
-```{r warning=FALSE, message=FALSE}
-# Df wrangling for plotting
-tmp = measure_labels %>%
-  mutate(dv = as.character(dv)) %>%
-  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')
-
-tmp = tmp %>%
-  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
-  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
-  separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
-  mutate(task_group = gsub("_", " ", task_group),
-         var = gsub("_", " ", var)) %>%
-  arrange(task_group, var)
-
-tmp = tmp %>%
-  left_join(rel_df[,c("dv", "icc")], by = "dv") %>%
-  rename(icc = icc.x, point_est = icc.y)
-
-#Manual correction
-tmp = tmp %>%
-  mutate(task = ifelse(task_group == 'holt laury survey', "task", as.character(task))) %>%
-  mutate(task_group = gsub("survey", "", task_group),
-         task_group = gsub("task", "", task_group),
-         task_group = str_to_title(task_group)) %>%
-  mutate(task_group = ifelse(task_group == "Psychological Refractory Period Two Choices", "Psychological Refractory Period", ifelse(task_group == "Angling Risk Always Sunny", "Angling Risk", ifelse(task_group == "Two Stage", "Two Step", ifelse(task_group == "Threebytwo", "Task Switching", ifelse(task_group == "Adaptive N Back", "Adaptive N-back", ifelse(task_group == "Go Nogo", "Go/No-go",  ifelse(task_group == "Ravens", "Raven's", task_group)))))))) %>%
-  mutate(task_group = ifelse(task_group == "Bis Bas ", "BIS-BAS", ifelse(task_group == "Bis11 ", "BIS-11", ifelse(task_group == "Dospert Eb ", "DOSPERT EB", ifelse(task_group == "Dospert Rp ", "DOSPOERT RP", ifelse(task_group == "Dospert Rt ", "DOSPERT RT", ifelse(task_group == "Erq ", "ERQ", ifelse(task_group == "Upps Impulsivity ", "UPPS-P", task_group))))))))
-```
-
-Extract trial number info to add to boot plot instead of adding another table
-
-```{r}
-tmp_mngfl = tmp %>%
-  filter(dv %in% meaningful_vars)
-
-trial_num_info = tmp %>%
-  group_by(task_group, task) %>%
-  summarise(mean_num_all_trials = round(mean(num_all_trials)),
-            num_measures = length(unique(dv)))
-
-trial_num_info_mngfl = tmp_mngfl %>%
-  group_by(task_group, task) %>%
-  summarise(mean_num_all_trials = round(mean(num_all_trials)),
-            num_measures = length(unique(dv)))
-
-tmp = tmp %>%
-  left_join(trial_num_info, by=c("task_group", "task"))
-
-tmp_mngfl = tmp_mngfl %>%
-  left_join(trial_num_info_mngfl, by=c("task_group", "task"))
-```
-
-Boot plot for tasks with trial info (only using meaningful vars)
-
-```{r warning=FALSE, message=FALSE}
-p4_t <- tmp_mngfl %>%
-  filter(task == 'task') %>%
-ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) +
-  geom_violin(fill='#00BFC4')+
-  theme_bw() +
-  theme(axis.text = element_text(size=30))+
-  xlab("")+
-  ylab("")+
-  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1), position = "right")+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
-  geom_hline(yintercept = 0, color = "red", size = 1)+
-  coord_flip()
-
-task_trial_num = trial_num_info_mngfl %>%
-  filter(task == "task") %>%
-  ungroup() %>%
-  select(-task)
-
-task_trial_num_table = task_trial_num %>%
-  mutate(y_axis = rev(ggplot_build(p4_t)$layout$panel_params[[1]]$y.major)) %>%
-  gather(key, value, -y_axis, -task_group) %>%
-  ggplot(aes(key, factor(y_axis)))+
-  geom_text(aes(label=value), size=14)+
-  xlab("")+
-  ylab("")+
-  theme(axis.ticks=element_blank(),
-        axis.text.y = element_blank(),
-        panel.grid = element_blank(),
-        panel.border = element_blank(),
-        axis.text.x = element_text(size=30))+
-  scale_x_discrete(position = "top",
-                   breaks=c("mean_num_all_trials", "num_measures"),
-                   labels=c("Mean Num Trials", "Num Measures"))
-
-boot_task_plot = arrangeGrob(p4_t, task_trial_num_table, nrow=1, widths = c(3,2))
-
-ggsave('Task_Boot_w_trialinfo.jpg', plot = boot_task_plot, device = "jpeg", path = "../output/figures/", width = 20, height = 48, units = "in", limitsize = FALSE, dpi = 100)
-
-```
-
-Boot plot for surveys with trial info (only using meaningful vars)
-
-```{r}
-p5_t <- tmp %>%
-  filter(task == 'survey') %>%
-ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) +
-  geom_violin(fill='#F8766D')+
-  theme_bw() +
-  theme(axis.text = element_text(size=30))+
-  xlab("")+
-  ylab("")+
-  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1), position = "right")+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
-  geom_hline(yintercept = 0, color = "red", size = 1)+
-  coord_flip()
-
-survey_trial_num = trial_num_info %>%
-  filter(task == "survey") %>%
-  ungroup() %>%
-  select(-task)
-
-survey_trial_num_table = survey_trial_num %>%
-  mutate(y_axis = rev(ggplot_build(p5_t)$layout$panel_params[[1]]$y.major)) %>%
-  gather(key, value, -y_axis, -task_group) %>%
-  ggplot(aes(key, factor(y_axis)))+
-  geom_text(aes(label=value), size=14)+
-  xlab("")+
-  ylab("")+
-  theme(axis.ticks=element_blank(),
-        axis.text.y = element_blank(),
-        panel.grid = element_blank(),
-        panel.border = element_blank(),
-        axis.text.x = element_text(size=30))+
-  scale_x_discrete(position = "top",
-                   breaks=c("mean_num_all_trials", "num_measures"),
-                   labels=c("Mean Num Trials", "Num Measures"))
-
-boot_survey_plot = arrangeGrob(p5_t, survey_trial_num_table, nrow=1, widths = c(3,2))
-
-ggsave('Survey_Boot_w_trialinfo.jpg', plot = boot_survey_plot, device = "jpeg", path = "../output/figures/", width = 20, height = 48, units = "in", limitsize = FALSE, dpi = 100)
-```
-
-Both task level boot plots with trial info together
-
-```{r}
-mycaption = textGrob(label = str_wrap("FIGURE 4: Summary of bootstrapped reliability estimates for tasks (left) and surveys (right).
-We sampled 150 subjects with replacement 1000 times to create a distribution of bootstrapped reliability estimate for each measure.
-Reliability measure depicted is ICC.
-Red lines indicate 0 reliability.
-Columns following each graph present the mean number of trials used for dependent measures in that task and the number of ‘meaningful measures,’ dependent measures used in the literature from each task.", width = 165), gp = gpar(fontfamily="Times", lineheight = 2, fontsize = 40), hjust = 0, vjust = 0.5, x = unit(0, "npc"))
-
-boot_both_w_trial = arrangeGrob(arrangeGrob(boot_task_plot, boot_survey_plot, nrow=1), mycaption, nrow=2, heights = c(10,1))
-
-ggsave('Boot_Both_w_trialinfo.tiff', plot = boot_both_w_trial, device = "tiff", path = "../output/figures/", width = 38, height = 55, units = "in", limitsize = FALSE, dpi = 200)
+```{r echo=FALSE, out.width='100%'}
+fig_name = 'Boot_Both_w_trialinfo.jpeg'
+
+knitr::include_graphics(paste0(fig_path, fig_name))
 ```
@@
 
-```{r warning=FALSE, message=FALSE}
-p4 <- tmp %>%
-  filter(task == 'task',
-         raw_fit == 'raw') %>%
-ggplot(aes(y = var, x = icc)) +
-  geom_point(color = '#00BFC4')+
-  geom_point(aes(y = var, x = point_est), color = "black")+
-  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y", labeller = label_wrap_gen(width=20)) +
-  theme(panel.spacing = unit(0.75, "lines"),
-        strip.placement = "outside",
-        strip.text.y = element_text(angle=180, size=36),
-        axis.text.y = element_text(size=20),
-        panel.background = element_rect(fill = NA),
-        panel.grid.major = element_line(colour = "grey80")) +
-  xlab("")+
-  ylab("")+
-  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
-  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
-  geom_vline(xintercept = 0, color = "red", size = 1)
-
-p5 <- tmp %>%
-  filter(task == 'survey') %>%
-ggplot(aes(y = var, x = icc)) +
-  geom_point(color = '#F8766D')+
-  geom_point(aes(y = var, x = point_est), color = "black")+
-  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y", labeller = label_wrap_gen(width=20)) +
-  theme(panel.spacing = unit(0.75, "lines"),
-        strip.placement = "outside",
-        strip.text.y = element_text(angle=180, size=36),
-        axis.text.y = element_text(size=20),
-        panel.background = element_rect(fill = NA),
-        panel.grid.major = element_line(colour = "grey80")) +
-  xlab("")+
-  ylab("")+
-  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
-  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
-  geom_vline(xintercept = 0, color = "red", size = 1)
-
-p6 <- arrangeGrob(p4, p5,nrow=1)
-
-ggsave('Bootstrap_Raw_Var_Plot.jpg', plot = p6, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 36, height = 72, units = "in", limitsize = FALSE, dpi=50)
-
-rm(p4, p5, p6)
-```
-
 ```{r echo=FALSE, out.width='100%'}
-knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Bootstrap_Raw_Var_Plot.jpg')
+fig_name = 'Bootstrap_Raw_Var_Plot.jpeg'
+
+knitr::include_graphics(paste0(fig_path, fig_name))
 ```
@@
 
-```{r}
-p1<- tmp %>%
-  filter(grepl('selection_optimization', dv)) %>%
-ggplot(aes(x = var, y = icc)) +
-  geom_violin(fill='#F8766D')+
-  theme_bw() +
-  theme(axis.text.y = element_text(size=30))+
-  xlab("")+
-  ylab("")+
-  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
-  geom_hline(yintercept = 0, color = "red", size = 1)+
-  coord_flip()
-
-p2<- tmp %>%
-  filter(grepl('selection_optimization', dv)) %>%
-ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc, group=dv)) +
-  geom_violin(fill='#F8766D', position = 'identity')+
-  theme_bw() +
-  theme(axis.text.y = element_text(size=30))+
-  xlab("")+
-  ylab("")+
-  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
-  geom_hline(yintercept = 0, color = "red", size = 1)+
-  coord_flip()
-
-p3<- tmp %>%
-  filter(grepl('selection_optimization', dv)) %>%
-ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) +
-  geom_violin(fill='#F8766D', position = 'identity')+
-  theme_bw() +
-  theme(axis.text.y = element_text(size=30))+
-  xlab("")+
-  ylab("")+
-  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
-  geom_hline(yintercept = 0, color = "red", size = 1)+
-  coord_flip()
-
-p4 <- arrangeGrob(p1,p2, p3,nrow=1)
-
-ggsave('Bootstrap_Example_Plot_t.jpg', plot = p4, device = "jpeg", path = "../output/figures/", width = 41, height = 5, units = "in", limitsize = FALSE, dpi = 300)
-```
-
 ```{r echo=FALSE, out.width='100%'}
-knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Bootstrap_Example_Plot_t.jpg')
-```
-
-```{r}
-rm(p1, p2, p3, p4)
+fig_name = 'Bootstrap_Example_Plot_t.jpeg'
+
+knitr::include_graphics(paste0(fig_path, fig_name))
 ```
@@
 summary(icc_by_task_model)
+```
+
+```{r echo=FALSE}
+rm(icc_by_task_model)
 ```

### 2018-10-16 code/figure_scripts/Boot_w_trialinfo.R

@@ -1,0 +1,161 @@
+source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/figure_scripts/figure_res_wrapper.R')
+
+if(!exists('lit_review')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/lit_review_data.R')
+}
+
+if(!exists('meaningful_vars')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/meaningful_vars_data.R')
+}
+
+if(!exists('measure_labels')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/measure_labels_data.R')
+}
+
+if(!exists('boot_df')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/boot_rel_data.R')
+}
+
+require(grid)
+
+tmp = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% meaningful_vars == FALSE)])
+tmp = tmp[-grep('survey', tmp)]
+
+meaningful_vars = c(meaningful_vars, tmp)
+meaningful_vars = sort(meaningful_vars)
+
+tmp = measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')
+
+tmp = tmp %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
+  mutate(task_group = gsub("_", " ", task_group),
+         var = gsub("_", " ", var)) %>%
+  arrange(task_group, var)
+
+tmp = tmp %>%
+  left_join(rel_df[,c("dv", "icc")], by = "dv") %>%
+  rename(icc = icc.x, point_est = icc.y)
+
+#Manual correction
+tmp = tmp %>%
+  mutate(task = ifelse(task_group == 'holt laury survey', "task", as.character(task))) %>%
+  mutate(task_group = gsub("survey", "", task_group),
[…]

### 2018-10-16 code/figure_scripts/Bootstrap_Example_Plot_t.R

@@ -1,0 +1,86 @@
+source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/figure_scripts/figure_res_wrapper.R')
+
+if(!exists('lit_review')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/lit_review_data.R')
+}
+
+if(!exists('measure_labels')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/measure_labels_data.R')
+}
+
+if(!exists('boot_df')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/boot_rel_data.R')
+}
+
+tmp = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% meaningful_vars == FALSE)])
+tmp = tmp[-grep('survey', tmp)]
+
+tmp = measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')
+
+tmp = tmp %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
+  mutate(task_group = gsub("_", " ", task_group),
+         var = gsub("_", " ", var)) %>%
+  arrange(task_group, var)
+
+tmp = tmp %>%
+  left_join(rel_df[,c("dv", "icc")], by = "dv") %>%
+  rename(icc = icc.x, point_est = icc.y)
+
+#Manual correction
+tmp = tmp %>%
+  mutate(task = ifelse(task_group == 'holt laury survey', "task", as.character(task))) %>%
+  mutate(task_group = gsub("survey", "", task_group),
+         task_group = gsub("task", "", task_group),
+         task_group = str_to_title(task_group)) %>%
[…]

### 2018-10-16 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 
-```{r warning=FALSE, message=FALSE}
-tmp = rel_df %>%
-  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
-         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100,
-         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
-  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
-  mutate(dv = factor(dv, levels = dv[order(task)])) %>%
-  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
-  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
-  arrange(task_group, var_subs_pct) %>%
-  mutate(rank = row_number()) %>%
-  arrange(task, task_group, rank) %>%
-  gather(key, value, -dv, -task_group, -var, -task, -rank) %>%
-  ungroup()%>%
-  mutate(task_group = gsub("_", " ", task_group),
-         var = gsub("_", " ", var)) %>%
-  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
-  mutate(task_group = gsub("survey", "", task_group)) %>%
-  filter(task=="task",
-         !grepl("EZ|hddm", dv))%>%
-  arrange(task_group, rank)
-labels = tmp %>%
-  distinct(dv, .keep_all=T)
-
-p1 <- tmp %>%
-  ggplot(aes(x=factor(rank), y=value, fill=factor(key, levels = c("var_resid_pct", "var_ind_pct", "var_subs_pct"))))+
-  geom_bar(stat='identity', alpha = 0.75, color='#00BFC4')+
-  scale_x_discrete(breaks = labels$rank,
-                       labels = labels$var)+
-  coord_flip()+
-  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
-  theme(panel.spacing = unit(0.5, "lines"),
-        strip.placement = "outside",
-        strip.text.y = element_text(angle=180),
-        panel.background = element_rect(fill = NA),
-        panel.grid.major = element_line(colour = "grey85"),
-        legend.position = 'bottom')+
-  theme(legend.title = element_blank())+
-  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
-                      labels = c("Variance between individuals",
-                                 "Variance between sessions",
-                                 "Error variance"),
-                  values=c("grey65", "grey45", "grey25"))+
-  ylab("")+
-  xlab("")
-
-tmp = rel_df %>%
-  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
-         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100,
-         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
-  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
-  mutate(dv = factor(dv, levels = dv[order(task)])) %>%
-  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
-  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
-  arrange(task_group, var_subs_pct) %>%
-  mutate(rank = row_number()) %>%
-  arrange(task, task_group, rank) %>%
-  gather(key, value, -dv, -task_group, -var, -task, -rank) %>%
-  ungroup()%>%
-  mutate(task_group = gsub("_", " ", task_group),
-         var = gsub("_", " ", var)) %>%
-  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
-  mutate(task_group = gsub("survey", "", task_group)) %>%
-  filter(task=="survey")%>%
-  arrange(task_group, rank)
-labels = tmp %>%
-  distinct(dv, .keep_all=T)
-
-p2 <- tmp %>%
-  ggplot(aes(x=factor(rank), y=value, fill=factor(key, levels = c("var_resid_pct", "var_ind_pct", "var_subs_pct"))))+
-  geom_bar(stat='identity', alpha = 0.75)+
-  geom_bar(stat='identity', color='#F8766D', show.legend=FALSE)+
-  scale_x_discrete(breaks = labels$rank,
-                       labels = labels$var)+
-  coord_flip()+
-  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
-  theme(panel.spacing = unit(0.5, "lines"),
-        strip.placement = "outside",
-        strip.text.y = element_text(angle=180),
-        panel.background = element_rect(fill = NA),
-        panel.grid.major = element_line(colour = "grey85"),
-        legend.position = 'bottom')+
-  theme(legend.title = element_blank())+
-  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
-                      labels = c("Variance between individuals",
-                                 "Variance between sessions",
-                                 "Error variance"),
-                  values=c("grey65", "grey45", "grey25"))+
-  ylab("")+
-  xlab("")
-
-mylegend<-g_legend(p2)
-
-p3 <- arrangeGrob(arrangeGrob(p1 +theme(legend.position="none"),
-                         p2 + theme(legend.position="none"),
-                         nrow=1),
-             mylegend, nrow=2,heights=c(10, 1))
-
-ggsave('Variance_Breakdown_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 24, height = 20, units = "in", dpi = 100)
-rm(tmp, labels, p1, p2 , p3)
-```
-
 ```{r echo=FALSE, out.width='100%'}
-knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Variance_Breakdown_Plot.jpg')
+fig_name = 'Variance_Breakdown_Plot.jpeg'
+
+knitr::include_graphics(paste0(fig_path, fig_name))
 ```
@@
 summary(var_resid_pct_by_task_model)
+```
+
+```{r}
+rm(var_subs_pct_by_task_model, var_ind_pct_by_task_model, var_resid_pct_by_task_model)
 ```
@@
 
-```{r}
-sjt.df(tmp_save %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/var_breakdown_summary.doc")
-```
-
 Summarizing for clearer presentation. This graph is currently using the bootstrapped reliabilities and is therefore messier than if just using the point estimates.
 
-```{r}
-tmp %>%
-  gather(key, value, -dv, -task) %>%
-  group_by(task, key) %>%
-  summarise(mean_pct = mean(value),
-            sd_pct = sd(value, na.rm=T),
-            n = n()) %>%
-  mutate(cvl = qt(0.025, n-1),
-         cvu = qt(0.975, n-1),
-         cil = mean_pct+(sd_pct*cvl)/sqrt(n),
-         ciu = mean_pct+(sd_pct*cvu)/sqrt(n),
-         sem_pct = sd_pct/sqrt(n)) %>%
-  ggplot(aes(factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
-                    labels = c("Between subject variance",
-                               "Within subject variance",
-                               "Error variance")), mean_pct))+
-  geom_errorbar(aes(ymin=cil, ymax=ciu, group=task), position=position_dodge(width = 0.25), width=0.25, size=2, alpha = 0.85, color="gray")+
-  geom_point(position=position_dodge(width = 0.25), size=3, aes(color=task, shape=task))+
-  #geom_bar(position=position_dodge(width = 0.5), width=0.5, aes(fill=task), stat='identity', alpha=0.5)+
-  #geom_errorbar(aes(ymin=mean_pct-sd_pct, ymax=mean_pct+sd_pct), position=position_dodge(width = 0.25), width=0, size=2)+
-  theme_bw()+
-  xlab('')+
-  ylab('Percent of total variance')+
-  theme(legend.title = element_blank(),
-        legend.text = element_text(size=14),
-        legend.position = 'bottom',
-        axis.text = element_text(size=12),
-        axis.title.y = element_text(size=12),
-        plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0)) +
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
-  ylim(0,100)+
-  labs(caption = str_wrap("FIGURE 5:  Percentage of variance explained by each of the three sources of variance: between subjects, within subjects (between sessions) and error variance for 1000 bootstrapped samples.
-Error bars are 95% confidence intervals.", width = 120))
-
-ggsave('Variance_Breakdown_DotPlot.tiff', device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 7, height = 4, units = "in", dpi = 300)
+```{r echo=FALSE, out.width='100%'}
+fig_name = 'Variance_Breakdown_DotPlot.jpeg'
+
+knitr::include_graphics(paste0(fig_path, fig_name))
 ```

### 2018-10-16 code/figure_scripts/Variance_Breakdown_DotPlot.R

@@ -1,0 +1,42 @@
+source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/figure_scripts/figure_res_wrapper.R')
+
+if(!exists('boot_df')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/boot_rel_data.R')
+}
+
+tmp = boot_df %>%
+  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct)
+
+p1 = tmp %>%
+  gather(key, value, -dv, -task) %>%
+  group_by(task, key) %>%
+  summarise(mean_pct = mean(value),
+            sd_pct = sd(value, na.rm=T),
+            n = n()) %>%
+  mutate(cvl = qt(0.025, n-1),
+         cvu = qt(0.975, n-1),
+         cil = mean_pct+(sd_pct*cvl)/sqrt(n),
+         ciu = mean_pct+(sd_pct*cvu)/sqrt(n),
+         sem_pct = sd_pct/sqrt(n)) %>%
+  ggplot(aes(factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
+                    labels = c("Between subject variance",
+                               "Within subject variance",
+                               "Error variance")), mean_pct))+
+  geom_errorbar(aes(ymin=cil, ymax=ciu, group=task), position=position_dodge(width = 0.25), width=0.25, size=2, alpha = 0.85, color="gray")+
+  geom_point(position=position_dodge(width = 0.25), size=3, aes(color=task, shape=task))+
+  #geom_bar(position=position_dodge(width = 0.5), width=0.5, aes(fill=task), stat='identity', alpha=0.5)+
+  #geom_errorbar(aes(ymin=mean_pct-sd_pct, ymax=mean_pct+sd_pct), position=position_dodge(width = 0.25), width=0, size=2)+
+  theme_bw()+
+  xlab('')+
+  ylab('Percent of total variance')+
+  theme(legend.title = element_blank(),
+        legend.text = element_text(size=14),
+        legend.position = 'bottom',
+        axis.text = element_text(size=12),
+        axis.title.y = element_text(size=12),
+        plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0)) +
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
+  ylim(0,100)+
[…]

### 2018-10-16 code/figure_scripts/Variance_Breakdown_Plot.R

@@ -1,0 +1,116 @@
+source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/figure_scripts/figure_res_wrapper.R')
+
+if(!exists('rel_df')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/subject_data.R')
+  
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/make_rel_df.R')
+  
+  rel_df = make_rel_df(t1_df = test_data, t2_df = retest_data, metrics = c('spearman', 'icc', 'pearson', 'var_breakdown', 'partial_eta', 'sem'))
+  
+  rel_df$task = 'task'
+  rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
+  rel_df[grep('holt', rel_df$dv), 'task'] = "task"
+  rel_df = rel_df %>%
+    select(dv, task, spearman, icc, pearson, partial_eta, sem, var_subs, var_ind, var_resid)
+}
+
+tmp = rel_df %>%
+  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
+         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100,
+         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
+  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
+  mutate(dv = factor(dv, levels = dv[order(task)])) %>%
+  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
+  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
+  arrange(task_group, var_subs_pct) %>%
+  mutate(rank = row_number()) %>%
+  arrange(task, task_group, rank) %>%
+  gather(key, value, -dv, -task_group, -var, -task, -rank) %>%
+  ungroup()%>%
+  mutate(task_group = gsub("_", " ", task_group),
+         var = gsub("_", " ", var)) %>%
+  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
[…]

### 2018-10-16 code/SRO_Retest_Analyses.Rmd
removed exploratory analyses on systematic effects of time

@@
 ```
-
-## Systematic effects between time points
-
-### Anova time effects
-
-The type of ICC we have chosen does not take within subject (between session/systematic) variance in to account.
-This is why Weir recommends checking whether there is a significant change based on time and examining the SEMs.
-These systematic effects could be meaningful and important to account for for some measures (e.g.
-task measures that show learning effects).
-
-Had we chosen another kind of ICC taking this source of variance into account (e.g. 2,1 or 2,k) they could have suggested that tasks have lower reliability.
-
-Doing a simple t-test on the difference score alone would not be a very rigourous way of testing whether any change is meaningful because two distributions from both time points with error would be compared to each other.
-Fortunately there are ways to take the error for both measurements in to account.
-
-To check whether a measure shows systematic differences between the two time points in a meaningful number of bootstrapped samples we can: check if the effect of time is significant in each bootstrapped sample and filter variables that have more than 5% of the boostrapped samples showing significant time effects.
-
-Another way might be to compute confidence intervals using SEMs as described in the second half of Weir (2005) and check what percent of participants have scores that fall out of this range.
-
-First we ask: Which variables have significant time effects in more than 5% of the bootstrapped samples?
-
-23/74 survey measures
-133/372 task measures
-
-```{r}
-boot_df %>%
-  select(dv, p_time, task) %>%
-  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
-  group_by(dv)%>%
-  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
-            task = unique(task))%>%
-  filter(pct_sig_time_effect>5) %>%
-  arrange(task,-pct_sig_time_effect) %>%
-  ungroup()%>%
-  group_by(task) %>%
-  summarise(count=n()) %>%
-  mutate(total_num_vars = c(74, 372),
-         prop = count/total_num_vars) %>%
-  ggplot(aes(task, prop, fill=task))+
-  geom_bar(stat="identity", alpha=0.5, width=0.5)+
-  theme(legend.position = "none",
-        axis.text.x = element_text(size=14),
-        axis.title.y = element_text(size=14))+
-  ylab("Proportiono of bootstrap samples")+
-  xlab("")+
-  ylim(0,1)
-
-ggsave('PropTimeEffects.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 3, height = 5, units = "in", limitsize = FALSE, dpi = 300)
-
-```
-
-### SEM CI calculation
-
-Step 1: T = Grand mean + ICC * (Subject score - Grand mean)
-Step 2: SEP = SD of both measurements * sqrt(1-ICC^2)
-
-Here I calculate the proportion of subjects that move more than one standard error of prediction (SEP) in t2 compared to t1 for each measure.
-
-This is odd to think about because the larger the ICC of a measure the smaller the SEP. So very small differences between the two time points can be categorized as 'meaningful' based on the tiny SEP.
-
-What you are interested in is not necessarily whether individuals change at all between the two time points though. You want to know if this change is systematic in one direction.
-
-Here I calculate the proportion of people showing 'meaningful' changes in one direction or the other.
-To integrate both of these direction I subtracted one from the other and filtered the variables that have more than 5% of the participants showing meaningful change in one direction over the other (so if a variable has 10 participants showing difference in one and 10 in the other direction this would cancel out but a variables with 15 people showing a positive and 5 negative change would remain).
-
-```{r}
-get_ind_ci = function(dv_var){
-  matched = match_t1_t2(dv_var)
-  grand_mean = mean(matched$score)
-  grand_sd = sd(matched$score)
-  dv_icc = get_icc(dv_var)
-  sep = grand_sd * sqrt(1-(dv_icc^2))
-  matched = matched %>%
-    spread(time, score) %>%
-    rename("t1"="1", "t2"="2") %>%
-    mutate(true_score = grand_mean+(dv_icc*(t1-grand_mean)),
-           ci_up = true_score+(1.96*sep),
-           ci_low = true_score-(1.96*sep),
-           t2_above_ci = ifelse(t2>ci_up,1,0),
-           t2_below_ci = ifelse(t2<ci_low,1, 0))
-    return(matched)
-}
-
-get_prop_out_ci = function(dv_var){
-  get_ind_ci(dv_var) %>%
-    summarise(prop_above_ci = sum(t2_above_ci)/n(),
-              prop_below_ci = sum(t2_below_ci/n()))
-}
-
-#Create df of point estimate reliabilities
-ind_ci_df <- data.frame(prop_above_ci = rep(NA, length(numeric_cols)),
-                        prop_below_ci = rep(NA, length(numeric_cols)))
-
-row.names(ind_ci_df) <- numeric_cols
-
-for(i in 1:length(numeric_cols)){
-    ind_ci_df[numeric_cols[i], 'prop_above_ci'] <- get_prop_out_ci(numeric_cols[i])$prop_above_ci
-    ind_ci_df[numeric_cols[i], 'prop_below_ci'] <- get_prop_out_ci(numeric_cols[i])$prop_below_ci
-}
-
-ind_ci_df$dv = row.names(ind_ci_df)
-row.names(ind_ci_df) = seq(1:nrow(ind_ci_df))
-ind_ci_df$task = 'task'
-ind_ci_df[grep('survey', ind_ci_df$dv), 'task'] = 'survey'
-ind_ci_df[grep('holt', ind_ci_df$dv), 'task'] = "task"
-ind_ci_df = ind_ci_df %>%
-  select(dv, task, prop_above_ci, prop_below_ci)
-
-mean_diff_df = ind_ci_df %>%
-  mutate(prop_one_direction = prop_above_ci-prop_below_ci) %>%
-  filter(abs(prop_one_direction)>0.05) %>%
-  arrange(-abs(prop_one_direction))
-
-mean_diff_df
-```
-
-This doesn't make it easier to interpret whether it is a performance improvement or decline. In fact 'performance' isn't even necessarily the correct term here.
-
 ## Task Reliabilities

### 2018-10-16 code/SRO_Retest_Analyses.Rmd
refactoring

@@
 Here is a graph of how the point estimates of the retest reliability changes for each of the dependent measures using different numbers of trials to estimate them.
-
-Post process dv's from cluster to calculate reliabilities
-```{r}
-t1_dvs = t1_dvs %>% select(-X)
-t2_dvs = t2_dvs %>% select(-X)
-```
-
-```{r eval=FALSE}
-hr_merge = merge(t1_dvs, t2_dvs, by = c("worker_id", "level_1"))
-
-hr_merge = hr_merge %>%
-  gather(key, value, -worker_id, -level_1) %>%
-  separate(key, c("dv", "time"), sep="\\.") %>%
-  mutate(time = ifelse(time == "x", 1, 2))%>%
-  rename(sub_id = worker_id,
-         breaks = level_1)
-
-t1_dvs = hr_merge %>%
-  filter(time == 1) %>%
-  select(-time) %>%
-  spread(dv, value)
-
-t2_dvs = hr_merge %>%
-  filter(time == 2) %>%
-  select(-time) %>%
-  spread(dv, value)
-
-# calculate point estimates for reliability of each of the variables for each break
-# get_icc for each break of tmp_t1_dvs and tmp_t2_dvs
-
-trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))),
-                              acc_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              avg_rt_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              conceptual_responses_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              fail_to_maintain_set_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              learning_rate_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              learning_to_learn_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              nonperseverative_errors_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              perseverative_errors_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              perseverative_responses_icc=rep(NA, length(unique(t1_dvs$breaks))),
-                              total_errors_icc=rep(NA, length(unique(t1_dvs$breaks))))
-
-for(i in 1:length(unique(t1_dvs$breaks))){
-  cur_break = unique(t1_dvs$breaks)[i]
-  tmp_t1_dvs = t1_dvs %>% filter(breaks == cur_break)
-  tmp_t2_dvs = t2_dvs %>% filter(breaks == cur_break)
-  trial_num_rel_df$breaks[i] = cur_break
-  trial_num_rel_df$acc_icc[i] = get_icc("acc", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$avg_rt_icc[i] = get_icc("avg_rt", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$conceptual_responses_icc[i] = get_icc("conceptual_responses", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$fail_to_maintain_set_icc[i] = get_icc("fail_to_maintain_set", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$learning_rate_icc[i] = get_icc("learning_rate", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$learning_to_learn_icc[i] = get_icc("learning_to_learn", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$nonperseverative_errors_icc[i] = get_icc("nonperseverative_errors", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$perseverative_errors_icc[i] = get_icc("perseverative_errors", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$perseverative_responses_icc[i] = get_icc("perseverative_responses", tmp_t1_dvs, tmp_t2_dvs)
-  trial_num_rel_df$total_errors_icc[i] = get_icc("total_errors", tmp_t1_dvs, tmp_t2_dvs)
-}
-rm(i, cur_break, tmp_t1_dvs, tmp_t2_dvs)
-
-trial_num_rel_df$breaks = as.numeric(trial_num_rel_df$breaks)
-
-# write.csv(trial_num_rel_df, paste0(retest_data_path, 'trial_num_rel_df_shift.csv'))
-```
 
@@
 These measures show the different types of relationships reliability estimates have based on the trial numbers used to estimate them.", width = 180))
-
-ggsave('Shift_Task_Intrameasure_Trialnum_Dependendence.tiff', device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in", dpi = 300)
 ```
@@
 ```{r}
-# summary(lmerTest::lmer(icc ~ contrast + (1|dv) ,tmp))
-summary(MCMCglmm(icc ~ contrast, random = ~ dv, data=tmp))
+summary(lmerTest::lmer(icc ~ contrast + (1|dv) ,tmp))
+# summary(MCMCglmm(icc ~ contrast, random = ~ dv, data=tmp, verbose=FALSE))
 ```
@@
 
-```{r}
-ddm_boot_plot = tmp %>%
-  group_by(dv) %>%
-  summarise(mean_icc = mean(icc),
-            raw_fit = unique(raw_fit),
-            contrast = unique(contrast),
-            rt_acc = unique(rt_acc)) %>%
-  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), mean_icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
-  geom_boxplot()+
-  facet_wrap(~factor(contrast, levels=c("non-contrast", "contrast"), labels=c("Non-contrast", "Contrast")))+
-  theme_bw()+
-  ylab("ICC")+
-  xlab("")+
-  theme(legend.title = element_blank(),
-        legend.position = 'bottom',
-        legend.text = element_text(size=16),
-        strip.text = element_text(size=16),
-        axis.text = element_text(size = 16),
-        text = element_text(size=16))+
-  guides(fill = guide_legend(ncol = 2, byrow=F))+
-  scale_fill_brewer(palette="Greys",
-                    breaks=c( "Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))
-
-mylegend<-g_legend(ddm_boot_plot)
-
-grob_name <- names(mylegend$grobs)[1]
-
-#manually fix the legend
-#move non-decision down
-#key
-mylegend$grobs[grob_name][[1]]$layout[11,c(1:4)] <- c(4,8,4,8)
-mylegend$grobs[grob_name][[1]]$layout[12,c(1:4)] <- c(4,8,4,8)
-#text
-mylegend$grobs[grob_name][[1]]$layout[17,c(1:4)] <- c(4,10,4,10)
-#move threshold down
-#key
-mylegend$grobs[grob_name][[1]]$layout[9,c(1:4)] <- c(3,8,3,8)
-mylegend$grobs[grob_name][[1]]$layout[10,c(1:4)] <- c(3,8,3,8)
-#text
-mylegend$grobs[grob_name][[1]]$layout[16,c(1:4)] <- c(3,10,3,10)
-#move drift rate right and up
-#key
-mylegend$grobs[grob_name][[1]]$layout[7,c(1:4)] <- c(2,8,2,8)
-mylegend$grobs[grob_name][[1]]$layout[8,c(1:4)] <- c(2,8,2,8)
-#text
-mylegend$grobs[grob_name][[1]]$layout[15,c(1:4)] <- c(2,10,2,10)
-
-mycaption = textGrob(label = str_wrap("FIGURE 7: Average bootstrapped reliability estimates per measure comparing raw measures and model parameters as well as contrast and non-contrast measures for task measures.", width = 130), gp = gpar(fontfamily="Times", lineheight = 2, fontsize = 18), hjust = 0, vjust = 0.5, x = unit(0, "npc"))
-
-ddm_boot_legend = arrangeGrob(ddm_boot_plot +theme(legend.position="none"),
-             mylegend, mycaption, nrow=3, heights=c(10, 1, 1))
-
-ggsave('Bootstrap_DDM_Comp_Legend.tiff', plot = ddm_boot_legend, device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 14, height = 10, units = "in", limitsize = FALSE, dpi=300)
+```{r echo=FALSE}
+rm(icc_by_rawfit_con_model, icc_by_rawfit_noncon_model)
+```
+
+```{r echo=FALSE, out.width='100%'}
+fig_name = 'Bootstrap_DDM_Comp_Legend.jpeg'
+
+knitr::include_graphics(paste0(fig_path, fig_name))
 ```
@@
 
-```{r}
-tmp2 = measure_labels %>%
-  mutate(dv = as.character(dv),
-         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
-  filter(ddm_task == 1,
-         rt_acc != 'other') %>%
-  drop_na() %>%
-  left_join(rel_df[,c("dv", "icc")], by = 'dv')
-
-ddm_point_plot = tmp2 %>%
-  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
-  geom_boxplot()+
-  facet_wrap(~factor(contrast, levels=c("non-contrast", "contrast"), labels=c("Non-contrast", "Contrast")))+
-  theme_bw()+
-  ylab("ICC")+
-  xlab("")+
-  theme(legend.title = element_blank(),
-        legend.position = 'bottom',
-        legend.text = element_text(size=16),
-        strip.text = element_text(size=16),
-        axis.text = element_text(size = 16),
-        text = element_text(size=16))+
-  guides(fill = guide_legend(ncol = 2))+
-  scale_fill_brewer(palette="Greys",
-                    breaks=c( "Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))+
-  ylim(-0.4, 1)
-
-mylegend<-g_legend(ddm_point_plot)
-
-grob_name <- names(mylegend$grobs)[1]
-
-#manually fix the legend
-#move non-decision down
-#key
-mylegend$grobs[grob_name][[1]]$layout[11,c(1:4)] <- c(4,8,4,8)
-mylegend$grobs[grob_name][[1]]$layout[12,c(1:4)] <- c(4,8,4,8)
-#text
-mylegend$grobs[grob_name][[1]]$layout[17,c(1:4)] <- c(4,10,4,10)
-#move threshold down
-#key
-mylegend$grobs[grob_name][[1]]$layout[9,c(1:4)] <- c(3,8,3,8)
-mylegend$grobs[grob_name][[1]]$layout[10,c(1:4)] <- c(3,8,3,8)
-#text
-mylegend$grobs[grob_name][[1]]$layout[16,c(1:4)] <- c(3,10,3,10)
-#move drift rate right and up
-#key
-mylegend$grobs[grob_name][[1]]$layout[7,c(1:4)] <- c(2,8,2,8)
-mylegend$grobs[grob_name][[1]]$layout[8,c(1:4)] <- c(2,8,2,8)
-#text
-mylegend$grobs[grob_name][[1]]$layout[15,c(1:4)] <- c(2,10,2,10)
-
-ddm_point_legend = arrangeGrob(ddm_point_plot +theme(legend.position="none"),
-             mylegend, nrow=2, heights=c(10, 1))
-
-ggsave('PointEst_DDM_Comp.jpg', plot=ddm_point_legend, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 15, height = 7, units = "in", limitsize = FALSE)
+```{r echo=FALSE, out.width='100%'}
+fig_name = 'PointEst_DDM_Comp.jpeg'
+
+knitr::include_graphics(paste0(fig_path, fig_name))
 ```

### 2018-10-16 code/figure_scripts/Bootstrap_DDM_Comp_Legend.R

@@ -1,0 +1,70 @@
+source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/figure_scripts/figure_res_wrapper.R')
+
+if(!exists('measure_labels')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/measure_labels_data.R')
+}
+
+if(!exists('boot_df')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/boot_rel_data.R')
+}
+
+tmp = measure_labels %>%
+  mutate(dv = as.character(dv),
+         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
+  filter(ddm_task == 1,
+         rt_acc != 'other') %>%
+  drop_na() %>%
+  left_join(boot_df[,c("dv", "icc")], by = 'dv')
+
+ddm_boot_plot = tmp %>%
+  group_by(dv) %>%
+  summarise(mean_icc = mean(icc),
+            raw_fit = unique(raw_fit),
+            contrast = unique(contrast),
+            rt_acc = unique(rt_acc)) %>%
+  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), mean_icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
+  geom_boxplot()+
+  facet_wrap(~factor(contrast, levels=c("non-contrast", "contrast"), labels=c("Non-contrast", "Contrast")))+
+  theme_bw()+
+  ylab("ICC")+
+  xlab("")+
+  theme(legend.title = element_blank(),
+        legend.position = 'bottom',
+        legend.text = element_text(size=16),
+        strip.text = element_text(size=16),
+        axis.text = element_text(size = 16),
+        text = element_text(size=16))+
+  guides(fill = guide_legend(ncol = 2, byrow=F))+
+  scale_fill_brewer(palette="Greys",
[…]

### 2018-10-16 code/figure_scripts/PointEst_DDM_Comp.R

@@ -1,0 +1,77 @@
+source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/figure_scripts/figure_res_wrapper.R')
+
+if(!exists('measure_labels')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/measure_labels_data.R')
+}
+
+if(!exists('rel_df')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/subject_data.R')
+  
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/make_rel_df.R')
+  
+  rel_df = make_rel_df(t1_df = test_data, t2_df = retest_data, metrics = c('spearman', 'icc', 'pearson', 'var_breakdown', 'partial_eta', 'sem'))
+  
+  rel_df$task = 'task'
+  rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
+  rel_df[grep('holt', rel_df$dv), 'task'] = "task"
+  rel_df = rel_df %>%
+    select(dv, task, spearman, icc, pearson, partial_eta, sem, var_subs, var_ind, var_resid)
+}
+
+
+tmp2 = measure_labels %>%
+  mutate(dv = as.character(dv),
+         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
+  filter(ddm_task == 1,
+         rt_acc != 'other') %>%
+  drop_na() %>%
+  left_join(rel_df[,c("dv", "icc")], by = 'dv')
+
+ddm_point_plot = tmp2 %>%
+  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
+  geom_boxplot()+
+  facet_wrap(~factor(contrast, levels=c("non-contrast", "contrast"), labels=c("Non-contrast", "Contrast")))+
+  theme_bw()+
+  ylab("ICC")+
+  xlab("")+
[…]

### 2018-10-16 code/workspace_scripts/intratrial_rel_data.R

@@ -5,4 +5,63 @@
 # t1_dvs = read.csv(paste0(retest_data_path, 't1_shift_dvs.csv'))
 # t2_dvs = read.csv(paste0(retest_data_path, 't2_shift_dvs.csv'))
 
+# t1_dvs = t1_dvs %>% select(-X)
+# t2_dvs = t2_dvs %>% select(-X)
+
+# hr_merge = merge(t1_dvs, t2_dvs, by = c("worker_id", "level_1"))
+# 
+# hr_merge = hr_merge %>%
+#   gather(key, value, -worker_id, -level_1) %>%
+#   separate(key, c("dv", "time"), sep="\\.") %>%
+#   mutate(time = ifelse(time == "x", 1, 2))%>%
+#   rename(sub_id = worker_id,
+#          breaks = level_1)
+# 
+# t1_dvs = hr_merge %>%
+#   filter(time == 1) %>%
+#   select(-time) %>%
+#   spread(dv, value)
+# 
+# t2_dvs = hr_merge %>%
+#   filter(time == 2) %>%
+#   select(-time) %>%
+#   spread(dv, value)
+
+# calculate point estimates for reliability of each of the variables for each break
+# get_retest_stat for each break of tmp_t1_dvs and tmp_t2_dvs
+
+# trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))),
+#                               acc_icc=rep(NA, length(unique(t1_dvs$breaks))),
+#                               avg_rt_icc=rep(NA, length(unique(t1_dvs$breaks))),
+#                               conceptual_responses_icc=rep(NA, length(unique(t1_dvs$breaks))),
+#                               fail_to_maintain_set_icc=rep(NA, length(unique(t1_dvs$breaks))),
+#                               learning_rate_icc=rep(NA, length(unique(t1_dvs$breaks))),
+#                               learning_to_learn_icc=rep(NA, length(unique(t1_dvs$breaks))),
+#                               nonperseverative_errors_icc=rep(NA, length(unique(t1_dvs$breaks))),
+#                               perseverative_errors_icc=rep(NA, length(unique(t1_dvs$breaks))),
[…]

### 2018-10-16 code/SRO_Retest_Analyses.Rmd
rendered new report

@@
 
-```{r}
-tmp_save = tmp_save%>%
-  mutate(task_name = gsub("_", " ", task_name),
-         task_name = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", task_name, perl=TRUE),
-         task_name = gsub("Survey", "", task_name))
-
-names(tmp_save) = gsub("_", " ", names(tmp_save))
-names(tmp_save) = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", names(tmp_save), perl=TRUE)
-
-sjt.df(tmp_save %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/survey_rel_table.doc")
-```
-
 ### Number of items

### 2018-10-16 code/workspace_scripts/battery_completion_data.R

@@ -24,7 +24,7 @@ comp_dates$retest_comp = as.Date(comp_dates$retest_comp)
 comp_dates$test_comp = as.Date(comp_dates$test_comp)
 comp_dates$days_btw = with(comp_dates, retest_comp-test_comp)
 
-rm(test_comp_date, retest_comp_date, comp_dates)
+rm(test_comp_date, retest_comp_date)
 
 ### Completion time data
 

### 2018-12-12 code/analysis_nbs/ResponseToReviewers.Rmd
working on response to reviewers

---
title: 'SRO Retest Response to Reviewers'
output:
github_document:
toc: yes
toc_float: yes
---

```{r}
library(tidyverse)
library(jsonlite)

workspace_scripts = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/'

source(paste0(workspace_scripts,'SRO_Retest_Analyses_Helper_Functions.R'))

test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_03-29-2018/'

retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-29-2018/'

fig_path = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/'

source(paste0(workspace_scripts, 'battery_completion_data.R'))

source(paste0(workspace_scripts,'lit_review_data.R'))

source(paste0(workspace_scripts,'subject_data.R'))

source(paste0(workspace_scripts,'intratrial_rel_data.R'))

source(paste0(workspace_scripts,'demog_data.R'))

source(paste0(workspace_scripts,'boot_rel_data.R'))

source(paste0(workspace_scripts,'rel_comp_data.R'))

source(paste0(workspace_scripts,'duplicate_items_data.R'))

source(paste0(workspace_scripts,'measure_labels_data.R'))

source(paste0(workspace_scripts,'meaningful_vars_data.R'))

source(paste0(workspace_scripts,'bayesian_models_data.R'))
```

#R1

##R1.5
>If the common assumption that threshold and non-decision time do not vary between conditions in tasks with intermixed trials is true, we could interpret the contrasts between those parameters generated from the EZ diffusion model to simply be noise. If that were the case, we shouldn't expect those contrasts to be reliable.

TODO: Check if EZ contrast estimates are >0

```{r}

```

##R1.6
>In our paper, we report ICC(2,1)...

TODO: All results with ICC using ICC(2,1) instead of ICC(3,k)  
- recode `get_retest_stats` to report all kinds of ICCs
- make new `rel_df` (with both types of ICC)
- make new `boot_df` (with both types of ICC)
- rerun MCMC models with ICC(2,1)

```{r}

```

##R1.7
>It is stated on pg. 9 that the ICC ranges from -1 to 1. Though statistical packages report negative ICCs, it is sometimes suggested that they should be treated as zero (e.g. Bartko, 1976), as a proportion of variance cannot theoretically be negative. I am unsure what the best approach is for the current purposes, but I note it for consideration. As there don't appear to be a large number of negative ICCs, I suspect it wouldn't affect the averages much.

TODO:
- report how many negative ICC's there are
- run all analyses that include ICC's with 
  - replacing negative values with 0's 
  - removing them

```{r}

```

##R1.8
>I think it is a strength of the paper overall that the authors consider the importance of trial numbers, though I'm curious why they chose the number of trials they did for their tasks (e.g. if they came from particular studies or an average)? The role of trial numbers was also something we were interested in (see our Supplementary material D: https://link.springer.com/article/10.3758/s13428-017-0935-1#SupplementaryMaterial), and is discussed by Rouder & Haaf (2018).

TODO:
- extract trial numbers for papers that went in to the lit search and compare to ours
- code pipeline to get reliability with k number of trials

```{r}

```

#R2

##R2.1
>The researchers were careful in their sampling procedure to try to minimize differences between participants who completed (vs. did not complete) the retest phase of the test-retest. Some simple statistical comparisons between the completers (N = 157) and non-completers/non-responders (N = 242-157 = 85) would help characterize this subset of the sample better and provide an additional data quality check.

### 2018-12-13 code/analysis_nbs/ResponseToReviewers.Rmd
working on response to reviewers

@@
 
-```{r}
+```{r echo=FALSE, message=FALSE, warning=FALSE}
+from_gh =FALSE
+
 library(tidyverse)
 library(jsonlite)
+
+cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+theme_set(theme_bw())
+ggplot <- function(...) ggplot2::ggplot(...) + scale_fill_manual(values=cbbPalette) + scale_color_manual(values=cbbPalette)+theme(legend.position="bottom")
 
@@
 
-source(paste0(workspace_scripts, 'battery_completion_data.R'))
-
 source(paste0(workspace_scripts,'lit_review_data.R'))
 
-source(paste0(workspace_scripts,'subject_data.R'))
-
-source(paste0(workspace_scripts,'intratrial_rel_data.R'))
-
-source(paste0(workspace_scripts,'demog_data.R'))
-
-source(paste0(workspace_scripts,'boot_rel_data.R'))
-
-source(paste0(workspace_scripts,'rel_comp_data.R'))
-
-source(paste0(workspace_scripts,'duplicate_items_data.R'))
-
-source(paste0(workspace_scripts,'measure_labels_data.R'))
-
-source(paste0(workspace_scripts,'meaningful_vars_data.R'))
-
-source(paste0(workspace_scripts,'bayesian_models_data.R'))
+# source(paste0(workspace_scripts,'subject_data.R'))
+# 
+# source(paste0(workspace_scripts,'boot_rel_data.R'))
+# 
+# source(paste0(workspace_scripts,'measure_labels_data.R'))
 ```
@@
 
-TODO: Check if EZ contrast estimates are >0
+TODO: 
+### Are EZ contrast estimates are >0?
+
+Yes.
+The assumption that thresholds and non-decision times are the same across conditions does not hold in our data as the distributions of these parameters are systematically different than 0 for both time point.
 
 ```{r}
+if(from_gh){
+  eval(parse(text = getURL('https://raw.githubusercontent.com/zenkavi/SRO_DDM_Analyses/master/code/workspace_scripts/g_legend.R', ssl.verifypeer = FALSE)))
+}else{
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_DDM_Analyses/code/workspace_scripts/ddm_subject_data.R')
+}
+```
 
+```{r}
+ez_contrast_vars = measure_labels %>%
+  filter(raw_fit == "EZ" & overall_difference == "contrast") %>%
+  select(dv)
 ```
+
+```{r}
+get_tval = function(x, val=0){
+  return((mean(x, na.rm=T) - val)/(sd(x, na.rm=T)/sqrt(length(x))))
+}
+
+get_mean = function(x){
+  return(mean(x, na.rm=T))
+}
+```
+
+```{r}
+retest_data %>%
+  select(ez_contrast_vars$dv) %>%
+  gather(key, value) %>%
+  group_by(key) %>%
+  summarise(tvals = get_tval(value), 
+            means = get_mean(value))
+```
+
+```{r}
+test_data_522 %>%
+  select(ez_contrast_vars$dv) %>%
+  gather(key, value) %>%
+  group_by(key) %>%
+  summarise(tvals = get_tval(value), 
+            means = get_mean(value))
+```
+
+```{r}
+retest_data %>%
+  select(ez_contrast_vars$dv) %>%
+  mutate(time = "Time 1") %>%
+  bind_rows(test_data %>%
+              select(ez_contrast_vars$dv) %>%
+              mutate(time = "Time 2")) %>%
+  gather(key, value, -time) %>%
+  rename(dv = key) %>%
+  left_join(measure_labels %>% select(dv, rt_acc), by = 'dv') %>%
+  ggplot(aes(value))+
+  geom_density(aes(group=dv, col=rt_acc), linetype="dotted")+
+  geom_density(aes(col=rt_acc), size=2.5)+
+  xlim(-1.5,1.5)+
+  geom_vline(xintercept=0, linetype="dashed", size=1.5)+
+  theme(legend.title=element_blank())+
+  xlab("")+
+  ylab("")+
+  facet_wrap(~time)
+```
+
+### Are their reliabilities >0?
+
+... Although the thresholds and non-decision times for contrasts are >0 they are still not reliable
+
+*Response:* Measures do not have to be noise to be unreliable.
+In our data the EZ thresholds and non-decision times for contrasts are systematically different than 0 suggesting that they capture a systematic difference instead of noise.
+Still these measures are not reliable si
+similar to differences in raw measures of response times and accuracies.
 
@@
 ```{r}
-
+'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_DDM_Analyses/code/workspace_scripts/ddm_measure_labels.R'
 ```

### 2018-12-13 code/workspace_scripts/boot_rel_data.R

@@ -10,7 +10,7 @@ if(!exists('process_boot_df')){
   source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/process_boot_df.R')
 }
 
-if(!retest_report_vars){
+if(!exists('retest_report_vars')){
   tmp1 <- read.csv(paste0(test_data_path,'meaningful_variables.csv'))
   tmp2 <- read.csv(paste0(test_data_path,'meaningful_variables_noDDM.csv'))
   tmp3 <- read.csv(paste0(test_data_path,'meaningful_variables_EZ.csv'))

### 2018-12-13 code/analysis_nbs/ResponseToReviewers.Rmd
working on response to reviewers

@@
 ggplot <- function(...) ggplot2::ggplot(...) + scale_fill_manual(values=cbbPalette) + scale_color_manual(values=cbbPalette)+theme(legend.position="bottom")
-
-workspace_scripts = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/'
-
-source(paste0(workspace_scripts,'SRO_Retest_Analyses_Helper_Functions.R'))
-
-test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_03-29-2018/'
-
-retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-29-2018/'
-
-fig_path = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/'
-
-source(paste0(workspace_scripts,'lit_review_data.R'))
-
-# source(paste0(workspace_scripts,'subject_data.R'))
-# 
-# source(paste0(workspace_scripts,'boot_rel_data.R'))
-# 
-# source(paste0(workspace_scripts,'measure_labels_data.R'))
 ```
@@
 TODO: 
-### Are EZ contrast estimates are >0?
+### Are EZ threshold and non-decision time contrast estimates are >0?
 
@@
 
+Means and and T values comparing the means to 0 for T1 data.
+
 ```{r}
-retest_data %>%
+test_data_522 %>%
   select(ez_contrast_vars$dv) %>%
@@
 
+Means and and T values comparing the means to 0 for T2 data.
+
 ```{r}
-test_data_522 %>%
+retest_data %>%
   select(ez_contrast_vars$dv) %>%
@@
 
+```{r}
+retest_data %>%
+  select(ez_contrast_vars$dv) %>%
+  mutate(time = "Time 1") %>%
+  bind_rows(test_data %>%
+              select(ez_contrast_vars$dv) %>%
+              mutate(time = "Time 2")) %>%
+  gather(key, value, -time) %>%
+  rename(dv = key) %>%
+  left_join(measure_labels %>% select(dv, rt_acc), by = 'dv') %>%
+  group_by(rt_acc, time) %>%
+  summarise(tvals=get_tval(value),
+            means=get_mean(value))
+```
+
 ### Are their reliabilities >0?
@@
 ... Although the thresholds and non-decision times for contrasts are >0 they are still not reliable
+
+```{r}
+rt_ddm_vars = measure_labels %>%
+  filter(overall_difference %in% c("non-contrast", "contrast")) %>%
+  select(dv)
+
+if(from_gh){
+  eval(parse(text = getURL('https://raw.githubusercontent.com/zenkavi/SRO_Retest_Analyses/master/code/helper_functions/make_rel_df.R', ssl.verifypeer = FALSE)))
+}else{
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/make_rel_df.R')
+}
+```
 
@@
 ```{r}
-'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_DDM_Analyses/code/workspace_scripts/ddm_measure_labels.R'
+
 ```

### 2018-12-13 code/helper_functions/get_retest_stats.R

@@ -2,10 +2,14 @@ require(psych)
 require(tidyr)
 
 if(!exists('match_t1_t2')){
-  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/match_t1_t2.R')
+  if(from_gh){
+    eval(parse(text = getURL('https://raw.githubusercontent.com/zenkavi/SRO_DDM_Analyses/master/code/helper_functions/match_t1_t2.R', ssl.verifypeer = FALSE)))
+  }else{
+    source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/match_t1_t2.R')
+  }
 }
 
-get_retest_stats = function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec, metric = c('spearman', 'icc', 'pearson', 'var_breakdown', 'partial_eta', 'sem')){
+get_retest_stats = function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec, metric = c('spearman', 'pearson', 'var_breakdown', 'partial_eta', 'sem', 'icc1.1','icc1.k','icc2.1', 'icc2.k','icc3.1','icc3.k')){
   
   if(sample=='full'){
     df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
@@ -34,11 +38,31 @@ get_retest_stats = function(dv_var, t1_df = test_data, t2_df = retest_data, merg
     out$pearson = cor(df$`1`, df$`2`, method='pearson')
   }
   
-  if('icc' %in% metric | 'var_breakdown' %in% metric){
+  if(sum(c('icc', 'var_breakdown','icc1.1','icc1.k','icc2.1', 'icc2.k','icc3.1','icc3.k') %in% metric) > 0){
     icc = ICC(df %>% select(-dv, -sub_id))
     
-    if('icc' %in% metric){
-      out$icc = icc$results['Average_fixed_raters', 'ICC']
+    if('icc1.1' %in% metric){
+      out$icc1.1 = icc$results['Single_raters_absolute', 'ICC']
+    }
+    
+    if('icc1.k' %in% metric){
+      out$icc1.k = icc$results['Average_raters_absolute', 'ICC']
+    }
+    
+    if('icc2.1' %in% metric){
[…]

### 2018-12-13 code/analysis_nbs/ResponseToReviewers.Rmd
working on response to reviewers

@@
 TODO: All results with ICC using ICC(2,1) instead of ICC(3,k)  
-- recode `get_retest_stats` to report all kinds of ICCs
+- [DONE] recode `get_retest_stats` to report all kinds of ICCs
 - make new `rel_df` (with both types of ICC)

### 2018-12-13 code/SRO_Retest_Analyses.Rmd
working on response to reviewers

@@
   group_by(dv) %>%
-  summarise(median_icc = quantile(icc, probs=0.5),
-            icc_2.5 = quantile(icc, probs = 0.025),
-            icc_97.5 = quantile(icc, probs = 0.975)) %>%
-  arrange(-median_icc)
+  summarise(median_icc3.k = quantile(icc3.k, probs=0.5),
+            icc3.k_2.5 = quantile(icc3.k, probs = 0.025),
+            icc3.k_97.5 = quantile(icc3.k, probs = 0.975)) %>%
+  arrange(-median_icc3.k)
 ```
@@
 ```{r}
-demog_rel_df = make_rel_df(test_demog, t2_df = retest_demog, metrics=c('icc'))
+demog_rel_df = make_rel_df(test_demog, t2_df = retest_demog, metrics=c('icc3.k'))
 
 demog_rel_df %>%
-  select(dv, icc) %>%
-  arrange(-icc)
+  select(dv, icc3.k) %>%
+  arrange(-icc3.k)
 ```
@@
   mutate(timed = ifelse(dv %in% timed_demogs, 1, 0)) %>%
-  ggplot(aes(icc, fill = factor(timed)))+
+  ggplot(aes(icc3.k, fill = factor(timed)))+
   geom_histogram(position = "identity", alpha = 0.7, color = NA)+
-  xlab("ICC")+
+  xlab("icc3.k")+
   ylab("Count")+
@@
   xlab("")+
-  ylab("Mean ICC")+
+  ylab("Mean icc3.k")+
   ylim(-0.4,1)
@@
 r^2 of retest_reliability ~ sampled_reliability vs.
-r^2 of retest_reliability ~ mean_icc
+r^2 of retest_reliability ~ mean_icc3.k
 
 coef of retest_reliability ~ sampled_reliability vs.
-coef of retest_reliability ~ mean_icc
+coef of retest_reliability ~ mean_icc3.k
 
@@
 
-Though we are primarily reporting ICC's as our metric of reliability the results don't change depending on the metric chosen.
-Here we plot point estimates of three different reliability metrics against each other (ICC, Pearson, Spearman).
+Though we are primarily reporting icc3.k's as our metric of reliability the results don't change depending on the metric chosen.
+Here we plot point estimates of three different reliability metrics against each other (icc3.k, Pearson, Spearman).
 The bootstrapped version is essentially the same but the plots are busier due to more datapoints.
@@
 ```{r}
-rel_df = make_rel_df(t1_df = test_data, t2_df = retest_data, metrics = c('spearman', 'icc', 'pearson', 'var_breakdown', 'partial_eta', 'sem'))
+rel_df = make_rel_df(t1_df = test_data, t2_df = retest_data, metrics = c('spearman', 'icc3.k', 'pearson', 'var_breakdown', 'partial_eta', 'sem'))
 
@@
 rel_df = rel_df %>%
-  select(dv, task, spearman, icc, pearson, partial_eta, sem, var_subs, var_ind, var_resid)
+  select(dv, task, spearman, icc3.k, pearson, partial_eta, sem, var_subs, var_ind, var_resid)
 ```
@@
 ```{r}
-cor(rel_df[,c('spearman', 'icc', 'pearson')])
-```
-
-Note: Some variables have <0 ICC's. This would be the case if the $MS_{error}$>$MS_{between}$. Data for these variables have no relationship between the two time points.
+cor(rel_df[,c('spearman', 'icc3.k', 'pearson')])
+```
+
+Note: Some variables have <0 icc3.k's. This would be the case if the $MS_{error}$>$MS_{between}$. Data for these variables have no relationship between the two time points.
 
@@
   group_by(dv) %>%
-  summarise(icc_median = quantile(icc, probs = 0.5),
-            icc_2.5 = quantile(icc, probs = 0.025),
-            icc_97.5 = quantile(icc, probs = 0.975),
+  summarise(icc3.k_median = quantile(icc3.k, probs = 0.5),
+            icc3.k_2.5 = quantile(icc3.k, probs = 0.025),
+            icc3.k_97.5 = quantile(icc3.k, probs = 0.975),
             spearman_median = quantile(spearman, probs = 0.5),
@@
   datatable() %>%
-  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
+  formatRound(columns=c('icc3.k_median', 'icc3.k_2.5', 'icc3.k_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
 ```
@@
   group_by(task) %>%
-  summarise(icc_median = quantile(icc, probs = 0.5),
-            icc_2.5 = quantile(icc, probs = 0.025),
-            icc_97.5 = quantile(icc, probs = 0.975),
+  summarise(icc3.k_median = quantile(icc3.k, probs = 0.5),
+            icc3.k_2.5 = quantile(icc3.k, probs = 0.025),
+            icc3.k_97.5 = quantile(icc3.k, probs = 0.975),
             spearman_median = quantile(spearman, probs = 0.5),
@@
 ```{r eval=FALSE}
-summary(icc_by_task_model)
+summary(icc3.k_by_task_model)
 ```
@@
 ```{r echo=FALSE}
-rm(icc_by_task_model)
+rm(icc3.k_by_task_model)
 ```
@@
 (2017), lies in the difference in sources of variance between these measures.
-Specifically, the ICC is calculated as the ratio of variance between subjects variance to all sources of variance.
+Specifically, the icc3.k is calculated as the ratio of variance between subjects variance to all sources of variance.
 Thus, measures with high between subjects variance would have high test-retest reliability.
@@
          dv %in% meaningful_vars) %>%
-  left_join(boot_df[,c("dv", "icc")], by = 'dv') %>%
+  left_join(boot_df[,c("dv", "icc3.k")], by = 'dv') %>%
   separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
@@
   group_by(task_name) %>%
-  summarise(median_icc = median(icc),
-            icc_2.5 = quantile(icc, probs = 0.025),
-            icc_97.5 = quantile(icc, probs = 0.975),
+  summarise(median_icc3.k = median(icc3.k),
+            icc3.k_2.5 = quantile(icc3.k, probs = 0.025),
+            icc3.k_97.5 = quantile(icc3.k, probs = 0.975),
             num_measures = n()/1000,
             mean_num_trials = round(mean(num_all_trials)))%>%
-  arrange(-median_icc)
+  arrange(-median_icc3.k)
 
@@
   datatable() %>%
-  formatRound(columns=c('median_icc','icc_2.5','icc_97.5'), digits=3)
+  formatRound(columns=c('median_icc3.k','icc3.k_2.5','icc3.k_97.5'), digits=3)
 ```
@@
 
-Does number of items in a task have a significant effect on the average ICC of meaningful measures for all trials from a task? No.
+Does number of items in a task have a significant effect on the average icc3.k of meaningful measures for all trials from a task? No.
 
@@
 
-summary(icc_by_num_trials_model)
+summary(icc3.k_by_num_trials_model)
 ```
@@
 tmp %>%
-  ggplot(aes(num_all_trials, icc))+
+  ggplot(aes(num_all_trials, icc3.k))+
   geom_point()+
@@
   xlab("Number of trials")+
-  ylab("ICC")
+  ylab("icc3.k")
 ```
@@
   drop_na() %>%
-  left_join(boot_df[,c("dv", "icc")], by = 'dv')
+  left_join(boot_df[,c("dv", "icc3.k")], by = 'dv')
 
@@
   group_by(contrast, raw_fit, rt_acc) %>%
-  summarise(icc_median = quantile(icc, probs = 0.5),
-            icc_2.5 = quantile(icc, probs = 0.025),
-            icc_97.5 = quantile(icc, probs = 0.975),
+  summarise(icc3.k_median = quantile(icc3.k, probs = 0.5),
+            icc3.k_2.5 = quantile(icc3.k, probs = 0.025),
+            icc3.k_97.5 = quantile(icc3.k, probs = 0.975),
             num_vars = n()/1000)
@@
   datatable() %>%
-  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5'), digits=3)
+  formatRound(columns=c('icc3.k_median', 'icc3.k_2.5', 'icc3.k_97.5'), digits=3)
 ```
@@
 ```{r}
-summary(lmerTest::lmer(icc ~ contrast + (1|dv) ,tmp))
-# summary(MCMCglmm(icc ~ contrast, random = ~ dv, data=tmp, verbose=FALSE))
+summary(lmerTest::lmer(icc3.k ~ contrast + (1|dv) ,tmp))
+# summary(MCMCglmm(icc3.k ~ contrast, random = ~ dv, data=tmp, verbose=FALSE))
 ```
@@
 ```{r}
-summary(icc_by_rawfit_noncon_model)
+summary(icc3.k_by_rawfit_noncon_model)
 ```
@@
 ```{r}
-summary(icc_by_rawfit_con_model)
+summary(icc3.k_by_rawfit_con_model)
 ```
@@
 ```{r echo=FALSE}
-rm(icc_by_rawfit_con_model, icc_by_rawfit_noncon_model)
+rm(icc3.k_by_rawfit_con_model, icc3.k_by_rawfit_noncon_model)
 ```
@@
   group_by(contrast) %>%
-  summarise(mean_icc = mean(icc),
-            sd_icc = sd(icc))
+  summarise(mean_icc3.k = mean(icc3.k),
+            sd_icc3.k = sd(icc3.k))
 ```
@@
   filter(task == 'survey') %>%
-  left_join(boot_df[,c("dv", "icc")], by = 'dv') %>%
+  left_join(boot_df[,c("dv", "icc3.k")], by = 'dv') %>%
   separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
@@
   datatable() %>%
-  formatRound(columns=c('median_icc', 'icc_2.5','icc_97.5'), digits=3)
+  formatRound(columns=c('median_icc3.k', 'icc3.k_2.5','icc3.k_97.5'), digits=3)
 ```
@@
 
-Does number of items in a survey have a significant effect on the average ICC of survey measures? No.
+Does number of items in a survey have a significant effect on the average icc3.k of survey measures? No.
 
 ```{r warning=FALSE, message=FALSE}
-summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
+summary(lmerTest::lmer(icc3.k ~ num_all_trials + (1|dv), data = tmp))
 ```
@@
   xlab("Number of trials")+
-  ylab("ICC")
-```
+  ylab("icc3.k")
+```

### 2018-12-13 code/helper_functions/make_rel_df.R
working on response to reviewers

@@ -26,7 +26,7 @@ if(!exists('get_numeric_cols')){
 
 make_rel_df = function(t1_df, t2_df, metrics, vars = NA){
 
-  if(vars = NA){
+  if(is.na(vars)){
     numeric_cols = get_numeric_cols(df1 = t1_df, df2 = t2_df)
   }else{
       numeric_cols = vars

### 2018-12-13 code/analysis_nbs/ResponseToReviewers.Rmd
working on response to reviewers

--- 2018-12-13 code/analysis_nbs/ResponseToReviewers.Rmd
@@
 
+rt_ddm_vars = rt_ddm_vars[,1]
+
 if(from_gh){
@@
 
-*Response:* Measures do not have to be noise to be unreliable.
-In our data the EZ thresholds and non-decision times for contrasts are systematically different than 0 suggesting that they capture a systematic difference instead of noise.
-Still these measures are not reliable si
-similar to differences in raw measures of response times and accuracies.
+```{r}
+rel_df = make_rel_df(test_data, retest_data, metrics = c("icc3.k", 'icc2.1'), vars = rt_ddm_vars)
+
+rel_df %>%
+  left_join(measure_labels %>% select("rt_acc", "raw_fit", "dv", "overall_difference"), by = "dv") %>%
+  mutate(overall_difference = factor(overall_difference, levels = c("non-contrast", "contrast"), labels = c("Non-contrast", "Contrast")),
+         raw_fit = factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels = c("Raw", "EZ", "HDDM")),
+         rt_acc = factor(rt_acc, levels = c("drift rate", "threshold", "non-decision", "rt", "accuracy"), labels = c("Drift Rate", "Threshold", "Non-decision", "RT", "Accuracy"))) %>%
+  ggplot(aes(raw_fit, icc2.1, fill=rt_acc))+
+  geom_boxplot()+
+  facet_wrap(~overall_difference)+
+  geom_hline(yintercept=0, linetype="dashed")+
+  guides(fill = guide_legend(nrow=3, byrow=FALSE))+
+  theme(legend.title = element_blank())
+```
+
+```{r}
+rel_df %>%
+  left_join(measure_labels %>% select("rt_acc", "raw_fit", "dv", "overall_difference"), by = "dv") %>%
+  mutate(overall_difference = factor(overall_difference, levels = c("non-contrast", "contrast"), labels = c("Non-contrast", "Contrast")),
+         raw_fit = factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels = c("Raw", "EZ", "HDDM")),
+         rt_acc = factor(rt_acc, levels = c("drift rate", "threshold", "non-decision", "rt", "accuracy"), labels = c("Drift Rate", "Threshold", "Non-decision", "RT", "Accuracy"))) %>%
+  group_by(overall_difference, raw_fit, rt_acc) %>%
+  summarise(mean_icc2.1 = mean(icc2.1),
+            tvals_icc2.1 = get_tval(icc2.1))
+```
+
+*Response:* We thank the reviewer for providing a potential explanation for the low reliability of the EZ threshold and non-decision time variables for contrasts.
+In our data the EZ thresholds and non-decision times for contrasts are systematically different than 0 suggesting that they capture a systematic difference instead of the common assumption of noise.
+Still these contrast measures are much less reliable than non-contrast measures.
+Similar to the constrasts in raw measures of response times and accuracies, which are less reliable than their non-contrast counterparts, measures do not have to be noise to be unreliable.
+Because the assumption fails we chose not to present this possibility in the manuscript.
+The details of our analyses on this question can however be found [on:  https://zenkavi.github.io/SRO_Retest_Analyses/output/reports/ResponseToRevisers.nb.html#R1](https://zenkavi.github.io/SRO_Retest_Analyses/output/reports/ResponseToRevisers.nb.html#R1)
 
@@
 TODO: All results with ICC using ICC(2,1) instead of ICC(3,k)  
-- recode `get_retest_stats` to report all kinds of ICCs
-- make new `rel_df` (with both types of ICC)
-- make new `boot_df` (with both types of ICC)
+- [DONE] recode `get_retest_stats` to report all kinds of ICCs
+- make new `rel_df` (with both types of ICC for retest paper vars)
+- make new `boot_df` (with both types of ICC for retest paper vars)
 - rerun MCMC models with ICC(2,1)
@@
 ```{r}
+rel_df = make_rel_df(test_data, retest_data, metrics = c("icc3.k", 'icc2.1', 'pearson'), vars = rt_ddm_vars)
 
+rel_df %>%
+  gather(key, value, -dv, -icc2.1)%>%
+  ggplot(aes(icc2.1, value))+
+  geom_point()+
+  facet_wrap(~key)+
+  geom_abline(aes(slope=1, intercept=0), linetype="dashed")+
+  xlim(-0.5, 1)+
+  ylim(-0.5, 1)+
+  ylab("")
 ```

### 2018-12-13 code/workspace_scripts/SRO_Retest_Analyses_Helper_Functions.R
working on response to reviewers

@@ -6,40 +6,27 @@ library(stringr)
 library(plotly)
 library(DT)
 library(RecordLinkage)
-library(MCMCglmm)
-library(RCurl)
-
-theme_set(theme_bw())
+# library(MCMCglmm)
 
 render_this <- function(){rmarkdown::render('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Analyses.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, toc_depth = 2, code_folding = 'hide'))}
 
 options(scipen = 1, digits = 4)
 
-if(from_gh){
-  helper_func_path = 'https://raw.githubusercontent.com/zenkavi/SRO_Retest_Analyses/master/code/helper_functions/'
-  
-  eval(parse(text = getURL(paste0(helper_func_path,'g_legend.R'), ssl.verifypeer = FALSE)))
-  eval(parse(text = getURL(paste0(helper_func_path,'g_caption.R'), ssl.verifypeer = FALSE)))
-  eval(parse(text = getURL(paste0(helper_func_path,'sem.R'), ssl.verifypeer = FALSE)))
-  eval(parse(text = getURL(paste0(helper_func_path,'trim.R'), ssl.verifypeer = FALSE)))
-  eval(parse(text = getURL(paste0(helper_func_path,'get_numeric_cols.R'), ssl.verifypeer = FALSE)))
-  eval(parse(text = getURL(paste0(helper_func_path,'match_t1_t2.R'), ssl.verifypeer = FALSE)))
-  eval(parse(text = getURL(paste0(helper_func_path,'get_retest_stats.R'), ssl.verifypeer = FALSE)))
-  eval(parse(text = getURL(paste0(helper_func_path,'process_boot_df.R'), ssl.verifypeer = FALSE)))
-  eval(parse(text = getURL(paste0(helper_func_path,'make_rel_df.R'), ssl.verifypeer = FALSE)))
+file_names = c('g_legend.R', 'g_caption.R', 'sem.R', 'trim.R', 'get_numeric_cols.R', 'match_t1_t2.R', 'get_retest_stats.R', 'process_boot_df.R', 'make_rel_df.R')
 
+if(from_gh){
+  library(RCurl)
[…]

### 2018-12-13 code/workspace_scripts/SRO_Retest_Analyses_Workspace.R

@@ -3,34 +3,37 @@
 library(tidyverse)
 library(jsonlite)
 
-workspace_scripts = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/'
-
-source(paste0(workspace_scripts,'SRO_Retest_Analyses_Helper_Functions.R'))
-
-test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_03-29-2018/'
-
-retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-29-2018/'
-
 fig_path = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/'
 
-source(paste0(workspace_scripts, 'battery_completion_data.R'))
+cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+theme_set(theme_bw())
+ggplot <- function(...) ggplot2::ggplot(...) + scale_fill_manual(values=cbbPalette) + scale_color_manual(values=cbbPalette)+theme(legend.position="bottom")
 
-source(paste0(workspace_scripts,'lit_review_data.R'))
+file_names = c('SRO_Retest_Analyses_Helper_Functions.R', 'battery_completion_data.R', 'lit_review_data.R', 'subject_data.R', 'intratrial_rel_data.R', 'demog_data.R', 'boot_rel_data.R', 'rel_comp_data.R', 'duplicate_items_data.R', 'measure_labels_data.R', 'meaningful_var_data.R', 'bayesian_models_data.R')
 
-source(paste0(workspace_scripts,'subject_data.R'))
+if(from_gh){
+  library(RCurl)
+  
+  workspace_scripts = 'https://raw.githubusercontent.com/zenkavi/SRO_Retest_Analyses/master/code/workspace_scripts/'
+  
+  test_data_path = 'https://raw.githubusercontent.com/zenkavi/Self_Regulation_Ontology/master/Data/Complete_03-29-2018/'
+  
+  retest_data_path = 'https://raw.githubusercontent.com/zenkavi/Self_Regulation_Ontology/master/Data/Retest_03-29-2018/'
+  
+  for(file_name in file_names){
[…]

### 2018-12-13 code/analysis_nbs/ResponseToReviewers.Rmd
working on response to reviewers

@@
 ```{r echo=FALSE, message=FALSE, warning=FALSE}
-from_gh =FALSE
+from_gh=FALSE
+script_loader = function(file, path, remote=from_gh){
+  if(remote){
+    library(RCurl)
+    gh_path = paste('https://raw.githubusercontent.com/zenkavi',
+                     strsplit(path, '/')[[1]][1],
+                     'master',
+                     paste(strsplit(path, '/')[[1]][-1],'/',sep = '', collapse=""),
+                    sep="/")
+    eval(parse(text = getURL(paste0(gh_path, file), ssl.verifypeer = FALSE)))
+  }else{
+    source(paste0('/Users/zeynepenkavi/Dropbox/PoldrackLab/',path, file))
+  }
+}
 
@@
 ggplot <- function(...) ggplot2::ggplot(...) + scale_fill_manual(values=cbbPalette) + scale_color_manual(values=cbbPalette)+theme(legend.position="bottom")
+
+to_keep = c('from_gh',"script_loader", "cbbPalette", "ggplot")
 ```
@@
 ```{r}
-if(from_gh){
-  eval(parse(text = getURL('https://raw.githubusercontent.com/zenkavi/SRO_DDM_Analyses/master/code/workspace_scripts/g_legend.R', ssl.verifypeer = FALSE)))
-}else{
-  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_DDM_Analyses/code/workspace_scripts/ddm_subject_data.R')
-}
+script_loader(file='ddm_subject_data.R', path='SRO_DDM_Analyses/code/workspace_scripts/')
 ```
@@
 
-... Although the thresholds and non-decision times for contrasts are >0 they are still not reliable
+Although the thresholds and non-decision times for contrasts are >0 still have low reliabilities.
 
@@
 
-if(from_gh){
-  eval(parse(text = getURL('https://raw.githubusercontent.com/zenkavi/SRO_Retest_Analyses/master/code/helper_functions/make_rel_df.R', ssl.verifypeer = FALSE)))
-}else{
-  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/make_rel_df.R')
-}
+script_loader(file="make_rel_df.R", path="SRO_Retest_Analyses/code/helper_functions/")
 ```
 
-```{r}
+```{r message=FALSE, warning=FALSE}
 rel_df = make_rel_df(test_data, retest_data, metrics = c("icc3.k", 'icc2.1'), vars = rt_ddm_vars)
@@
 
+```{r echo=FALSE}
+rm(list=setdiff(ls(), to_keep))
+```
+
 ##R1.6
@@
 
+```{r message=FALSE}
+script_loader(file='subject_data.R', path="SRO_Retest_Analyses/code/workspace_scripts/")
+
+script_loader(file='make_rel_df.R', path="SRO_Retest_Analyses/code/helper_functions/")
+
+script_loader(file='measure_labels_data.R', path="SRO_Retest_Analyses/code/workspace_scripts/")
+```
+
 ```{r}
-rel_df = make_rel_df(test_data, retest_data, metrics = c("icc3.k", 'icc2.1', 'pearson'), vars = rt_ddm_vars)
+rel_df = make_rel_df(test_data, retest_data, metrics = c("icc3.k", 'icc2.1', 'pearson', 'spearman'))
+```
 
+```{r}
 rel_df %>%
   gather(key, value, -dv, -icc2.1)%>%
+  left_join(measure_labels %>% select(dv, task),by="dv") %>%
   ggplot(aes(icc2.1, value))+
-  geom_point()+
+  geom_point(aes(col=task))+
   facet_wrap(~key)+
@@
   ylim(-0.5, 1)+
-  ylab("")
+  ylab("")+
+  theme(legend.title = element_blank(),
+        aspect.ratio = 1)
+
+measure_labels %>%
+  arrange(task)
 ```

### 2018-12-13 code/helper_functions/make_rel_df.R

@@ -1,7 +1,6 @@
-library(RCurl)
-
 if(!exists('helper_func_path')){
   if(from_gh){
+    library(RCurl)
     helper_func_path = 'https://raw.githubusercontent.com/zenkavi/SRO_Retest_Analyses/master/code/helper_functions/'
   }else{
     helper_func_path = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/'
@@ -10,6 +9,7 @@ if(!exists('helper_func_path')){
 
 if(!exists('get_retest_stats')){
   if(from_gh){
+    library(RCurl)
     eval(parse(text = getURL(paste0(helper_func_path,'get_retest_stats.R'), ssl.verifypeer = FALSE)))
   }else{
     source(paste0(helper_func_path, 'get_retest_stats.R'))
@@ -18,6 +18,7 @@ if(!exists('get_retest_stats')){
 
 if(!exists('get_numeric_cols')){
   if(from_gh){
+    library(RCurl)
     eval(parse(text = getURL(paste0(helper_func_path,'get_numeric_cols.R'), ssl.verifypeer = FALSE)))
   }else{
     source(paste0(helper_func_path, 'get_numeric_cols.R'))

### 2018-12-14 code/analysis_nbs/ResponseToReviewers.Rmd
working on response to reviewers

@@
 - [DONE] recode `get_retest_stats` to report all kinds of ICCs
-- make new `rel_df` (with both types of ICC for retest paper vars)
+- [DONE] make new `rel_df` (with both types of ICC for retest paper vars)
 - make new `boot_df` (with both types of ICC for retest paper vars)
@@
 
-```{r}
+```{r message=FALSE}
 rel_df %>%
@@
         aspect.ratio = 1)
-
-measure_labels %>%
-  arrange(task)
 ```

### 2018-12-17 code/SRO_Retest_Analyses.Rmd
working on response to reviewers

@@
 ```{r, message=FALSE, warning=FALSE, include=FALSE}
+from_gh = TRUE
 source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/SRO_Retest_Analyses_Workspace.R')

### 2018-12-17 code/workspace_scripts/SRO_Retest_Analyses_Helper_Functions.R

@@ -15,16 +15,16 @@ options(scipen = 1, digits = 4)
 file_names = c('g_legend.R', 'g_caption.R', 'sem.R', 'trim.R', 'get_numeric_cols.R', 'match_t1_t2.R', 'get_retest_stats.R', 'process_boot_df.R', 'make_rel_df.R')
 
 if(from_gh){
-  library(RCurl)
+  require(RCurl)
   helper_func_path = 'https://raw.githubusercontent.com/zenkavi/SRO_Retest_Analyses/master/code/helper_functions/'
   for(file_name in file_names){
-    eval(parse(text = getURL(paste0(workspace_scripts,file_name), ssl.verifypeer = FALSE)))
+    eval(parse(text = getURL(paste0(helper_func_path,file_name), ssl.verifypeer = FALSE)))
   }
   
 } else{
   helper_func_path = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/' 
   for(file_name in file_names){
-    source(paste0(workspace_scripts,file_name))
+    source(paste0(helper_func_path,file_name))
   }
 }
 

### 2018-12-18 code/analysis_nbs/ResponseToReviewers.Rmd
working on reviewer responses

@@
 from_gh=FALSE
-script_loader = function(file, path, remote=from_gh){
+script_loader = function(file, path, remote=from_gh, branch="master"){
   if(remote){
@@
                      strsplit(path, '/')[[1]][1],
-                     'master',
+                     branch,
                      paste(strsplit(path, '/')[[1]][-1],'/',sep = '', collapse=""),

### 2018-12-18 code/SRO_Retest_Analyses.Rmd
working on reviewer responses

--- 2018-10-16 code/SRO_Retest_Analyses.Rmd
@@
   group_by(dv) %>%
-  summarise(median_icc = quantile(icc, probs=0.5),
-            icc_2.5 = quantile(icc, probs = 0.025),
-            icc_97.5 = quantile(icc, probs = 0.975)) %>%
-  arrange(-median_icc)
+  summarise(median_icc2.1 = quantile(icc2.1, probs=0.5),
+            icc2.1_2.5 = quantile(icc2.1, probs = 0.025),
+            icc2.1_97.5 = quantile(icc2.1, probs = 0.975)) %>%
+  arrange(-median_icc2.1)
 ```
@@
 ```{r}
-demog_rel_df = make_rel_df(test_demog, t2_df = retest_demog, metrics=c('icc'))
+demog_rel_df = make_rel_df(test_demog, t2_df = retest_demog, metrics=c('icc2.1'))
 
 demog_rel_df %>%
-  select(dv, icc) %>%
-  arrange(-icc)
+  select(dv, icc2.1) %>%
+  arrange(-icc2.1)
 ```
@@
   mutate(timed = ifelse(dv %in% timed_demogs, 1, 0)) %>%
-  ggplot(aes(icc, fill = factor(timed)))+
+  ggplot(aes(icc2.1, fill = factor(timed)))+
   geom_histogram(position = "identity", alpha = 0.7, color = NA)+
-  xlab("ICC")+
+  xlab("icc2.1")+
   ylab("Count")+
@@
 for(i in 1:length(numeric_cols)){
-  tmp = match_t1_t2(numeric_cols[i],format='wide')
+  tmp = match_t1_t2(numeric_cols[i],t1_df=test_data ,t2_df=retest_data,format='wide')
   tmp = tmp %>%
@@
 
-```{r}
+```{r message=FALSE}
 tmp = duplicate_items %>%
@@
 ```{r eval=FALSE, echo=FALSE}
-summary(MCMCglmm(value ~ key*scale(similarity), data=tmp, nitt = 50000))
+# summary(MCMCglmm(value ~ key*scale(similarity), data=tmp, nitt = 50000))
 ```
@@
 summary(rel_comp$sample_size[rel_comp$task == "task"])
-
+```
+
+```{r}
 rel_comp %>%
@@
   xlab("")+
-  ylab("Mean ICC")+
+  ylab("Mean icc2.1")+
   ylim(-0.4,1)
@@
 
-lit_emp_cor_out = plyr::rdply(100, lit_emp_cor)
-
-write.csv(lit_emp_cor_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/lit_emp_cor_out.csv')
+# lit_emp_cor_out = plyr::rdply(100, lit_emp_cor)
+
+# write.csv(lit_emp_cor_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/lit_emp_cor_out.csv')
 ```
@@
 r^2 of retest_reliability ~ sampled_reliability vs.
-r^2 of retest_reliability ~ mean_icc
+r^2 of retest_reliability ~ mean_icc2.1
 
 coef of retest_reliability ~ sampled_reliability vs.
-coef of retest_reliability ~ mean_icc
+coef of retest_reliability ~ mean_icc2.1
 
@@
 
-comp_lit_pred_out = plyr::rdply(1000, comp_lit_pred(rel_comp))
-
-write.csv(comp_lit_pred_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/comp_lit_pred_out.csv')
+# comp_lit_pred_out = plyr::rdply(1000, comp_lit_pred(rel_comp))
+
+# write.csv(comp_lit_pred_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/comp_lit_pred_out.csv')
 ```
@@
 
-Though we are primarily reporting ICC's as our metric of reliability the results don't change depending on the metric chosen.
-Here we plot point estimates of three different reliability metrics against each other (ICC, Pearson, Spearman).
+Though we are primarily reporting icc2.1's as our metric of reliability the results don't change depending on the metric chosen.
+Here we plot point estimates of three different reliability metrics against each other (icc2.1, Pearson, Spearman).
 The bootstrapped version is essentially the same but the plots are busier due to more datapoints.
@@
 ```{r}
-rel_df = make_rel_df(t1_df = test_data, t2_df = retest_data, metrics = c('spearman', 'icc', 'pearson', 'var_breakdown', 'partial_eta', 'sem'))
+rel_df = make_rel_df(t1_df = test_data, t2_df = retest_data, metrics = c('spearman', 'icc2.1','icc3.k', 'pearson', 'var_breakdown', 'partial_eta', 'sem'))
 
@@
 rel_df = rel_df %>%
-  select(dv, task, spearman, icc, pearson, partial_eta, sem, var_subs, var_ind, var_resid)
+  select(dv, task, spearman, icc2.1,icc3.k, pearson, partial_eta, sem, var_subs, var_ind, var_resid)
 ```
@@
 ```{r}
-cor(rel_df[,c('spearman', 'icc', 'pearson')])
-```
-
-Note: Some variables have <0 ICC's. This would be the case if the $MS_{error}$>$MS_{between}$. Data for these variables have no relationship between the two time points.
+cor(rel_df[,c('spearman', 'icc2.1', 'icc3.k', 'pearson')])
+```
+
+Note: Some variables have <0 icc2.1's. This would be the case if the $MS_{error}$>$MS_{between}$. Data for these variables have no relationship between the two time points.
 
@@
   group_by(dv) %>%
-  summarise(icc_median = quantile(icc, probs = 0.5),
-            icc_2.5 = quantile(icc, probs = 0.025),
-            icc_97.5 = quantile(icc, probs = 0.975),
+  summarise(icc2.1_median = quantile(icc2.1, probs = 0.5),
+            icc2.1_2.5 = quantile(icc2.1, probs = 0.025),
+            icc2.1_97.5 = quantile(icc2.1, probs = 0.975),
             spearman_median = quantile(spearman, probs = 0.5),
@@
   datatable() %>%
-  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
+  formatRound(columns=c('icc2.1_median', 'icc2.1_2.5', 'icc2.1_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
 ```
@@
   group_by(task) %>%
-  summarise(icc_median = quantile(icc, probs = 0.5),
-            icc_2.5 = quantile(icc, probs = 0.025),
-            icc_97.5 = quantile(icc, probs = 0.975),
+  summarise(icc2.1_median = quantile(icc2.1, probs = 0.5),
+            icc2.1_2.5 = quantile(icc2.1, probs = 0.025),
+            icc2.1_97.5 = quantile(icc2.1, probs = 0.975),
             spearman_median = quantile(spearman, probs = 0.5),
@@
 ```{r eval=FALSE}
-summary(icc_by_task_model)
+summary(icc2.1_by_task_model)
 ```
@@
 
+```{r}
+summary(MCMCglmm(icc2.1 ~ task, data=rel_df, verbose=F))
+```
+
 ### Variance breakdown
@@
 (2017), lies in the difference in sources of variance between these measures.
-Specifically, the ICC is calculated as the ratio of variance between subjects variance to all sources of variance.
+Specifically, the icc2.1 is calculated as the ratio of variance between subjects variance to all sources of variance.
 Thus, measures with high between subjects variance would have high test-retest reliability.
@@
 
-summary(var_subs_pct_by_task_model)
+# summary(var_subs_pct_by_task_model)
+
+rel_df = rel_df %>% 
+  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
+                             var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100,
+                             var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100)
+
+summary(MCMCglmm(var_subs_pct ~ task, data=rel_df, verbose=F))
 ```
@@
 ```{r}
-summary(var_ind_pct_by_task_model)
-```
-
-```{r}
-summary(var_resid_pct_by_task_model)
+# summary(var_ind_pct_by_task_model)
+
+summary(MCMCglmm(var_ind_pct ~ task, data=rel_df, verbose=F))
+```
+
+```{r}
+# summary(var_resid_pct_by_task_model)
+
+summary(MCMCglmm(var_resid_pct ~ task, data=rel_df, verbose=F))
 ```
@@
 ```
+
 ## Task Reliabilities
@@
          dv %in% meaningful_vars) %>%
-  left_join(boot_df[,c("dv", "icc")], by = 'dv') %>%
+  left_join(boot_df[,c("dv", "icc2.1")], by = 'dv') %>%
   separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
@@
   group_by(task_name) %>%
-  summarise(median_icc = median(icc),
-            icc_2.5 = quantile(icc, probs = 0.025),
-            icc_97.5 = quantile(icc, probs = 0.975),
+  summarise(median_icc2.1 = median(icc2.1),
+            icc2.1_2.5 = quantile(icc2.1, probs = 0.025),
+            icc2.1_97.5 = quantile(icc2.1, probs = 0.975),
             num_measures = n()/1000,
             mean_num_trials = round(mean(num_all_trials)))%>%
-  arrange(-median_icc)
+  arrange(-median_icc2.1)
 
@@
   datatable() %>%
-  formatRound(columns=c('median_icc','icc_2.5','icc_97.5'), digits=3)
+  formatRound(columns=c('median_icc2.1','icc2.1_2.5','icc2.1_97.5'), digits=3)
 ```
@@
 
-Does number of items in a task have a significant effect on the average ICC of meaningful measures for all trials from a task? No.
+Does number of items in a task have a significant effect on the average icc2.1 of meaningful measures for all trials from a task? No.
 
@@
          dv %in% meaningful_vars) %>%
-  left_join(boot_df[,c("dv", "icc")], by = 'dv') %>%
+  # left_join(boot_df[,c("dv", "icc2.1")], by = 'dv') %>%
+  left_join(rel_df[,c("dv", "icc2.1")], by = 'dv') %>%
   separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
@@
 
-summary(icc_by_num_trials_model)
+#summary(icc2.1_by_num_trials_model)
+summary(MCMCglmm(icc2.1 ~ num_all_trials, data=tmp, verbose=F))
 ```
@@
 tmp %>%
-  ggplot(aes(num_all_trials, icc))+
+  ggplot(aes(num_all_trials, icc2.1))+
   geom_point()+
@@
   xlab("Number of trials")+
-  ylab("ICC")
+  ylab("icc2.1")
 ```
@@
   drop_na() %>%
-  left_join(boot_df[,c("dv", "icc")], by = 'dv')
+  # left_join(boot_df[,c("dv", "icc2.1")], by = 'dv')
+  left_join(rel_df[,c("dv", "icc2.1")], by = 'dv')
 
@@
   group_by(contrast, raw_fit, rt_acc) %>%
-  summarise(icc_median = quantile(icc, probs = 0.5),
-            icc_2.5 = quantile(icc, probs = 0.025),
-            icc_97.5 = quantile(icc, probs = 0.975),
+  summarise(icc2.1_median = quantile(icc2.1, probs = 0.5),
+            icc2.1_2.5 = quantile(icc2.1, probs = 0.025),
+            icc2.1_97.5 = quantile(icc2.1, probs = 0.975),
             num_vars = n()/1000)
@@
   datatable() %>%
-  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5'), digits=3)
+  formatRound(columns=c('icc2.1_median', 'icc2.1_2.5', 'icc2.1_97.5'), digits=3)
 ```
@@
 ```{r}
-summary(lmerTest::lmer(icc ~ contrast + (1|dv) ,tmp))
-# summary(MCMCglmm(icc ~ contrast, random = ~ dv, data=tmp, verbose=FALSE))
+# summary(lmerTest::lmer(icc2.1 ~ contrast + (1|dv) ,tmp))
+# summary(MCMCglmm(icc2.1 ~ contrast, random = ~ dv, data=tmp, verbose=FALSE))
+summary(MCMCglmm(icc2.1 ~ contrast, data=tmp, verbose=FALSE))
 ```
@@
 ```{r}
-summary(icc_by_rawfit_noncon_model)
+# summary(icc2.1_by_rawfit_noncon_model)
+summary(MCMCglmm(icc2.1 ~ raw_fit, data=tmp %>% filter(contrast == "non-contrast"), verbose=FALSE))
 ```
@@
 ```{r}
-summary(icc_by_rawfit_con_model)
+# summary(icc2.1_by_rawfit_con_model)
+summary(MCMCglmm(icc2.1 ~ raw_fit, data=tmp %>% filter(contrast == "contrast"), verbose=FALSE))
 ```
@@
   group_by(contrast) %>%
-  summarise(mean_icc = mean(icc),
-            sd_icc = sd(icc))
+  summarise(mean_icc2.1 = mean(icc2.1),
+            sd_icc2.1 = sd(icc2.1))
 ```
@@
   filter(task == 'survey') %>%
-  left_join(boot_df[,c("dv", "icc")], by = 'dv') %>%
+  # left_join(boot_df[,c("dv", "icc2.1")], by = 'dv') %>%
+  left_join(rel_df[,c("dv", "icc2.1")], by = 'dv') %>%
   separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
@@
   datatable() %>%
-  formatRound(columns=c('median_icc', 'icc_2.5','icc_97.5'), digits=3)
+  formatRound(columns=c('median_icc2.1', 'icc2.1_2.5','icc2.1_97.5'), digits=3)
 ```
@@
 
-Does number of items in a survey have a significant effect on the average ICC of survey measures? No.
+Does number of items in a survey have a significant effect on the average icc2.1 of survey measures? No.
 
 ```{r warning=FALSE, message=FALSE}
-summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
+# summary(lmerTest::lmer(icc2.1 ~ num_all_trials + (1|dv), data = tmp))
+summary(MCMCglmm(icc2.1 ~ num_all_trials, data=tmp, verbose=FALSE))
 ```
@@
   xlab("Number of trials")+
-  ylab("ICC")
-```
+  ylab("icc2.1")
+```

### 2018-12-18 code/figure_scripts/Boot_w_trialinfo.R

@@ -26,7 +26,7 @@ meaningful_vars = sort(meaningful_vars)
 
 tmp = measure_labels %>%
   mutate(dv = as.character(dv)) %>%
-  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')
+  left_join(boot_df[,c("dv", "icc2.1", "spearman")], by = 'dv')
 
 tmp = tmp %>%
   separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
@@ -37,8 +37,8 @@ tmp = tmp %>%
   arrange(task_group, var)
 
 tmp = tmp %>%
-  left_join(rel_df[,c("dv", "icc")], by = "dv") %>%
-  rename(icc = icc.x, point_est = icc.y)
+  left_join(rel_df[,c("dv", "icc2.1")], by = "dv") %>%
+  rename(icc2.1 = icc2.1.x, point_est = icc2.1.y)
 
 #Manual correction
 tmp = tmp %>%
@@ -74,7 +74,7 @@ tmp_mngfl = tmp_mngfl %>%
 
 p4_t <- tmp_mngfl %>%
   filter(task == 'task') %>%
-  ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) +
+  ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc2.1)) +
   geom_violin(fill='#00BFC4')+
   theme_bw() +
   theme(axis.text = element_text(size=30))+
@@ -114,7 +114,7 @@ ggsave(paste0('Task_Boot_w_trialinfo.', out_device), plot = boot_task_plot, devi
 
 p5_t <- tmp %>%
   filter(task == 'survey') %>%
-  ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) +
+  ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc2.1)) +
   geom_violin(fill='#F8766D')+
   theme_bw() +
   theme(axis.text = element_text(size=30))+

### 2018-12-18 code/figure_scripts/Bootstrap_DDM_Comp_Legend.R

@@ -14,19 +14,19 @@ tmp = measure_labels %>%
   filter(ddm_task == 1,
          rt_acc != 'other') %>%
   drop_na() %>%
-  left_join(boot_df[,c("dv", "icc")], by = 'dv')
+  left_join(boot_df[,c("dv", "icc2.1")], by = 'dv')
 
 ddm_boot_plot = tmp %>%
   group_by(dv) %>%
-  summarise(mean_icc = mean(icc),
+  summarise(mean_icc2.1 = mean(icc2.1),
             raw_fit = unique(raw_fit),
             contrast = unique(contrast),
             rt_acc = unique(rt_acc)) %>%
-  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), mean_icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
+  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), mean_icc2.1, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
   geom_boxplot()+
   facet_wrap(~factor(contrast, levels=c("non-contrast", "contrast"), labels=c("Non-contrast", "Contrast")))+
   theme_bw()+
-  ylab("ICC")+
+  ylab("icc2.1")+
   xlab("")+
   theme(legend.title = element_blank(),
         legend.position = 'bottom',

### 2018-12-18 code/figure_scripts/Bootstrap_Example_Plot_t.R

@@ -17,7 +17,7 @@ tmp = tmp[-grep('survey', tmp)]
 
 tmp = measure_labels %>%
   mutate(dv = as.character(dv)) %>%
-  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')
+  left_join(boot_df[,c("dv", "icc2.1", "spearman")], by = 'dv')
 
 tmp = tmp %>%
   separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
@@ -28,8 +28,8 @@ tmp = tmp %>%
   arrange(task_group, var)
 
 tmp = tmp %>%
-  left_join(rel_df[,c("dv", "icc")], by = "dv") %>%
-  rename(icc = icc.x, point_est = icc.y)
+  left_join(rel_df[,c("dv", "icc2.1")], by = "dv") %>%
+  rename(icc2.1 = icc2.1.x, point_est = icc2.1.y)
 
 #Manual correction
 tmp = tmp %>%
@@ -42,7 +42,7 @@ tmp = tmp %>%
 
 p1<- tmp %>%
   filter(grepl('selection_optimization', dv)) %>%
-  ggplot(aes(x = var, y = icc)) +
+  ggplot(aes(x = var, y = icc2.1)) +
   geom_violin(fill='#F8766D')+
   theme_bw() +
   theme(axis.text.y = element_text(size=30))+
@@ -55,7 +55,7 @@ p1<- tmp %>%
 
 p2<- tmp %>%
   filter(grepl('selection_optimization', dv)) %>%
-  ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc, group=dv)) +
+  ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc2.1, group=dv)) +
   geom_violin(fill='#F8766D', position = 'identity')+
   theme_bw() +
   theme(axis.text.y = element_text(size=30))+
@@ -68,7 +68,7 @@ p2<- tmp %>%
 
 p3<- tmp %>%
   filter(grepl('selection_optimization', dv)) %>%
-  ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) +
+  ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc2.1)) +
   geom_violin(fill='#F8766D', position = 'identity')+
   theme_bw() +
   theme(axis.text.y = element_text(size=30))+

### 2018-12-18 code/figure_scripts/Bootstrap_Raw_Var_Plot.R

@@ -17,7 +17,7 @@ tmp = tmp[-grep('survey', tmp)]
 
 tmp = measure_labels %>%
   mutate(dv = as.character(dv)) %>%
-  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')
+  left_join(boot_df[,c("dv", "icc2.1", "spearman")], by = 'dv')
 
 tmp = tmp %>%
   separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
@@ -28,8 +28,8 @@ tmp = tmp %>%
   arrange(task_group, var)
 
 tmp = tmp %>%
-  left_join(rel_df[,c("dv", "icc")], by = "dv") %>%
-  rename(icc = icc.x, point_est = icc.y)
+  left_join(rel_df[,c("dv", "icc2.1")], by = "dv") %>%
+  rename(icc2.1 = icc2.1.x, point_est = icc2.1.y)
 
 #Manual correction
 tmp = tmp %>%
@@ -43,7 +43,7 @@ tmp = tmp %>%
 p4 <- tmp %>%
   filter(task == 'task',
          raw_fit == 'raw') %>%
-  ggplot(aes(y = var, x = icc)) +
+  ggplot(aes(y = var, x = icc2.1)) +
   geom_point(color = '#00BFC4')+
   geom_point(aes(y = var, x = point_est), color = "black")+
   facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y", labeller = label_wrap_gen(width=20)) +
@@ -61,7 +61,7 @@ p4 <- tmp %>%
 
 p5 <- tmp %>%
   filter(task == 'survey') %>%
-  ggplot(aes(y = var, x = icc)) +
+  ggplot(aes(y = var, x = icc2.1)) +
   geom_point(color = '#F8766D')+
   geom_point(aes(y = var, x = point_est), color = "black")+
   facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y", labeller = label_wrap_gen(width=20)) +

### 2018-12-18 code/figure_scripts/LitAndBoot_Noise_Ceiling.R

@@ -1,14 +1,31 @@
+if(from_gh){
+  require(RCurl)
+}
+
 source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/figure_scripts/figure_res_wrapper.R')
 
 if(!exists('g_legend')){
-  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/g_legend.R')
+  if(from_gh){
+    eval(parse(text = getURL('https://raw.githubusercontent.com/zenkavi/SRO_Retest_Analyses/master/code/helper_functions/g_legend.R', ssl.verifypeer = FALSE)))
+  }else{
+    source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/g_legend.R')
+  }
+  
 }
 
 if(!exists('g_caption')){
-  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/g_caption.R')
+  if(from_gh){
+    eval(parse(text = getURL('https://raw.githubusercontent.com/zenkavi/SRO_Retest_Analyses/master/code/helper_functions/g_caption.R', ssl.verifypeer = FALSE)))
+  }else{
+    source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/g_caption.R')
+  }
 }
 
-comp_lit_pred_out = read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/comp_lit_pred_out.csv')
+if(!exists('comp_lit_pred_out')){
+  comp_lit_pred_out = read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/comp_lit_pred_out.csv')
+  
+}
+
 
 tmp = comp_lit_pred_out %>%
   select(-.n, -m_lit, -m_boot, -X) %>%

### 2018-12-18 code/figure_scripts/Metric_Scatterplots.R

@@ -5,7 +5,7 @@ if(!exists('rel_df')){
   
   source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/make_rel_df.R')
   
-  rel_df = make_rel_df(t1_df = test_data, t2_df = retest_data, metrics = c('spearman', 'icc', 'pearson', 'var_breakdown', 'partial_eta', 'sem'))
+  rel_df = make_rel_df(t1_df = test_data, t2_df = retest_data, metrics = c('spearman', 'icc2.1','icc3.k', 'pearson', 'var_breakdown', 'partial_eta', 'sem'))
   
   rel_df$task = 'task'
   rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
@@ -15,7 +15,7 @@ if(!exists('rel_df')){
 }
 
 p1 = rel_df %>%
-  ggplot(aes(spearman, icc, col=task))+
+  ggplot(aes(spearman, icc2.1, col=task))+
   geom_point()+
   theme_bw()+
   theme(legend.title = element_blank(),
@@ -23,7 +23,7 @@ p1 = rel_df %>%
   geom_abline(intercept = 0, slope=1)
 
 p2 = rel_df %>%
-  ggplot(aes(pearson, icc, col=task))+
+  ggplot(aes(pearson, icc2.1, col=task))+
   geom_point()+
   theme_bw()+
   theme(legend.title = element_blank(),
@@ -38,6 +38,30 @@ p3 = rel_df %>%
         legend.position = "none")+
   geom_abline(intercept = 0, slope=1)
 
-ggsave(paste0('Metric_Scatterplots.',out_device), plot = grid.arrange(p1, p2, p3, nrow=1), device = out_device, path = fig_path, width = 12, height = 4, units = "in", dpi=img_dpi)
+p4 = rel_df %>%
+  ggplot(aes(spearman, icc3.k, col=task))+
+  geom_point()+
+  theme_bw()+
+  theme(legend.title = element_blank(),
+        legend.position = "none")+
+  geom_abline(intercept = 0, slope=1)
 
-rm(p1,p2,p3)
+p5 = rel_df %>%
+  ggplot(aes(pearson, icc3.k, col=task))+
+  geom_point()+
+  theme_bw()+
+  theme(legend.title = element_blank(),
+        legend.position = "none")+
+  geom_abline(intercept = 0, slope=1)
+
[…]

### 2018-12-18 code/figure_scripts/PointEst_DDM_Comp.R

@@ -9,13 +9,13 @@ if(!exists('rel_df')){
   
   source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/make_rel_df.R')
   
-  rel_df = make_rel_df(t1_df = test_data, t2_df = retest_data, metrics = c('spearman', 'icc', 'pearson', 'var_breakdown', 'partial_eta', 'sem'))
+  rel_df = make_rel_df(t1_df = test_data, t2_df = retest_data, metrics = c('spearman', 'icc2.1', 'pearson', 'var_breakdown', 'partial_eta', 'sem'))
   
   rel_df$task = 'task'
   rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
   rel_df[grep('holt', rel_df$dv), 'task'] = "task"
   rel_df = rel_df %>%
-    select(dv, task, spearman, icc, pearson, partial_eta, sem, var_subs, var_ind, var_resid)
+    select(dv, task, spearman, icc2.1, pearson, partial_eta, sem, var_subs, var_ind, var_resid)
 }
 
 
@@ -25,14 +25,14 @@ tmp2 = measure_labels %>%
   filter(ddm_task == 1,
          rt_acc != 'other') %>%
   drop_na() %>%
-  left_join(rel_df[,c("dv", "icc")], by = 'dv')
+  left_join(rel_df[,c("dv", "icc2.1")], by = 'dv')
 
 ddm_point_plot = tmp2 %>%
-  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
+  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc2.1, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
   geom_boxplot()+
[…]

### 2018-12-18 code/workspace_scripts/SRO_Retest_Analyses_Helper_Functions.R

@@ -3,10 +3,9 @@ library(lme4)
 library(GGally)
 library(rmarkdown)
 library(stringr)
-library(plotly)
 library(DT)
 library(RecordLinkage)
-# library(MCMCglmm)
+library(MCMCglmm)
 
 render_this <- function(){rmarkdown::render('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Analyses.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, toc_depth = 2, code_folding = 'hide'))}
 

### 2018-12-18 code/workspace_scripts/bayesian_models_data.R

@@ -2,45 +2,17 @@
 #########################
 ## Bayesian models ####
 #########################
-# tmp = boot_df %>%
-#   select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct)
 
-#summary(lmerTest::lmer(icc ~  task + (1|dv), boot_df))
-# m = MCMCglmm(icc ~  task, random = ~dv, data=boot_df, nitt = 1300, burnin = 300)
 icc_by_task_model = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_task_model.rds')
 
-
-# summary(lmerTest::lmer(var_subs_pct~task+(1|dv),tmp%>%select(-var_ind_pct,-var_resid_pct)))
 var_subs_pct_by_task_model = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_subs_pct_by_task_model.rds')
 
-# summary(lmerTest::lmer(var_ind_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_resid_pct)))
 var_ind_pct_by_task_model = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_ind_pct_by_task_model.rds')
 
-# summary(lmerTest::lmer(var_resid_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_ind_pct)))
 var_resid_pct_by_task_model = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_resid_pct_by_task_model.rds')
 
-# tmp = measure_labels %>%
-#   mutate(dv = as.character(dv)) %>%
-#   filter(task == 'task',
-#          dv %in% meaningful_vars) %>%
-#   left_join(boot_df[,c("dv", "icc")], by = 'dv') %>%
-#   separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
-#   select(-extra_1, -extra_2)
-
-# summary(lm(icc ~ num_all_trials, data = tmp))
-# summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
[…]

### 2018-12-18 code/workspace_scripts/boot_rel_data.R

@@ -97,10 +97,11 @@ rm(refit_boot_df)
 boot_df = boot_df %>% mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
                              var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100,
                              var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100)
-# 
+
 # var_boot_df = boot_df %>%
 #   group_by(dv) %>%
-#   summarise(mean_icc = mean(icc),
+#   summarise(mean_icc2.1 = mean(icc2.1),
+#             mean_icc3.k = mean(icc3.k),
 #             mean_pearson = mean(pearson))
 # 
 # rel_comp = lit_review %>%

### 2018-12-18 code/analysis_nbs/ResponseToReviewers.Rmd
rendered new report

@@
 - [DONE] make new `rel_df` (with both types of ICC for retest paper vars)
-- make new `boot_df` (with both types of ICC for retest paper vars)
-- rerun MCMC models with ICC(2,1)
+- [DONE] make new `boot_df` (with both types of ICC for retest paper vars)
+- [DONE] rerun MCMC models with ICC(2,1)
+- [DONE] run SRO_Retest_Analyses.Rmd with ICC(2,1) and confirm results don't change
+- [DONE] replace fig S3 with new metric scatterplot including icc(2,1)
+- [DONE] replace all ICC(3,k)'s in main text
 

### 2018-12-18 code/SRO_Retest_Analyses.Rmd
rendered new report

@@
 ```{r, message=FALSE, warning=FALSE, include=FALSE}
+set.seed(10394839)
 from_gh = TRUE
@@
             icc2.1_2.5 = quantile(icc2.1, probs = 0.025),
-            icc2.1_97.5 = quantile(icc2.1, probs = 0.975),
-            num_vars = n()/1000)
+            icc2.1_97.5 = quantile(icc2.1, probs = 0.975))
+            # num_vars = n()/1000)
 

### 2018-12-18 code/analysis_nbs/ResponseToReviewers.Rmd
working on response to reviewers

@@
 
-```{r}
+```{r message=FALSE, warning=FALSE}
 retest_data %>%
@@
 
-```{r}
+```{r  message=FALSE, warning=FALSE}
 rt_ddm_vars = measure_labels %>%
@@
 
+There are 21 variables with negative point estimate ICC's. This is less than 5% of the measures.
+
 ```{r}
+rel_df %>%
+  mutate(neg_icc = ifelse(icc2.1<0,1,0)) %>%
+  summarise(sum_neg = sum(neg_icc))
+```
 
+### Replacing negative ICC's with 0's
+
+```{r}
+rel_df_rep=rel_df %>%
+  select(dv, task, icc2.1) %>%
+  mutate(icc2.1=ifelse(icc2.1<0,0,icc2.1))
+```
+
+Reliability by task vs survey
+```{r}
+summary(MCMCglmm(icc2.1 ~ task, data=rel_df_rep, verbose=F))
+```
+
+Reliability depending on number of trials
+```{r warning=FALSE, message=FALSE}
+tmp = measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(task == 'task',
+         dv %in% meaningful_vars) %>%
+  left_join(rel_df_rep[,c("dv", "icc2.1")], by = 'dv') %>%
+  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
+  select(-extra_1, -extra_2)
+
+summary(MCMCglmm(icc2.1 ~ num_all_trials, data=tmp, verbose=F))
+```
+
+```{r warning=FALSE, message=FALSE}
+tmp = measure_labels %>%
+  mutate(dv = as.character(dv),
+         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
+  filter(ddm_task == 1,
+         rt_acc != 'other') %>%
+  drop_na() %>%
+  left_join(rel_df_rep[,c("dv", "icc2.1")], by = 'dv')
+```
+
+Comparing contrast vs non-contrast: overall has higher reliability than difference.
+
+```{r}
+summary(MCMCglmm(icc2.1 ~ contrast, data=tmp, verbose=FALSE))
+```
+
+Comparing raw vs ddm in overall estimates
+
+```{r message=FALSE, warning=FALSE}
+summary(MCMCglmm(icc2.1 ~ raw_fit, data=tmp %>% filter(contrast == "non-contrast"), verbose=FALSE))
+```
+
+Comparing raw vs ddm in difference scores
+
+```{r message=FALSE, warning=FALSE}
+summary(MCMCglmm(icc2.1 ~ raw_fit, data=tmp %>% filter(contrast == "contrast"), verbose=FALSE))
+```
+
+### Removing negative ICC's
+
+```{r}
+rel_df_ex = rel_df %>%
+  select(dv, task, icc2.1) %>%
+  filter(icc2.1>0)
+```
+
+Reliability by task vs survey
+```{r}
+summary(MCMCglmm(icc2.1 ~ task, data=rel_df_ex, verbose=F))
+```
+
+Reliability depending on number of trials
+```{r warning=FALSE, message=FALSE}
+tmp = measure_labels %>%
+  mutate(dv = as.character(dv)) %>%
+  filter(task == 'task',
+         dv %in% meaningful_vars) %>%
+  left_join(rel_df_ex[,c("dv", "icc2.1")], by = 'dv') %>%
+  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
+  select(-extra_1, -extra_2)
+
+summary(MCMCglmm(icc2.1 ~ num_all_trials, data=tmp, verbose=F))
+```
+
+```{r warning=FALSE, message=FALSE}
+tmp = measure_labels %>%
+  mutate(dv = as.character(dv),
+         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
+  filter(ddm_task == 1,
+         rt_acc != 'other') %>%
+  drop_na() %>%
+  left_join(rel_df_ex[,c("dv", "icc2.1")], by = 'dv')
+```
+
+Comparing contrast vs non-contrast: overall has higher reliability than difference.
+
+```{r}
+summary(MCMCglmm(icc2.1 ~ contrast, data=tmp, verbose=FALSE))
+```
+
+Comparing raw vs ddm in overall estimates
+
+```{r}
+summary(MCMCglmm(icc2.1 ~ raw_fit, data=tmp %>% filter(contrast == "non-contrast"), verbose=FALSE))
+```
+
+Comparing raw vs ddm in difference scores
+
+```{r}
+summary(MCMCglmm(icc2.1 ~ raw_fit, data=tmp %>% filter(contrast == "contrast"), verbose=FALSE))
 ```
@@
 TODO:
-- extract trial numbers for papers that went in to the lit search and compare to ours
+- [DONE] extract trial numbers for papers that went in to the lit search and compare to ours
 - code pipeline to get reliability with k number of trials
 
-```{r}
+```{r warning=FALSE, message=FALSE}
+tmp1 = lit_review %>%
+  filter(task == "task") %>%
+  select(dv, total_trial_numbers) %>%
+  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.') %>%
+  select(-extra_1, -extra_2) %>%
+  group_by(task_name) %>%
+  summarise(mean_num_trials_lit = mean(total_trial_numbers, na.rm=T))
 
+tmp2 = measure_labels %>%
+  filter(task == "task") %>%
+  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.') %>%
+  select(-extra_1, -extra_2) %>%
+  group_by(task_name) %>%
+  summarise(mean_num_trials_emp = mean(num_all_trials))
+
+tmp2 %>%
+  left_join(tmp1, by="task_name")
 ```

### 2018-12-18 code/analysis_nbs/ResponseToReviewers.Rmd
working on response to reviewers

@@
 Some simple statistical comparisons between the completers (N = 157) and non-completers/non-responders (N = 242-157 = 85) would help characterize this subset of the sample better and provide an additional data quality check.
+
+TODO: Compare invited but not completing
+
+```{r warning=FALSE, message=FALSE}
+mturk_worker_data = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/User_717570_workers.csv')
+
+worker_lookup = read_json('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/worker_lookup.json')
+
+worker_lookup = data.frame(worker_lookup) %>%
+  gather(sub_id, worker_id)
+
+retest_workers = mturk_worker_data %>%
+  select(Worker.ID, CURRENT.RetestWorker, CURRENT.RetestWorkerB2, CURRENT.RetestWorkerB3, CURRENT.RetestWorkerB4, CURRENT.RetestWorkerB5) %>%
+  replace(., is.na(.), 0) %>%
+  mutate(retest_worker = ifelse(CURRENT.RetestWorker+ CURRENT.RetestWorkerB2+CURRENT.RetestWorkerB3+CURRENT.RetestWorkerB4+ CURRENT.RetestWorkerB5>0,1,0)) %>%
+  filter(retest_worker==1) %>%
+  select(Worker.ID) %>%
+  rename(worker_id = Worker.ID) %>%
+  left_join(worker_lookup, by = "worker_id") %>%
+  select(-worker_id)
+```

### 2018-12-18 code/analysis_nbs/ResponseToReviewers.Rmd
working on response to reviewers

--- 2018-12-18 code/analysis_nbs/ResponseToReviewers.Rmd
@@
 Some simple statistical comparisons between the completers (N = 157) and non-completers/non-responders (N = 242-157 = 85) would help characterize this subset of the sample better and provide an additional data quality check.
+
+TODO: How many variables are significantly different than each other between the subjects who have been invited and completed the retest battery and those who have not after FDR correcting for multiple comparisons?
+
+```{r warning=FALSE, message=FALSE}
+mturk_worker_data = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/User_717570_workers.csv')
+
+worker_lookup = read_json('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/worker_lookup.json')
+
+worker_lookup = data.frame(worker_lookup) %>%
+  gather(sub_id, worker_id)
+
+retest_workers = mturk_worker_data %>%
+  select(Worker.ID, CURRENT.RetestWorker, CURRENT.RetestWorkerB2, CURRENT.RetestWorkerB3, CURRENT.RetestWorkerB4, CURRENT.RetestWorkerB5) %>%
+  replace(., is.na(.), 0) %>%
+  mutate(retest_worker = ifelse(CURRENT.RetestWorker+ CURRENT.RetestWorkerB2+CURRENT.RetestWorkerB3+CURRENT.RetestWorkerB4+ CURRENT.RetestWorkerB5>0,1,0)) %>%
+  filter(retest_worker==1) %>%
+  select(Worker.ID) %>%
+  rename(worker_id = Worker.ID) %>%
+  left_join(worker_lookup, by = "worker_id") %>%
+  select(-worker_id)
+
+test_data_522 = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_03-29-2018/variables_exhaustive.csv')
+
+test_data_522 = test_data_522 %>%
+  rename(sub_id = X)
+
+test_data_522_subs = test_data_522$sub_id
+
+test_data_522 <- test_data_522[,names(test_data_522) %in% retest_report_vars]
+
+test_data_522$sub_id = test_data_522_subs
+
+non_completers = retest_workers %>%
+  filter(sub_id %in% retest_data$sub_id==FALSE)
+
+completers = retest_data %>%
+  select(sub_id)
+
+non_completer_data = test_data_522 %>%
+  filter(sub_id %in% non_completers$sub_id)
+
+completer_data = test_data_522 %>%
+  filter(sub_id %in% completers$sub_id)
+
+out_df = data.frame(dv=NA, p_val=NA)
+
+for(i in retest_report_vars[-1]){
+  x = non_completer_data %>% select(i)
+  y = completer_data %>% select(i)
+  tmp = data.frame(dv = i, p_val = t.test(x,y)$p.value)
+  out_df = rbind(out_df, tmp)
+}
+out_df = out_df[-1,]
+
+sum(p.adjust(out_df$p_val, method = "fdr") < 0.05)
+```

### 2018-12-21 code/analysis_nbs/ResponseToReviewers.Rmd
working on response to reviwers

@@
 - [DONE] extract trial numbers for papers that went in to the lit search and compare to ours
-- code pipeline to get reliability with k number of trials
+- [PARTIALLY DONE] code pipeline to get reliability with k number of trials
 
@@
   left_join(tmp1, by="task_name")
+```
+
+```{r}
+script_loader(file='make_rel_df.R', path='SRO_Retest_Analyses/code/helper_functions/')
+
+input_path = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/trial_num/ordered/'
+
+for(i in c(0.25, 0.5, 0.75)){
+  df1 = read.csv(paste0(input_path, 'complete_', as.character(i) ,'_variables_exhaustive.csv'))
+  df1 = df1 %>% rename(sub_id = X)
+
+  df2 = read.csv(paste0(input_path, 'retest_', as.character(i) ,'_variables_exhaustive.csv'))
+  df2 = df2 %>% rename(sub_id = X) %>% 
+    filter(sub_id %in% df1$sub_id)
+
+  numeric_cols = get_numeric_cols(df1, df2)
+
+  subs = df1$sub_id
+
+  df1 = df1[,numeric_cols]
+  df2 = df2[,numeric_cols]
+
+  df1 = df1 %>%
+    select_if(function(col) !is.na(sd(col))) %>%
+    select_if(function(col) sd(col) != 0)
+
+  df2 = df2 %>%
+    select_if(function(col) !is.na(sd(col))) %>%
+    select_if(function(col) sd(col) != 0)
+
+  df1$sub_id = subs
+  df2$sub_id = subs
+
+  cur_rel_df = make_rel_df(t1_df=df1, t2_df=df2, metrics = c("icc2.1", "icc3.k", "var_breakdown"))
+  cur_rel_df$proptrials = i
+  if(!exists('rel_df')){
+    rel_df = cur_rel_df
+  } else{
+    rel_df = rbind(rel_df, cur_rel_df)
+  }
+}
+rm(cur_rel_df)
+```
+
+```{r message=FALSE, warning=FALSE}
+rel_df %>% 
+  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
+  filter(task_name != "columbia_card_task_cold") %>%
+  mutate(task_name = factor(task_name, levels = c("columbia_card_task_hot","go_nogo", "hierarchical_rule", "keep_track","kirby", "ravens"),
+                            labels = c("Columbia Card Task (24)","Go/No-go (200)","Hierarchical Rule (300)", "Keep Track (9)","Kirby (27)", "Ravens (18)"))) %>%
+  ggplot(aes(factor(proptrials), icc2.1, col=task_name, shape=task_name))+
+  geom_point(aes(group=dv))+
+  geom_line(aes(group=dv))+
+  xlab("Proportion of trials")+
+  ylab("ICC 2.1")+
+  theme(legend.title=element_blank(),
+        panel.grid=element_blank())+
+  guides(color = guide_legend(nrow=2))+
+  scale_color_manual(values=c('#762a83','#af8dc3','#e7d4e8','#d9f0d3','#7fbf7b','#1b7837'))
+```
+
+```{r}
+summary(MCMCglmm(icc2.1 ~ factor(proptrials), random=~dv, data = rel_df, verbose=FALSE))
 ```

### 2018-12-21 code/analysis_nbs/ResponseToReviewers.Rmd
added new report for response to reviewers

@@
 library(jsonlite)
+library(MCMCglmm)
 
@@
 rel_df_rep=rel_df %>%
+  left_join(measure_labels %>% select(dv, task), by="dv") %>%
   select(dv, task, icc2.1) %>%
@@
 ```{r warning=FALSE, message=FALSE}
+script_loader('meaningful_vars_data.R', path="SRO_Retest_Analyses/code/workspace_scripts/")
+
 tmp = measure_labels %>%
@@
 rel_df_ex = rel_df %>%
+  left_join(measure_labels %>% select(dv, task), by="dv") %>%
   select(dv, task, icc2.1) %>%
@@
 ```{r}
+rm(rel_df)
+
 script_loader(file='make_rel_df.R', path='SRO_Retest_Analyses/code/helper_functions/')
@@
 
-  df2 = df2 %>%
-    select_if(function(col) !is.na(sd(col))) %>%
-    select_if(function(col) sd(col) != 0)
+  # df2 = df2 %>%
+  #   select_if(function(col) !is.na(sd(col))) %>%
+  #   select_if(function(col) sd(col) != 0)
+
+  df2 = df2[,c(names(df1))]
 
@@
 TODO: How many variables are significantly different than each other between the subjects who have been invited and completed the retest battery and those who have not after FDR correcting for multiple comparisons?
+
+Answer: None.
 

### 2019-01-22 code/SRO_Retest_Analyses.Rmd
rerunning everything with new release

@@
 set.seed(10394839)
-from_gh = TRUE
+from_gh = FALSE
 source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/SRO_Retest_Analyses_Workspace.R')

### 2019-01-22 code/workspace_scripts/SRO_Retest_Analyses_Workspace.R

@@ -16,9 +16,9 @@ if(from_gh){
   
   workspace_scripts = 'https://raw.githubusercontent.com/zenkavi/SRO_Retest_Analyses/master/code/workspace_scripts/'
   
-  test_data_path = 'https://raw.githubusercontent.com/zenkavi/Self_Regulation_Ontology/master/Data/Complete_03-29-2018/'
+  test_data_path = 'https://raw.githubusercontent.com/zenkavi/Self_Regulation_Ontology/master/Data/Complete_12-19-2018/'
   
-  retest_data_path = 'https://raw.githubusercontent.com/zenkavi/Self_Regulation_Ontology/retest_scripts/Data/Retest_03-29-2018/'
+  retest_data_path = 'https://raw.githubusercontent.com/zenkavi/Self_Regulation_Ontology/retest_scripts/Data/Retest_12-19-2018/'
   
   for(file_name in file_names){
     eval(parse(text = getURL(paste0(workspace_scripts,file_name), ssl.verifypeer = FALSE)))
@@ -26,9 +26,9 @@ if(from_gh){
 } else{
   workspace_scripts = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/'
   
-  test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_03-29-2018/'
+  test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_12-19-2018/'
   
-  retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-29-2018/'
+  retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_12-19-2018/'
   
   for(file_name in file_names){
     source(paste0(workspace_scripts,file_name))

### 2019-01-23 code/SRO_Retest_Analyses.Rmd
more figure work

@@
         legend.position = 'bottom',
-        plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0))+
-  labs(caption = str_wrap("FIGURE 2: Correlation between mean reliability estimates for each measure found in the literature with the mean reliability from our data.", width = 120))
+        plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0))
 ```

### 2019-01-23 code/figure_scripts/LitAndBoot_Noise_Ceiling.R

@@ -1,60 +1,39 @@
+if(!exists('fig_path')){
+  fig_path = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/'
+}
+
+if(!exists('from_gh')){
+  from_gh=FALSE
+}
+
 if(from_gh){
   require(RCurl)
 }
 
 source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/figure_scripts/figure_res_wrapper.R')
 
-if(!exists('g_legend')){
-  if(from_gh){
-    eval(parse(text = getURL('https://raw.githubusercontent.com/zenkavi/SRO_Retest_Analyses/master/code/helper_functions/g_legend.R', ssl.verifypeer = FALSE)))
-  }else{
-    source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/g_legend.R')
-  }
-  
-}
-
-if(!exists('g_caption')){
-  if(from_gh){
-    eval(parse(text = getURL('https://raw.githubusercontent.com/zenkavi/SRO_Retest_Analyses/master/code/helper_functions/g_caption.R', ssl.verifypeer = FALSE)))
-  }else{
-    source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/g_caption.R')
-  }
-}
-
 if(!exists('comp_lit_pred_out')){
   comp_lit_pred_out = read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/comp_lit_pred_out.csv')
   
 }
-
 
 tmp = comp_lit_pred_out %>%
   select(-.n, -m_lit, -m_boot, -X) %>%
   gather(key, value) %>%
   separate(key, c("stat", "sample"), sep = "_")
 
-# tmp$stat = as.factor(tmp$stat)
-# levels(tmp$stat) <- c("coefficient", expression(r^"2"))
-
 tmp %>%  
   ggplot(aes(value, fill=sample))+
   geom_density(alpha = 0.5, position='identity', color=NA)+
-  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
   scale_fill_manual(breaks=c("boot","lit"),
                     labels=c("Empirical", "Literature"),
                     name="Predictor",
                     values = c("gray15", "gray75"))+
[…]

### 2019-01-23 code/figure_scripts/LitAndEmpAveCorr.R

@@ -1,0 +1,32 @@
+if(!exists('fig_path')){
+  fig_path = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/'
+}
+
+if(!exists('from_gh')){
+  from_gh=FALSE
+}
+
+source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/figure_scripts/figure_res_wrapper.R')
+
+if(!exists('rel_comp')){
+  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/rel_comp_data.R')
+}
+
+rel_comp %>%
+  mutate(task = factor(task, levels = c("task", "survey"), labels = c("Task", "Survey"))) %>%
+  group_by(dv, task) %>%
+  summarise(mean_lit = mean(retest_reliability),
+            mean_emp = unique(mean_pearson)) %>%
+  ggplot(aes(mean_emp, mean_lit, col=task, shape=task))+
+  geom_smooth(method="lm")+
+  geom_point()+
+  xlim(-0.25, 1)+
+  ylim(-0.25, 1)+
+  ylab("Average Literature\nReliability Estimate")+
+  xlab("Average Empirical Reliability Estimate")+
+  theme(legend.title = element_blank(),
+        legend.position = 'bottom',
+        legend.box.margin=margin(-10,-10,-10,-10),
+        legend.key.size = unit(0.25,"cm"))
+
+ggsave(paste0('LitAndEmpAveCorr_Plot.', out_device), device = out_device, path = fig_path, width = 3.4, height = 2, units = "in", dpi = img_dpi)

### 2019-01-23 code/figure_scripts/LitVsEmp_Measure_Plot.R

@@ -1,3 +1,11 @@
+if(!exists('fig_path')){
+  fig_path = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/'
+}
+
+if(!exists('from_gh')){
+  from_gh=FALSE
+}
+
 source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/figure_scripts/figure_res_wrapper.R')
 
 if(!exists('rel_comp')){

### 2021-11-08 code/SRO_Retest_Analyses.Rmd
path corrections

@@
 from_gh = FALSE
-source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/SRO_Retest_Analyses_Workspace.R')
+library(here)
+workspace_scripts = here('code/workspace_scripts/')
+source(paste0(workspace_scripts,'SRO_Retest_Analyses_Workspace.R'))
 ```

### 2021-11-08 code/workspace_scripts/SRO_Retest_Analyses_Helper_Functions.R

@@ -21,7 +21,7 @@ if(from_gh){
   }
   
 } else{
-  helper_func_path = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/' 
+  helper_func_path = here('code/helper_functions/') 
   for(file_name in file_names){
     source(paste0(helper_func_path,file_name))
   }

### 2021-11-08 code/workspace_scripts/SRO_Retest_Analyses_Workspace.R

@@ -2,8 +2,9 @@
 
 library(tidyverse)
 library(jsonlite)
+library(here)
 
-fig_path = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/'
+fig_path = here('output/figures')
 
 cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
 theme_set(theme_bw())
@@ -24,7 +25,7 @@ if(from_gh){
     eval(parse(text = getURL(paste0(workspace_scripts,file_name), ssl.verifypeer = FALSE)))
   }
 } else{
-  workspace_scripts = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/'
+  workspace_scripts = here('code/workspace_scripts/')
   
   test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_12-19-2018/'
   

### 2021-11-08 code/workspace_scripts/bayesian_models_data.R

@@ -3,16 +3,19 @@
 ## Bayesian models ####
 #########################
 
-icc_by_task_model = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_task_model.rds')
+# icc_by_task_model = readRDS(here('input/icc_by_task_model.rds'))
 
-var_subs_pct_by_task_model = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_subs_pct_by_task_model.rds')
+# var_subs_pct_by_task_model = readRDS(here('input/var_subs_pct_by_task_model.rds'))
 
-var_ind_pct_by_task_model = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_ind_pct_by_task_model.rds')
+# var_ind_pct_by_task_model = readRDS(here('input/var_ind_pct_by_task_model.rds'))
 
-var_resid_pct_by_task_model = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_resid_pct_by_task_model.rds')
+# var_resid_pct_by_task_model = readRDS(here('input/var_resid_pct_by_task_model.rds'))
 
-icc_by_num_trials_model = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_num_trials_model.rds')
+icc_by_num_trials_model = readRDS(here('input/icc_by_num_trials_model.rds'))
 
-icc_by_rawfit_noncon_model = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_rawfit_noncon_model.rds')
+icc_by_rawfit_noncon_model = readRDS(here('input/icc_by_rawfit_noncon_model.rds'))
 
-icc_by_rawfit_con_model = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_rawfit_con_model.rds')
+icc_by_rawfit_con_model = readRDS(here('input/icc_by_rawfit_con_model.rds'))
+
+icc_by_contrast_model = readRDS(here('input/icc_by_contrast_model.rds'))
+

### 2021-11-08 code/workspace_scripts/boot_rel_data.R

@@ -29,7 +29,7 @@ if(!exists('grabRemoteGz')){
   if(from_gh){
     eval(parse(text = getURL('https://raw.githubusercontent.com/zenkavi/SRO_Retest_Analyses/master/code/helper_functions/grabRemoteGz.R', ssl.verifypeer = FALSE)))
   }
-  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/grabRemoteGz.R')
+  source(here('code/helper_functions/grabRemoteGz.R'))
 }
 
 if(!exists('retest_report_vars')){
@@ -39,7 +39,7 @@ if(!exists('retest_report_vars')){
   retest_report_vars = c(names(tmp1), names(tmp2), names(tmp3))
   retest_report_vars = unique(retest_report_vars)
   if(!exists('lit_review')){
-    source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/lit_review_data.R')
+    source(here('code/workspace_scripts/lit_review_data.R'))
   }
   lit_rev_vars = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% retest_report_vars == FALSE)])
   retest_report_vars = c(retest_report_vars, lit_rev_vars)

### 2021-11-08 code/workspace_scripts/lit_review_data.R

@@ -6,7 +6,7 @@ if(from_gh){
   require(RCurl)
   lit_review <- read.csv('https://raw.githubusercontent.com/zenkavi/SRO_Retest_Analyses/master/input/lit_review_figure.csv')
 }else {
-  lit_review <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/lit_review_figure.csv')
+  lit_review <- read.csv(here('input/lit_review_figure.csv'))
   }
 
 require(tidyverse)

### 2021-11-08 code/workspace_scripts/measure_labels_data.R

@@ -2,7 +2,7 @@ if(from_gh){
   require(RCurl)
   input_path = 'https://raw.githubusercontent.com/zenkavi/SRO_Retest_Analyses/master/input/'
 }else{
-  input_path = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/'
+  input_path = here('input/')
 }
 
 #########################

### 2021-11-08 code/workspace_scripts/rel_comp_data.R

@@ -2,4 +2,4 @@
 ## Reliability Comparison data ####
 #########################
 
-rel_comp <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/rel_comp.csv')
+rel_comp <- read.csv(here('input/rel_comp.csv'))
